### 2021-02-18 Paper.rmd
Added rmd

---
title: "Depression and suicidality as costly signals of need"
author: "Michael Gaffney, Kai Adams, Kristen Syme, and Edward Hagen"
date: "2/18/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2021-02-18 analysis.R

@@ -361,3 +361,67 @@ summary(out)
 plot(out)
 
 # mediation_model <- mediate(model.m, model.y, treat = 'signal', mediator = 'delta_needs_money', boot = T)
+
+d_mediate <-
+  d %>%
+  dplyr::filter(
+    signal %in% c(
+      'Depression',
+      'Suicide attempt')
+  ) %>%
+  mutate(
+    signal = factor(signal, levels = c('Depression', 'Suicide attempt'))
+  )
+
+mmediator <- lm(T2Belief ~ signal + T1Belief + vignette + Sex, d_mediate)
+mout <- lm(T2Action ~ signal + T2Belief + T1Action + T1Belief + vignette + Sex, d_mediate)
+
+out <- mediate(mmediator, mout,treat = "signal", mediator = "T2Belief")
+
+summary(out)
+plot(out)
+
+# to do: moderated mediation model
+
+d_mediate <-
+  d %>%
+  dplyr::filter(
+    signal %in% c(
+      'Verbal request',
+      'Depression'),
+    vignette != "Thwarted marriage"
+  ) %>%
+  mutate(
+    signal = factor(signal, levels = c('Verbal request', 'Depression'))
+  )
+
+mmediator <- lm(T2Belief ~ signal + T1Belief + vignette, d_mediate)
+mout <- lm(T2Action ~ signal + T2Belief + T1Action + T1Belief + vignette, d_mediate)
+
+out <- mediate(mmediator, mout, treat = "signal", mediator = "T2Belief")
+
+summary(out)
+plot(out)
+
+
+
+d_mediate <-
+  d %>%
+  dplyr::filter(
+    signal %in% c(
+      'Depression',
+      'Suicide attempt'),
+    vignette != "Thwarted marriage",
+    Sex == "Male"
+  ) %>%
+  mutate(
+    signal = factor(signal, levels = c('Depression', 'Suicide attempt'))
+  )
+
+mmediator <- lm(T2Belief ~ signal + T1Belief + vignette, d_mediate)
+mout <- lm(T2Action ~ signal + T2Belief + T1Action + T1Belief + vignette, d_mediate)
+
+out <- mediate(mmediator, mout, treat = "signal", mediator = "T2Belief")
+
+summary(out)
+plot(out)

### 2021-02-18 Paper.rmd
Added MA text to rmd

@@
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-```
+# Abstract
 
-## R Markdown
+Due to the fact much of major depression research often focuses on methods of treatment or causal explanations emphasizing the role of psychological malfunctions, the responses of others to the depressed are largely overlooked.
+Although such responses are of little use to such explanations, the potential ability for depression to elicit positive changes in social relationships through signaling honest need has been suggested as way depression could be adaptive, making responses to it a critical piece of evidence.
+To examine if depression often comes with social benefits, we compared it to other proposed signals of need in a vignette study that also manipulated the amount and type of information about whether one’s need was honest and the presence of conflict within an imagined relationship.
+Overall, we found evidence for the predicted interaction between signal type and conflict on relationship outcomes as well as the predicted main effects of information and conflict.
+Contrary to our predictions, costlier signals did not result in more positive responses across signal types, with there also being little evidence in favor of the predicted signal by information interaction.
+However, depression outperformed all the other proposed signals of need on our four outcome measures across social circumstances, and our predicted relationships for the signals as a whole were largely supported when looking solely at the verbal request, crying, and depression manipulations.
+This suggests that depression is a relatively successful way of demonstrating honest need and eliciting support, consistent with signaling explanations.
 
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
+# Introduction
 
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
+Long considered pathological sadness, depression has gained increased attention for its potential to function as a signal of need capable of bringing about positive changes in social relationships [@Hagen2002; @Hagen2003].
+Referred to as the bargaining model of depression, this view shares much in common with signaling explanations for crying [@Hasson2009; @HendriksEtAl2008], self-harm [@HagenEtAl2008], suicide attempts [@Rosenthal1993; @SymeEtAl2016], and illness symptoms [@Steinkopf2015; @Tiokhin2016], all of which view the costs involved as a key component of eliciting important social support.
+Based mainly in signaling theory, such approaches have all benefited greatly from economics and game theory, with the result being explanations for the existence of such states that emphasize the causal role of one’s social environment rather than simply focusing on one’s internal state.
 
-```{r cars}
-summary(cars)
-```
+Due to the similarities between the ways in which they are suggested to achieve their hypothesized functions, there is much to be gained by comparing depression to the other proposed signals of need to better understand both the situations that bring them about and what determines differences in how they are responded to.
+In doing so, it should be possible to identify the fundamental similarities they share and create testable hypotheses that transcend signal type and, therefore, have the potential to further influence costly signaling theory.
 
-## Including Plots
+Of all their similarities, the most basic is that positive responses are frequently expected so that the benefits received outweigh the costs involved on average.
+However, such responses are underexamined relative to the predictors of the symptoms involved and potential treatments, something which is especially true of depression [@BillingsMoos1985] due to the suffering it causes to those who have it.
+The result of this is that one of the most important lines of evidence for an oftentimes adaptive explanation for depression and the other proposed signals of need is largely missing.
 
-You can also embed plots, for example:
+# Thesis Outline
 
-```{r pressure, echo=FALSE}
-plot(pressure)
-```
+In this thesis, I briefly review the evidence for why the proposed signals of need are unlikely to solely be the result of malfunctions before reviewing the basics of signaling theory that tie them all together.
+I then review depression and how adaptive and nonadaptive approaches differ in their casual explanations.
+After examining the other proposed signals of need, I explore the empirical work that has been done on responses to the proposed signals before examining what should be expected from signaling theory.
+Lastly, I report the findings of a vignette study conducted with Edward Hagen examining if the proposed signals of need result in positive responses in the situations predicted by the previously mentioned signaling explanations.
 
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
+# Opposition to adaptive explanations and initial indications they are adaptive
+
+In general, the dominant view of the proposed signals of need is that they are symptoms of harmful byproducts or malfunctions.
+Likely the main reason for this is the harm they cause the one experiencing them, which can be quite severe with the costlier signals [@Kessler2012].
+However, subjective suffering and negative fitness outcomes are not inextricably linked.
+This is most obviously seen with negative emotions motivating fitness enhancing behavioral shifts, as is widely recognized to be the case with hunger, thirst, or pain [@Nesse1990; @ToobyCosmides2008].
+Just as these explanations attribute a functional role to negative experiences, the costs of proposed signals of need are suggested to be adaptive for their ability to increase the confidence of others who may be motivated to help that one’s need is genuine in ways non-costly displays could not [@Hagen2003; @Rosenthal1993; @SymeEtAl2016].
+
+However, to this point, the evidence suggesting that the proposed signals of need are adaptive comes primarily from outside indications of increased social support.
+For example, major depression [@BrometEtAl2011; @KesslerEtAl2010], suicide attempts [@CDC2014], placebo responses [@Humphrey2002], and crying [@vanHemertEtAl2011] are all more common than should be expected of maladaptive malfunctions due to the likelihood of strong selection pressures against those who incur extra costs in times of need.
+For the proposed signals of need to still be maladaptive with this prevalence, the traits responsible for such malfunctions would likely have to result primarily from environmental mismatches [@Hidaka2012] or pleiotropic traits in which major benefits come from the genes responsible for the proposed signals of need [@Williams1957].
+However, neither situation is safe to assume due to the proposed signals of need being found across a wide range of environments and social settings [@BrometEtAl2011; @SymeEtAl2016] and the fact that genetic modularity often results in the potential of other genes to limit the negative effects of pleiotropy while preserving the benefits in polygenic traits [@Hansen2003].
+
+Another important indication that the proposed signals of need are often the result of the result of functional mechanisms is the fact they tend occur when individuals are in need and can benefit from others.
+This is seen in both depression and suicide attempts occurring most frequently in times of social adversity in which individuals are experiencing costs due to the actions of others or the loss of existing social relationships [@Hammen2005; @Mazure1998; @SymeEtAl2016].
+Likewise, placebo responses, which have been proposed to be the downregulation of signaling through increased illness symptom severity [@Steinkopf2015; @Tiokhin2016], often happen in response to individuals receiving support after feeling a lack of it in conjunction with perceived need [@Humphrey2002].
+Although not evidence of increased support, this connection between the proposed signals of need and times of need suggests that malfunction cannot be safely assumed as long as there are those around who would be motivated to help.
+
+# Social support in humans
+
+Such a scenario in which costly emotional states lead to increased benefits is possible due to the degree to which humans cooperate with another, something which was necessary for our survival over much of our evolutionary history and is reflected in our adaptations today [@SugiyamaSugiyama2003].
+Unlike most species, this support can often come from a wide range of individuals in humans, with kin beyond parents playing an important role in childcare across generations [@KaplanEtAl2009; @Meehan2005; @SearMace2008] and unrelated individuals often helping in a wide range of situations due to the benefits of both direct and indirect reciprocity as well as reputation gains [@Alexander1987; @Barclay2013; @JaeggiGurven2013].
+The result of these benefits is a situation in which many individuals may be potential targets of a costly signaling strategy.
+
+While important at almost any time, cooperation is especially important in times of need.
+Illness, injury, and physical conflict with others have all been recurrent problems over the course of human evolution, with their outcomes often resulting in times in which individuals could not survive without short-term support [@SugiyamaChacon2000].
+In these times, help often takes the form of temporary increases in provisioning or labor to decrease the workload of the ill [@SugiyamaSugiyama2003].
+However, evidence of long-term support also exists with both Neandertals and modern humans being known to help those who are disabled [@TrinkausVillotte2017].
+Beyond showing that such cooperation does not rely solely on expectations of direct reciprocity, the presence of long-term support for those who are unlikely to recover, together with the fact that humans can often reliably find support in times of need, suggests that lasting changes might be possible in times of need outside of instances of disability.
+
+However, despite the likelihood of individuals benefiting from increasing their support of others in times of need and the widespread evidence that it often happens, devoting a large amount of resources to another is only likely to be worth it if the need is genuine.
+It is in these instances when the proposed signals of need are expected to be adaptive, as long as the result is an increase in the likelihood of support due to the signal enhancing one’s appearance of need and the benefits outweighing the costs of producing the signal [@Zahavi1993].
+Although this limitation precludes the costlier signals from being adaptive in relatively minor instances of need, it does rule out adaptive explanations in times when one’s need is great and unlikely to be believed.
+
+# Costly Signaling
+
+All organisms can benefit from altering the behavior, physiology, and psychological states of others, something which is seen from single celled organisms to social animals [@Dawkins1982].
+Such changes can be accomplished through chemical or behavioral means, with information flowing from the signaler to the receiver in ways meant to benefit the one sending the message, regardless of whether or not it benefits the one receiving it [@Dawkins1976].
+In social animals, members of one’s own species are often the target, with sexual selection and intrasexual competition creating many situations in which one’s reproductive success depends greatly on the responses of others [@Clutton-BrockHuchard2013; @DalyWilson1983].
+The results of this are strong selection pressures favoring those who can make the most of these opportunities to outcompete others and receive the largest benefits through both cooperation and competition.
+
+Of the strategies used to influence the behavior of conspecifics, costly signaling to provide believable information about one’s quality or current state is likely to be one of the most common and effective ways to do so [@Zahavi1975].
+A signal differs from a cue in that it is intentionally sent by an organism to alter the behavior or thoughts of other individuals, while a cue is any piece of information an organism uses to alter its behavior or physiological state that was created without the intent to do so [@MaynardSmithHarper1995].
+Since signals are created for the purpose of communication, they are by definition easy to fake, especially in situations where they can be disconnected from the qualities being signaled [@Zahavi1975].
+This coupled with the selection pressures resulting from the fact that conflicts of interest are ubiquitous among living things [@Trivers1974; @Zahavi1993] means that there is much to gain from successfully faking a signal as one could receive the benefits without paying the costs associated with the underlying quality.
+For this reason, strong selection pressures exist favoring adaptations to spot fake signals, something which has been shown to exist in many species [@Hasson1994].
+
+To overcome such counter-adaptations to cheating, an organism may produce a signal that cannot be achieved without meaningful costs in order to increase the believability of the signal [@Zahavi1975].
+The result of such signals are relatively honest displays compared to those which involve lesser costs so long as the costs involved with the signal make the signal only worth producing for those who have the underlying qualities associated with the signal [@Zahavi1993].
+Although originally formulated as an explanation for the role of costly traits in attracting mates (i.e.
+colorful plumage or large physical weaponry) [@GangestadScheyd2005; @Zahavi1975], there is no reason why it cannot be applied to the proposed signals of need as long as their costs are prohibitively high for those who are not in need.
+
+# Depression
+
+Of all the proposed signals of need, major depression has received the most attention and likely causes the most suffering.
+Although often overlooked due to its indirect connection with mortality [@PatelEtAl2004], it is the leading cause of nonfatal disease burden in the world and the second greatest contributor to global years lost to disability [@FerrariEtAl2013; @SlavichIrwin2014].
+Around 8% of people in the U.S.
+experience major depression each year, and almost 20% will experience major depression in their lifetime [@KesslerEtAl2010].
+In general, similar prevalences are often reported for depression as a whole, with there being some evidence that it is more often diagnosed in developed countries [@BrometEtAl2011].
+However, in no country is there a good understanding about how people respond to the depressed.
+
+Major depression typically involves a large-scale reduction in activity along with persistent negative feelings [@FriedNesse2014].
+These symptoms take many forms but generally fall into the categories of insomnia, weight loss, fatigue, agitation, attention problems and feelings of worthlessness.
+As these symptoms can accompany normal sadness, length is primarily used to distinguish it from minor depression, with DSM-5 requiring the existence of at least five symptoms for at least two weeks [@AmericanPsychiatricAssociation2013].
+However, it often also differs in severity, as is seen with depression’s connection to increased suicidal ideation [@BostwickPankratz2000].
+From an evolutionary perspective, it can be described as partial to complete abandonment of normally fitness enhancing behavior that also results in a reduction of benefits one provides to others [@Hagen2003].
+
+In  addition to these symptoms used by DSM-5, depression is often associated with impaired social functioning [@HirschfeldEtAl2000].
+Although causality is likely to go both ways, such impairments encompass almost the totality of social functioning with depressed individuals having smaller social groups, being more likely to perceive social interactions as negative, and having lower levels of social support [@GotlibLee1989].
+Beyond simply being a symptom of depression, a lack of improvement in various measures of social functioning is also associated with reduced chances of remission [@BillingsMoos1985], although even those who return to a non-depressed state may still have lower measures of social functioning than healthy controls [@WeissmanPaykel1974].
+
+Regardless of the exact combination of symptoms, most cases of depression are closely tied to major negative life events [@Hammen2005].
+This is clearly seen when comparing those with depression other groups, with depressed individuals often reporting at least twice as many instances of negative events than nondepressed individuals [@Mazure1998] and more negative events than those mental disorders like schizophrenia and bipolar disorder across a wide range of studies [@Paykel1994].
+In addition to differences in recent experience, the connection between negative events and depression is also seen in the high percentage of depression cases that are preceded by negative events and the rapid onset of depression following the event, both of which are seen in a largescale study of female twins that found 80% of depression cases were preceded by at least one negative life event and symptoms tending to occur within one month of the event [@KendlerEtAl1999].
+
+This strong connection between negative life events and depression along with the need and distress that likely accompanies these events has led to the suggestion that this relationship is causal [@KendlerEtAl1999].
+Support for this comes from the fact that the relationship between negative events and depression holds true when looking solely at events outside of one’s control, which shows that the connection is unlikely to be driven solely by depressed individuals creating situations where negative events are likely to be common [@Hammen2005; @KendlerEtAl1999].
+In addition to this, twin studies have shown that one’s history of negative events is still a strong predictor when controlling for genetic similarity and that part of the heritability of depression stems from the heritability of negative events, like divorce and family conflict [@KendlerBaker2007; @KendlerEtAl1999].
+
+Of the many types of negative life events associated with depression, those which involve social adversity tend to be more strongly associated with depression [@Hammen2005; @KendlerEtAl1999; @Mazure1998].
+Like the relationship between negative events as a whole and depression, this relationship is also seen cross-culturally, with the loss of a loved one, threat of divorce, or abusive relationships all increasing one’s chances of becoming depressed [@KendlerEtAl1999; @KendlerEtAl1995].
+Of these predictors, physical assault has been found to be the strongest predictor of depression in the few studies in which it has been examined [@KendlerEtAl1999; @KendlerEtAl1995] and may have been much more common throughout our evolutionary history than is often thought based on rates of spousal abuse in small-scale societies [@StieglitzEtAl2011].
+
+Except for the loss of a loved one, conflict is likely to often be present in all the previously mentioned forms of social adversity and may be one of the most meaningful aspects in bringing about depression.
+For example, breakups in both romantic and cooperative relationships are often preceded by conflict [@AmatoHohmann-Marriott2007], and surely contain it when one side wants reconciliation and the other does not.
+Likewise, abusive relationships are bound to be conflictual, with one side holding the power to harm the other and doing so.
+When looking solely at conflict as a predictor, it is often reported to be linked with depression [@AsgeirsdottirEtAl2011], with both conflict without abuse and conflict among family members also being strong predictors of depression in Western societies [@KendlerEtAl1995].
+Although too few studies exist outside of Western societies to be sure of the generalizability of this, initial studies are consistent with this, with conflict outside of the family being a predictor of depression among the Tsimané [@StieglitzEtAl2015].
+
+# Nonadaptive explanations
+
+Explanations for the relationship between social adversity and depression often involve the malfunction of mechanisms relating to low mood, which is almost universally considered adaptive when it functions properly [@Hagen2003; @Nesse1999; @WakefieldFirst2012].
+One influential version of this is the stress-diathesis model , which suggests that stressful situations interact with one’s predisposition to depression to bring about depressive symptoms [@MonroeSimons1991].
+In general, such approaches do not make distinctions between different types of stress and their effects on risk of depression nor do they predict different outcomes based on variables outside of stress levels and personality differences.
+From this perspective, the social adversity often associated with depression may simply be one way for extreme levels of stress to accumulate thereby turning what would normally be short-term sadness into long-term depression.
+
+Such approaches also generally do not make predictions on the types of responses the depressed are likely to receive, although there are exceptions.
+This is due in large part to the previously mentioned costs involved, which shift the focus of most research towards treatment [@PatelEtAl2004] and increases the size of the benefits needed for it to adaptive.
+When predictions are made about responses, they tend to involve depression resulting in negative responses due to strain the depressed’s anhedonia and impaired social functioning puts on relationships [@Coyne1976].
+From these perspectives, the costs of depression are simply too great to warrant a focus on the positive responses or too unexpected to be examined.
+
+# The bargaining model of depression
+
+Unlike these approaches, the bargaining model of depression emphasizes both the roles of social adversity and potential benefits in its explanation for why most instances of depression happen [@Hagen2002 ;@Hagen2003].
+It views depression as an oftentimes adaptive response to social adversity or other hardships in which support from others or more beneficial cooperative relationships can be gained.
+Since any biological mechanism can fail, maladaptive cases of depression are still expected to exist under this model [@Hagen2011].
+However, in many instances, it is expected to serve as a viable option to elicit more social support for those who may have few other options.
+
+The bargaining model of depression is based on the idea that for much of our evolutionary history the small groups humans lived in created many situations in which certain forms of cooperation were unlikely to be easily replaced by others while also allowing for harmful or unfair social relationships to develop [@Hagen2003].
+In these instances, one’s monopoly on one or more types of cooperation could be leveraged to change how one is treated if others value the depressed’s cooperation enough and view the depressed as being in honest need.
+In other words, depression could function similarly to a labor strike, demonstrating that one’s need was genuine; and that if the target of the signal wanted to continue receiving benefits from the depressed, he or she would need to increase support towards the signaler.
+
+Like with the other proposed signals, the costs experienced by the depressed play an important role in its function as an indicator of honest need [@Hagen2003].
+As previously mentioned, depression often involves substantial psychological pain and a largescale reduction in one’s normal routine of fitness enhancing behavior.
+This means that depression is likely unprofitable to fake as the costs involved are likely only worth experiencing by those who have high levels of need, thereby increasing the confidence of others that the signal is honest as is suggested with the other costly signaling hypotheses.
+Importantly, these costs only need to be maintained until the signaling function is thought to be met, with symptoms being expected to subside shortly after indications that future changes in social support are likely to come.
+This increases the chance that the benefits received will outweigh the costs relative to explanations that require continuous signaling and results in clear predictions about why depression ends when it does.
+
+Despite predicting many cases of depression to stem from situations in which it was adaptive ancestrally, the bargaining model does not suggest that depression should go untreated.
+This is because adaptation is not to be confused with subjective wellbeing, which is a much more important concern in every area except for explanations of why depression exists [@CosmidesTooby1999].
+However, it does suggest an explanation for why most medical treatments perform similarly to cognitive therapy [@HollonEtAl2005] and placebos [@WalshEtAl2002] in that all three methods demonstrate the existence of a knowledgeable medical professional giving active support to the depressed.
+In other words, such treatments may provide sufficient cues that the signal has worked, even though none may treat the underlying cause.
+
+# Other proposed costly signals of need
+
+As previously mentioned, the bargaining model of depression is not unique as an oftentimes adaptive explanation for harmful symptoms, with crying [@Hasson1994; @HendriksEtAl2008], self-harm [@HagenEtAl2008], suicide attempts [@Rosenthal1993; @SymeEtAl2016], and illness symptoms [@Steinkopf2015; @Tiokhin2016] having all been argued to signal need.
+
+Of these proposed signals, self-harm and suicide have the most in common with depression.
+Both are much more common for their costs than should be expected for malfunctions [@HagenEtAl2008], with suicide attempts being found across a wide range of cultures [@SymeEtAl2016; @WeissmanEtAl1999].
+As with depression, self-harm and suicide attempts tend to come in times of social adversity like divorce or neglect, both of which are situations when it is likely that social support is both greatly needed and difficult to obtain [@HagenEtAl2008].
+This connection to social adversity is clearly seen among instances of suicide attempts in the HRAF database, in which 77.4% of attempts were found to be linked to times of social conflict, and 88.7% were linked to fitness threats in general [@SymeEtAl2016].
+Importantly, 84.9% of attempts were linked to situations in which attempters were powerless to resolve their situation alone [@SymeEtAl2016], further indicating its potential as a signal of need in times when other less costly methods of bargaining are less likely to be successful, assuming the benefits are large enough on average.
+
+Unlike depression, where the costs are directly felt by the signaler and his or her targets, the bulk of the costs associated with suicide attempts are only felt in times that result in death or severe bodily harm.
+For this reason, the way others view and respond to suicide attempts is likely to be strongly influenced by the probability that the attempt would have been successful [@Rosenthal1993].
+Differences in these probabilities result primarily from the method of the attempt, which can range from little to no risk to almost certain death [@Weiss1957].
+Of the possible risk values on this continuum, the best candidates for bargaining are those in which there is a “non-negligible” but relatively unlikely chance of death [@Rosenthal1993] as those which involve minimal risk are likely to be thought of as manipulative and those which are riskier than need be not being what is expected of fine-tuned adaptations.
+Therefore, a key prediction of the bargaining model of suicide is that attempts should often result in the attempter surviving [@SymeEtAl2016].
+This is clearly the cases across the world, with attempts that do not result in death far outnumbering those that do [@CDC2014] and individuals often choosing less risky forms of suicide when methods with higher probabilities exist (i.e.
+overdosing on pills instead of jumping off of a tall building) [@Rosenthal1993].
+
+Of the proposed signals, crying has the longest history of being examined as a signal which often results in benefits and is the least controversial due to its low costs [@HendriksEtAl2008].
+For example, infant crying is almost always considered adaptive, although how it functions to elicit support is still debated, with many proposed explanations involving functions outside of signaling honest need like demonstrating quality, blackmailing parents through increased risk of predation, or manipulating parents into investing less in other offspring [@Lummaa1998].
+However, like the other proposed signals of need, it is more common when one is in need and can benefit from the support of others.
+This is seen both observationally, with crying bouts being shorter in cultures which have higher levels of parent-offspring contact [@Lummaa1998] and experimentally, with longer crying bouts being associated with shorter holding times [@HunzikerBarr1986].
+
+Like infant crying, adult crying is a human universal, with emotional tears likely being unique to humans [@HendriksEtAl2008a].
+Due to differences in what motivates support as well as differences in both the prevalence and the costs involved, it is likely that adult crying often differs from infant crying in both function and the many of the underlying psychological mechanisms.
+However, in both infants and adults, crying is an effective signal that something is wrong, with tear production and the facial sadness that often accompanies crying both increasing the perception of sadness by others [@Hasson2009] and humans being well equipped to distinguish tears of joy from tears of sadness [@HendriksVingerhoets2006].
+
+Unlike the other proposed signals of need, adult crying is frequently reported to occur without a specific external referent, with even the crier often left to wonder why it happened when it did [@VingerhoetsEtAl2000].
+However, when looking solely at bouts of crying that can be traced to a cause, it is clear that social factors are the strongest predictors, especially when conflict or loss is involved [@VingerhoetsEtAl2000; @Young1937].
+In addition to showing that crying appears in the right contexts for it to potentially be adaptive, the fact that tears which can be traced to a cause rarely occur outside of times of social need hints that it is often an honest signal.
+In line with this reasoning, the absence of an effective sadness display has been shown to reduce supportive behavior, suggesting that properly displaying sadness (with which crying helps) increases the confidence of others that one is in need [@Barr-Zisowitz2000; @Diminich2016].
+However, the fact that adults often cry out of sight of others suggests that its occurrence cannot be explained solely by a signaling explanation [@VingerhoetsEtAl2000].
+
+Compared to depression, self-harm, and suicide attempts, the costs of crying are much less severe, and it is unclear if its costs are significant enough to result in honest displays on their own [@Hasson2009].
+One important area in which the costs of crying are likely to be felt is through reputation hits, with crying often lowering how others view a person  [@HendriksVingerhoets2006].
+While true of both sexes, this may be particularly true if the target of the signal is a man, as men have been shown to simply avoid crying people more often than women in experimental settings.
+Although not directly linked to crying, sadness, which almost certainly accompanies most instances of crying, tends to slow both cognitive and motor functioning [@Diminich2016; @Ekman2003; @EllgringScherer1996] thereby imposing at least some opportunity costs surrounding and during bouts of crying, something that may be directly seen with the blurred vision that comes with tears [@Hasson2009].
+When sadness is already present, crying may simply exacerbate this distress, as is seen physiologically with the increased hearts rate and blood pressure that typically accompanies crying taking time to return to normal levels after crying [@HendriksEtAl2008]
+
+Although tied to a different type of need and not included in the study presented here, illness symptoms provide another strong candidate as a way for costly symptoms to function as a signal of need and are, therefore, worthy of being included in this comparison.
+Referred to as the signaling theory of symptoms, the idea is that while illness symptoms initially arose as the result of defenses against disease or a pathogen’s circumvention of these defenses, they quickly became cues for conspecifics to alter their behavior to better avoid illness, take advantage of a rival’s weakened state, or help kin and close allies [@Steinkopf2015; @Tiokhin2016].
+Although the first two conditions would likely favor the suppression of symptoms, times in which help could be received may have favored times in which symptoms would become signals of honest need as opposed to just cues.
+The reason for this is once strategies for providing support to the sick became common enough, selection would likely favor those who could fake symptoms, which would then favor anti-cheating adaptations that require symptoms that were hard to fake to be believed.
+In these instances, those who upregulated already present symptoms beyond the optimum for disease fighting would provide a more honest, costly signal and, therefore, be more likely to satisfy the anti-cheating adaptations of others and increase their chances of receiving aid.
+
+Formulated as an explanation for placebo responses, the best evidence in favor of the signaling theory of symptoms comes from the observation that placebo responses tend to occur after signs that care has been given, with the placebo response simply being viewed as the return to symptom levels appropriate for disease fighting without the added signaling component [@Steinkopf2015].
+Therefore, like the other proposed signals of need, its occurrence is expected to be highly dependent on social context in both predicting its occurrence and its cessation.
+This is seen experimentally in that placebo responses which often work in the presence of healthcare providers can be completely negated if the person is instructed to complete their treatment alone [@HashishEtAl1988].
+However, presence alone is also not enough, as should be expected of a signaling explanation.
+Instead, demeanor is also highly important, with facial expression indicating care and concern resulting in more placebo responses than neutral or disinterested faces [@Benedetti2009; @Steinkopf2015].
+
+# Key similarities shared by the proposed costly signals of need
+
+Viewed collectively, the proposed signals of need clearly share some important similarities which can allow for generalizations about when they should be most common and under which situations they are most likely to be adaptive.
+When it comes to prevalence, their hypothesized functions as signals suggests they should all be more common when there is a high degree of private information held by the signaler (i.e.
+when the targets of the signal do not have information about the honesty of need) [@Hagen2003].
+This is due to the previously mentioned ubiquity of conflicts of interest, which incentivizes deception and favors strategies in which individuals are only likely to increase their support of others if their counter-cheating adaptations are satisfied.
+For this reason, signals should be more common when the target has little information to confirm the signaler is in need and less common when such information exists as the signaling component of any trait or state is created primarily to provide another organism with information.
+Indeed, in instances of public information, the expectation is that both parties should be able to bargain quickly as there is nothing in the way of both sides figuring out how the benefits should be divided [@KennanWilson1993].
+
+One basic similarity that allows for more detailed predictions is that all the proposed signals are predicted to result in benefits that make up for the costs involved, at least on average.
+Although this seems more relevant to what happens after the signal, it also has important implications for when signals might be employed since smaller forms of support are likely to be sufficient for the less-costly signals to be worth it, with the costlier signals requiring larger gains all else being equal.
+Therefore, it is reasonable to expect the less costly signals to be more common, something which is seen with instances of crying far outnumbering cases of depression, which far outnumbers the cases of suicide attempts [@KesslerBromet2013; @NockKessler2006; @vanHemertEtAl2011].
+
+One way to reduce the average costs of the proposed signals, and therefore increase the times which they may be applicable, is to only engage in them in situations where large payoffs are relatively likely [@Rosenthal1993].
+Although little has been done to investigate the existence of such mechanisms, it is a reasonable trait to expect of the proposed costly signals of need if they are adaptive.
+This is because the absence of such systems would decrease the amount of ways the proposed signals could have evolved as adaptations due to the role selection would play in disfavoring strategies that led to dangerous misfires and worsened conditions in times in which such outcomes may be the costliest.
+Without these mechanisms, the adaptive nature of the proposed signals of need may be confined only to times of extreme need, as such situations may reduce the costs of signaling to such an extent that the relevance of the likelihood of support to levels where it becomes much less relevant [@HagenEtAl2008; @Tiokhin2016].
+
+Evidence for this may be seen with findings that suggest that some of the proposed costly signals of need are more common in situations where they are more culturally acceptable and where help may be more available.
+For example, the size of the female biased sex difference in depression was found to differ in relation to gender equity, with more equitable societies experiencing larger gender gaps despite overall lower rates of depression [@HopcroftBradley2007].
+This same pattern is seen with crying, with women crying more often in countries with greater gender equality, something which clearly runs counter to models which emphasize the causal role of stress overloads [@vanHemertEtAl2011].
+One possible reason for these relationships is that women in more equal societies signal more because they are more likely to receive support.
+Consistent with this interpretation is the fact that while crying tends to not result in improved emotional states in general [@HendriksEtAl2008], it does result in women feeling better after crying in countries with relative equality [@BechtVingerhoets2002] and when social support is present [@RottenbergEtAl2008].
+
+In addition to not engaging in a signaling strategy that is likely to result in insufficient support, only investing in a signal of need when one does not have any less costly alternative options is another likely way to reduce the average costs of the proposed signals.
+This prediction is clearly built into the unified model of anger and depression, which proposes that anger and depression may be complementary strategies, with aggression being favored by those who have the formidability to bargain effectively through the use of force and depression favored by those that cannot [@HagenRosenstrom2016].
+Support for this comes from the finding that differences in upper body strength account for much of the female biased sex difference seen in depression.
+Importantly, this sexually dimorphic pattern of women experiencing depression symptoms more often than men is also seen in all the other proposed costly signals examined here [@CDC2014; @vanHemertEtAl2011], suggesting that less costly bargaining methods are reliably favored, assuming there is a similar scarcity of alternatives for women relative to men.
+
+Although not derived from the similarities of the theories explored here in the same way as the previous traits, a key similarity shared by the signals is that the costs associated with signaling will almost always be less than the costs of the symptoms themselves since some level of symptomology is likely to be present that is not tied to a signaling function.
+In other words, the cost of engaging in a costly signal of need is often going to be less than the symptoms the recipient sees.
+This is clearly seen with illness symptoms if the signaling theory of symptoms is correct, in that much of one’s symptoms will be the result the body’s defense mechanisms or a pathogens circumvention of these defenses even in instances in which they are upregulated for a signaling function [@Steinkopf2015; @Tiokhin2016].
+Therefore, the costs of signaling may only be a small part of the totality of the symptom.
+Although such a situation is harder to imagine with depression or suicide attempts, extreme cases of conflict or abuse may result in situations in which the difference between a depressed and a nondepressed state may be much closer than normal [@Hagen2003].
+
+# Benefits
+
+For the proposed signals of need to be worth the costs, substantial benefits in terms of social support are expected by their corresponding theories, either in the form of support or renegotiated social relationships.
+When it comes to depression, self-harm, and suicide, the most likely benefits are expected to be long-term changes in how one is treated [@Hagen2003; @HagenEtAl2008; @SymeEtAl2016].
+This can take the form of reconciliations in failing relationships, increased fairness in cooperative relationships, or an increase of resources being directed towards an individual.
+Of all the benefits, a reduction in physical abuse may be one of the most important, with physical abuse likely being a common occurrence over our evolutionary history based on the high prevalence of it in traditional societies [@StieglitzEtAl2011].
+
+The benefits of the less costly signals are likely to be more varied due to their low costs allowing smaller benefits to make them worthwhile.
+These benefits may therefore be more short-term in nature and come from relationships without large conflicts of interest.
+In regard to crying, a demonstration of need beyond a verbal request may increase the chances of short-term changes in resource allocation or interventions into social conflicts outside of the signaler-target relationship.
+When it comes to illness symptoms, greater symptomology is expected to increase the likelihood of support when one cannot satisfy their own needs [@Steinkopf2015; @Tiokhin2016] and may also decrease the risk of reputation hits that might come from the belief that one is faking illness , both of which might be well worth a minor increase in symptomology which might already exist.
+
+Whether long-term or short-term, social support is often classified as emotional or instrumental (material support), with there currently being little empirical evidence on their relative importance (Jacobson, 1986).
+However, if emotions are viewed as motivators to guide behavior towards adaptive outcomes (Nesse, 1990; Tooby & Cosmides, 2008), it is unlikely emotional support is the ultimate goal.
+Instead, emotional support may be the desired outcome of proximate mechanisms which favor greater investment in relationships to increase the likelihood of future instrumental support if one needs it (the ultimate benefit).
+It is also conceivable that emotional support might track achieved support so that emotional support is high when one’s needs are being met.
+If this is the case, changes in emotional support may still be informative to signaling approaches as achieved support is likely to cause individuals to believe there is less need to signal, assuming an honest display needs to only be made once.
+
+Although less meaningful when examining responses to the proposed signals, the distinction between received and perceived social support is likely more useful when considering how information about social support is stored, with received support being material support and perceived support being one’s perceptions about the likelihood and adequacy of future support [@NorrisKaniasty1996; @WethingtonKessler1986].
+Unlike the relative importance of material and emotional support where the evidence is ambiguous, here, the evidence suggests that perceived support is the more powerful of the two in predicting positive outcomes, with the two not being as closely related to each other as often expected [@HaberEtAl2007; @NorrisKaniasty1996].
+Although evident in many areas, the disconnect between received and perceived social support is particularly noticeable in the finding that perceived social support often decreases in times of need, even in situations in which one is likely experiencing more material support than in one’s life before the need [@NorrisKaniasty1996].
+
+When examining the costly signals of need, the gap between current levels of received social support and the potential support that could be gained through a signaling strategy is likely to be the most important measure as this is what defines the size of the benefits.
+As this would involve information about both one’s level of need as well as information about the likelihood and size of potential help, it may essentially be a measure of perceived support as defined above.
+Therefore, perceived social support might form an important link between the severity of one’s situation and the amount of help deemed sufficient to avoid or stop a signaling strategy.
+In connecting the two, this conceptualization has the potential to explain why low levels of perceived social support are a strong predictor of depression [@KendlerGardner2014; @LeskelaEtAl2008; @ParkEtAl2016] and a potential predictor of the symptom upregulation found in placebo responses [@Humphrey2002].
+
+# Responses to the proposed costly signals of need
+
+Most studies examining responses to depression have been observational and focused on responses outside of changes in social support.
+In general, most report aversive responses and high levels of rejection towards the depressed, and depressed individuals are often linked to impaired social functioning [@EvraireDozois2011; @GotlibLee1989; @HirschfeldEtAl2000].
+One explanation for this is that depressed individuals engage in behaviors that drive others away.
+In line with this reasoning, both excessive reassurance seeking and negative feedback seeking, which often accompany depression, have been shown to elicit negative emotional responses from others and increase the chance of rejection from others [@JoinerMetalsky1995; @StarrDavila2008].
+Negative interactions are also seen in families as depressed children tend to report less support and more negative responses from parents than non-depressed children, although it has not been demonstrated that such interactions did not lead to depression in the first place [@MesserGross1995; @SchwartzEtAl2012].
+
+Beneficial responses to the depressed are also reported.
+This is seen in that depression has been shown to reduce the likelihood of aggression within families, particularly in families already experiencing high levels of conflict [@SheeberEtAl2001].
+There is also limited evidence that depression can result in increased levels of support from others outside the family.
+For example, non-depressed individuals were shown to be more cooperative and exhibit more caretaking behavior towards their college depressed roommates over the course of their time living together [@HokansonEtAl1986].
+Likewise, a vignette study found that individuals were more likely to provide advice and support to depressed individuals than anxious individuals despite similar levels of distress [@StephensEtAl1987].
+
+Responses to crying have received more attention, often from a signaling perspective.
+These responses are generally positive when it comes to infant crying and instrumental outcomes like the amount of care directed towards the infant or its proximity to its parents [@LinMcFatter2012].
+However, crying is also associated with increased distress and other negative emotions in parents and may increase the child’s risk of maltreatment if it is in poor condition [@LinMcFatter2012; @Soltis2004].
+Responses to adult crying tend to be similar with negative responses typically involving emotions and positive ones involving the likelihood of providing support.
+For example, individuals faced with crying scenarios in a vignette study experienced more negative emotions relative to controls while also being more likely to provide emotional help and hide negative feelings [@HendriksEtAl2008].
+Likewise, another experimental study found that while crying increased social support, it came at the cost of being perceived as helpless [@VingerhoetsEtAl2016].
+It is important to note, however, that this trend is not always the case as crying can elicit positive emotions like perceived friendliness [@VingerhoetsEtAl2016] and result in negative outward responses like confrontations or mocking at the extreme end [@WagnerEtAl1997].
+
+Unfortunately, there are few studies examining how individuals respond to suicide attempt survivors.
+In those which exist, stigmatization is commonly reported within and outside families [@FreyEtAl2017; @ScoccoEtAl2012], with perceptions of survivors as being weak, selfish, mentally ill, and antisocial all being commonly reported [@BatterhamEtAl2013; @FreyEtAl2016; @TzengLipson2004].
+Although these types of stigmatization have been reported across relationships types, the likelihood of stigma has been found to differ based on who the survivor is to the person being questioned.
+This is seen in a study which found that individuals felt the most stigma from members of their preexisting social networks than mental health providers, with family members providing more stigmatization (57.1% of the time) than romantic partners (41.2% of the time) and close friends (28.2% of the time) [@FreyEtAl2016a].
+
+A factor analysis of responses to suicide survivors found that stigma related to suicide attempts could largely be described by three factors: weak, crazy, and distressed [@CorriganEtAl2017].
+When it existed, prejudice was described by two factors (fear/distrust and anger) and discrimination by three (avoidance, disdain, and coercion).
+A later vignette study which examined these factors across mental health problems found that participants had higher levels of stigmatization towards imagined characters who attempted suicide (both survivors and non-survivors) than depressed or mentally ill characters [@SheehanEtAl2017].
+In addition to this, the suicide vignettes also resulted in more anger than the other conditions; however, discriminatory behavior was about equal regardless of whether the attempt resulted in death or accompanied depression.
+
+Although negative responses to suicide survivors are more often studied and reported, positive responses have also been found.
+Increased social support and changes to important relationships are often reported to follow suicide attempts with some indication that these effects may hold long term [@Stengel1956].
+For example, a study of 100 women who survived suicide attempts found that in 75 cases, individuals gained identifiable benefits through the attempt, with 41 individuals benefiting from reconciliations with others [@Lukianowicz1971].
+As for the type of support received, emotional support seems to be more commonly provided than instrumental support based on initial evidence [@FreyEtAl2017]; however, it is currently unclear how this might change with social context.
+
+Unfortunately, the evidence regarding responses to suicide in traditional societies is indirect or anecdotal.
+Unlike Western countries, where suicide is often viewed as pathological [@Hidaka2012], members of traditional societies have been reported to view suicide attempts as cries for help rather than mental illness [@Shostak1981], suggesting that help is at least occasionally provided or reliably expected.
+Further evidence for this comes primarily from the situations in which suicide attempts are made, with suicide attempts often being described as ways of escaping unwanted marriage arrangements, persistent abuse, or a lack of support in obtaining mates [@GutierrezdePinedaMuirden1948; @Hilger1957; @Karsten1935; @Tessmann1930; @Wilson1960].
+Although most reports focus mainly on suicide attempts that result in death, there is some indication that the threat of it or a survived attempt can result in increased support, as was the case with the threat of suicide helping a !Kung woman escape an arranged marriage [@Shostak1981].
+
+# Why responses differ
+
+Compared to the empirical examinations of the responses of others to the proposed signals of need, the theory is much more advanced and responsible for several testable hypotheses.
+Likely the most basic is that costlier signals will elicit greater benefits all else being equal.
+This is mainly due to the previously mentioned relationship between the costs of a signal and its honesty, which results in costlier signals better satisfying the anti-cheating adaptations of others than less costly alternatives [@Zahavi1993].
+In addition to this, the requirement that the benefits received need to outweigh the costs of producing the signals on average also suggests that the costlier signals will often result in more substantial support as increased costs must be met by increased benefits for them to be adaptive.
+
+One area where all else is not equal and less costly signals may outperform costlier ones is times of minor need.
+Though not yet demonstrated empirically, it is reasonable to suspect an interaction between signal strength and need whereby stronger signals only tend to result in more positive responses in times where the signal is proportional to the need.
+In other words, too strong of a signal in times of minor need might send a stronger message of dysfunction than need.
+This may be problematic for the signaler because although dysfunction might still mean support is needed, its presence likely indicates that there is less to gain through supporting the individual through direct reciprocity regardless of relationship type and inclusive fitness if the supporter is related to the signaler and the perception of dysfunction is substantial [@SugiyamaSugiyama2003].
+
+Although less examined empirically than the relationship between the cost of a signal and its honesty, it is also reasonable to expect that existing conflict will require costlier signals to be effective.
+This is mainly due to the likelihood that existing social conflict means larger conflicts of interest are involved, which would therefore require the signaler to be in relatively greater need to be worth helping than in instances with no conflict.
+High degrees of conflict with the signaler may also increase one’s scrutiny of the signals, which would once again favor costly displays.
+In addition to fitting signaling theory, such a prediction is also consistent with the previously mentioned predictive relationship between conflict and depression, as depression is an extremely costly state to experience.
+Since the proposed signals of need often come in response to social adversity and are predicted to serve as a way to increase social support, it is also reasonable to expect that relational level differences are likely be more important than individual level differences in affecting how others respond to signaling.
+This seems to be borne indirectly out in the few studies that exist on the topic with relational level differences being the better predictor of the amount of disclosure suicide survivors were likely to give family members [@FreyFulginiti2017; @FulginitiEtAl2016], something that is associated with more positive responses from family members and lower depression scores [@FreyEtAl2016a].
+However, it is unclear if it was disclosure itself or being in a more open family that resulted in positive responses.
+
+Another situation when relational level variables might be important is in times of divergent welfare tradeoff ratios (i.e.
+when one partner values the other more than they are valued in return) in relationships defined by reciprocal altruism [@Sell2005].
+In these instances, the less valued partner may have more to gain in supporting the more valued individual due to the benefits of maintaining future support, assuming the reason for the differential WTR is not due to kinship (i.e.
+younger kin valuing older kin less) or disability (which would make reciprocal altruism unlikely).
+In addition to this, such times of need would also create opportunities for the less valued partner to close the gap in WTR for future benefits by providing important support, potentially making support more likely than if the roles were reversed.
+
+It is important to note that the relative importance of relational level differences does not mean individual differences are likely to be unimportant.
+This is especially the case when these differences contribute to differences in one social environment [@KendlerEtAl1999].
+Although not evidence of responses to need, such a situation is seen with many of the social situations associated with depression being heritable like divorce and family conflict [@KendlerBaker2007].
+If positive relationship outcomes are also heritable in a similar way as is reasonable to expect, then individual level differences would also affect how much help is provided in ways that would be hidden by relational variables, rather than simply leading to differences in likelihoods of occurrence.
+
+Beyond one’s social environment, individual differences may also result in differences in how effective various signals and their alternatives are, thereby influencing how one is responded to.
+Although not a costly signal as envisioned here, anger is clearly involved with signaling displays and should be expected to work better for those with more formidability [@HagenRosenstrom2016].
+As previously mentioned, this has been suggested to explain the sex difference in depression, with women being less likely to effectively bargain through aggression.
+However, if depression and anger from complementary bargaining strategies, it is also conceivable that men may have more to lose from depression.
+Although speculative with depression, this appears to be the case with crying, with men often being responded to less favorably to than women [@CretserEtAl1982; @Jesser1989] although this is not a universal finding [@HendriksEtAl2008].
+
+# Study Aims and Predictions
+
+The relative lack of studies on responses to the proposed signals of need thus far has meant that a key line of evidence regarding the plausibility of their adaptive nature is underdeveloped, something which is compounded by the fact that many of the studies examining the costlier signals are focused solely on negative responses.
+In this study, we examine responses to many of the proposed signals of need in response to different social circumstances (i.e.
+high or low conflict and the amount and direction of information about honest need).
+Although this is done for all the signals in the confirmatory portion of the study, we turn our focus to depression and the less costly signals in our exploratory analyses.
+
+In response to the previously mentioned hypotheses, we predict that stronger signals will result in higher levels of both emotional and instrumental social support (i.e.
+likelihood of providing help or how much money one is willing to give) towards the signaler.
+Specifically, we predict that the signals will have the following rank order form low to high: no signal (control), verbal request, facial sadness with crying, depression, depression with display of suicidal ideation, and suicide attempt.
+We also predict that anger will have a positive impact on helping with a similar magnitude to the depression condition.
+Unlike the hypothesized signals of need, we predict that the schizophrenic break condition will decrease the likelihood of help relative to the control since it indicates cognitive dysfunction and its symptoms are not expected to have a signaling component.
+
+Although instances of private information are likely to result in the highest prevalence of signaling behavior, it is unlikely that they will result in the most helping behavior.
+Instead, we predict that instances of public information of honest need are likely to result in the most help as external information of need is likely a more reliable indicator of need than signals under most circumstances.
+In line with this reasoning, we also predict that private information will result in more support than public information of cheating as even costly signaling attempts may not overcome reliable information of a lack of need.
+Due to the previously mentioned likelihood that conflict increases skepticism on the part of signal targets, our last predicted main effect is that a lack of conflict will result in more favorable reactions than the conflict conditions.
+
+In addition to these main effects we also predict several interactions.
+Regarding signal strength and information, we predict that the signals will have the greatest impact on the participant's responses when a participant has no information about whether the character is lying or telling the truth so that the coefficient for signal strength will be greater in the private information condition relative to the public information conditions.
+In instances where participants have information that the sister is likely cheating, we predict that the costlier signals will be more aversive than the less costly signals, in opposition to our prediction on the main effect of signal strength.
+
+Due to the same reason underlying our prediction for the main effect of conflict, we also predict two interactions with conflict.
+The first is that the effect of signal strength will be larger in the conflict condition compared to no conflict condition.
+The second is that private information will have a greater negative impact on helping in the conflict condition than the no conflict condition.
+
+# Materials and methods
+
+## Vignettes
+
+The vignettes for this study were designed to result in a situation in which requested support was costly but worth providing if the requester was truly in need.
+In this study, this took the form of having participants put themselves in situations in which an imagined sister was requesting a loan of $50,000 from them that was originally saved for their imagined daughter’s college education.
+Regardless of the manipulations, each vignette consisted of two parts, the main storyline which included the conflict and information manipulations and a signal portion that was presented after the participants answered the first set of main outcome questions and the only attention check.
+
+## Factorial Design
+
+The design of this study was a between-subject full factorial design in which three theoretically relevant variables were manipulated: (1) the level of conflict in the relationship, (2) the degree to which one had information about whether or not the person in the vignette is genuinely in need, and (3) the type of signal (or control).
+
+The amount of conflict within the relationship had a high and a low condition, which was manipulated by describing the participants’ relationship with their sister as “competitive and full of conflict” or “supportive and free of conflict.” The amount of information the participant had on the likelihood the request representing honest need had three conditions: (1) information their sister was misleading them, (2) information their sister was experiencing honest need, and (3) a high degree of private information in which no information about the likelihood of it being an honest request was given.
+Due to the fact that baseline levels for the emotional and instrumental variables were not taken before the conflict and information manipulations, comparisons on the impact of these manipulations must be between-subjects.
+
+For our signal manipulation, six types of signals accompanying verbal requests were tested: (1) a verbal request alone, (2) facial sadness with crying, (3) depression, (4) anger, (5) depression with display of suicidal ideation, and (6) a suicide attempt.
+As the amount of crying in those with depression is moderately associated with depression severity [@VingerhoetsEtAl2016] and depression is a major risk factor for suicide [@BostwickPankratz2000; @Kessler2012], each signal was designed to build off of the less costly signals so that each signal contained elements of any signal it was costlier than.
+In addition to these hypothesized signals, two controls were also tested: (1) a no signal control in which the participant attempts to talk to her or his sister but finds that she is not home and (2) a psychotic break condition in which the sister displayed symptoms consistent with schizophrenia to control for severity alone causing changes in help.
+
+Unfortunately, it became clear after the study was completed that our no signal control was flawed due to the fact that a verbal request was always included in the main part of the vignette.
+Therefore, although the control had no signal after the main vignette, there was still a signal present before.
+For this reason, verbal request may be the closest condition to a control we have, with our original control simply being a one-time verbal request.
+
+## Sampling
+
+Participants for this study were recruited from Amazon Mechanical Turk, a crowdsourcing platform that allows for the creation of Human Intelligence Tasks (HITs) that workers can complete for pay.
+As Amazon provides the infrastructure, it allows for a relatively low-cost way of collecting data for academic research at the cost of the data not being representative of any real population.
+Despite this limitation, it is more diverse than most convenience samples [@KennedyEtAl2018; @DworkinEtAl2016], with turkers in the U.S.
+mainly differing in being younger, more educated, lower income, and more female biased than the greater U.S.
+population [@RossEtAl2010].
+
+Overall, the quality of data provided by MTurk workers tends to resemble that of university sample pools, with there being some indication that it might outperform university samples in a few important areas.
+This is seen in that while both MTurk workers and university students engage in problematic behaviors that might lessen data quality to similar amounts [@NeckaEtAl2016], workers on MTurk have been shown to be more attentive than samples of university students [@HauserSchwarz2016].
+For this reason, concerns about data quality come primarily from potential bot use and respondents faking their location to take surveys in a language they do not understand well, with the former concern being largely unfounded and the latter able to be corrected for with the tools used in this study [@KennedyEtAl2018]
+
+## Sample
+
+All participants were over 18, located in the United States, had a HIT approval rate of over 95%, and had successfully completed at least 100 HITs as anything less results in approval rates of 100% [@KennedyEtAl2018].
+To ensure participants were paying attention to the vignette, a 5-question attention check was included which involved questions addressing the topics of manipulations as well as who was making the request and how much money was saved for the daughter.
+Informed consent was given by proceeding with the study after reading the consent form, and all participants who passed at least 4 of the 5 attention checks were paid $1 for their time.
+
+Although all participants who passed the attention checks and finished the survey were paid, additional exclusions were made to reduce the noise from low quality data.
+This involved removing data with response times under 215 seconds unless the participant provided a comment of over 10 words in response to the open-ended feedback prompt, with the time cutoff being selected for being as fast as one could complete the study while paying attention to the relevant parts based on trial runs and the word cutoff being based on the likelihood that someone rushing through the study would not spend the extra time to fill in an optional section.
+In addition to this, participants were also excluded for either having identical GeoIP addresses to at least six other survey completions or an IP address flagged as suspicious of VPS use by the R package rIP.
+This was due to the reported association between fraudulent, low quality responses to both VPS use and multiple responses [@KennedyEtAl2018].
+The cutoff of 6 was chosen through the use of regression trees which indicated an attention check failure rate of almost 64% for individuals whose GeoIP matched at least 6 other responses.
+
+## Survey
+
+Although distributed through MTurk, every participant took the survey using Qualtrics.
+In every instance, the elements of the survey were laid out in the following order: 1) the consent form, 2) the main body of the vignette, 3) the first set of outcome measures (pre-signal), 4) the first set of manipulation checks, 5) the attention checks, 6) the signal portion of the vignette, 7) the second set of outcome measures (post-signal), 8) the second set of manipulation checks, 9) a set of demographic questions, and 10) an open feedback prompt.
+See Appendix 10 for the complete survey.
+
+### Outcome measures
+
+Both emotional and instrumental responses were measured in the survey portion of the study.
+In a small pilot study, we initially asked the same questions before and after the signal was shown to measure how the signal affected one’s responses.
+However, due to the prevalence of ceiling and floor effects, the majority of the questions following the signal in this study were revised to ask if and how one’s likelihood of helping or feeling certain emotions changed.
+This resulted in 22 outcome measures, with 11 being asked before the signal and 11 after (See Table 1 for the full list and Table 2 for summary statistics).
+In both instances, the order of the questions was randomized to avoid order effects [@KrosnickAlwin1987].
+
+To measure these responses, sliders which functioned largely as visual analogue scales were used due to the fact they allow for finer grained changes than categorical scales and provide a continuum of scores [@KlimekEtAl2017].
+For the pre-signal set of questions, only the ends of each continuum were labeled with some variant of extremely likely and extremely unlikely being used for each measure.
+For the second set, the center was labelled no change, and the ends of each continuum were labelled as some variant of much more likely and much less likely.
+
+Compared to our pre-signal measures, we had more missing values in the post-signal questions.
+We attributed this to the fact that Qualtrics only records responses if the slider is touched, which most participants probably did not realize.
+Since the slider was preset at the center at Time 2, we assumed that the missing values were largely due to participants meaning to report no change.
+We therefore replaced the missing values with the middle value for Time 2 variables only.
+The minimum perent of a entries replaced was $`r signif(df_na_sum["Min."], 2)`$%, and the maximum was $`r signif(df_na_sum["Max."], 2)`$%, with the mean percentage of missing values replaced being $`r signif(df_na_sum["Mean"], 2)`$%.
+We did not replace missing values for Time 1 because the slider was preset to the far left (e.g.
+0 percieved need).
+
+In addition to this, the amount of money participants were comfortable lending to their imagined sisters was asked and was measured with a slider which ranged from $0 to $50,000 and allowed the participant to see the amount they were selecting.
+Unlike the previously described measures, it was repeated identically at both time periods and asked on its own page due to the desire to save the only question that allowed for partial support for after those with less flexibility were asked.
+
+Of these variables, 3 post-signal measures (Time 2) are used as dependent variables in confirmatory analyses, (1) the amount the sister needed the money as percieved by the participants, (2) the likelihood that participants would lend the money, and (3) the amount of money participants would be comfortable lending in this sceario.
+
+Variable | Wording | Coding
+---------|---------|-------
+Perceived need of money at T1 | How much do you think your sister needs this money? | 0: Not at all; 100: A great deal
+How likely to lend money at T1 | How likely are you to lend the money to your sister? | 0: Very unlikely; 100: Very likely
+How angry are you about the request at T1 | How angry do you feel about this request? | 0: Not at all angry; 100: Extremely angry
+How satisfied to help at T1 | How much satisfaction would you get from helping with this request? | 0: No satisfaction; 100: A great deal of satisfaction
+How sad about health problem at T1 | How sad were you to learn about your sister’s child’s health problem? | 0: Not sad; 100: Devastated
+How reasonable is the amount requested at T1 | How reasonable is the amount of money being requested? | 0: Extremely unreasonable; 100: Extremely reasonable
+How much do believe the niece is ill at T1 | How much do you believe your sister’s child has a health problem? | 0: Extremely unbelieving; 100: Extremely believing
+How much harm will your daughter suffer at T1 | How much harm do you think this would cause to your daughter Sophie? | 0: None at all; 100: A great deal
+Suspicion of sister at T1 | How much do you suspect that this might be an attempt by your sister to get you to lend her money for another purpose?
+| 0: I'm very suspicious; 100: I'm completely unsuspicious
+Perceived benefit to sister at T1 | How much help would lending the money to your sister help her and her child? | 0: None at all; 100: A great deal
+Trust that sister will repay at T1 | How much do you trust that your sister will pay you back? | 0: Extremely distrustful; 100: Extremely trustful
+Amount conformtable lending at T1 in dollars | What amount of money would you be comfortable with lending to your sister in this scenario in US dollars? | 0 - 50000
+How close to sister at T1 | Having read the story, how close do you feel to your sister? | 0: Extremely distant; 100: Extremely close
+Change in perceived need of money at T2 | After going to your sister’s house, has your belief that your sister needs the money increased, decreased, or not changed?
+| -50: Decreased greatly; 0: No change; 50: Increased greatly
+Change in how likely to lend money at T2 | After going to your sister’s house, are you more willing to lend her the money than before, less willing than before, or no change?
+| -50: Much less willing; 0: No change; 50: Much more willing
+Change in anger about the request at T2 | After going to your sister’s house, has your sister’s request for money made you more angry than you were, less angry than you were, or no change?
+| -50: Much less angry; 0: No change; 50: Much more angry
+Change in How satisfied to help at T2 | After going to your sister's house, would you feel more satisfaction from helping your sister, less satisfaction, or no change?
+| -50: Much less satisfaction; 0: No change; 50: Much more satisfaction
+Change in How sad about health problem at T2 | After going to your sister’s house, are you more sad than you were about your sister’s child’s health problem, less sad than you were, or no change?
+| -50: Much less sad; 0: No change; 50: Much more sad
+Change in How reasonable is the amount requested at T2 | After going to your sister’s house, do you think the amount of money she requested is more reasonable than before, less reasonable than before, or no change?
+| -50: Much less reasonable; 0: No change; 50: Much more reasonable
+Change in How much do believe the niece is ill at T2 | After going to your sister’s house, has your belief that your sister’s child has a health problem increased, decreased, or not changed?
+| -50: Decreased greatly; 0: No change; 50: Increased greatly
+Change in How much harm will your daughter suffer at T2 | After going to your sister’s house, do you now think lending the money to your sister would harm your daughter Sophie more than you thought, less than you thought, or no change?
+| -50: Cause much less harm; 0: No change; 50: Cause much more harm
+Change in Suspicion of sister at T2 | After going to your sister’s house, are you more suspicious that this might be an attempt to get you to lend her money for another purpose, less suspicious, or no change?
+| -50: Much less suspicious; 0: No change; 50: Much more suspicious
+Change in Perceived benefit to sister at T2 | After going to your sister’s house, do you think lending the money to your sister would help her child more than you did before, less than before did before, or no change?
+| -50: Much less help; 0: No change; 50: Much more help
+Change in Trust that sister will repay at T2 | After going to your sister’s house, are you more trusting that your sister will pay you back than you were before, less trusting than you were before, or no change?
+| -50: Much less trusting ; 0:  No change; 50: Much more trusting
+Change in Amount conformtable lending at T2 in dollars | After going to your sister's house, what amount of money would you now be comfortable with lending to your sister in this scenario in US dollars?
+| 0 - 50000
+How close to sister at T2 | After going to your sister's house, how close do you feel to your sister? | 0: Extremely distant; 100: Extremely close
+How easy to imagine | How challenging was it to imagine yourself in this scenario? | 0: Extremely difficult; 100: Extremely easy
+
+### Manipulation checks
+
+To understand if our manipulations had the desired effect two brief manipulation checks were also included, one before the signal and one following it.
+The first set of checks involved a question about how close participants felt to the one requesting the help in the imagined scenario and a question about how significant of a request the $50,000 was perceived to be.
+The second set of checks also had these questions plus one examining what emotional state they thought the imagined signaler was experiencing, in which participants could select from a number of boxes.
+
+Beyond a way to determine if participants were responding to the study as desired, these questions are also likely meaningful as outcome measures as one’s perception of another’s subjective experience is likely to play a role in their decision making.
+As such, they are only used in exploratory analysis portion of this study and in principle component analyses.
+
+### Demographic Questions
+
+The final part of the survey was a brief demographic questionnaire which examined: (1) the age, (2) sex, (3) state of residence, (4) number of children, (5) number of siblings, (6) birth order, (7) current relationship status, and (7) highest level of education of each participant.
+
+## Confirmatory Analyses
+
+To analyze the effects of conflict and the amount and type of information (hereafter information) on helping behavior, we used a linear model that included conflict and information as independent variables with PCA1 from our pre-signal principle components analysis T1 as the dependent variable.
+See figures 1, 2, and 3.
+We also fit a model in which information interacted with conflict, with PCA1 as the outcome variable.
+
+To understand the effects of the signals, we fit linear models for each of our four dependent variables.
+For the models of change in perceived need of money and change in likelihood of lending money, each was modeled with signal type as the sole independent variable.
+For the model looking at change in the amount of money participants were willing to lend, the same measure pre-signal was controlled for.
+And in the PCA model, PC1 post-signal was modeled controlling for PC1 pre-signal.
+
+We also fit interaction models for the same outcome variables post-signal, with each being the independent variable for model that interacted signal with information and signal with conflict.

### 2021-02-19 Paper.rmd
Updated YAML header and r code in setup chunk.

@@
 title: "Depression and suicidality as costly signals of need"
-author: "Michael Gaffney, Kai Adams, Kristen Syme, and Edward Hagen"
-date: "2/18/2021"
-output: html_document
+author: "Michael Gaffney, Kai Adams, Kristen L. Syme, and Edward H. Hagen"
+date: '`r format(Sys.Date(), "%B %d, %Y")`'
+always_allow_html: true
+output: 
+  bookdown::html_document2:
+    number_sections: false
+bibliography: MTBib.bib
+csl: apa-6th-edition.csl
 ---
+
+```{r setup, include=F}
+knitr::opts_chunk$set(echo = F, warning = F, error = F, message = F)
+source('analysis.R')
+```
 
@@
 
-Compared to our pre-signal measures, we had more missing values in the post-signal questions.
-We attributed this to the fact that Qualtrics only records responses if the slider is touched, which most participants probably did not realize.
-Since the slider was preset at the center at Time 2, we assumed that the missing values were largely due to participants meaning to report no change.
-We therefore replaced the missing values with the middle value for Time 2 variables only.
-The minimum perent of a entries replaced was $`r signif(df_na_sum["Min."], 2)`$%, and the maximum was $`r signif(df_na_sum["Max."], 2)`$%, with the mean percentage of missing values replaced being $`r signif(df_na_sum["Mean"], 2)`$%.
-We did not replace missing values for Time 1 because the slider was preset to the far left (e.g.
-0 percieved need).
+[deleted MA results stuff]
 

### 2021-02-20 analysis.R
Fixed name in bib file Added APA csl file Gave ggplots names to use in ms Tweaked appearence of most plots

@@ -24,6 +24,15 @@ library(gt)
 library(hagenutils)
 library(mediation)
 
+
+# Functions ---------------------------------------------------------------
+
+theme_bw2 <-
+  theme_bw(15) +
+  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
+
+# Prepare data ------------------------------------------------------------
+
 d <-
   signaling2020 %>%
   dplyr::filter(CompleteSurvey) %>%
@@ -44,8 +53,12 @@ m1 <- lm(T2Belief ~ T1Belief * signal, d)
 summary(m1)
 Anova(m1, type = 3)
 
-p <- visreg(m1, xvar='signal', by = 'T1Belief', partial = F, rug = F, gg = T)
-p + theme_bw() + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
+plot_belief <-
+  visreg(m1, xvar='signal', by = 'T1Belief', partial = F, rug = F, gg = T) +
+  ylim(c(0, 100)) +
+  labs(x = '', y = 'T2 Belief\n') +
+  theme_bw2
+plot_belief
 
 # Signals vs belief in each vignette
 
@@ -53,8 +66,12 @@ m1b <- lm(T2Belief ~ T1Belief + signal*vignette, d)
 # summary(m1b)
 Anova(m1b, type = 3)
 
-p <- visreg(m1b, xvar='signal', by = 'vignette', partial = F, rug = F, gg = T)
-p + theme_bw() + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
+plot_belief_vignettes <-
+  visreg(m1b, xvar='signal', by = 'vignette', partial = F, rug = F, gg = T) +
+  ylim(c(0, 100)) +
+  labs(x = '', y = 'T2 Belief\n') +
+  theme_bw2
+plot_belief_vignettes
 
 # Plot of raw data
 
@@ -76,19 +93,31 @@ d4c <-
   group_by(signal, vignette, Time) %>%
   dplyr::summarise(value = mean(value))
 
-ggplot() +
+plot_raw_beliefs <-
+  ggplot() +
   geom_line(data = d4b, aes(Time, value, group = id), alpha = 0.1) +
   geom_line(data = d4c, aes(Time, value, group = 1), colour = 'red') +
+  scale_x_discrete(expand = expansion(mult=0.1)) +
   facet_grid(vignette~signal) +
[…]

### 2021-02-25 analysis.R
Many tweaks to the code

@@ -13,17 +13,17 @@
 #+ warning=F, message=F
 
 library(signaling2020data)
+library(car)
+library(ggbiplot)
 library(tidyverse)
 library(broom)
 library(effects)
 library(visreg)
-library(car)
-library(ggbiplot)
 library(ggforce)
 library(gt)
 library(hagenutils)
 library(mediation)
-
+library(gglm)
 
 # Functions ---------------------------------------------------------------
 
@@ -36,7 +36,8 @@ theme_bw2 <-
 d <-
   signaling2020 %>%
   dplyr::filter(CompleteSurvey) %>%
-  mutate(
+  dplyr::mutate(
+    across(.cols = c(contains('Belief'), contains('Action')), ~.x/100),
     signal = ordered(signal, levels = c('Verbal request', 'Crying', 'Mild depression', 'Depression', 'Suicide attempt'))
   )
 
@@ -45,30 +46,46 @@ d2 <-
   d %>%
   dplyr::filter(vignette == 'Thwarted marriage')
 
+plot_age_distribution <-
+  ggplot(d, aes(Age, colour = vignette)) +
+  geom_density() +
+  labs(x = '\nAge', y = 'Density\n') +
+  theme_bw(15)
+plot_age_distribution
+
 # Belief ------------------------------------------------------------------
+
+plot_T1Belief_distributions <-
+  ggplot(d, aes(T1Belief, colour = vignette)) +
+  geom_density() +
+  labs(x = '\nT1 Belief', y = 'Density\n') +
+  theme_bw(15)
+plot_T1Belief_distributions
 
 # contrasts(d$signal, how.many = 2) <- contr.poly(5)
 
-m1 <- lm(T2Belief ~ T1Belief * signal, d)
+m1 <- glm(T2Belief ~ T1Belief * signal, family = quasibinomial, d)
 summary(m1)
 Anova(m1, type = 3)
+gglm(m1)
 
 plot_belief <-
-  visreg(m1, xvar='signal', by = 'T1Belief', partial = F, rug = F, gg = T) +
-  ylim(c(0, 100)) +
+  visreg(m1, xvar='signal', by = 'T1Belief', partial = F, rug = F, gg = T, scale = 'response') +
+  ylim(c(0, 1)) +
   labs(x = '', y = 'T2 Belief\n') +
   theme_bw2
[…]

### 2021-02-25 analysis.R
Added mediation models

@@ -383,6 +383,7 @@ plot(out)
 
 # to do: moderated mediation model
 
+# Depression vs Verbal
 d_mediate <-
   d %>%
   dplyr::filter(
@@ -402,6 +403,95 @@ out <- mediate(mmediator, mout, treat = "signal", mediator = "T2Belief")
 
 summary(out)
 plot(out)
+
+
+# Suicide attempt vs Verbal
+d_mediate <-
+  d %>%
+  dplyr::filter(
+    signal %in% c(
+      'Verbal request',
+      'Suicide attempt'),
+    vignette != "Thwarted marriage"
+  ) %>%
+  mutate(
+    signal = factor(signal, levels = c('Verbal request', 'Suicide attempt'))
+  )
+
+mmediator <- lm(T2Belief ~ signal + T1Belief + vignette, d_mediate)
+mout <- lm(T2Action ~ signal + T2Belief + T1Action + T1Belief + vignette, d_mediate)
+
+out <- mediate(mmediator, mout, treat = "signal", mediator = "T2Belief")
+
+summary(out)
+plot(out)
+
+
+# Suicide attempt vs Depression
+d_mediate <-
+  d %>%
+  dplyr::filter(
+    signal %in% c(
+      'Depression',
+      'Suicide attempt'),
+    vignette != "Thwarted marriage"
+  ) %>%
+  mutate(
+    signal = factor(signal, levels = c('Depression', 'Suicide attempt'))
+  )
+
+mmediator <- lm(T2Belief ~ signal + T1Belief + vignette, d_mediate)
+mout <- lm(T2Action ~ signal + T2Belief + T1Action + T1Belief + vignette, d_mediate)
+
+out <- mediate(mmediator, mout, treat = "signal", mediator = "T2Belief")
+
+summary(out)
+plot(out)
+
+# Minor depression vs Depression
+d_mediate <-
+  d %>%
+  dplyr::filter(
+    signal %in% c(
+      'Mild depression',
+      'Depression'),
+    vignette != "Thwarted marriage"
+  ) %>%
+  mutate(
+    signal = factor(signal, levels = c('Mild depression', 'Depression'))
+  )
+
+mmediator <- lm(T2Belief ~ signal + T1Belief + vignette, d_mediate)
+mout <- lm(T2Action ~ signal + T2Belief + T1Action + T1Belief + vignette, d_mediate)
+
[…]

### 2021-03-04 Paper.rmd
Fixed name in bib file Added APA csl file Gave ggplots names to use in ms Tweaked appearence of most plots
Added rough draft on intro

@@
 source('analysis.R')
+library(equatiomatic)
 ```
 
+# Introduction
+Since Durkheim’s pioneering effort to use quantitative social science to explain suicide, varied attempts by anthropologists, psychologists, and sociologists and substantial investment by funding agencies, rates of depression and suicide attempts have remained largely unchanged over the last 100 years (confirm and cite), and there is still substantial uncertainty about why both are as common as they are (cite).
+Due to their high costs, the vast majority of these approaches have been built on the assumption that they are the result of internal dysfunction (cite examples).
+However, a subset of anthropologists and evolutionary theorists have challenged this idea, suggesting that despite the subjective suffering they cause, they may function as a means to limit negative fitness outcomes in times of substantial adversity (Firth + others).
+
+Within anthropology, Raymond Firth was likely the first to do this.
+Based on observations that suicide attempts often followed social conflict or loss and varied substantially in their likelihood of death, he argued that a sizable subset of the suicide attempts among the Tikopia were not meant to end in death but instead were a means to elicit attention, status, and immediate reintegration into the community following negative events (Firth 1967[not original date]).
+Compared to suicide, however, anthropological explanations for depression are a much more recent occurrence (cite), despite frequent reports of depression or depression-like behavior in a wide range of societies (cite) and the potential for cross-cultural research to help understand depressive states (cite).
+
+## Connection to Adversity
+Likely the most reliable finding when it comes to depression and suicidal behavior is that most cases are closely tied to major negative life events (Hammen, 2005 + others; citations for suicide).
+Compared to non-depressed individuals, those with depression tend to report at least twice as many instances of negative events in both community and clinical samples (Mazure, 1998) and more negative events than those with schizophrenia and bipolar depression across a wide range of studies (Paykel, 1994).
+In instances where this is the case, the onset of depression tends to be rapid, often occurring within one month of the event (Kendler et al., 1999 [double check and find others]).
+
+This strong connection between negative life events and depression along with the need and distress that likely accompanies these events has led to the suggestion that this relationship is causal (Kendler et al., 1999).
+Support for this comes from the fact that the relationship between negative events and depression holds true when looking solely at events outside of one's control, which shows that the connection is unlikely to be driven solely by depressed individuals creating situations where negative events are likely to be common (Hammen, 2005; Kendler et al., 1999).
+In addition to this, twin studies have shown that one's history of negative events is still a strong predictor when controlling for genetic similarity and that part of the heritability of depression stems from the heritability of negative events, like divorce and family conflict (Kendler & Baker, 2007; Kendler et al., 1999).
+
+Of the many types of negative life events associated with depression, those which involve social adversity tend to be more strongly associated with depression (Hammen, 2005; Kendler et al., 1999; Mazure, 1998).
+Like the relationship between negative events as a whole and depression, this relationship is also seen cross-culturally, with the loss of a loved one, threat of divorce, or abusive relationships all increasing one's chances of becoming depressed (Kendler et al., 1999, 1995).
+Of these events, physical assault has been found to be the strongest predictor of depression in the few studies in which it has been examined (Kendler et al., 1999, 1995) and may have been much more common throughout our evolutionary history than is often thought based on rates of spousal abuse in small-scale societies with little or no policing (Levinson, 1989; Stieglitz et al., 2018).
+
+Suicide attempts also tend to co-occur with social adversity (Hagen et al., 2008 + cite and describe), with evidence of this existing cross-culturally.
+Greif over the loss of a loved one (Firth; Devries et al.
+2011), bullying (Alavi et al., 2017; Butler et al., 2019; Ford et al., 2017; Wang et al., 2020), and instances of social transgression (Firth; Malinowski; Syme and Hagen 2018; find Western citation to confirm) have all been reported to lead to suicidal behavior in both industrialized (confirm the transgression part) and traditional societies.
+As with depression, assault is a powerful risk factor for suicidal behavior, something which has been found in multiple large-scale multi-country studies (Devries et al.
+2011; Ellsberg et al.
+2008).
+Both sexual and non-sexual assault were also associated with more self-harm and suicidal behaviors among both indigenous Sami and majority Norwegian adolescents, with those who attempted suicides reporting more than twice the number of negative life events than those who did not (Reigstad and Kvernmo 2017).
+The connection between social adversity and suicide is also seen in the Human Relations Area Files (HRAF), in which 77.4% of attempts were found to be linked to times of social conflict, 88.7% were linked to fitness threats in general, and 84.9% were linked to situations in which attempters were powerless to resolve their situation alone (Syme et al., 2016).
+
+## Depression and suicide attempts as both signals and bargaining tools 
+One possible reason for the connection between depression and social adversity is that depression functions to elicit increased support from others in times when an individual cannot solve substantial fitness-relevant challenges on their own.
+The bargaining model of depression is based on the idea that for much of our evolutionary history the small groups humans lived in created many situations in which certain forms of cooperation were unlikely to be easily replaced by others while also allowing for harmful or unfair social relationships to develop (Hagen, 2003).
+In these instances, one's monopoly on one or more types of cooperation could be leveraged to change how one is treated if others value the depressed person's cooperation sufficiently.
+
+One way depression and suicidal behavior are thought to lead to beneficial treatment is by reliably demonstrating that one’s need is genuine by making one’s private information about their condition public.
+This information is necessary due to the ease in which signals can be faked (Zahavi, 1975) and the costs of accepting a deceptive signal as reliable (cite), both of which have favored adaptations to spot fake signals in many species (Hasson, 1994) and demand trustworthy information before believing a given signal (check Hasson and cite + try to find others).
+
+Although there may be other ways for honest signals evolve (cite), one of the most widely accepted (confirm) means is through costly signaling.
+The evolution of costly signals is possible whenever the signal in question is comparatively cheaper to produce for those who have the underlying quality compared to those who lack it (Grafen 1990).
+In these instances, individuals with the quality maximize their fitness at greater levels of investment in the signal compared to those who lack the quality or possess it to a lesser degree (Gangestad and Scheyd 2005; Zahavi 1977).
+The end result of this is expected to be a signal that either tends to not be worth faking (Gangestad and Scheyd 2005) or is impossible to fake to a large degree due to selection against fakers constraining the physiology behind the signal (Zahavi 1977).
+
+Both depression and suicidal behavior fit this criterion as they are both relatively costly for those not facing adversity than those who are.
+In the case of depression, the largescale reduction in one's normal routine of fitness enhancing behavior hurts those in need less when one has limited ability to obtain fitness-relevant benefits, with depression likely adding no additional costs in instances of extreme deprivation (Hagen 2003).
+However, when it comes to suicide, the bulk of the costs associated with suicide attempts are only felt in times that result in death or severe bodily harm.
+For this reason, the way others view and respond to suicide attempts is likely to be strongly influenced by the probability that the attempt would result in death or severe injury (Rosenthal, 1993).
+That given, the previously mentioned logic still applies with increased risk of death being relatively costly for those able to enhance their fitness prospects in their day-to-day lives.
+
+Beyond resulting in the cost differential that allows for costly signaling in the first place, the costs of depression and suicidal behavior may be particularly important in times of conflict or when the level of support needed to address one’s situation is substantial.
+Importantly, there are likely few forms of adversity that do not come with conflict.
+For example, breakups in both romantic and cooperative relationships are often preceded by conflict (Amato & Hohmann-Marriott, 2007), and surely involve conflict when one side wants reconciliation and the other does not.
+Likewise, the death of a loved one may also be a source of conflict as the survivor may turn to others for more support who might not want to invest more in the survivor (Hagen, 2003).
+Regardless of the source of conflict, greater conflict should correspond with greater conflicts of interests, something which would favor greater investment in manipulating others through fake signals.
+In these instances, less costly signals like verbal requests, facial sadness, and crying are likely to be unreliable as their low costs can easily be made up for with increased social support, thereby favoring the use of costlier signals in those experiencing need they cannot resolve on their own.
+Importantly, the amount of conflict
+
+In addition to signaling need to those invested in the well-being of the signaler, depression and suicidal behavior may also help an individual bargain for increased support.
+This is possible due to the reduced investment in others that frequently accompanies depression or the threat to future cooperation that comes from a suicide.
+In these instances, depression is suggested to function analogously to a labor strike, sending the message that one’s need is genuine and that if the target of the signal wanted to continue receiving benefits from the depressed, he or she would need to increase support towards the signaler.
+
+## Responses to depression and suicidal behavior 
+For depression and suicide attempts to be worth the costs, substantial benefits in terms of social support are expected, either in the form of temporary but impactful support or long-term changes in how one is treated (Hagen, 2003; Hagen et al., 2008; Syme et al., 2016).
+This can take the form of reconciliations in failing relationships, increased fairness in cooperative relationships, or an increase of resources being directed towards an individual.
+Of all the benefits, a reduction in physical abuse may be one of the most important due to the threat of death or severe injury to oneself and one’s family (cite).
+
+Most studies examining responses to depression have been observational and focused on responses outside of changes in social support.
+In general, most report aversive responses and high levels of rejection towards the depressed, and depressed individuals are often linked to impaired social functioning (Evraire & Dozois, 2011; Gotlib & Lee, 1989; Hirschfeld et al., 2000).
+One explanation for this is that depressed individuals engage in behaviors that drive others away.
+In line with this reasoning, both excessive reassurance seeking and negative feedback seeking, which often accompany depression, have been shown to elicit negative emotional responses from others and increase the chance of rejection from others (Joiner & Metalsky, 1995; Starr & Davila, 2008).
+Negative interactions are also seen in families as depressed children tend to report less support and more negative responses from parents than non-depressed children, although it has not been demonstrated that such interactions did not lead to depression in the first place (Messer & Gross, 1995; Schwartz et al., 2012).
+
+Despite being looked for less frequently, beneficial responses to depressed individuals are also reported.
+This is seen in that depression has been shown to reduce the likelihood of aggression within families (Hops 1987[read]; Dadds et al.
+1982 [read]), particularly in families already experiencing high levels of conflict (Sheeber et al., 2001).
+There is also limited evidence that depression can result in increased levels of support from others outside the family.
+For example, non-depressed individuals were shown to be more cooperative and exhibit more caretaking behavior towards their college depressed roommates over the course of their time living together (Hokanson et al., 1986).
+Likewise, a study examining responses to confederates trained to appear ‘depressed’, ‘anxious’, or ‘normal’ found that individuals were more likely to provide advice and support to ‘depressed’ individuals than ‘anxious’ or ‘normal’ individuals despite the confederate in ‘depression’ condition being viewed more negatively than the other conditions and the ‘depression’ condition involving similar levels of distress compared to the ‘anxious’ condition (Stephens et al., 1987 [tweaked based on your paper with Kristen]).
+
+Unfortunately, there are few studies examining how individuals respond to suicide attempt survivors, with the majority examining responses after death.
+In those which exist, stigmatization is commonly reported within and outside families (Frey et al., 2017; Scocco et al., 2012), with perceptions of survivors as being weak, selfish, mentally ill, and antisocial all being commonly reported (Batterham et al., 2013; Frey et al., 2016a; Tzeng & Lipson, 2004).
+Although these types of stigmatization have been reported across relationships types, the likelihood of stigma has been found to differ based on who the survivor is to the person being questioned.
+This is seen in a study which found that individuals felt the most stigma from members of their preexisting social networks than mental health providers, with family members providing more stigmatization (57.1% of the time) than romantic partners (41.2% of the time) and close friends (28.2% of the time) (Frey et al., 2016b).
+
+Although negative responses to suicide survivors are more often studied and reported, positive responses have also been found.
+Increased social support and changes to important relationships are often reported to follow suicide attempts with some indication that these effects may hold long term (Stengel, 1956).
+For example, a study of 100 women who survived suicide attempts found that in 75 cases individuals gained identifiable benefits through the attempt, with 41 individuals benefiting from reconciliations with others (Lukianowicz, 1971).
+As for the type of support received, emotional support seems to be more commonly provided than instrumental support based on initial evidence (Frey et al., 2017); however, it is currently unclear how this might change with social context.
+
+Beneficial social changes are also reported in traditional societies.
+Unlike Western countries, where suicide is often viewed as pathological (Hidaka, 2012), members of traditional societies have been reported to view suicide attempts as cries for help rather than mental illness (Shostak, 1981).
+For example, attempts have been described as ways of escaping unwanted marriage arrangements, persistent abuse, or a lack of support in obtaining mates by those engaging in the behavior and observers (Gutierrez de Pineda & Muirden, 1948; Hilger, 1957; Karsten, 1935; Tessmann, 1930; Wilson, 1960), suggesting that help is at least occasionally provided or reliably expected.
+In support of this, 30 out of 84 examples of suicidal behavior included in the HRAF resulted in positive changes for the survivor, even though suicide was rarely if ever the main topic (Syme et al., 2016).
+
+New Draft Done
 # Abstract
@@
 
+## Preregistrations
+
+`r extract_eq(m1, intercept = 'beta', wrap = T)`
+
 ## Sampling
@@
 We also fit interaction models for the same outcome variables post-signal, with each being the independent variable for model that interacted signal with information and signal with conflict.
+
+# Results

### 2021-03-04 analysis.R
Working on models

@@ -24,6 +24,7 @@ library(gt)
 library(hagenutils)
 library(mediation)
 library(gglm)
+library(glmmboot)
 
 # Functions ---------------------------------------------------------------
 
@@ -68,6 +69,15 @@ m1 <- glm(T2Belief ~ T1Belief * signal, family = quasibinomial, d)
 summary(m1)
 Anova(m1, type = 3)
 gglm(m1)
+
+# glmmboot
+
+m1boot <- bootstrap_model(
+  base_model = m1,
+  base_data = d,
+  resamples = 999,
+  parallelism = 'parallel'
+)
 
 plot_belief <-
   visreg(m1, xvar='signal', by = 'T1Belief', partial = F, rug = F, gg = T, scale = 'response') +
@@ -162,9 +172,17 @@ plot_T2Belief_T2Action <-
 plot_T2Belief_T2Action
 
 m2 <- glm(T2Action ~ T1Action * signal, family = quasibinomial, d)
-# summary(m2)
+summary(m2)
 Anova(m2, type = 3)
 gglm(m2)
+
+# glmmboot
+m2boot <- bootstrap_model(
+  base_model = m2,
+  base_data = d,
+  resamples = 999,
+  parallelism = 'parallel'
+)
 
 plot_action <-
   visreg(m2, xvar='signal', by = 'T1Action', partial = F, rug = F, gg = T, scale = 'response') +

### 2021-03-04 analysis.R
Added PCA of T2 emotions

@@ -8,7 +8,7 @@
 #'
 #' **Brother-in-law**: Your teenage daughter claims your sister's husband sexually assaulted her (but might just be jealous of your sister's popular daughter)
 #'
-#' **Thwarted marriage**: Marriagable daughter refuses to marry available man (but might just want a bigger dowry)
+#' **Thwarted marriage**: Marriageable daughter refuses to marry available man (but might just want a bigger dowry)
 
 #+ warning=F, message=F
 
@@ -706,3 +706,23 @@ out <- mediate(mmediator, mout, treat = "signal", mediator = "T2Belief", boot = 
 
 summary(out)
 plot(out)
+
+
+# Emotion PCA -------------------------------------------------------------
+
+d_emotions <-
+  d %>%
+  dplyr::select(
+    starts_with('T2'),
+    -T2Action,
+    -T2Belief,
+    -T2Divide
+  )
+
+pca_emotions <- prcomp(d_emotions, scale. = F)
+
+d$PC1emotion <- -pca_emotions$x[,1]
+d$PC2emotion <- -pca_emotions$x[,2]
+
+m_emotion_belief <- glm(T2Belief ~ T1Belief + signal + PC1emotion + PC2emotion, family = quasibinomial, d)
+m_emotion_action <- glm(T2Action ~ T1Action * signal + PC1emotion + PC2emotion, family = quasibinomial, d)

### 2021-03-18 Paper.rmd
Added methods draft to RMD

@@
 
-New Draft Done
-# Abstract
+# Materials and methods
 
-Due to the fact much of major depression research often focuses on methods of treatment or causal explanations emphasizing the role of psychological malfunctions, the responses of others to the depressed are largely overlooked.
-Although such responses are of little use to such explanations, the potential ability for depression to elicit positive changes in social relationships through signaling honest need has been suggested as way depression could be adaptive, making responses to it a critical piece of evidence.
-To examine if depression often comes with social benefits, we compared it to other proposed signals of need in a vignette study that also manipulated the amount and type of information about whether one’s need was honest and the presence of conflict within an imagined relationship.
-Overall, we found evidence for the predicted interaction between signal type and conflict on relationship outcomes as well as the predicted main effects of information and conflict.
-Contrary to our predictions, costlier signals did not result in more positive responses across signal types, with there also being little evidence in favor of the predicted signal by information interaction.
-However, depression outperformed all the other proposed signals of need on our four outcome measures across social circumstances, and our predicted relationships for the signals as a whole were largely supported when looking solely at the verbal request, crying, and depression manipulations.
-This suggests that depression is a relatively successful way of demonstrating honest need and eliciting support, consistent with signaling explanations.
+## notes: 
+add funding info somewhere
 
-# Introduction
+## Design
 
-Long considered pathological sadness, depression has gained increased attention for its potential to function as a signal of need capable of bringing about positive changes in social relationships [@Hagen2002; @Hagen2003].
-Referred to as the bargaining model of depression, this view shares much in common with signaling explanations for crying [@Hasson2009; @HendriksEtAl2008], self-harm [@HagenEtAl2008], suicide attempts [@Rosenthal1993; @SymeEtAl2016], and illness symptoms [@Steinkopf2015; @Tiokhin2016], all of which view the costs involved as a key component of eliciting important social support.
-Based mainly in signaling theory, such approaches have all benefited greatly from economics and game theory, with the result being explanations for the existence of such states that emphasize the causal role of one’s social environment rather than simply focusing on one’s internal state.
+This study involved a vignette study with between subjects pre-test/post-test design with one factor (signal) and 5 levels (verbal request, crying, crying with behavioral changes, depression, and suicide attempt), with the outcome of interest being how believe and likelihood of helping changed in response to a given signal.
 
-Due to the similarities between the ways in which they are suggested to achieve their hypothesized functions, there is much to be gained by comparing depression to the other proposed signals of need to better understand both the situations that bring them about and what determines differences in how they are responded to.
-In doing so, it should be possible to identify the fundamental similarities they share and create testable hypotheses that transcend signal type and, therefore, have the potential to further influence costly signaling theory.
+## Pilot Studies
 
-Of all their similarities, the most basic is that positive responses are frequently expected so that the benefits received outweigh the costs involved on average.
-However, such responses are underexamined relative to the predictors of the symptoms involved and potential treatments, something which is especially true of depression [@BillingsMoos1985] due to the suffering it causes to those who have it.
-The result of this is that one of the most important lines of evidence for an oftentimes adaptive explanation for depression and the other proposed signals of need is largely missing.
+The first pilot study used a vignette study to examine how the presence of conflict, private information, and emotional signaling impacted the degree participants believed the signaler to be in need and provide support using an MTurk sample of 1,447 Americans.
+Of the signals, depression resulted in the most pro-signaler responses (reword), separating itself from the less costly signals when conflict and private information was present and substantially outperforming the schizophrenic break control.
+However, the suicide attempt condition was responded to relatively poorly, contrary to predictions.
 
-# Thesis Outline
+One potential explanation is that the initial scenario of a mother asking their sibling for help paying for their young daughter's heart surgery was not severe enough for a suicide attempt to be a functional signal, due to a lack of beleivability or due to its costs appearing manipulative.
+For this reason, we designed this study with more severe scenarios that were also associated with suicide attempts both ethnographically and clinically, including instances of sexual assasult, non-sexual assault, and thwarted marriage.
 
-In this thesis, I briefly review the evidence for why the proposed signals of need are unlikely to solely be the result of malfunctions before reviewing the basics of signaling theory that tie them all together.
-I then review depression and how adaptive and nonadaptive approaches differ in their casual explanations.
-After examining the other proposed signals of need, I explore the empirical work that has been done on responses to the proposed signals before examining what should be expected from signaling theory.
-Lastly, I report the findings of a vignette study conducted with Edward Hagen examining if the proposed signals of need result in positive responses in the situations predicted by the previously mentioned signaling explanations.
+add that we ask now ask same question twice? (interpretabilty)
 
-# Opposition to adaptive explanations and initial indications they are adaptive
-
-In general, the dominant view of the proposed signals of need is that they are symptoms of harmful byproducts or malfunctions.
-Likely the main reason for this is the harm they cause the one experiencing them, which can be quite severe with the costlier signals [@Kessler2012].
-However, subjective suffering and negative fitness outcomes are not inextricably linked.
-This is most obviously seen with negative emotions motivating fitness enhancing behavioral shifts, as is widely recognized to be the case with hunger, thirst, or pain [@Nesse1990; @ToobyCosmides2008].
-Just as these explanations attribute a functional role to negative experiences, the costs of proposed signals of need are suggested to be adaptive for their ability to increase the confidence of others who may be motivated to help that one’s need is genuine in ways non-costly displays could not [@Hagen2003; @Rosenthal1993; @SymeEtAl2016].
-
-However, to this point, the evidence suggesting that the proposed signals of need are adaptive comes primarily from outside indications of increased social support.
-For example, major depression [@BrometEtAl2011; @KesslerEtAl2010], suicide attempts [@CDC2014], placebo responses [@Humphrey2002], and crying [@vanHemertEtAl2011] are all more common than should be expected of maladaptive malfunctions due to the likelihood of strong selection pressures against those who incur extra costs in times of need.
-For the proposed signals of need to still be maladaptive with this prevalence, the traits responsible for such malfunctions would likely have to result primarily from environmental mismatches [@Hidaka2012] or pleiotropic traits in which major benefits come from the genes responsible for the proposed signals of need [@Williams1957].
-However, neither situation is safe to assume due to the proposed signals of need being found across a wide range of environments and social settings [@BrometEtAl2011; @SymeEtAl2016] and the fact that genetic modularity often results in the potential of other genes to limit the negative effects of pleiotropy while preserving the benefits in polygenic traits [@Hansen2003].
-
-Another important indication that the proposed signals of need are often the result of the result of functional mechanisms is the fact they tend occur when individuals are in need and can benefit from others.
-This is seen in both depression and suicide attempts occurring most frequently in times of social adversity in which individuals are experiencing costs due to the actions of others or the loss of existing social relationships [@Hammen2005; @Mazure1998; @SymeEtAl2016].
-Likewise, placebo responses, which have been proposed to be the downregulation of signaling through increased illness symptom severity [@Steinkopf2015; @Tiokhin2016], often happen in response to individuals receiving support after feeling a lack of it in conjunction with perceived need [@Humphrey2002].
-Although not evidence of increased support, this connection between the proposed signals of need and times of need suggests that malfunction cannot be safely assumed as long as there are those around who would be motivated to help.
-
-# Social support in humans
-
-Such a scenario in which costly emotional states lead to increased benefits is possible due to the degree to which humans cooperate with another, something which was necessary for our survival over much of our evolutionary history and is reflected in our adaptations today [@SugiyamaSugiyama2003].
-Unlike most species, this support can often come from a wide range of individuals in humans, with kin beyond parents playing an important role in childcare across generations [@KaplanEtAl2009; @Meehan2005; @SearMace2008] and unrelated individuals often helping in a wide range of situations due to the benefits of both direct and indirect reciprocity as well as reputation gains [@Alexander1987; @Barclay2013; @JaeggiGurven2013].
-The result of these benefits is a situation in which many individuals may be potential targets of a costly signaling strategy.
-
-While important at almost any time, cooperation is especially important in times of need.
-Illness, injury, and physical conflict with others have all been recurrent problems over the course of human evolution, with their outcomes often resulting in times in which individuals could not survive without short-term support [@SugiyamaChacon2000].
-In these times, help often takes the form of temporary increases in provisioning or labor to decrease the workload of the ill [@SugiyamaSugiyama2003].
-However, evidence of long-term support also exists with both Neandertals and modern humans being known to help those who are disabled [@TrinkausVillotte2017].
-Beyond showing that such cooperation does not rely solely on expectations of direct reciprocity, the presence of long-term support for those who are unlikely to recover, together with the fact that humans can often reliably find support in times of need, suggests that lasting changes might be possible in times of need outside of instances of disability.
-
-However, despite the likelihood of individuals benefiting from increasing their support of others in times of need and the widespread evidence that it often happens, devoting a large amount of resources to another is only likely to be worth it if the need is genuine.
-It is in these instances when the proposed signals of need are expected to be adaptive, as long as the result is an increase in the likelihood of support due to the signal enhancing one’s appearance of need and the benefits outweighing the costs of producing the signal [@Zahavi1993].
-Although this limitation precludes the costlier signals from being adaptive in relatively minor instances of need, it does rule out adaptive explanations in times when one’s need is great and unlikely to be believed.
-
-# Costly Signaling
-
-All organisms can benefit from altering the behavior, physiology, and psychological states of others, something which is seen from single celled organisms to social animals [@Dawkins1982].
-Such changes can be accomplished through chemical or behavioral means, with information flowing from the signaler to the receiver in ways meant to benefit the one sending the message, regardless of whether or not it benefits the one receiving it [@Dawkins1976].
-In social animals, members of one’s own species are often the target, with sexual selection and intrasexual competition creating many situations in which one’s reproductive success depends greatly on the responses of others [@Clutton-BrockHuchard2013; @DalyWilson1983].
-The results of this are strong selection pressures favoring those who can make the most of these opportunities to outcompete others and receive the largest benefits through both cooperation and competition.
-
-Of the strategies used to influence the behavior of conspecifics, costly signaling to provide believable information about one’s quality or current state is likely to be one of the most common and effective ways to do so [@Zahavi1975].
-A signal differs from a cue in that it is intentionally sent by an organism to alter the behavior or thoughts of other individuals, while a cue is any piece of information an organism uses to alter its behavior or physiological state that was created without the intent to do so [@MaynardSmithHarper1995].
-Since signals are created for the purpose of communication, they are by definition easy to fake, especially in situations where they can be disconnected from the qualities being signaled [@Zahavi1975].
-This coupled with the selection pressures resulting from the fact that conflicts of interest are ubiquitous among living things [@Trivers1974; @Zahavi1993] means that there is much to gain from successfully faking a signal as one could receive the benefits without paying the costs associated with the underlying quality.
-For this reason, strong selection pressures exist favoring adaptations to spot fake signals, something which has been shown to exist in many species [@Hasson1994].
-
-To overcome such counter-adaptations to cheating, an organism may produce a signal that cannot be achieved without meaningful costs in order to increase the believability of the signal [@Zahavi1975].
-The result of such signals are relatively honest displays compared to those which involve lesser costs so long as the costs involved with the signal make the signal only worth producing for those who have the underlying qualities associated with the signal [@Zahavi1993].
-Although originally formulated as an explanation for the role of costly traits in attracting mates (i.e.
-colorful plumage or large physical weaponry) [@GangestadScheyd2005; @Zahavi1975], there is no reason why it cannot be applied to the proposed signals of need as long as their costs are prohibitively high for those who are not in need.
-
-# Depression
-
-Of all the proposed signals of need, major depression has received the most attention and likely causes the most suffering.
-Although often overlooked due to its indirect connection with mortality [@PatelEtAl2004], it is the leading cause of nonfatal disease burden in the world and the second greatest contributor to global years lost to disability [@FerrariEtAl2013; @SlavichIrwin2014].
-Around 8% of people in the U.S.
-experience major depression each year, and almost 20% will experience major depression in their lifetime [@KesslerEtAl2010].
-In general, similar prevalences are often reported for depression as a whole, with there being some evidence that it is more often diagnosed in developed countries [@BrometEtAl2011].
-However, in no country is there a good understanding about how people respond to the depressed.
-
-Major depression typically involves a large-scale reduction in activity along with persistent negative feelings [@FriedNesse2014].
-These symptoms take many forms but generally fall into the categories of insomnia, weight loss, fatigue, agitation, attention problems and feelings of worthlessness.
-As these symptoms can accompany normal sadness, length is primarily used to distinguish it from minor depression, with DSM-5 requiring the existence of at least five symptoms for at least two weeks [@AmericanPsychiatricAssociation2013].
-However, it often also differs in severity, as is seen with depression’s connection to increased suicidal ideation [@BostwickPankratz2000].
-From an evolutionary perspective, it can be described as partial to complete abandonment of normally fitness enhancing behavior that also results in a reduction of benefits one provides to others [@Hagen2003].
-
-In  addition to these symptoms used by DSM-5, depression is often associated with impaired social functioning [@HirschfeldEtAl2000].
-Although causality is likely to go both ways, such impairments encompass almost the totality of social functioning with depressed individuals having smaller social groups, being more likely to perceive social interactions as negative, and having lower levels of social support [@GotlibLee1989].
-Beyond simply being a symptom of depression, a lack of improvement in various measures of social functioning is also associated with reduced chances of remission [@BillingsMoos1985], although even those who return to a non-depressed state may still have lower measures of social functioning than healthy controls [@WeissmanPaykel1974].
-
-Regardless of the exact combination of symptoms, most cases of depression are closely tied to major negative life events [@Hammen2005].
-This is clearly seen when comparing those with depression other groups, with depressed individuals often reporting at least twice as many instances of negative events than nondepressed individuals [@Mazure1998] and more negative events than those mental disorders like schizophrenia and bipolar disorder across a wide range of studies [@Paykel1994].
-In addition to differences in recent experience, the connection between negative events and depression is also seen in the high percentage of depression cases that are preceded by negative events and the rapid onset of depression following the event, both of which are seen in a largescale study of female twins that found 80% of depression cases were preceded by at least one negative life event and symptoms tending to occur within one month of the event [@KendlerEtAl1999].
-
-This strong connection between negative life events and depression along with the need and distress that likely accompanies these events has led to the suggestion that this relationship is causal [@KendlerEtAl1999].
-Support for this comes from the fact that the relationship between negative events and depression holds true when looking solely at events outside of one’s control, which shows that the connection is unlikely to be driven solely by depressed individuals creating situations where negative events are likely to be common [@Hammen2005; @KendlerEtAl1999].
-In addition to this, twin studies have shown that one’s history of negative events is still a strong predictor when controlling for genetic similarity and that part of the heritability of depression stems from the heritability of negative events, like divorce and family conflict [@KendlerBaker2007; @KendlerEtAl1999].
-
-Of the many types of negative life events associated with depression, those which involve social adversity tend to be more strongly associated with depression [@Hammen2005; @KendlerEtAl1999; @Mazure1998].
-Like the relationship between negative events as a whole and depression, this relationship is also seen cross-culturally, with the loss of a loved one, threat of divorce, or abusive relationships all increasing one’s chances of becoming depressed [@KendlerEtAl1999; @KendlerEtAl1995].
-Of these predictors, physical assault has been found to be the strongest predictor of depression in the few studies in which it has been examined [@KendlerEtAl1999; @KendlerEtAl1995] and may have been much more common throughout our evolutionary history than is often thought based on rates of spousal abuse in small-scale societies [@StieglitzEtAl2011].
-
-Except for the loss of a loved one, conflict is likely to often be present in all the previously mentioned forms of social adversity and may be one of the most meaningful aspects in bringing about depression.
-For example, breakups in both romantic and cooperative relationships are often preceded by conflict [@AmatoHohmann-Marriott2007], and surely contain it when one side wants reconciliation and the other does not.
-Likewise, abusive relationships are bound to be conflictual, with one side holding the power to harm the other and doing so.
-When looking solely at conflict as a predictor, it is often reported to be linked with depression [@AsgeirsdottirEtAl2011], with both conflict without abuse and conflict among family members also being strong predictors of depression in Western societies [@KendlerEtAl1995].
-Although too few studies exist outside of Western societies to be sure of the generalizability of this, initial studies are consistent with this, with conflict outside of the family being a predictor of depression among the Tsimané [@StieglitzEtAl2015].
-
-# Nonadaptive explanations
-
-Explanations for the relationship between social adversity and depression often involve the malfunction of mechanisms relating to low mood, which is almost universally considered adaptive when it functions properly [@Hagen2003; @Nesse1999; @WakefieldFirst2012].
-One influential version of this is the stress-diathesis model , which suggests that stressful situations interact with one’s predisposition to depression to bring about depressive symptoms [@MonroeSimons1991].
-In general, such approaches do not make distinctions between different types of stress and their effects on risk of depression nor do they predict different outcomes based on variables outside of stress levels and personality differences.
-From this perspective, the social adversity often associated with depression may simply be one way for extreme levels of stress to accumulate thereby turning what would normally be short-term sadness into long-term depression.
-
-Such approaches also generally do not make predictions on the types of responses the depressed are likely to receive, although there are exceptions.
-This is due in large part to the previously mentioned costs involved, which shift the focus of most research towards treatment [@PatelEtAl2004] and increases the size of the benefits needed for it to adaptive.
-When predictions are made about responses, they tend to involve depression resulting in negative responses due to strain the depressed’s anhedonia and impaired social functioning puts on relationships [@Coyne1976].
-From these perspectives, the costs of depression are simply too great to warrant a focus on the positive responses or too unexpected to be examined.
-
-# The bargaining model of depression
-
-Unlike these approaches, the bargaining model of depression emphasizes both the roles of social adversity and potential benefits in its explanation for why most instances of depression happen [@Hagen2002 ;@Hagen2003].
-It views depression as an oftentimes adaptive response to social adversity or other hardships in which support from others or more beneficial cooperative relationships can be gained.
-Since any biological mechanism can fail, maladaptive cases of depression are still expected to exist under this model [@Hagen2011].
-However, in many instances, it is expected to serve as a viable option to elicit more social support for those who may have few other options.
-
-The bargaining model of depression is based on the idea that for much of our evolutionary history the small groups humans lived in created many situations in which certain forms of cooperation were unlikely to be easily replaced by others while also allowing for harmful or unfair social relationships to develop [@Hagen2003].
-In these instances, one’s monopoly on one or more types of cooperation could be leveraged to change how one is treated if others value the depressed’s cooperation enough and view the depressed as being in honest need.
-In other words, depression could function similarly to a labor strike, demonstrating that one’s need was genuine; and that if the target of the signal wanted to continue receiving benefits from the depressed, he or she would need to increase support towards the signaler.
-
-Like with the other proposed signals, the costs experienced by the depressed play an important role in its function as an indicator of honest need [@Hagen2003].
-As previously mentioned, depression often involves substantial psychological pain and a largescale reduction in one’s normal routine of fitness enhancing behavior.
-This means that depression is likely unprofitable to fake as the costs involved are likely only worth experiencing by those who have high levels of need, thereby increasing the confidence of others that the signal is honest as is suggested with the other costly signaling hypotheses.
-Importantly, these costs only need to be maintained until the signaling function is thought to be met, with symptoms being expected to subside shortly after indications that future changes in social support are likely to come.
-This increases the chance that the benefits received will outweigh the costs relative to explanations that require continuous signaling and results in clear predictions about why depression ends when it does.
-
-Despite predicting many cases of depression to stem from situations in which it was adaptive ancestrally, the bargaining model does not suggest that depression should go untreated.
-This is because adaptation is not to be confused with subjective wellbeing, which is a much more important concern in every area except for explanations of why depression exists [@CosmidesTooby1999].
-However, it does suggest an explanation for why most medical treatments perform similarly to cognitive therapy [@HollonEtAl2005] and placebos [@WalshEtAl2002] in that all three methods demonstrate the existence of a knowledgeable medical professional giving active support to the depressed.
-In other words, such treatments may provide sufficient cues that the signal has worked, even though none may treat the underlying cause.
-
-# Other proposed costly signals of need
-
-As previously mentioned, the bargaining model of depression is not unique as an oftentimes adaptive explanation for harmful symptoms, with crying [@Hasson1994; @HendriksEtAl2008], self-harm [@HagenEtAl2008], suicide attempts [@Rosenthal1993; @SymeEtAl2016], and illness symptoms [@Steinkopf2015; @Tiokhin2016] having all been argued to signal need.
-
-Of these proposed signals, self-harm and suicide have the most in common with depression.
-Both are much more common for their costs than should be expected for malfunctions [@HagenEtAl2008], with suicide attempts being found across a wide range of cultures [@SymeEtAl2016; @WeissmanEtAl1999].
-As with depression, self-harm and suicide attempts tend to come in times of social adversity like divorce or neglect, both of which are situations when it is likely that social support is both greatly needed and difficult to obtain [@HagenEtAl2008].
-This connection to social adversity is clearly seen among instances of suicide attempts in the HRAF database, in which 77.4% of attempts were found to be linked to times of social conflict, and 88.7% were linked to fitness threats in general [@SymeEtAl2016].
-Importantly, 84.9% of attempts were linked to situations in which attempters were powerless to resolve their situation alone [@SymeEtAl2016], further indicating its potential as a signal of need in times when other less costly methods of bargaining are less likely to be successful, assuming the benefits are large enough on average.
-
-Unlike depression, where the costs are directly felt by the signaler and his or her targets, the bulk of the costs associated with suicide attempts are only felt in times that result in death or severe bodily harm.
-For this reason, the way others view and respond to suicide attempts is likely to be strongly influenced by the probability that the attempt would have been successful [@Rosenthal1993].
-Differences in these probabilities result primarily from the method of the attempt, which can range from little to no risk to almost certain death [@Weiss1957].
-Of the possible risk values on this continuum, the best candidates for bargaining are those in which there is a “non-negligible” but relatively unlikely chance of death [@Rosenthal1993] as those which involve minimal risk are likely to be thought of as manipulative and those which are riskier than need be not being what is expected of fine-tuned adaptations.
-Therefore, a key prediction of the bargaining model of suicide is that attempts should often result in the attempter surviving [@SymeEtAl2016].
-This is clearly the cases across the world, with attempts that do not result in death far outnumbering those that do [@CDC2014] and individuals often choosing less risky forms of suicide when methods with higher probabilities exist (i.e.
-overdosing on pills instead of jumping off of a tall building) [@Rosenthal1993].
-
-Of the proposed signals, crying has the longest history of being examined as a signal which often results in benefits and is the least controversial due to its low costs [@HendriksEtAl2008].
-For example, infant crying is almost always considered adaptive, although how it functions to elicit support is still debated, with many proposed explanations involving functions outside of signaling honest need like demonstrating quality, blackmailing parents through increased risk of predation, or manipulating parents into investing less in other offspring [@Lummaa1998].
-However, like the other proposed signals of need, it is more common when one is in need and can benefit from the support of others.
-This is seen both observationally, with crying bouts being shorter in cultures which have higher levels of parent-offspring contact [@Lummaa1998] and experimentally, with longer crying bouts being associated with shorter holding times [@HunzikerBarr1986].
-
-Like infant crying, adult crying is a human universal, with emotional tears likely being unique to humans [@HendriksEtAl2008a].
-Due to differences in what motivates support as well as differences in both the prevalence and the costs involved, it is likely that adult crying often differs from infant crying in both function and the many of the underlying psychological mechanisms.
-However, in both infants and adults, crying is an effective signal that something is wrong, with tear production and the facial sadness that often accompanies crying both increasing the perception of sadness by others [@Hasson2009] and humans being well equipped to distinguish tears of joy from tears of sadness [@HendriksVingerhoets2006].
-
-Unlike the other proposed signals of need, adult crying is frequently reported to occur without a specific external referent, with even the crier often left to wonder why it happened when it did [@VingerhoetsEtAl2000].
-However, when looking solely at bouts of crying that can be traced to a cause, it is clear that social factors are the strongest predictors, especially when conflict or loss is involved [@VingerhoetsEtAl2000; @Young1937].
-In addition to showing that crying appears in the right contexts for it to potentially be adaptive, the fact that tears which can be traced to a cause rarely occur outside of times of social need hints that it is often an honest signal.
-In line with this reasoning, the absence of an effective sadness display has been shown to reduce supportive behavior, suggesting that properly displaying sadness (with which crying helps) increases the confidence of others that one is in need [@Barr-Zisowitz2000; @Diminich2016].
-However, the fact that adults often cry out of sight of others suggests that its occurrence cannot be explained solely by a signaling explanation [@VingerhoetsEtAl2000].
-
-Compared to depression, self-harm, and suicide attempts, the costs of crying are much less severe, and it is unclear if its costs are significant enough to result in honest displays on their own [@Hasson2009].
-One important area in which the costs of crying are likely to be felt is through reputation hits, with crying often lowering how others view a person  [@HendriksVingerhoets2006].
-While true of both sexes, this may be particularly true if the target of the signal is a man, as men have been shown to simply avoid crying people more often than women in experimental settings.
-Although not directly linked to crying, sadness, which almost certainly accompanies most instances of crying, tends to slow both cognitive and motor functioning [@Diminich2016; @Ekman2003; @EllgringScherer1996] thereby imposing at least some opportunity costs surrounding and during bouts of crying, something that may be directly seen with the blurred vision that comes with tears [@Hasson2009].
-When sadness is already present, crying may simply exacerbate this distress, as is seen physiologically with the increased hearts rate and blood pressure that typically accompanies crying taking time to return to normal levels after crying [@HendriksEtAl2008]
-
-Although tied to a different type of need and not included in the study presented here, illness symptoms provide another strong candidate as a way for costly symptoms to function as a signal of need and are, therefore, worthy of being included in this comparison.
-Referred to as the signaling theory of symptoms, the idea is that while illness symptoms initially arose as the result of defenses against disease or a pathogen’s circumvention of these defenses, they quickly became cues for conspecifics to alter their behavior to better avoid illness, take advantage of a rival’s weakened state, or help kin and close allies [@Steinkopf2015; @Tiokhin2016].
-Although the first two conditions would likely favor the suppression of symptoms, times in which help could be received may have favored times in which symptoms would become signals of honest need as opposed to just cues.
-The reason for this is once strategies for providing support to the sick became common enough, selection would likely favor those who could fake symptoms, which would then favor anti-cheating adaptations that require symptoms that were hard to fake to be believed.
-In these instances, those who upregulated already present symptoms beyond the optimum for disease fighting would provide a more honest, costly signal and, therefore, be more likely to satisfy the anti-cheating adaptations of others and increase their chances of receiving aid.
-
-Formulated as an explanation for placebo responses, the best evidence in favor of the signaling theory of symptoms comes from the observation that placebo responses tend to occur after signs that care has been given, with the placebo response simply being viewed as the return to symptom levels appropriate for disease fighting without the added signaling component [@Steinkopf2015].
-Therefore, like the other proposed signals of need, its occurrence is expected to be highly dependent on social context in both predicting its occurrence and its cessation.
-This is seen experimentally in that placebo responses which often work in the presence of healthcare providers can be completely negated if the person is instructed to complete their treatment alone [@HashishEtAl1988].
-However, presence alone is also not enough, as should be expected of a signaling explanation.
-Instead, demeanor is also highly important, with facial expression indicating care and concern resulting in more placebo responses than neutral or disinterested faces [@Benedetti2009; @Steinkopf2015].
-
-# Key similarities shared by the proposed costly signals of need
-
-Viewed collectively, the proposed signals of need clearly share some important similarities which can allow for generalizations about when they should be most common and under which situations they are most likely to be adaptive.
-When it comes to prevalence, their hypothesized functions as signals suggests they should all be more common when there is a high degree of private information held by the signaler (i.e.
-when the targets of the signal do not have information about the honesty of need) [@Hagen2003].
-This is due to the previously mentioned ubiquity of conflicts of interest, which incentivizes deception and favors strategies in which individuals are only likely to increase their support of others if their counter-cheating adaptations are satisfied.
-For this reason, signals should be more common when the target has little information to confirm the signaler is in need and less common when such information exists as the signaling component of any trait or state is created primarily to provide another organism with information.
-Indeed, in instances of public information, the expectation is that both parties should be able to bargain quickly as there is nothing in the way of both sides figuring out how the benefits should be divided [@KennanWilson1993].
-
-One basic similarity that allows for more detailed predictions is that all the proposed signals are predicted to result in benefits that make up for the costs involved, at least on average.
-Although this seems more relevant to what happens after the signal, it also has important implications for when signals might be employed since smaller forms of support are likely to be sufficient for the less-costly signals to be worth it, with the costlier signals requiring larger gains all else being equal.
-Therefore, it is reasonable to expect the less costly signals to be more common, something which is seen with instances of crying far outnumbering cases of depression, which far outnumbers the cases of suicide attempts [@KesslerBromet2013; @NockKessler2006; @vanHemertEtAl2011].
-
-One way to reduce the average costs of the proposed signals, and therefore increase the times which they may be applicable, is to only engage in them in situations where large payoffs are relatively likely [@Rosenthal1993].
-Although little has been done to investigate the existence of such mechanisms, it is a reasonable trait to expect of the proposed costly signals of need if they are adaptive.
-This is because the absence of such systems would decrease the amount of ways the proposed signals could have evolved as adaptations due to the role selection would play in disfavoring strategies that led to dangerous misfires and worsened conditions in times in which such outcomes may be the costliest.
-Without these mechanisms, the adaptive nature of the proposed signals of need may be confined only to times of extreme need, as such situations may reduce the costs of signaling to such an extent that the relevance of the likelihood of support to levels where it becomes much less relevant [@HagenEtAl2008; @Tiokhin2016].
-
-Evidence for this may be seen with findings that suggest that some of the proposed costly signals of need are more common in situations where they are more culturally acceptable and where help may be more available.
-For example, the size of the female biased sex difference in depression was found to differ in relation to gender equity, with more equitable societies experiencing larger gender gaps despite overall lower rates of depression [@HopcroftBradley2007].
-This same pattern is seen with crying, with women crying more often in countries with greater gender equality, something which clearly runs counter to models which emphasize the causal role of stress overloads [@vanHemertEtAl2011].
-One possible reason for these relationships is that women in more equal societies signal more because they are more likely to receive support.
-Consistent with this interpretation is the fact that while crying tends to not result in improved emotional states in general [@HendriksEtAl2008], it does result in women feeling better after crying in countries with relative equality [@BechtVingerhoets2002] and when social support is present [@RottenbergEtAl2008].
-
-In addition to not engaging in a signaling strategy that is likely to result in insufficient support, only investing in a signal of need when one does not have any less costly alternative options is another likely way to reduce the average costs of the proposed signals.
-This prediction is clearly built into the unified model of anger and depression, which proposes that anger and depression may be complementary strategies, with aggression being favored by those who have the formidability to bargain effectively through the use of force and depression favored by those that cannot [@HagenRosenstrom2016].
-Support for this comes from the finding that differences in upper body strength account for much of the female biased sex difference seen in depression.
-Importantly, this sexually dimorphic pattern of women experiencing depression symptoms more often than men is also seen in all the other proposed costly signals examined here [@CDC2014; @vanHemertEtAl2011], suggesting that less costly bargaining methods are reliably favored, assuming there is a similar scarcity of alternatives for women relative to men.
-
-Although not derived from the similarities of the theories explored here in the same way as the previous traits, a key similarity shared by the signals is that the costs associated with signaling will almost always be less than the costs of the symptoms themselves since some level of symptomology is likely to be present that is not tied to a signaling function.
-In other words, the cost of engaging in a costly signal of need is often going to be less than the symptoms the recipient sees.
-This is clearly seen with illness symptoms if the signaling theory of symptoms is correct, in that much of one’s symptoms will be the result the body’s defense mechanisms or a pathogens circumvention of these defenses even in instances in which they are upregulated for a signaling function [@Steinkopf2015; @Tiokhin2016].
-Therefore, the costs of signaling may only be a small part of the totality of the symptom.
-Although such a situation is harder to imagine with depression or suicide attempts, extreme cases of conflict or abuse may result in situations in which the difference between a depressed and a nondepressed state may be much closer than normal [@Hagen2003].
-
-# Benefits
-
-For the proposed signals of need to be worth the costs, substantial benefits in terms of social support are expected by their corresponding theories, either in the form of support or renegotiated social relationships.
-When it comes to depression, self-harm, and suicide, the most likely benefits are expected to be long-term changes in how one is treated [@Hagen2003; @HagenEtAl2008; @SymeEtAl2016].
-This can take the form of reconciliations in failing relationships, increased fairness in cooperative relationships, or an increase of resources being directed towards an individual.
-Of all the benefits, a reduction in physical abuse may be one of the most important, with physical abuse likely being a common occurrence over our evolutionary history based on the high prevalence of it in traditional societies [@StieglitzEtAl2011].
-
-The benefits of the less costly signals are likely to be more varied due to their low costs allowing smaller benefits to make them worthwhile.
-These benefits may therefore be more short-term in nature and come from relationships without large conflicts of interest.
-In regard to crying, a demonstration of need beyond a verbal request may increase the chances of short-term changes in resource allocation or interventions into social conflicts outside of the signaler-target relationship.
-When it comes to illness symptoms, greater symptomology is expected to increase the likelihood of support when one cannot satisfy their own needs [@Steinkopf2015; @Tiokhin2016] and may also decrease the risk of reputation hits that might come from the belief that one is faking illness , both of which might be well worth a minor increase in symptomology which might already exist.
-
-Whether long-term or short-term, social support is often classified as emotional or instrumental (material support), with there currently being little empirical evidence on their relative importance (Jacobson, 1986).
-However, if emotions are viewed as motivators to guide behavior towards adaptive outcomes (Nesse, 1990; Tooby & Cosmides, 2008), it is unlikely emotional support is the ultimate goal.
-Instead, emotional support may be the desired outcome of proximate mechanisms which favor greater investment in relationships to increase the likelihood of future instrumental support if one needs it (the ultimate benefit).
-It is also conceivable that emotional support might track achieved support so that emotional support is high when one’s needs are being met.
-If this is the case, changes in emotional support may still be informative to signaling approaches as achieved support is likely to cause individuals to believe there is less need to signal, assuming an honest display needs to only be made once.
-
-Although less meaningful when examining responses to the proposed signals, the distinction between received and perceived social support is likely more useful when considering how information about social support is stored, with received support being material support and perceived support being one’s perceptions about the likelihood and adequacy of future support [@NorrisKaniasty1996; @WethingtonKessler1986].
-Unlike the relative importance of material and emotional support where the evidence is ambiguous, here, the evidence suggests that perceived support is the more powerful of the two in predicting positive outcomes, with the two not being as closely related to each other as often expected [@HaberEtAl2007; @NorrisKaniasty1996].
-Although evident in many areas, the disconnect between received and perceived social support is particularly noticeable in the finding that perceived social support often decreases in times of need, even in situations in which one is likely experiencing more material support than in one’s life before the need [@NorrisKaniasty1996].
-
-When examining the costly signals of need, the gap between current levels of received social support and the potential support that could be gained through a signaling strategy is likely to be the most important measure as this is what defines the size of the benefits.
-As this would involve information about both one’s level of need as well as information about the likelihood and size of potential help, it may essentially be a measure of perceived support as defined above.
-Therefore, perceived social support might form an important link between the severity of one’s situation and the amount of help deemed sufficient to avoid or stop a signaling strategy.
-In connecting the two, this conceptualization has the potential to explain why low levels of perceived social support are a strong predictor of depression [@KendlerGardner2014; @LeskelaEtAl2008; @ParkEtAl2016] and a potential predictor of the symptom upregulation found in placebo responses [@Humphrey2002].
-
-# Responses to the proposed costly signals of need
-
-Most studies examining responses to depression have been observational and focused on responses outside of changes in social support.
-In general, most report aversive responses and high levels of rejection towards the depressed, and depressed individuals are often linked to impaired social functioning [@EvraireDozois2011; @GotlibLee1989; @HirschfeldEtAl2000].
-One explanation for this is that depressed individuals engage in behaviors that drive others away.
-In line with this reasoning, both excessive reassurance seeking and negative feedback seeking, which often accompany depression, have been shown to elicit negative emotional responses from others and increase the chance of rejection from others [@JoinerMetalsky1995; @StarrDavila2008].
-Negative interactions are also seen in families as depressed children tend to report less support and more negative responses from parents than non-depressed children, although it has not been demonstrated that such interactions did not lead to depression in the first place [@MesserGross1995; @SchwartzEtAl2012].
-
-Beneficial responses to the depressed are also reported.
-This is seen in that depression has been shown to reduce the likelihood of aggression within families, particularly in families already experiencing high levels of conflict [@SheeberEtAl2001].
-There is also limited evidence that depression can result in increased levels of support from others outside the family.
-For example, non-depressed individuals were shown to be more cooperative and exhibit more caretaking behavior towards their college depressed roommates over the course of their time living together [@HokansonEtAl1986].
-Likewise, a vignette study found that individuals were more likely to provide advice and support to depressed individuals than anxious individuals despite similar levels of distress [@StephensEtAl1987].
-
-Responses to crying have received more attention, often from a signaling perspective.
-These responses are generally positive when it comes to infant crying and instrumental outcomes like the amount of care directed towards the infant or its proximity to its parents [@LinMcFatter2012].
-However, crying is also associated with increased distress and other negative emotions in parents and may increase the child’s risk of maltreatment if it is in poor condition [@LinMcFatter2012; @Soltis2004].
-Responses to adult crying tend to be similar with negative responses typically involving emotions and positive ones involving the likelihood of providing support.
-For example, individuals faced with crying scenarios in a vignette study experienced more negative emotions relative to controls while also being more likely to provide emotional help and hide negative feelings [@HendriksEtAl2008].
-Likewise, another experimental study found that while crying increased social support, it came at the cost of being perceived as helpless [@VingerhoetsEtAl2016].
-It is important to note, however, that this trend is not always the case as crying can elicit positive emotions like perceived friendliness [@VingerhoetsEtAl2016] and result in negative outward responses like confrontations or mocking at the extreme end [@WagnerEtAl1997].
-
-Unfortunately, there are few studies examining how individuals respond to suicide attempt survivors.
-In those which exist, stigmatization is commonly reported within and outside families [@FreyEtAl2017; @ScoccoEtAl2012], with perceptions of survivors as being weak, selfish, mentally ill, and antisocial all being commonly reported [@BatterhamEtAl2013; @FreyEtAl2016; @TzengLipson2004].
-Although these types of stigmatization have been reported across relationships types, the likelihood of stigma has been found to differ based on who the survivor is to the person being questioned.
-This is seen in a study which found that individuals felt the most stigma from members of their preexisting social networks than mental health providers, with family members providing more stigmatization (57.1% of the time) than romantic partners (41.2% of the time) and close friends (28.2% of the time) [@FreyEtAl2016a].
-
-A factor analysis of responses to suicide survivors found that stigma related to suicide attempts could largely be described by three factors: weak, crazy, and distressed [@CorriganEtAl2017].
-When it existed, prejudice was described by two factors (fear/distrust and anger) and discrimination by three (avoidance, disdain, and coercion).
-A later vignette study which examined these factors across mental health problems found that participants had higher levels of stigmatization towards imagined characters who attempted suicide (both survivors and non-survivors) than depressed or mentally ill characters [@SheehanEtAl2017].
-In addition to this, the suicide vignettes also resulted in more anger than the other conditions; however, discriminatory behavior was about equal regardless of whether the attempt resulted in death or accompanied depression.
-
-Although negative responses to suicide survivors are more often studied and reported, positive responses have also been found.
-Increased social support and changes to important relationships are often reported to follow suicide attempts with some indication that these effects may hold long term [@Stengel1956].
-For example, a study of 100 women who survived suicide attempts found that in 75 cases, individuals gained identifiable benefits through the attempt, with 41 individuals benefiting from reconciliations with others [@Lukianowicz1971].
-As for the type of support received, emotional support seems to be more commonly provided than instrumental support based on initial evidence [@FreyEtAl2017]; however, it is currently unclear how this might change with social context.
-
-Unfortunately, the evidence regarding responses to suicide in traditional societies is indirect or anecdotal.
-Unlike Western countries, where suicide is often viewed as pathological [@Hidaka2012], members of traditional societies have been reported to view suicide attempts as cries for help rather than mental illness [@Shostak1981], suggesting that help is at least occasionally provided or reliably expected.
-Further evidence for this comes primarily from the situations in which suicide attempts are made, with suicide attempts often being described as ways of escaping unwanted marriage arrangements, persistent abuse, or a lack of support in obtaining mates [@GutierrezdePinedaMuirden1948; @Hilger1957; @Karsten1935; @Tessmann1930; @Wilson1960].
-Although most reports focus mainly on suicide attempts that result in death, there is some indication that the threat of it or a survived attempt can result in increased support, as was the case with the threat of suicide helping a !Kung woman escape an arranged marriage [@Shostak1981].
-
-# Why responses differ
-
-Compared to the empirical examinations of the responses of others to the proposed signals of need, the theory is much more advanced and responsible for several testable hypotheses.
-Likely the most basic is that costlier signals will elicit greater benefits all else being equal.
-This is mainly due to the previously mentioned relationship between the costs of a signal and its honesty, which results in costlier signals better satisfying the anti-cheating adaptations of others than less costly alternatives [@Zahavi1993].
-In addition to this, the requirement that the benefits received need to outweigh the costs of producing the signals on average also suggests that the costlier signals will often result in more substantial support as increased costs must be met by increased benefits for them to be adaptive.
-
-One area where all else is not equal and less costly signals may outperform costlier ones is times of minor need.
-Though not yet demonstrated empirically, it is reasonable to suspect an interaction between signal strength and need whereby stronger signals only tend to result in more positive responses in times where the signal is proportional to the need.
-In other words, too strong of a signal in times of minor need might send a stronger message of dysfunction than need.
-This may be problematic for the signaler because although dysfunction might still mean support is needed, its presence likely indicates that there is less to gain through supporting the individual through direct reciprocity regardless of relationship type and inclusive fitness if the supporter is related to the signaler and the perception of dysfunction is substantial [@SugiyamaSugiyama2003].
-
-Although less examined empirically than the relationship between the cost of a signal and its honesty, it is also reasonable to expect that existing conflict will require costlier signals to be effective.
-This is mainly due to the likelihood that existing social conflict means larger conflicts of interest are involved, which would therefore require the signaler to be in relatively greater need to be worth helping than in instances with no conflict.
-High degrees of conflict with the signaler may also increase one’s scrutiny of the signals, which would once again favor costly displays.
-In addition to fitting signaling theory, such a prediction is also consistent with the previously mentioned predictive relationship between conflict and depression, as depression is an extremely costly state to experience.
-Since the proposed signals of need often come in response to social adversity and are predicted to serve as a way to increase social support, it is also reasonable to expect that relational level differences are likely be more important than individual level differences in affecting how others respond to signaling.
-This seems to be borne indirectly out in the few studies that exist on the topic with relational level differences being the better predictor of the amount of disclosure suicide survivors were likely to give family members [@FreyFulginiti2017; @FulginitiEtAl2016], something that is associated with more positive responses from family members and lower depression scores [@FreyEtAl2016a].
-However, it is unclear if it was disclosure itself or being in a more open family that resulted in positive responses.
-
-Another situation when relational level variables might be important is in times of divergent welfare tradeoff ratios (i.e.
-when one partner values the other more than they are valued in return) in relationships defined by reciprocal altruism [@Sell2005].
-In these instances, the less valued partner may have more to gain in supporting the more valued individual due to the benefits of maintaining future support, assuming the reason for the differential WTR is not due to kinship (i.e.
-younger kin valuing older kin less) or disability (which would make reciprocal altruism unlikely).
-In addition to this, such times of need would also create opportunities for the less valued partner to close the gap in WTR for future benefits by providing important support, potentially making support more likely than if the roles were reversed.
-
-It is important to note that the relative importance of relational level differences does not mean individual differences are likely to be unimportant.
-This is especially the case when these differences contribute to differences in one social environment [@KendlerEtAl1999].
-Although not evidence of responses to need, such a situation is seen with many of the social situations associated with depression being heritable like divorce and family conflict [@KendlerBaker2007].
-If positive relationship outcomes are also heritable in a similar way as is reasonable to expect, then individual level differences would also affect how much help is provided in ways that would be hidden by relational variables, rather than simply leading to differences in likelihoods of occurrence.
-
-Beyond one’s social environment, individual differences may also result in differences in how effective various signals and their alternatives are, thereby influencing how one is responded to.
-Although not a costly signal as envisioned here, anger is clearly involved with signaling displays and should be expected to work better for those with more formidability [@HagenRosenstrom2016].
-As previously mentioned, this has been suggested to explain the sex difference in depression, with women being less likely to effectively bargain through aggression.
-However, if depression and anger from complementary bargaining strategies, it is also conceivable that men may have more to lose from depression.
-Although speculative with depression, this appears to be the case with crying, with men often being responded to less favorably to than women [@CretserEtAl1982; @Jesser1989] although this is not a universal finding [@HendriksEtAl2008].
-
-# Study Aims and Predictions
-
-The relative lack of studies on responses to the proposed signals of need thus far has meant that a key line of evidence regarding the plausibility of their adaptive nature is underdeveloped, something which is compounded by the fact that many of the studies examining the costlier signals are focused solely on negative responses.
-In this study, we examine responses to many of the proposed signals of need in response to different social circumstances (i.e.
-high or low conflict and the amount and direction of information about honest need).
-Although this is done for all the signals in the confirmatory portion of the study, we turn our focus to depression and the less costly signals in our exploratory analyses.
-
-In response to the previously mentioned hypotheses, we predict that stronger signals will result in higher levels of both emotional and instrumental social support (i.e.
-likelihood of providing help or how much money one is willing to give) towards the signaler.
-Specifically, we predict that the signals will have the following rank order form low to high: no signal (control), verbal request, facial sadness with crying, depression, depression with display of suicidal ideation, and suicide attempt.
-We also predict that anger will have a positive impact on helping with a similar magnitude to the depression condition.
-Unlike the hypothesized signals of need, we predict that the schizophrenic break condition will decrease the likelihood of help relative to the control since it indicates cognitive dysfunction and its symptoms are not expected to have a signaling component.
-
-Although instances of private information are likely to result in the highest prevalence of signaling behavior, it is unlikely that they will result in the most helping behavior.
-Instead, we predict that instances of public information of honest need are likely to result in the most help as external information of need is likely a more reliable indicator of need than signals under most circumstances.
-In line with this reasoning, we also predict that private information will result in more support than public information of cheating as even costly signaling attempts may not overcome reliable information of a lack of need.
-Due to the previously mentioned likelihood that conflict increases skepticism on the part of signal targets, our last predicted main effect is that a lack of conflict will result in more favorable reactions than the conflict conditions.
-
-In addition to these main effects we also predict several interactions.
-Regarding signal strength and information, we predict that the signals will have the greatest impact on the participant's responses when a participant has no information about whether the character is lying or telling the truth so that the coefficient for signal strength will be greater in the private information condition relative to the public information conditions.
-In instances where participants have information that the sister is likely cheating, we predict that the costlier signals will be more aversive than the less costly signals, in opposition to our prediction on the main effect of signal strength.
-
-Due to the same reason underlying our prediction for the main effect of conflict, we also predict two interactions with conflict.
-The first is that the effect of signal strength will be larger in the conflict condition compared to no conflict condition.
-The second is that private information will have a greater negative impact on helping in the conflict condition than the no conflict condition.
-
-# Materials and methods
+The second was posted on the samplesize subreddit with the goals of testing the beleivability of the new vignettes and how pro-signaler participants were at T1, with a power analysis with simulated data showing this would limit our power.
+In this small sample of 28, we saw no evidence that beleivabilty was a problem and no evidence that participants as a whole would be too pro-sister at T1.
 
@@
 
-The vignettes for this study were designed to result in a situation in which requested support was costly but worth providing if the requester was truly in need.
-In this study, this took the form of having participants put themselves in situations in which an imagined sister was requesting a loan of $50,000 from them that was originally saved for their imagined daughter’s college education.
-Regardless of the manipulations, each vignette consisted of two parts, the main storyline which included the conflict and information manipulations and a signal portion that was presented after the participants answered the first set of main outcome questions and the only attention check.
+Four vignettes were used in this study, with participants in the US sample being randomly assigned to either the "basketball coach," "romantic partner," or "brother-in-law" vignettes.
+In the "basketball coach" scenario, the star player on a unversity basketball team comes to the participant (who is asked to imagine themselves as the athletic director at a university) and claims she was sexually assaulted by the coach.
+However, there are indications the player might be lying to get more playing time.
 
-## Factorial Design
+The "brother-in-law" vignette involved participants imagining that they let their sister, brother-in-law, and niece move in with the participant and an imagined 15-year-old daughter after they lost their house in a fire.
+During this time, the participant's daughter becomes jealous of your niece before accusing her uncle of sexually assaulting her.
 
-The design of this study was a between-subject full factorial design in which three theoretically relevant variables were manipulated: (1) the level of conflict in the relationship, (2) the degree to which one had information about whether or not the person in the vignette is genuinely in need, and (3) the type of signal (or control).
+The "romantic partner" vignette hard participants imagine that they found the best partner they have ever had after years of being single.
+However, their 13-year-old daughter, who has a history of trying to get in the way of their relationships is clearly not happy with this.
+At one point, she accuses the romantic partner of physically assaulting her but cannot produce any evidence.
 
-The amount of conflict within the relationship had a high and a low condition, which was manipulated by describing the participants’ relationship with their sister as “competitive and full of conflict” or “supportive and free of conflict.” The amount of information the participant had on the likelihood the request representing honest need had three conditions: (1) information their sister was misleading them, (2) information their sister was experiencing honest need, and (3) a high degree of private information in which no information about the likelihood of it being an honest request was given.
-Due to the fact that baseline levels for the emotional and instrumental variables were not taken before the conflict and information manipulations, comparisons on the impact of these manipulations must be between-subjects.
+Those in the Indian sample only saw the "thwarted marriage vignette." In this scenario, the participant and their family is trying to arrange a dowry for their older daughter so she can marry the man she loves.
+After his family demands more money, the participant's family tries to find another man, who the older daughter claims to find unattractive.
+However, it is unclear how unattractive he is and any additional investment in the dowry will come at the expense of the younger daughter.
 
-For our signal manipulation, six types of signals accompanying verbal requests were tested: (1) a verbal request alone, (2) facial sadness with crying, (3) depression, (4) anger, (5) depression with display of suicidal ideation, and (6) a suicide attempt.
+The full vignettes are available in the supplementary information.
+
+## Signals
+
+The sole treatment in this study was the signal participants saw, with these signals including: (1) a verbal request without additional signaling, (2) crying, (3) mild-depression, (4) depression and, (5) a suicide attempt.
+
 As the amount of crying in those with depression is moderately associated with depression severity [@VingerhoetsEtAl2016] and depression is a major risk factor for suicide [@BostwickPankratz2000; @Kessler2012], each signal was designed to build off of the less costly signals so that each signal contained elements of any signal it was costlier than.
-In addition to these hypothesized signals, two controls were also tested: (1) a no signal control in which the participant attempts to talk to her or his sister but finds that she is not home and (2) a psychotic break condition in which the sister displayed symptoms consistent with schizophrenia to control for severity alone causing changes in help.
-
-Unfortunately, it became clear after the study was completed that our no signal control was flawed due to the fact that a verbal request was always included in the main part of the vignette.
-Therefore, although the control had no signal after the main vignette, there was still a signal present before.
-For this reason, verbal request may be the closest condition to a control we have, with our original control simply being a one-time verbal request.
 
 ## Preregistrations
+
+add pregistered predictions here or at end of intro?
 
@@
 
-All participants were over 18, located in the United States, had a HIT approval rate of over 95%, and had successfully completed at least 100 HITs as anything less results in approval rates of 100% [@KennedyEtAl2018].
-To ensure participants were paying attention to the vignette, a 5-question attention check was included which involved questions addressing the topics of manipulations as well as who was making the request and how much money was saved for the daughter.
-Informed consent was given by proceeding with the study after reading the consent form, and all participants who passed at least 4 of the 5 attention checks were paid $1 for their time.
+All participants in the US sample were over 18, located in the United States, had a HIT approval rate of over 98%, and had successfully completed at least 100 HITs as anything less results in approval rates of 100% [@KennedyEtAl2018].
+The Indian sample was the same except for only including participants who resided in India at the time of the study and the inclusion two participants who were included with a stricter HIT approval rate of over 99%.
 
-Although all participants who passed the attention checks and finished the survey were paid, additional exclusions were made to reduce the noise from low quality data.
-This involved removing data with response times under 215 seconds unless the participant provided a comment of over 10 words in response to the open-ended feedback prompt, with the time cutoff being selected for being as fast as one could complete the study while paying attention to the relevant parts based on trial runs and the word cutoff being based on the likelihood that someone rushing through the study would not spend the extra time to fill in an optional section.
-In addition to this, participants were also excluded for either having identical GeoIP addresses to at least six other survey completions or an IP address flagged as suspicious of VPS use by the R package rIP.
-This was due to the reported association between fraudulent, low quality responses to both VPS use and multiple responses [@KennedyEtAl2018].
-The cutoff of 6 was chosen through the use of regression trees which indicated an attention check failure rate of almost 64% for individuals whose GeoIP matched at least 6 other responses.
+To ensure participants were paying attention, we used a variety of attention checks, which we clearly labeled in an attempt to avoid demand characteristics.
+The first was shown immediately after the consent form and provided participants with a random word and asked them to enter the vowels in the order in which they are found in the word.
+Capitalization did not matter and no word contained repeat vowels.
+Failure to enter the correct vowels in order resulted in the participants being filtered out of the study.
+The second followed the vignette and involved asking three questions about the story that should be easy to answer for anyone paying attention.
+
+We also filtered out those who read the vignette faster than one-third the time it took MG to read it as fast as possible without concern for comprehension immediately after the vignette.
+
+Informed consent was given by proceeding with the study after reading the consent form, and all participants who passed the attention checks were paid $1 for their time. (mention time here)
 
@@
 
-Although distributed through MTurk, every participant took the survey using Qualtrics.
-In every instance, the elements of the survey were laid out in the following order: 1) the consent form, 2) the main body of the vignette, 3) the first set of outcome measures (pre-signal), 4) the first set of manipulation checks, 5) the attention checks, 6) the signal portion of the vignette, 7) the second set of outcome measures (post-signal), 8) the second set of manipulation checks, 9) a set of demographic questions, and 10) an open feedback prompt.
-See Appendix 10 for the complete survey.
+After accepting the HIT on MTurk, every participant took the survey using Qualtrics.
+In every instance, the elements of the survey were laid out in the following order: 1) the consent form, 2) the vowel attention check, 3) the main body of the vignette, 3) the pre-test baseline measures (T1), 4) the story content attention check, 5)  the signal portion of the vignette, 7) the post-test outcome measures (T2), 8) an attention check that did not filter out participants, 9) a set of demographic questions, and 10) an open feedback prompt.
+The full survey can be found in the SI.
 
-### Outcome measures
+### Baseline measures (T1)
 
-Both emotional and instrumental responses were measured in the survey portion of the study.
-In a small pilot study, we initially asked the same questions before and after the signal was shown to measure how the signal affected one’s responses.
-However, due to the prevalence of ceiling and floor effects, the majority of the questions following the signal in this study were revised to ask if and how one’s likelihood of helping or feeling certain emotions changed.
-This resulted in 22 outcome measures, with 11 being asked before the signal and 11 after (See Table 1 for the full list and Table 2 for summary statistics).
-In both instances, the order of the questions was randomized to avoid order effects [@KrosnickAlwin1987].
+In both samples, we recorded self-reports on how much participants believed the signaler to be telling the truth (BeliefT1) and the likelihood of them helping the signaler as requestedc (ActionT1).
+With the thwarted marriage vignette we also asked how they would split the money they had saved for the dowry between their daughters (Divide T1).
+In every instance, the order of the questions was randomized to avoid order effects [@KrosnickAlwin1987].
 
-To measure these responses, sliders which functioned largely as visual analogue scales were used due to the fact they allow for finer grained changes than categorical scales and provide a continuum of scores [@KlimekEtAl2017].
-For the pre-signal set of questions, only the ends of each continuum were labeled with some variant of extremely likely and extremely unlikely being used for each measure.
-For the second set, the center was labelled no change, and the ends of each continuum were labelled as some variant of much more likely and much less likely.
+Responses were recorded with sliders due to the fact they allow for finer grained changes than categorical scales [@KlimekEtAl2017].
+In every instance the position started at the left due to findings that people may be less likely to move the slider when it starts in the center (cite and word better).
+For the exact wording of the question and the ends of each continuum, see table 1.
 
-[deleted MA results stuff]
+We also asked which emotions participants felt the signaler was experiencing using a multiple choice question in which they could select multiple options.
+This included emotions directly related to the signals (e.g., sad, depressed, and suicidal), states which suggest genuine need (traumatized and violated), and states which suggest deception (e.g., deviousness or jealousy).
+The complete list can be found in the SI.
 
-In addition to this, the amount of money participants were comfortable lending to their imagined sisters was asked and was measured with a slider which ranged from $0 to $50,000 and allowed the participant to see the amount they were selecting.
-Unlike the previously described measures, it was repeated identically at both time periods and asked on its own page due to the desire to save the only question that allowed for partial support for after those with less flexibility were asked.
+### Post-treatment measures (T2-T4)
 
-Of these variables, 3 post-signal measures (Time 2) are used as dependent variables in confirmatory analyses, (1) the amount the sister needed the money as percieved by the participants, (2) the likelihood that participants would lend the money, and (3) the amount of money participants would be comfortable lending in this sceario.
+We asked questions identical to those asked at T1 as the main post-treatment variables of interest (T2).
+For the belief, action, and divide variables, the position of the slider starting where participants placed it at T1.
+For the T2 emotion variables this involved no changes from the T1 version.
 
-Variable | Wording | Coding
----------|---------|-------
-Perceived need of money at T1 | How much do you think your sister needs this money? | 0: Not at all; 100: A great deal
-How likely to lend money at T1 | How likely are you to lend the money to your sister? | 0: Very unlikely; 100: Very likely
-How angry are you about the request at T1 | How angry do you feel about this request? | 0: Not at all angry; 100: Extremely angry
-How satisfied to help at T1 | How much satisfaction would you get from helping with this request? | 0: No satisfaction; 100: A great deal of satisfaction
-How sad about health problem at T1 | How sad were you to learn about your sister’s child’s health problem? | 0: Not sad; 100: Devastated
-How reasonable is the amount requested at T1 | How reasonable is the amount of money being requested? | 0: Extremely unreasonable; 100: Extremely reasonable
-How much do believe the niece is ill at T1 | How much do you believe your sister’s child has a health problem? | 0: Extremely unbelieving; 100: Extremely believing
-How much harm will your daughter suffer at T1 | How much harm do you think this would cause to your daughter Sophie? | 0: None at all; 100: A great deal
-Suspicion of sister at T1 | How much do you suspect that this might be an attempt by your sister to get you to lend her money for another purpose?
-| 0: I'm very suspicious; 100: I'm completely unsuspicious
-Perceived benefit to sister at T1 | How much help would lending the money to your sister help her and her child? | 0: None at all; 100: A great deal
-Trust that sister will repay at T1 | How much do you trust that your sister will pay you back? | 0: Extremely distrustful; 100: Extremely trustful
-Amount conformtable lending at T1 in dollars | What amount of money would you be comfortable with lending to your sister in this scenario in US dollars? | 0 - 50000
-How close to sister at T1 | Having read the story, how close do you feel to your sister? | 0: Extremely distant; 100: Extremely close
-Change in perceived need of money at T2 | After going to your sister’s house, has your belief that your sister needs the money increased, decreased, or not changed?
-| -50: Decreased greatly; 0: No change; 50: Increased greatly
-Change in how likely to lend money at T2 | After going to your sister’s house, are you more willing to lend her the money than before, less willing than before, or no change?
-| -50: Much less willing; 0: No change; 50: Much more willing
-Change in anger about the request at T2 | After going to your sister’s house, has your sister’s request for money made you more angry than you were, less angry than you were, or no change?
-| -50: Much less angry; 0: No change; 50: Much more angry
-Change in How satisfied to help at T2 | After going to your sister's house, would you feel more satisfaction from helping your sister, less satisfaction, or no change?
-| -50: Much less satisfaction; 0: No change; 50: Much more satisfaction
-Change in How sad about health problem at T2 | After going to your sister’s house, are you more sad than you were about your sister’s child’s health problem, less sad than you were, or no change?
-| -50: Much less sad; 0: No change; 50: Much more sad
-Change in How reasonable is the amount requested at T2 | After going to your sister’s house, do you think the amount of money she requested is more reasonable than before, less reasonable than before, or no change?
-| -50: Much less reasonable; 0: No change; 50: Much more reasonable
-Change in How much do believe the niece is ill at T2 | After going to your sister’s house, has your belief that your sister’s child has a health problem increased, decreased, or not changed?
-| -50: Decreased greatly; 0: No change; 50: Increased greatly
-Change in How much harm will your daughter suffer at T2 | After going to your sister’s house, do you now think lending the money to your sister would harm your daughter Sophie more than you thought, less than you thought, or no change?
-| -50: Cause much less harm; 0: No change; 50: Cause much more harm
-Change in Suspicion of sister at T2 | After going to your sister’s house, are you more suspicious that this might be an attempt to get you to lend her money for another purpose, less suspicious, or no change?
-| -50: Much less suspicious; 0: No change; 50: Much more suspicious
-Change in Perceived benefit to sister at T2 | After going to your sister’s house, do you think lending the money to your sister would help her child more than you did before, less than before did before, or no change?
-| -50: Much less help; 0: No change; 50: Much more help
-Change in Trust that sister will repay at T2 | After going to your sister’s house, are you more trusting that your sister will pay you back than you were before, less trusting than you were before, or no change?
-| -50: Much less trusting ; 0:  No change; 50: Much more trusting
-Change in Amount conformtable lending at T2 in dollars | After going to your sister's house, what amount of money would you now be comfortable with lending to your sister in this scenario in US dollars?
-| 0 - 50000
-How close to sister at T2 | After going to your sister's house, how close do you feel to your sister? | 0: Extremely distant; 100: Extremely close
-How easy to imagine | How challenging was it to imagine yourself in this scenario? | 0: Extremely difficult; 100: Extremely easy
+As both a validity check and a way to understand the degree participants would be willing to help if they believed the participant completely, we presented participants with strong evidence that the claims were true (Action T3).
+In the US sample, this involved video evidence of the event in question occuring or a similar event after the fact.
+With the thwarted marriage vignette, this involved the participant seeing the man their daughter wants to marry trash talk their daughter and their family.
+As a final attention check, we presented participants with the Action T3 question but included instructions to ignore this and drag the slider all the way to the left (T4AttentionCheck).
+We did not exclude anyone from the study for failing this nor did we withhold payment.
 
-### Manipulation checks
-
-To understand if our manipulations had the desired effect two brief manipulation checks were also included, one before the signal and one following it.
-The first set of checks involved a question about how close participants felt to the one requesting the help in the imagined scenario and a question about how significant of a request the $50,000 was perceived to be.
-The second set of checks also had these questions plus one examining what emotional state they thought the imagined signaler was experiencing, in which participants could select from a number of boxes.
-
-Beyond a way to determine if participants were responding to the study as desired, these questions are also likely meaningful as outcome measures as one’s perception of another’s subjective experience is likely to play a role in their decision making.
-As such, they are only used in exploratory analysis portion of this study and in principle component analyses.
+Variable | Vignette | Wording | Coding 
+---------|----------|---------|-------
+T1Belief | Basketball | How much do you believe the star player is telling the truth about the coach? | 0: Not at all; 100: Completely
+T1Belief | Brother-in-law | How much do you believe your daughter is telling the truth about your brother-in-law? | 0: Not at all; 100: Completely
+T1Belief | Romantic partner | How much do you believe your daughter is telling the truth about your partner? | 0: Not at all; 100: Completely
+T1Belief | Thwarted Marriage | How much do you believe your older(bold) daughter is telling the truth about the second man not being a good match for her?  | 0: Not at all; 100: Completely
+T1Action | Basketball | How likely are you to recommend that the president of the university should suspend the coach? | 0: Very unlikely; 100: Very likely
+T1Action | Brother-in-law | How likely are you to kick your brother-in-law out? | 0: Very unlikely; 100: Very likely
+T1Action | Romantic partner | How likely are you to kick your partner out? | 0: Very unlikely; 100: Very likely
+T1Action | Thwarted Marriage | How likely are you to provide the large dowry so your older(bold) daughter can marry the man she is in love with?  | 0: Very unlikely; 100: Very likely
+T1Divide | Thwarted Marriage | How would you plan on dividing the money between your daughters?  | 0: Much more for the younger daughter; 50: Even division; 100: Much more for the older daughter
 
@@
 
-The final part of the survey was a brief demographic questionnaire which examined: (1) the age, (2) sex, (3) state of residence, (4) number of children, (5) number of siblings, (6) birth order, (7) current relationship status, and (7) highest level of education of each participant.
+The final part of the survey was a brief demographic questionnaire which examined: (1) the age, (2) sex, (3) number of siblings, (4) number of sons, (5) number of daughters, (6) current relationship status, (7) highest level of education, and (8) the annual household income of each participant.
 
@@
 
-To analyze the effects of conflict and the amount and type of information (hereafter information) on helping behavior, we used a linear model that included conflict and information as independent variables with PCA1 from our pre-signal principle components analysis T1 as the dependent variable.
-See figures 1, 2, and 3.
-We also fit a model in which information interacted with conflict, with PCA1 as the outcome variable.
+We used linear regression to analyze our results for the main effect of signal on belief in need and likelihood of help, controlling for baseline levels of belief in need and likelihood of help.
+(Need more detail)
 
-To understand the effects of the signals, we fit linear models for each of our four dependent variables.
-For the models of change in perceived need of money and change in likelihood of lending money, each was modeled with signal type as the sole independent variable.
-For the model looking at change in the amount of money participants were willing to lend, the same measure pre-signal was controlled for.
-And in the PCA model, PC1 post-signal was modeled controlling for PC1 pre-signal.
+Belief in need t2 ~ Signal + Belief in need t1
+Likelihood of help t2 ~ Signal + Likelihood of help t1
 
-We also fit interaction models for the same outcome variables post-signal, with each being the independent variable for model that interacted signal with information and signal with conflict.
+Based on advice from our statistical consultant, we also fit the following interaction models:
+
+Belief in need t2 ~ Signal * Belief in need t1
+Likelihood of help t2 ~ Signal * Likelihood of help t1
+
+The rationale for the interaction is that for individuals who indicate high levels of belief and helping at baseline, the signals might have reduced effect.
+
+To examine our hypothesis that beneficial treatment would be largely due to a signal's positive impact on the participant's beleif in need we ran the following mediaton models for each pairwise combination of signals:
+
+Mediator model: Belief in need t2 ~ Signal + Belief in need t1
+Outcome model: Likelihood of help t2  ~ Signal + Belief in need t2 + Likelihood of help t1 + Belief in need t1
 

### 2021-03-18 Paper.rmd
Commit to pull Michael's changes

--- 2021-03-04 Paper.rmd
@@
 knitr::opts_chunk$set(echo = F, warning = F, error = F, message = F)
-source('analysis.R')
+# source('analysis.R')
+tar_load(c('models', 'effectsPlots', 'plot_T1Belief_T1Action'))
 library(equatiomatic)
@@
 
-`r extract_eq(m1, intercept = 'beta', wrap = T)`
-
 ## Sampling
@@
 # Results
+
+```{r t1plot}
+plot_T1Belief_T1Action
+```

### 2021-03-18 analysis.R

@@ -478,7 +478,7 @@ ggplot(d, aes(PC1emotion, PC2emotion, colour = T2Belief)) +
   scale_color_viridis_c(option='A') +
   theme_minimal(15)
 
-m_emotion_belief <- glm(T2Belief ~ T1Belief + signal + PC1emotion + PC2emotion, family = quasibinomial, d)
+m_emotion_belief <- glm(T2Belief ~ T1Belief * signal + PC1emotion + PC2emotion, family = quasibinomial, d)
 Anova(m_emotion_belief)
 x <- visreg(m_emotion_belief, scale = 'response', gg=T, rug = F)
 (x[[1]] + x[[2]])/(x[[3]] + x[[4]]) & theme_bw()
@@ -724,3 +724,4 @@ out <- mediate(mmediator, mout, treat = "signal", mediator = "T2Belief", boot = 
 
 summary(out)
 plot(out)
+

### 2021-03-18 Paper.rmd

--- 2021-03-18 Paper.rmd
@@
 
-add pregistered predictions here or at end of intro?
-
-`r extract_eq(m1, intercept = 'beta', wrap = T)`
-
 ## Sampling

### 2021-03-19 Paper.rmd
conversion to renv and targets

--- 2021-03-18 Paper.rmd
@@
 knitr::opts_chunk$set(echo = F, warning = F, error = F, message = F)
-source('analysis.R')
 library(equatiomatic)
+library(knitr)
+library(kableExtra)
+library(ggplot2)
+library(patchwork)
+
+tar_load(
+  c(
+    'd',
+    'models', 
+    'effectsPlots', 
+    'plot_T1Belief_T1Action',
+    'plot_emotions',
+    'plot_raw_beliefs',
+    'plot_raw_actions',
+    'med1'
+    )
+  )
+
 ```
@@
 # Results
+
+## Summary statistics
+
+```{r sumtab}
+
+# d$Income <- ifelse(d$CurrencyType == 'USD', d$Income, d$Income*0.014)
+
+d$minutes <- d$TotalTime/60
+
+vars <- c(
+  Age = 'Age (years)',
+  Income = 'Income (USD)',
+  minutes = 'Time to complete (minutes)',
+  T1Belief = 'T1 Belief',
+  T1Action = 'T1 Action',
+  T1Divide = 'T1 Division',
+  T1LowMood = 'T1 Low mood',
+  T1Manipulative = 'T1 Manipulative',
+  T2Belief = 'T2 Belief',
+  T2Action = 'T2 Action',
+  T2Divide = 'T2 Division',
+  T2LowMood = 'T2 Low mood',
+  T2Manipulative = 'T2 Manipulative',
+  T3Action = 'T3 Action'
+)
+kable(custom.summarize(d, vars), caption = "Summary statistics for study variables.
+Original 0-100 values scaled to 0-1.
+Indian participants reported income in rupees, which we converted to USD at the current exchange rate (1 rupee == 0.014 USD).") %>% kable_styling()
+```
+
+## Distributions of beliefs and actions at time 1
+
+```{r t1plot, fig.width=10, fig.height=10, fig.cap="The distributions of Time 1 Belief vs.
+Time 1 Action, by vignette.
+Each dot is one participant.
+Original 0-100 values scaled to 0-1.
+Contour lines represent equal densities, estimated using a bivariate normal kernal (Venables and Ripley, 2002).
+Lines fit by linear regression.
+Dot size indicates the number of overlapping points."}
+plot_T1Belief_T1Action
+```
+
+## Effects of signals on beliefs and actions
+
+```{r beliefeffect, fig.width=8, fig.height=8, fig.cap="The effect of the signals on T2 Belief (top) and Action (bottom) controlling for T1 values of Belief and Action, respectively, with an interaction between T1 values and the signal.
+Estimated using generalized linear regression models with the quasibinomial family."}
+(effectsPlots$m1plot + theme(axis.text.x = element_blank()))/effectsPlots$m3plot + plot_layout(ncol = 1) & theme(plot.margin = unit(c(0,0,0,0), units = 'mm'))
+```
+
+```{r beliefvignette, fig.width=8, fig.height=8, fig.cap=paste0("The effect of the signals on T2 Belief (top) and Action (bottom) in each vignette, controlling for T1 values of Belief and Action, respectively.
+Effects computed with T1 values set to their median value (T1Belief=", median(d$T1Belief, na.rm=T), ", T1Action=", median(d$T1Action, na.rm=T), ").
+Estimated using generalized linear regression models with the quasibinomial family.")}
+(effectsPlots$m2plot + theme(axis.text.x = element_blank()))/effectsPlots$m4plot + plot_layout(ncol = 1) & theme(plot.margin = unit(c(0,0,0,0), units = 'mm'))
+
+```
+
+## Effects of signals on victim's perceived emotional state
+
+```{r emotionsplot, fig.width=10, fig.height=8, fig.cap="The effect of the signals on the inferred *low mood* and *manipulative* emotion ratings from T1 (arrow base) to T2 (arrow head), in each of the four vignettes.
+Thick arrows: mean change.
+Thin arrows: means of 500 bootstrap resamples."}
+plot_emotions
+```
+
+## Mediation of action by belief
+
+```{r medation, fig.cap="Mediation of T2 Action by T2 Belief."}
+plot(med1, treatment = 'treated')
+```
+
+# Supplementary information
+
+## Demographic effects
+
+```{r demoeffectsbeliefs, fig.width=9, fig.height=8, fig.cap="Demographic effects on Belief.
+**Top**: Association of age with T2 Belief, controlling for T1 Belief, sex, and vignette.
+**Bottom**: Sex interacting with the effect of the signals on T2 Belief controlling for T1 Belief, age, and vignette.
+Estimated using a generalized linear regression model with the quasibinomial family."}
+effectsPlots$m24plotAge / effectsPlots$m24plotSex
+```
+
+```{r demoeffectsaction, fig.width=9, fig.height=8, fig.cap="Demographic effects on Action.
+**Top**: Association of age with T2 Action, controlling for T1 Action, sex, and vignette.
+**Bottom**: Association of sex with T2 Action controlling for T1 Action, age, and vignette.
+Estimated using a generalized linear regression model with the quasibinomial family."}
+effectsPlots$m25plotAge / effectsPlots$m25plotSex
+```
+
+## Raw beliefs and actions
+
+```{r rawbeliefs, fig.width=10, fig.height=10, fig.cap="Change in beliefs from T1 to T2 for participants in each condition. Each grey line is one participant. Red lines are the mean change."}
+plot_raw_beliefs
+```
+
+```{r rawactions, fig.width=10, fig.height=10, fig.cap="Change in actions from T1 to T2 for participants in each condition. Each grey line is one participant. Red lines are the mean change."}
+plot_raw_actions
+```
+
+## Mentally ill
+
+```{r mentallyill, fig.width=8, fig.cap="Proportion of participants in each condition who thought that the vignette victim was mentally ill.
+Means estimated with a generalized linear regression model with the quasibinomial family."}
+effectsPlots$m21plot
+```
+
+# References

### 2021-03-19 R/functions.R

@@ -1,0 +1,166 @@
+
+
+fit_models2 <- function(d, d_thwarted, family = 'quasibinomial'){
+  list(
+    m1 = glm(T2Belief ~ T1Belief * signal, family = family, d),
+    m2 = glm(T2Belief ~ T1Belief + signal * vignette, family = family, d),
+    m3 = glm(T2Action ~ T1Action * signal, family = family, d),
+    m4 = glm(T2Action ~ T1Action + signal * vignette, family = family, d),
+    m5 = glm(T3Action ~ T2Action * signal, family = family, d),
+    m6 = glm(T3Action ~ T2Action * vignette + signal, family = family, d),
+    m7 = glm(T2Divide ~ T1Divide * signal, family = family, d_thwarted),
+    m8 = glm(T2Divide ~ T1Divide + Age * signal, family = family, d_thwarted),
+    m9 = glm(T2Jealous ~ T1Jealous * signal, family = family, d),
+    m10 = glm(T2Devious ~ T1Devious + signal, family = family, d),
+    m11 = glm(T2Angry ~ T1Angry + signal, family = family, d),
+    m12 = glm(T2Belief ~ T1Belief + signal*Sex, family = family, d),
+    m13 = glm(T2Belief ~ T1Belief + vignette*Sex, family = family, d),
+    m14 = glm(T2Action ~ T1Action + signal*Sex, family = family, d),
+    m15 = glm(T2Action ~ T1Action + vignette*Sex, family = family, d),
+    m16 = glm(T2Belief ~ T1Belief + signal * Age, family = family, d),
+    m17 = glm(T2Action ~ T1Action + signal * Age, family = family, d),
+    m18 = glm(T2Belief ~ T1Belief + signal + vignette*Age, family = family, d),
+    m19 = glm(T2Action ~ T1Action + signal + vignette*Age, family = family, d),
+    m20 = glm(T2MentallyIll ~ T1MentallyIll + signal, family = family, d),
+    m21 = glm(T2MentallyIll ~ T1MentallyIll + signal*vignette, family = family, d),
+    m22 = glm(T2Belief ~ T1Belief * signal + PC1emotionT1 + PC2emotionT1, family = family, d),
+    m23 = glm(T2Action ~ T1Action * signal + PC1emotionT1 + PC2emotionT1, family = family, d)
+  )
+}
+
+fit_models <- function(data, formulas, family = 'quasibinomial'){
+  tibble(
[…]

### 2021-03-19 _packages.R

@@ -1,0 +1,27 @@
+# Generated by targets::tar_renv(): do not edit by hand
+library(broom)
+library(bs4Dash)
+library(car)
+library(clustermq)
+library(dplyr)
+library(effects)
+library(forcats)
+library(future)
+library(ggbiplot)
+library(ggforce)
+library(gglm)
+library(ggplot2)
+library(glmmboot)
+library(gt)
+library(hagenutils)
+library(mediation)
+library(pingr)
+library(purrr)
+library(rstudioapi)
+library(shiny)
+library(shinycssloaders)
+library(shinyWidgets)
+library(signaling2020data)
+library(tidyr)
+library(visNetwork)
+library(visreg)

### 2021-03-19 _targets.R

@@ -1,0 +1,191 @@
+library(targets)
+library(tarchetypes)
+
+# Define custom functions and other global objects.
+
+source("R/functions.R")
+
+# Set target-specific options such as packages.
+tar_option_set(
+  packages = c("signaling2020data", "dplyr", "tidyr", "purrr", "ggplot2", "forcats", "car", "ggbiplot", "hagenutils", "visreg", "effects", "glmmboot", "broom", "mediation", "gglm", "gt", "ggforce"),
+  imports = c("signaling2020data")
+  )
+
+# List of target objects
+list(
+
+# Data preparation --------------------------------------------------------
+
+  tar_target(signaling2020, signaling2020data::signaling2020),
+  tar_target(
+  d_tmp,
+    signaling2020 %>%
+    dplyr::filter(CompleteSurvey) %>%
+    dplyr::mutate(
+      id = MTurkID,
+      across(.cols = c(contains('Belief'), contains('Action'), contains('Divide')), ~.x/100),
+      signal = ordered(signal, levels = c('Verbal request', 'Crying', 'Mild depression', 'Depression', 'Suicide attempt')),
+      T1LowMood = T1Depressed + T1Distressed + T1Sad,
+      T1Manipulative = T1Devious + T1Jealous,
+      T2LowMood = T2Depressed + T2Distressed + T2Sad,
+      T2Manipulative = T2Devious + T2Jealous
+    )
+  ),
+
+# PCA ---------------------------------------------------------------------
+
+  tar_target(
+    mpcaT1,
+    d_tmp %>%
+      dplyr::select(T1Angry:T1Violated) %>%
+      prcomp()
+  ),
+  tar_target(
+    mpcaT2,
+    d_tmp %>%
+      dplyr::select(T2Angry:T2Violated) %>%
+      prcomp()
+  ),
+
+# Final data --------------------------------------------------------------
+
+  tar_target(
+    d,
+    d_tmp %>%
+      mutate(
+        PC1emotionT1 = -mpcaT1$x[,1],
+        PC2emotionT1 = -mpcaT1$x[,2],
+        PC1emotionT2 = -mpcaT2$x[,1],
+        PC2emotionT2 = -mpcaT2$x[,2]
+      )
+  ),
+
+  tar_target(
+    d_thwarted,
+    d %>%
+      dplyr::filter(vignette == 'Thwarted marriage')
+  ),
+
[…]

### 2021-03-19 analysis.R

@@ -14,7 +14,7 @@
 
 library(signaling2020data)
 library(car)
-library(ggbiplot)
+# library(ggbiplot)
 library(tidyverse)
 library(broom)
 library(effects)

### 2021-03-20 R/functions.R
Updated to R 4.0.4 and also updated all packages.

@@ -1,6 +1,6 @@
 
 
-fit_models2 <- function(d, d_thwarted, family = 'quasibinomial'){
+fit_models2 <- function(d, family = 'quasibinomial'){
   list(
     m1 = glm(T2Belief ~ T1Belief * signal, family = family, d),
     m2 = glm(T2Belief ~ T1Belief + signal * vignette, family = family, d),
@@ -28,11 +28,11 @@ fit_models2 <- function(d, d_thwarted, family = 'quasibinomial'){
   )
 }
 
-fit_models <- function(data, formulas, family = 'quasibinomial'){
+fit_models <- function(data, formulas){
   tibble(
     Name = names(formulas),
     Formula = unname(formulas),
-    Model = map(Formula, ~glm(formula = .x, family = family, data = data)),
+    Model = map(Formula, ~glm(formula = .x, family = 'quasibinomial', data = data)),
     Anova = map(Model, ~Anova(.x, type = 3)),
     Tidy = map(Model, ~tidy(.x, conf.int = T))
   )

### 2021-03-21 Paper.rmd
Added several new plots and tables. Added glmmboot models Changed mediation models to include interaction Updated mediation package to latest github version Updated hagenutils to latest version

@@
 library(patchwork)
+library(hagenutils)
 
@@
     'models',
+    'models_prereg',
     'effectsPlots', 
@@
     'plot_raw_actions',
-    'med1'
+    'med1b',
+    'm1b_boot',
+    'm3b_boot'
     )
@@
 
+Table: (\#tab:outcomes) Outcome variables in each vignette.
+
 ### Demographic Questions
@@
 Estimated using generalized linear regression models with the quasibinomial family."}
-(effectsPlots$m1plot + theme(axis.text.x = element_blank()))/effectsPlots$m3plot + plot_layout(ncol = 1) & theme(plot.margin = unit(c(0,0,0,0), units = 'mm'))
+(effectsPlots$m1bplot + theme(axis.text.x = element_blank()))/effectsPlots$m3bplot + plot_layout(ncol = 1) & theme(plot.margin = unit(c(0,0,0,0), units = 'mm'))
 ```
@@
 (effectsPlots$m2plot + theme(axis.text.x = element_blank()))/effectsPlots$m4plot + plot_layout(ncol = 1) & theme(plot.margin = unit(c(0,0,0,0), units = 'mm'))
+```
 
+## The effect of signals on action is largely mediated by belief
+
+According to our theoretical model, credible signals of need increase observers' belief that the victim is telling the truth.
+Increased belief then increases the likelihood of helping the victim (action).
+See Figure \@ref(fig:medmodel).
+
+```{r medmodel, fig.cap="Possible causal effects of the signal on helping behavior.
+A credible signal of need increases belief that the victim is telling the truth and needs help, which increase the likelihood of helping.
+The direct path from the signal to action represents other causal effects of the signal on observers, such as perceptions of the victim's emotional state (and other factors not measured in this study) that might alter observer behavior."}
+
+knitr::include_graphics('paths.svg')
+```
+
+The total effect of the *Depression* signal (treatment) vs.
+*Verbal request* (control) on the likelihood of *Action* was to increase it by `r 100*signif(med1b$tau.coef, 3)` points from T1 to T2 (on the original 100-point scale).
+Of this increase, `r 100*signif(med1b$n.avg, 2)`% was mediated by the increased *Belief* that the victim was telling the truth.
+See Figure \@ref(fig:mediation).
+
+```{r mediation, fig.height=4, fig.cap="The effect of Depression (treatment) vs.
+Verbal request (control) on Action is largely mediated by Belief.
+ACME: Average causal mediation effect.
+ADE: Average direct effect.
+The mediation model controlled for T1 Belief, and the outcome model controlled for T1 Belief and T1 Action.
+Both models were GLMs with the binomial family (the mediation package does not support the quasibinomial family)."}
+ggmediation(med1b)
 ```
@@
 
-```{r emotionsplot, fig.width=10, fig.height=8, fig.cap="The effect of the signals on the inferred *low mood* and *manipulative* emotion ratings from T1 (arrow base) to T2 (arrow head), in each of the four vignettes.
+```{r emotionsplot, fig.width=10, fig.height=8, fig.cap="The effect of the signals on participants' inferred *manipulative* and *low mood* emotional states of the victim, from T1 (arrow base) to T2 (arrow head), in each of the four vignettes.
 Thick arrows: mean change.
@@
 
-## Mediation of action by belief
+# Supplementary information
 
-```{r medation, fig.cap="Mediation of T2 Action by T2 Belief."}
-plot(med1, treatment = 'treated')
+## Sample size in each condition
+
+```{r conditions}
+as.data.frame.matrix(xtabs(~signal+vignette, d)) %>% 
+  kable(caption = "Sample size in each condition.") %>% 
+  kable_styling()
 ```
-
-# Supplementary information
 
@@
 effectsPlots$m25plotAge / effectsPlots$m25plotSex
+```
+
+```{r demovignettebelief, fig.width=8, fig.height=8, fig.cap="Associations of age (top) and sex (bottom) with T2 Belief by vignette, controlling for T1 Belief and signal.
+Estimated using a generalized linear regression model with the quasibinomial family."}
+effectsPlots$m18plot / effectsPlots$m13plot
+```
+
+```{r demovignetteaction, fig.width=8, fig.height=8, fig.cap="Associations of age (top) and sex (bottom) with T2 Action by vignette, controlling for T1 Action and signal.
+Estimated using a generalized linear regression model with the quasibinomial family."}
+effectsPlots$m19plot / effectsPlots$m15plot
 ```
@@
 
+## T3 Action vs. T2 Action
+
+```{r t2action, fig.width=10, fig.cap="The effect of post-signal (T3) information that the victim was telling the truth on the likelihood of acting to help her (T3 Action), controlling for T2 Action."}
+effectsPlots$m26plot
+```
+
+## Regression tables
+
+```{r regressiontables}
+tmp <- models %>% 
+  dplyr::filter(Name %in% c('m1', 'm2', 'm3', 'm4', 'm21', 'm24', 'm25'))
+
+regressiontable(tmp$Model, caption = 'Regression coefficients')
+```
+
+## ANOVA tables
+
+ANOVA tables for generalized linear regression models (quasibinomial family).
+
+```{r anovatables}
+
+bind_rows(tmp$TidyANOVA, .id = 'Model') %>%
+  dplyr::rename(Variable = term, `LR Chisq` = statistic) %>% 
+  gt::gt(groupname_col = "Model", caption = "ANOVA tables") %>% 
+  gt::cols_label(Variable = "") %>% 
+  gt::fmt_number(columns=3, decimals = 1) %>% 
+  gt::fmt_scientific(5, decimals = 1) %>% 
+  gt::tab_style(style = gt::cell_text(indent = gt::px(40)), 
+                locations = gt::cells_body(columns = "Variable"))
+```
+
+## Preregistered OLS models
+
+```{r preregbelief, fig.width=8, fig.height=8, fig.cap="The effect of the signals on T2 Belief (top) and Action (bottom) controlling for T1 values of Belief and Action, respectively.
+Estimated using OLS linear regression models (gaussian)."}
+p1 <- effect_plot(fit=models_prereg$Model$m1, xvar='signal',ylbl='T2 Belief', data=d)
+
+p2 <- effect_plot(fit=models_prereg$Model$m3, xvar='signal', ylbl='T2 Action', data=d)
+
+(p1 + theme(axis.text.x = element_blank()))/p2 + plot_layout(ncol = 1) & theme(plot.margin = unit(c(0,0,0,0), units = 'mm'))
+```
+
+```{r preregbeliefB, fig.width=8, fig.height=8, fig.cap="The effect of the signals on T2 Belief (top) and Action (bottom) controlling for T1 values of Belief and Action, respectively, with an interaction between T1 values and the signal.
+Estimated using OLS linear regression models (gaussian)."}
+p1 <- effect_plot(fit=models_prereg$Model$m1b, xvar='signal', by='T1Belief', ylbl='T2 Belief', data=d)
+
+p2 <- effect_plot(fit=models_prereg$Model$m3b, xvar='signal', by='T1Action', ylbl='T2 Action', data=d)
+
+(p1 + theme(axis.text.x = element_blank()))/p2 + plot_layout(ncol = 1) & theme(plot.margin = unit(c(0,0,0,0), units = 'mm'))
+```
+
+### OLS regression tables
+
+```{r preregtables}
+regressiontable(models_prereg$Model, caption = 'OLS regression coefficients for preregistered linear regression models.')
+```
+
+### OLS Anova tables
+
+```{r prepreganova}
+bind_rows(models_prereg$TidyANOVA, .id = 'Model') %>%
+  dplyr::rename(Variable = term, `LR Chisq` = statistic) %>% 
+  gt::gt(groupname_col = "Model", caption = "OLS ANOVA tables") %>% 
+  gt::cols_label(Variable = "") %>% 
+  gt::fmt_number(columns=c(3,5), decimals = 1) %>% 
+  gt::fmt_scientific(6, decimals = 1) %>% 
+  gt::fmt_missing(columns=5:6, rows = everything(), missing_text = "---") %>% 
+  gt::tab_style(style = gt::cell_text(indent = gt::px(40)), 
+                locations = gt::cells_body(columns = "Variable"))
+
+```
+
+## Differences between quasibinomial and bootstrapped confidence intervals
+
+```{r}
+m1b_quasi <- models$TidyModel$m1b
+m1b_diff <- (m1b_boot[,'boot 97.5%'] - m1b_boot[,'boot 2.5%'])/(m1b_quasi$conf.high-m1b_quasi$conf.low)
+
+m3b_quasi <- models$TidyModel$m3b
+m3b_diff <- (m3b_boot[,'boot 97.5%'] - m3b_boot[,'boot 2.5%'])/(m3b_quasi$conf.high-m3b_quasi$conf.low)
+
+diff_sum <- summary(c(m1b_diff, m3b_diff))
+```
+
 # References

### 2021-03-21 R/functions.R

@@ -1,41 +1,22 @@
 
 
-fit_models2 <- function(d, family = 'quasibinomial'){
-  list(
-    m1 = glm(T2Belief ~ T1Belief * signal, family = family, d),
-    m2 = glm(T2Belief ~ T1Belief + signal * vignette, family = family, d),
-    m3 = glm(T2Action ~ T1Action * signal, family = family, d),
-    m4 = glm(T2Action ~ T1Action + signal * vignette, family = family, d),
-    m5 = glm(T3Action ~ T2Action * signal, family = family, d),
-    m6 = glm(T3Action ~ T2Action * vignette + signal, family = family, d),
-    m7 = glm(T2Divide ~ T1Divide * signal, family = family, d_thwarted),
-    m8 = glm(T2Divide ~ T1Divide + Age * signal, family = family, d_thwarted),
-    m9 = glm(T2Jealous ~ T1Jealous * signal, family = family, d),
-    m10 = glm(T2Devious ~ T1Devious + signal, family = family, d),
-    m11 = glm(T2Angry ~ T1Angry + signal, family = family, d),
-    m12 = glm(T2Belief ~ T1Belief + signal*Sex, family = family, d),
-    m13 = glm(T2Belief ~ T1Belief + vignette*Sex, family = family, d),
-    m14 = glm(T2Action ~ T1Action + signal*Sex, family = family, d),
-    m15 = glm(T2Action ~ T1Action + vignette*Sex, family = family, d),
-    m16 = glm(T2Belief ~ T1Belief + signal * Age, family = family, d),
-    m17 = glm(T2Action ~ T1Action + signal * Age, family = family, d),
-    m18 = glm(T2Belief ~ T1Belief + signal + vignette*Age, family = family, d),
-    m19 = glm(T2Action ~ T1Action + signal + vignette*Age, family = family, d),
-    m20 = glm(T2MentallyIll ~ T1MentallyIll + signal, family = family, d),
-    m21 = glm(T2MentallyIll ~ T1MentallyIll + signal*vignette, family = family, d),
-    m22 = glm(T2Belief ~ T1Belief * signal + PC1emotionT1 + PC2emotionT1, family = family, d),
-    m23 = glm(T2Action ~ T1Action * signal + PC1emotionT1 + PC2emotionT1, family = family, d)
-  )
-}
-
-fit_models <- function(data, formulas){
-  tibble(
[…]

### 2021-03-21 _targets.R

@@ -71,9 +71,11 @@ list(
   tar_target(
     model_formulas,
     c(
-      m1 = "T2Belief ~ T1Belief * signal",
+      m1 = "T2Belief ~ T1Belief + signal",
+      m1b = "T2Belief ~ T1Belief * signal",
       m2 = "T2Belief ~ T1Belief + signal * vignette",
-      m3 = "T2Action ~ T1Action * signal",
+      m3 = "T2Action ~ T1Action + signal",
+      m3b = "T2Action ~ T1Action * signal",
       m4 = "T2Action ~ T1Action + signal * vignette",
       m5 = "T3Action ~ T2Action * signal",
       m6 = "T3Action ~ T2Action * vignette + signal",
@@ -85,7 +87,7 @@ list(
       m12 = "T2Belief ~ T1Belief + signal * Sex",
       m13 = "T2Belief ~ T1Belief + vignette * Sex",
       m14 = "T2Action ~ T1Action + signal * Sex",
-      m15 = "T2Action ~ T1Action + vignette * Sex",
+      m15 = "T2Action ~ T1Action + signal + vignette * Sex",
       m16 = "T2Belief ~ T1Belief + signal * Age",
       m17 = "T2Action ~ T1Action + signal * Age",
       m18 = "T2Belief ~ T1Belief + signal + vignette * Age",
@@ -95,14 +97,43 @@ list(
       m22 = "T2Belief ~ T1Belief * signal + PC1emotionT1 + PC2emotionT1",
       m23 = "T2Action ~ T1Action * signal + PC1emotionT1 + PC2emotionT1",
       m24 = "T2Belief ~ T1Belief + Age + Sex * signal + vignette",
-      m25 = "T2Action ~ T1Action + Age + Sex + signal + vignette"
+      m25 = "T2Action ~ T1Action + Age + Sex + signal + vignette",
+      m26 = 'T3Action ~ T2Action + vignette'
     )
   ),
 
   tar_target(
     models,
-    fit_models(d, model_formulas)
+    fit_models(d, model_formulas, family = 'quasibinomial')
   ),
+
+  tar_target(
+    models_prereg,
+    fit_models(d, model_formulas[c('m1', 'm1b', 'm3', 'm3b')], family = 'gaussian')
+  ),
+
+
+# Bootstrapped models -----------------------------------------------------
+
+  tar_target(
+    m1b_boot,
+    bootstrap_model(
+      base_model = glm(T2Belief ~ T1Belief * signal, family = binomial, d),
[…]

### 2021-03-21 Paper.rmd
Added Division effects plots

@@
 knitr::opts_chunk$set(echo = F, warning = F, error = F, message = F)
+# options(warn = 2)
 library(equatiomatic)
@@
 ```{r mediation, fig.height=4, fig.cap="The effect of Depression (treatment) vs.
-Verbal request (control) on Action is largely mediated by Belief.
+Verbal request (control) on Action (0-1 scale) is largely mediated by Belief.
 ACME: Average causal mediation effect.
@@
 
+## The effect of signals on T2 division in thwarted marriage vignette
+
+```{r division, fig.width=9, fig.cap="Effect of signals on division of dowry between the daughters in the thwarted marriage vignette, with an interaction between T1 Division and signal.
+Means estimated with a generalized linear regression model with the quasibinomial family."}
+effectsPlots$m7
+```
+
+```{r divisionage, fig.width=9, fig.cap="Interaction of age with signals on T2 Division of dowry between the daughters in the thwarted marriage vignette."}
+effectsPlots$m8
+```
+
 ## T3 Action vs. T2 Action
@@
 ```{r t2action, fig.width=10, fig.cap="The effect of post-signal (T3) information that the victim was telling the truth on the likelihood of acting to help her (T3 Action), controlling for T2 Action."}
-effectsPlots$m26plot
+effectsPlots$m26plot + theme(panel.spacing = unit(1.5, "lines"))
 ```

### 2021-03-21 R/functions.R

@@ -27,14 +27,19 @@ effect_plot <- function(m, ...){
   args$gg <- T
   args$scale <- 'response'
 
-  p <- exec('visreg', !!!args)
-  p + ylim(c(0, 1)) +
-    labs(x = '', y = args$ylbl) +
+  p <- exec('visreg', !!!args) +
+    ylim(0, 1) +
+    ylab(args$ylbl) +
     theme_bw(15) +
-    theme(
-      axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
-      axis.title.y = element_text(angle = 0)
-    )
+    theme(axis.title.y = element_text(angle = 0))
+
+  d <- args$data
+  vartype = class(d[[args$xvar]])
+  if('numeric' %in% vartype) return(p)
+
+  p +
+    xlab('') +
+    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
 }
 
 effect_plots <- function(models, data){
@@ -45,6 +50,8 @@ effect_plots <- function(models, data){
     m3plot = effect_plot(fit=models$m3, xvar='signal', ylbl='T2 Action', data=data),
     m3bplot = effect_plot(fit=models$m3b, xvar='signal', by='T1Action', ylbl='T2 Action', data=data),
     m4plot = effect_plot(fit=models$m4, xvar='signal', by='vignette', ylbl='T2 Action', data=data),
+    m7plot = effect_plot(fit=models$m7, xvar='signal', by='T1Divide', ylbl='T2 Division', data=data),
+    m8plot = effect_plot(fit=models$m8, xvar='Age', by='signal', ylbl='T2 Division', data=data),
     m12plot = effect_plot(fit=models$m12, xvar='Sex', by='signal', ylbl='T2 Belief', data=data),
     m13plot = effect_plot(fit=models$m13, xvar='Sex', by='vignette', ylbl='T2 Belief', data=data),
     m14plot = effect_plot(fit=models$m14, xvar='Sex', by='signal', ylbl='T2 Action', data=data),
@@ -55,16 +62,10 @@ effect_plots <- function(models, data){
     m19plot = effect_plot(fit=models$m19, xvar='Age', by='vignette', ylbl='T2 Action', data=data),
     m21plot = effect_plot(fit=models$m21, xvar='signal', by='vignette', ylbl = "Mentally ill", data=data),
[…]

### 2021-03-21 Paper.rmd
Added limitations section

--- 2021-03-21 Paper.rmd
@@
 add funding info somewhere
+update MTurk (Ed email links + mine)
+Find a place for the predictions
 
@@
 
+# Discussion
+
+## The effect of signaling on belief
+
+## Mediation models
+
+## Limitations
+
+The largest source of limitations of this study is its lack of ecological validity, something which had to be sacrificed for any experimental design involving depression and suicide attempts.
+It is almost certain that participants experienced this study differently than they would if the event actually happened to them.
+This may have biased results in a pro-signaler direction due to the lack of meaningful costs making support feel less costly or through the likely inability of participants to imagine themselves in an anonymous scenario (cite your paper on this) leading them to take an opportunity to signal generosity cheaply.
+It may have also biased participants against helping if they could not fully imagine the characters in the story as kin or important cooperative partners, while the survey's short duration may have weakened the strength of the bargaining of the costlier signals.
+However, both the findings of a main effect of signal and the effect of signal type on likelihood of support was largely mediated by change in belief suggest that participants were paying attention to the theoretically relevant details in ways that influenced their behavior.
+
+Another limitation is our uncertainty over the data quality from the Indian sample.
+Compared to the US sample, far more participants were filtered out by our attention checks, something which could be consistent with botting, unfamiliarity with English, or low effort responses.
+Assuming this corresponded with more low-quality responses among those who passed the attention checks, the differences seen among those in the thwarted marriage vignette may simply be due to added noise rather than differences in the scenarios or the effectiveness of the signals among Indians compared to Americans.
+
+# Conclusion
+
 # Supplementary information

### 2021-03-22 Paper.rmd
Added rough draft of discussion to RMD

@@
 update MTurk (Ed email links + mine)
-Find a place for the predictions
+Find a place for the predictions and preregistration 
+go back and emohasize conflit and PI in the methods (at least in the pilot studies portion)
 
@@
 
-## The effect of signaling on belief
+## The effect of signaling on belief and likelihood of support
+
+Consistent with costly signaling theory, costlier signals resulted in greater perceptions of need and increased the liklihood of participants helping the signaler than the less costly signals.
+This effect was largest in the "brother-in-law" and "romantic partner" vignettes, both of which involved claims of assault against participants' imagined daughters.
+However, the effect of signal type was much smaller in both the "basketball coach" and the "thwarted marriage" vignette.
+In the "basketball coach" vignette, part of the reason for this may have been the lack of relatedness participants had with the alleged victim.
+However, this was still a surprising finding due to the relatively small size of the request (i.e., recommend the coach be suspended rather than kick out family or a romantic partner).
+With the thwarted marriage vignette, the fact that support came at the cost of one's younger daughter may explain the relatively small effect of signal strength.
+However, data from the Indian sample appears to be of lower quality (see limitations for more information).
+
+In the "brother-in-law" and "romantic partner" scenarios, there was a noticeable jump in the magnitude of pro-signaler responses when going from the crying to mild depression and then a second, smaller jump from depression to a sucide attempt (Ed please check this is the right interpretation.
+It's definitely not the most conservative one).
+One potential reason for this is the increase in symptoms from mild depression to depression was not costly enough to result in a large effect as the symptoms only differed in severity (e.g., grades dropping from As to Bs [mild depression] or Cs [depression]).
+
+We also found evidence for the predicted interaction between signal and belief in need and likelihood of help at T1, with the pro-signaler effects being larger at intermediate but low levels of believe at T1.
+In real-life scenarios, it would be reasonable to expect that costly-signaling would not be engaged in when others already believe one's need.
+For this reason, too strong of a signal may be seen as manipulative or a cue of dysfunction, and therefore, be responded to aversively.
+However, belief in need and likelihood of help at T2 still remained high when it was high at T1, suggesting that this may not be a significant risk when one is in severe enough need (want to bring in MA here.
+Is that a bad idea?).
 
@@
 
+Our prediction that the effect of signal cost on likelihood of help would largely be mediated by signal's effect on belief in need was also met, as would be expected if the main function of signaling need is a reduction in the amount of private information one has relative to those motivated to care for the signaler (cite).
+However, there was still a positive main effect of the signal in many pairwise comparisons between the costlier signals and the less costly signals, including the comparison between the depression and verbal request condition (See SI for other mediation models).
+One possible reason for this is that someone may still be distressed and face real adversity without being forthcoming about one's problems.
+For example, participants who saw the "brother-in-law" vignette may have thought the daughter was lying about the assault due to jealously over her cousin, with stronger signals still conveying the severity of the competition between her and her cousin in ways words alone could not.
+
+## Broader discussion
+
+Scenarios likely favor cheating due to high potential of benefits
 ## Limitations

### 2021-03-22 Paper.rmd
Added histograms. Tweaked a few other plots.

--- 2021-03-21 Paper.rmd
@@
 
+## Distributions of T2 Belief and Action by signal and vignette
+
+```{r distbelief, fig.width=10, fig.height=10, fig.cap="Histograms of T2 Belief by signal and vignette."}
+ggplot(d, aes(x = T2Belief, fill=signal)) +
+  geom_histogram(colour='grey') +
+  scale_x_continuous(breaks = c(0, 0.5, 1)) +
+  facet_grid(vignette~signal) +
+  guides(fill='none') +
+  xlab('\n T2 Belief') +
+  theme_minimal(15) + 
+  theme(strip.text.y = element_text(angle=0, hjust=0))
+```
+
+```{r distaction, fig.width=10, fig.height=10, fig.cap="Histograms of T2 Action by signal and vignette."}
+ggplot(d, aes(x = T2Action, fill=signal)) +
+  geom_histogram(colour='grey') +
+  scale_x_continuous(breaks = c(0, 0.5, 1)) +
+  facet_grid(vignette~signal) +
+  guides(fill='none') +  
+  xlab('\n T2 Action') +
+  theme_minimal(15) + 
+  theme(strip.text.y = element_text(angle=0, hjust=0))
+```
+
 ## Demographic effects
@@
 
-```{r mentallyill, fig.width=8, fig.cap="Proportion of participants in each condition who thought that the vignette victim was mentally ill.
+```{r mentallyillT1, fig.width=8, fig.cap="Proportion of participants in each vignette who thought that the victim was mentally ill at T1.
 Means estimated with a generalized linear regression model with the quasibinomial family."}
-effectsPlots$m21plot
+effectsPlots$m27plot + ggtitle('Time 1')
+```
+
+```{r mentallyillT2, fig.width=8, fig.cap="Proportion of participants in each condition who thought that the victim was mentally ill at T2, controlling for perceptions of mental illness at T1.
+Means estimated with a generalized linear regression model with the quasibinomial family."}
+effectsPlots$m21plot + ggtitle('Time 2')
 ```

### 2021-03-22 Paper.rmd

--- 2021-03-22 Paper.rmd
@@
 
-```{r mentallyill, fig.width=8, fig.cap="Proportion of participants in each condition who thought that the vignette victim was mentally ill.
+```{r mentallyillT1, fig.width=8, fig.cap="Proportion of participants in each vignette who thought that the victim was mentally ill at T1.
 Means estimated with a generalized linear regression model with the quasibinomial family."}
-effectsPlots$m21plot
+effectsPlots$m27plot + ggtitle('Time 1')
+```
+
+```{r mentallyillT2, fig.width=8, fig.cap="Proportion of participants in each condition who thought that the victim was mentally ill at T2, controlling for perceptions of mental illness at T1.
+Means estimated with a generalized linear regression model with the quasibinomial family."}
+effectsPlots$m21plot + ggtitle('Time 2')
+```
+
+## The effect of signals on T2 division in thwarted marriage vignette
+
+```{r division, fig.width=9, fig.cap="Effect of signals on division of dowry between the daughters in the thwarted marriage vignette, with an interaction between T1 Division and signal.
+Means estimated with a generalized linear regression model with the quasibinomial family."}
+effectsPlots$m7
+```
+
+```{r divisionage, fig.width=9, fig.cap="Interaction of age with signals on T2 Division of dowry between the daughters in the thwarted marriage vignette."}
+effectsPlots$m8
 ```

### 2021-03-22 R/functions.R
Added correlation coefficients to Action vs. Belief plot

@@ -1,4 +1,27 @@
 
+T1Belief_Action_dist <- function(d){
+
+  dcor <-
+    d %>%
+    group_by(vignette) %>%
+    summarise(
+      r = signif(cor(T1Belief, T1Action), 2)
+    ) %>%
+    mutate(r = paste('r =', r))
+
+  ggplot(d, aes(T1Belief, T1Action, colour = vignette)) +
+    geom_density2d(alpha = 0.5, show.legend = F) +
+    geom_count(alpha = 0.5) +
+    geom_smooth(se=F, method = 'lm', show.legend = F) +
+    geom_text(data = dcor, aes(label = r), x = .15, y = 0.95, size=5, colour='black') +
+    coord_fixed() +
+    labs(x = '\nT1 Belief', y = 'T1 Action\n') +
+    guides(colour = 'none', size = guide_legend(title = 'Overlapping\npoints')) +
+    facet_wrap(~vignette) +
+    theme_minimal(15) +
+    theme(axis.title.y = element_text(angle=0))
+
+}
 
 fit_models <- function(data, formulas, family = 'quasibinomial'){
   d <- tibble(
@@ -60,7 +83,7 @@ effect_plots <- function(models, data){
     m17plot = effect_plot(fit=models$m17, xvar='Age', by='signal', ylbl='T2 Action', data=data),
     m18plot = effect_plot(fit=models$m18, xvar='Age', by='vignette', ylbl='T2 Belief', data=data),
     m19plot = effect_plot(fit=models$m19, xvar='Age', by='vignette', ylbl='T2 Action', data=data),
-    m21plot = effect_plot(fit=models$m21, xvar='signal', by='vignette', ylbl = "Mentally ill", data=data),
+    m21plot = effect_plot(fit=models$m21, xvar='signal', by='vignette', ylbl = "T2 Mentally ill", data=data),
     m24plotAge = visreg(fit=models$m24, xvar='Age', partial=F, rug=F, gg=T, scale='response', data=data) +
       theme_bw(15) + theme(axis.title.y = element_text(angle = 0)),
     m24plotSex = effect_plot(fit=models$m24, xvar='Sex', by = 'signal', ylbl='T2 Belief', data=data),
@@ -68,7 +91,8 @@ effect_plots <- function(models, data){
       theme_bw(15) + theme(axis.title.y = element_text(angle = 0)),
[…]

### 2021-03-22 Paper.rmd
added some notes to the RMD
Added emotion heatmaps

@@
     'm1b_boot',
-    'm3b_boot'
+    'm3b_boot',
+    'plot_T1emotion_heatmap',
+    'plot_T2emotion_heatmap'
     )
@@
 Scenarios likely favor cheating due to high potential of benefits
+
 ## Limitations
@@
 plot_raw_actions
+```
+
+## T1 emotion vs vignette heatmap
+
+```{r t1emotionheatmap, fig.width=8, fig.cap="Time 1 inference of victim's emotional state in each vignette.
+Each cell represents the proportion of participants who inferred that emotion.
+Participants could check multiple emotions from the list."}
+plot_T1emotion_heatmap
+```
+
+## T2 emotion vs signal heatmap
+
+```{r t2emotionheatmap, fig.width=8, fig.cap="Time 2 inference of victim's emotional state following the signal.
+Each cell represents the proportion of participants who inferred that emotion.
+Participants could check multiple emotions from the list."}
+plot_T2emotion_heatmap
 ```

### 2021-03-22 R/functions.R

@@ -189,8 +189,29 @@ plot_raw_data <- function(d, type){
     )
 }
 
+T2emotion_heatmap <- function(d){
+  d %>%
+    dplyr::select(signal, T2Angry:T2Violated) %>%
+    pivot_longer(-signal) %>%
+    mutate(name = stringr::str_remove(name, 'T2')) %>%
+    group_by(name, signal) %>%
+    summarise(n = sum(value)/n()) %>%
+    pivot_wider(names_from = signal, values_from = n, values_fill = 0) %>%
+    hagenheat(rotate_labels = F, seriation_method = 'PCA_angle', viridis_option = 'B') +
+    theme_minimal(15)
+}
 
-
+T1emotion_heatmap <- function(d){
+  d %>%
+    dplyr::select(vignette, T1Angry:T1Violated) %>%
+    pivot_longer(-vignette) %>%
+    mutate(name = stringr::str_remove(name, 'T1')) %>%
+    group_by(name, vignette) %>%
+    summarise(n = sum(value)/n()) %>%
+    pivot_wider(names_from = vignette, values_from = n, values_fill = 0) %>%
+    hagenheat(rotate_labels = F, seriation_method = 'PCA_angle', viridis_option = 'B') +
+    theme_minimal(15)
+}
 
 ######### Alternate mediators ############
 

### 2021-03-22 _targets.R

@@ -201,6 +201,15 @@ tar_target(
     emotion_plot(d)
   ),
 
+  tar_target(
+    plot_T1emotion_heatmap,
+    T1emotion_heatmap(d)
+  ),
+
+  tar_target(
+    plot_T2emotion_heatmap,
+    T2emotion_heatmap(d)
+  ),
 
 # Raw data plots ----------------------------------------------------------
 

### 2021-03-22 analysis.R

@@ -725,3 +725,23 @@ out <- mediate(mmediator, mout, treat = "signal", mediator = "T2Belief", boot = 
 summary(out)
 plot(out)
 
+d %>%
+  # dplyr::filter(vignette != 'Thwarted marriage') %>%
+  dplyr::select(signal, T2Angry:T2Violated) %>%
+  pivot_longer(-signal) %>%
+  mutate(name = str_remove(name, 'T2')) %>%
+  # dplyr::filter(value>0) %>%
+  group_by(name, signal) %>%
+  summarise(n = sum(value)/n()) %>%
+  pivot_wider(names_from = signal, values_from = n, values_fill = 0) %>%
+  hagenheat(rotate_labels = F, seriation_method = 'PCA_angle', viridis_option = 'B')
+
+d %>%
+  dplyr::select(vignette, T1Angry:T1Violated) %>%
+  pivot_longer(-vignette) %>%
+  mutate(name = str_remove(name, 'T1')) %>%
+  # dplyr::filter(value>0) %>%
+  group_by(name, vignette) %>%
+  summarise(n = sum(value)/n()) %>%
+  pivot_wider(names_from = vignette, values_from = n, values_fill = 0) %>%
+  hagenheat(rotate_labels = F, seriation_method = 'PCA_angle', viridis_option = 'B')

### 2021-03-22 Paper.rmd
Added to the discussion

@@
 
-Consistent with costly signaling theory, costlier signals resulted in greater perceptions of need and increased the liklihood of participants helping the signaler than the less costly signals.
+Consistent with costly signaling theory, costlier signals resulted in greater perceptions of need and increased the likelihood of participants helping the signaler than the less costly signals.
 This effect was largest in the "brother-in-law" and "romantic partner" vignettes, both of which involved claims of assault against participants' imagined daughters.
 However, the effect of signal type was much smaller in both the "basketball coach" and the "thwarted marriage" vignette.
-In the "basketball coach" vignette, part of the reason for this may have been the lack of relatedness participants had with the alleged victim.
+In the "basketball coach" vignette, part of the reason for this may have been the lack of relatedness between participants and the alleged victim.
 However, this was still a surprising finding due to the relatively small size of the request (i.e., recommend the coach be suspended rather than kick out family or a romantic partner).
 With the thwarted marriage vignette, the fact that support came at the cost of one's younger daughter may explain the relatively small effect of signal strength.
-However, data from the Indian sample appears to be of lower quality (see limitations for more information).
+However, data from the Indian sample appears to be of lower quality, limiting our confidence in this interpretation (see limitations for more information).
 
-In the "brother-in-law" and "romantic partner" scenarios, there was a noticeable jump in the magnitude of pro-signaler responses when going from the crying to mild depression and then a second, smaller jump from depression to a sucide attempt (Ed please check this is the right interpretation.
-It's definitely not the most conservative one).
+In the "brother-in-law" and "romantic partner" scenarios, there was a noticeable jump in the magnitude of pro-signaler responses when going from the crying to mild depression and then a second, smaller jump from depression to a suicide attempt.
 One potential reason for this is the increase in symptoms from mild depression to depression was not costly enough to result in a large effect as the symptoms only differed in severity (e.g., grades dropping from As to Bs [mild depression] or Cs [depression]).
+Such small changes may be less impactful in vignette form than in real-life scenarios in which the effects of signaling may increase in severity and be prolonged over a lenghty period of time.
 
@@
 One possible reason for this is that someone may still be distressed and face real adversity without being forthcoming about one's problems.
-For example, participants who saw the "brother-in-law" vignette may have thought the daughter was lying about the assault due to jealously over her cousin, with stronger signals still conveying the severity of the competition between her and her cousin in ways words alone could not.
+For example, participants who saw the "brother-in-law" vignette may have thought the daughter was lying about the assault due to jealously over her cousin, but the stronger signals may have still conveyed the severity of the competition between her and her cousin in ways words alone could not.
 
@@
 
-Scenarios likely favor cheating due to high potential of benefits
+Our results on the connection between belief in need and likelihood of help are consistent with the bargaining models of depression and suicide.
+In addition to the effect of signal cost on support being largely mediated by the signal's effect on belief in need, belief in need and likelihood of support were highly correlated but distinct at T1 (pre-signal).
+This situation should arise in any instance when a target of a signal of need would benefit from helping if the need was genuine and known to reasonable precision.
+Importantly, such problems are common among humans today (cite) and have likely been so since individuals could increase their inclusive fitness through supporting kin or important cooperative partners in times of need or conflict over acceptable one's contributions joint endeavors (cite).
+
+Although this study was not designed to examine whether the costs of signaling would be made up for by the increased support stemming from depression and suicide attempts directly, the results are encouraging.
+In general, the costs required to honestly convey one's qualities should be expected to increase with the potential payoffs of deception (cite), with the vignettes in this study emphasizing the existence of private information and sizable conflicts of interest to increase the perceived risk of being taken advantage of.
+In similar real-world scenarios, this difficulty of signaling honest need would coincide with the substantial fitness-relevant benefits of preventing future assaults or being able to marry the partner of one's choice.
+These benefits coupled with the fact (too strong?) that depression and suicide attempts become relatively less costly with increased need (Hagen 2003), suggest that the increased support seen in this study may be worth the costs required to signal need more often than is often appreciated when counting the entire costs of depression as the signal rather than only the upregulation of symptoms for a communicative purpose.
 

### 2021-03-25 Paper.rmd
Added diff heatmap and effect sizes plot

--- 2021-03-22 Paper.rmd
@@
     'models_prereg',
+    'effect_sizes',
     'effectsPlots', 
@@
     'm3b_boot',
-    'plot_T1emotion_heatmap',
-    'plot_T2emotion_heatmap'
+    'dfT1emotion_vignette',
+    'dfT1emotion_signal',
+    'dfT2emotion_signal'
     )
@@
 
+## Signal effect sizes
+
+```{r effectsizes, fig.width=10, fig.height=8, fig.cap="Cohen's d (95% CI) for the effect of each signal on Action and Belief in each vignette relative to the Verbal request signal, ranked by effect size."}
+
+relbl <- function(lb){
+  map_chr(lb, ~str_split(.x, ',')[[1]][2])
+}
+
+ggplot(effect_sizes, aes(est, fct_reorder(id, est), xmin=low, xmax=high, colour = signal, shape=Outcome)) +
+  geom_pointrange(position = position_dodge(width = 0.7), lwd = 2.5, fatten = 1, alpha=0.5) +
+  geom_vline(xintercept = 0, linetype = 'dotted') +
+  scale_y_discrete(labels = relbl) +
+  scale_color_manual(name=NULL, values = c('black', 'darkred', 'red', 'orange')) +
+  # scale_color_viridis_d(option='A') +
+  guides(colour = guide_legend(override.aes = list(size = 1)), shape = guide_legend(title=NULL, override.aes = list(size = 1))) +
+  # facet_wrap(~Outcome, ncol=1) +
+  labs(x="\nCohn's d (95% CI)", y=NULL) +
+  theme_minimal(15) +
+  theme(legend.position = 'top')
+```
+
 ## Demographic effects
@@
 Each cell represents the proportion of participants who inferred that emotion.
-Participants could check multiple emotions from the list."}
-plot_T1emotion_heatmap
+Participants could check multiple emotions from the list.
+Rows and columns ordered with the PCA angle method in the seriation package."}
+hagenheat(dfT1emotion_vignette, rotate_labels = F, seriation_method = 'PCA_angle', viridis_option = 'B') + theme_minimal(15)
 ```
@@
 Each cell represents the proportion of participants who inferred that emotion.
-Participants could check multiple emotions from the list."}
-plot_T2emotion_heatmap
+Participants could check multiple emotions from the list.
+Rows and columns ordered with the PCA angle method in the seriation package."}
+
+hagenheat(dfT2emotion_signal, rotate_labels = F, seriation_method = 'PCA_angle', viridis_option = 'B') + theme_minimal(15)
+```
+
+## Change in emotions T1 to T2 by signal
+
+```{r diffemotions, fig.width=8, fig.cap="Change in inference of victim's emotional state From pre- to post-signal.
+Each cell represents the difference in proportions of participants who inferred that emotion (T2 - T1).
+Participants could check multiple emotions from the list.
+Rows and columns ordered with the PCA angle method in the seriation package."}
+
+d_diff <- as.matrix(dfT2emotion_signal[-1]) - as.matrix(dfT1emotion_signal[-1])
+rownames(d_diff) <- dfT2emotion_signal$name
+
+hagenheat(d_diff, rotate_labels = F, seriation_method = 'PCA_angle') + scale_fill_gradient2()
+
 ```

### 2021-03-25 R/functions.R

@@ -189,28 +189,63 @@ plot_raw_data <- function(d, type){
     )
 }
 
-T2emotion_heatmap <- function(d){
-  d %>%
-    dplyr::select(signal, T2Angry:T2Violated) %>%
-    pivot_longer(-signal) %>%
-    mutate(name = stringr::str_remove(name, 'T2')) %>%
-    group_by(name, signal) %>%
-    summarise(n = sum(value)/n()) %>%
-    pivot_wider(names_from = signal, values_from = n, values_fill = 0) %>%
-    hagenheat(rotate_labels = F, seriation_method = 'PCA_angle', viridis_option = 'B') +
-    theme_minimal(15)
-}
-
-T1emotion_heatmap <- function(d){
+T1emotion_vignette <- function(d){
   d %>%
     dplyr::select(vignette, T1Angry:T1Violated) %>%
     pivot_longer(-vignette) %>%
     mutate(name = stringr::str_remove(name, 'T1')) %>%
     group_by(name, vignette) %>%
     summarise(n = sum(value)/n()) %>%
-    pivot_wider(names_from = vignette, values_from = n, values_fill = 0) %>%
-    hagenheat(rotate_labels = F, seriation_method = 'PCA_angle', viridis_option = 'B') +
-    theme_minimal(15)
+    pivot_wider(names_from = vignette, values_from = n)
+}
+
+T1emotion_signal <- function(d){
+  d %>%
+    dplyr::select(signal, T1Angry:T1Violated) %>%
+    pivot_longer(-signal) %>%
+    mutate(name = stringr::str_remove(name, 'T2')) %>%
+    group_by(signal, name) %>%
+    summarise(n = sum(value)/n()) %>%
+    pivot_wider(names_from = signal, values_from = n)
+}
+
+T2emotion_signal <- function(d){
+  d %>%
+    dplyr::select(signal, T2Angry:T2Violated) %>%
+    pivot_longer(-signal) %>%
+    mutate(name = stringr::str_remove(name, 'T2')) %>%
+    group_by(signal, name) %>%
+    summarise(n = sum(value)/n()) %>%
+    pivot_wider(names_from = signal, values_from = n)
+}
+
+
+# Effect sizes ------------------------------------------------------------
+
+eff_sizes <- function(d){
+  signals <- as.character(unique(d$signal))[-1]
+  vignettes <- unique(d$vignette)
[…]

### 2021-03-25 _packages.R

@@ -1,12 +1,9 @@
 # Generated by targets::tar_renv(): do not edit by hand
 library(broom)
-library(bs4Dash)
 library(car)
-library(clustermq)
 library(dplyr)
 library(effects)
 library(forcats)
-library(future)
 library(ggforce)
 library(gglm)
 library(ggplot2)
@@ -14,12 +11,7 @@ library(glmmboot)
 library(gt)
 library(hagenutils)
 library(mediation)
-library(pingr)
 library(purrr)
-library(rstudioapi)
-library(shiny)
-library(shinycssloaders)
-library(shinyWidgets)
 library(signaling2020data)
 library(tidyr)
 library(visNetwork)

### 2021-03-25 _targets.R

@@ -7,7 +7,7 @@ source("R/functions.R")
 
 # Set target-specific options such as packages.
 tar_option_set(
-  packages = c("signaling2020data", "car", "hagenutils", "visreg", "effects", "glmmboot", "broom", "mediation", "gglm", "gt", "ggforce", "dplyr", "tidyr", "purrr", "ggplot2", "forcats"),
+  packages = c("signaling2020data", "car", "hagenutils", "visreg", "effects", "glmmboot", "broom", "mediation", "gglm", "gt", "ggforce", "dplyr", "tidyr", "purrr", "ggplot2", "forcats", "stringr"),
   imports = c("signaling2020data")
   )
 
@@ -194,7 +194,7 @@ tar_target(
     T1Belief_Action_dist(d)
   ),
 
-# Emotion plot ------------------------------------------------------------
+# Emotion plots -----------------------------------------------------------
 
   tar_target(
     plot_emotions,
@@ -202,13 +202,18 @@ tar_target(
   ),
 
   tar_target(
-    plot_T1emotion_heatmap,
-    T1emotion_heatmap(d)
+    dfT1emotion_vignette,
+    T1emotion_vignette(d)
   ),
 
   tar_target(
-    plot_T2emotion_heatmap,
-    T2emotion_heatmap(d)
+  dfT1emotion_signal,
+  T1emotion_signal(d)
+),
+
+  tar_target(
+    dfT2emotion_signal,
+    T2emotion_signal(d)
   ),
 
 # Raw data plots ----------------------------------------------------------
@@ -221,6 +226,14 @@ tar_target(
   tar_target(
     plot_raw_actions,
     plot_raw_data(d, 'Action')
+  ),
+
+
+# Effect sizes ------------------------------------------------------------
+
+  tar_target(
+    effect_sizes,
+    eff_sizes(d)
   ),
 
 # Paper -------------------------------------------------------------------

### 2021-03-25 analysis.R

@@ -725,7 +725,8 @@ out <- mediate(mmediator, mout, treat = "signal", mediator = "T2Belief", boot = 
 summary(out)
 plot(out)
 
-d %>%
+dT2signal <-
+  d %>%
   # dplyr::filter(vignette != 'Thwarted marriage') %>%
   dplyr::select(signal, T2Angry:T2Violated) %>%
   pivot_longer(-signal) %>%
@@ -733,15 +734,34 @@ d %>%
   # dplyr::filter(value>0) %>%
   group_by(name, signal) %>%
   summarise(n = sum(value)/n()) %>%
-  pivot_wider(names_from = signal, values_from = n, values_fill = 0) %>%
-  hagenheat(rotate_labels = F, seriation_method = 'PCA_angle', viridis_option = 'B')
+  pivot_wider(names_from = signal, values_from = n, values_fill = 0)
 
-d %>%
+hagenheat(dT2, rotate_labels = F, seriation_method = 'PCA_angle', viridis_option = 'B')
+
+dT1vignette <-
+  d %>%
   dplyr::select(vignette, T1Angry:T1Violated) %>%
   pivot_longer(-vignette) %>%
   mutate(name = str_remove(name, 'T1')) %>%
   # dplyr::filter(value>0) %>%
   group_by(name, vignette) %>%
   summarise(n = sum(value)/n()) %>%
-  pivot_wider(names_from = vignette, values_from = n, values_fill = 0) %>%
-  hagenheat(rotate_labels = F, seriation_method = 'PCA_angle', viridis_option = 'B')
+  pivot_wider(names_from = vignette, values_from = n, values_fill = 0)
+
+hagenheat(dT1, rotate_labels = F, seriation_method = 'PCA_angle', viridis_option = 'B')
+
+dT1signal <-
+  d %>%
+  dplyr::select(signal, T1Angry:T1Violated) %>%
+  pivot_longer(-signal) %>%
+  mutate(name = str_remove(name, 'T1')) %>%
+  group_by(name, signal) %>%
+  summarise(n = sum(value)/n()) %>%
+  pivot_wider(names_from = signal, values_from = n, values_fill = 0)
+
+
+d_diff <- as.matrix(dT2signal[-1]) - as.matrix(dT1signal[-1])
+rownames(d_diff) <- dT2signal$name
+
+hagenheat(d_diff, rotate_labels = F, seriation_method = 'PCA_angle') + scale_fill_gradient2()
+

### 2021-03-25 Paper.rmd
power analysis with pilot data suicide mediation models effect sizes

@@
     'd',
+    'power_curve',
     'models',
@@
     'effect_sizes',
+    'effect_sizes2',
     'effectsPlots', 
@@
     'med1b',
+    'med4',
     'm1b_boot',
@@
 
-## Preregistrations
+## Preregistration
+
+https://osf.io/g3s6n
 
@@
 
-## Sample size in each condition
+## Pilot study description
+
+Briefly, Participants read a vignette that put them in situations in which an imagined sister was requesting a loan of $50,000 from the participant that was originally saved for the participant's imagined daughter’s college education.
+The sister claims the money is needed for medical treatment for her own child, but she has incentives to deceive.
+The manipulations were signals very similar to those used in this study, and the outcomes were belief that the sister really needed the money and intention to load her the money.
+See XX for the full write-up.
+See https://osf.io/3rg8b for preregistration of the pilot study.
+
+## Power from pilot study
+
+We estimated power using our pilot study data by comparing the effect of the *Depression* signal vs.
+the *Verbal request* signal on *Belief* (that the sister needed the money) at T2 controlling for *Belief* at T1 in a linear regression model.
+Specifically, we resampled the pilot data with replacement with sample sizes ranging from N=20 to N=100, fit the linear regression model, and extracted the p-value for the signal coefficient, repeating this 1000 times for each sample size.
+Power was computed as the proportion of p-values < 0.05.
+Power was about 80% for a sample size of about 35, and was about 90% for a sample size of about 45.
+
+```{r power}
+  ggplot(power_curve, aes(sample_size, power)) +
+    geom_line() +
+    labs(x = '\n Sample size (2 conditions)', y = 'Power\n') +
+    theme_minimal(15)
+```
+
+## Sample size in each condition in the current study
 
@@
 
-```{r effectsizes, fig.width=10, fig.height=8, fig.cap="Cohen's d (95% CI) for the effect of each signal on Action and Belief in each vignette relative to the Verbal request signal, ranked by effect size."}
+```{r effectsizes2, fig.width=10, fig.height=7, fig.cap="Within-subjects Cohen's d (95% CI) for the effect of each signal on Belief and Action in each vignette relative to T1 baseline Belief and  Action, respectively, ranked by effect size."}
 
@@
 
+ggplot(effect_sizes2, aes(effsize, fct_reorder(id, effsize), xmin=conf.low, xmax=conf.high, colour = signal, shape=Outcome)) +
+  geom_pointrange(position = position_dodge(width = 0.7), lwd = 2.5, fatten = 1, alpha=0.5) +
+  geom_vline(xintercept = 0, linetype = 'dotted') +
+  scale_y_discrete(labels = relbl) +
+  scale_color_manual(name=NULL, values = c('black', 'darkblue', 'darkred', 'red', 'orange')) +
+  # scale_color_viridis_d(option='A') +
+  guides(colour = guide_legend(override.aes = list(size = 1)), shape = guide_legend(title=NULL, override.aes = list(size = 1))) +
+  # facet_wrap(~Outcome, ncol=1) +
+  labs(x="\nCohn's d (95% CI)", y=NULL) +
+  theme_minimal(15) +
+  theme(legend.position = 'top')
+```
+
+```{r effectsizes, fig.width=10, fig.height=7, fig.cap="Between-subjects Cohen's d (95% CI) for the effect of each signal on Belief and Action in each vignette relative to the Verbal request signal, ranked by effect size."}
+
 ggplot(effect_sizes, aes(est, fct_reorder(id, est), xmin=low, xmax=high, colour = signal, shape=Outcome)) +
@@
   scale_y_discrete(labels = relbl) +
-  scale_color_manual(name=NULL, values = c('black', 'darkred', 'red', 'orange')) +
+  scale_color_manual(name=NULL, values = c('darkblue', 'darkred', 'red', 'orange')) +
   # scale_color_viridis_d(option='A') +
@@
 effectsPlots$m19plot / effectsPlots$m15plot
+```
+
+## Mediation of Suicide attempt signal
+
+The total effect of the *Suicide attempt* signal (treatment) vs.
+*Verbal request* (control) on the likelihood of *Action* was to increase it by `r 100*signif(med4$tau.coef, 3)` points from T1 to T2 (on the original 100-point scale).
+Of this increase, `r 100*signif(med4$n.avg, 2)`% was mediated by the increased *Belief* that the victim was telling the truth.
+See Figure \@ref(fig:mediationsuicide).
+
+```{r mediationsuicide, fig.height=4, fig.cap="The effect of a Suicide attempt (treatment) vs.
+Verbal request (control) on Action (0-1 scale) is largely mediated by Belief.
+ACME: Average causal mediation effect.
+ADE: Average direct effect.
+The mediation model controlled for T1 Belief, and the outcome model controlled for T1 Belief and T1 Action.
+Both models were GLMs with the binomial family (the mediation package does not support the quasibinomial family)."}
+ggmediation(med4)
 ```

### 2021-03-25 R/functions.R

@@ -248,6 +248,50 @@ eff_sizes <- function(d){
     pivot_longer(Belief_low:Action_high, names_to = c('Outcome', '.value'), names_sep = '_')
 }
 
+eff_sizes2 <- function(d){
+
+  tmp1 <-
+    d %>%
+    dplyr::select(vignette, signal, T1Belief, T2Belief) %>%
+    pivot_longer(cols = c(T1Belief, T2Belief)) %>%
+    mutate(name = factor(name, levels = c('T2Belief', 'T1Belief'))) %>%
+    group_by(vignette, signal) %>%
+    rstatix::cohens_d(., value ~ name, paired=T, ci=T, nboot = 1000)
+
+  tmp2 <-
+    d %>%
+    dplyr::select(vignette, signal, T1Action, T2Action) %>%
+    pivot_longer(cols = c(T1Action, T2Action)) %>%
+    mutate(name = factor(name, levels = c('T2Action', 'T1Action'))) %>%
+    group_by(vignette, signal) %>%
+    rstatix::cohens_d(., value ~ name, paired=T, ci=T, nboot = 1000)
+
+  tmp <- bind_rows(list(Belief = tmp1, Action = tmp2), .id = 'Outcome')
+  tmp$id <- paste0(tmp$signal, ',', tmp$vignette)
+  tmp
+}
+
+
+# Power -------------------------------------------------------------------
+
+pwr_curve <- function(signalingdata2018){
+
+  e <-
+    signalingdata2018 %>%
+    dplyr::filter(signal == "Depression:Sister" | signal == "VerbalRequest:Sister") %>%
+    mutate(signal = factor(signal, levels = c("VerbalRequest:Sister", "Depression:Sister")))
+
+  pwr <- function(sample_size){
+    pvalues <- map_dbl(1:2000, ~summary(lm(needsmoneyt2 ~ needsmoneyt1 + signal, e[sample(1:nrow(e), sample_size, replace = T),]))$coefficients["signalDepression:Sister","Pr(>|t|)"])
+    sum(pvalues < 0.05)/length(pvalues)
+  }
+
+  tibble(
+      sample_size = seq(20, 100, 5),
+      power = map_dbl(sample_size, pwr)
+    )
+}
+
 ######### Alternate mediators ############
 
 # tmp <-

### 2021-03-25 _targets.R

@@ -7,8 +7,8 @@ source("R/functions.R")
 
 # Set target-specific options such as packages.
 tar_option_set(
-  packages = c("signaling2020data", "car", "hagenutils", "visreg", "effects", "glmmboot", "broom", "mediation", "gglm", "gt", "ggforce", "dplyr", "tidyr", "purrr", "ggplot2", "forcats", "stringr"),
-  imports = c("signaling2020data")
+  packages = c("signalingdata2018", "signaling2020data", "car", "hagenutils", "visreg", "effects", "glmmboot", "broom", "mediation", "gglm", "gt", "ggforce", "dplyr", "tidyr", "purrr", "ggplot2", "forcats", "stringr"),
+  imports = c("signalingdata2018", "signaling2020data")
   )
 
 # List of target objects
@@ -16,7 +16,10 @@ list(
 
 # Data preparation --------------------------------------------------------
 
+  tar_target(signalingdata2018, signalingdata2018::signalingdata2018),
+
   tar_target(signaling2020, signaling2020data::signaling2020),
+
   tar_target(
   d_tmp,
     signaling2020 %>%
@@ -64,6 +67,14 @@ list(
     d_thwarted,
     d %>%
       dplyr::filter(vignette == 'Thwarted marriage')
+  ),
+
+
+# Power -------------------------------------------------------------------
+
+  tar_target(
+    power_curve,
+    pwr_curve(signalingdata2018)
   ),
 
 # Models ------------------------------------------------------------------
@@ -186,6 +197,26 @@ tar_target(
       mediator = 'T2Belief'
     )
   ),
+  tar_target(
+    med4,
+    signal_mediate(
+      data=d,
+      treat.value = 'Suicide attempt',
+      med_f = 'T2Belief ~ signal + T1Belief',
+      out_f = 'T2Action ~ signal + T1Belief + T1Action + T2Belief',
+      mediator = 'T2Belief'
+    )
+  ),
+tar_target(
+  med4b,
+  signal_mediate(
+    data=d,
+    treat.value = 'Suicide attempt',
+    med_f = 'T2Belief ~ signal * T1Belief',
+    out_f = 'T2Action ~ signal * T1Belief + T1Action + T2Belief',
+    mediator = 'T2Belief'
+  )
+),
 
 # T1 plot -----------------------------------------------------------------
 
@@ -234,6 +265,11 @@ tar_target(
   tar_target(
     effect_sizes,
     eff_sizes(d)
+  ),
+
[…]

### 2021-03-25 analysis.R

@@ -764,4 +764,3 @@ d_diff <- as.matrix(dT2signal[-1]) - as.matrix(dT1signal[-1])
 rownames(d_diff) <- dT2signal$name
 
 hagenheat(d_diff, rotate_labels = F, seriation_method = 'PCA_angle') + scale_fill_gradient2()
-

### 2021-03-25 Paper.rmd
Added pilot data doi
Fixed spelling error

@@
   # facet_wrap(~Outcome, ncol=1) +
-  labs(x="\nCohn's d (95% CI)", y=NULL) +
+  labs(x="\nCohen's d (95% CI)", y=NULL) +
   theme_minimal(15) +

### 2021-03-29 Paper.rmd
Added doi for 2020 data
Added text to the methods section

--- 2021-03-25 Paper.rmd
@@
 title: "Depression and suicidality as costly signals of need"
-author: "Michael Gaffney, Kai Adams, Kristen L. Syme, and Edward H. Hagen"
+author: "Michael R. Gaffney, Kai Adams, Kristen L. Syme, and Edward H. Hagen"
 date: '`r format(Sys.Date(), "%B %d, %Y")`'
@@
 go back and emohasize conflit and PI in the methods (at least in the pilot studies portion)
+add abstract
+add conclusion
 
@@
 
+## Data availibility
+
+http://doi.org/10.5281/zenodo.4637904
+
 # Results
+
+1,950 participants started the study by clicking the link to Qualtrics (1,213 American and 737 Indian).
+After removing participants who did not finish the survey, failed attention checks, or moved through the study at an unrealistc pace, our sample dropped to N = 1,240 (937 American and 303 Indian).
+Basic summary statistics on the remaining N = 1,240 participants (Male = 759, Female = 479) can be found in table XX.
 
@@
 
+Power analyses prior to data collection showed that high proportions of participants scoring extremely high on belief or likelihood of helping at T1 would result in low power for this study's design, a problem which we appeared to largely avoid (see figure XX).
+
+Although not a part of our pre-registered predictions, both T1Belief and T1Action were highly correlated across the four vignettes (enter correlation coefficients), consistent with help being worth providing if the signaler's claims were true (see figure XX).
+
 ```{r t1plot, fig.width=10, fig.height=10, fig.cap="The distributions of Time 1 Belief vs.
@@
 ## Effects of signals on beliefs and actions
+
+As a whole, our predictions for the effect of signal cost on belief and likelihood of helping T2 were met, with costlier signals eliciting greater pro-signaler responses.
+There was also support for an interaction between signal and T1Belief or T1Action, although the effect was not large (See figure 2).
+However, the effect of signal cost varied by vignette, with signal type having the greatest effect in the "basketball coach" and "brother-in-law" vignettes.
+When ordered according to cost, the greatest jump in support tended to occur between crying and mild-depression, with the next largest jump tending to occur between depression and suicide attempt.
+Overall, there was little difference between the effect of mild depression and the effect of depression.
 
@@
 See Figure \@ref(fig:mediation).
+The total effect of the *Suicide attempt* signal (treatment) vs.
+*Verbal request* (control) on the likelihood of *Action* was to increase it by `r 100*signif(med4b$tau.coef, 3)` points from T1 to T2.
+Of this increase, `r 100*signif(med4b$n.avg, 2)`% was mediated by the increased *Belief* that the victim was telling the truth (Check if med4 or med4b is correct; they look identical to me).
 
@@
 ## Effects of signals on victim's perceived emotional state
+
+We also examined the effect of signaling on how participants perceived the signaler's emotional state.
+To do this, we created four new variables: LowMood (T1 and T2) and Manipulative (T1 and T2).
+This was done by adding the dummy variables for whether a participant thought the signaler was depressed, distressed or sad for the LowMood variables and by adding the dummy variables for whether they thought the particpant was Devious or Jealous for the Manipulative variables.
+In all instances, 0 indicated a participant did not select the emotion, while 1 indicated selection.
+
+We then plotted the mean change seen in the data in addition to the change seen in 500 bootstrap resamples (see figure 6).
 
@@
 See https://osf.io/3rg8b for preregistration of the pilot study.
+See http://doi.org/10.5281/zenodo.4637883 for pilot data.
 

### 2021-03-30 Paper.rmd
Edited the intro

@@
 # Introduction
-Since Durkheim’s pioneering effort to use quantitative social science to explain suicide, varied attempts by anthropologists, psychologists, and sociologists and substantial investment by funding agencies, rates of depression and suicide attempts have remained largely unchanged over the last 100 years (confirm and cite), and there is still substantial uncertainty about why both are as common as they are (cite).
-Due to their high costs, the vast majority of these approaches have been built on the assumption that they are the result of internal dysfunction (cite examples).
+Since Durkheim’s pioneering effort to use quantitative social science to explain suicide (cite), anthropologists, psychologists, and sociologists have made varied attempts at explaining depression and suicide.
+However, despite this effort and substantial investment by funding agencies, rates of depression and suicide attempts have remained largely unchanged over the last 100 years (confirm and cite), and there is still substantial uncertainty about why both are as common as they are (cite).
+Likely due to their high costs and the suffering they cause, the vast majority of these approaches have been built on the assumption that they are the result of internal dysfunction (cite examples).
 However, a subset of anthropologists and evolutionary theorists have challenged this idea, suggesting that despite the subjective suffering they cause, they may function as a means to limit negative fitness outcomes in times of substantial adversity (Firth + others).
@@
 Compared to non-depressed individuals, those with depression tend to report at least twice as many instances of negative events in both community and clinical samples (Mazure, 1998) and more negative events than those with schizophrenia and bipolar depression across a wide range of studies (Paykel, 1994).
-In instances where this is the case, the onset of depression tends to be rapid, often occurring within one month of the event (Kendler et al., 1999 [double check and find others]).
+In instances where depression is preceded by negative events, the onset of depression tends to be rapid, often occurring within one month of the event (Kendler et al., 1999 [double check and find others]).
 
@@
 Support for this comes from the fact that the relationship between negative events and depression holds true when looking solely at events outside of one's control, which shows that the connection is unlikely to be driven solely by depressed individuals creating situations where negative events are likely to be common (Hammen, 2005; Kendler et al., 1999).
-In addition to this, twin studies have shown that one's history of negative events is still a strong predictor when controlling for genetic similarity and that part of the heritability of depression stems from the heritability of negative events, like divorce and family conflict (Kendler & Baker, 2007; Kendler et al., 1999).
+In addition to this, twin studies have shown that one's history of negative events is still a strong predictor of major depression when controlling for genetic similarity and that part of the heritability of depression stems from the heritability of negative events, like divorce and family conflict (Kendler & Baker, 2007; Kendler et al., 1999).
 
@@
 Suicide attempts also tend to co-occur with social adversity (Hagen et al., 2008 + cite and describe), with evidence of this existing cross-culturally.
-Greif over the loss of a loved one (Firth; Devries et al.
+Grief over the loss of a loved one (Firth; Devries et al.
 2011), bullying (Alavi et al., 2017; Butler et al., 2019; Ford et al., 2017; Wang et al., 2020), and instances of social transgression (Firth; Malinowski; Syme and Hagen 2018; find Western citation to confirm) have all been reported to lead to suicidal behavior in both industrialized (confirm the transgression part) and traditional societies.
-As with depression, assault is a powerful risk factor for suicidal behavior, something which has been found in multiple large-scale multi-country studies (Devries et al.
+Of the recorded instances of suicide attempts in the Human Relations Area Files (HRAF), 77.4% of attempts were found to be linked to times of social conflict, 88.7% were linked to fitness threats in general, and 84.9% were linked to situations in which attempters were powerless to resolve their situation alone (Syme et al., 2016).
+As with depression, assault is an particularly powerful risk factor for suicidal behavior based on multiple large-scale multi-country studies (Devries et al.
 2011; Ellsberg et al.
-2008).
-Both sexual and non-sexual assault were also associated with more self-harm and suicidal behaviors among both indigenous Sami and majority Norwegian adolescents, with those who attempted suicides reporting more than twice the number of negative life events than those who did not (Reigstad and Kvernmo 2017).
-The connection between social adversity and suicide is also seen in the Human Relations Area Files (HRAF), in which 77.4% of attempts were found to be linked to times of social conflict, 88.7% were linked to fitness threats in general, and 84.9% were linked to situations in which attempters were powerless to resolve their situation alone (Syme et al., 2016).
+2008) and more localized examinations.
+For example, both sexual and non-sexual assault were also associated with more self-harm and suicidal behaviors among both indigenous Sami and majority Norwegian adolescents, with those who attempted suicides also reporting more than twice the number of negative life events than those who did not (Reigstad and Kvernmo 2017).
 
@@
 Beyond resulting in the cost differential that allows for costly signaling in the first place, the costs of depression and suicidal behavior may be particularly important in times of conflict or when the level of support needed to address one’s situation is substantial.
-Importantly, there are likely few forms of adversity that do not come with conflict.
+Importantly, there are likely few forms of social adversity that do not come with conflict.
 For example, breakups in both romantic and cooperative relationships are often preceded by conflict (Amato & Hohmann-Marriott, 2007), and surely involve conflict when one side wants reconciliation and the other does not.
@@
 In these instances, less costly signals like verbal requests, facial sadness, and crying are likely to be unreliable as their low costs can easily be made up for with increased social support, thereby favoring the use of costlier signals in those experiencing need they cannot resolve on their own.
-Importantly, the amount of conflict
 
@@
 This is possible due to the reduced investment in others that frequently accompanies depression or the threat to future cooperation that comes from a suicide.
-In these instances, depression is suggested to function analogously to a labor strike, sending the message that one’s need is genuine and that if the target of the signal wanted to continue receiving benefits from the depressed, he or she would need to increase support towards the signaler.
+In these instances, depression and suicide attempts are suggested to function analogously to a labor strike, sending the message that one’s need is genuine and that if the target of the signal wanted to continue receiving benefits from the depressed, he or she would need to increase support towards the signaler.
 
@@
 Beneficial social changes are also reported in traditional societies.
-Unlike Western countries, where suicide is often viewed as pathological (Hidaka, 2012), members of traditional societies have been reported to view suicide attempts as cries for help rather than mental illness (Shostak, 1981).
+Unlike many Western countries, where suicide is often viewed as pathological (Hidaka, 2012), members of traditional societies have been reported to view suicide attempts as cries for help rather than mental illness (Shostak, 1981).
 For example, attempts have been described as ways of escaping unwanted marriage arrangements, persistent abuse, or a lack of support in obtaining mates by those engaging in the behavior and observers (Gutierrez de Pineda & Muirden, 1948; Hilger, 1957; Karsten, 1935; Tessmann, 1930; Wilson, 1960), suggesting that help is at least occasionally provided or reliably expected.

### 2021-03-31 Paper.rmd
Edited methods: - removed Pilot Studies section (MG draft; EH still in SI) - Improved wording on the design and vignette sections - minor edits and proofreading fixes elsewhere

@@
 Find a place for the predictions and preregistration 
-go back and emohasize conflit and PI in the methods (at least in the pilot studies portion)
+go back and emphasize conflict and PI in the methods (at least in the pilot studies portion)
 add abstract
@@
 
-This study involved a vignette study with between subjects pre-test/post-test design with one factor (signal) and 5 levels (verbal request, crying, crying with behavioral changes, depression, and suicide attempt), with the outcome of interest being how believe and likelihood of helping changed in response to a given signal.
-
-## Pilot Studies
-
-The first pilot study used a vignette study to examine how the presence of conflict, private information, and emotional signaling impacted the degree participants believed the signaler to be in need and provide support using an MTurk sample of 1,447 Americans.
-Of the signals, depression resulted in the most pro-signaler responses (reword), separating itself from the less costly signals when conflict and private information was present and substantially outperforming the schizophrenic break control.
-However, the suicide attempt condition was responded to relatively poorly, contrary to predictions.
-
-One potential explanation is that the initial scenario of a mother asking their sibling for help paying for their young daughter's heart surgery was not severe enough for a suicide attempt to be a functional signal, due to a lack of beleivability or due to its costs appearing manipulative.
-For this reason, we designed this study with more severe scenarios that were also associated with suicide attempts both ethnographically and clinically, including instances of sexual assasult, non-sexual assault, and thwarted marriage.
-
-add that we ask now ask same question twice? (interpretabilty)
-
-The second was posted on the samplesize subreddit with the goals of testing the beleivability of the new vignettes and how pro-signaler participants were at T1, with a power analysis with simulated data showing this would limit our power.
-In this small sample of 28, we saw no evidence that beleivabilty was a problem and no evidence that participants as a whole would be too pro-sister at T1.
+This study involved a between-subjects pretest-posttest design to examine how different emotional signals would influence (1) the degree participants believed a fictional character to be in need and (2) the likelihood they would provide help within a vignette study.
 
@@
 
-Four vignettes were used in this study, with participants in the US sample being randomly assigned to either the "basketball coach," "romantic partner," or "brother-in-law" vignettes.
-In the "basketball coach" scenario, the star player on a unversity basketball team comes to the participant (who is asked to imagine themselves as the athletic director at a university) and claims she was sexually assaulted by the coach.
+Four vignettes were used in this study in which both the presence of conflicts of interest and the existence of private information about one's need were emphasized.
+Due to the expectation that depression and suicide are likely too costly of signals for relatively minor instances of need, we designed this study to involve severe scenarios associated with suicide attempts both ethnographically and clinically (i.e, sexual assault (cite), non-sexual assault (cite), and thwarted marriage (cite)).
+
+Participants in the US sample were randomly assigned to either the "basketball coach," "romantic partner," or "brother-in-law" vignettes.
+In the "basketball coach" scenario, the star player on a university basketball team comes to the participant (who is asked to imagine themselves as the athletic director at a university) and claims she was sexually assaulted by the coach.
 However, there are indications the player might be lying to get more playing time.
 
-The "brother-in-law" vignette involved participants imagining that they let their sister, brother-in-law, and niece move in with the participant and an imagined 15-year-old daughter after they lost their house in a fire.
-During this time, the participant's daughter becomes jealous of your niece before accusing her uncle of sexually assaulting her.
+The "brother-in-law" vignette involved participants imagining that they let their sister, brother-in-law, and niece move in with the participant and their 15-year-old daughter after they lost their house in a fire.
+During this time, the participant's daughter becomes jealous of her cousin before accusing her uncle of sexually assaulting her.
 
-The "romantic partner" vignette hard participants imagine that they found the best partner they have ever had after years of being single.
+The "romantic partner" vignette had participants imagine that they found a highly desirable partner after years of being single.
 However, their 13-year-old daughter, who has a history of trying to get in the way of their relationships is clearly not happy with this.
-At one point, she accuses the romantic partner of physically assaulting her but cannot produce any evidence.
+After a period of sustained conflict, she accuses the romantic partner of physically assaulting her but cannot produce any evidence.
 
-Those in the Indian sample only saw the "thwarted marriage vignette." In this scenario, the participant and their family is trying to arrange a dowry for their older daughter so she can marry the man she loves.
-After his family demands more money, the participant's family tries to find another man, who the older daughter claims to find unattractive.
-However, it is unclear how unattractive he is and any additional investment in the dowry will come at the expense of the younger daughter.
+Those in the Indian sample only saw the "thwarted marriage vignette." In this scenario, the participant and their family is described as trying to arrange a dowry for their older daughter so she can marry the man she loves.
+After the man's family demands more money, the participant's family tries to find a second man, who the older daughter claims to find unattractive.
+However, it is unclear if the second man is as unattractive as the older daughter says or if she does not value her younger sister enough, since any additional investment in the dowry will come at the expense of the younger daughter.
 
-The full vignettes are available in the supplementary information.
+The full vignettes are available in the SI.
 
@@
 
-As the amount of crying in those with depression is moderately associated with depression severity [@VingerhoetsEtAl2016] and depression is a major risk factor for suicide [@BostwickPankratz2000; @Kessler2012], each signal was designed to build off of the less costly signals so that each signal contained elements of any signal it was costlier than.
+As the amount of crying in those with depression is moderately associated with depression severity [@VingerhoetsEtAl2016] (check this.
+he might have a paper saying it's not associated with depression as people tend to think) and depression is a major risk factor for suicide [@BostwickPankratz2000; @Kessler2012], each signal was designed to build off of the less costly signals so that each signal contained elements of any signal it was costlier than.
 
@@
 This is seen in that while both MTurk workers and university students engage in problematic behaviors that might lessen data quality to similar amounts [@NeckaEtAl2016], workers on MTurk have been shown to be more attentive than samples of university students [@HauserSchwarz2016].
-For this reason, concerns about data quality come primarily from potential bot use and respondents faking their location to take surveys in a language they do not understand well, with the former concern being largely unfounded and the latter able to be corrected for with the tools used in this study [@KennedyEtAl2018]
+For this reason, concerns about data quality come primarily from potential bot use and respondents faking their location to take surveys in a language they do not understand well, with the former concern being largely unfounded (at least for full on bots?
+do we mention human-assisted?)[@KennedyEtAl2018] and the risk of the latter able to be minimized through well designed attention checks (cite) .
 
@@
 After accepting the HIT on MTurk, every participant took the survey using Qualtrics.
-In every instance, the elements of the survey were laid out in the following order: 1) the consent form, 2) the vowel attention check, 3) the main body of the vignette, 3) the pre-test baseline measures (T1), 4) the story content attention check, 5)  the signal portion of the vignette, 7) the post-test outcome measures (T2), 8) an attention check that did not filter out participants, 9) a set of demographic questions, and 10) an open feedback prompt.
+In every instance, the elements of the survey were laid out in the following order: 1) the consent form, 2) the vowel attention check, 3) the main body of the vignette, 3) the pre-test baseline measures (T1), 4) the story content attention check, 5)  the signal portion of the vignette, 7) the post-test outcome measures (T2-T3), 8) an attention check that did not filter out participants (T4), 9) a set of demographic questions, and 10) an open feedback prompt.
 The full survey can be found in the SI.
@@
 
-In both samples, we recorded self-reports on how much participants believed the signaler to be telling the truth (BeliefT1) and the likelihood of them helping the signaler as requestedc (ActionT1).
-With the thwarted marriage vignette we also asked how they would split the money they had saved for the dowry between their daughters (Divide T1).
+In both samples, we recorded self-reports on how much participants believed the signaler to be telling the truth (T1Belief) and the likelihood of them helping the signaler as requested (T1Action).
+With the thwarted marriage vignette we also asked how they would split the money they had saved for the dowry between their daughters (T1Divide).
 In every instance, the order of the questions was randomized to avoid order effects [@KrosnickAlwin1987].
@@
 Responses were recorded with sliders due to the fact they allow for finer grained changes than categorical scales [@KlimekEtAl2017].
-In every instance the position started at the left due to findings that people may be less likely to move the slider when it starts in the center (cite and word better).
-For the exact wording of the question and the ends of each continuum, see table 1.
+In every instance the position started at the left due to findings that people may be less likely to move the slider from central starting positions (cite and word better).
+For the exact wording of the question and the labels on the sliders, see table 1.
 
@@
 
-As both a validity check and a way to understand the degree participants would be willing to help if they believed the participant completely, we presented participants with strong evidence that the claims were true (Action T3).
-In the US sample, this involved video evidence of the event in question occuring or a similar event after the fact.
+As both a validity check and a way to understand the degree participants would be willing to help if they believed the participant completely, we presented participants with strong evidence that the claims were true (T3Action).
+In the US sample, this involved video evidence of the event in question occurring or a similar event after the fact.
 With the thwarted marriage vignette, this involved the participant seeing the man their daughter wants to marry trash talk their daughter and their family.
-As a final attention check, we presented participants with the Action T3 question but included instructions to ignore this and drag the slider all the way to the left (T4AttentionCheck).
+As a final attention check, we presented participants with the T3Action question but included instructions to ignore this and drag the slider all the way to the left (T4AttentionCheck).
 We did not exclude anyone from the study for failing this nor did we withhold payment.
@@
 
-Consistent with costly signaling theory, costlier signals resulted in greater perceptions of need and increased the likelihood of participants helping the signaler than the less costly signals.
+Consistent with costly signaling theory (is this a common enough prediction to say this?), costlier signals resulted in greater perceptions of need and increased the likelihood of participants helping the signaler than the less costly signals.
 This effect was largest in the "brother-in-law" and "romantic partner" vignettes, both of which involved claims of assault against participants' imagined daughters.
@@
 One potential reason for this is the increase in symptoms from mild depression to depression was not costly enough to result in a large effect as the symptoms only differed in severity (e.g., grades dropping from As to Bs [mild depression] or Cs [depression]).
-Such small changes may be less impactful in vignette form than in real-life scenarios in which the effects of signaling may increase in severity and be prolonged over a lenghty period of time.
+Such small changes may be less impactful in vignette form than in real-life scenarios in which the effects of signaling may increase in severity and be prolonged over a lengthy period of time.
 
@@
 For this reason, too strong of a signal may be seen as manipulative or a cue of dysfunction, and therefore, be responded to aversively.
-However, belief in need and likelihood of help at T2 still remained high when it was high at T1, suggesting that this may not be a significant risk when one is in severe enough need (want to bring in MA here.
-Is that a bad idea?).
+However, belief in need and likelihood of help at T2 still remained high when it was high at T1, suggesting that this may not be a significant risk when one is in severe enough need.
 
@@
 
-Although this study was not designed to examine whether the costs of signaling would be made up for by the increased support stemming from depression and suicide attempts directly, the results are encouraging.
+Although this study was not designed to examine whether the costs of signaling would be made up for by the increased support stemming from depression and suicide attempts directly, the results are encouraging (reword).
 In general, the costs required to honestly convey one's qualities should be expected to increase with the potential payoffs of deception (cite), with the vignettes in this study emphasizing the existence of private information and sizable conflicts of interest to increase the perceived risk of being taken advantage of.

### 2021-04-01 Paper.rmd
Edited methods and limitations

@@
 Since Durkheim’s pioneering effort to use quantitative social science to explain suicide (cite), anthropologists, psychologists, and sociologists have made varied attempts at explaining depression and suicide.
-However, despite this effort and substantial investment by funding agencies, rates of depression and suicide attempts have remained largely unchanged over the last 100 years (confirm and cite), and there is still substantial uncertainty about why both are as common as they are (cite).
+Despite this effort and substantial investment by funding agencies, rates of depression and suicide attempts have remained largely unchanged over the last 100 years (confirm and cite), and there is still substantial uncertainty about why both are as common as they are (cite).
 Likely due to their high costs and the suffering they cause, the vast majority of these approaches have been built on the assumption that they are the result of internal dysfunction (cite examples).
@@
 
-The "brother-in-law" vignette involved participants imagining that they let their sister, brother-in-law, and niece move in with the participant and their 15-year-old daughter after they lost their house in a fire.
+The "brother-in-law" vignette involved participants imagining that they let their sister, brother-in-law, and niece move in with the participant and their 15-year-old daughter after their sister's family lost their house in a fire.
 During this time, the participant's daughter becomes jealous of her cousin before accusing her uncle of sexually assaulting her.
@@
 After the man's family demands more money, the participant's family tries to find a second man, who the older daughter claims to find unattractive.
-However, it is unclear if the second man is as unattractive as the older daughter says or if she does not value her younger sister enough, since any additional investment in the dowry will come at the expense of the younger daughter.
+Due to the younger daughter in the story only being two years younger, any additional investment in the dowry will come at the younger daughter's expsense.
 
@@
 As the amount of crying in those with depression is moderately associated with depression severity [@VingerhoetsEtAl2016] (check this.
-he might have a paper saying it's not associated with depression as people tend to think) and depression is a major risk factor for suicide [@BostwickPankratz2000; @Kessler2012], each signal was designed to build off of the less costly signals so that each signal contained elements of any signal it was costlier than.
+IIRC he might have a more recent paper saying it's not associated with depression as people tend to think) and depression is a major risk factor for suicide [@BostwickPankratz2000; @Kessler2012], each signal was designed to build off of the less costly signals so that each signal contained elements of any signal it was costlier than.
+The full text for the signals are availible in the SI.
 
@@
 Participants for this study were recruited from Amazon Mechanical Turk, a crowdsourcing platform that allows for the creation of Human Intelligence Tasks (HITs) that workers can complete for pay.
-As Amazon provides the infrastructure, it allows for a relatively low-cost way of collecting data for academic research at the cost of the data not being representative of any real population.
-Despite this limitation, it is more diverse than most convenience samples [@KennedyEtAl2018; @DworkinEtAl2016], with turkers in the U.S.
-mainly differing in being younger, more educated, lower income, and more female biased than the greater U.S.
-population [@RossEtAl2010].
+As Amazon provides the infrastructure, it allows for a relatively low-cost way of collecting data for academic research at the cost of the data not being representative of any real population (Thomas and Clifford 2017).
+Despite this limitation, it is more diverse than most convenience samples [@KennedyEtAl2018(2020 now); @DworkinEtAl2016; (Thomas and Clifford 2017)], with turkers in the US mainly differing in being younger, more educated, and lower income than the greater U.S.
+population [@RossEtAl2010]; Boas et al.
+2018).
+Indian samples are also likely to be younger and more educated than the general population but differ from US samples in that they are less diverse, have higher incomes relative to other Indians, and are more likely to come from regions with good internet access (Boas et al.
+2018)
 
-Overall, the quality of data provided by MTurk workers tends to resemble that of university sample pools, with there being some indication that it might outperform university samples in a few important areas.
-This is seen in that while both MTurk workers and university students engage in problematic behaviors that might lessen data quality to similar amounts [@NeckaEtAl2016], workers on MTurk have been shown to be more attentive than samples of university students [@HauserSchwarz2016].
-For this reason, concerns about data quality come primarily from potential bot use and respondents faking their location to take surveys in a language they do not understand well, with the former concern being largely unfounded (at least for full on bots?
-do we mention human-assisted?)[@KennedyEtAl2018] and the risk of the latter able to be minimized through well designed attention checks (cite) .
+Overall, the quality of data provided by MTurk workers tends to resemble that of university sample pools[@NeckaEtAl2016, Robinson et al.
+2019], with there being some indication that it might outperform university samples due to its previously mentioned diversity (Thomas and Clifford 2017) or the overall attentiveness of turkers [@HauserSchwarz2016].
+For this reason, concerns about data quality come primarily from the threat of bot use or respondents faking their location to take surveys in a language they do not understand well, with there being little evidence of the former [@KennedyEtAl2018] and the risk of the latter able to be minimized through well designed attention checks, timed responses, or general study design (Aguinis et al.
+2020; Huang et al.
+2015; Kennedy et al.
+2020; Thomas and Clifford 2017).
 
@@
 
-To ensure participants were paying attention, we used a variety of attention checks, which we clearly labeled in an attempt to avoid demand characteristics.
+To reduce the risk of low quality responses, we used a variety of attention checks, which we clearly labeled in an attempt to avoid demand characteristics.
 The first was shown immediately after the consent form and provided participants with a random word and asked them to enter the vowels in the order in which they are found in the word.
@@
 
-We also filtered out those who read the vignette faster than one-third the time it took MG to read it as fast as possible without concern for comprehension immediately after the vignette.
+We also filtered out those who read the vignette faster than one-third the time it took MG to read it as fast as possible without concern for comprehension.
+This occured immediately after participants finished the vignette.
 
-Informed consent was given by proceeding with the study after reading the consent form, and all participants who passed the attention checks were paid $1 for their time. (mention time here)
+Informed consent was given by proceeding with the study after reading the consent form, and all participants who passed the attention checks were paid $1 for their time, with us estimating it would take 4-8 minutes before data collection.
+This study was certified exempt by the Washington State University Human Research Protection Program (certification number: 18528-001).
 
@@
 
-The largest source of limitations of this study is its lack of ecological validity, something which had to be sacrificed for any experimental design involving depression and suicide attempts.
+The main limitation of this study is its lack of ecological validity, something which had to be sacrificed for any experimental design involving depression and suicide attempts.
 It is almost certain that participants experienced this study differently than they would if the event actually happened to them.
-This may have biased results in a pro-signaler direction due to the lack of meaningful costs making support feel less costly or through the likely inability of participants to imagine themselves in an anonymous scenario (cite your paper on this) leading them to take an opportunity to signal generosity cheaply.
-It may have also biased participants against helping if they could not fully imagine the characters in the story as kin or important cooperative partners, while the survey's short duration may have weakened the strength of the bargaining of the costlier signals.
-However, both the findings of a main effect of signal and the effect of signal type on likelihood of support was largely mediated by change in belief suggest that participants were paying attention to the theoretically relevant details in ways that influenced their behavior.
+This may have biased results in a pro-signaler direction if the lack of meaningful costs made support feel less costly or if the likely inability of participants to imagine themselves in an anonymous scenario (cite your paper on this) led them to take an opportunity to signal generosity cheaply.
+It may have also biased participants against helping if they could not fully imagine the characters in the story as kin or important cooperative partners, while the survey's short duration may have weakened the strength of the costlier signals as bargaining tools.
+However, the fact that the relationships among signal cost, belief in need, and likelihood of providing support all largely fit existing theory (narrow and broad) indicates that participants paid attention to the relevant details and responded in ways that suggest some degree of external validity.
+For this reason, the benefits of addressing causal relationships that came through our experimental vignette approach likely outweighed the costs.
 
@@
 Compared to the US sample, far more participants were filtered out by our attention checks, something which could be consistent with botting, unfamiliarity with English, or low effort responses.
-Assuming this corresponded with more low-quality responses among those who passed the attention checks, the differences seen among those in the thwarted marriage vignette may simply be due to added noise rather than differences in the scenarios or the effectiveness of the signals among Indians compared to Americans.
+Assuming this corresponded with lower-quality responses among those who passed the attention checks, the differences seen among those in the thwarted marriage vignette may simply be due to added noise rather than differences in the scenarios or the effectiveness of the signals among Indians compared to Americans.
 

### 2021-04-01 Paper.rmd
Small text edits throughout the paper

@@
 # Introduction
-Since Durkheim’s pioneering effort to use quantitative social science to explain suicide (cite), anthropologists, psychologists, and sociologists have made varied attempts at explaining depression and suicide.
+Since Durkheim’s pioneering effort to use quantitative social science to explain suicide (cite), anthropologists, psychologists, and sociologists have made varied attempts at better understanding depression and suicide.
 Despite this effort and substantial investment by funding agencies, rates of depression and suicide attempts have remained largely unchanged over the last 100 years (confirm and cite), and there is still substantial uncertainty about why both are as common as they are (cite).
-Likely due to their high costs and the suffering they cause, the vast majority of these approaches have been built on the assumption that they are the result of internal dysfunction (cite examples).
+Likely due to  the suffering they cause, the vast majority of these approaches have been built on the assumption that they are the result of internal dysfunction (cite examples).
 However, a subset of anthropologists and evolutionary theorists have challenged this idea, suggesting that despite the subjective suffering they cause, they may function as a means to limit negative fitness outcomes in times of substantial adversity (Firth + others).
@@
 Compared to non-depressed individuals, those with depression tend to report at least twice as many instances of negative events in both community and clinical samples (Mazure, 1998) and more negative events than those with schizophrenia and bipolar depression across a wide range of studies (Paykel, 1994).
-In instances where depression is preceded by negative events, the onset of depression tends to be rapid, often occurring within one month of the event (Kendler et al., 1999 [double check and find others]).
+In instances where depression is preceded by negative events, it's onset tends to quickly follow, often occurring within one month of the event (Kendler et al., 1999 [double check and find others]).
 
-This strong connection between negative life events and depression along with the need and distress that likely accompanies these events has led to the suggestion that this relationship is causal (Kendler et al., 1999).
-Support for this comes from the fact that the relationship between negative events and depression holds true when looking solely at events outside of one's control, which shows that the connection is unlikely to be driven solely by depressed individuals creating situations where negative events are likely to be common (Hammen, 2005; Kendler et al., 1999).
+This strong connection between negative life events and depression along with the adversity and distress that likely accompanies these events has led to the suggestion that this relationship is causal (Kendler et al., 1999).
+Support for this comes from the fact that the relationship between negative events and depression holds true when looking solely at events outside of one's control, showing that the connection is unlikely to be driven solely by depressed individuals creating situations where negative events are likely to be common (Hammen, 2005; Kendler et al., 1999).
 In addition to this, twin studies have shown that one's history of negative events is still a strong predictor of major depression when controlling for genetic similarity and that part of the heritability of depression stems from the heritability of negative events, like divorce and family conflict (Kendler & Baker, 2007; Kendler et al., 1999).
@@
 Of the many types of negative life events associated with depression, those which involve social adversity tend to be more strongly associated with depression (Hammen, 2005; Kendler et al., 1999; Mazure, 1998).
-Like the relationship between negative events as a whole and depression, this relationship is also seen cross-culturally, with the loss of a loved one, threat of divorce, or abusive relationships all increasing one's chances of becoming depressed (Kendler et al., 1999, 1995).
-Of these events, physical assault has been found to be the strongest predictor of depression in the few studies in which it has been examined (Kendler et al., 1999, 1995) and may have been much more common throughout our evolutionary history than is often thought based on rates of spousal abuse in small-scale societies with little or no policing (Levinson, 1989; Stieglitz et al., 2018).
+Like the relationship between negative events as a whole and depression, this relationship is also seen cross-culturally, with the loss of a loved one, threat of divorce, or abusive relationships all increasing one's chances of becoming depressed (Kendler et al., 1999, 1995 [check if this fits the cross-cultural claim]).
+Of these events, physical assault has been found to be the strongest predictor of depression in the few studies in which it has been examined (Kendler et al., 1999, 1995) and may have been much more common throughout our evolutionary history than is often appreciated based on rates of spousal abuse in small-scale societies with little or no policing (Levinson, 1989; Stieglitz et al., 2018).
 
@@
 
-Although there may be other ways for honest signals evolve (cite), one of the most widely accepted (confirm) means is through costly signaling.
+Although there may be other ways for honest signals evolve (cite), one of the most widely accepted (is this fair?) means is through costly signaling.
 The evolution of costly signals is possible whenever the signal in question is comparatively cheaper to produce for those who have the underlying quality compared to those who lack it (Grafen 1990).
@@
 For this reason, the way others view and respond to suicide attempts is likely to be strongly influenced by the probability that the attempt would result in death or severe injury (Rosenthal, 1993).
-That given, the previously mentioned logic still applies with increased risk of death being relatively costly for those able to enhance their fitness prospects in their day-to-day lives.
+That given, the previously mentioned logic still applies with increased risk of death being relatively costly for those able to advance their fitness prospects in their day-to-day lives.
 
@@
 
-In addition to signaling need to those invested in the well-being of the signaler, depression and suicidal behavior may also help an individual bargain for increased support.
+In addition to signaling need to those invested in the well-being of the signaler, depression and suicidal behavior may also help an individual bargain for increased support (Hagen 2003).
 This is possible due to the reduced investment in others that frequently accompanies depression or the threat to future cooperation that comes from a suicide.
@@
 Although negative responses to suicide survivors are more often studied and reported, positive responses have also been found.
-Increased social support and changes to important relationships are often reported to follow suicide attempts with some indication that these effects may hold long term (Stengel, 1956).
+Increased social support and changes to important relationships have been reported to follow suicide attempts with some indication that these effects may hold long term (Stengel, 1956).
 For example, a study of 100 women who survived suicide attempts found that in 75 cases individuals gained identifiable benefits through the attempt, with 41 individuals benefiting from reconciliations with others (Lukianowicz, 1971).
@@
 add funding info somewhere
-update MTurk (Ed email links + mine)
 Find a place for the predictions and preregistration 
@@
 1,950 participants started the study by clicking the link to Qualtrics (1,213 American and 737 Indian).
-After removing participants who did not finish the survey, failed attention checks, or moved through the study at an unrealistc pace, our sample dropped to N = 1,240 (937 American and 303 Indian).
+After removing participants who did not finish the survey, failed attention checks, or moved through the study at an unrealistic pace, our sample dropped to N = 1,240 (937 American and 303 Indian).
 Basic summary statistics on the remaining N = 1,240 participants (Male = 759, Female = 479) can be found in table XX.
@@
 
-Power analyses prior to data collection showed that high proportions of participants scoring extremely high on belief or likelihood of helping at T1 would result in low power for this study's design, a problem which we appeared to largely avoid (see figure XX).
+Power analyses prior to data collection showed that high proportions of participants scoring extremely high on belief or likelihood of helping at T1 would result in low power for this study's design, a problem which we appeared to largely avoid (word better) (see figure XX).
 
@@
 
-As a whole, our predictions for the effect of signal cost on belief and likelihood of helping T2 were met, with costlier signals eliciting greater pro-signaler responses.
+As a whole, our predictions for the effect of signal cost on belief and likelihood of helping T2 were met, with costlier signals eliciting greater pro-signaler responses (reword).
 There was also support for an interaction between signal and T1Belief or T1Action, although the effect was not large (See figure 2).
@@
 To do this, we created four new variables: LowMood (T1 and T2) and Manipulative (T1 and T2).
-This was done by adding the dummy variables for whether a participant thought the signaler was depressed, distressed or sad for the LowMood variables and by adding the dummy variables for whether they thought the particpant was Devious or Jealous for the Manipulative variables.
-In all instances, 0 indicated a participant did not select the emotion, while 1 indicated selection.
+This was done by adding the dummy variables for whether a participant thought the signaler was depressed, distressed or sad for the LowMood variables and by adding the dummy variables for whether they thought the participant was Devious or Jealous for the Manipulative variables.
+For each original emotion variable, 0 indicated a participant did not select the emotion, while 1 indicated selection.
 
-We then plotted the mean change seen in the data in addition to the change seen in 500 bootstrap resamples (see figure 6).
+We then plotted the mean change in the LowMood and Manipulative variables seen in the data in addition to the change seen in 500 bootstrap resamples (see figure 6).
 
@@
 
-Although this study was not designed to examine whether the costs of signaling would be made up for by the increased support stemming from depression and suicide attempts directly, the results are encouraging (reword).
+Although this study was not designed to examine whether the costs of signaling would be made up for by the increased support stemming from depression and suicide attempts directly, the results are suggestive (reword?).
 In general, the costs required to honestly convey one's qualities should be expected to increase with the potential payoffs of deception (cite), with the vignettes in this study emphasizing the existence of private information and sizable conflicts of interest to increase the perceived risk of being taken advantage of.

### 2021-04-01 Paper.rmd
Added abstract (edited from 2020 AAPA poster)

@@
 ```
+
+# Abstract
+
+Major depression and suicide are generally viewed as pathological responses to stress that elicit aversive responses from others.
+Alternatively, depression and suicide attempts might be the result of adaptations for reliably signaling need and bargaining for increased support from reluctant others.
+To test this hypothesis, we examined responses to  emotional signals in a vignette study in which the existence of conflicts of interest and private information about one's need were emphasized in four scenarios involving claims of extreme need.
+Although the effect of signal type varied by vignette, costlier signals like depression and suicide attempts resulted in greater perceptions of need and increased likelihood of support compared to simple verbal requests and crying without further symptoms in our sample of 1,240 participants recruited from Amazon Mechanical Turk.
+Additionally, the effect of signal type on likelihood of support was largely mediated by the effect of signaling on believe in need as predicted.
+Our results suggest that depression and suicide attempts, apparent human universals, are a relatively successful way of signaling honest need and eliciting support, consistent with costly signaling explanations.
 

### 2021-04-01 Paper.rmd
added ecdf plot

--- 2021-04-01 Paper.rmd
@@
     'power_curve',
+    'power_curve2',
     'models',
@@
     'effectsPlots', 
+    'ecdf_plot',
     'plot_T1Belief_T1Action',
@@
     'plot_raw_actions',
+    'plot_raw_belief_action2d',
     'med1b',
@@
 # Introduction
-Since Durkheim’s pioneering effort to use quantitative social science to explain suicide (cite), anthropologists, psychologists, and sociologists have made varied attempts at explaining depression and suicide.
-Despite this effort and substantial investment by funding agencies, rates of depression and suicide attempts have remained largely unchanged over the last 100 years (confirm and cite), and there is still substantial uncertainty about why both are as common as they are (cite).
-Likely due to their high costs and the suffering they cause, the vast majority of these approaches have been built on the assumption that they are the result of internal dysfunction (cite examples).
+Since Durkheim’s pioneering effort to use quantitative social science to explain suicide, varied attempts by anthropologists, psychologists, and sociologists and substantial investment by funding agencies, rates of depression and suicide attempts have remained largely unchanged over the last 100 years (confirm and cite), and there is still substantial uncertainty about why both are as common as they are (cite).
+Due to their high costs, the vast majority of these approaches have been built on the assumption that they are the result of internal dysfunction (cite examples).
 However, a subset of anthropologists and evolutionary theorists have challenged this idea, suggesting that despite the subjective suffering they cause, they may function as a means to limit negative fitness outcomes in times of substantial adversity (Firth + others).
@@
 Compared to non-depressed individuals, those with depression tend to report at least twice as many instances of negative events in both community and clinical samples (Mazure, 1998) and more negative events than those with schizophrenia and bipolar depression across a wide range of studies (Paykel, 1994).
-In instances where depression is preceded by negative events, the onset of depression tends to be rapid, often occurring within one month of the event (Kendler et al., 1999 [double check and find others]).
+In instances where this is the case, the onset of depression tends to be rapid, often occurring within one month of the event (Kendler et al., 1999 [double check and find others]).
 
@@
 Support for this comes from the fact that the relationship between negative events and depression holds true when looking solely at events outside of one's control, which shows that the connection is unlikely to be driven solely by depressed individuals creating situations where negative events are likely to be common (Hammen, 2005; Kendler et al., 1999).
-In addition to this, twin studies have shown that one's history of negative events is still a strong predictor of major depression when controlling for genetic similarity and that part of the heritability of depression stems from the heritability of negative events, like divorce and family conflict (Kendler & Baker, 2007; Kendler et al., 1999).
+In addition to this, twin studies have shown that one's history of negative events is still a strong predictor when controlling for genetic similarity and that part of the heritability of depression stems from the heritability of negative events, like divorce and family conflict (Kendler & Baker, 2007; Kendler et al., 1999).
 
@@
 Suicide attempts also tend to co-occur with social adversity (Hagen et al., 2008 + cite and describe), with evidence of this existing cross-culturally.
-Grief over the loss of a loved one (Firth; Devries et al.
+Greif over the loss of a loved one (Firth; Devries et al.
 2011), bullying (Alavi et al., 2017; Butler et al., 2019; Ford et al., 2017; Wang et al., 2020), and instances of social transgression (Firth; Malinowski; Syme and Hagen 2018; find Western citation to confirm) have all been reported to lead to suicidal behavior in both industrialized (confirm the transgression part) and traditional societies.
-Of the recorded instances of suicide attempts in the Human Relations Area Files (HRAF), 77.4% of attempts were found to be linked to times of social conflict, 88.7% were linked to fitness threats in general, and 84.9% were linked to situations in which attempters were powerless to resolve their situation alone (Syme et al., 2016).
-As with depression, assault is an particularly powerful risk factor for suicidal behavior based on multiple large-scale multi-country studies (Devries et al.
+As with depression, assault is a powerful risk factor for suicidal behavior, something which has been found in multiple large-scale multi-country studies (Devries et al.
 2011; Ellsberg et al.
-2008) and more localized examinations.
-For example, both sexual and non-sexual assault were also associated with more self-harm and suicidal behaviors among both indigenous Sami and majority Norwegian adolescents, with those who attempted suicides also reporting more than twice the number of negative life events than those who did not (Reigstad and Kvernmo 2017).
+2008).
+Both sexual and non-sexual assault were also associated with more self-harm and suicidal behaviors among both indigenous Sami and majority Norwegian adolescents, with those who attempted suicides reporting more than twice the number of negative life events than those who did not (Reigstad and Kvernmo 2017).
+The connection between social adversity and suicide is also seen in the Human Relations Area Files (HRAF), in which 77.4% of attempts were found to be linked to times of social conflict, 88.7% were linked to fitness threats in general, and 84.9% were linked to situations in which attempters were powerless to resolve their situation alone (Syme et al., 2016).
 
@@
 Beyond resulting in the cost differential that allows for costly signaling in the first place, the costs of depression and suicidal behavior may be particularly important in times of conflict or when the level of support needed to address one’s situation is substantial.
-Importantly, there are likely few forms of social adversity that do not come with conflict.
+Importantly, there are likely few forms of adversity that do not come with conflict.
 For example, breakups in both romantic and cooperative relationships are often preceded by conflict (Amato & Hohmann-Marriott, 2007), and surely involve conflict when one side wants reconciliation and the other does not.
@@
 In these instances, less costly signals like verbal requests, facial sadness, and crying are likely to be unreliable as their low costs can easily be made up for with increased social support, thereby favoring the use of costlier signals in those experiencing need they cannot resolve on their own.
+Importantly, the amount of conflict
 
@@
 This is possible due to the reduced investment in others that frequently accompanies depression or the threat to future cooperation that comes from a suicide.
-In these instances, depression and suicide attempts are suggested to function analogously to a labor strike, sending the message that one’s need is genuine and that if the target of the signal wanted to continue receiving benefits from the depressed, he or she would need to increase support towards the signaler.
+In these instances, depression is suggested to function analogously to a labor strike, sending the message that one’s need is genuine and that if the target of the signal wanted to continue receiving benefits from the depressed, he or she would need to increase support towards the signaler.
 
@@
 Beneficial social changes are also reported in traditional societies.
-Unlike many Western countries, where suicide is often viewed as pathological (Hidaka, 2012), members of traditional societies have been reported to view suicide attempts as cries for help rather than mental illness (Shostak, 1981).
+Unlike Western countries, where suicide is often viewed as pathological (Hidaka, 2012), members of traditional societies have been reported to view suicide attempts as cries for help rather than mental illness (Shostak, 1981).
 For example, attempts have been described as ways of escaping unwanted marriage arrangements, persistent abuse, or a lack of support in obtaining mates by those engaging in the behavior and observers (Gutierrez de Pineda & Muirden, 1948; Hilger, 1957; Karsten, 1935; Tessmann, 1930; Wilson, 1960), suggesting that help is at least occasionally provided or reliably expected.
@@
 Find a place for the predictions and preregistration 
-go back and emphasize conflict and PI in the methods (at least in the pilot studies portion)
-add abstract
-add conclusion
+go back and emohasize conflit and PI in the methods (at least in the pilot studies portion)
 
@@
 
-This study involved a between-subjects pretest-posttest design to examine how different emotional signals would influence (1) the degree participants believed a fictional character to be in need and (2) the likelihood they would provide help within a vignette study.
+This study involved a vignette study with between subjects pre-test/post-test design with one factor (signal) and 5 levels (verbal request, crying, crying with behavioral changes, depression, and suicide attempt), with the outcome of interest being how believe and likelihood of helping changed in response to a given signal.
+
+## Pilot Studies
+
+The first pilot study used a vignette study to examine how the presence of conflict, private information, and emotional signaling impacted the degree participants believed the signaler to be in need and provide support using an MTurk sample of 1,447 Americans.
+Of the signals, depression resulted in the most pro-signaler responses (reword), separating itself from the less costly signals when conflict and private information was present and substantially outperforming the schizophrenic break control.
+However, the suicide attempt condition was responded to relatively poorly, contrary to predictions.
+
+One potential explanation is that the initial scenario of a mother asking their sibling for help paying for their young daughter's heart surgery was not severe enough for a suicide attempt to be a functional signal, due to a lack of beleivability or due to its costs appearing manipulative.
+For this reason, we designed this study with more severe scenarios that were also associated with suicide attempts both ethnographically and clinically, including instances of sexual assasult, non-sexual assault, and thwarted marriage.
+
+add that we ask now ask same question twice? (interpretabilty)
+
+The second was posted on the samplesize subreddit with the goals of testing the beleivability of the new vignettes and how pro-signaler participants were at T1, with a power analysis with simulated data showing this would limit our power.
+In this small sample of 28, we saw no evidence that beleivabilty was a problem and no evidence that participants as a whole would be too pro-sister at T1.
 
@@
 
-Four vignettes were used in this study in which both the presence of conflicts of interest and the existence of private information about one's need were emphasized.
-Due to the expectation that depression and suicide are likely too costly of signals for relatively minor instances of need, we designed this study to involve severe scenarios associated with suicide attempts both ethnographically and clinically (i.e, sexual assault (cite), non-sexual assault (cite), and thwarted marriage (cite)).
-
-Participants in the US sample were randomly assigned to either the "basketball coach," "romantic partner," or "brother-in-law" vignettes.
-In the "basketball coach" scenario, the star player on a university basketball team comes to the participant (who is asked to imagine themselves as the athletic director at a university) and claims she was sexually assaulted by the coach.
+Four vignettes were used in this study, with participants in the US sample being randomly assigned to either the "basketball coach," "romantic partner," or "brother-in-law" vignettes.
+In the "basketball coach" scenario, the star player on a unversity basketball team comes to the participant (who is asked to imagine themselves as the athletic director at a university) and claims she was sexually assaulted by the coach.
 However, there are indications the player might be lying to get more playing time.
 
-The "brother-in-law" vignette involved participants imagining that they let their sister, brother-in-law, and niece move in with the participant and their 15-year-old daughter after their sister's family lost their house in a fire.
-During this time, the participant's daughter becomes jealous of her cousin before accusing her uncle of sexually assaulting her.
+The "brother-in-law" vignette involved participants imagining that they let their sister, brother-in-law, and niece move in with the participant and an imagined 15-year-old daughter after they lost their house in a fire.
+During this time, the participant's daughter becomes jealous of your niece before accusing her uncle of sexually assaulting her.
 
-The "romantic partner" vignette had participants imagine that they found a highly desirable partner after years of being single.
+The "romantic partner" vignette hard participants imagine that they found the best partner they have ever had after years of being single.
 However, their 13-year-old daughter, who has a history of trying to get in the way of their relationships is clearly not happy with this.
-After a period of sustained conflict, she accuses the romantic partner of physically assaulting her but cannot produce any evidence.
+At one point, she accuses the romantic partner of physically assaulting her but cannot produce any evidence.
 
-Those in the Indian sample only saw the "thwarted marriage vignette." In this scenario, the participant and their family is described as trying to arrange a dowry for their older daughter so she can marry the man she loves.
-After the man's family demands more money, the participant's family tries to find a second man, who the older daughter claims to find unattractive.
-Due to the younger daughter in the story only being two years younger, any additional investment in the dowry will come at the younger daughter's expsense.
+Those in the Indian sample only saw the "thwarted marriage vignette." In this scenario, the participant and their family is trying to arrange a dowry for their older daughter so she can marry the man she loves.
+After his family demands more money, the participant's family tries to find another man, who the older daughter claims to find unattractive.
+However, it is unclear how unattractive he is and any additional investment in the dowry will come at the expense of the younger daughter.
 
-The full vignettes are available in the SI.
+The full vignettes are available in the supplementary information.
 
@@
 
-As the amount of crying in those with depression is moderately associated with depression severity [@VingerhoetsEtAl2016] (check this.
-IIRC he might have a more recent paper saying it's not associated with depression as people tend to think) and depression is a major risk factor for suicide [@BostwickPankratz2000; @Kessler2012], each signal was designed to build off of the less costly signals so that each signal contained elements of any signal it was costlier than.
-The full text for the signals are availible in the SI.
+As the amount of crying in those with depression is moderately associated with depression severity [@VingerhoetsEtAl2016] and depression is a major risk factor for suicide [@BostwickPankratz2000; @Kessler2012], each signal was designed to build off of the less costly signals so that each signal contained elements of any signal it was costlier than.
 
@@
 Participants for this study were recruited from Amazon Mechanical Turk, a crowdsourcing platform that allows for the creation of Human Intelligence Tasks (HITs) that workers can complete for pay.
-As Amazon provides the infrastructure, it allows for a relatively low-cost way of collecting data for academic research at the cost of the data not being representative of any real population (Thomas and Clifford 2017).
-Despite this limitation, it is more diverse than most convenience samples [@KennedyEtAl2018(2020 now); @DworkinEtAl2016; (Thomas and Clifford 2017)], with turkers in the US mainly differing in being younger, more educated, and lower income than the greater U.S.
-population [@RossEtAl2010]; Boas et al.
-2018).
-Indian samples are also likely to be younger and more educated than the general population but differ from US samples in that they are less diverse, have higher incomes relative to other Indians, and are more likely to come from regions with good internet access (Boas et al.
-2018)
+As Amazon provides the infrastructure, it allows for a relatively low-cost way of collecting data for academic research at the cost of the data not being representative of any real population.
+Despite this limitation, it is more diverse than most convenience samples [@KennedyEtAl2018; @DworkinEtAl2016], with turkers in the U.S.
+mainly differing in being younger, more educated, lower income, and more female biased than the greater U.S.
+population [@RossEtAl2010].
 
-Overall, the quality of data provided by MTurk workers tends to resemble that of university sample pools[@NeckaEtAl2016, Robinson et al.
-2019], with there being some indication that it might outperform university samples due to its previously mentioned diversity (Thomas and Clifford 2017) or the overall attentiveness of turkers [@HauserSchwarz2016].
-For this reason, concerns about data quality come primarily from the threat of bot use or respondents faking their location to take surveys in a language they do not understand well, with there being little evidence of the former [@KennedyEtAl2018] and the risk of the latter able to be minimized through well designed attention checks, timed responses, or general study design (Aguinis et al.
-2020; Huang et al.
-2015; Kennedy et al.
-2020; Thomas and Clifford 2017).
+Overall, the quality of data provided by MTurk workers tends to resemble that of university sample pools, with there being some indication that it might outperform university samples in a few important areas.
+This is seen in that while both MTurk workers and university students engage in problematic behaviors that might lessen data quality to similar amounts [@NeckaEtAl2016], workers on MTurk have been shown to be more attentive than samples of university students [@HauserSchwarz2016].
+For this reason, concerns about data quality come primarily from potential bot use and respondents faking their location to take surveys in a language they do not understand well, with the former concern being largely unfounded and the latter able to be corrected for with the tools used in this study [@KennedyEtAl2018]
 
@@
 
-To reduce the risk of low quality responses, we used a variety of attention checks, which we clearly labeled in an attempt to avoid demand characteristics.
+To ensure participants were paying attention, we used a variety of attention checks, which we clearly labeled in an attempt to avoid demand characteristics.
 The first was shown immediately after the consent form and provided participants with a random word and asked them to enter the vowels in the order in which they are found in the word.
@@
 
-We also filtered out those who read the vignette faster than one-third the time it took MG to read it as fast as possible without concern for comprehension.
-This occured immediately after participants finished the vignette.
+We also filtered out those who read the vignette faster than one-third the time it took MG to read it as fast as possible without concern for comprehension immediately after the vignette.
 
-Informed consent was given by proceeding with the study after reading the consent form, and all participants who passed the attention checks were paid $1 for their time, with us estimating it would take 4-8 minutes before data collection.
-This study was certified exempt by the Washington State University Human Research Protection Program (certification number: 18528-001).
+Informed consent was given by proceeding with the study after reading the consent form, and all participants who passed the attention checks were paid $1 for their time. (mention time here)
 
@@
 After accepting the HIT on MTurk, every participant took the survey using Qualtrics.
-In every instance, the elements of the survey were laid out in the following order: 1) the consent form, 2) the vowel attention check, 3) the main body of the vignette, 3) the pre-test baseline measures (T1), 4) the story content attention check, 5)  the signal portion of the vignette, 7) the post-test outcome measures (T2-T3), 8) an attention check that did not filter out participants (T4), 9) a set of demographic questions, and 10) an open feedback prompt.
+In every instance, the elements of the survey were laid out in the following order: 1) the consent form, 2) the vowel attention check, 3) the main body of the vignette, 3) the pre-test baseline measures (T1), 4) the story content attention check, 5)  the signal portion of the vignette, 7) the post-test outcome measures (T2), 8) an attention check that did not filter out participants, 9) a set of demographic questions, and 10) an open feedback prompt.
 The full survey can be found in the SI.
@@
 
-In both samples, we recorded self-reports on how much participants believed the signaler to be telling the truth (T1Belief) and the likelihood of them helping the signaler as requested (T1Action).
-With the thwarted marriage vignette we also asked how they would split the money they had saved for the dowry between their daughters (T1Divide).
+In both samples, we recorded self-reports on how much participants believed the signaler to be telling the truth (BeliefT1) and the likelihood of them helping the signaler as requestedc (ActionT1).
+With the thwarted marriage vignette we also asked how they would split the money they had saved for the dowry between their daughters (Divide T1).
 In every instance, the order of the questions was randomized to avoid order effects [@KrosnickAlwin1987].
@@
 Responses were recorded with sliders due to the fact they allow for finer grained changes than categorical scales [@KlimekEtAl2017].
-In every instance the position started at the left due to findings that people may be less likely to move the slider from central starting positions (cite and word better).
-For the exact wording of the question and the labels on the sliders, see table 1.
+In every instance the position started at the left due to findings that people may be less likely to move the slider when it starts in the center (cite and word better).
+For the exact wording of the question and the ends of each continuum, see table 1.
 
@@
 
-As both a validity check and a way to understand the degree participants would be willing to help if they believed the participant completely, we presented participants with strong evidence that the claims were true (T3Action).
-In the US sample, this involved video evidence of the event in question occurring or a similar event after the fact.
+As both a validity check and a way to understand the degree participants would be willing to help if they believed the participant completely, we presented participants with strong evidence that the claims were true (Action T3).
+In the US sample, this involved video evidence of the event in question occuring or a similar event after the fact.
 With the thwarted marriage vignette, this involved the participant seeing the man their daughter wants to marry trash talk their daughter and their family.
-As a final attention check, we presented participants with the T3Action question but included instructions to ignore this and drag the slider all the way to the left (T4AttentionCheck).
+As a final attention check, we presented participants with the Action T3 question but included instructions to ignore this and drag the slider all the way to the left (T4AttentionCheck).
 We did not exclude anyone from the study for failing this nor did we withhold payment.
@@
 
-1,950 participants started the study by clicking the link to Qualtrics (1,213 American and 737 Indian).
-After removing participants who did not finish the survey, failed attention checks, or moved through the study at an unrealistc pace, our sample dropped to N = 1,240 (937 American and 303 Indian).
-Basic summary statistics on the remaining N = 1,240 participants (Male = 759, Female = 479) can be found in table XX.
-
 ## Summary statistics
@@
 
-## Distributions of beliefs and actions at time 1
-
-Power analyses prior to data collection showed that high proportions of participants scoring extremely high on belief or likelihood of helping at T1 would result in low power for this study's design, a problem which we appeared to largely avoid (see figure XX).
-
-Although not a part of our pre-registered predictions, both T1Belief and T1Action were highly correlated across the four vignettes (enter correlation coefficients), consistent with help being worth providing if the signaler's claims were true (see figure XX).
+## Distributions of beliefs and actions at Time 1
 
@@
 
-As a whole, our predictions for the effect of signal cost on belief and likelihood of helping T2 were met, with costlier signals eliciting greater pro-signaler responses.
-There was also support for an interaction between signal and T1Belief or T1Action, although the effect was not large (See figure 2).
-However, the effect of signal cost varied by vignette, with signal type having the greatest effect in the "basketball coach" and "brother-in-law" vignettes.
-When ordered according to cost, the greatest jump in support tended to occur between crying and mild-depression, with the next largest jump tending to occur between depression and suicide attempt.
-Overall, there was little difference between the effect of mild depression and the effect of depression.
-
 ```{r beliefeffect, fig.width=8, fig.height=8, fig.cap="The effect of the signals on T2 Belief (top) and Action (bottom) controlling for T1 values of Belief and Action, respectively, with an interaction between T1 values and the signal.
-Estimated using generalized linear regression models with the quasibinomial family."}
+Fit using generalized linear regression models with the quasibinomial family."}
 (effectsPlots$m1bplot + theme(axis.text.x = element_blank()))/effectsPlots$m3bplot + plot_layout(ncol = 1) & theme(plot.margin = unit(c(0,0,0,0), units = 'mm'))
@@
 Effects computed with T1 values set to their median value (T1Belief=", median(d$T1Belief, na.rm=T), ", T1Action=", median(d$T1Action, na.rm=T), ").
-Estimated using generalized linear regression models with the quasibinomial family.")}
+Fit using generalized linear regression models with the quasibinomial family.")}
 (effectsPlots$m2plot + theme(axis.text.x = element_blank()))/effectsPlots$m4plot + plot_layout(ncol = 1) & theme(plot.margin = unit(c(0,0,0,0), units = 'mm'))
+```
+
+```{r ecdf, fig.width=11, fig.height=6, fig.cap="Empirical cummulative distribution functions for Time 2 Belief (top) and Action (bottom) compared to their Time 1 baseline values (red), by signal and vignette.
+Dots indicate median values of Belief and Action, by signal and vignette."}
+ecdf_plot
 ```
@@
 See Figure \@ref(fig:mediation).
-The total effect of the *Suicide attempt* signal (treatment) vs.
-*Verbal request* (control) on the likelihood of *Action* was to increase it by `r 100*signif(med4b$tau.coef, 3)` points from T1 to T2.
-Of this increase, `r 100*signif(med4b$n.avg, 2)`% was mediated by the increased *Belief* that the victim was telling the truth (Check if med4 or med4b is correct; they look identical to me).
 
@@
 
-We also examined the effect of signaling on how participants perceived the signaler's emotional state.
-To do this, we created four new variables: LowMood (T1 and T2) and Manipulative (T1 and T2).
-This was done by adding the dummy variables for whether a participant thought the signaler was depressed, distressed or sad for the LowMood variables and by adding the dummy variables for whether they thought the particpant was Devious or Jealous for the Manipulative variables.
-In all instances, 0 indicated a participant did not select the emotion, while 1 indicated selection.
-
-We then plotted the mean change seen in the data in addition to the change seen in 500 bootstrap resamples (see figure 6).
-
 ```{r emotionsplot, fig.width=10, fig.height=8, fig.cap="The effect of the signals on participants' inferred *manipulative* and *low mood* emotional states of the victim, from T1 (arrow base) to T2 (arrow head), in each of the four vignettes.
@@
 
-Consistent with costly signaling theory (is this a common enough prediction to say this?), costlier signals resulted in greater perceptions of need and increased the likelihood of participants helping the signaler than the less costly signals.
+Consistent with costly signaling theory, costlier signals resulted in greater perceptions of need and increased the likelihood of participants helping the signaler than the less costly signals.
 This effect was largest in the "brother-in-law" and "romantic partner" vignettes, both of which involved claims of assault against participants' imagined daughters.
@@
 One potential reason for this is the increase in symptoms from mild depression to depression was not costly enough to result in a large effect as the symptoms only differed in severity (e.g., grades dropping from As to Bs [mild depression] or Cs [depression]).
-Such small changes may be less impactful in vignette form than in real-life scenarios in which the effects of signaling may increase in severity and be prolonged over a lengthy period of time.
+Such small changes may be less impactful in vignette form than in real-life scenarios in which the effects of signaling may increase in severity and be prolonged over a lenghty period of time.
 
@@
 For this reason, too strong of a signal may be seen as manipulative or a cue of dysfunction, and therefore, be responded to aversively.
-However, belief in need and likelihood of help at T2 still remained high when it was high at T1, suggesting that this may not be a significant risk when one is in severe enough need.
+However, belief in need and likelihood of help at T2 still remained high when it was high at T1, suggesting that this may not be a significant risk when one is in severe enough need (want to bring in MA here.
+Is that a bad idea?).
 
@@
 
-Although this study was not designed to examine whether the costs of signaling would be made up for by the increased support stemming from depression and suicide attempts directly, the results are encouraging (reword).
+Although this study was not designed to examine whether the costs of signaling would be made up for by the increased support stemming from depression and suicide attempts directly, the results are encouraging.
 In general, the costs required to honestly convey one's qualities should be expected to increase with the potential payoffs of deception (cite), with the vignettes in this study emphasizing the existence of private information and sizable conflicts of interest to increase the perceived risk of being taken advantage of.
@@
 
-The main limitation of this study is its lack of ecological validity, something which had to be sacrificed for any experimental design involving depression and suicide attempts.
+The largest source of limitations of this study is its lack of ecological validity, something which had to be sacrificed for any experimental design involving depression and suicide attempts.
 It is almost certain that participants experienced this study differently than they would if the event actually happened to them.
-This may have biased results in a pro-signaler direction if the lack of meaningful costs made support feel less costly or if the likely inability of participants to imagine themselves in an anonymous scenario (cite your paper on this) led them to take an opportunity to signal generosity cheaply.
-It may have also biased participants against helping if they could not fully imagine the characters in the story as kin or important cooperative partners, while the survey's short duration may have weakened the strength of the costlier signals as bargaining tools.
-However, the fact that the relationships among signal cost, belief in need, and likelihood of providing support all largely fit existing theory (narrow and broad) indicates that participants paid attention to the relevant details and responded in ways that suggest some degree of external validity.
-For this reason, the benefits of addressing causal relationships that came through our experimental vignette approach likely outweighed the costs.
+This may have biased results in a pro-signaler direction due to the lack of meaningful costs making support feel less costly or through the likely inability of participants to imagine themselves in an anonymous scenario (cite your paper on this) leading them to take an opportunity to signal generosity cheaply.
+It may have also biased participants against helping if they could not fully imagine the characters in the story as kin or important cooperative partners, while the survey's short duration may have weakened the strength of the bargaining of the costlier signals.
+However, both the findings of a main effect of signal and the effect of signal type on likelihood of support was largely mediated by change in belief suggest that participants were paying attention to the theoretically relevant details in ways that influenced their behavior.
 
@@
 Compared to the US sample, far more participants were filtered out by our attention checks, something which could be consistent with botting, unfamiliarity with English, or low effort responses.
-Assuming this corresponded with lower-quality responses among those who passed the attention checks, the differences seen among those in the thwarted marriage vignette may simply be due to added noise rather than differences in the scenarios or the effectiveness of the signals among Indians compared to Americans.
+Assuming this corresponded with more low-quality responses among those who passed the attention checks, the differences seen among those in the thwarted marriage vignette may simply be due to added noise rather than differences in the scenarios or the effectiveness of the signals among Indians compared to Americans.
 
@@
 
-We estimated power using our pilot study data by comparing the effect of the *Depression* signal vs.
+```{r}
+pwr80_90 <- 
+  power_curve %>% 
+  group_by(Base) %>% 
+  summarise(
+    pwr80 = min(sample_size[power>=.8]), 
+    pwr90 = min(sample_size[power>=.9])
+  )
+```
+
+We estimated power using our pilot study data to compared the effect of the *Depression* signal vs.
 the *Verbal request* signal on *Belief* (that the sister needed the money) at T2 controlling for *Belief* at T1 in a linear regression model.
-Specifically, we resampled the pilot data with replacement with sample sizes ranging from N=20 to N=100, fit the linear regression model, and extracted the p-value for the signal coefficient, repeating this 1000 times for each sample size.
+Specifically, we resampled the pilot data with replacement, fit the linear regression model, and extracted the p-value for the signal coefficient, repeating this 2000 times for each sample size ranging from N=20 to N=200.
 Power was computed as the proportion of p-values < 0.05.
-Power was about 80% for a sample size of about 35, and was about 90% for a sample size of about 45.
+Power was about 80% for a sample size of about `r pwr80_90[2,2]`, and was about 90% for a sample size of about `r pwr80_90[2,3]`.
+We then repeated this entire procedure to compare *Depression* to a *Control* condition that was meant to not include any signaling (but which we realized, post hoc, did include a verbal request).
+Power was about 80% for a sample size of about `r pwr80_90[1,2]`, and was about 90% for a sample size of about `r pwr80_90[1,3]`.
+See Figure \@ref(fig:power).
 
-```{r power}
-  ggplot(power_curve, aes(sample_size, power)) +
+```{r power, fig.cap="Power curve for between-subjects effect of Depression vs. Verbal request signal on T2 Belief, controlling for T1 Belief."}
+  ggplot(power_curve, aes(sample_size, power, color=Base)) +
     geom_line() +
-    labs(x = '\n Sample size (2 conditions)', y = 'Power\n') +
+    labs(x = '\n Sample size', y = 'Power\n') +
     theme_minimal(15)
+```
+
+<!-- Second, for participants in the *Depression* condition only, we compared their T2 Belief to their T1 Belief using a paired t-test (in the full pilot data, *Depression* increased belief by about 8 points on a 100 point scale).
+We again resampled our pilot data 2000 times for each sample size from N=20 to N=200.
+Power was about 80% for a sample size of 125, and about 90% for a sample size of 175.
+See Figure \@ref(fig:power2).
+-->
+
+```{r power2, fig.cap="Power curve for within-subjects effect of Depression signal on T2 Belief relative to T1 Belief."}
+  # ggplot(power_curve2, aes(sample_size, power)) +
+  #   geom_line() +
+  #   labs(x = '\n Sample size', y = 'Power\n') +
+  #   theme_minimal(15)
 ```
@@
 
-## Distributions of T2 Belief and Action by signal and vignette
+<!-- ## Distributions of T2 Belief and Action by signal and vignette -->
 
 ```{r distbelief, fig.width=10, fig.height=10, fig.cap="Histograms of T2 Belief by signal and vignette."}
-ggplot(d, aes(x = T2Belief, fill=signal)) +
-  geom_histogram(colour='grey') +
-  scale_x_continuous(breaks = c(0, 0.5, 1)) +
-  facet_grid(vignette~signal) +
-  guides(fill='none') +
-  xlab('\n T2 Belief') +
-  theme_minimal(15) + 
-  theme(strip.text.y = element_text(angle=0, hjust=0))
+
+# h <- hist(d$T2Belief, breaks = "FD", plot = FALSE)
+# 
+# ggplot(d, aes(x = T2Belief, fill=signal)) +
+#   geom_histogram(colour='grey', breaks = h$breaks) +
+#   scale_x_continuous(breaks = c(0, 0.5, 1)) +
+#   facet_grid(signal~vignette, as.table = F) +
+#   guides(fill='none') +
+#   xlab('\n T2 Belief') +
+#   theme_minimal(15) +
+#   theme(strip.text.y = element_text(angle=0, hjust=0))
 ```
@@
 ```{r distaction, fig.width=10, fig.height=10, fig.cap="Histograms of T2 Action by signal and vignette."}
-ggplot(d, aes(x = T2Action, fill=signal)) +
-  geom_histogram(colour='grey') +
-  scale_x_continuous(breaks = c(0, 0.5, 1)) +
-  facet_grid(vignette~signal) +
-  guides(fill='none') +  
-  xlab('\n T2 Action') +
-  theme_minimal(15) + 
-  theme(strip.text.y = element_text(angle=0, hjust=0))
+
+# h <- hist(d$T2Action, breaks = "FD", plot = FALSE)
+# 
+# ggplot(d, aes(x = T2Action, fill=signal)) +
+#   geom_histogram(colour='grey', breaks=h$breaks) +
+#   scale_x_continuous(breaks = c(0, 0.5, 1)) +
+#   facet_grid(signal~vignette, as.table = F) +
+#   guides(fill='none') +  
+#   xlab('\n T2 Action') +
+#   theme_minimal(15) + 
+#   theme(strip.text.y = element_text(angle=0, hjust=0))
 ```
@@
 ```{r rawbeliefs, fig.width=10, fig.height=10, fig.cap="Change in beliefs from T1 to T2 for participants in each condition. Each grey line is one participant. Red lines are the mean change."}
-plot_raw_beliefs
+# plot_raw_beliefs
 ```
@@
 ```{r rawactions, fig.width=10, fig.height=10, fig.cap="Change in actions from T1 to T2 for participants in each condition. Each grey line is one participant. Red lines are the mean change."}
-plot_raw_actions
+# plot_raw_actions
+```
+
+```{r rawbeliefactions2d, fig.width=10, fig.height=10, fig.cap="Change in beliefs and actions from T1 (arrow base) to T2 arrow head) for participants in each condition.
+Each grey arrow is one participant.
+Red arrows are the mean change."}
+plot_raw_belief_action2d
 ```

### 2021-04-01 _targets.R

@@ -7,7 +7,7 @@ source("R/functions.R")
 
 # Set target-specific options such as packages.
 tar_option_set(
-  packages = c("signalingdata2018", "signaling2020data", "car", "hagenutils", "visreg", "effects", "glmmboot", "broom", "mediation", "gglm", "gt", "ggforce", "dplyr", "tidyr", "purrr", "ggplot2", "forcats", "stringr"),
+  packages = c("signalingdata2018", "signaling2020data", "ks", "car", "hagenutils", "visreg", "effects", "glmmboot", "broom", "mediation", "gglm", "gt", "ggforce", "dplyr", "tidyr", "purrr", "ggplot2", "patchwork", "forcats", "stringr"),
   imports = c("signalingdata2018", "signaling2020data")
   )
 
@@ -225,6 +225,33 @@ tar_target(
     T1Belief_Action_dist(d)
   ),
 
+
+# ECDF plot ---------------------------------------------------------------
+
+  tar_target(
+    ecdf_plot,
+    plot_ecdf(d)
+  ),
+
+# 2D densities ------------------------------------------------------------
+
+  tar_target(
+    d_density2d,
+    density2d(d)
+  ),
+
+  tar_target(
+    densityplot,
+    plot_densities(d_density2d),
+    format = "file"
+  ),
+
+  tar_target(
+    ggdensityplot,
+    ggplot_densities(d_density2d),
+    format = "file"
+  ),
+
 # Emotion plots -----------------------------------------------------------
 
   tar_target(
@@ -259,6 +286,10 @@ tar_target(
     plot_raw_data(d, 'Action')
   ),
 
+  tar_target(
+    plot_raw_belief_action2d,
+    plot_raw_data2d(d)
+  ),
 
 # Effect sizes ------------------------------------------------------------
 

### 2021-04-01 Paper.rmd

--- 2021-04-01 Paper.rmd
@@
 
-## Distributions of beliefs and actions at time 1
+## Distributions of beliefs and actions at Time 1
 
@@
 ```{r beliefeffect, fig.width=8, fig.height=8, fig.cap="The effect of the signals on T2 Belief (top) and Action (bottom) controlling for T1 values of Belief and Action, respectively, with an interaction between T1 values and the signal.
-Estimated using generalized linear regression models with the quasibinomial family."}
+Fit using generalized linear regression models with the quasibinomial family."}
 (effectsPlots$m1bplot + theme(axis.text.x = element_blank()))/effectsPlots$m3bplot + plot_layout(ncol = 1) & theme(plot.margin = unit(c(0,0,0,0), units = 'mm'))

### 2021-04-01 Paper.rmd
Started to work on the intro.

@@
 # Introduction
-Since Durkheim’s pioneering effort to use quantitative social science to explain suicide (cite), anthropologists, psychologists, and sociologists have made varied attempts at better understanding depression and suicide.
-Despite this effort and substantial investment by funding agencies, rates of depression and suicide attempts have remained largely unchanged over the last 100 years (confirm and cite), and there is still substantial uncertainty about why both are as common as they are (cite).
+
+Durkheim’s pioneering study of suicide [@durkheim1897] arguably launched sociology as a quantitative discipline.
+Sociological investigations of suicide flourished through much of the 20th century, but began to be supplanted by medical and public health approaches as the biomedical model of mental health took hold in the late 1970's and early 1980's [@wray2011; @syme2020].
+The biomedical model tends to frame suicide as an individiual-level problem, e.g., as one involving psychiatric disturbance, drug addiction, or severe stress [@wray2011].
+This theoretical approach has made little progress: Despite substantial investment by funding agencies, rates of suicide have remained largely unchanged over the last 100 years (confirm and cite).
+
+Early on, anthropologists also tackled the problem of suicide as manifested in the small, traditional socities in which they conducted their fieldwork.
+Suicide, they found, was commonly a form of protest, revenge, and/or appeal (e.g., Malinowski, 1985; Niehaus, 2012).
+Some ethnographers, such as Hezel (1987), conceptualized suicide as a form of anger, whereas others, such as Giddens (1964), conceptualized suicide as a form of social pressure.
+Counts (1980) emphasized the powerlessness of suicide victims.
+Common to almost all theoretical and empirical investigations of suicide is a focus on *completed* suicides, i.e., suicide deaths.
+@SymeEtAl2016, in contrast, argued that because the vast majority of suicidal behavior does not result in death, the proper focus should be on suicide ideation and suicide attempts, not deaths.
+
+Within anthropology, Raymond Firth was likely the first to put the focus on suicidality as a gamble to improve one's circumstances in the here and now.
+Based on observations that suicide attempts often followed social conflict or loss and varied substantially in their likelihood of death, he argued that a sizable subset of the suicide attempts among the Tikopia were not meant to end in death but instead were a means to elicit attention, status, and immediate reintegration into the community following negative events (Firth 1967[not original date]).
+Compared to suicide, however, anthropological explanations for depression are a much more recent occurrence (cite), despite frequent reports of depression or depression-like behavior in a wide range of societies (cite) and the potential for cross-cultural research to help understand depressive states (cite).
+
+and there is still substantial uncertainty about why both are as common as they are (cite).
 Likely due to  the suffering they cause, the vast majority of these approaches have been built on the assumption that they are the result of internal dysfunction (cite examples).
@@
 
-Within anthropology, Raymond Firth was likely the first to do this.
-Based on observations that suicide attempts often followed social conflict or loss and varied substantially in their likelihood of death, he argued that a sizable subset of the suicide attempts among the Tikopia were not meant to end in death but instead were a means to elicit attention, status, and immediate reintegration into the community following negative events (Firth 1967[not original date]).
-Compared to suicide, however, anthropological explanations for depression are a much more recent occurrence (cite), despite frequent reports of depression or depression-like behavior in a wide range of societies (cite) and the potential for cross-cultural research to help understand depressive states (cite).
+## Connection to Adversity
 
-## Connection to Adversity
 Likely the most reliable finding when it comes to depression and suicidal behavior is that most cases are closely tied to major negative life events (Hammen, 2005 + others; citations for suicide).

### 2021-04-01 Paper.rmd
Removed 1 note

--- 2021-04-01 Paper.rmd
@@
     'power_curve',
-    'power_curve2',
     'models',
@@
     'effectsPlots', 
-    'ecdf_plot',
     'plot_T1Belief_T1Action',
@@
     'plot_raw_actions',
-    'plot_raw_belief_action2d',
     'med1b',
@@
 go back and emphasize conflict and PI in the methods (at least in the pilot studies portion)
-add abstract
 add conclusion
@@
 
-## Distributions of beliefs and actions at Time 1
+## Distributions of beliefs and actions at time 1
 
@@
 ```{r beliefeffect, fig.width=8, fig.height=8, fig.cap="The effect of the signals on T2 Belief (top) and Action (bottom) controlling for T1 values of Belief and Action, respectively, with an interaction between T1 values and the signal.
-Fit using generalized linear regression models with the quasibinomial family."}
+Estimated using generalized linear regression models with the quasibinomial family."}
 (effectsPlots$m1bplot + theme(axis.text.x = element_blank()))/effectsPlots$m3bplot + plot_layout(ncol = 1) & theme(plot.margin = unit(c(0,0,0,0), units = 'mm'))
@@
 Effects computed with T1 values set to their median value (T1Belief=", median(d$T1Belief, na.rm=T), ", T1Action=", median(d$T1Action, na.rm=T), ").
-Fit using generalized linear regression models with the quasibinomial family.")}
+Estimated using generalized linear regression models with the quasibinomial family.")}
 (effectsPlots$m2plot + theme(axis.text.x = element_blank()))/effectsPlots$m4plot + plot_layout(ncol = 1) & theme(plot.margin = unit(c(0,0,0,0), units = 'mm'))
-```
-
-```{r ecdf, fig.width=11, fig.height=6, fig.cap="Empirical cummulative distribution functions for Time 2 Belief (top) and Action (bottom) compared to their Time 1 baseline values (red), by signal and vignette.
-Dots indicate median values of Belief and Action, by signal and vignette."}
-ecdf_plot
 ```
@@
 
-```{r}
-pwr80_90 <- 
-  power_curve %>% 
-  group_by(Base) %>% 
-  summarise(
-    pwr80 = min(sample_size[power>=.8]), 
-    pwr90 = min(sample_size[power>=.9])
-  )
-```
+We estimated power using our pilot study data by comparing the effect of the *Depression* signal vs.
+the *Verbal request* signal on *Belief* (that the sister needed the money) at T2 controlling for *Belief* at T1 in a linear regression model.
+Specifically, we resampled the pilot data with replacement with sample sizes ranging from N=20 to N=100, fit the linear regression model, and extracted the p-value for the signal coefficient, repeating this 1000 times for each sample size.
+Power was computed as the proportion of p-values < 0.05.
+Power was about 80% for a sample size of about 35, and was about 90% for a sample size of about 45.
 
-We estimated power using our pilot study data to compared the effect of the *Depression* signal vs.
-the *Verbal request* signal on *Belief* (that the sister needed the money) at T2 controlling for *Belief* at T1 in a linear regression model.
-Specifically, we resampled the pilot data with replacement, fit the linear regression model, and extracted the p-value for the signal coefficient, repeating this 2000 times for each sample size ranging from N=20 to N=200.
-Power was computed as the proportion of p-values < 0.05.
-Power was about 80% for a sample size of about `r pwr80_90[2,2]`, and was about 90% for a sample size of about `r pwr80_90[2,3]`.
-We then repeated this entire procedure to compare *Depression* to a *Control* condition that was meant to not include any signaling (but which we realized, post hoc, did include a verbal request).
-Power was about 80% for a sample size of about `r pwr80_90[1,2]`, and was about 90% for a sample size of about `r pwr80_90[1,3]`.
-See Figure \@ref(fig:power).
-
-```{r power, fig.cap="Power curve for between-subjects effect of Depression vs. Verbal request signal on T2 Belief, controlling for T1 Belief."}
-  ggplot(power_curve, aes(sample_size, power, color=Base)) +
+```{r power}
+  ggplot(power_curve, aes(sample_size, power)) +
     geom_line() +
-    labs(x = '\n Sample size', y = 'Power\n') +
+    labs(x = '\n Sample size (2 conditions)', y = 'Power\n') +
     theme_minimal(15)
-```
-
-<!-- Second, for participants in the *Depression* condition only, we compared their T2 Belief to their T1 Belief using a paired t-test (in the full pilot data, *Depression* increased belief by about 8 points on a 100 point scale).
-We again resampled our pilot data 2000 times for each sample size from N=20 to N=200.
-Power was about 80% for a sample size of 125, and about 90% for a sample size of 175.
-See Figure \@ref(fig:power2).
--->
-
-```{r power2, fig.cap="Power curve for within-subjects effect of Depression signal on T2 Belief relative to T1 Belief."}
-  # ggplot(power_curve2, aes(sample_size, power)) +
-  #   geom_line() +
-  #   labs(x = '\n Sample size', y = 'Power\n') +
-  #   theme_minimal(15)
 ```
@@
 
-<!-- ## Distributions of T2 Belief and Action by signal and vignette -->
+## Distributions of T2 Belief and Action by signal and vignette
 
 ```{r distbelief, fig.width=10, fig.height=10, fig.cap="Histograms of T2 Belief by signal and vignette."}
-
-# h <- hist(d$T2Belief, breaks = "FD", plot = FALSE)
-# 
-# ggplot(d, aes(x = T2Belief, fill=signal)) +
-#   geom_histogram(colour='grey', breaks = h$breaks) +
-#   scale_x_continuous(breaks = c(0, 0.5, 1)) +
-#   facet_grid(signal~vignette, as.table = F) +
-#   guides(fill='none') +
-#   xlab('\n T2 Belief') +
-#   theme_minimal(15) +
-#   theme(strip.text.y = element_text(angle=0, hjust=0))
+ggplot(d, aes(x = T2Belief, fill=signal)) +
+  geom_histogram(colour='grey') +
+  scale_x_continuous(breaks = c(0, 0.5, 1)) +
+  facet_grid(vignette~signal) +
+  guides(fill='none') +
+  xlab('\n T2 Belief') +
+  theme_minimal(15) + 
+  theme(strip.text.y = element_text(angle=0, hjust=0))
 ```
@@
 ```{r distaction, fig.width=10, fig.height=10, fig.cap="Histograms of T2 Action by signal and vignette."}
-
-# h <- hist(d$T2Action, breaks = "FD", plot = FALSE)
-# 
-# ggplot(d, aes(x = T2Action, fill=signal)) +
-#   geom_histogram(colour='grey', breaks=h$breaks) +
-#   scale_x_continuous(breaks = c(0, 0.5, 1)) +
-#   facet_grid(signal~vignette, as.table = F) +
-#   guides(fill='none') +  
-#   xlab('\n T2 Action') +
-#   theme_minimal(15) + 
-#   theme(strip.text.y = element_text(angle=0, hjust=0))
+ggplot(d, aes(x = T2Action, fill=signal)) +
+  geom_histogram(colour='grey') +
+  scale_x_continuous(breaks = c(0, 0.5, 1)) +
+  facet_grid(vignette~signal) +
+  guides(fill='none') +  
+  xlab('\n T2 Action') +
+  theme_minimal(15) + 
+  theme(strip.text.y = element_text(angle=0, hjust=0))
 ```
@@
   # facet_wrap(~Outcome, ncol=1) +
-  labs(x="\nCohen's d (95% CI)", y=NULL) +
+  labs(x="\nCohn's d (95% CI)", y=NULL) +
   theme_minimal(15) +
@@
 ```{r rawbeliefs, fig.width=10, fig.height=10, fig.cap="Change in beliefs from T1 to T2 for participants in each condition. Each grey line is one participant. Red lines are the mean change."}
-# plot_raw_beliefs
+plot_raw_beliefs
 ```
@@
 ```{r rawactions, fig.width=10, fig.height=10, fig.cap="Change in actions from T1 to T2 for participants in each condition. Each grey line is one participant. Red lines are the mean change."}
-# plot_raw_actions
-```
-
-```{r rawbeliefactions2d, fig.width=10, fig.height=10, fig.cap="Change in beliefs and actions from T1 (arrow base) to T2 arrow head) for participants in each condition.
-Each grey arrow is one participant.
-Red arrows are the mean change."}
-plot_raw_belief_action2d
+plot_raw_actions
 ```

### 2021-04-02 Paper.rmd
added second depression option

@@
 Based on observations that suicide attempts often followed social conflict or loss and varied substantially in their likelihood of death, he argued that a sizable subset of the suicide attempts among the Tikopia were not meant to end in death but instead were a means to elicit attention, status, and immediate reintegration into the community following negative events (Firth 1967[not original date]).
-Compared to suicide, however, anthropological explanations for depression are a much more recent occurrence (cite), despite frequent reports of depression or depression-like behavior in a wide range of societies (cite) and the potential for cross-cultural research to help understand depressive states (cite).
+Compared to suicide, however, anthropological explanations for depression are a much more recent occurrence (cite examples), despite frequent reports of depression or depression-like behavior in a wide range of societies (cite) and the potential for cross-cultural research to help understand depressive states (cite).
+
+Alternative depression idea:
+- move Firth up before Syme et al. 2016 and tweak slighlty or reword Firth and put behind Syme in the same paragraph
+- delete the previous depression stuff
+- then follow with this
+As with suicide, research on depression has been dominated by biomedical approaches of limited success.
+However, evolutionary and anthropological explanations for low mood have become more common.
+In general, these approaches see sadness and minor depression as ways to motivate adaptive behavior changes in response to negative outcomes in one's environment (cite Nesse and others), mainly differing in how they view major depression.
+While some approaches present most forms of major depression as dysfunctional (inflammation and some of Nesse), others have extended the logic on the benefits of low mood and reduced behavior to more severe instances of sadness.
+Of the possible benefits, the ability of depression to help solve fitness-relevant in times of social conflict is the most emphasized, with depression being suggested to help by reallocating resources with the body for problem solving (cite ARH), reducing the costs of interacting with higher status individuals (cite), or serving as a means to both signal one's need and bargain for increased support (cite).
 
@@
 
-Likely the most reliable finding when it comes to depression and suicidal behavior is that most cases are closely tied to major negative life events (Hammen, 2005 + others; citations for suicide).
+Likely the most reliable finding when it comes to depression and suicidal behavior is that most cases are closely tied to major negative life events (Hammen, 2005; Mazure, 1998; Devries et al.
+2011; Ellsberg et al.
+2008).
 Compared to non-depressed individuals, those with depression tend to report at least twice as many instances of negative events in both community and clinical samples (Mazure, 1998) and more negative events than those with schizophrenia and bipolar depression across a wide range of studies (Paykel, 1994).
@@
 
-Suicide attempts also tend to co-occur with social adversity (Hagen et al., 2008 + cite and describe), with evidence of this existing cross-culturally.
+Suicide attempts also tend to co-occur with social adversity.
 Grief over the loss of a loved one (Firth; Devries et al.
@@
 ## Depression and suicide attempts as both signals and bargaining tools
+
 One possible reason for the connection between depression and social adversity is that depression functions to elicit increased support from others in times when an individual cannot solve substantial fitness-relevant challenges on their own.

### 2021-04-02 Paper.rmd
Added m1 and m3 glmmboot models. Worked on methods section.

--- 2021-04-02 Paper.rmd
@@
     'd',
+    'signaling2018',
     'power_curve',
@@
     'plot_raw_belief_action2d',
+    'med_prereg',
+    'med1',
     'med1b',
     'med4',
+    'med4b',
+    'm1_boot',
+    'm3_boot',
     'm1b_boot',
@@
 go back and emphasize conflict and PI in the methods (at least in the pilot studies portion)
+add abstract
 add conclusion
@@
 
-https://osf.io/g3s6n
+We preregistered four OLS linear regression models and one mediation model (https://osf.io/g3s6n).
+The first two regression models tested the effects of our ordinal signal variable on Time 2 *Belief* and *Action*, controlling for T1 *Belief* and *Action*, respectively (a pre-test/post-test design):
+
+`r extract_eq(models_prereg$Model$m1, intercept='beta', wrap=T)`
+`r extract_eq(models_prereg$Model$m3, intercept='beta', wrap=T)`
+
+The second two models added interaction terms between signal and T1 *Belief* and *Action*, with the rationale that the signals might have reduced effect for individuals who indicate high levels of belief and helping at baseline:
+
+`r extract_eq(models_prereg$Model$m1b, intercept='beta', wrap=T)`
+`r extract_eq(models_prereg$Model$m3b, intercept='beta', wrap=T)`
+
+The mediation model is in Figure \@ref(fig:medmodel):
+
+```{r medmodel, fig.cap="Possible causal effects of the signal on helping behavior.
+A credible signal of need increases belief that the victim is telling the truth and needs help, which increase the likelihood of helping.
+The direct path from the signal to action represents other causal effects of the signal on observers, such as perceptions of the victim's emotional state (and other factors not measured in this study) that might alter observer behavior."}
+
+knitr::include_graphics('paths.svg')
+```
+
+Specifically, the mediation and outcome models, respectively, are:
+
+`r extract_eq(med_prereg$model.m, intercept='beta', wrap=T)`
+`r extract_eq(med_prereg$model.y, intercept='beta', wrap=T)`
+
+For reasons we explain in the *Statistical methods* section, we report the OLS models in the Supplementary Information (SI), and in the Results section instead report conceptually equivalent generalized linear regression models (GLMs).
+
+## Power analysis
+
+```{r}
+pwr80_90 <- 
+  power_curve %>% 
+  group_by(Base) %>% 
+  summarise(
+    pwr80 = min(sample_size[power>=.8]), 
+    pwr90 = min(sample_size[power>=.9])
+  )
+```
+
+The current study is a refinement of a pilot study (N=`r nrow(signalingdata2018)`) with very similar signals and outcomes.
+We used these pilot data to estimate the sample sizes needed to detect an effect of the *Depression* vs.
+*Verbal request* signal (two conditions) on *Belief* in the victim's need.
+Power was about 80% for a sample size of about `r pwr80_90[[2,2]]`, and was about 90% for a sample size of about `r pwr80_90[[2,3]]`.
+We also estimated the sample size needed to detect an effect of *Depression* vs.
+a *Control* condition that was meant to not include any signaling (but which we realized, post hoc, did include a verbal request).
+Power was about 80% for a sample size of about `r pwr80_90[[1,2]]`, and was about 90% for a sample size of about `r pwr80_90[[1,3]]`.
+See Figure \@ref(fig:power).
+Given our $1500 USD budget, we aimed for a sample size of 125 for two conditions, and 1250 for all conditions in the study.
+For more details, see the SI and XX.
 
@@
 
-Overall, the quality of data provided by MTurk workers tends to resemble that of university sample pools[@NeckaEtAl2016, Robinson et al.
+Overall, the quality of data provided by MTurk workers tends to resemble that of university sample pools [@NeckaEtAl2016, Robinson et al.
 2019], with there being some indication that it might outperform university samples due to its previously mentioned diversity (Thomas and Clifford 2017) or the overall attentiveness of turkers [@HauserSchwarz2016].
@@
 
-## Confirmatory Analyses
+## Statistical analyses
 
-We used linear regression to analyze our results for the main effect of signal on belief in need and likelihood of help, controlling for baseline levels of belief in need and likelihood of help.
-(Need more detail)
+Our pre-test and post-test measures, *T1 & T2 Belief* and *T1 & T2 Action*, were all measured on a 0-100 point scale, which we rescaled to 0-1.
+A substantial number of participants rated their beliefs and actions as exactly 0 or exactly 1 at either T1 or T2.
+OLS linear regression models are not suitable for a closed and bounded distribution with so many values on the boundary because the residuals would not be normally distributed or have constant variance.
+Beta regression, a possible alternative, is only defined on the open interval, (0, 1), whereas our data had many values on the boundaries (a closed interval).
+A variant of beta regression, zero-one inflated beta, is inappropriate because it assumes separate processes for the generation of data on the boundaries vs.
+the interior, and we had no reason to believe that our zeros and ones were generated by a different process than the rest of our observations.
 
-Belief in need t2 ~ Signal + Belief in need t1
-Likelihood of help t2 ~ Signal + Likelihood of help t1
+We therefore fit models of our two outcome variables in three ways.
+First, we used fractional regression models, introduced in a seminal paper by @papke1996 for outcomes on [0, 1], which, in brief, involve fitting a quasi-likelihood version of logistic regression with robust standard errors.
+This method is implemented in the R `frm` package [@ramalho2019].
+Second, we fit GLM logistic regression models, computing 95% CI's via bootstrapping, using the R `glmmboot` package created to model outcomes on [0, 1] [@humphrey2020].
+Finally, we fit GLM models with the quasibinomial family and logit link using the `glm` function in R stats library.
+The estimated coefficients, standard errors, and confidence intervals produced by the three methods were *very* similar, and often identical.
+We therefore proceeded to fit models using `glm` with the quasibinomilal family and logit link because model objects produced by this function are compatible with numerous other R packages for estimating and plotting effects.
 
-Based on advice from our statistical consultant, we also fit the following interaction models:
+Although two of our four preregistered OLS regression models included an interaction term, the rationale for it was less convincing for quasibinomial models using a logit link, which transforms [0, 1] to (-$\infty$, $\infty$).
+We therefore only included it if there was clear evidence of superior fit.
+Our intervention was *signal*, coded as an ordinal variable with the following preregistered rank order: verbal request, crying, mild depression, depression, suicide attempt.
+We used the default `glm` settings, which code such variables as orthogonal polynomial contrasts.
+Our primary confirmatory regression models were as follows (where the signal subscripts indicate polynomial degree):
 
-Belief in need t2 ~ Signal * Belief in need t1
-Likelihood of help t2 ~ Signal * Likelihood of help t1
+`r extract_eq(models$Model$m1, intercept='beta', wrap=T)`
+`r extract_eq(models$Model$m3, intercept='beta', wrap=T)`
 
-The rationale for the interaction is that for individuals who indicate high levels of belief and helping at baseline, the signals might have reduced effect.
+To test our hypothesis that the likelihood of acting to help the victim would be largely mediated by a signal's positive impact on the participant's beleif in the victim's need, we used the `mediation` package [@tingley2014] to fit a mediaton model for *Depression* vs.
+*Verbal request*.
+The mediation and outcome models, respectively, were:
 
-To examine our hypothesis that beneficial treatment would be largely due to a signal's positive impact on the participant's beleif in need we ran the following mediaton models for each pairwise combination of signals:
-
-Mediator model: Belief in need t2 ~ Signal + Belief in need t1
-Outcome model: Likelihood of help t2  ~ Signal + Belief in need t2 + Likelihood of help t1 + Belief in need t1
+`r extract_eq(med1$model.m, intercept='beta', wrap=T)`
+`r extract_eq(med1$model.y, intercept='beta', wrap=T)`
 
@@
 
-```{r beliefeffect, fig.width=8, fig.height=8, fig.cap="The effect of the signals on T2 Belief (top) and Action (bottom) controlling for T1 values of Belief and Action, respectively, with an interaction between T1 values and the signal.
+```{r beliefeffect, fig.width=8, fig.height=8, fig.cap="The effect of the signals on T2 Belief (top) and Action (bottom) controlling for T1 values of Belief and Action, respectively.
 Fit using generalized linear regression models with the quasibinomial family."}
-(effectsPlots$m1bplot + theme(axis.text.x = element_blank()))/effectsPlots$m3bplot + plot_layout(ncol = 1) & theme(plot.margin = unit(c(0,0,0,0), units = 'mm'))
+(effectsPlots$m1plot + theme(axis.text.x = element_blank()))/effectsPlots$m3plot + plot_layout(ncol = 1) & theme(plot.margin = unit(c(0,0,0,0), units = 'mm'))
 ```
@@
 See Figure \@ref(fig:medmodel).
-
-```{r medmodel, fig.cap="Possible causal effects of the signal on helping behavior.
-A credible signal of need increases belief that the victim is telling the truth and needs help, which increase the likelihood of helping.
-The direct path from the signal to action represents other causal effects of the signal on observers, such as perceptions of the victim's emotional state (and other factors not measured in this study) that might alter observer behavior."}
-
-knitr::include_graphics('paths.svg')
-```
 
@@
 
-```{r}
-pwr80_90 <- 
-  power_curve %>% 
-  group_by(Base) %>% 
-  summarise(
-    pwr80 = min(sample_size[power>=.8]), 
-    pwr90 = min(sample_size[power>=.9])
-  )
-```
-
-We estimated power using our pilot study data to compared the effect of the *Depression* signal vs.
+We estimated power using our pilot study data to compare the effect of the *Depression* signal vs.
 the *Verbal request* signal on *Belief* (that the sister needed the money) at T2 controlling for *Belief* at T1 in a linear regression model.
@@
 Power was computed as the proportion of p-values < 0.05.
-Power was about 80% for a sample size of about `r pwr80_90[2,2]`, and was about 90% for a sample size of about `r pwr80_90[2,3]`.
+Power was about 80% for a sample size of about `r pwr80_90[[2,2]]`, and was about 90% for a sample size of about `r pwr80_90[[2,3]]`.
 We then repeated this entire procedure to compare *Depression* to a *Control* condition that was meant to not include any signaling (but which we realized, post hoc, did include a verbal request).
-Power was about 80% for a sample size of about `r pwr80_90[1,2]`, and was about 90% for a sample size of about `r pwr80_90[1,3]`.
+Power was about 80% for a sample size of about `r pwr80_90[[1,2]]`, and was about 90% for a sample size of about `r pwr80_90[[1,3]]`.
 See Figure \@ref(fig:power).

### 2021-04-02 _targets.R

@@ -128,6 +128,26 @@ list(
 # Bootstrapped models -----------------------------------------------------
 
   tar_target(
+    m1_boot,
+    bootstrap_model(
+      base_model = glm(T2Belief ~ T1Belief + signal, family = binomial, d),
+      base_data = d,
+      resamples = 999,
+      parallelism = 'parallel'
+    )
+  ),
+
+  tar_target(
+    m3_boot,
+    bootstrap_model(
+      base_model = glm(T2Action ~ T1Action + signal, family = binomial, d),
+      base_data = d,
+      resamples = 999,
+      parallelism = 'parallel'
+    )
+  ),
+
+  tar_target(
     m1b_boot,
     bootstrap_model(
       base_model = glm(T2Belief ~ T1Belief * signal, family = binomial, d),
@@ -155,6 +175,18 @@ tar_target(
   ),
 
 # Mediation models --------------------------------------------------------
+
+  tar_target(
+    med_prereg,
+    signal_mediate(
+      data=d,
+      treat.value ='Depression',
+      med_f = 'T2Belief ~ signal + T1Belief',
+      out_f = 'T2Action ~ signal + T1Belief + T1Action + T2Belief',
+      mediator = 'T2Belief',
+      family = 'gaussian'
+    )
+  ),
 
   tar_target(
     med1,

### 2021-04-02 Paper.rmd
Working on intro, added refs to bib file

@@
 
-Durkheim’s pioneering study of suicide [@durkheim1897] arguably launched sociology as a quantitative discipline.
-Sociological investigations of suicide flourished through much of the 20th century, but began to be supplanted by medical and public health approaches as the biomedical model of mental health took hold in the late 1970's and early 1980's [@wray2011; @syme2020].
-The biomedical model tends to frame suicide as an individiual-level problem, e.g., as one involving psychiatric disturbance, drug addiction, or severe stress [@wray2011].
-This theoretical approach has made little progress: Despite substantial investment by funding agencies, rates of suicide have remained largely unchanged over the last 100 years (confirm and cite).
+Durkheim’s pioneering study of suicide [@durkheim1897] helped launch sociology as a quantitative discipline.
+Sociological investigations of suicide flourished through much of the 20th century, but were supplanted by medical and public health approaches as the biomedical model of mental health took hold in the late 1970's and early 1980's [@wray2011; @syme2020].
+The biomedical model tends to frame suicide as a problem with the individual, e.g., as one involving psychiatric disturbance, drug addiction, or stress sensitivity [@wray2011].
+This theoretical approach has made little progress: Rates of suicide, which vary widely by country, have remained relatively flat in countries for which there are long-term data, such as the US, UK, Japan, and Sweden [@owidsuicide].
 
-Early on, anthropologists also tackled the problem of suicide as manifested in the small, traditional socities in which they conducted their fieldwork.
-Suicide, they found, was commonly a form of protest, revenge, and/or appeal (e.g., Malinowski, 1985; Niehaus, 2012).
-Some ethnographers, such as Hezel (1987), conceptualized suicide as a form of anger, whereas others, such as Giddens (1964), conceptualized suicide as a form of social pressure.
-Counts (1980) emphasized the powerlessness of suicide victims.
+Early on, anthropologists also tackled the problem of suicide as manifested in the small traditional societies in which they conducted their fieldwork.
+Suicide, they found, was commonly a form of protest, revenge, and/or appeal [e.g., @Malinowski:1932; @niehaus2012].
+Some ethnographers, such as @Hezel:1987, conceptualized suicide as a form of anger, whereas others, such as @Giddens:1964, conceptualized suicide as a form of social pressure.
+@Counts:1980 emphasized the powerlessness of suicide victims.
 Common to almost all theoretical and empirical investigations of suicide is a focus on *completed* suicides, i.e., suicide deaths.
-@SymeEtAl2016, in contrast, argued that because the vast majority of suicidal behavior does not result in death, the proper focus should be on suicide ideation and suicide attempts, not deaths.
+@SymeEtAl2016, in contrast, argued that because the vast majority of suicidal behavior does not result in death, the proper focus should be on suicide ideation and suicide attempts, with death as an unintended consequence.
+See Figure \@ref(fig:cdc).
+
+```{r cdc, fig.width=8, fig.cap="US Suicide attempt and completion rates by age and sex (2001-2011)."}
+library(hrafsuicidedata)
+cdc %>% 
+  pivot_longer(c(`Suicide rate`, `Attempt rate`)) %>% 
+  ggplot(aes(age2, value, colour = sex, linetype = name)) + 
+  geom_line() +
+  hagenutils::scale_color_binary() +
+  guides(colour = guide_legend(title='Sex'), linetype = guide_legend(title=NULL)) +
+  labs(x = '\nAge (years)', y = 'Rate\n(per 100,000)', hjust=0) +
+  theme_minimal(15) +
+  theme(axis.title.y = element_text(angle = 0))
+```
 
 Within anthropology, Raymond Firth was likely the first to put the focus on suicidality as a gamble to improve one's circumstances in the here and now.
-Based on observations that suicide attempts often followed social conflict or loss and varied substantially in their likelihood of death, he argued that a sizable subset of the suicide attempts among the Tikopia were not meant to end in death but instead were a means to elicit attention, status, and immediate reintegration into the community following negative events (Firth 1967[not original date]).
-Compared to suicide, however, anthropological explanations for depression are a much more recent occurrence (cite examples), despite frequent reports of depression or depression-like behavior in a wide range of societies (cite) and the potential for cross-cultural research to help understand depressive states (cite).
+Based on observations that suicide attempts often followed social conflict or loss, and varied substantially in their likelihood of death, he argued that a sizable subset of the suicide attempts among the Tikopia were not meant to end in death but instead were a means to elicit attention, status, and immediate reintegration into the community following negative events [@firth1936: @Firth:1961].
+
+Suicidality is closely linked to depression.
+Suicidal ideation is one of nine diagnostic criteria for a major depressive episode [MDE, @dsm5], it is associated with depression across cultures [@haroz2017], and depression is a major risk factor for suicidal behavior [@hawton2013].
+Compared to suicide, however, there are fewer anthropological investigations of depression [@kleinman1985] despite frequent reports of depression or depression-like behavior in a wide range of societies [@haroz2017; @liu2020] and the potential for cross-cultural research to help understand depressive states [@haroz2017].
+
+Evolutionary theories of depression tend to either ignore suicidality, or take it as evidence that depression is dysfunctional [for reviews of evolutionary theories of depression, see @].
+
+and anthropological explanations for low mood have become more common.
+In general, these approaches see sadness and minor depression as ways to motivate adaptive behavior changes in response to negative outcomes in one's environment (cite Nesse and others), mainly differing in how they view major depression.
+While some approaches present most forms of major depression as dysfunctional (inflammation and some of Nesse), others have extended the logic on the benefits of low mood and reduced behavior to more severe instances of sadness.
+Of the possible benefits, the ability of depression to help solve fitness-relevant in times of social conflict is the most emphasized, with depression being suggested to help by reallocating resources with the body for problem solving (cite ARH), reducing the costs of interacting with higher status individuals (cite), or serving as a means to both signal one's need and bargain for increased support (cite).
 
@@
 - then follow with this
-As with suicide, research on depression has been dominated by biomedical approaches of limited success.
-However, evolutionary and anthropological explanations for low mood have become more common.
-In general, these approaches see sadness and minor depression as ways to motivate adaptive behavior changes in response to negative outcomes in one's environment (cite Nesse and others), mainly differing in how they view major depression.
-While some approaches present most forms of major depression as dysfunctional (inflammation and some of Nesse), others have extended the logic on the benefits of low mood and reduced behavior to more severe instances of sadness.
-Of the possible benefits, the ability of depression to help solve fitness-relevant in times of social conflict is the most emphasized, with depression being suggested to help by reallocating resources with the body for problem solving (cite ARH), reducing the costs of interacting with higher status individuals (cite), or serving as a means to both signal one's need and bargain for increased support (cite).
+
+As with suicide, research on depression since the 1980's has been dominated by biomedical approaches of limited success [@patten2016; @ormel2019].
 

### 2021-04-02 Paper.rmd
Worked on signaling section - Added signal vs. cue paragraph - Minor edits combining both bargaining models

@@
 
+- emphasize conflict more
+
 Likely the most reliable finding when it comes to depression and suicidal behavior is that most cases are closely tied to major negative life events (Hammen, 2005; Mazure, 1998; Devries et al.
@@
 
-One possible reason for the connection between depression and social adversity is that depression functions to elicit increased support from others in times when an individual cannot solve substantial fitness-relevant challenges on their own.
-The bargaining model of depression is based on the idea that for much of our evolutionary history the small groups humans lived in created many situations in which certain forms of cooperation were unlikely to be easily replaced by others while also allowing for harmful or unfair social relationships to develop (Hagen, 2003).
-In these instances, one's monopoly on one or more types of cooperation could be leveraged to change how one is treated if others value the depressed person's cooperation sufficiently.
+- add suicide as a pure signal
+- merge the hypotheses more
 
-One way depression and suicidal behavior are thought to lead to beneficial treatment is by reliably demonstrating that one’s need is genuine by making one’s private information about their condition public.
+One possible reason for the connection between depression, suicide, and social adversity is that some instances of depression and suicide attempts serve as means to elicit increased support from others in times when an individual cannot solve substantial fitness-relevant challenges on their own (cite).
+Referred to as the bargaining models of depression and suicide, the idea is that the small groups humans lived in for much of our evolutionary history created many situations in which certain forms of cooperation were unlikely to be easily replaced by others while also allowing for harmful or unfair social relationships to develop (Hagen, 2003).
+In these instances, one's monopoly on one or more types of cooperation could be leveraged to change how one is treated if others valued an individual's cooperation sufficiently.
+
+One way this approach expects depression and suicidal behavior to lead to beneficial treatment is their ability to reliably demonstrate that one’s need is genuine by making one’s private information about their condition public (cite).
 This information is necessary due to the ease in which signals can be faked (Zahavi, 1975) and the costs of accepting a deceptive signal as reliable (cite), both of which have favored adaptations to spot fake signals in many species (Hasson, 1994) and demand trustworthy information before believing a given signal (check Hasson and cite + try to find others).
@@
 Although there may be other ways for honest signals evolve (cite), one of the most widely accepted (is this fair?) means is through costly signaling.
-The evolution of costly signals is possible whenever the signal in question is comparatively cheaper to produce for those who have the underlying quality compared to those who lack it (Grafen 1990).
-In these instances, individuals with the quality maximize their fitness at greater levels of investment in the signal compared to those who lack the quality or possess it to a lesser degree (Gangestad and Scheyd 2005; Zahavi 1977).
-The end result of this is expected to be a signal that either tends to not be worth faking (Gangestad and Scheyd 2005) or is impossible to fake to a large degree due to selection against fakers constraining the physiology behind the signal (Zahavi 1977).
+The evolution of costly signals is possible whenever the signal in question is comparatively cheaper to produce for those who have the underlying quality being compared to those who lack it (Grafen 1990).
+In these instances, individuals with the quality maximize their fitness at greater levels of investment in the signal compared to those who lack the quality or possess it to a lesser degree (New paper from Barclay paper; Zahavi 1977).
+The end result of this is expected to be a signal that either tends to not be worth faking (New paper from Barclay paper) or is impossible to fake to a large degree due to selection against fakers constraining the physiology behind the signal (Zahavi 1977).
 
@@
 In these instances, less costly signals like verbal requests, facial sadness, and crying are likely to be unreliable as their low costs can easily be made up for with increased social support, thereby favoring the use of costlier signals in those experiencing need they cannot resolve on their own.
+
+As with any study examining signaling, distinguishing between the information provided by signals vs.
+cues is a major challenge.
+A signal differs from a cue in that it is intentionally sent by an organism to alter the behavior or thoughts of other individuals, while a cue is any piece of information an organism uses to alter its behavior or physiological state that was created without the intent to do so (Maynard Smith & Harper, 1995).
+When it comes to this study, suicide attempts are more likely to take the form of a pure, external signal than depression symptoms.
+This is because behavioral shifts motivated by low mood for non-signaling benefits would convey information as cues in addition to what might exist for signaling purposes.
+In other words, the signaling portion of depression may come from greater investment in symptoms than would be optimal for motivating behavior changes alone instead of the creation of entirely new symptoms.
+As most suicide attempts likely do not have non-signaling functions (see DC for possible exceptions), it is likely much easier to interpret the effect of signaling compared to depression.
 

### 2021-04-04 Paper.rmd
Changed adversity section

@@
 
-Alternative depression idea:
-- move Firth up before Syme et al. 2016 and tweak slighlty or reword Firth and put behind Syme in the same paragraph
-- delete the previous depression stuff
-- then follow with this
-
 As with suicide, research on depression since the 1980's has been dominated by biomedical approaches of limited success [@patten2016; @ormel2019].
@@
 
-- emphasize conflict more
-
-Likely the most reliable finding when it comes to depression and suicidal behavior is that most cases are closely tied to major negative life events (Hammen, 2005; Mazure, 1998; Devries et al.
+Likely the most reliable finding regarding depression and suicidality is that most cases are closely tied to major negative life events (Hammen, 2005; Mazure, 1998; Devries et al.
 2011; Ellsberg et al.
 2008).
-Compared to non-depressed individuals, those with depression tend to report at least twice as many instances of negative events in both community and clinical samples (Mazure, 1998) and more negative events than those with schizophrenia and bipolar depression across a wide range of studies (Paykel, 1994).
-In instances where depression is preceded by negative events, it's onset tends to quickly follow, often occurring within one month of the event (Kendler et al., 1999 [double check and find others]).
+Compared to non-depressed individuals, those with depression tend to report at least twice as many instances of negative events than non-depressed individuals (Mazure, 1998) and more negative events than those with schizophrenia and bipolar depression across a wide range of studies (Paykel, 1994).
+In longitudinal studies, the onset of depression tends to quickly follow the negative event (Kendler et al., 1999; search for others) or coincide with periods where conflict is likely to increase prior to it (e.g., depression starting before a divorce rather than after) (Rosenstrom).
 
@@
 
-Of the many types of negative life events associated with depression, those which involve social adversity tend to be more strongly associated with depression (Hammen, 2005; Kendler et al., 1999; Mazure, 1998).
-Like the relationship between negative events as a whole and depression, this relationship is also seen cross-culturally, with the loss of a loved one, threat of divorce, or abusive relationships all increasing one's chances of becoming depressed (Kendler et al., 1999, 1995 [check if this fits the cross-cultural claim]).
-Of these events, physical assault has been found to be the strongest predictor of depression in the few studies in which it has been examined (Kendler et al., 1999, 1995) and may have been much more common throughout our evolutionary history than is often appreciated based on rates of spousal abuse in small-scale societies with little or no policing (Levinson, 1989; Stieglitz et al., 2018).
+Of the types of negative life events associated with depression, those which involve social adversity tend to be more strongly associated with depression (Hammen, 2005; Mazure, 1998).
+The loss of a loved one, marital problems, bullying (cite), and the existence of abusive relationships are all commonly cited risk factors for depression (Kendler et al., 1999, 1995 [find others]), with  assault (both sexual and non-sexual), in particular, greatly increasing one's risk of depression (Kendler et al., 1999, 1995).
+Other notable risk factors like financial problems, job loss, or severe illness, might seem to lack this social element.
+However, the ability for others to provide meaningful support to limit the harm caused by such events (sugiyama + others) combined with the ubiquity of conflicts of interests mean that many types of problems will become social even if they did not start that way (Cite you?).
 
-Suicide attempts also tend to co-occur with social adversity.
+As depression is the leading cause of suicide compared to mental disorders (Hagen 2003 (find more direct citation)), it should not be surprising that suicidality also often co-occurs with social adversity.
 Grief over the loss of a loved one (Firth; Devries et al.
@@
 ## Depression and suicide attempts as both signals and bargaining tools
-
-- add suicide as a pure signal
-- merge the hypotheses more
 
@@
 For this reason, the way others view and respond to suicide attempts is likely to be strongly influenced by the probability that the attempt would result in death or severe injury (Rosenthal, 1993).
-That given, the previously mentioned logic still applies with increased risk of death being relatively costly for those able to advance their fitness prospects in their day-to-day lives.
+That given, the previously mentioned logic still applies with increased risk of death being relatively more costly for those able to advance their fitness prospects in their day-to-day lives.
 
 Beyond resulting in the cost differential that allows for costly signaling in the first place, the costs of depression and suicidal behavior may be particularly important in times of conflict or when the level of support needed to address one’s situation is substantial.
-Importantly, there are likely few forms of social adversity that do not come with conflict.
-For example, breakups in both romantic and cooperative relationships are often preceded by conflict (Amato & Hohmann-Marriott, 2007), and surely involve conflict when one side wants reconciliation and the other does not.
+As previously mentioned, there are likely few forms of social adversity that do not come with conflict.
+For example, breakups in both romantic and cooperative relationships are often preceded by conflict (Amato & Hohmann-Marriott, 2007; Rosenstrom), and surely involve conflict when one side wants reconciliation and the other does not.
 Likewise, the death of a loved one may also be a source of conflict as the survivor may turn to others for more support who might not want to invest more in the survivor (Hagen, 2003).
@@
 
-As with any study examining signaling, distinguishing between the information provided by signals vs.
-cues is a major challenge.
+As with any study examining signaling, distinguishing between the information provided by signals versus cues is a major challenge.
 A signal differs from a cue in that it is intentionally sent by an organism to alter the behavior or thoughts of other individuals, while a cue is any piece of information an organism uses to alter its behavior or physiological state that was created without the intent to do so (Maynard Smith & Harper, 1995).
-When it comes to this study, suicide attempts are more likely to take the form of a pure, external signal than depression symptoms.
+Regarding the signals of interest, suicide attempts are more likely to take the form of a pure, external signal than depression symptoms.
 This is because behavioral shifts motivated by low mood for non-signaling benefits would convey information as cues in addition to what might exist for signaling purposes.
-In other words, the signaling portion of depression may come from greater investment in symptoms than would be optimal for motivating behavior changes alone instead of the creation of entirely new symptoms.
-As most suicide attempts likely do not have non-signaling functions (see DC for possible exceptions), it is likely much easier to interpret the effect of signaling compared to depression.
+In other words, the signaling portion of depression may come from the upregulation of symptoms beyond what would be optimal for motivating behavior changes alone instead of the creation of entirely new symptoms.
+As most suicide attempts likely do not have non-signaling functions (see DC for a possible exception), this is less likely to be a challenge with suicide attempts.
 
-In addition to signaling need to those invested in the well-being of the signaler, depression and suicidal behavior may also help an individual bargain for increased support (Hagen 2003).
+Beyond signaling need to those invested in the well-being of the signaler, depression and suicidal behavior may also help an individual bargain for increased support (Hagen 2003).
 This is possible due to the reduced investment in others that frequently accompanies depression or the threat to future cooperation that comes from a suicide.
@@
 ## Responses to depression and suicidal behavior
-For depression and suicide attempts to be worth the costs, substantial benefits in terms of social support are expected, either in the form of temporary but impactful support or long-term changes in how one is treated (Hagen, 2003; Hagen et al., 2008; Syme et al., 2016).
+
+For depression and suicide attempts to be worth the costs involved with signaling, substantial benefits in terms of social support are expected, either in the form of temporary but impactful support or long-term changes in how one is treated (Hagen, 2003; Hagen et al., 2008; Syme et al., 2016).
 This can take the form of reconciliations in failing relationships, increased fairness in cooperative relationships, or an increase of resources being directed towards an individual.

### 2021-04-04 Paper.rmd
Added in-text citations to RMD Added citations to Bib Added study aims and predictions General but minor edits to intro

@@
 
-Likely the most reliable finding regarding depression and suicidality is that most cases are closely tied to major negative life events (Hammen, 2005; Mazure, 1998; Devries et al.
-2011; Ellsberg et al.
-2008).
-Compared to non-depressed individuals, those with depression tend to report at least twice as many instances of negative events than non-depressed individuals (Mazure, 1998) and more negative events than those with schizophrenia and bipolar depression across a wide range of studies (Paykel, 1994).
-In longitudinal studies, the onset of depression tends to quickly follow the negative event (Kendler et al., 1999; search for others) or coincide with periods where conflict is likely to increase prior to it (e.g., depression starting before a divorce rather than after) (Rosenstrom).
+Likely the most reliable finding regarding depression and suicidality is that most cases are closely tied to major negative life events [@Hammen2005; @Mazure1998; @devries2011; @ellsberg2008].
+Compared to non-depressed individuals, those with depression tend to report at least twice as many instances of negative events than non-depressed individuals [@Mazure1998] and more negative events than those with schizophrenia and bipolar depression across a wide range of studies [@Paykel1994].
+In longitudinal studies, the onset of depression tends to quickly follow the negative event [@KendlerEtAl1999] (search for others) or coincide with periods where conflict is likely to increase prior to it (e.g., depression starting before a divorce rather than after; @rosenstrom2017).
 
-This strong connection between negative life events and depression along with the adversity and distress that likely accompanies these events has led to the suggestion that this relationship is causal (Kendler et al., 1999).
-Support for this comes from the fact that the relationship between negative events and depression holds true when looking solely at events outside of one's control, showing that the connection is unlikely to be driven solely by depressed individuals creating situations where negative events are likely to be common (Hammen, 2005; Kendler et al., 1999).
-In addition to this, twin studies have shown that one's history of negative events is still a strong predictor of major depression when controlling for genetic similarity and that part of the heritability of depression stems from the heritability of negative events, like divorce and family conflict (Kendler & Baker, 2007; Kendler et al., 1999).
+This strong connection between negative life events and depression along with the adversity and distress that likely accompanies these events has led to the suggestion that this relationship is causal [@KendlerEtAl1999].
+Support for this comes from the fact that the relationship between negative events and depression holds true when looking solely at events outside of one's control, showing that the connection is unlikely to be driven solely by depressed individuals creating situations where negative events are likely to be common [@Hammen2005; @KendlerEtAl1999].
+In addition to this, twin studies have shown that one's history of negative events is still a strong predictor of major depression when controlling for genetic similarity and that part of the heritability of depression stems from the heritability of negative events, like divorce and family conflict [@KendlerBaker2007; @KendlerEtAl1999].
 
-Of the types of negative life events associated with depression, those which involve social adversity tend to be more strongly associated with depression (Hammen, 2005; Mazure, 1998).
-The loss of a loved one, marital problems, bullying (cite), and the existence of abusive relationships are all commonly cited risk factors for depression (Kendler et al., 1999, 1995 [find others]), with  assault (both sexual and non-sexual), in particular, greatly increasing one's risk of depression (Kendler et al., 1999, 1995).
-Other notable risk factors like financial problems, job loss, or severe illness, might seem to lack this social element.
-However, the ability for others to provide meaningful support to limit the harm caused by such events (sugiyama + others) combined with the ubiquity of conflicts of interests mean that many types of problems will become social even if they did not start that way (Cite you?).
+Of the types of negative life events associated with depression, those which involve social adversity tend to be more strongly associated with depression [@Hammen2005; @Mazure1998].
+The loss of a loved one, marital problems, bullying, and the existence of abusive relationships are all commonly cited risk factors for depression [@KendlerEtAl1995; @KendlerEtAl1999; @klomek2007; @klomek2019], with  assault (both sexual and non-sexual), in particular, greatly increasing one's risk of depression [@KendlerEtAl1995; @KendlerEtAl1999].
+Other notable risk factors like financial problems, job loss, or severe or prolonged illness, might seem to lack this social element.
+However, the ability for others to provide meaningful support to limit the harm caused by such events [@SugiyamaSugiyama2003] combined with the ubiquity of conflicts of interests mean that many types of problems will become social even if they did not start that way [@Hagen2003)]
 
 As depression is the leading cause of suicide compared to mental disorders (Hagen 2003 (find more direct citation)), it should not be surprising that suicidality also often co-occurs with social adversity.
-Grief over the loss of a loved one (Firth; Devries et al.
-2011), bullying (Alavi et al., 2017; Butler et al., 2019; Ford et al., 2017; Wang et al., 2020), and instances of social transgression (Firth; Malinowski; Syme and Hagen 2018; find Western citation to confirm) have all been reported to lead to suicidal behavior in both industrialized (confirm the transgression part) and traditional societies.
-Of the recorded instances of suicide attempts in the Human Relations Area Files (HRAF), 77.4% of attempts were found to be linked to times of social conflict, 88.7% were linked to fitness threats in general, and 84.9% were linked to situations in which attempters were powerless to resolve their situation alone (Syme et al., 2016).
-As with depression, assault is an particularly powerful risk factor for suicidal behavior based on multiple large-scale multi-country studies (Devries et al.
-2011; Ellsberg et al.
-2008) and more localized examinations.
-For example, both sexual and non-sexual assault were also associated with more self-harm and suicidal behaviors among both indigenous Sami and majority Norwegian adolescents, with those who attempted suicides also reporting more than twice the number of negative life events than those who did not (Reigstad and Kvernmo 2017).
+Grief over the loss of a loved one [@firth1936: @Firth:1961; @devries2011], bullying [@alavi2017; @butler2019; @ford2017; @wang2020], and instances of social transgression [@Firth:1961; @Malinowski:1932; @SymeHagen2018; @lester1997] have all been reported to lead to suicidal behavior in both industrialized and traditional societies.
+Of the recorded instances of suicide attempts in the Human Relations Area Files (HRAF), 77.4% of attempts were found to be linked to times of social conflict, 88.7% were linked to fitness threats in general, and 84.9% were linked to situations in which attempters were powerless to resolve their situation alone [@SymeEtAl2016].
+As with depression, assault is an particularly powerful risk factor for suicidal behavior based on multiple large-scale multi-country studies [@devries2011; @ellsberg2008] and more localized examinations.
+For example, both sexual and non-sexual assault were also associated with more self-harm and suicidal behaviors among both indigenous Sami and majority Norwegian adolescents, with those who attempted suicides also reporting more than twice the number of negative life events than those who did not [@reigstad2017].
 
@@
 
-One possible reason for the connection between depression, suicide, and social adversity is that some instances of depression and suicide attempts serve as means to elicit increased support from others in times when an individual cannot solve substantial fitness-relevant challenges on their own (cite).
-Referred to as the bargaining models of depression and suicide, the idea is that the small groups humans lived in for much of our evolutionary history created many situations in which certain forms of cooperation were unlikely to be easily replaced by others while also allowing for harmful or unfair social relationships to develop (Hagen, 2003).
+One possible reason for the connection between depression, suicide, and social adversity is that some instances of depression and suicide attempts serve as means to elicit increased support from others in times when an individual cannot solve substantial fitness-relevant challenges on their own.
+Referred to as the bargaining models of depression and suicide, the idea is that the small groups humans lived in for much of our evolutionary history created many situations in which certain forms of cooperation were unlikely to be easily replaced by others while also allowing for harmful or unfair social relationships to develop [@Hagen2003; @Hagen2002; @SymeEtAl2016].
 In these instances, one's monopoly on one or more types of cooperation could be leveraged to change how one is treated if others valued an individual's cooperation sufficiently.
 
-One way this approach expects depression and suicidal behavior to lead to beneficial treatment is their ability to reliably demonstrate that one’s need is genuine by making one’s private information about their condition public (cite).
-This information is necessary due to the ease in which signals can be faked (Zahavi, 1975) and the costs of accepting a deceptive signal as reliable (cite), both of which have favored adaptations to spot fake signals in many species (Hasson, 1994) and demand trustworthy information before believing a given signal (check Hasson and cite + try to find others).
+One way this approach expects depression and suicidal behavior to lead to beneficial treatment is through their ability to reliably demonstrate that one’s need is genuine by making one’s private information about their condition public [@Hagen2003].
+This information is necessary due to the ease in which signals can be faked [@Zahavi1975; @mokkonen2016] and the costs of accepting a deceptive signal as reliable [@dawkins1978; @johnstone1993; @Hasson1994], both of which have favored adaptations to spot or ignore fake signals in many species [@dawkins1991].
 
-Although there may be other ways for honest signals evolve (cite), one of the most widely accepted (is this fair?) means is through costly signaling.
-The evolution of costly signals is possible whenever the signal in question is comparatively cheaper to produce for those who have the underlying quality being compared to those who lack it (Grafen 1990).
-In these instances, individuals with the quality maximize their fitness at greater levels of investment in the signal compared to those who lack the quality or possess it to a lesser degree (New paper from Barclay paper; Zahavi 1977).
-The end result of this is expected to be a signal that either tends to not be worth faking (New paper from Barclay paper) or is impossible to fake to a large degree due to selection against fakers constraining the physiology behind the signal (Zahavi 1977).
+One way for honest signals to evolve is through costly signaling [@Zahavi1975].
+The evolution of costly signals is possible whenever the signal in question is comparatively cheaper to produce for those who have the underlying quality being compared to those who lack it [@grafen1990].
+In these instances, individuals with the quality maximize their fitness at greater levels of investment in the signal compared to those who lack the quality or possess it to a lesser degree [@zahavi1977].
+The end result of this is expected to be a signal that either tends to not be worth faking or is impossible to fake to a large degree due to selection against fakers constraining the physiology behind the signal [@zahavi1977; @gangestad2005].
 
 Both depression and suicidal behavior fit this criterion as they are both relatively costly for those not facing adversity than those who are.
-In the case of depression, the largescale reduction in one's normal routine of fitness enhancing behavior hurts those in need less when one has limited ability to obtain fitness-relevant benefits, with depression likely adding no additional costs in instances of extreme deprivation (Hagen 2003).
+In the case of depression, the largescale reduction in one's normal routine of fitness enhancing behavior is relatively less costly for those whose situations result in a limited ability to obtain fitness-relevant benefits, with depression likely adding no additional costs in instances of extreme deprivation [@Hagen2003].
 However, when it comes to suicide, the bulk of the costs associated with suicide attempts are only felt in times that result in death or severe bodily harm.
-For this reason, the way others view and respond to suicide attempts is likely to be strongly influenced by the probability that the attempt would result in death or severe injury (Rosenthal, 1993).
+For this reason, the way others view and respond to suicide attempts is likely to be strongly influenced by the probability that the attempt would result in death or severe injury [@Rosenthal1993].
 That given, the previously mentioned logic still applies with increased risk of death being relatively more costly for those able to advance their fitness prospects in their day-to-day lives.
@@
 As previously mentioned, there are likely few forms of social adversity that do not come with conflict.
-For example, breakups in both romantic and cooperative relationships are often preceded by conflict (Amato & Hohmann-Marriott, 2007; Rosenstrom), and surely involve conflict when one side wants reconciliation and the other does not.
-Likewise, the death of a loved one may also be a source of conflict as the survivor may turn to others for more support who might not want to invest more in the survivor (Hagen, 2003).
+For example, breakups in both romantic and cooperative relationships are often preceded by conflict [@amato2007], and surely involve conflict when one side wants reconciliation and the other does not.
+Likewise, the death of a loved one may also be a source of conflict as the survivor may turn to others for more support who might not want to invest more in the survivor [@Hagen2003].
 Regardless of the source of conflict, greater conflict should correspond with greater conflicts of interests, something which would favor greater investment in manipulating others through fake signals.
-In these instances, less costly signals like verbal requests, facial sadness, and crying are likely to be unreliable as their low costs can easily be made up for with increased social support, thereby favoring the use of costlier signals in those experiencing need they cannot resolve on their own.
+In these instances, less costly signals like verbal requests, facial sadness, and crying are expected to be less reliable as their low costs can easily be made up for with increased social support, thereby favoring the use of costlier signals in those experiencing need they cannot resolve on their own.
 
-As with any study examining signaling, distinguishing between the information provided by signals versus cues is a major challenge.
-A signal differs from a cue in that it is intentionally sent by an organism to alter the behavior or thoughts of other individuals, while a cue is any piece of information an organism uses to alter its behavior or physiological state that was created without the intent to do so (Maynard Smith & Harper, 1995).
-Regarding the signals of interest, suicide attempts are more likely to take the form of a pure, external signal than depression symptoms.
-This is because behavioral shifts motivated by low mood for non-signaling benefits would convey information as cues in addition to what might exist for signaling purposes.
-In other words, the signaling portion of depression may come from the upregulation of symptoms beyond what would be optimal for motivating behavior changes alone instead of the creation of entirely new symptoms.
-As most suicide attempts likely do not have non-signaling functions (see DC for a possible exception), this is less likely to be a challenge with suicide attempts.
-
-Beyond signaling need to those invested in the well-being of the signaler, depression and suicidal behavior may also help an individual bargain for increased support (Hagen 2003).
+Beyond signaling need to those invested in the well-being of the signaler, depression and suicidal behavior may also help an individual bargain for increased support [@Hagen2003].
 This is possible due to the reduced investment in others that frequently accompanies depression or the threat to future cooperation that comes from a suicide.
@@
 
+### Determining the impact of cues versus signals
+
+Distinguishing between the information provided by signals versus cues is a major challenge is a major challenge for signaling approaches to behavior.
+A signal differs from a cue in that it is intentionally sent by an organism to alter the behavior or thoughts of other individuals, while a cue is any piece of information an organism uses to alter its behavior or physiological state that was created without the intent to do so [@MaynardSmithHarper1995].
+Regarding the signals of interest, suicide attempts are more likely to take the form of a pure, external signal than depression symptoms.
+This is because behavioral shifts motivated by low mood for non-signaling benefits would convey information as cues in addition to what might exist for signaling purposes.
+In other words, the signaling portion of depression may come from the upregulation of symptoms beyond what would be optimal for non-signaling purposes alone instead of the creation of entirely new symptoms.
+As most suicide attempts likely do not have non-signaling functions (see @deCatanzaro1991 for a possible exception), this is less likely to be a challenge with suicide attempts.
+
 ## Responses to depression and suicidal behavior
 
-For depression and suicide attempts to be worth the costs involved with signaling, substantial benefits in terms of social support are expected, either in the form of temporary but impactful support or long-term changes in how one is treated (Hagen, 2003; Hagen et al., 2008; Syme et al., 2016).
+For depression and suicide attempts to be worth the costs involved with signaling, substantial benefits in terms of social support are expected, either in the form of temporary but impactful support or long-term changes in how one is treated [@Hagen2003; @SymeEtAl2016].
 This can take the form of reconciliations in failing relationships, increased fairness in cooperative relationships, or an increase of resources being directed towards an individual.
@@
 Most studies examining responses to depression have been observational and focused on responses outside of changes in social support.
-In general, most report aversive responses and high levels of rejection towards the depressed, and depressed individuals are often linked to impaired social functioning (Evraire & Dozois, 2011; Gotlib & Lee, 1989; Hirschfeld et al., 2000).
+In general, most report aversive responses and high levels of rejection towards the depressed, and depressed individuals are often linked to impaired social functioning [@EvraireDozois2011; @GotlibLee1989; @HirschfeldEtAl2000].
 One explanation for this is that depressed individuals engage in behaviors that drive others away.
-In line with this reasoning, both excessive reassurance seeking and negative feedback seeking, which often accompany depression, have been shown to elicit negative emotional responses from others and increase the chance of rejection from others (Joiner & Metalsky, 1995; Starr & Davila, 2008).
-Negative interactions are also seen in families as depressed children tend to report less support and more negative responses from parents than non-depressed children, although it has not been demonstrated that such interactions did not lead to depression in the first place (Messer & Gross, 1995; Schwartz et al., 2012).
+In line with this reasoning, both excessive reassurance seeking and negative feedback seeking, which often accompany depression, have been shown to elicit negative emotional responses from others and increase the chance of rejection from others [@JoinerMetalsky1995; @StarrDavila2008].
+Negative interactions are also seen in families as depressed children tend to report less support and more negative responses from parents than non-depressed children, although it has not been demonstrated that such interactions did not lead to depression in the first place [@MesserGross1995; @SchwartzEtAl2012].
 
 Despite being looked for less frequently, beneficial responses to depressed individuals are also reported.
-This is seen in that depression has been shown to reduce the likelihood of aggression within families (Hops 1987[read]; Dadds et al.
-1982 [read]), particularly in families already experiencing high levels of conflict (Sheeber et al., 2001).
+This is seen in that depression has been shown to reduce the likelihood of aggression within families [@hops1987; @dadds1992], including those already experiencing high levels of conflict [@SheeberEtAl2001].
 There is also limited evidence that depression can result in increased levels of support from others outside the family.
-For example, non-depressed individuals were shown to be more cooperative and exhibit more caretaking behavior towards their college depressed roommates over the course of their time living together (Hokanson et al., 1986).
-Likewise, a study examining responses to confederates trained to appear ‘depressed’, ‘anxious’, or ‘normal’ found that individuals were more likely to provide advice and support to ‘depressed’ individuals than ‘anxious’ or ‘normal’ individuals despite the confederate in ‘depression’ condition being viewed more negatively than the other conditions and the ‘depression’ condition involving similar levels of distress compared to the ‘anxious’ condition (Stephens et al., 1987 [tweaked based on your paper with Kristen]).
+For example, non-depressed individuals were shown to be more cooperative and exhibit more caretaking behavior towards their college depressed roommates over the course of their time living together [@HokansonEtAl1986].
+Likewise, a study examining responses to confederates trained to appear ‘depressed’, ‘anxious’, or ‘normal’ found that individuals were more likely to provide advice and support to ‘depressed’ individuals than ‘anxious’ or ‘normal’ individuals despite the confederate in ‘depression’ condition being viewed more negatively than the other conditions and the ‘depression’ condition involving similar levels of distress compared to the ‘anxious’ condition [@stephens1987].
 
 Unfortunately, there are few studies examining how individuals respond to suicide attempt survivors, with the majority examining responses after death.
-In those which exist, stigmatization is commonly reported within and outside families (Frey et al., 2017; Scocco et al., 2012), with perceptions of survivors as being weak, selfish, mentally ill, and antisocial all being commonly reported (Batterham et al., 2013; Frey et al., 2016a; Tzeng & Lipson, 2004).
+In those which exist, stigmatization is commonly reported within and outside families [@FreyEtAl2016; @ScoccoEtAl2012], with perceptions of survivors as being weak, selfish, mentally ill, and antisocial all being commonly reported [@BatterhamEtAl2013; @TzengLipson2004].
 Although these types of stigmatization have been reported across relationships types, the likelihood of stigma has been found to differ based on who the survivor is to the person being questioned.
-This is seen in a study which found that individuals felt the most stigma from members of their preexisting social networks than mental health providers, with family members providing more stigmatization (57.1% of the time) than romantic partners (41.2% of the time) and close friends (28.2% of the time) (Frey et al., 2016b).
+This is seen in a study which found that individuals felt the most stigma from members of their preexisting social networks than mental health providers, with family members providing more stigmatization (57.1% of the time) than romantic partners (41.2% of the time) and close friends (28.2% of the time) [@FreyEtAl2016].
 
 Although negative responses to suicide survivors are more often studied and reported, positive responses have also been found.
-Increased social support and changes to important relationships have been reported to follow suicide attempts with some indication that these effects may hold long term (Stengel, 1956).
-For example, a study of 100 women who survived suicide attempts found that in 75 cases individuals gained identifiable benefits through the attempt, with 41 individuals benefiting from reconciliations with others (Lukianowicz, 1971).
-As for the type of support received, emotional support seems to be more commonly provided than instrumental support based on initial evidence (Frey et al., 2017); however, it is currently unclear how this might change with social context.
+Increased social support and changes to important relationships have been reported to follow suicide attempts with some indication that these effects may hold long term [@Stengel1956].
+For example, a study of 100 women who survived suicide attempts found that in 75 cases individuals gained identifiable benefits through the attempt, with 41 individuals benefiting from reconciliations with others [@Lukianowicz1971].
+Unlike many Western countries, where suicide is often viewed as pathological [@Hidaka2012], members of traditional societies have been reported to view suicide attempts as cries for help rather than mental illness [@Shostak1981].
+For example, attempts have been described as ways of escaping unwanted marriage arrangements, persistent abuse, or a lack of support in obtaining mates by those engaging in the behavior and observers [@utierrezdePinedaMuirden1948; @Hilger1957; @arsten1935; @Tessmann1930; @Wilson1960], consistent with the idea that help is at least occasionally provided.
+In support of this, 30 out of 84 examples of suicidal behavior included in the HRAF resulted in positive changes for the survivor, even though suicide was rarely if ever the main topic [@SymeEtAl2016].
 
-Beneficial social changes are also reported in traditional societies.
-Unlike many Western countries, where suicide is often viewed as pathological (Hidaka, 2012), members of traditional societies have been reported to view suicide attempts as cries for help rather than mental illness (Shostak, 1981).
-For example, attempts have been described as ways of escaping unwanted marriage arrangements, persistent abuse, or a lack of support in obtaining mates by those engaging in the behavior and observers (Gutierrez de Pineda & Muirden, 1948; Hilger, 1957; Karsten, 1935; Tessmann, 1930; Wilson, 1960), suggesting that help is at least occasionally provided or reliably expected.
-In support of this, 30 out of 84 examples of suicidal behavior included in the HRAF resulted in positive changes for the survivor, even though suicide was rarely if ever the main topic (Syme et al., 2016).
+# Study aims and predictions
+
+The primary aim of this study was to examine responses to various forms of emotional signaling in an experimental vignette study.
+We predicted that costlier signals would increase the participants' self-reported belief in the signaler's claims and the likelihood of them providing help.
+Specifically, we predicted that the signals will have the following rank order from low to high cost: verbal request, crying, mild-depression, depression, and suicide attempt.
+We also predicted that changes in the likelihood participants would provide support would be mediated by changes in the participants' belief in the signaler's need pre-signal to post-signal.
+For the full preregistration, see https://osf.io/4m9wb/.
 
@@
 Find a place for the predictions and preregistration 
-go back and emphasize conflict and PI in the methods (at least in the pilot studies portion)
 add conclusion
@@
 Four vignettes were used in this study in which both the presence of conflicts of interest and the existence of private information about one's need were emphasized.
-Due to the expectation that depression and suicide are likely too costly of signals for relatively minor instances of need, we designed this study to involve severe scenarios associated with suicide attempts both ethnographically and clinically (i.e, sexual assault (cite), non-sexual assault (cite), and thwarted marriage (cite)).
+Due to the expectation that depression and suicide are likely too costly of signals for relatively minor instances of need, we designed this study to involve severe scenarios associated with suicide attempts both ethnographically and clinically (i.e, sexual assault, non-sexual assault, and thwarted marriage).
 
@@
 
-As the amount of crying in those with depression is moderately associated with depression severity [@VingerhoetsEtAl2016] (check this.
-IIRC he might have a more recent paper saying it's not associated with depression as people tend to think) and depression is a major risk factor for suicide [@BostwickPankratz2000; @Kessler2012], each signal was designed to build off of the less costly signals so that each signal contained elements of any signal it was costlier than.
-The full text for the signals are availible in the SI.
+As many depression scales include measures of crying (for discussion on the relationship between crying and depression see @bylsma2020) and depression is a major risk factor for suicide [@BostwickPankratz2000; @Kessler2012], each signal was designed to build off of the less costly signals so that each signal contained elements of any signal it was costlier than.
+The full text for the signals are available in the SI.
 
@@
 
-To test our hypothesis that the likelihood of acting to help the victim would be largely mediated by a signal's positive impact on the participant's beleif in the victim's need, we used the `mediation` package [@tingley2014] to fit a mediaton model for *Depression* vs.
+To test our hypothesis that the likelihood of acting to help the victim would be largely mediated by a signal's positive impact on the participant's beleif in the victim's need, we used the `mediation` package [@tingley2014] to fit a mediation model for *Depression* vs.
 *Verbal request*.

### 2021-04-04 Paper.rmd
Working on results

--- 2021-04-02 Paper.rmd
@@
 library(kableExtra)
+library(glue)
 library(ggplot2)
@@
     'd',
-    'signaling2018',
+    'signalingdata2018b',
+    'signaling2020',
+    'pilot_results',
     'power_curve',
@@
 
-```{r cdc, fig.width=8, fig.cap="US Suicide attempt and completion rates by age and sex (2001-2011)."}
+```{r cdc, fig.width=8, fig.cap="US Suicide attempt and completion rates by age and sex (2001-2019)."}
 library(hrafsuicidedata)
-cdc %>% 
-  pivot_longer(c(`Suicide rate`, `Attempt rate`)) %>% 
-  ggplot(aes(age2, value, colour = sex, linetype = name)) + 
+cdc2 %>% 
+  na.omit() %>% 
+  ggplot(aes(Age, `Crude Rate`, colour = Sex, linetype = Type)) + 
   geom_line() +
   hagenutils::scale_color_binary() +
-  guides(colour = guide_legend(title='Sex'), linetype = guide_legend(title=NULL)) +
-  labs(x = '\nAge (years)', y = 'Rate\n(per 100,000)', hjust=0) +
+  guides(
+    colour = guide_legend(title=NULL),
+    linetype = guide_legend(title=NULL, reverse = T)
+  ) +
+  labs(x = '\nAge (years)', y = 'Annual rate\n(per 100,000)') +
   theme_minimal(15) +
-  theme(axis.title.y = element_text(angle = 0))
+  theme(axis.title.y = element_text(angle = 0, hjust=0))
 ```
 
-Within anthropology, Raymond Firth was likely the first to put the focus on suicidality as a gamble to improve one's circumstances in the here and now.
-Based on observations that suicide attempts often followed social conflict or loss, and varied substantially in their likelihood of death, he argued that a sizable subset of the suicide attempts among the Tikopia were not meant to end in death but instead were a means to elicit attention, status, and immediate reintegration into the community following negative events [@firth1936: @Firth:1961].
+Within anthropology, Raymond Firth was likely the first to conceputalize suicidality as a gamble to improve one's circumstances in the here and now.
+Based on observations that suicide attempts often followed social conflict or loss, and varied substantially in their likelihood of death, he argued that a sizable subset of the suicide attempts among the Tikopia were not meant to end in death but instead were a means to elicit attention, status, and immediate reintegration into the community following negative events [@firth1936; @Firth:1961].
 
@@
 ## Connection to Adversity
-
-- emphasize conflict more
 
@@
 
-- add suicide as a pure signal
-- merge the hypotheses more
+One possible reason for the connection between depression and social adversity is that depression functions to elicit increased support from others in times when an individual cannot solve substantial fitness-relevant challenges on their own.
+The bargaining model of depression is based on the idea that for much of our evolutionary history the small groups humans lived in created many situations in which certain forms of cooperation were unlikely to be easily replaced by others while also allowing for harmful or unfair social relationships to develop (Hagen, 2003).
+In these instances, one's monopoly on one or more types of cooperation could be leveraged to change how one is treated if others value the depressed person's cooperation sufficiently.
 
-One possible reason for the connection between depression, suicide, and social adversity is that some instances of depression and suicide attempts serve as means to elicit increased support from others in times when an individual cannot solve substantial fitness-relevant challenges on their own (cite).
-Referred to as the bargaining models of depression and suicide, the idea is that the small groups humans lived in for much of our evolutionary history created many situations in which certain forms of cooperation were unlikely to be easily replaced by others while also allowing for harmful or unfair social relationships to develop (Hagen, 2003).
-In these instances, one's monopoly on one or more types of cooperation could be leveraged to change how one is treated if others valued an individual's cooperation sufficiently.
-
-One way this approach expects depression and suicidal behavior to lead to beneficial treatment is their ability to reliably demonstrate that one’s need is genuine by making one’s private information about their condition public (cite).
+One way depression and suicidal behavior are thought to lead to beneficial treatment is by reliably demonstrating that one’s need is genuine by making one’s private information about their condition public.
 This information is necessary due to the ease in which signals can be faked (Zahavi, 1975) and the costs of accepting a deceptive signal as reliable (cite), both of which have favored adaptations to spot fake signals in many species (Hasson, 1994) and demand trustworthy information before believing a given signal (check Hasson and cite + try to find others).
@@
 Although there may be other ways for honest signals evolve (cite), one of the most widely accepted (is this fair?) means is through costly signaling.
-The evolution of costly signals is possible whenever the signal in question is comparatively cheaper to produce for those who have the underlying quality being compared to those who lack it (Grafen 1990).
-In these instances, individuals with the quality maximize their fitness at greater levels of investment in the signal compared to those who lack the quality or possess it to a lesser degree (New paper from Barclay paper; Zahavi 1977).
-The end result of this is expected to be a signal that either tends to not be worth faking (New paper from Barclay paper) or is impossible to fake to a large degree due to selection against fakers constraining the physiology behind the signal (Zahavi 1977).
+The evolution of costly signals is possible whenever the signal in question is comparatively cheaper to produce for those who have the underlying quality compared to those who lack it (Grafen 1990).
+In these instances, individuals with the quality maximize their fitness at greater levels of investment in the signal compared to those who lack the quality or possess it to a lesser degree (Gangestad and Scheyd 2005; Zahavi 1977).
+The end result of this is expected to be a signal that either tends to not be worth faking (Gangestad and Scheyd 2005) or is impossible to fake to a large degree due to selection against fakers constraining the physiology behind the signal (Zahavi 1977).
 
@@
 In these instances, less costly signals like verbal requests, facial sadness, and crying are likely to be unreliable as their low costs can easily be made up for with increased social support, thereby favoring the use of costlier signals in those experiencing need they cannot resolve on their own.
-
-As with any study examining signaling, distinguishing between the information provided by signals vs.
-cues is a major challenge.
-A signal differs from a cue in that it is intentionally sent by an organism to alter the behavior or thoughts of other individuals, while a cue is any piece of information an organism uses to alter its behavior or physiological state that was created without the intent to do so (Maynard Smith & Harper, 1995).
-When it comes to this study, suicide attempts are more likely to take the form of a pure, external signal than depression symptoms.
-This is because behavioral shifts motivated by low mood for non-signaling benefits would convey information as cues in addition to what might exist for signaling purposes.
-In other words, the signaling portion of depression may come from greater investment in symptoms than would be optimal for motivating behavior changes alone instead of the creation of entirely new symptoms.
-As most suicide attempts likely do not have non-signaling functions (see DC for possible exceptions), it is likely much easier to interpret the effect of signaling compared to depression.
 
@@
 
-This study involved a between-subjects pretest-posttest design to examine how different emotional signals would influence (1) the degree participants believed a fictional character to be in need and (2) the likelihood they would provide help within a vignette study.
+This study utilized a between-subjects pretest-posttest design to examine how five different emotional signals would influence (1) the degree participants believed a fictional character to be in need (*Belief*) and (2) the likelihood they would provide help (*Action*) in four different vignettes, for a total of 20 conditions.
 
@@
 
-The sole treatment in this study was the signal participants saw, with these signals including: (1) a verbal request without additional signaling, (2) crying, (3) mild-depression, (4) depression and, (5) a suicide attempt.
+The sole treatment in this study was the signal participants saw, with these signals including: (1) a verbal request without additional signaling, (2) crying, (3) mild-depression, (4) depression, and (5) a suicide attempt.
 
 As the amount of crying in those with depression is moderately associated with depression severity [@VingerhoetsEtAl2016] (check this.
-IIRC he might have a more recent paper saying it's not associated with depression as people tend to think) and depression is a major risk factor for suicide [@BostwickPankratz2000; @Kessler2012], each signal was designed to build off of the less costly signals so that each signal contained elements of any signal it was costlier than.
+IIRC he might have a more recent paper saying it's not associated with depression as people tend to think) and depression is a major risk factor for suicide [@BostwickPankratz2000; @Kessler2012], each signal was designed to build off the less costly signals so that each signal contained elements of each lower cost signal.
 The full text for the signals are availible in the SI.
+
+## Lessons learned from a pilot study
+
+The current study is a refinement of a vignette-based pilot study (N=`r nrow(signalingdata2018b)`) with very similar signals and outcomes.
+In the pilot study, there was a single vignette in which an imagined sister claims her child needs an expensive emergency medical procedure, and asks for a very large loan.
+We learned five major lessons from the pilot study that influenced the design of the current study.
+First, as predicted, belief in the sister's need was low in the *Verbal request* condition and high in the *Depression* condition, giving us confidence to continue this research (see Figure \@ref(fig:piloteffects)).
+Second, to rule out that believability and willingness to help were simply artifacts of the sister's psychiatric distress, we included a "signaling" condition in which the sister exhibited schizophrenic symptoms.
+As predicted, believability and willingness to help in this condition were dramatically lower than in any other condition, ruling out this alternative explanation.
+We therefore did not replicate the schizophrenic condition in the current study.
+Third, baseline (T1) believability was very high (mean = `r signif(pilot_results$meanT1belief, 2)`, median = `r signif(pilot_results$medianT1belief, 2)` on a 0-100 point scale), leaving little scope for signals to increase believability.
+In the current study we therefore endeavored to provide details in the vignettes that would undermine the victim's believability at baseline.
+Fourth, contrary to our hypothesis, the *Suicide threat* and *Suicide attempt* signals reduced believability relative to *Depression*.
+We surmised that the sister's adversity -- a sick child -- was not sufficient to justify a suicide attempt, thus undermining her believability.
+In the current study the signaler herself is therefore the victim, and the forms of adversity -- physical and sexual assault and thwarted and forced marriage -- are those that are frequently associated with suicidality.
+Fifth, the content of the vignette matters, so instead of a single vignette we decided to use four different vignettes to help determine the extent to which signaling effects were sensitive to seemingly irrelevant details of the vignettes.
 
@@
 
-The current study is a refinement of a pilot study (N=`r nrow(signalingdata2018)`) with very similar signals and outcomes.
-We used these pilot data to estimate the sample sizes needed to detect an effect of the *Depression* vs.
+We used the pilot data to estimate the sample sizes needed to detect an effect of the *Depression* vs.
 *Verbal request* signal (two conditions) on *Belief* in the victim's need.
@@
 Beta regression, a possible alternative, is only defined on the open interval, (0, 1), whereas our data had many values on the boundaries (a closed interval).
-A variant of beta regression, zero-one inflated beta, is inappropriate because it assumes separate processes for the generation of data on the boundaries vs.
+A variant of beta regression, zero-one inflated beta, is inappropriate because it assumes different processes for the generation of data on the boundaries vs.
 the interior, and we had no reason to believe that our zeros and ones were generated by a different process than the rest of our observations.
 
-We therefore fit models of our two outcome variables in three ways.
-First, we used fractional regression models, introduced in a seminal paper by @papke1996 for outcomes on [0, 1], which, in brief, involve fitting a quasi-likelihood version of logistic regression with robust standard errors.
+We therefore fit models of our two outcome variables in four ways.
+First, we fit the preregistered OLS models (reported in the SI).
+Second, we fit fractional regression models, introduced in a seminal paper by @papke1996 for outcomes on [0, 1], which, in brief, involve fitting a quasi-likelihood version of logistic regression with robust standard errors.
 This method is implemented in the R `frm` package [@ramalho2019].
-Second, we fit GLM logistic regression models, computing 95% CI's via bootstrapping, using the R `glmmboot` package created to model outcomes on [0, 1] [@humphrey2020].
+Third, we fit GLM logistic regression models, computing 95% CI's via bootstrapping, using the R `glmmboot` package created to model outcomes on [0, 1] [@humphrey2020].
 Finally, we fit GLM models with the quasibinomial family and logit link using the `glm` function in R stats library.
-The estimated coefficients, standard errors, and confidence intervals produced by the three methods were *very* similar, and often identical.
-We therefore proceeded to fit models using `glm` with the quasibinomilal family and logit link because model objects produced by this function are compatible with numerous other R packages for estimating and plotting effects.
+The estimated coefficients, standard errors, and confidence intervals produced by the latter three methods were *very* similar, and often identical.
+We therefore proceeded to fit and report models using `glm` with the quasibinomilal family and logit link because model objects produced by this function are compatible with numerous other R packages for estimating and plotting effects.
 
@@
 
-1,950 participants started the study by clicking the link to Qualtrics (1,213 American and 737 Indian).
-After removing participants who did not finish the survey, failed attention checks, or moved through the study at an unrealistic pace, our sample dropped to N = 1,240 (937 American and 303 Indian).
-Basic summary statistics on the remaining N = 1,240 participants (Male = 759, Female = 479) can be found in table XX.
+```{r}
+nationT0 <- table(signaling2020$sample)
+removed <- sum(!signaling2020$CompleteSurvey)
+removed_pct <- 100*signif(removed/nrow(signaling2020), 2)
+nationT1 <- table(d$sample)
+sexT1 <- table(d$Sex)
+```
 
-## Summary statistics
+The study was started by N=`r nrow(signaling2020)` participants who clicked the link to Qualtrics (`r nationT0['American']` US and `r nationT0['Indian']` India).
+After removing participants who did not finish the survey, failed attention checks, or moved through the study at an unrealistic pace (N=`r removed`, `r removed_pct`%), our final sample was N = `r nrow(d)` (`r nationT1['American']` US and `r nationT1['Indian']` India), with `r sexT1['Male']` males and `r sexT1['Female']` females.
+For summary statistics, see Table \@ref(tab:sumtab).
 
 ```{r sumtab}
-
-# d$Income <- ifelse(d$CurrencyType == 'USD', d$Income, d$Income*0.014)
 
@@
 Original 0-100 values scaled to 0-1.
-Indian participants reported income in rupees, which we converted to USD at the current exchange rate (1 rupee == 0.014 USD).") %>% kable_styling()
+Indian participants reported income in rupees, which we converted to USD at the current exchange rate (1 rupee = 0.014 USD).") %>% kable_styling()
 ```
@@
 
-Power analyses prior to data collection showed that high proportions of participants scoring extremely high on belief or likelihood of helping at T1 would result in low power for this study's design, a problem which we appeared to largely avoid (word better) (see figure XX).
-
-Although not a part of our pre-registered predictions, both T1Belief and T1Action were highly correlated across the four vignettes (enter correlation coefficients), consistent with help being worth providing if the signaler's claims were true (see figure XX).
+Across the four vignettes, mean belief of the victim was relatively low at baseline (T1), Mean = `r signif(mean(d$T1Belief, na.rm = T), 2)`, albeit with wide variation, SD = `r signif(sd(d$T1Belief, na.rm=T), 2)`; `r sum(d$T1Belief==0)` participants (`r 100*signif(sum(d$T1Belief==0)/nrow(d), 2)`%) rated their belief = 0, and `r sum(d$T1Belief==1)` participants (`r 100*signif(sum(d$T1Belief==1)/nrow(d), 2)`%) rated it as = 1.
+The distribution of likelihood of helping the victim (action) was similar, Mean = `r signif(mean(d$T1Action, na.rm = T), 2)`, SD = `r signif(sd(d$T1Action, na.rm=T), 2)`, with `r sum(d$T1Action==0)` participants (`r 100*signif(sum(d$T1Action==0)/nrow(d), 2)`%) rating their action = 0, and `r sum(d$T1Action==1)` participants (`r 100*signif(sum(d$T1Action==1)/nrow(d), 2)`%) rated action as = 1.
+Although not a pre-registered prediction, T1 Belief and T1 Action were highly correlated across the four vignettes, consistent with help being worth providing if the signaler's claims were true (see Figure \@ref(fig:t1plot)).
 
@@
 Each dot is one participant.
-Original 0-100 values scaled to 0-1.
-Contour lines represent equal densities, estimated using a bivariate normal kernal (Venables and Ripley, 2002).
+Original 0-100 values rescaled to 0-1.
 Lines fit by linear regression.
-Dot size indicates the number of overlapping points."}
+Dot size indicates the number of overlapping points.
+Black cross is the mean of each variable."}
 plot_T1Belief_T1Action
@@
 
-## Effects of signals on beliefs and actions
+## Confirmatory: Effects of signals on beliefs and actions
 
-As a whole, our predictions for the effect of signal cost on belief and likelihood of helping T2 were met, with costlier signals eliciting greater pro-signaler responses (reword).
-There was also support for an interaction between signal and T1Belief or T1Action, although the effect was not large (See figure 2).
-However, the effect of signal cost varied by vignette, with signal type having the greatest effect in the "basketball coach" and "brother-in-law" vignettes.
-When ordered according to cost, the greatest jump in support tended to occur between crying and mild-depression, with the next largest jump tending to occur between depression and suicide attempt.
-Overall, there was little difference between the effect of mild depression and the effect of depression.
+```{r}
+suicide_belief_eff <- signif(models$Margins$m1$AME['signalSuicide attempt']/sd(d$T2Belief), 2)
 
-```{r beliefeffect, fig.width=8, fig.height=8, fig.cap="The effect of the signals on T2 Belief (top) and Action (bottom) controlling for T1 values of Belief and Action, respectively.
-Fit using generalized linear regression models with the quasibinomial family."}
+suicide_action_eff <- signif(models$Margins$m3$AME['signalSuicide attempt']/sd(d$T2Belief), 2)
+```
+
+As predicted, there was a strong statistically significant positive causal effect of the ordinal signal on T2 Belief and Action (controlling for T1 Belief and Action, respectively), with the effect of each signal increasing in the predicted rank order.
+The marginal between-subjects effect of the high cost *Suicide attempt* vs.
+low cost *Verbal request* signal on T2 *Belief* (averaging over all four vignettes and all values of T1 *Belief*) was an increase of `r fmt_margins(models$Margins$m1, 'signalSuicide attempt')` points on the original 0-100 point scale.
+The equivalent increase for T2 *Action* was `r fmt_margins(models$Margins$m3, 'signalSuicide attempt')` points.
+Given that the standard deviations of T2 *Belief* and *Action* are `r signif(sd(100*d$T2Belief), 2)` and `r signif(sd(100*d$T2Action), 2)`, respectively, these increases represent `r suicide_belief_eff` and `r suicide_action_eff` SD increases, respectively.
+
+There was modest evidence for a nonlinear effect of the signals on *Belief* and *Action*, which, based on visual inspection, was probably due to the *Mild depression* and *Depression* signals both having similar large effects compared to *Crying* and *Verbal request*.
+See Figure \@ref(fig:beliefeffect) and model m1 in Tables \@ref(tab:regressiontables) and \@ref(tab:anovatables).
+
+```{r beliefeffect, fig.width=6, fig.height=8, fig.cap="The effect of the signals on T2 Belief (top) and Action (bottom) controlling for T1 values of Belief and Action, respectively.
+Fit using generalized linear regression models with the quasibinomial family.
+For model coefficents, p-values, and other statistics, see Tables \\@ref(tab:regressiontables) and \\@ref(tab:anovatables)."}
 (effectsPlots$m1plot + theme(axis.text.x = element_blank()))/effectsPlots$m3plot + plot_layout(ncol = 1) & theme(plot.margin = unit(c(0,0,0,0), units = 'mm'))
 ```
+
+## Exploratory: effects of signals by vignette
+
+The effects of the signals varied substantially by vignette, with signal type having the greatest effect in the "basketball coach" and "brother-in-law" vignettes.
+Overall, there was little difference between the effect of mild depression and the effect of depression.
 
@@
 
-## The effect of signals on action is largely mediated by belief
+## Confirmatory: The effect of signals on action is largely mediated by belief
 
@@
 
-## Effects of signals on victim's perceived emotional state
+## Exploratory: Effects of signals on victim's perceived emotional state
 
@@
 The sister claims the money is needed for medical treatment for her own child, but she has incentives to deceive.
-The manipulations were signals very similar to those used in this study, and the outcomes were belief that the sister really needed the money and intention to load her the money.
+The manipulations were signals very similar to those used in this study, and the outcomes were belief that the sister really needed the money and intention to loan her the money.
 See XX for the full write-up.
@@
 See http://doi.org/10.5281/zenodo.4637883 for pilot data.
+
+```{r piloteffects, fig.width=10, fig.cap="Pilot study effect of the signals.
+A.
+Effect on Belief at T2, controlling for Belief at T1.
+B: Proportion of participants who inferred the victim was mentally ill."}
+pilot_results$effectplot + (pilot_results$mentalplot + theme(axis.text.y = element_blank())) + plot_annotation(tag_levels = 'A')
+```
 
@@
 #   theme(strip.text.y = element_text(angle=0, hjust=0))
+```
+
+## Socioeconomic distribution
+
+```{r socioeconomic, fig.width=8, fig.cap="Distribution of participants by age, income (USD), and nationality.
+A small number of participants who did not report income, or reported values < $10 USD, were removed from this plot.
+A small amount of jitter was added to reveal overlapping points."}
+
+clrs <- viridisLite::magma(11)[c(4, 8)]
+
+d %>% 
+  dplyr::filter(!is.na(Age), !is.na(Income), Income >= 10) %>% 
+  mutate(
+    Nationality = ifelse(sample == 'American', 'US', 'India'),
+    logIncome = log10(Income)
+  ) %>% 
+  ggplot(aes(Age, logIncome, colour = Nationality)) +
+  geom_jitter(width = 0.5) +
+  geom_hline(yintercept = log10(1670), linetype = 'dotted', colour = clrs[1]) +
+  geom_hline(yintercept = log10(35977), linetype = 'dotted', colour = clrs[2]) +
+  annotate('text', 15, log10(35977), label = 'Median US income', hjust = 1) +
+  annotate('text', 15, log10(1670), label = 'Median India income', hjust = 1) +
+  scale_color_binary() +
+  guides(colour = guide_legend(reverse = T)) +
+  coord_cartesian(clip = 'off') +
+  labs(x = '\nAge (years)', y = 'Log annual\nincome (USD)') +
+  theme_minimal(15) +
+  theme(axis.title.y = element_text(angle = 0, hjust=0))
+
 ```
@@
 
-## Raw beliefs and actions
+## Change in beliefs and actions from T1 to T2
 

### 2021-04-04 R/functions.R

@@ -1,4 +1,55 @@
 
+prep_pilotdata <- function(d){
+
+  var_dict <-
+    c(
+    'Control:Sister' = 'Control',
+    'Schizophrenia:Sister' = 'Schizophrenia',
+    'VerbalRequest:Sister' = 'Verbal request',
+    'Anger:Sister' = 'Anger',
+    'FacialSadnesswithCrying:Sister' = 'Mild depression',
+    'Depression:Sister' = 'Depression',
+    'DepressionwithSuicideThreat:Sister' = 'Depression + Suicide threat',
+    'SuicideAttempt:Sister' = 'Suicide attempt'
+  )
+
+  d %>%
+    mutate(
+      signal = var_dict[signal],
+      signal = factor(signal, levels = var_dict)
+    )
+}
+
+pilotResults <- function(d){
+
+  d <-
+    d %>%
+    mutate(
+      MentallyIll = str_detect(MC2.3, 'Mentally ill')
+    )
+
+  rslts <- list(
+    m_pilot_belief = glm(needsmoneyt2/100 ~ needsmoneyt1 + signal, family = quasibinomial, d),
+    m_pilot_mentallyill = glm(MentallyIll ~ signal, family = binomial, d),
+    meanT1belief = mean(d$needsmoneyt1, na.rm = T),
+    medianT1belief = median(d$needsmoneyt1, na.rm = T)
+  )
+
+  rslts$effectplot <-
+    visreg(rslts$m_pilot_belief, xvar='signal', scale='response', rug=F, gg=T) +
+    labs(title = 'Pilot study results: Belief', x = '', y = '\nT2 Belief') +
+    coord_flip() +
+    theme_bw(15)
+
+  rslts$mentalplot <-
+    visreg(rslts$m_pilot_mentallyill, xvar = 'signal', scale = 'response', rug = F, gg = T) +
+    labs(title = 'Pilot study results: Mentally ill', x = '', y = '\nT2 Mentally ill') +
+    coord_flip() +
+    theme_bw(15)
+
+  return(rslts)
+}
+
 T1Belief_Action_dist <- function(d){
 
   dcor <-
@@ -9,10 +60,16 @@ T1Belief_Action_dist <- function(d){
     ) %>%
     mutate(r = paste('r =', r))
 
+  dmean <-
+    d %>%
+    group_by(vignette) %>%
+    summarise(T1Belief = mean(T1Belief, na.rm = T), T1Action = mean(T1Action, na.rm = T))
+
[…]

### 2021-04-04 _targets.R

@@ -7,7 +7,7 @@ source("R/functions.R")
 
 # Set target-specific options such as packages.
 tar_option_set(
-  packages = c("signalingdata2018", "signaling2020data", "ks", "car", "hagenutils", "visreg", "effects", "glmmboot", "broom", "mediation", "gglm", "gt", "ggforce", "dplyr", "tidyr", "purrr", "ggplot2", "patchwork", "forcats", "stringr"),
+  packages = c("ks", "car", "margins", "hagenutils", "visreg", "effects", "glmmboot", "broom", "mediation", "frm", "gglm", "gt", "ggforce", "dplyr", "tidyr", "purrr", "ggplot2", "patchwork", "forcats", "stringr", "furrr"),
   imports = c("signalingdata2018", "signaling2020data")
   )
 
@@ -16,9 +16,15 @@ list(
 
 # Data preparation --------------------------------------------------------
 
-  tar_target(signalingdata2018, signalingdata2018::signalingdata2018),
+  tar_target(
+    signalingdata2018b,
+    prep_pilotdata(signalingdata2018::signalingdata2018)
+  ),
 
-  tar_target(signaling2020, signaling2020data::signaling2020),
+  tar_target(
+    signaling2020,
+    signaling2020data::signaling2020
+  ),
 
   tar_target(
   d_tmp,
@@ -74,7 +80,14 @@ list(
 
   tar_target(
     power_curve,
-    pwr_curve(signalingdata2018)
+    pwr_curve(signalingdata2018b)
+  ),
+
+# Pilot results -----------------------------------------------------------
+
+  tar_target(
+    pilot_results,
+    pilotResults(signalingdata2018b)
   ),
 
 # Models ------------------------------------------------------------------
@@ -157,15 +170,27 @@ list(
     )
   ),
 
-tar_target(
-  m3b_boot,
-  bootstrap_model(
-    base_model = glm(T2Action ~ T1Action * signal, family = binomial, d),
-    base_data = d,
-    resamples = 999,
-    parallelism = 'parallel'
-  )
-),
+  tar_target(
+    m3b_boot,
+    bootstrap_model(
+      base_model = glm(T2Action ~ T1Action * signal, family = binomial, d),
+      base_data = d,
+      resamples = 999,
+      parallelism = 'parallel'
+    )
+  ),
+
+# Fractional regression models --------------------------------------------
+
+  tar_target(
+    m1_frac,
+    fractional_model(models$Model$m1)
+  ),
+
[…]

### 2021-04-04 Paper.rmd
Resolved merge conflict

--- 2021-04-04 Paper.rmd
@@
 
-The sole treatment in this study was the signal participants saw, with these signals including: (1) a verbal request without additional signaling, (2) crying, (3) mild-depression, (4) depression and, (5) a suicide attempt.
+The sole treatment in this study was the signal participants saw, with these signals including: (1) a verbal request without additional signaling, (2) crying, (3) mild-depression, (4) depression, and (5) a suicide attempt.
 
@@
 The full text for the signals are available in the SI.
+
+## Lessons learned from a pilot study
+
+The current study is a refinement of a vignette-based pilot study (N=`r nrow(signalingdata2018b)`) with very similar signals and outcomes.
+In the pilot study, there was a single vignette in which an imagined sister claims her child needs an expensive emergency medical procedure, and asks for a very large loan.
+We learned five major lessons from the pilot study that influenced the design of the current study.
+First, as predicted, belief in the sister's need was low in the *Verbal request* condition and high in the *Depression* condition, giving us confidence to continue this research (see Figure \@ref(fig:piloteffects)).
+Second, to rule out that believability and willingness to help were simply artifacts of the sister's psychiatric distress, we included a "signaling" condition in which the sister exhibited schizophrenic symptoms.
+As predicted, believability and willingness to help in this condition were dramatically lower than in any other condition, ruling out this alternative explanation.
+We therefore did not replicate the schizophrenic condition in the current study.
+Third, baseline (T1) believability was very high (mean = `r signif(pilot_results$meanT1belief, 2)`, median = `r signif(pilot_results$medianT1belief, 2)` on a 0-100 point scale), leaving little scope for signals to increase believability.
+In the current study we therefore endeavored to provide details in the vignettes that would undermine the victim's believability at baseline.
+Fourth, contrary to our hypothesis, the *Suicide threat* and *Suicide attempt* signals reduced believability relative to *Depression*.
+We surmised that the sister's adversity -- a sick child -- was not sufficient to justify a suicide attempt, thus undermining her believability.
+In the current study the signaler herself is therefore the victim, and the forms of adversity -- physical and sexual assault and thwarted and forced marriage -- are those that are frequently associated with suicidality.
+Fifth, the content of the vignette matters, so instead of a single vignette we decided to use four different vignettes to help determine the extent to which signaling effects were sensitive to seemingly irrelevant details of the vignettes.
 

### 2021-04-05 Paper.rmd
Working on results section

@@
 We learned five major lessons from the pilot study that influenced the design of the current study.
-First, as predicted, belief in the sister's need was low in the *Verbal request* condition and high in the *Depression* condition, giving us confidence to continue this research (see Figure \@ref(fig:piloteffects)).
+First, as predicted, belief in the sister's need was highest in the *Depression* condition and lowest in the *Verbal request* condition, giving us confidence to continue this research (see Figure \@ref(fig:piloteffects)).
 Second, to rule out that believability and willingness to help were simply artifacts of the sister's psychiatric distress, we included a "signaling" condition in which the sister exhibited schizophrenic symptoms.
 As predicted, believability and willingness to help in this condition were dramatically lower than in any other condition, ruling out this alternative explanation.
-We therefore did not replicate the schizophrenic condition in the current study.
-Third, baseline (T1) believability was very high (mean = `r signif(pilot_results$meanT1belief, 2)`, median = `r signif(pilot_results$medianT1belief, 2)` on a 0-100 point scale), leaving little scope for signals to increase believability.
+We therefore did not include the schizophrenic condition in the current study.
+Third, baseline (T1) believability was very high (mean = `r signif(pilot_results$meanT1belief, 2)` and median = `r signif(pilot_results$medianT1belief, 2)` on a 0-100 point scale), leaving little scope for signals to increase believability.
 In the current study we therefore endeavored to provide details in the vignettes that would undermine the victim's believability at baseline.
@@
 ```{r}
+
 suicide_belief_eff <- signif(models$Margins$m1$AME['signalSuicide attempt']/sd(d$T2Belief), 2)
@@
 suicide_action_eff <- signif(models$Margins$m3$AME['signalSuicide attempt']/sd(d$T2Belief), 2)
+
+signal_belief_ttest <- t.test(100*d$T2Belief, 100*d$T1Belief, paired = T)
+signal_action_ttest <- t.test(100*d$T2Action, 100*d$T1Action, paired = T)
+
 ```
@@
 
-```{r beliefeffect, fig.width=6, fig.height=8, fig.cap="The effect of the signals on T2 Belief (top) and Action (bottom) controlling for T1 values of Belief and Action, respectively.
+```{r beliefeffect, fig.width=6, fig.height=8, fig.cap=paste0("The effect of the signals on T2 Belief (top) and Action (bottom) controlling for T1 values of Belief and Action, respectively.
+Effects plotted for T1 values set to their median value (T1Belief=", median(d$T1Belief, na.rm=T), ", T1Action=", median(d$T1Action, na.rm=T), ").
 Fit using generalized linear regression models with the quasibinomial family.
-For model coefficents, p-values, and other statistics, see Tables \\@ref(tab:regressiontables) and \\@ref(tab:anovatables)."}
+For coefficents, p-values, and other statistics, see models m1 and m3 in Tables \\@ref(tab:regressiontables) and \\@ref(tab:anovatables).")}
 (effectsPlots$m1plot + theme(axis.text.x = element_blank()))/effectsPlots$m3plot + plot_layout(ncol = 1) & theme(plot.margin = unit(c(0,0,0,0), units = 'mm'))
@@
 
+Within-subjects, the average effect across all signals on *Belief* at T2 compared to T1 was `r inline_ttest(signal_belief_ttest)`, and on *Action* was `r inline_ttest(signal_action_ttest)` (on the original 0-100 point scale).
+
 ## Exploratory: effects of signals by vignette
 
-The effects of the signals varied substantially by vignette, with signal type having the greatest effect in the "basketball coach" and "brother-in-law" vignettes.
-Overall, there was little difference between the effect of mild depression and the effect of depression.
+```{r}
+
+thwart_sv_bdiff <- visreg_diff(models$Model$m2, 'Thwarted marriage', 'Suicide attempt', 'Verbal request', d)
+
+thwart_sv_adiff <- visreg_diff(models$Model$m4, 'Thwarted marriage', 'Suicide attempt', 'Verbal request', d)
+
+brother_sv_bdiff <- visreg_diff(models$Model$m2, 'Brother-in-law', 'Suicide attempt', 'Verbal request', d)
+
+brother_sv_adiff <- visreg_diff(models$Model$m4, 'Brother-in-law', 'Suicide attempt', 'Verbal request', d)
+
+```
+
+The effects of the signals varied substantially by vignette.
+Signals had the smallest effect in the "Thwarted marriage" vignette, where the effect of the *Suicide attempt* signal on *Belief* and *Action* relative to the *Verbal request* signal was only `r thwart_sv_bdiff` and and `r thwart_sv_adiff` points, respectively (on the original 0-100 point scale).
+Signals had the largest effect in the "Brother-in-law" vignette, where the effect of the *Suicide attempt* signal on *Belief* and *Action* relative to the *Verbal request* signal was `r brother_sv_bdiff` and and `r brother_sv_adiff` points, respectively.
+See Figures \@ref(fig:beliefvignette) and \@ref(fig:ecdf).
+
+```{r}
+bil_b_suicide <- signif(effect_sizes$est[effect_sizes$id=="Suicide attempt,Brother-in-law" & effect_sizes$Outcome=="Belief"], 2)
+
+rom_b_crying <- signif(effect_sizes$est[effect_sizes$id=="Crying,Romantic partner" & effect_sizes$Outcome=="Belief"], 2)
+```
+
+Effect sizes (Cohen's d), between- and within-subjects, reveals a similar pattern.
+The largest between-subjects effect was *Suicide attempt* vs.
+*Verbal request* on *Belief* in the "Brother-in-law" vignette, d = `r bil_b_suicide`, and the smallest was the effect of *Crying* on *Belief* in the "Romantic partner" vignette, d =`r rom_b_crying`.
+
+We note the following patterns, which we will return to in the Discussion section.
+First, as we intended, the distributions of *Belief* and *Action* in the *Verbal request* condition were very similar to their distributions at T1 baseline across vignettes.
+In the "Basketball coach" and "Brother-in-law" vignettes, though, their distributions in the *Verbal request* condition were shifted to somewhat lower values relative to baseline (i.e., the verbal request slightly *reduced* belief and action in those vignettes).
+Second, in the "Romantic partner" and "Brother-in-law" vignettes, the effect of *Crying* differed little from *Verbal request*, but in the "Basketball coach" vignette, it differed little from the *Depression* and *Suicide attempt* signals.
+Third, the effect of the *Suicide attempt* signal on *Belief* was similar to that of *Depression* across all vignettes, but had a noticeably greater effect on *Action* in the "Romantic partner" and "Brother-in-law" vignettes.
+Fourth, there was little difference between the effect of the *Mild depression* vs.
+*Depression* signals.
+See Figures \@ref(fig:beliefvignette) and \@ref(fig:ecdf).
 
 ```{r beliefvignette, fig.width=8, fig.height=8, fig.cap=paste0("The effect of the signals on T2 Belief (top) and Action (bottom) in each vignette, controlling for T1 values of Belief and Action, respectively.
-Effects computed with T1 values set to their median value (T1Belief=", median(d$T1Belief, na.rm=T), ", T1Action=", median(d$T1Action, na.rm=T), ").
-Fit using generalized linear regression models with the quasibinomial family.")}
+Effects plotted for T1 values set to their median value (T1Belief=", median(d$T1Belief, na.rm=T), ", T1Action=", median(d$T1Action, na.rm=T), ").
+Fit using generalized linear regression models with the quasibinomial family.
+For coefficents, p-values, and other statistics, see models m2 and m4 in Tables \\@ref(tab:regressiontables) and \\@ref(tab:anovatables).")}
 (effectsPlots$m2plot + theme(axis.text.x = element_blank()))/effectsPlots$m4plot + plot_layout(ncol = 1) & theme(plot.margin = unit(c(0,0,0,0), units = 'mm'))
@@
 ```
+
+## Exploratory: Demographic associations
 
@@
 
-```{r socioeconomic, fig.width=8, fig.cap="Distribution of participants by age, income (USD), and nationality.
+```{r socioeconomic, fig.width=8, fig.cap="Distribution of participants by age, log income (USD), and nationality.
 A small number of participants who did not report income, or reported values < $10 USD, were removed from this plot.
@@
   ggplot(aes(Age, logIncome, colour = Nationality)) +
-  geom_jitter(width = 0.5) +
+  geom_jitter(width = 0.5, alpha = 0.35) +
   geom_hline(yintercept = log10(1670), linetype = 'dotted', colour = clrs[1]) +
@@
   scale_color_binary() +
-  guides(colour = guide_legend(reverse = T)) +
+  guides(colour = guide_legend(reverse = T, override.aes = list(alpha=1))) +
   coord_cartesian(clip = 'off') +

### 2021-04-05 R/functions.R

@@ -92,7 +92,7 @@ fit_models <- function(data, formulas, family = 'quasibinomial'){
     TidyModel = map(Model, ~tidy(.x, conf.int = T)),
     Anova = map(Model, ~Anova(.x, type = 3)),
     TidyANOVA = map(Anova, ~tidy(.x, conf.int = T)),
-    Margins = map(Model, ~summary(margins(.x, type = 'response')))
+    Margins = map(Model, ~margins(.x, type = 'response'))
   )
 
   names(d$Model) <- d$Name
@@ -103,7 +103,8 @@ fit_models <- function(data, formulas, family = 'quasibinomial'){
   return(d)
 }
 
-fmt_margins <- function(m, var){
+fmt_margins <- function(m, var, by = NULL){
+  m <- summary(m)
   ame <- 100*signif(m[m$factor == var, 'AME'], 2)
   lower <- 100*signif(m[m$factor == var, 'lower'], 2)
   upper <- 100*signif(m[m$factor == var, 'upper'], 2)
@@ -168,7 +169,15 @@ effect_plots <- function(models, data){
       theme(axis.text.x = element_text(angle = 0)) + xlab('\nT2 Action'),
     m27plot = effect_plot(fit=models$m27, xvar='vignette', ylbl='T1 Mentally ill', data=data)
   )
-}#"T2Belief ~ T1Belief + Age + Sex * signal + vignette"
+}
+
+visreg_diff <- function(m, vignette, signal1, signal2, d, sig = 2){
+  obj <- visreg(m, xvar='signal', by = 'vignette', scale='response', data = d, plot = F)
+  fit <- obj$fit
+  v1 <- fit$visregFit[fit$signal==signal1 & fit$vignette==vignette]
+  v2 <- fit$visregFit[fit$signal==signal2 & fit$vignette==vignette]
+  signif(100*(v1 - v2), sig)
+}
 
 signal_mediate <- function(
   data = NULL,

### 2021-04-05 _targets.R

@@ -34,6 +34,7 @@ list(
       id = MTurkID,
       across(.cols = c(contains('Belief'), contains('Action'), contains('Divide')), ~.x/100),
       signal = ordered(signal, levels = c('Verbal request', 'Crying', 'Mild depression', 'Depression', 'Suicide attempt')),
+      vignette = factor(vignette, levels = c('Thwarted marriage', 'Basketball coach', 'Romantic partner', 'Brother-in-law')),
       T1LowMood = T1Depressed + T1Distressed + T1Sad,
       T1Manipulative = T1Devious + T1Jealous,
       T2LowMood = T2Depressed + T2Distressed + T2Sad,

### 2021-04-05 Paper.rmd

@@
 The loss of a loved one, marital problems, bullying, and the existence of abusive relationships are all commonly cited risk factors for depression [@KendlerEtAl1995; @KendlerEtAl1999; @klomek2007; @klomek2019], with  assault (both sexual and non-sexual), in particular, greatly increasing one's risk of depression [@KendlerEtAl1995; @KendlerEtAl1999].
+Among the Tsimane, conflict in general has also been significantly associated with depression, particularly among non-kin [@StieglitzEtAl2015a].
 Other notable risk factors like financial problems, job loss, or severe or prolonged illness, might seem to lack this social element.
-However, the ability for others to provide meaningful support to limit the harm caused by such events [@SugiyamaSugiyama2003] combined with the ubiquity of conflicts of interests mean that many types of problems will become social even if they did not start that way [@Hagen2003)]
-
-As depression is the leading cause of suicide compared to mental disorders (Hagen 2003 (find more direct citation)), it should not be surprising that suicidality also often co-occurs with social adversity.
+However, the ability for others to provide meaningful support to limit the harm caused by such events [@SugiyamaSugiyama2003] combined with the ubiquity of conflicts of interests mean that many types of problems will eventually involve social conflict even if they did not start that way [@Hagen2003)].
+
+As depression is the leading cause of suicide compared to mental disorders [@who2001] (need to find something more recent), it should not be surprising that suicidality also often coincides with social adversity.
 Grief over the loss of a loved one [@firth1936: @Firth:1961; @devries2011], bullying [@alavi2017; @butler2019; @ford2017; @wang2020], and instances of social transgression [@Firth:1961; @Malinowski:1932; @SymeHagen2018; @lester1997] have all been reported to lead to suicidal behavior in both industrialized and traditional societies.
@@
 
-One possible reason for the connection between depression, suicide, and social adversity is that some instances of depression and suicide attempts serve as means to elicit increased support from others in times when an individual cannot solve substantial fitness-relevant challenges on their own.
-Referred to as the bargaining models of depression and suicide, the idea is that the small groups humans lived in for much of our evolutionary history created many situations in which certain forms of cooperation were unlikely to be easily replaced by others while also allowing for harmful or unfair social relationships to develop [@Hagen2003; @Hagen2002; @SymeEtAl2016].
+One possible reason for the connection between depression, suicide, and social adversity is that some instances of depression and suicide attempts serve as means to elicit increased support from others [@andrews2006; @Hagen2002; @Hagen2003; @HagenEtAl2008; @nock2008; @Rosenthal1993; @Stengel1956; @SymeEtAl2016], particularly in times when an individual cannot solve substantial fitness-relevant challenges on their own [@Hagen2003; @SymeEtAl2016].
+According to the bargaining models of depression and suicide, the idea is that the small groups humans lived in for much of our evolutionary history created many situations in which certain forms of cooperation were unlikely to be easily replaced by others while also allowing for harmful or unfair social relationships to develop [@Hagen2003; @SymeEtAl2016].
 In these instances, one's monopoly on one or more types of cooperation could be leveraged to change how one is treated if others valued an individual's cooperation sufficiently.
@@
 
-Distinguishing between the information provided by signals versus cues is a major challenge is a major challenge for signaling approaches to behavior.
+Distinguishing between the information provided by signals versus cues is a major challenge for signaling approaches to behavior.
 A signal differs from a cue in that it is intentionally sent by an organism to alter the behavior or thoughts of other individuals, while a cue is any piece of information an organism uses to alter its behavior or physiological state that was created without the intent to do so [@MaynardSmithHarper1995].
-Regarding the signals of interest, suicide attempts are more likely to take the form of a pure, external signal than depression symptoms.
-This is because behavioral shifts motivated by low mood for non-signaling benefits would convey information as cues in addition to what might exist for signaling purposes.
-In other words, the signaling portion of depression may come from the upregulation of symptoms beyond what would be optimal for non-signaling purposes alone instead of the creation of entirely new symptoms.
-As most suicide attempts likely do not have non-signaling functions (see @deCatanzaro1991 for a possible exception), this is less likely to be a challenge with suicide attempts.
+Regarding the signals of interest, suicide attempts are more likely to take the form of pure, external signals than other symptoms of depression.
+This is because low mood's impact on behavior for non-signaling benefits likely conveys information as cues in addition to what might exist for signaling purposes.
+In other words, the signaling component of depression may come from the upregulation of symptoms beyond what would be optimal for non-signaling purposes rather than the creation of entirely new symptoms.
+Suicidality is likely an exception to this, due to the likelihood most suicide attempts likely do not have non-signaling functions (see @deCatanzaro1991 for a possible exception).
 
@@
 This can take the form of reconciliations in failing relationships, increased fairness in cooperative relationships, or an increase of resources being directed towards an individual.
-Of all the benefits, a reduction in physical abuse may be one of the most important due to the threat of death or severe injury to oneself and one’s family (cite).
+Of all the benefits, a reduction in physical abuse may be one of the most important due to the threat of death or severe injury to oneself and one’s family.
 
@@
 The primary aim of this study was to examine responses to various forms of emotional signaling in an experimental vignette study.
-We predicted that costlier signals would increase the participants' self-reported belief in the signaler's claims and the likelihood of them providing help.
-Specifically, we predicted that the signals will have the following rank order from low to high cost: verbal request, crying, mild-depression, depression, and suicide attempt.
+We predicted that costlier signals would increase the participants' self-reported belief in the signaler's claims and the likelihood of them providing help, with this prediction entailing the following rank from low to high cost: verbal request, crying, mild-depression, depression, and suicide attempt.
 We also predicted that changes in the likelihood participants would provide support would be mediated by changes in the participants' belief in the signaler's need pre-signal to post-signal.
-For the full preregistration, see https://osf.io/4m9wb/.
 
@@
 ## notes: 
-add funding info somewhere
-Find a place for the predictions and preregistration 
 add conclusion
+I cannot knit (works with library targets in chunk starting at line 13). But then i get an error bc I don't have hrafsuicidedata package
 
@@
 
-Those in the Indian sample only saw the "thwarted marriage vignette." In this scenario, the participant and their family is described as trying to arrange a dowry for their older daughter so she can marry the man she loves.
+Those in the Indian sample only saw the "thwarted marriage vignette." In this scenario, the participant and their family is described as trying to arrange a dowry for their older daughter so she can marry a man she already loves.
 After the man's family demands more money, the participant's family tries to find a second man, who the older daughter claims to find unattractive.
-Due to the younger daughter in the story only being two years younger, any additional investment in the dowry will come at the younger daughter's expsense.
+Due to the younger daughter in the story only being two years younger, any additional investment in the dowry will come at the younger daughter's expense.
 
@@
 
-As many depression scales include measures of crying (for discussion on the relationship between crying and depression see @bylsma2020) and depression is a major risk factor for suicide [@BostwickPankratz2000; @Kessler2012], each signal was designed to build off of the less costly signals so that each signal contained elements of any signal it was costlier than.
+As many depression scales include measures of crying [for discussion on the relationship between crying and depression see @bylsma2020] and depression is a major risk factor for suicide [@BostwickPankratz2000; @Kessler2012], each signal was designed to build off of the less costly signals so that each signal contained elements of any signal it was costlier than.
 The full text for the signals are available in the SI.
@@
 Participants for this study were recruited from Amazon Mechanical Turk, a crowdsourcing platform that allows for the creation of Human Intelligence Tasks (HITs) that workers can complete for pay.
-As Amazon provides the infrastructure, it allows for a relatively low-cost way of collecting data for academic research at the cost of the data not being representative of any real population (Thomas and Clifford 2017).
-Despite this limitation, it is more diverse than most convenience samples [@KennedyEtAl2018(2020 now); @DworkinEtAl2016; (Thomas and Clifford 2017)], with turkers in the US mainly differing in being younger, more educated, and lower income than the greater U.S.
-population [@RossEtAl2010]; Boas et al.
-2018).
-Indian samples are also likely to be younger and more educated than the general population but differ from US samples in that they are less diverse, have higher incomes relative to other Indians, and are more likely to come from regions with good internet access (Boas et al.
-2018)
-
-Overall, the quality of data provided by MTurk workers tends to resemble that of university sample pools [@NeckaEtAl2016, Robinson et al.
-2019], with there being some indication that it might outperform university samples due to its previously mentioned diversity (Thomas and Clifford 2017) or the overall attentiveness of turkers [@HauserSchwarz2016].
-For this reason, concerns about data quality come primarily from the threat of bot use or respondents faking their location to take surveys in a language they do not understand well, with there being little evidence of the former [@KennedyEtAl2018] and the risk of the latter able to be minimized through well designed attention checks, timed responses, or general study design (Aguinis et al.
-2020; Huang et al.
-2015; Kennedy et al.
-2020; Thomas and Clifford 2017).
+As Amazon provides the infrastructure, it allows for a relatively low-cost way of collecting data for academic research at the cost of the data not being representative of any real population [@thomas2017].
+Despite this limitation, it is more diverse than most convenience samples [@kennedy2020; @DworkinEtAl2016; @thomas2017], with turkers in the US mainly differing in being younger, more educated, and lower income than the greater U.S.
+population [@RossEtAl2010; @boas2020].
+Indian samples are also likely to be younger and more educated than the general population but differ from US samples in that they are less diverse, have higher incomes relative to other Indians, and are more likely to come from regions with good internet access [@boas2020].
+
+Overall, the quality of data provided by MTurk workers tends to resemble that of university sample pools [@NeckaEtAl2016; @robinson2019], with there being some indication that it might outperform university samples due to its previously mentioned diversity [@thomas2017] or the overall attentiveness of turkers [@HauserSchwarz2016].
+For this reason, concerns about data quality come primarily from the threat of bot use or respondents faking their location to take surveys in a language they do not understand well, with there being little evidence of the former [@kennedy2020] and the risk of the latter able to be minimized through well designed attention checks, timed responses, or general study design [@aguinis2020; @huang2015; @kennedy2020; @thomas2017).
 
@@
 
-All participants in the US sample were over 18, located in the United States, had a HIT approval rate of over 98%, and had successfully completed at least 100 HITs as anything less results in approval rates of 100% [@KennedyEtAl2018].
+All participants in the US sample were over 18, located in the United States, had a HIT approval rate of over 98%, and had successfully completed at least 100 HITs as anything less results in approval rates of 100% [@kennedy2020].
 The Indian sample was the same except for only including participants who resided in India at the time of the study and the inclusion two participants who were included with a stricter HIT approval rate of over 99%.
@@
 We also filtered out those who read the vignette faster than one-third the time it took MG to read it as fast as possible without concern for comprehension.
-This occured immediately after participants finished the vignette.
+This occurred immediately after participants finished the vignette.
 
@@
 Responses were recorded with sliders due to the fact they allow for finer grained changes than categorical scales [@KlimekEtAl2017].
-In every instance the position started at the left due to findings that people may be less likely to move the slider from central starting positions (cite and word better).
+Due to findings that a slider's starting position may bias results [@liu2019], each T1 slider started fully to the left (0) (don't exactly remember the logic for left instead of click to start).
 For the exact wording of the question and the labels on the sliders, see table 1.
@@
 As a final attention check, we presented participants with the T3Action question but included instructions to ignore this and drag the slider all the way to the left (T4AttentionCheck).
-We did not exclude anyone from the study for failing this nor did we withhold payment.
+We did not exclude anyone from the study for failing this nor did we withhold payment due to the time participants had invested in the study at this point.
 
@@
 
-In the "brother-in-law" and "romantic partner" scenarios, there was a noticeable jump in the magnitude of pro-signaler responses when going from the crying to mild depression and then a second, smaller jump from depression to a suicide attempt.
-One potential reason for this is the increase in symptoms from mild depression to depression was not costly enough to result in a large effect as the symptoms only differed in severity (e.g., grades dropping from As to Bs [mild depression] or Cs [depression]).
+In the "brother-in-law" and "romantic partner" scenarios, there was a noticeable increase in the magnitude of pro-signaler responses when going from the crying to mild depression and then a second increase when going from depression to a suicide attempt with the "Action' variable.
+One potential reason for former is the increase in symptoms from mild depression to depression was not costly enough to result in a large effect as the symptoms only differed in severity (e.g., grades dropping from As to Bs [mild depression] or Cs [depression]).
 Such small changes may be less impactful in vignette form than in real-life scenarios in which the effects of signaling may increase in severity and be prolonged over a lengthy period of time.
@@
 
-Our prediction that the effect of signal cost on likelihood of help would largely be mediated by signal's effect on belief in need was also met, as would be expected if the main function of signaling need is a reduction in the amount of private information one has relative to those motivated to care for the signaler (cite).
+Our prediction that the effect of signal cost on likelihood of help would largely be mediated by signal's effect on belief in need was also met, as would be expected if the main function of signaling need is providing trustworthy information about one's internal state to others [@Hagen2003].
 However, there was still a positive main effect of the signal in many pairwise comparisons between the costlier signals and the less costly signals, including the comparison between the depression and verbal request condition (See SI for other mediation models).
@@
 
-Our results on the connection between belief in need and likelihood of help are consistent with the bargaining models of depression and suicide.
+Our results on the connection between belief in need and likelihood of help are consistent with costly signaling and bargaining approaches to depression and suicide.
 In addition to the effect of signal cost on support being largely mediated by the signal's effect on belief in need, belief in need and likelihood of support were highly correlated but distinct at T1 (pre-signal).
 This situation should arise in any instance when a target of a signal of need would benefit from helping if the need was genuine and known to reasonable precision.
-Importantly, such problems are common among humans today (cite) and have likely been so since individuals could increase their inclusive fitness through supporting kin or important cooperative partners in times of need or conflict over acceptable one's contributions joint endeavors (cite).
-
-Although this study was not designed to examine whether the costs of signaling would be made up for by the increased support stemming from depression and suicide attempts directly, the results are suggestive (reword?).
-In general, the costs required to honestly convey one's qualities should be expected to increase with the potential payoffs of deception (cite), with the vignettes in this study emphasizing the existence of private information and sizable conflicts of interest to increase the perceived risk of being taken advantage of.
+Importantly, such problems are common among modern humans and have likely been so since individuals could increase their inclusive fitness through supporting kin or important cooperative partners in times of genuine need [@SugiyamaSugiyama2003; @tooby1996].
+
+Although this study was not designed to examine whether the costs of signaling would be made up for by the increased support stemming from depression and suicide attempts directly, the results are consistent with this hypothesis.
+In general, the costs required to honestly convey one's qualities should be expected to increase with the potential payoffs of deception [@Rosenthal1993], with the vignettes in this study emphasizing the existence of private information and sizable conflicts of interest to increase the perceived risk of being taken advantage of.
 In similar real-world scenarios, this difficulty of signaling honest need would coincide with the substantial fitness-relevant benefits of preventing future assaults or being able to marry the partner of one's choice.
-These benefits coupled with the fact (too strong?) that depression and suicide attempts become relatively less costly with increased need (Hagen 2003), suggest that the increased support seen in this study may be worth the costs required to signal need more often than is often appreciated when counting the entire costs of depression as the signal rather than only the upregulation of symptoms for a communicative purpose.
+These benefits coupled with the fact (too strong?) that depression and suicide attempts become relatively less costly with increased need [@Hagen2003], suggest that the increased support seen in this study may be worth the costs required to signal need more often than is often appreciated when counting the entire costs of depression as the signal rather than only the upregulation of symptoms for a communicative purpose.
 
@@
 It is almost certain that participants experienced this study differently than they would if the event actually happened to them.
-This may have biased results in a pro-signaler direction if the lack of meaningful costs made support feel less costly or if the likely inability of participants to imagine themselves in an anonymous scenario (cite your paper on this) led them to take an opportunity to signal generosity cheaply.
+This may have biased results in a pro-signaler direction if the lack of meaningful costs made support feel less costly or if the likely inability of participants to imagine themselves in an anonymous scenario [@hagen2006] led them to take an opportunity to signal generosity cheaply.
 It may have also biased participants against helping if they could not fully imagine the characters in the story as kin or important cooperative partners, while the survey's short duration may have weakened the strength of the costlier signals as bargaining tools.
@@
 Another limitation is our uncertainty over the data quality from the Indian sample.
-Compared to the US sample, far more participants were filtered out by our attention checks, something which could be consistent with botting, unfamiliarity with English, or low effort responses.
-Assuming this corresponded with lower-quality responses among those who passed the attention checks, the differences seen among those in the thwarted marriage vignette may simply be due to added noise rather than differences in the scenarios or the effectiveness of the signals among Indians compared to Americans.
+Compared to the US sample, far more participants were filtered out by our attention checks, something which could be consistent with botting, unfamiliarity with English, or low effort responses [@kennedy2020].
+Assuming this corresponded with lower-quality responses among those who passed the attention checks, the differences seen among those in the thwarted marriage vignette may simply be due to added noise rather than differences in the scenarios or the effectiveness of the signals among Indians compared to those in the US.
 
 # Conclusion
+
+The need to explain suicide's connection to depression is often overlooked by explanations for major depression, particularly those which propose non-signaling functions.
+One explanation for their connection, is that both suicidality and depression may function to limit negative fitness outcomes in times of substantial adversity [@andrews2006; @Hagen2002; @Hagen2003; @HagenEtAl2008; @nock2008; @Rosenthal1993; @Stengel1956; @SymeEtAl2016], with costlier signals helping elicit support when the payoffs to faking need are high [@Rosenthal199].
+For this hypothesis to be correct, instrumental support would need to be provided frequently enough with large enough impacts so that the costs of signaling are outweighed by the benefits on average.
+Although possible benefits to depressive states are rarely examined, we found exposure to depression and suicide attempts resulted in greater belief in need and increased likelihood of support in fictional scenarios.
+This coupled with findings that depression can be simultaneously aversive and elicit support [@HokansonEtAl1986; @stephens1987], suggests that more attention should be paid to the responses of others to depressed individuals, especially from those the depressed are in conflict with and those with the capability to provide meaningful benefits.
+
+# Acknowledgements
+
+This study was funded through a Washington State University, Vancouver research mini grant.
+
+Who to thank:
+Lab group?
+Arpita?
+Committee? 
+Anne sounds like she will provide a lot of feedback, so her after that?
 

### 2021-04-05 _packages.R
Added more packages to _packages.R and renv.lock

@@ -1,18 +1,31 @@
 # Generated by targets::tar_renv(): do not edit by hand
 library(broom)
+library(bs4Dash)
 library(car)
+library(clustermq)
 library(dplyr)
 library(effects)
 library(forcats)
+library(frm)
+library(furrr)
+library(future)
 library(ggforce)
 library(gglm)
 library(ggplot2)
 library(glmmboot)
 library(gt)
 library(hagenutils)
+library(ks)
+library(margins)
 library(mediation)
+library(patchwork)
+library(pingr)
 library(purrr)
-library(signaling2020data)
+library(rstudioapi)
+library(shiny)
+library(shinycssloaders)
+library(shinyWidgets)
+library(stringr)
 library(tidyr)
 library(visNetwork)
 library(visreg)

### 2021-04-05 Paper.rmd
Minor changes: - Fixed citations - Changed Rosenthal sentence in conclusion

@@
 Unlike many Western countries, where suicide is often viewed as pathological [@Hidaka2012], members of traditional societies have been reported to view suicide attempts as cries for help rather than mental illness [@Shostak1981].
-For example, attempts have been described as ways of escaping unwanted marriage arrangements, persistent abuse, or a lack of support in obtaining mates by those engaging in the behavior and observers [@utierrezdePinedaMuirden1948; @Hilger1957; @arsten1935; @Tessmann1930; @Wilson1960], consistent with the idea that help is at least occasionally provided.
+For example, attempts have been described as ways of escaping unwanted marriage arrangements, persistent abuse, or a lack of support in obtaining mates by those engaging in the behavior and observers [@GutierrezdePinedaMuirden1948; @Hilger1957; @Karsten1935; @Tessmann1930; @Wilson1960], consistent with the idea that help is at least occasionally provided.
 In support of this, 30 out of 84 examples of suicidal behavior included in the HRAF resulted in positive changes for the survivor, even though suicide was rarely if ever the main topic [@SymeEtAl2016].
@@
 The need to explain suicide's connection to depression is often overlooked by explanations for major depression, particularly those which propose non-signaling functions.
-One explanation for their connection, is that both suicidality and depression may function to limit negative fitness outcomes in times of substantial adversity [@andrews2006; @Hagen2002; @Hagen2003; @HagenEtAl2008; @nock2008; @Rosenthal1993; @Stengel1956; @SymeEtAl2016], with costlier signals helping elicit support when the payoffs to faking need are high [@Rosenthal199].
+One explanation for their connection, is that both suicidality and depression may function to limit negative fitness outcomes in times of substantial adversity [@andrews2006; @Hagen2002; @Hagen2003; @HagenEtAl2008; @nock2008; @Rosenthal1993; @Stengel1956; @SymeEtAl2016], with costlier signals being required to elicit support when the payoffs to faking need are high enough so that less costly signals are not reliable indicators of one's need [@Rosenthal1993].
 For this hypothesis to be correct, instrumental support would need to be provided frequently enough with large enough impacts so that the costs of signaling are outweighed by the benefits on average.

### 2021-04-06 Paper.rmd
Tweaking plots and adding refs to plots

@@
 
-Evolutionary theories of depression tend to either ignore suicidality, or take it as evidence that depression is dysfunctional [for reviews of evolutionary theories of depression, see @].
+Evolutionary theories of depression tend to either ignore suicidality, or take it as evidence that depression is dysfunctional.
+Wakefield, for instance, who has devoted much of his career to arguing that most cases of depression are simply severe but normal sadness and grief, nevertheless takes suicidality to indicate pathology for some cases of depression [e.g., @wakefield2017].
+@nettle2004 argues that the costs of depression, including suicidality, outweigh any benefits, and therefore adaptationist models of depression are implausible.
+@gilbert2006 sees suicidality as an example of a dysregulated escape defense [for reviews of evolutionary theories of depression, see @].
 
@@
 
-This study utilized a between-subjects pretest-posttest design to examine how five different emotional signals would influence (1) the degree participants believed a fictional character to be in need (*Belief*) and (2) the likelihood they would provide help (*Action*) in four different vignettes, for a total of 20 conditions.
+This study utilized a between-subjects pretest-posttest design to examine how four different emotional signals would influence (1) the degree participants believed a fictional character to be in need (*Belief*) and (2) the likelihood they would provide help (*Action*) relative to a simple verbal request (the control condition), in four different vignettes, for a total of 20 conditions.
+In this design, the outcomes are measured at pre-treatment (T1), participants are then randomized into either a control group or one or more treatment groups (one of the emotional signals), and the outcomes are measured again (T2).
+Regression models are used to determine the effect of the treatment conditions on the posttest outcome variables, relative to the control condition, controlling for pretest levels of the outcome variables.
+We also explored within-subjects effects of the signal on outcomes at T2 compared to T1.
 
@@
 
-The sole treatment in this study was the signal participants saw, with these signals including: (1) a verbal request without additional signaling, (2) crying, (3) mild-depression, (4) depression, and (5) a suicide attempt.
+The sole randomized treatment in this study was the signal participants saw, with these signals being one of (1) the control condition: a verbal request without additional signaling, (2) crying, (3) mild-depression, (4) depression, and (5) a suicide attempt.
 
@@
 
-Our pre-test and post-test measures, *T1 & T2 Belief* and *T1 & T2 Action*, were all measured on a 0-100 point scale, which we rescaled to 0-1.
-A substantial number of participants rated their beliefs and actions as exactly 0 or exactly 1 at either T1 or T2.
+Our pre-test and post-test measures, *T1 & T2 Belief* and *T1 & T2 Action*, were all measured on a 0-100 point scale.
+A substantial number of participants rated their beliefs and actions as exactly 0 or exactly 100 at either T1 or T2.
 OLS linear regression models are not suitable for a closed and bounded distribution with so many values on the boundary because the residuals would not be normally distributed or have constant variance.
@@
 
-We therefore fit models of our two outcome variables in four ways.
+We therefore fit models of our two outcome variables (which we rescaled to the continuous interval [0, 1]) in four ways.
 First, we fit the preregistered OLS models (reported in the SI).
-Second, we fit fractional regression models, introduced in a seminal paper by @papke1996 for outcomes on [0, 1], which, in brief, involve fitting a quasi-likelihood version of logistic regression with robust standard errors.
+Second, we fit fractional regression models, introduced in a seminal paper by @papke1996 for continuous outcomes on the interval [0, 1], which, in brief, involve fitting a quasi-likelihood version of logistic regression with robust standard errors.
 This method is implemented in the R `frm` package [@ramalho2019].
-Third, we fit GLM logistic regression models, computing 95% CI's via bootstrapping, using the R `glmmboot` package created to model outcomes on [0, 1] [@humphrey2020].
-Finally, we fit GLM models with the quasibinomial family and logit link using the `glm` function in R stats library.
+Third, we fit GLM logistic regression models, computing 95% CI's via bootstrapping, using the R `glmmboot` package created to model continuous outcomes on [0, 1] [@humphrey2020].
+Finally, we fit GLM models with the quasibinomial family and logit link using the `glm` function in R stats library, which can accept continous outcomes on [0, 1].
 The estimated coefficients, standard errors, and confidence intervals produced by the latter three methods were *very* similar, and often identical.
@@
 sexT1 <- table(d$Sex)
+n_cond <- xtabs(~signal+vignette, d)
 ```
@@
 After removing participants who did not finish the survey, failed attention checks, or moved through the study at an unrealistic pace (N=`r removed`, `r removed_pct`%), our final sample was N = `r nrow(d)` (`r nationT1['American']` US and `r nationT1['Indian']` India), with `r sexT1['Male']` males and `r sexT1['Female']` females.
+The median number of participants per condition was `r median(n_cond)` (min=`r min(n_cond)`, max=`r max(n_cond)`).
+For the number of participants in each condition, see Table \@ref(tab:conditions).
 For summary statistics, see Table \@ref(tab:sumtab).
+For the distributions of participants by age, income, and nationality, see Figure \@ref(fig:socioeconomic).
 
@@
 Within-subjects, the average effect across all signals on *Belief* at T2 compared to T1 was `r inline_ttest(signal_belief_ttest)`, and on *Action* was `r inline_ttest(signal_action_ttest)` (on the original 0-100 point scale).
+For the change in *Belief* and *Action* for, T1 to T2 for all participants in all conditions, see Figure \@ref(fig:rawbeliefactions2d).
 
@@
 The effects of the signals varied substantially by vignette.
-Signals had the smallest effect in the "Thwarted marriage" vignette, where the effect of the *Suicide attempt* signal on *Belief* and *Action* relative to the *Verbal request* signal was only `r thwart_sv_bdiff` and and `r thwart_sv_adiff` points, respectively (on the original 0-100 point scale).
+Signals had the smallest effect in the "Thwarted marriage" vignette, where the effect of the *Suicide attempt* signal on *Belief* and *Action* relative to the *Verbal request* signal was only `r thwart_sv_bdiff` and `r thwart_sv_adiff` points, respectively (on the original 0-100 point scale).
 Signals had the largest effect in the "Brother-in-law" vignette, where the effect of the *Suicide attempt* signal on *Belief* and *Action* relative to the *Verbal request* signal was `r brother_sv_bdiff` and and `r brother_sv_adiff` points, respectively.
@@
 rom_b_crying <- signif(effect_sizes$est[effect_sizes$id=="Crying,Romantic partner" & effect_sizes$Outcome=="Belief"], 2)
+
+bil_a_suicide <- signif(effect_sizes2$effsize[effect_sizes2$id=="Suicide attempt,Brother-in-law" & effect_sizes2$Outcome=="Action"], 2)
+
+bil_a_verbal <- signif(effect_sizes2$effsize[effect_sizes2$id=="Verbal request,Brother-in-law" & effect_sizes2$Outcome=="Action"], 2)
+
 ```
@@
 *Verbal request* on *Belief* in the "Brother-in-law" vignette, d = `r bil_b_suicide`, and the smallest was the effect of *Crying* on *Belief* in the "Romantic partner" vignette, d =`r rom_b_crying`.
+The largest within-subjects effect was *Suicide attempt* vs.
+*Verbal request* on *Action* in the "Brother-in-law" vignette, d = `r bil_a_suicide`, and the smallest was the *negative* effect of *Verbal request* on *Action* in the "Brother-in-law" vignette, d =`r bil_a_verbal`.
+See Figures \@ref(fig:effectsizes) and \@ref(fig:effectsizes2).
 
@@
 
-We also examined the effect of signaling on how participants perceived the signaler's emotional state.
-To do this, we created four new variables: LowMood (T1 and T2) and Manipulative (T1 and T2).
-This was done by adding the dummy variables for whether a participant thought the signaler was depressed, distressed or sad for the LowMood variables and by adding the dummy variables for whether they thought the participant was Devious or Jealous for the Manipulative variables.
-For each original emotion variable, 0 indicated a participant did not select the emotion, while 1 indicated selection.
-
-We then plotted the mean change in the LowMood and Manipulative variables seen in the data in addition to the change seen in 500 bootstrap resamples (see figure 6).
-
-```{r emotionsplot, fig.width=10, fig.height=8, fig.cap="The effect of the signals on participants' inferred *manipulative* and *low mood* emotional states of the victim, from T1 (arrow base) to T2 (arrow head), in each of the four vignettes.
+The proportion of participants inferring each emotion in each vignette at T1 is depicted in Figure \@ref(fig:t1emotionheatmap), after each signal at T2 in Figure \@ref(fig:t2emotionheatmap), and the change in proportions from T1 to T2 in Figure \@ref(fig:diffemotions).
+The increase in inferred depression in the *Depression* and *Suicide attempt* conditions, but not the *Verbal request* and *Crying* conditions, helps validate these manipulations, as does the increase in inferred suicidality in the *Suicide attempt* condition.
+
+To further explore the effect of signaling on participants' inferences of the signaler's emotional state, we created four new variables: *Low mood* (T1 and T2) was the sum of the binary variables *Depressed*, *Distressed* and *Sad*; and *Manipulative* (T1 and T2) was the sum of the binary variables *Devious* and *Jealous.* The mean change in the *Low mood* and *Manipulative* variables from T1 to T2 for each signal in each vignette reveals a large decrease in inferred *Manipulation* for costly signals, and a large increase in inferred *Low mood* (with the exception of the Thwarted marriage vignette, in which changes are small).
+See Figure \@ref(fig:emotionsplot)).
+
+```{r emotionsplot, fig.width=10, fig.height=8, fig.cap="The within-subjects effect of the signals on participants' inferred *Manipulative* and *LowMood* emotional states of the victim, from T1 (arrow base) to T2 (arrow head), for each signal in each of the four vignettes.
 Thick arrows: mean change.
@@
 ## Exploratory: Demographic associations
+
+Overall, women participants were more likely to believe and help the victim than men, and younger participants were more likely to believe and help the victim than older participants.
+The caveats are that the sex differences in *Belief* only emerged for the costly signals, the sex differences in *Action* were quite small (but applied across all signals), and the sex and age effects in the Indian sample were non-existent or slightly reversed.
+We found no significant effects of *Income* on *Belief* or *Action* (results not reported).
+See Figures \@ref(fig:demographicsignal), \@ref(fig:demovignettebelief), and \@ref(fig:demovignetteaction).
+
+```{r demographicsignal, fig.width=11, fig.height=8, fig.cap="Demographic effects on *Belief* and *Action*.
+**Top**: Association of age with T2 Belief and Action, controlling for T1 Belief and Action, respectively, and sex and vignette.
+**Bottom, left**: Sex interacting with the effect of the signals on T2 Belief controlling for T1 Belief, age, and vignette.
+**Bottom, right**: Main effect of sex on T2 Action, controlling for T1 Action and age.
+Estimated using generalized linear regression models with the quasibinomial family."}
+# effectsPlots$m24plotAge / effectsPlots$m24plotSex
+
+(effectsPlots$m24plotAge + ylim(0, 1) + effectsPlots$m25plotAge + ylim(0, 1))  / (effectsPlots$m24plotSex + effectsPlots$m25plotSex + plot_layout(widths = c(5,1)))
+
+```
 
@@
 The need to explain suicide's connection to depression is often overlooked by explanations for major depression, particularly those which propose non-signaling functions.
-One explanation for their connection, is that both suicidality and depression may function to limit negative fitness outcomes in times of substantial adversity [@andrews2006; @Hagen2002; @Hagen2003; @HagenEtAl2008; @nock2008; @Rosenthal1993; @Stengel1956; @SymeEtAl2016], with costlier signals being required to elicit support when the payoffs to faking need are high enough so that less costly signals are not reliable indicators of one's need [@Rosenthal1993].
+One explanation for their connection, is that both suicidality and depression may function to limit negative fitness outcomes in times of substantial adversity [@andrews2006; @Hagen2002; @Hagen2003; @HagenEtAl2008; @nock2008; @Rosenthal1993; @Stengel1956; @SymeEtAl2016], with costlier signals helping elicit support when the payoffs to faking need are high [@Rosenthal1993].
 For this hypothesis to be correct, instrumental support would need to be provided frequently enough with large enough impacts so that the costs of signaling are outweighed by the benefits on average.
@@
 A.
-Effect on Belief at T2, controlling for Belief at T1.
-B: Proportion of participants who inferred the victim was mentally ill."}
+Effect of signal on Belief at T2, controlling for Belief at T1.
+B: Proportion of participants who inferred the victim was mentally ill.
+Fit with a generalized linear model with the quasibinomial family."}
 pilot_results$effectplot + (pilot_results$mentalplot + theme(axis.text.y = element_blank())) + plot_annotation(tag_levels = 'A')
@@
 
-```{r effectsizes2, fig.width=10, fig.height=7, fig.cap="Within-subjects Cohen's d (95% CI) for the effect of each signal on Belief and Action in each vignette relative to T1 baseline Belief and  Action, respectively, ranked by effect size."}
+```{r effectsizes, fig.width=10, fig.height=7, fig.cap="Between-subjects Cohen's d (95% CI) for the effect of each signal on Belief and Action in each vignette relative to the Verbal request signal, ranked by effect size."}
 
@@
 }
+
+ggplot(effect_sizes, aes(est, fct_reorder(id, est), xmin=low, xmax=high, colour = signal, shape=Outcome)) +
+  geom_pointrange(position = position_dodge(width = 0.7), lwd = 2.5, fatten = 1, alpha=0.5) +
+  geom_vline(xintercept = 0, linetype = 'dotted') +
+  scale_y_discrete(labels = relbl) +
+  scale_color_manual(name=NULL, values = c('darkblue', 'darkred', 'red', 'orange')) +
+  # scale_color_viridis_d(option='A') +
+  guides(colour = guide_legend(override.aes = list(size = 1)), shape = guide_legend(title=NULL, override.aes = list(size = 1))) +
+  # facet_wrap(~Outcome, ncol=1) +
+  labs(x="\nCohen's d (95% CI)", y=NULL) +
+  theme_minimal(15) +
+  theme(legend.position = 'top')
+```
+
+```{r effectsizes2, fig.width=10, fig.height=7, fig.cap="Within-subjects Cohen's d (95% CI) for the effect of each signal on Belief and Action in each vignette relative to T1 baseline Belief and  Action, respectively, ranked by effect size."}
 
@@
 
-```{r effectsizes, fig.width=10, fig.height=7, fig.cap="Between-subjects Cohen's d (95% CI) for the effect of each signal on Belief and Action in each vignette relative to the Verbal request signal, ranked by effect size."}
-
-ggplot(effect_sizes, aes(est, fct_reorder(id, est), xmin=low, xmax=high, colour = signal, shape=Outcome)) +
-  geom_pointrange(position = position_dodge(width = 0.7), lwd = 2.5, fatten = 1, alpha=0.5) +
-  geom_vline(xintercept = 0, linetype = 'dotted') +
-  scale_y_discrete(labels = relbl) +
-  scale_color_manual(name=NULL, values = c('darkblue', 'darkred', 'red', 'orange')) +
-  # scale_color_viridis_d(option='A') +
-  guides(colour = guide_legend(override.aes = list(size = 1)), shape = guide_legend(title=NULL, override.aes = list(size = 1))) +
-  # facet_wrap(~Outcome, ncol=1) +
-  labs(x="\nCohen's d (95% CI)", y=NULL) +
-  theme_minimal(15) +
-  theme(legend.position = 'top')
-```
-
 ## Demographic effects
-
-```{r demoeffectsbeliefs, fig.width=9, fig.height=8, fig.cap="Demographic effects on Belief.
-**Top**: Association of age with T2 Belief, controlling for T1 Belief, sex, and vignette.
-**Bottom**: Sex interacting with the effect of the signals on T2 Belief controlling for T1 Belief, age, and vignette.
-Estimated using a generalized linear regression model with the quasibinomial family."}
-effectsPlots$m24plotAge / effectsPlots$m24plotSex
-```
 
@@
 Estimated using a generalized linear regression model with the quasibinomial family."}
-effectsPlots$m25plotAge / effectsPlots$m25plotSex
+# effectsPlots$m25plotAge / effectsPlots$m25plotSex
 ```
@@
 Estimated using a generalized linear regression model with the quasibinomial family."}
-effectsPlots$m18plot / effectsPlots$m13plot
+(effectsPlots$m18plot / effectsPlots$m13plot)
 ```

### 2021-04-06 R/functions.R

@@ -215,8 +215,8 @@ emotion_plot <- function(d){
       dplyr::summarise(
         T1LowMood_mean = mean(T1LowMood),
         T1Manipulative_mean = mean(T1Manipulative),
-        T2LowMood_mean = mean(T2LowMood),
-        T2Manipulative_mean = mean(T2Manipulative),
+        T2LowMood_mean = mean(T2LowMood - T1LowMood),
+        T2Manipulative_mean = mean(T2Manipulative - T1Manipulative),
         .groups='drop'
       )
   }
@@ -231,8 +231,8 @@ emotion_plot <- function(d){
   d_boot <- map_df(1:500, boot_emotions)
 
   ggplot() +
-    geom_segment(data = d_boot, aes(x = T1LowMood_mean, y = T1Manipulative_mean, xend = T2LowMood_mean, yend = T2Manipulative_mean, colour=signal), alpha = 0.02, arrow = arrow(length = unit(3, "mm"))) +
-    geom_segment(data = d_full, aes(x = T1LowMood_mean, y = T1Manipulative_mean, xend = T2LowMood_mean, yend = T2Manipulative_mean, colour=signal), alpha = 1, size = 1, arrow = arrow(length = unit(3, "mm"))) +
+    geom_segment(data = d_boot, aes(x = T1LowMood_mean, y = T1Manipulative_mean, xend = T1LowMood_mean + T2LowMood_mean, yend = T1Manipulative_mean + T2Manipulative_mean, colour=signal), alpha = 0.02, arrow = arrow(length = unit(3, "mm"))) +
+    geom_segment(data = d_full, aes(x = T1LowMood_mean, y = T1Manipulative_mean, xend = T1LowMood_mean + T2LowMood_mean, yend = T1Manipulative_mean + T2Manipulative_mean, colour=signal), alpha = 1, size = 1, arrow = arrow(length = unit(3, "mm"))) +
     xlim(0, NA) +
     facet_wrap(~vignette) +
     labs(title = 'Change in mean emotions from T1 to T2', x = '\nLow mood', y = 'Manipulative\n') +

### 2021-04-06 Paper.rmd

@@
 The need to explain suicide's connection to depression is often overlooked by explanations for major depression, particularly those which propose non-signaling functions.
-One explanation for their connection, is that both suicidality and depression may function to limit negative fitness outcomes in times of substantial adversity [@andrews2006; @Hagen2002; @Hagen2003; @HagenEtAl2008; @nock2008; @Rosenthal1993; @Stengel1956; @SymeEtAl2016], with costlier signals helping elicit support when the payoffs to faking need are high [@Rosenthal1993].
+One explanation for their connection, is that both suicidality and depression may function to limit negative fitness outcomes in times of substantial adversity [@andrews2006; @Hagen2002; @Hagen2003; @HagenEtAl2008; @nock2008; @Rosenthal1993; @Stengel1956; @SymeEtAl2016], with costlier signals being required to elicit support when the payoffs to faking need are high enough so that less costly signals are not reliable indicators of one's need [@Rosenthal1993].
 For this hypothesis to be correct, instrumental support would need to be provided frequently enough with large enough impacts so that the costs of signaling are outweighed by the benefits on average.

### 2021-04-08 Paper.rmd
Demographic models now US only (to reduce confounds).
Updated some packages.

@@
     'effectsPlots', 
+    'effectsPlots_US',
+    'effectsPlots_India',
     'ecdf_plot',
@@
 Third, we fit GLM logistic regression models, computing 95% CI's via bootstrapping, using the R `glmmboot` package created to model continuous outcomes on [0, 1] [@humphrey2020].
-Finally, we fit GLM models with the quasibinomial family and logit link using the `glm` function in R stats library, which can accept continous outcomes on [0, 1].
+Finally, we fit GLM models with the quasibinomial family and logit link using the `glm` function in R stats library, which can accept continuous outcomes on [0, 1].
 The estimated coefficients, standard errors, and confidence intervals produced by the latter three methods were *very* similar, and often identical.
-We therefore proceeded to fit and report models using `glm` with the quasibinomilal family and logit link because model objects produced by this function are compatible with numerous other R packages for estimating and plotting effects.
-
-Although two of our four preregistered OLS regression models included an interaction term, the rationale for it was less convincing for quasibinomial models using a logit link, which transforms [0, 1] to (-$\infty$, $\infty$).
-We therefore only included it if there was clear evidence of superior fit.
-Our intervention was *signal*, coded as an ordinal variable with the following preregistered rank order: verbal request, crying, mild depression, depression, suicide attempt.
+We therefore proceeded to fit and report models using `glm` with the quasibinomial family and logit link because model objects produced by this function are compatible with numerous other R packages for estimating and plotting effects.
+
+Although two of our four preregistered OLS regression models included an interaction term, the rationale for it was less convincing for quasibinomial models using a logit link, which maps [0, 1] to (-$\infty$, $\infty$).
+The interaction would also increase the number of parameters to estimate, increasing the risk of overfitting.
+We therefore did not include it in the GLM models (but we still report OLS models with the interaction term).
+
+Our intervention was *signal*, an ordinal variable with the following preregistered rank order: verbal request, crying, mild depression, depression, suicide attempt.
 We used the default `glm` settings, which code such variables as orthogonal polynomial contrasts.
@@
 
-To test our hypothesis that the likelihood of acting to help the victim would be largely mediated by a signal's positive impact on the participant's beleif in the victim's need, we used the `mediation` package [@tingley2014] to fit a mediation model for *Depression* vs.
+To test our hypothesis that the likelihood of acting to help the victim would be largely mediated by a signal's positive impact on the participant's belief in the victim's need, we used the `mediation` package [@tingley2014] to fit a mediation model for *Depression* vs.
 *Verbal request*.
@@
   Income = 'Income (USD)',
+  years_education = 'Education (years)',
   minutes = 'Time to complete (minutes)',
@@
 ```{r}
-
-suicide_belief_eff <- signif(models$Margins$m1$AME['signalSuicide attempt']/sd(d$T2Belief), 2)
-
-suicide_action_eff <- signif(models$Margins$m3$AME['signalSuicide attempt']/sd(d$T2Belief), 2)
+sm1 <- summary(models$Margins$m1)
+suicide_belief_eff <- signif(sm1$AME['signalSuicide attempt']/sd(d$T2Belief), 2)
+
+sm3 <- summary(models$Margins$m3)
+suicide_action_eff <- signif(sm3$AME['signalSuicide attempt']/sd(d$T2Belief), 2)
 
@@
 As predicted, there was a strong statistically significant positive causal effect of the ordinal signal on T2 Belief and Action (controlling for T1 Belief and Action, respectively), with the effect of each signal increasing in the predicted rank order.
+See Figure \@ref(fig:beliefeffect) and models m1 and m3 in Tables \@ref(tab:regressiontables) and \@ref(tab:anovatables).
+
 The marginal between-subjects effect of the high cost *Suicide attempt* vs.
-low cost *Verbal request* signal on T2 *Belief* (averaging over all four vignettes and all values of T1 *Belief*) was an increase of `r fmt_margins(models$Margins$m1, 'signalSuicide attempt')` points on the original 0-100 point scale.
+low cost *Verbal request* control on T2 *Belief* (averaging over all four vignettes and all values of T1 *Belief*) was an increase of `r fmt_margins(models$Margins$m1, 'signalSuicide attempt')` points on the original 0-100 point scale.
 The equivalent increase for T2 *Action* was `r fmt_margins(models$Margins$m3, 'signalSuicide attempt')` points.
-Given that the standard deviations of T2 *Belief* and *Action* are `r signif(sd(100*d$T2Belief), 2)` and `r signif(sd(100*d$T2Action), 2)`, respectively, these increases represent `r suicide_belief_eff` and `r suicide_action_eff` SD increases, respectively.
-
-There was modest evidence for a nonlinear effect of the signals on *Belief* and *Action*, which, based on visual inspection, was probably due to the *Mild depression* and *Depression* signals both having similar large effects compared to *Crying* and *Verbal request*.
-See Figure \@ref(fig:beliefeffect) and model m1 in Tables \@ref(tab:regressiontables) and \@ref(tab:anovatables).
+Given that the standard deviations of T2 *Belief* and *Action* are `r signif(sd(100*d$T2Belief), 2)` and `r signif(sd(100*d$T2Action), 2)`, respectively, these represent increases of `r suicide_belief_eff` and `r suicide_action_eff` SD's, respectively.
 
@@
 We note the following patterns, which we will return to in the Discussion section.
-First, as we intended, the distributions of *Belief* and *Action* in the *Verbal request* condition were very similar to their distributions at T1 baseline across vignettes.
+First, as we intended, the distributions of *Belief* and *Action* in the *Verbal request* control condition were very similar to their distributions at T1 baseline across vignettes.
 In the "Basketball coach" and "Brother-in-law" vignettes, though, their distributions in the *Verbal request* condition were shifted to somewhat lower values relative to baseline (i.e., the verbal request slightly *reduced* belief and action in those vignettes).
@@
 
+The demographic variables were strongly confounded with the Indian sample (younger, lower income, more years of education) vs.
+the US sample (older, higher income, fewer years of education), which, in turn, were confounded with vignette (responses in the Thwarted marriage vignette differed substantially from those in the other vignettes).
+We therefore restricted our exploration of the sociodemographic variables to the US sample.
+
 Overall, women participants were more likely to believe and help the victim than men, and younger participants were more likely to believe and help the victim than older participants.
-The caveats are that the sex differences in *Belief* only emerged for the costly signals, the sex differences in *Action* were quite small (but applied across all signals), and the sex and age effects in the Indian sample were non-existent or slightly reversed.
-We found no significant effects of *Income* on *Belief* or *Action* (results not reported).
+The caveats are that the sex differences in *Belief* only emerged for the costly signals, the sex differences in *Action* were quite small (but applied across all signals).
+We found no significant effects of *Income* or *Education* on *Belief* or *Action* (results not reported).
 See Figures \@ref(fig:demographicsignal), \@ref(fig:demovignettebelief), and \@ref(fig:demovignetteaction).
@@
 
-(effectsPlots$m24plotAge + ylim(0, 1) + effectsPlots$m25plotAge + ylim(0, 1))  / (effectsPlots$m24plotSex + effectsPlots$m25plotSex + plot_layout(widths = c(5,1)))
+(effectsPlots_US$m24plotAge + ylim(0, 1) + effectsPlots_US$m25plotAge + ylim(0, 1))  / (effectsPlots_US$m24plotSex + effectsPlots_US$m25plotSex + plot_layout(widths = c(5,1)))
 
@@
 Estimated using a generalized linear regression model with the quasibinomial family."}
-(effectsPlots$m18plot / effectsPlots$m13plot)
+(effectsPlots_US$m18plot / effectsPlots_US$m13plot)
 ```
@@
 Estimated using a generalized linear regression model with the quasibinomial family."}
-effectsPlots$m19plot / effectsPlots$m15plot
+effectsPlots_US$m19plot / effectsPlots_US$m15plot
 ```

### 2021-04-08 R/functions.R

@@ -148,8 +148,6 @@ effect_plots <- function(models, data){
     m3plot = effect_plot(fit=models$m3, xvar='signal', ylbl='T2 Action', data=data),
     m3bplot = effect_plot(fit=models$m3b, xvar='signal', by='T1Action', ylbl='T2 Action', data=data),
     m4plot = effect_plot(fit=models$m4, xvar='signal', by='vignette', ylbl='T2 Action', data=data),
-    m7plot = effect_plot(fit=models$m7, xvar='signal', by='T1Divide', ylbl='T2 Division', data=data),
-    m8plot = effect_plot(fit=models$m8, xvar='Age', by='signal', ylbl='T2 Division', data=data),
     m12plot = effect_plot(fit=models$m12, xvar='Sex', by='signal', ylbl='T2 Belief', data=data),
     m13plot = effect_plot(fit=models$m13, xvar='Sex', by='vignette', ylbl='T2 Belief', data=data),
     m14plot = effect_plot(fit=models$m14, xvar='Sex', by='signal', ylbl='T2 Action', data=data),
@@ -168,6 +166,13 @@ effect_plots <- function(models, data){
     m26plot = effect_plot(fit=models$m26, xvar='T2Action', by='vignette', ylbl='T3 Action', data=data) +
       theme(axis.text.x = element_text(angle = 0)) + xlab('\nT2 Action'),
     m27plot = effect_plot(fit=models$m27, xvar='vignette', ylbl='T1 Mentally ill', data=data)
+  )
+}
+
+effect_plots_India <- function(models, data){
+  list(
+    m7plot = effect_plot(fit=models$m7, xvar='signal', by='T1Divide', ylbl='T2 Division', data=data),
+    m8plot = effect_plot(fit=models$m8, xvar='Age', by='signal', ylbl='T2 Division', data=data)
   )
 }
 

### 2021-04-08 _targets.R

@@ -1,5 +1,7 @@
 library(targets)
 library(tarchetypes)
+library(future)
+plan(multisession)
 
 # Define custom functions and other global objects.
 
@@ -71,11 +73,17 @@ list(
   ),
 
   tar_target(
-    d_thwarted,
+    d_India,
     d %>%
       dplyr::filter(vignette == 'Thwarted marriage')
   ),
 
+  tar_target(
+    d_US,
+    d %>%
+      dplyr::filter(vignette != 'Thwarted marriage') %>%
+      mutate(vignette = fct_drop(vignette))
+  ),
 
 # Power -------------------------------------------------------------------
 
@@ -104,8 +112,6 @@ list(
       m4 = "T2Action ~ T1Action + signal * vignette",
       m5 = "T3Action ~ T2Action * signal",
       m6 = "T3Action ~ T2Action * vignette + signal",
-      m7 = "T2Divide ~ T1Divide * signal",
-      m8 = "T2Divide ~ T1Divide + Age * signal",
       m9 = "T2Jealous ~ T1Jealous * signal",
       m10 = "T2Devious ~ T1Devious + signal",
       m11 = "T2Angry ~ T1Angry + signal",
@@ -129,8 +135,26 @@ list(
   ),
 
   tar_target(
+    model_formulas_India,
+    c(
+      m7 = "T2Divide ~ T1Divide * signal",
+      m8 = "T2Divide ~ T1Divide + Age * signal"
+    )
+  ),
+
+  tar_target(
     models,
-    fit_models(d, model_formulas, family = 'quasibinomial')
+    fit_models(d, c(model_formulas, model_formulas_India), family = 'quasibinomial')
+  ),
+
+  tar_target(
+    models_US,
+    fit_models(d_US, model_formulas, family = 'quasibinomial')
+  ),
+
+  tar_target(
+    models_India,
+    fit_models(d_India, model_formulas_India, family = 'quasibinomial')
   ),
 
   tar_target(
@@ -200,6 +224,16 @@ list(
     effect_plots(models$Model, d)
   ),
 
+  tar_target(
+    effectsPlots_US,
+    effect_plots(models_US$Model, d_US)
+  ),
+
+  tar_target(
+    effectsPlots_India,
+    effect_plots_India(models_India$Model, d_India)
+  ),
+
 # Mediation models --------------------------------------------------------
 
   tar_target(
@@ -248,7 +282,7 @@ list(
   tar_target(
     med3,
[…]

### 2021-04-08 Paper.rmd
Worked on the discussion - Added discussion about why suicide attempt may have resulted in greater likelihood of action by not belief. This involved merging the main effect and mediation sections in addition to other edits.

@@
 
-## notes: 
-add conclusion
-I cannot knit (works with library targets in chunk starting at line 13). But then i get an error bc I don't have hrafsuicidedata package
-
 ## Design
@@
 In the "basketball coach" vignette, part of the reason for this may have been the lack of relatedness between participants and the alleged victim.
-However, this was still a surprising finding due to the relatively small size of the request (i.e., recommend the coach be suspended rather than kick out family or a romantic partner).
+However, this was still a surprising finding due to the relatively small size of the request (i.e., recommend the coach be suspended rather than kick out family members or a romantic partner).
 With the thwarted marriage vignette, the fact that support came at the cost of one's younger daughter may explain the relatively small effect of signal strength.
 However, data from the Indian sample appears to be of lower quality, limiting our confidence in this interpretation (see limitations for more information).
-
-In the "brother-in-law" and "romantic partner" scenarios, there was a noticeable increase in the magnitude of pro-signaler responses when going from the crying to mild depression and then a second increase when going from depression to a suicide attempt with the "Action' variable.
-One potential reason for former is the increase in symptoms from mild depression to depression was not costly enough to result in a large effect as the symptoms only differed in severity (e.g., grades dropping from As to Bs [mild depression] or Cs [depression]).
+It is also possible that our research in designing the vignettes was insufficient for the population or the content of the vignette.
+
+In the "brother-in-law" and "romantic partner" scenarios, *Crying* had little effect on the magnitude of pro-signaler responses, while both *Depression* conditions increased support to similar degrees.
+One potential reason for this is the increase in symptoms from mild depression to depression was not costly enough to result in a large effect as the symptoms only differed in severity (e.g., grades dropping from As to Bs [mild depression] or Cs [depression]).
 Such small changes may be less impactful in vignette form than in real-life scenarios in which the effects of signaling may increase in severity and be prolonged over a lengthy period of time.
 
-We also found evidence for the predicted interaction between signal and belief in need and likelihood of help at T1, with the pro-signaler effects being larger at intermediate but low levels of believe at T1.
-In real-life scenarios, it would be reasonable to expect that costly-signaling would not be engaged in when others already believe one's need.
-For this reason, too strong of a signal may be seen as manipulative or a cue of dysfunction, and therefore, be responded to aversively.
-However, belief in need and likelihood of help at T2 still remained high when it was high at T1, suggesting that this may not be a significant risk when one is in severe enough need.
-
-## Mediation models
-
-Our prediction that the effect of signal cost on likelihood of help would largely be mediated by signal's effect on belief in need was also met, as would be expected if the main function of signaling need is providing trustworthy information about one's internal state to others [@Hagen2003].
-However, there was still a positive main effect of the signal in many pairwise comparisons between the costlier signals and the less costly signals, including the comparison between the depression and verbal request condition (See SI for other mediation models).
-One possible reason for this is that someone may still be distressed and face real adversity without being forthcoming about one's problems.
-For example, participants who saw the "brother-in-law" vignette may have thought the daughter was lying about the assault due to jealously over her cousin, but the stronger signals may have still conveyed the severity of the competition between her and her cousin in ways words alone could not.
+While the effect of *Suicide attempt* on belief at T2 was similar to the *Depression* conditions, it resulted in greater likelihood of support.
+This may be due to our decision to measure belief in need as the degree participants believed the claims of the signaler (i.e., the assaults or incompatibility with a potential husband in the context of arranged marriage) rather than a more inclusive measure.
+For this reason, signal cost may have provided additional information about the costliness of the signaler's adversity in ways that would still be consistent with signaling theory.
+
+Support for this interpretation comes from our mediation analyses, which showed that the likelihood of help was largely, but not entirely, mediated by signal's effect on belief in need in this study but totally mediated by belief in need when measured as belief in need of financial support in the pilot study.
+However, the incomplete mediation in this study may have arisen if participants viewed the signal as providing information about adveristy outside of the signaler's claims.
+For example, participants who saw the "brother-in-law" vignette may have thought the daughter was lying about the assault due to jealously over her cousin, with the stronger signals still conveying the severity of the competition between her and her cousin.
 
@@
 Our results on the connection between belief in need and likelihood of help are consistent with costly signaling and bargaining approaches to depression and suicide.
-In addition to the effect of signal cost on support being largely mediated by the signal's effect on belief in need, belief in need and likelihood of support were highly correlated but distinct at T1 (pre-signal).
+In addition to the effect of signal cost on support being largely mediated by the signal's effect on belief in need, belief in need and likelihood of support were highly correlated but distinct at T1.
 This situation should arise in any instance when a target of a signal of need would benefit from helping if the need was genuine and known to reasonable precision.
@@
 It may have also biased participants against helping if they could not fully imagine the characters in the story as kin or important cooperative partners, while the survey's short duration may have weakened the strength of the costlier signals as bargaining tools.
-However, the fact that the relationships among signal cost, belief in need, and likelihood of providing support all largely fit existing theory (narrow and broad) indicates that participants paid attention to the relevant details and responded in ways that suggest some degree of external validity.
+However, the fact that the relationships among signal cost, belief in need, and likelihood of providing support all largely fit existing theory (narrow and broad) indicates that participants paid attention to the relevant details and responded in ways that suggest some degree of external validity (needs improvement.
 For this reason, the benefits of addressing causal relationships that came through our experimental vignette approach likely outweighed the costs.
@@
 Anne sounds like she will provide a lot of feedback, so her after that?
+
+# To do:
+- add vignettes to SI
+- mention somewhere referring to them all as signals even though we know they provide info as cues too
 

### 2021-04-08 Paper.rmd
Added line clarifying our use of the term signal in the methods section
Added citations for signals steming from cues.

@@
 As many depression scales include measures of crying [for discussion on the relationship between crying and depression see @bylsma2020] and depression is a major risk factor for suicide [@BostwickPankratz2000; @Kessler2012], each signal was designed to build off of the less costly signals so that each signal contained elements of any signal it was costlier than.
+Although referred to as signals throughout the paper for brevity, we expect that the hypothesized signals of need, like many signals, will also provide information to others in the form of cues [For discussion on the evolution of cues from signals see: @biernaskie2018; @Tiokhin2016; @Steinkopf2015].
 The full text for the signals are available in the SI.

### 2021-04-08 Paper.rmd
Dealing with US vs India separately for demographic

--- 2021-04-08 Paper.rmd
@@
 
-The demographic variables were strongly confounded with the Indian sample (younger, lower income, more years of education) vs.
-the US sample (older, higher income, fewer years of education), which, in turn, were confounded with vignette (responses in the Thwarted marriage vignette differed substantially from those in the other vignettes).
-We therefore restricted our exploration of the sociodemographic variables to the US sample.
-
-Overall, women participants were more likely to believe and help the victim than men, and younger participants were more likely to believe and help the victim than older participants.
-The caveats are that the sex differences in *Belief* only emerged for the costly signals, the sex differences in *Action* were quite small (but applied across all signals).
+The demographic variables were strongly confounded with Nationality (Indian was younger, lower income, with more years of education than the US), which, in turn, was confounded with vignette (responses in the Thwarted marriage vignette differed substantially from those in the other vignettes).
+We therefore conducted our exploration of the sociodemographic variables within Nationalities.
+
+Overall, US women participants were more likely to believe and help the victim than US men, and younger participants were more likely to believe and help the victim than older participants.
+The caveats are that the sex differences in *Belief* only emerged for the costly signals and the sex differences in *Action* were quite small (but applied across all signals).
 We found no significant effects of *Income* or *Education* on *Belief* or *Action* (results not reported).

### 2021-04-08 _targets.R

@@ -115,16 +115,16 @@ list(
       m9 = "T2Jealous ~ T1Jealous * signal",
       m10 = "T2Devious ~ T1Devious + signal",
       m11 = "T2Angry ~ T1Angry + signal",
-      m12 = "T2Belief ~ T1Belief + signal * Sex",
-      m13 = "T2Belief ~ T1Belief + vignette * Sex",
-      m14 = "T2Action ~ T1Action + signal * Sex",
-      m15 = "T2Action ~ T1Action + signal + vignette * Sex",
-      m16 = "T2Belief ~ T1Belief + signal * Age",
-      m17 = "T2Action ~ T1Action + signal * Age",
-      m18 = "T2Belief ~ T1Belief + signal + vignette * Age",
-      m19 = "T2Action ~ T1Action + signal + vignette * Age",
+      m12 = "T2Belief ~ T1Belief + vignette + Age + signal * Sex",
+      m13 = "T2Belief ~ T1Belief + signal + Age + vignette * Sex",
+      m14 = "T2Action ~ T1Action + vignette + Age + signal * Sex",
+      m15 = "T2Action ~ T1Action + signal + + Age + vignette * Sex",
+      m16 = "T2Belief ~ T1Belief + vignette + Sex + signal * Age",
+      m17 = "T2Action ~ T1Action + vignette + Sex + signal * Age",
+      m18 = "T2Belief ~ T1Belief + signal + Sex + vignette * Age",
+      m19 = "T2Action ~ T1Action + signal + Sex + vignette * Age",
       m20 = "T2MentallyIll ~ T1MentallyIll + signal",
-      m21 = "T2MentallyIll ~ T1MentallyIll + signal*vignette",
+      m21 = "T2MentallyIll ~ T1MentallyIll + signal * vignette",
       m22 = "T2Belief ~ T1Belief * signal + PC1emotionT1 + PC2emotionT1",
       m23 = "T2Action ~ T1Action * signal + PC1emotionT1 + PC2emotionT1",
       m24 = "T2Belief ~ T1Belief + Age + Sex * signal + vignette",

### 2021-04-08 _targets.R
Added years_education and income to demographic models

@@ -115,20 +115,34 @@ list(
       m9 = "T2Jealous ~ T1Jealous * signal",
       m10 = "T2Devious ~ T1Devious + signal",
       m11 = "T2Angry ~ T1Angry + signal",
-      m12 = "T2Belief ~ T1Belief + vignette + Age + signal * Sex",
-      m13 = "T2Belief ~ T1Belief + signal + Age + vignette * Sex",
-      m14 = "T2Action ~ T1Action + vignette + Age + signal * Sex",
-      m15 = "T2Action ~ T1Action + signal + + Age + vignette * Sex",
-      m16 = "T2Belief ~ T1Belief + vignette + Sex + signal * Age",
-      m17 = "T2Action ~ T1Action + vignette + Sex + signal * Age",
-      m18 = "T2Belief ~ T1Belief + signal + Sex + vignette * Age",
-      m19 = "T2Action ~ T1Action + signal + Sex + vignette * Age",
+
+      # Demographic models
+      m12 = "T2Belief ~ T1Belief + vignette + signal + years_education + Income + Age + Sex", # Age, sex sig
+      m13 = "T2Action ~ T1Action + signal + vignette + years_education + Income + Age + Sex", # Age, sex sig
+
+      m14 = "T2Belief ~ T1Belief + vignette + Age + years_education + Income + signal * Sex", # Interaction not sig
+      m15 = "T2Action ~ T1Action + vignette + Age + years_education + Income + signal * Sex", # Interaction not sig
+
+      m16 = "T2Belief ~ T1Belief + vignette + Sex + years_education + Income + signal * Age", # Interaction not sig
+      m17 = "T2Action ~ T1Action + vignette + Sex + years_education + Income + signal * Age", # Interaction not sig
+
+      m18 = "T2Belief ~ T1Belief + signal + Age + years_education + Income + vignette * Sex", # Interaction not sig
+      m19 = "T2Action ~ T1Action + signal + Age + years_education + Income + vignette * Sex", # Interaction not sig
+
+      m24 = "T2Belief ~ T1Belief + signal + Sex + years_education + Income + vignette * Age", # Interaction not sig
+      m25 = "T2Action ~ T1Action + signal + Sex + years_education + Income + vignette * Age", # Interaction not sig
+
+      m28 = "T2Belief ~ T1Belief + signal + Age + Income + vignette + years_education * Sex", # Interaction not sig
[…]

### 2021-04-09 Paper.rmd
change one note. Commiting to pull

--- 2021-04-08 Paper.rmd
@@
 # To do:
-- add vignettes to SI
+- add vignettes to SI (Mild depression = crying plus behavior change)
 - mention somewhere referring to them all as signals even though we know they provide info as cues too

### 2021-04-09 Paper.rmd
Working on introduction. - removed text from responses to depression and suicidal behavior - still working on emphasizing conflict in connection to social adversity

@@
 The loss of a loved one, marital problems, bullying, and the existence of abusive relationships are all commonly cited risk factors for depression [@KendlerEtAl1995; @KendlerEtAl1999; @klomek2007; @klomek2019], with  assault (both sexual and non-sexual), in particular, greatly increasing one's risk of depression [@KendlerEtAl1995; @KendlerEtAl1999].
+
+Add conflict here
+Mention anger
+
+Clearly present in some risk factors, conflict is 
 Among the Tsimane, conflict in general has also been significantly associated with depression, particularly among non-kin [@StieglitzEtAl2015a].
 Other notable risk factors like financial problems, job loss, or severe or prolonged illness, might seem to lack this social element.
-However, the ability for others to provide meaningful support to limit the harm caused by such events [@SugiyamaSugiyama2003] combined with the ubiquity of conflicts of interests mean that many types of problems will eventually involve social conflict even if they did not start that way [@Hagen2003)].
+However, the ability for others to provide meaningful support to limit the harm caused in times of need [@SugiyamaSugiyama2003] combined with the ubiquity of conflicts of interests mean that many types of problems will eventually involve social conflict even if they did not start that way [@Hagen2003)].
 
@@
 
-For depression and suicide attempts to be worth the costs involved with signaling, substantial benefits in terms of social support are expected, either in the form of temporary but impactful support or long-term changes in how one is treated [@Hagen2003; @SymeEtAl2016].
-This can take the form of reconciliations in failing relationships, increased fairness in cooperative relationships, or an increase of resources being directed towards an individual.
-Of all the benefits, a reduction in physical abuse may be one of the most important due to the threat of death or severe injury to oneself and one’s family.
-
+For depression and suicide attempts to be worth the costs involved with creating the signal, meaningful social support would be required, either in the form of temporary but impactful support or long-term changes in how one is treated [@Hagen2003; @SymeEtAl2016].
 Most studies examining responses to depression have been observational and focused on responses outside of changes in social support.
@@
 Despite being looked for less frequently, beneficial responses to depressed individuals are also reported.
-This is seen in that depression has been shown to reduce the likelihood of aggression within families [@hops1987; @dadds1992], including those already experiencing high levels of conflict [@SheeberEtAl2001].
+This is seen in that depression has been associated with reduced likelihood of aggression within families [@hops1987; @dadds1992], including those already experiencing high levels of conflict [@SheeberEtAl2001].
 There is also limited evidence that depression can result in increased levels of support from others outside the family.
 For example, non-depressed individuals were shown to be more cooperative and exhibit more caretaking behavior towards their college depressed roommates over the course of their time living together [@HokansonEtAl1986].
-Likewise, a study examining responses to confederates trained to appear ‘depressed’, ‘anxious’, or ‘normal’ found that individuals were more likely to provide advice and support to ‘depressed’ individuals than ‘anxious’ or ‘normal’ individuals despite the confederate in ‘depression’ condition being viewed more negatively than the other conditions and the ‘depression’ condition involving similar levels of distress compared to the ‘anxious’ condition [@stephens1987].
-
-Unfortunately, there are few studies examining how individuals respond to suicide attempt survivors, with the majority examining responses after death.
-In those which exist, stigmatization is commonly reported within and outside families [@FreyEtAl2016; @ScoccoEtAl2012], with perceptions of survivors as being weak, selfish, mentally ill, and antisocial all being commonly reported [@BatterhamEtAl2013; @TzengLipson2004].
-Although these types of stigmatization have been reported across relationships types, the likelihood of stigma has been found to differ based on who the survivor is to the person being questioned.
-This is seen in a study which found that individuals felt the most stigma from members of their preexisting social networks than mental health providers, with family members providing more stigmatization (57.1% of the time) than romantic partners (41.2% of the time) and close friends (28.2% of the time) [@FreyEtAl2016].
-
-Although negative responses to suicide survivors are more often studied and reported, positive responses have also been found.
-Increased social support and changes to important relationships have been reported to follow suicide attempts with some indication that these effects may hold long term [@Stengel1956].
-For example, a study of 100 women who survived suicide attempts found that in 75 cases individuals gained identifiable benefits through the attempt, with 41 individuals benefiting from reconciliations with others [@Lukianowicz1971].
-Unlike many Western countries, where suicide is often viewed as pathological [@Hidaka2012], members of traditional societies have been reported to view suicide attempts as cries for help rather than mental illness [@Shostak1981].
-For example, attempts have been described as ways of escaping unwanted marriage arrangements, persistent abuse, or a lack of support in obtaining mates by those engaging in the behavior and observers [@GutierrezdePinedaMuirden1948; @Hilger1957; @Karsten1935; @Tessmann1930; @Wilson1960], consistent with the idea that help is at least occasionally provided.
-In support of this, 30 out of 84 examples of suicidal behavior included in the HRAF resulted in positive changes for the survivor, even though suicide was rarely if ever the main topic [@SymeEtAl2016].
+Likewise, a study examining responses to confederates trained to appear ‘depressed’, ‘anxious’, or ‘normal’ found that individuals were more likely to provide advice and support to ‘depressed’ individuals than ‘anxious’ or ‘normal’ individuals despite the confederate in the ‘depression’ condition being viewed more negatively than the other conditions and the ‘depression’ condition involving similar levels of distress compared to the ‘anxious’ condition [@stephens1987].
+
+Most studies examining responses to those who have survived suicide attempts have focused on stigmatization.
+In these studies, perceptions of survivors as being weak, selfish, mentally ill, and antisocial are all being commonly reported [@BatterhamEtAl2013; @TzengLipson2004], with stigmatization often being found within and outside one's social network [@FreyEtAl2016; @ScoccoEtAl2012].
+Despite this potential for stigmatization, increased social support and changes to important relationships have been reported to follow suicide attempts with some indication that these effects may hold long term [@Stengel1956].
+For example, a study of 100 women who survived suicide attempts found that individuals gained identifiable benefits through the attempt in 75 cases, with 41 individuals benefiting from reconciliations with others [@Lukianowicz1971].
+Unlike many Western countries, where suicide is often viewed as pathological [@Hidaka2012], members of traditional societies have been reported to view suicide attempts as cries for help rather than mental illness [@Shostak1981], with attempts having been described as ways of escaping unwanted marriage arrangements, persistent abuse, or a lack of support in obtaining mates by those engaging in the behavior and observers [@GutierrezdePinedaMuirden1948; @Hilger1957; @Karsten1935; @Tessmann1930; @Wilson1960].
+Although findings that individuals view suicide attempts as cries for help is not necessarily evidence for them resulting in beneficial responses, 30 out of 84 examples of suicidal behavior included in the HRAF resulted in positive changes for the survivor, even though suicide was rarely if ever the main topic [@SymeEtAl2016].
 

### 2021-04-09 Paper.rmd
Added book chapter to bib manually (Syme and Hagen 2021).
Major introduction edits.

@@
 Likely the most reliable finding regarding depression and suicidality is that most cases are closely tied to major negative life events [@Hammen2005; @Mazure1998; @devries2011; @ellsberg2008].
-Compared to non-depressed individuals, those with depression tend to report at least twice as many instances of negative events than non-depressed individuals [@Mazure1998] and more negative events than those with schizophrenia and bipolar depression across a wide range of studies [@Paykel1994].
-In longitudinal studies, the onset of depression tends to quickly follow the negative event [@KendlerEtAl1999] (search for others) or coincide with periods where conflict is likely to increase prior to it (e.g., depression starting before a divorce rather than after; @rosenstrom2017).
+Compared to non-depressed individuals, those with depression tend to report at least twice as many instances of negative events than non-depressed individuals [@Mazure1998] and more negative events than those with schizophrenia and bipolar depression across multiple studies [@Paykel1994].
+In longitudinal studies, the onset of depression has been reported to quickly follow the negative event [@KendlerEtAl1999] or coincide with periods where conflict is likely to increase prior to it (e.g., depression starting before a divorce rather than after; @rosenstrom2017).
+<!-- look for other longitudinal studies -->
 
@@
 
-Of the types of negative life events associated with depression, those which involve social adversity tend to be more strongly associated with depression [@Hammen2005; @Mazure1998].
-The loss of a loved one, marital problems, bullying, and the existence of abusive relationships are all commonly cited risk factors for depression [@KendlerEtAl1995; @KendlerEtAl1999; @klomek2007; @klomek2019], with  assault (both sexual and non-sexual), in particular, greatly increasing one's risk of depression [@KendlerEtAl1995; @KendlerEtAl1999].
-
-Add conflict here
-Mention anger
-
-Clearly present in some risk factors, conflict is 
-Among the Tsimane, conflict in general has also been significantly associated with depression, particularly among non-kin [@StieglitzEtAl2015a].
-Other notable risk factors like financial problems, job loss, or severe or prolonged illness, might seem to lack this social element.
+Of the types of negative life events associated with depression, those which involve conflict tend to be more strongly associated with depression [@Hammen2005; @Mazure1998].
+Marital problems, bullying, and the existence of abusive relationships are all commonly cited risk factors for depression [@KendlerEtAl1995; @KendlerEtAl1999; @klomek2007; @klomek2019], with  assault (both sexual and non-sexual), in particular, greatly increasing one's risk of depression [@KendlerEtAl1995; @KendlerEtAl1999].
+Other notable risk factors like loss of a loved one, financial problems, job loss, or severe or prolonged illness, might seem less related to conflict.
 However, the ability for others to provide meaningful support to limit the harm caused in times of need [@SugiyamaSugiyama2003] combined with the ubiquity of conflicts of interests mean that many types of problems will eventually involve social conflict even if they did not start that way [@Hagen2003)].
-
-As depression is the leading cause of suicide compared to mental disorders [@who2001] (need to find something more recent), it should not be surprising that suicidality also often coincides with social adversity.
+In line with this reasoning, conflict, in general, was found to be associated with depression among the Tsimane, particularly when it involved non-kin [@StieglitzEtAl2015a].
+
+As depression is the leading cause of suicide compared to mental disorders [@who2001], it should not be surprising that suicidality also often coincides with social adversity and conflict.
 Grief over the loss of a loved one [@firth1936: @Firth:1961; @devries2011], bullying [@alavi2017; @butler2019; @ford2017; @wang2020], and instances of social transgression [@Firth:1961; @Malinowski:1932; @SymeHagen2018; @lester1997] have all been reported to lead to suicidal behavior in both industrialized and traditional societies.
 Of the recorded instances of suicide attempts in the Human Relations Area Files (HRAF), 77.4% of attempts were found to be linked to times of social conflict, 88.7% were linked to fitness threats in general, and 84.9% were linked to situations in which attempters were powerless to resolve their situation alone [@SymeEtAl2016].
-As with depression, assault is an particularly powerful risk factor for suicidal behavior based on multiple large-scale multi-country studies [@devries2011; @ellsberg2008] and more localized examinations.
-For example, both sexual and non-sexual assault were also associated with more self-harm and suicidal behaviors among both indigenous Sami and majority Norwegian adolescents, with those who attempted suicides also reporting more than twice the number of negative life events than those who did not [@reigstad2017].
-
+As with depression, assault is an particularly powerful risk factor for suicidal behavior based on multiple large-scale multi-country studies [@devries2011; @ellsberg2008] and more localized examinations [@reigstad2017].
+<!-- need to find something more recent citation than who2001 -->
 ## Depression and suicide attempts as both signals and bargaining tools
@@
 According to the bargaining models of depression and suicide, the idea is that the small groups humans lived in for much of our evolutionary history created many situations in which certain forms of cooperation were unlikely to be easily replaced by others while also allowing for harmful or unfair social relationships to develop [@Hagen2003; @SymeEtAl2016].
-In these instances, one's monopoly on one or more types of cooperation could be leveraged to change how one is treated if others valued an individual's cooperation sufficiently.
-
-One way this approach expects depression and suicidal behavior to lead to beneficial treatment is through their ability to reliably demonstrate that one’s need is genuine by making one’s private information about their condition public [@Hagen2003].
-This information is necessary due to the ease in which signals can be faked [@Zahavi1975; @mokkonen2016] and the costs of accepting a deceptive signal as reliable [@dawkins1978; @johnstone1993; @Hasson1994], both of which have favored adaptations to spot or ignore fake signals in many species [@dawkins1991].
-
-One way for honest signals to evolve is through costly signaling [@Zahavi1975].
-The evolution of costly signals is possible whenever the signal in question is comparatively cheaper to produce for those who have the underlying quality being compared to those who lack it [@grafen1990].
+In these instances, one's monopoly on one or more types of cooperation could be leveraged to change how one is treated if others valued an individual's cooperation sufficiently and believed them to be in genuine need.
+
+Due to the ease in which signals can be faked [@Zahavi1975; @mokkonen2016] and the costs of accepting a deceptive signal as reliable [@dawkins1978; @johnstone1993; @Hasson1994], demonstrating that one’s need is genuine has likely been a recurrent adaptive problem since humans evolved the capacity to provide instrumental support to one another.
+One possible solution to this is signaling in ways that are unprofitable to fake due to the costs involved.
+[@Zahavi1975].
+This is possible whenever the signal in question is comparatively cheaper to produce for those who have the underlying quality being compared to those who lack it [@grafen1990].
 In these instances, individuals with the quality maximize their fitness at greater levels of investment in the signal compared to those who lack the quality or possess it to a lesser degree [@zahavi1977].
@@
 In the case of depression, the largescale reduction in one's normal routine of fitness enhancing behavior is relatively less costly for those whose situations result in a limited ability to obtain fitness-relevant benefits, with depression likely adding no additional costs in instances of extreme deprivation [@Hagen2003].
-However, when it comes to suicide, the bulk of the costs associated with suicide attempts are only felt in times that result in death or severe bodily harm.
+When it comes to suicide, the bulk of the costs associated with suicide attempts are only felt in times that result in death or severe bodily harm.
 For this reason, the way others view and respond to suicide attempts is likely to be strongly influenced by the probability that the attempt would result in death or severe injury [@Rosenthal1993].
-That given, the previously mentioned logic still applies with increased risk of death being relatively more costly for those able to advance their fitness prospects in their day-to-day lives.
-
-Beyond resulting in the cost differential that allows for costly signaling in the first place, the costs of depression and suicidal behavior may be particularly important in times of conflict or when the level of support needed to address one’s situation is substantial.
-As previously mentioned, there are likely few forms of social adversity that do not come with conflict.
-For example, breakups in both romantic and cooperative relationships are often preceded by conflict [@amato2007], and surely involve conflict when one side wants reconciliation and the other does not.
-Likewise, the death of a loved one may also be a source of conflict as the survivor may turn to others for more support who might not want to invest more in the survivor [@Hagen2003].
-Regardless of the source of conflict, greater conflict should correspond with greater conflicts of interests, something which would favor greater investment in manipulating others through fake signals.
-In these instances, less costly signals like verbal requests, facial sadness, and crying are expected to be less reliable as their low costs can easily be made up for with increased social support, thereby favoring the use of costlier signals in those experiencing need they cannot resolve on their own.
+Despite this difference, the previously mentioned logic still applies with increased risk of death being relatively more costly for those able to advance their fitness prospects in their day-to-day lives.
+
+The costs of depression and suicidal behavior may be particularly important in times of conflict or when the level of support needed to address one’s situation is substantial, both of which should be expected to increase the payoff of manipulating others through fake signals.
+When either condition applies, less costly signals like verbal requests, facial sadness, and crying are likely to be less reliable as their low costs can easily be made up for with increased social support, thereby favoring the use of costlier signals, so long as the costs of signaling are outweighed by the benefits [@SymeHagen2021].
 
@@
 
-For depression and suicide attempts to be worth the costs involved with creating the signal, meaningful social support would be required, either in the form of temporary but impactful support or long-term changes in how one is treated [@Hagen2003; @SymeEtAl2016].
+For depression and suicide attempts to be worth the costs involved with signal creation, meaningful social support would be required, either in the form of temporary but impactful support or long-term changes in how one is treated [@Hagen2003; @SymeEtAl2016].
 Most studies examining responses to depression have been observational and focused on responses outside of changes in social support.

### 2021-04-11 Paper.rmd
Added plot of mediation models of all signals.
Added comparison plot of glm vs. frm vs. glmmboot

Tweaks to code

--- 2021-04-09 Paper.rmd
@@
     'models_prereg',
+    'belief_compare_plot',
+    'action_compare_plot',
     'effect_sizes',
@@
     'med1',
-    'med1b',
-    'med4',
-    'med4b',
+    'med2',
+    'all_mediations',
     'm1_boot',
@@
 
-This study utilized a between-subjects pretest-posttest design to examine how four different emotional signals would influence (1) the degree participants believed a fictional character to be in need (*Belief*) and (2) the likelihood they would provide help (*Action*) relative to a simple verbal request (the control condition), in four different vignettes, for a total of 20 conditions.
+This study utilized a between-subjects pretest-posttest design to examine how four different emotional signals would influence (1) the degree participants believed a fictional character to be in need (*Belief*) and (2) the likelihood they would provide help (*Action*) relative to a simple *Verbal request* (the control condition), in four different vignettes, for a total of 20 conditions.
 In this design, the outcomes are measured at pre-treatment (T1), participants are then randomized into either a control group or one or more treatment groups (one of the emotional signals), and the outcomes are measured again (T2).
@@
 
-We used the pilot data to estimate the sample sizes needed to detect an effect of the *Depression* vs.
-*Verbal request* signal (two conditions) on *Belief* in the victim's need.
+We used the pilot data to estimate the sample sizes needed to detect an effect of the *Depression* signal vs.
+*Verbal request* control (two conditions) on *Belief* in the victim's need.
 Power was about 80% for a sample size of about `r pwr80_90[[2,2]]`, and was about 90% for a sample size of about `r pwr80_90[[2,3]]`.
@@
 Second, we fit fractional regression models, introduced in a seminal paper by @papke1996 for continuous outcomes on the interval [0, 1], which, in brief, involve fitting a quasi-likelihood version of logistic regression with robust standard errors.
-This method is implemented in the R `frm` package [@ramalho2019].
-Third, we fit GLM logistic regression models, computing 95% CI's via bootstrapping, using the R `glmmboot` package created to model continuous outcomes on [0, 1] [@humphrey2020].
-Finally, we fit GLM models with the quasibinomial family and logit link using the `glm` function in R stats library, which can accept continuous outcomes on [0, 1].
-The estimated coefficients, standard errors, and confidence intervals produced by the latter three methods were *very* similar, and often identical.
-We therefore proceeded to fit and report models using `glm` with the quasibinomial family and logit link because model objects produced by this function are compatible with numerous other R packages for estimating and plotting effects.
+This method is implemented in the `frm` package [@ramalho2019].
+Third, we fit GLM logistic regression models, computing 95% CI's via bootstrapping, using the `glmmboot` package created to model continuous outcomes on [0, 1] [@humphrey2020].
+Finally, we fit GLM models with the quasibinomial family and logit link using the `glm` function in R stats library, which can fit continuous outcomes on [0, 1].
+The estimated coefficients, standard errors, and confidence intervals produced by the latter three methods were *very* similar, and often identical (see Figure \@ref(fig:modelcompareplots).
+We therefore proceeded to fit and report models using `glm` with the quasibinomial family and logit link because model objects produced by this function are compatible with numerous other R packages for summarizing and plotting effects.
 
@@
 
-Our intervention was *signal*, an ordinal variable with the following preregistered rank order: verbal request, crying, mild depression, depression, suicide attempt.
+Our intervention was *signal*, an ordinal variable with the following preregistered rank order: verbal request (control), crying, mild depression, depression, suicide attempt.
 We used the default `glm` settings, which code such variables as orthogonal polynomial contrasts.
@@
 
-To test our hypothesis that the likelihood of acting to help the victim would be largely mediated by a signal's positive impact on the participant's belief in the victim's need, we used the `mediation` package [@tingley2014] to fit a mediation model for *Depression* vs.
-*Verbal request*.
+To test our hypothesis that the likelihood of acting to help the victim would be largely mediated by a signal's positive impact on the participant's belief in the victim's need, we used the `mediation` package [@tingley2014] to fit a mediation model for *Depression* treatment vs.
+*Verbal request* control.
 The mediation and outcome models, respectively, were:
@@
 `r extract_eq(med1$model.y, intercept='beta', wrap=T)`
+
+All analyses were conducted using `r R.version.string`.
 
@@
 
-## Confirmatory: Effects of signals on beliefs and actions
+## Confirmatory: Signals increase beliefs and actions in the predicted rank order
 
@@
 
-## Exploratory: effects of signals by vignette
+## Exploratory: Signals effects differ by vignette
 
@@
 ```
-
-The effects of the signals varied substantially by vignette.
-Signals had the smallest effect in the "Thwarted marriage" vignette, where the effect of the *Suicide attempt* signal on *Belief* and *Action* relative to the *Verbal request* signal was only `r thwart_sv_bdiff` and `r thwart_sv_adiff` points, respectively (on the original 0-100 point scale).
-Signals had the largest effect in the "Brother-in-law" vignette, where the effect of the *Suicide attempt* signal on *Belief* and *Action* relative to the *Verbal request* signal was `r brother_sv_bdiff` and and `r brother_sv_adiff` points, respectively.
-See Figures \@ref(fig:beliefvignette) and \@ref(fig:ecdf).
 
@@
 The largest between-subjects effect was *Suicide attempt* vs.
-*Verbal request* on *Belief* in the "Brother-in-law" vignette, d = `r bil_b_suicide`, and the smallest was the effect of *Crying* on *Belief* in the "Romantic partner" vignette, d =`r rom_b_crying`.
-The largest within-subjects effect was *Suicide attempt* vs.
-*Verbal request* on *Action* in the "Brother-in-law" vignette, d = `r bil_a_suicide`, and the smallest was the *negative* effect of *Verbal request* on *Action* in the "Brother-in-law" vignette, d =`r bil_a_verbal`.
+*Verbal request* control on *Belief* in the "Brother-in-law" vignette, d = `r bil_b_suicide`, and the smallest was the effect of *Crying* on *Belief* in the "Romantic partner" vignette, d =`r rom_b_crying`.
+The largest within-subjects effect was *Suicide attempt* on *Action* at T2 vs.
+T1 in the "Brother-in-law" vignette, d = `r bil_a_suicide`, and the smallest was the *negative* effect of *Verbal request* on *Action* at T2 vs.
+T1 in the "Brother-in-law" vignette, d =`r bil_a_verbal`.
 See Figures \@ref(fig:effectsizes) and \@ref(fig:effectsizes2).
@@
 
+```{r medresults}
+rslts <- all_mediations$results
+
+suicidetotal <- 100*signif(rslts$point[rslts$signal == 'Suicide attempt' & rslts$Stat == 'Total'], 2)
+
+suicidemed <- 100*signif(rslts$n.avg[rslts$signal == 'Suicide attempt' & rslts$Stat == 'Total'], 2)
+
+depressiontotal <- 100*signif(rslts$point[rslts$signal == 'Depression' & rslts$Stat == 'Total'], 2)
+
+depressionmed <- 100*signif(rslts$n.avg[rslts$signal == 'Depression' & rslts$Stat == 'Total'], 2)
+
+```
+
 According to our theoretical model, credible signals of need increase observers' belief that the victim is telling the truth.
@@
 
+The total effect of the *Suicide attempt* signal (treatment) vs.
+*Verbal request* (control) on the likelihood of *Action* was to increase it by `r suicidetotal` points from T1 to T2 (on the original 100-point scale).
+Of this increase, `r suicidemed`% was mediated by the increased *Belief* that the victim was telling the truth.
 The total effect of the *Depression* signal (treatment) vs.
-*Verbal request* (control) on the likelihood of *Action* was to increase it by `r 100*signif(med1b$tau.coef, 3)` points from T1 to T2 (on the original 100-point scale).
-Of this increase, `r 100*signif(med1b$n.avg, 2)`% was mediated by the increased *Belief* that the victim was telling the truth.
+*Verbal request* (control) on the likelihood of *Action* was to increase it by `r depressiontotal` points from T1 to T2.
+Of this increase, `r depressionmed`% was mediated by the increased *Belief* that the victim was telling the truth.
 See Figure \@ref(fig:mediation).
-The total effect of the *Suicide attempt* signal (treatment) vs.
-*Verbal request* (control) on the likelihood of *Action* was to increase it by `r 100*signif(med4b$tau.coef, 3)` points from T1 to T2.
-Of this increase, `r 100*signif(med4b$n.avg, 2)`% was mediated by the increased *Belief* that the victim was telling the truth (Check if med4 or med4b is correct; they look identical to me).
-
-```{r mediation, fig.height=4, fig.cap="The effect of Depression (treatment) vs.
-Verbal request (control) on Action (0-1 scale) is largely mediated by Belief.
+
+<!-- (Check if med4 or med4b is correct; they look identical to me). -->
+
+```{r mediation, fig.width=8, fig.height=4, fig.cap="The effect of each signal (treatment) vs.
+Verbal request (control) on Action, [0, 1] scale, is largely mediated by Belief (percent mediated on the right).
+The mediation model controlled for T1 Belief, and the outcome model controlled for T1 Belief and T1 Action.
+Both models were GLMs with the binomial family (the mediation package does not support the quasibinomial family).
 ACME: Average causal mediation effect.
 ADE: Average direct effect.
-The mediation model controlled for T1 Belief, and the outcome model controlled for T1 Belief and T1 Action.
-Both models were GLMs with the binomial family (the mediation package does not support the quasibinomial family)."}
-ggmediation(med1b)
-```
-
-## Exploratory: Effects of signals on victim's perceived emotional state
+Total: Total effect (ADE + ACME)."}
+all_mediations$plot
+```
+
+## Exploratory: Costlier signals decrease perceived manipulation and increase perceived low mood
 
@@
 
-## Exploratory: Demographic associations
-
-The demographic variables were strongly confounded with Nationality (Indian was younger, lower income, with more years of education than the US), which, in turn, was confounded with vignette (responses in the Thwarted marriage vignette differed substantially from those in the other vignettes).
-We therefore conducted our exploration of the sociodemographic variables within Nationalities.
-
-Overall, US women participants were more likely to believe and help the victim than US men, and younger participants were more likely to believe and help the victim than older participants.
-The caveats are that the sex differences in *Belief* only emerged for the costly signals and the sex differences in *Action* were quite small (but applied across all signals).
-We found no significant effects of *Income* or *Education* on *Belief* or *Action* (results not reported).
-See Figures \@ref(fig:demographicsignal), \@ref(fig:demovignettebelief), and \@ref(fig:demovignetteaction).
-
-```{r demographicsignal, fig.width=11, fig.height=8, fig.cap="Demographic effects on *Belief* and *Action*.
-**Top**: Association of age with T2 Belief and Action, controlling for T1 Belief and Action, respectively, and sex and vignette.
-**Bottom, left**: Sex interacting with the effect of the signals on T2 Belief controlling for T1 Belief, age, and vignette.
-**Bottom, right**: Main effect of sex on T2 Action, controlling for T1 Action and age.
+## Exploratory: Sociodemographic associations
+
+The sociodemographic variables were strongly confounded with nationality (Indian participants were younger, lower income, with more years of education than US), which, in turn, were confounded with vignette (responses in the Indian Thwarted marriage vignette differed substantially from those in the US vignettes).
+We therefore conducted our exploration of the sociodemographic variables separately by nationality.
+
+In the US sample, women participants were more likely to believe and help the victim than men, and younger participants were more likely to believe and help the victim than older participants.
+We found no significant effects of *Income* or *Education* on *Belief* or *Action*.
+See Figure \@ref(fig:demographicsignal).
+
+```{r demographicsignal, fig.width=11, fig.height=8, fig.cap="Sociodemographic effects on *Belief* and *Action*.
+**Top**: Association of T2 Belief with Sex (left) and Age (right) controlling for T1 Belief, vignette, Education, and Income.
+**Bottom**: Association of T2 Action with Sex (left) and Age (right) controlling for T1 Action, vignette, Education, and Income.
 Estimated using generalized linear regression models with the quasibinomial family."}
-# effectsPlots$m24plotAge / effectsPlots$m24plotSex
-
-(effectsPlots_US$m24plotAge + ylim(0, 1) + effectsPlots_US$m25plotAge + ylim(0, 1))  / (effectsPlots_US$m24plotSex + effectsPlots_US$m25plotSex + plot_layout(widths = c(5,1)))
-
-```
+
+effectsPlots_US$m12plot + 
+    theme(axis.text.x = element_blank()) +
+effectsPlots_US$m12bplot + 
+    theme(
+      axis.text = element_blank(), 
+      axis.title.y = element_blank(), 
+      axis.title.x = element_blank()
+      ) + 
+effectsPlots_US$m13plot + 
+effectsPlots_US$m13bplot +
+    theme(axis.text.y = element_blank(), axis.title.y = element_blank())
+```
+
+In the Indian sample and vignette, in contrast, men were more likely to help the victim than women, those with more years of education were less likely to believe the victim, and there was a marked increase in likelihood of helping among older individuals in the suicide signal condition.
+We found no significant associations with age or income.
+See Figure \@ref(fig:indiademographics).
+
+```{r indiademographics, fig.width=10, fig.height=8, fig.cap="India participants (Thwarted marriage vignette).
+Sociodemographic associations with T2 Belief and Action.
+Each model included T1 Belief or Action, Income, Age, Sex, Years of education, and signal.
+Significant associations displayed here."}
+(effectsPlots_India$m12plot + xlab('Education (years)') + effectsPlots_India$m13plot) / effectsPlots_India$m17plot
+```
+
+## Validity check: T3 increase in Action with proof that victim was telling the truth
+
+```{r}
+t2t3actionttest <- t.test(d$T3Action, d$T2Action, paired = T)
+```
+
+As a partial check on the validity of our methods and results, at T3 we presented participants with strong evidence that the victim was telling the truth, and asked them to again rate their likelihood of acting to help the victim (T3Action).
+Compared to the mean T2Action (M=`r signif(mean(d$T2Action, na.rm=T), 2)`), mean T3Action increased substantially, `r inline_ttest(t2t3actionttest)`.
+Across the US vignettes, likelihood of acting at T3 increased to near-ceiling, regardless of participants' T2 Action values (M=`r signif(mean(d$T3Action[d$vignette != 'Thwarted marriage']), 2)`), indicating that propensity to act was indeed contingent on believing the victim.
+In the Indian Thwarted marriage vignette, however, there was little change in T3 Action compared to T2 action (Figure \@ref(fig:t3action)), perhaps because Indian participants' beliefs and actions were relatively insensitive to the signals to begin with (Figures \@ref(fig:beliefvignette) and \@ref(fig:ecdf)).
 
@@
 # To do:
-- add vignettes to SI (Mild depression = crying plus behavior change)
+- add vignettes to SI
 - mention somewhere referring to them all as signals even though we know they provide info as cues too
@@
 We estimated power using our pilot study data to compare the effect of the *Depression* signal vs.
-the *Verbal request* signal on *Belief* (that the sister needed the money) at T2 controlling for *Belief* at T1 in a linear regression model.
+the *Verbal request* control on *Belief* (that the sister needed the money) at T2 controlling for *Belief* at T1 in a linear regression model.
 Specifically, we resampled the pilot data with replacement, fit the linear regression model, and extracted the p-value for the signal coefficient, repeating this 2000 times for each sample size ranging from N=20 to N=200.
@@
 Power was about 80% for a sample size of about `r pwr80_90[[2,2]]`, and was about 90% for a sample size of about `r pwr80_90[[2,3]]`.
-We then repeated this entire procedure to compare *Depression* to a *Control* condition that was meant to not include any signaling (but which we realized, post hoc, did include a verbal request).
+We then repeated this entire procedure to compare *Depression* to a *Control* condition in the pilot study that was meant to not include any signaling (but which we realized, post hoc, did include a verbal request, and therefore was not used in the current study).
 Power was about 80% for a sample size of about `r pwr80_90[[1,2]]`, and was about 90% for a sample size of about `r pwr80_90[[1,3]]`.
@@
 
-```{r power, fig.cap="Power curve for between-subjects effect of Depression vs. Verbal request signal on T2 Belief, controlling for T1 Belief."}
+```{r power, fig.cap="Power curve for between-subjects effect of Depression vs.
+Verbal request signal on T2 Belief, controlling for T1 Belief, and Depression vs.
+a Control condition that was unique to the pilot study."}
   ggplot(power_curve, aes(sample_size, power, color=Base)) +
@@
 
-```{r effectsizes, fig.width=10, fig.height=7, fig.cap="Between-subjects Cohen's d (95% CI) for the effect of each signal on Belief and Action in each vignette relative to the Verbal request signal, ranked by effect size."}
+```{r effectsizes, fig.width=10, fig.height=7, fig.cap="Between-subjects Cohen's d (95% CI) for the effect of each signal on Belief and Action in each vignette relative to the Verbal request control condtion, ranked by effect size."}
 
@@
 
-```{r effectsizes2, fig.width=10, fig.height=7, fig.cap="Within-subjects Cohen's d (95% CI) for the effect of each signal on Belief and Action in each vignette relative to T1 baseline Belief and  Action, respectively, ranked by effect size."}
+```{r effectsizes2, fig.width=10, fig.height=7, fig.cap="Within-subjects Cohen's d (95% CI) for the effect of each signal on T2 Belief and Action in each vignette relative to T1 baseline Belief and Action, respectively, ranked by effect size."}
 
@@
 
-## Demographic effects
+<!-- ## Sociodemographic associations -->
 
@@
 Estimated using a generalized linear regression model with the quasibinomial family."}
-(effectsPlots_US$m18plot / effectsPlots_US$m13plot)
+# (effectsPlots_US$m18plot / effectsPlots_US$m13plot)
 ```
@@
 Estimated using a generalized linear regression model with the quasibinomial family."}
-effectsPlots_US$m19plot / effectsPlots_US$m15plot
-```
-
-## Mediation of Suicide attempt signal
+# effectsPlots_US$m19plot / effectsPlots_US$m15plot
+```
+
+## Mediation of Suicide attempt relative to Depression signals
 
 The total effect of the *Suicide attempt* signal (treatment) vs.
-*Verbal request* (control) on the likelihood of *Action* was to increase it by `r 100*signif(med4$tau.coef, 3)` points from T1 to T2 (on the original 100-point scale).
-Of this increase, `r 100*signif(med4$n.avg, 2)`% was mediated by the increased *Belief* that the victim was telling the truth.
+*Depression* (control) on the likelihood of *Action* was to increase it by `r 100*signif(med2$tau.coef, 3)` points from T1 to T2 (on the original 100-point scale).
+Of this increase, `r 100*signif(med2$n.avg, 2)`% was mediated by the increased *Belief* that the victim was telling the truth.
 See Figure \@ref(fig:mediationsuicide).
@@
 ```{r mediationsuicide, fig.height=4, fig.cap="The effect of a Suicide attempt (treatment) vs.
-Verbal request (control) on Action (0-1 scale) is largely mediated by Belief.
+Depression (control) on Action, [0-1 scale], is only partially mediated by Belief.
 ACME: Average causal mediation effect.
@@
 Both models were GLMs with the binomial family (the mediation package does not support the quasibinomial family)."}
-ggmediation(med4)
+ggmediation(med2)
 ```
@@
 Means estimated with a generalized linear regression model with the quasibinomial family."}
-effectsPlots$m7
+effectsPlots_India$m7plot
 ```
@@
 ```{r divisionage, fig.width=9, fig.cap="Interaction of age with signals on T2 Division of dowry between the daughters in the thwarted marriage vignette."}
-effectsPlots$m8
-```
-
-## T3 Action vs. T2 Action
-
-```{r t2action, fig.width=10, fig.cap="The effect of post-signal (T3) information that the victim was telling the truth on the likelihood of acting to help her (T3 Action), controlling for T2 Action."}
+effectsPlots_India$m8plot
+```
+
+## Validity check: T3 Action vs. T2 Action
+
+```{r t3action, fig.width=10, fig.cap="The effect of post-signal (T3) information that the victim was telling the truth on the likelihood of acting to help her (T3 Action), controlling for T2 Action, with a term for the interaction of T2 Action and vignette."}
 effectsPlots$m26plot + theme(panel.spacing = unit(1.5, "lines"))
@@
 ```{r}
-m1b_quasi <- models$TidyModel$m1b
-m1b_diff <- (m1b_boot[,'boot 97.5%'] - m1b_boot[,'boot 2.5%'])/(m1b_quasi$conf.high-m1b_quasi$conf.low)
-
-m3b_quasi <- models$TidyModel$m3b
-m3b_diff <- (m3b_boot[,'boot 97.5%'] - m3b_boot[,'boot 2.5%'])/(m3b_quasi$conf.high-m3b_quasi$conf.low)
-
-diff_sum <- summary(c(m1b_diff, m3b_diff))
+m1_quasi <- models$TidyModel$m1
+m1_diff <- (m1_boot[,'boot 97.5%'] - m1_boot[,'boot 2.5%'])/(m1_quasi$conf.high - m1_quasi$conf.low)
+
+m3_quasi <- models$TidyModel$m3
+m3_diff <- (m3_boot[,'boot 97.5%'] - m3_boot[,'boot 2.5%'])/(m3_quasi$conf.high - m3_quasi$conf.low)
+
+diff_sum <- summary(c(m1_diff, m3_diff))
+```
+
+```{r modelcompareplots, fig.width=11, fig.cap="Comparison of the coefficients and 95% CIs of the quasibinomial glm, fractional, and bootstrapped logistic regression models of T2 Belief and Action (for details, see the Statistical methods section)."}
+
+belief_compare_plot + action_compare_plot + plot_layout(guides = 'collect')
+
 ```

### 2021-04-11 _targets.R

@@ -112,8 +112,8 @@ list(
       m4 = "T2Action ~ T1Action + signal * vignette",
       m5 = "T3Action ~ T2Action * signal",
       m6 = "T3Action ~ T2Action * vignette + signal",
-      m9 = "T2Jealous ~ T1Jealous * signal",
-      m10 = "T2Devious ~ T1Devious + signal",
+      # m9 = "T2Jealous ~ T1Jealous * signal",
+      # m10 = "T2Devious ~ T1Devious + signal",
       m11 = "T2Angry ~ T1Angry + signal",
 
       # Demographic models
@@ -132,18 +132,12 @@ list(
       m24 = "T2Belief ~ T1Belief + signal + Sex + years_education + Income + vignette * Age", # Interaction not sig
       m25 = "T2Action ~ T1Action + signal + Sex + years_education + Income + vignette * Age", # Interaction not sig
 
-      m28 = "T2Belief ~ T1Belief + signal + Age + Income + vignette + years_education * Sex", # Interaction not sig
-      m29 = "T2Action ~ T1Action + signal + Age + Income + vignette + years_education * Sex", # Interaction not sig
-
-      m30 = "T2Belief ~ T1Belief + signal + Sex + Income + vignette + years_education * Age", # Interaction not sig
-      m31 = "T2Action ~ T1Action + signal + Sex + Income + vignette + years_education * Age", # Interaction not sig
-
-            # Misc models
+      # Misc models
       m20 = "T2MentallyIll ~ T1MentallyIll + signal",
       m21 = "T2MentallyIll ~ T1MentallyIll + signal * vignette",
       m22 = "T2Belief ~ T1Belief * signal + PC1emotionT1 + PC2emotionT1",
       m23 = "T2Action ~ T1Action * signal + PC1emotionT1 + PC2emotionT1",
-      m26 = 'T3Action ~ T2Action + vignette',
+      m26 = 'T3Action ~ T2Action * vignette',
       m27 = 'T1MentallyIll ~ vignette'
     )
   ),
@@ -152,7 +146,17 @@ list(
     model_formulas_India,
     c(
       m7 = "T2Divide ~ T1Divide * signal",
-      m8 = "T2Divide ~ T1Divide + Age * signal"
+      m8 = "T2Divide ~ T1Divide + Age * signal",
+
+      # Demographic models
[…]

### 2021-04-11 Paper.rmd

@@
 
-Of the types of negative life events associated with depression, those which involve social adversity tend to be more strongly associated with depression [@Hammen2005; @Mazure1998].
-The loss of a loved one, marital problems, bullying, and the existence of abusive relationships are all commonly cited risk factors for depression [@KendlerEtAl1995; @KendlerEtAl1999; @klomek2007; @klomek2019], with  assault (both sexual and non-sexual), in particular, greatly increasing one's risk of depression [@KendlerEtAl1995; @KendlerEtAl1999].
-Among the Tsimane, conflict in general has also been significantly associated with depression, particularly among non-kin [@StieglitzEtAl2015a].
-Other notable risk factors like financial problems, job loss, or severe or prolonged illness, might seem to lack this social element.
-However, the ability for others to provide meaningful support to limit the harm caused by such events [@SugiyamaSugiyama2003] combined with the ubiquity of conflicts of interests mean that many types of problems will eventually involve social conflict even if they did not start that way [@Hagen2003)].
-
-As depression is the leading cause of suicide compared to mental disorders [@who2001] (need to find something more recent), it should not be surprising that suicidality also often coincides with social adversity.
+Of the types of negative life events associated with depression, those which involve conflict tend to be more strongly associated with depression [@Hammen2005; @Mazure1998].
+Marital problems, bullying, and the existence of abusive relationships are all commonly cited risk factors for depression [@KendlerEtAl1995; @KendlerEtAl1999; @klomek2007; @klomek2019], with  assault (both sexual and non-sexual), in particular, greatly increasing one's risk of depression [@KendlerEtAl1995; @KendlerEtAl1999].
+Other notable risk factors like loss of a loved one, financial problems, job loss, or severe or prolonged illness, might seem less related to conflict.
+However, the ability for others to provide meaningful support to limit the harm caused in times of need [@SugiyamaSugiyama2003] combined with the ubiquity of conflicts of interests mean that many types of problems will eventually involve social conflict even if they did not start that way [@Hagen2003)].
+In line with this reasoning, conflict, in general, was found to be associated with depression among the Tsimane, particularly when it involved non-kin [@StieglitzEtAl2015a].
+
+As depression is the leading cause of suicide compared to mental disorders [@who2001], it should not be surprising that suicidality also often coincides with social adversity and conflict.
 Grief over the loss of a loved one [@firth1936: @Firth:1961; @devries2011], bullying [@alavi2017; @butler2019; @ford2017; @wang2020], and instances of social transgression [@Firth:1961; @Malinowski:1932; @SymeHagen2018; @lester1997] have all been reported to lead to suicidal behavior in both industrialized and traditional societies.
 Of the recorded instances of suicide attempts in the Human Relations Area Files (HRAF), 77.4% of attempts were found to be linked to times of social conflict, 88.7% were linked to fitness threats in general, and 84.9% were linked to situations in which attempters were powerless to resolve their situation alone [@SymeEtAl2016].
-As with depression, assault is an particularly powerful risk factor for suicidal behavior based on multiple large-scale multi-country studies [@devries2011; @ellsberg2008] and more localized examinations.
-For example, both sexual and non-sexual assault were also associated with more self-harm and suicidal behaviors among both indigenous Sami and majority Norwegian adolescents, with those who attempted suicides also reporting more than twice the number of negative life events than those who did not [@reigstad2017].
-
+As with depression, assault is an particularly powerful risk factor for suicidal behavior based on multiple large-scale multi-country studies [@devries2011; @ellsberg2008] and more localized examinations [@reigstad2017].
+<!-- need to find something more recent citation than who2001 -->
 ## Depression and suicide attempts as both signals and bargaining tools
@@
 
-For depression and suicide attempts to be worth the costs involved with signaling, substantial benefits in terms of social support are expected, either in the form of temporary but impactful support or long-term changes in how one is treated [@Hagen2003; @SymeEtAl2016].
-This can take the form of reconciliations in failing relationships, increased fairness in cooperative relationships, or an increase of resources being directed towards an individual.
-Of all the benefits, a reduction in physical abuse may be one of the most important due to the threat of death or severe injury to oneself and one’s family.
-
+For depression and suicide attempts to be worth the costs involved with signal creation, meaningful social support would be required, either in the form of temporary but impactful support or long-term changes in how one is treated [@Hagen2003; @SymeEtAl2016].
 Most studies examining responses to depression have been observational and focused on responses outside of changes in social support.

### 2021-04-11 Paper.rmd
Minor edits throughout the paper

--- 2021-04-09 Paper.rmd
@@
 Alternatively, depression and suicide attempts might be the result of adaptations for reliably signaling need and bargaining for increased support from reluctant others.
-To test this hypothesis, we examined responses to  emotional signals in a vignette study in which the existence of conflicts of interest and private information about one's need were emphasized in four scenarios involving claims of extreme need.
+To test this hypothesis, we examined responses to  emotional signals in a vignette study in which the existence of conflicts of interest and private information about one's need were emphasized in four scenarios involving claims of substantial need.
 Although the effect of signal type varied by vignette, costlier signals like depression and suicide attempts resulted in greater perceptions of need and increased likelihood of support compared to simple verbal requests and crying without further symptoms in our sample of 1,240 participants recruited from Amazon Mechanical Turk.
@@
 One possible reason for the connection between depression, suicide, and social adversity is that some instances of depression and suicide attempts serve as means to elicit increased support from others [@andrews2006; @Hagen2002; @Hagen2003; @HagenEtAl2008; @nock2008; @Rosenthal1993; @Stengel1956; @SymeEtAl2016], particularly in times when an individual cannot solve substantial fitness-relevant challenges on their own [@Hagen2003; @SymeEtAl2016].
-According to the bargaining models of depression and suicide, the idea is that the small groups humans lived in for much of our evolutionary history created many situations in which certain forms of cooperation were unlikely to be easily replaced by others while also allowing for harmful or unfair social relationships to develop [@Hagen2003; @SymeEtAl2016].
+According to the bargaining models of depression and suicide, the small groups humans lived in for much of our evolutionary history created many situations in which certain forms of cooperation were unlikely to be easily replaced by others while also allowing for harmful or unfair social relationships to develop [@Hagen2003; @SymeEtAl2016].
 In these instances, one's monopoly on one or more types of cooperation could be leveraged to change how one is treated if others valued an individual's cooperation sufficiently and believed them to be in genuine need.
@@
 
+<!-- some overalp with my wikipedia article -->
+
 Both depression and suicidal behavior fit this criterion as they are both relatively costly for those not facing adversity than those who are.
@@
 Despite being looked for less frequently, beneficial responses to depressed individuals are also reported.
-This is seen in that depression has been associated with reduced likelihood of aggression within families [@hops1987; @dadds1992], including those already experiencing high levels of conflict [@SheeberEtAl2001].
+Depression has been associated with reduced likelihood of aggression within families [@hops1987; @dadds1992], including those already experiencing high levels of conflict [@SheeberEtAl2001].
 There is also limited evidence that depression can result in increased levels of support from others outside the family.
@@
 Unlike many Western countries, where suicide is often viewed as pathological [@Hidaka2012], members of traditional societies have been reported to view suicide attempts as cries for help rather than mental illness [@Shostak1981], with attempts having been described as ways of escaping unwanted marriage arrangements, persistent abuse, or a lack of support in obtaining mates by those engaging in the behavior and observers [@GutierrezdePinedaMuirden1948; @Hilger1957; @Karsten1935; @Tessmann1930; @Wilson1960].
-Although findings that individuals view suicide attempts as cries for help is not necessarily evidence for them resulting in beneficial responses, 30 out of 84 examples of suicidal behavior included in the HRAF resulted in positive changes for the survivor, even though suicide was rarely if ever the main topic [@SymeEtAl2016].
-
-# Study aims and predictions
+Although findings that individuals view suicide attempts as cries for help is not necessarily evidence for their ability to lead to beneficial responses, 30 out of 84 examples of suicidal behavior included in the HRAF resulted in positive changes for the survivor, even though suicide was rarely if ever the main topic [@SymeEtAl2016].
+
+## Study aims and predictions
 
 The primary aim of this study was to examine responses to various forms of emotional signaling in an experimental vignette study.
-We predicted that costlier signals would increase the participants' self-reported belief in the signaler's claims and the likelihood of them providing help, with this prediction entailing the following rank from low to high cost: verbal request, crying, mild-depression, depression, and suicide attempt.
-We also predicted that changes in the likelihood participants would provide support would be mediated by changes in the participants' belief in the signaler's need pre-signal to post-signal.
+As costlier signals are expected in increase the reliability of the information provided, we predicted that costlier signals would increase self-reported belief in the signaler's claims and the likelihood of participants providing help, with this prediction entailing the following rank from low to high cost: verbal request, crying, mild-depression, depression, and suicide attempt.
+We also predicted that changes in the likelihood participants would provide support would be largely mediated by changes in the participants' belief in the signaler's need pre-signal to post-signal as expected with a costly signaling framework.
 
@@
 As many depression scales include measures of crying [for discussion on the relationship between crying and depression see @bylsma2020] and depression is a major risk factor for suicide [@BostwickPankratz2000; @Kessler2012], each signal was designed to build off of the less costly signals so that each signal contained elements of any signal it was costlier than.
-Although referred to as signals throughout the paper for brevity, we expect that the hypothesized signals of need, like many signals, will also provide information to others in the form of cues [For discussion on the evolution of cues from signals see: @biernaskie2018; @Tiokhin2016; @Steinkopf2015].
+Although referred to as signals throughout the paper for brevity, we expect that the hypothesized signals of need, like many signals, will also provide information to others in the form of cues [for discussion on the evolution of cues from signals see: @biernaskie2018; @Tiokhin2016; @Steinkopf2015].
 The full text for the signals are available in the SI.
@@
 As a final attention check, we presented participants with the T3Action question but included instructions to ignore this and drag the slider all the way to the left (T4AttentionCheck).
-We did not exclude anyone from the study for failing this nor did we withhold payment due to the time participants had invested in the study at this point.
+We did not exclude anyone from the study for failing this nor did we withhold payment.
 
@@
 This may be due to our decision to measure belief in need as the degree participants believed the claims of the signaler (i.e., the assaults or incompatibility with a potential husband in the context of arranged marriage) rather than a more inclusive measure.
-For this reason, signal cost may have provided additional information about the costliness of the signaler's adversity in ways that would still be consistent with signaling theory.
-
-Support for this interpretation comes from our mediation analyses, which showed that the likelihood of help was largely, but not entirely, mediated by signal's effect on belief in need in this study but totally mediated by belief in need when measured as belief in need of financial support in the pilot study.
-However, the incomplete mediation in this study may have arisen if participants viewed the signal as providing information about adveristy outside of the signaler's claims.
+For this reason, signal cost may have provided additional information about the costliness of the signaler's adversity in addition to information relevant to whether the event claimed actually happened.
+
+Support for this interpretation comes from our mediation analyses, which showed that the likelihood of help was largely, but not entirely, mediated by signal's effect on belief in need in this study but totally mediated by belief in need when measured as belief in need of financial support in the pilot study when comparing both depression and suicide attempts (confirm suicide) to verbal requests.
+However, the partial mediation in this study may have also arisen if participants viewed the signal as providing information about adveristy outside of the signaler's claims.
 For example, participants who saw the "brother-in-law" vignette may have thought the daughter was lying about the assault due to jealously over her cousin, with the stronger signals still conveying the severity of the competition between her and her cousin.
@@
 It may have also biased participants against helping if they could not fully imagine the characters in the story as kin or important cooperative partners, while the survey's short duration may have weakened the strength of the costlier signals as bargaining tools.
-However, the fact that the relationships among signal cost, belief in need, and likelihood of providing support all largely fit existing theory (narrow and broad) indicates that participants paid attention to the relevant details and responded in ways that suggest some degree of external validity (needs improvement.
+However, the fact that the relationships among signal cost, belief in need, and likelihood of providing support all largely fit existing theory (narrow and broad) indicates that participants paid attention to the relevant details and responded in ways that suggest some degree of external validity (needs improvement).
 For this reason, the benefits of addressing causal relationships that came through our experimental vignette approach likely outweighed the costs.
@@
 For this hypothesis to be correct, instrumental support would need to be provided frequently enough with large enough impacts so that the costs of signaling are outweighed by the benefits on average.
-Although possible benefits to depressive states are rarely examined, we found exposure to depression and suicide attempts resulted in greater belief in need and increased likelihood of support in fictional scenarios.
-This coupled with findings that depression can be simultaneously aversive and elicit support [@HokansonEtAl1986; @stephens1987], suggests that more attention should be paid to the responses of others to depressed individuals, especially from those the depressed are in conflict with and those with the capability to provide meaningful benefits.
+In support of this, we found exposure to depression and suicide attempts resulted in greater belief in need and increased likelihood of support in fictional scenarios.
+This coupled with findings that depression can simultaneously elicit both positive and negative responses [@HokansonEtAl1986; @stephens1987], suggests that more attention should be paid to the responses of others to depressed individuals, especially from those the depressed are in conflict with and those with the capability to provide meaningful benefits.
 

### 2021-04-11 Paper.rmd
Introduction and methods edits

@@
 Alternatively, depression and suicide attempts might be the result of adaptations for reliably signaling need and bargaining for increased support from reluctant others.
-To test this hypothesis, we examined responses to  emotional signals in a vignette study in which the existence of conflicts of interest and private information about one's need were emphasized in four scenarios involving claims of substantial need.
-Although the effect of signal type varied by vignette, costlier signals like depression and suicide attempts resulted in greater perceptions of need and increased likelihood of support compared to simple verbal requests and crying without further symptoms in our sample of 1,240 participants recruited from Amazon Mechanical Turk.
-Additionally, the effect of signal type on likelihood of support was largely mediated by the effect of signaling on believe in need as predicted.
+To address this hypothesis, we examined responses to emotional signals in an experimental vignette study involving claims of substantial need and the existence of conflicts of interest and private information about whether the signaler was actually in need.
+In our sample of 1,240 participants recruited from Amazon Mechanical Turk, costlier signals like depression and suicide attempts resulted in greater perceptions of need and increased likelihood of support compared to simple verbal requests and crying without further symptoms.
+Additionally, the effect of signal type on likelihood of support was largely mediated by the effect of signaling on belief in need as predicted.
 Our results suggest that depression and suicide attempts, apparent human universals, are a relatively successful way of signaling honest need and eliciting support, consistent with costly signaling explanations.
@@
 This strong connection between negative life events and depression along with the adversity and distress that likely accompanies these events has led to the suggestion that this relationship is causal [@KendlerEtAl1999].
-Support for this comes from the fact that the relationship between negative events and depression holds true when looking solely at events outside of one's control, showing that the connection is unlikely to be driven solely by depressed individuals creating situations where negative events are likely to be common [@Hammen2005; @KendlerEtAl1999].
+Support for this comes from the fact that the relationship between negative events and depression holds true when looking solely at events outside of one's control, showing that the connection is unlikely to be driven solely by individuals who are already depressed creating situations where negative events are likely to be common [@Hammen2005; @KendlerEtAl1999].
 In addition to this, twin studies have shown that one's history of negative events is still a strong predictor of major depression when controlling for genetic similarity and that part of the heritability of depression stems from the heritability of negative events, like divorce and family conflict [@KendlerBaker2007; @KendlerEtAl1999].
@@
 [@Zahavi1975].
-This is possible whenever the signal in question is comparatively cheaper to produce for those who have the underlying quality being compared to those who lack it [@grafen1990].
+This is possible whenever the signal in question is comparatively cheaper to produce for those who have the underlying quality relative to those who lack it [@grafen1990].
 In these instances, individuals with the quality maximize their fitness at greater levels of investment in the signal compared to those who lack the quality or possess it to a lesser degree [@zahavi1977].
@@
 
-<!-- some overalp with my wikipedia article -->
-
-Both depression and suicidal behavior fit this criterion as they are both relatively costly for those not facing adversity than those who are.
-In the case of depression, the largescale reduction in one's normal routine of fitness enhancing behavior is relatively less costly for those whose situations result in a limited ability to obtain fitness-relevant benefits, with depression likely adding no additional costs in instances of extreme deprivation [@Hagen2003].
+<!-- some overlap with my wikipedia article -->
+
+Depression and suicidal behavior fit this criterion as both are relatively costly for those not facing adversity than those who are.
+In the case of depression, the large-scale reduction in one's normal routine of fitness enhancing behavior is relatively less costly for those whose situations result in a limited ability to obtain fitness-relevant benefits, with depression likely adding no additional costs in instances of extreme deprivation [@Hagen2003].
 When it comes to suicide, the bulk of the costs associated with suicide attempts are only felt in times that result in death or severe bodily harm.
@@
 Beyond signaling need to those invested in the well-being of the signaler, depression and suicidal behavior may also help an individual bargain for increased support [@Hagen2003].
-This is possible due to the reduced investment in others that frequently accompanies depression or the threat to future cooperation that comes from a suicide.
-In these instances, depression and suicide attempts are suggested to function analogously to a labor strike, sending the message that one’s need is genuine and that if the target of the signal wanted to continue receiving benefits from the depressed, he or she would need to increase support towards the signaler.
+This is possible due to the reduced investment in others that frequently accompanies depression or the threat to future cooperation that comes from suicide.
+In these instances, depression and suicide attempts may function analogously to a labor strike, sending the message that one’s need is genuine and that if the target of the signal wanted to continue receiving benefits from the depressed, they would need to increase support towards the signaler.
+Due to this bargaining component, aversive responses from the targets of the signal to the signaler are expected throughout the bargaining process, with potential helpers likely signaling the costliness of providing support.
+Importantly, such responses do not prevent the delivery of meaningful benefits, they are simply expected to reduce the risk of helpers providing more support than would benefit them.
+
+<!-- reword this paragraph -->
 
@@
 In other words, the signaling component of depression may come from the upregulation of symptoms beyond what would be optimal for non-signaling purposes rather than the creation of entirely new symptoms.
-Suicidality is likely an exception to this, due to the likelihood most suicide attempts likely do not have non-signaling functions (see @deCatanzaro1991 for a possible exception).
+Suicidality is likely an exception to this, due to the likelihood most suicide attempts likely do not have non-signaling functions [see @deCatanzaro1991 for a possible exception].
 
@@
 
-For depression and suicide attempts to be worth the costs involved with signal creation, meaningful social support would be required, either in the form of temporary but impactful support or long-term changes in how one is treated [@Hagen2003; @SymeEtAl2016].
+For depression and suicide attempts to be worth the costs involved with signal creation, meaningful social support would be required [@Hagen2003; @SymeEtAl2016].
 Most studies examining responses to depression have been observational and focused on responses outside of changes in social support.
@@
 Unlike many Western countries, where suicide is often viewed as pathological [@Hidaka2012], members of traditional societies have been reported to view suicide attempts as cries for help rather than mental illness [@Shostak1981], with attempts having been described as ways of escaping unwanted marriage arrangements, persistent abuse, or a lack of support in obtaining mates by those engaging in the behavior and observers [@GutierrezdePinedaMuirden1948; @Hilger1957; @Karsten1935; @Tessmann1930; @Wilson1960].
-Although findings that individuals view suicide attempts as cries for help is not necessarily evidence for their ability to lead to beneficial responses, 30 out of 84 examples of suicidal behavior included in the HRAF resulted in positive changes for the survivor, even though suicide was rarely if ever the main topic [@SymeEtAl2016].
+Although findings that individuals view suicide attempts as cries for help is not necessarily evidence for their ability to lead to beneficial responses, 30 out of 84 examples of suicidal behavior included in the HRAF resulted in positive changes for the survivor, despite suicide rarely if ever being the main topic [@SymeEtAl2016].
 
@@
 The primary aim of this study was to examine responses to various forms of emotional signaling in an experimental vignette study.
-As costlier signals are expected in increase the reliability of the information provided, we predicted that costlier signals would increase self-reported belief in the signaler's claims and the likelihood of participants providing help, with this prediction entailing the following rank from low to high cost: verbal request, crying, mild-depression, depression, and suicide attempt.
-We also predicted that changes in the likelihood participants would provide support would be largely mediated by changes in the participants' belief in the signaler's need pre-signal to post-signal as expected with a costly signaling framework.
+As the costs of a signal are expected to correspond to the reliability of the information provided, we predicted that costlier signals would (1) increase self-reported belief in the signaler's claims and (2) increase the likelihood of participants providing help, with (3) changes in likelihood of support being largely mediated by changes in the participants' belief in the signaler's need from pre-signal to post-signal.
 
@@
 
-The sole randomized treatment in this study was the signal participants saw, with these signals being one of (1) the control condition: a verbal request without additional signaling, (2) crying, (3) mild-depression, (4) depression, and (5) a suicide attempt.
+The sole randomized treatment in this study was the signal participants saw, with these signals being one of (1) the control condition: a verbal request without additional signaling, (2) crying, (3) mild-depression, (4) depression, and (5) a suicide attempt, with the conditions being ordered from low to high cost.
 
@@
 Responses were recorded with sliders due to the fact they allow for finer grained changes than categorical scales [@KlimekEtAl2017].
-Due to findings that a slider's starting position may bias results [@liu2019], each T1 slider started fully to the left (0) (don't exactly remember the logic for left instead of click to start).
+Based on findings that a slider's starting position may bias results [@liu2019], we had concerns that participants would be less likely to move away from intermediate starting values than they  would be in reality.
+For this reason, we set each T1 slider to start fully to the left (0).
 For the exact wording of the question and the labels on the sliders, see table 1.
@@
 Support for this interpretation comes from our mediation analyses, which showed that the likelihood of help was largely, but not entirely, mediated by signal's effect on belief in need in this study but totally mediated by belief in need when measured as belief in need of financial support in the pilot study when comparing both depression and suicide attempts (confirm suicide) to verbal requests.
-However, the partial mediation in this study may have also arisen if participants viewed the signal as providing information about adveristy outside of the signaler's claims.
+However, the partial mediation in this study may have also arisen if participants viewed the signal as providing information about adversity outside of the signaler's claims.
 For example, participants who saw the "brother-in-law" vignette may have thought the daughter was lying about the assault due to jealously over her cousin, with the stronger signals still conveying the severity of the competition between her and her cousin.
@@
 In support of this, we found exposure to depression and suicide attempts resulted in greater belief in need and increased likelihood of support in fictional scenarios.
-This coupled with findings that depression can simultaneously elicit both positive and negative responses [@HokansonEtAl1986; @stephens1987], suggests that more attention should be paid to the responses of others to depressed individuals, especially from those the depressed are in conflict with and those with the capability to provide meaningful benefits.
+This coupled with findings that depression can simultaneously elicit both positive and negative responses [@HokansonEtAl1986; @stephens1987], suggests that more attention should be paid to the potential for positive responses depressed individuals, especially from those the depressed are in conflict with and those with the capability to provide meaningful benefits.
 

### 2021-04-11 Paper.rmd
Deleted paragraph listing survey flow (felt redundant)

@@
 
-After accepting the HIT on MTurk, every participant took the survey using Qualtrics.
-In every instance, the elements of the survey were laid out in the following order: 1) the consent form, 2) the vowel attention check, 3) the main body of the vignette, 3) the pre-test baseline measures (T1), 4) the story content attention check, 5)  the signal portion of the vignette, 7) the post-test outcome measures (T2-T3), 8) an attention check that did not filter out participants (T4), 9) a set of demographic questions, and 10) an open feedback prompt.
-The full survey can be found in the SI.
-
 ### Baseline measures (T1)

### 2021-04-12 Paper.rmd
Discussion changes - reasonably large

@@
 Other notable risk factors like loss of a loved one, financial problems, job loss, or severe or prolonged illness, might seem less related to conflict.
-However, the ability for others to provide meaningful support to limit the harm caused in times of need [@SugiyamaSugiyama2003] combined with the ubiquity of conflicts of interests mean that many types of problems will eventually involve social conflict even if they did not start that way [@Hagen2003)].
-In line with this reasoning, conflict, in general, was found to be associated with depression among the Tsimane, particularly when it involved non-kin [@StieglitzEtAl2015a].
+However, the ability for others to provide meaningful support to limit the harm caused in times of need [@SugiyamaSugiyama2003] combined with the ubiquity of conflicts of interests mean that many types of problems will eventually involve social conflict even if they did not start that way [@Hagen2003].
+In line with this reasoning, conflict, as a whole, was found to be associated with depression among the Tsimane, particularly when it involved non-kin [@StieglitzEtAl2015a].
 
@@
 [@Zahavi1975].
-This is possible whenever the signal in question is comparatively cheaper to produce for those who have the underlying quality relative to those who lack it [@grafen1990].
+This is possible whenever the signal in question is comparatively cheaper to produce for those who have the relevant underlying quality relative to those who lack it [@grafen1990].
 In these instances, individuals with the quality maximize their fitness at greater levels of investment in the signal compared to those who lack the quality or possess it to a lesser degree [@zahavi1977].
@@
 The costs of depression and suicidal behavior may be particularly important in times of conflict or when the level of support needed to address one’s situation is substantial, both of which should be expected to increase the payoff of manipulating others through fake signals.
-When either condition applies, less costly signals like verbal requests, facial sadness, and crying are likely to be less reliable as their low costs can easily be made up for with increased social support, thereby favoring the use of costlier signals, so long as the costs of signaling are outweighed by the benefits [@SymeHagen2021].
+When either condition applies, less costly signals like verbal requests, facial sadness, and crying are likely to be less reliable as their low costs can easily be made up for with increased social support, thereby favoring the use of costlier signals so long as the costs of signaling are outweighed by the benefits [@SymeHagen2021].
 
@@
 Due to this bargaining component, aversive responses from the targets of the signal to the signaler are expected throughout the bargaining process, with potential helpers likely signaling the costliness of providing support.
-Importantly, such responses do not prevent the delivery of meaningful benefits, they are simply expected to reduce the risk of helpers providing more support than would benefit them.
+Importantly, such responses do not prevent the delivery of meaningful benefits, they are simply expected to reduce the risk of helpers providing too much support for too little need.
 
@@
 
-The sole randomized treatment in this study was the signal participants saw, with these signals being one of (1) the control condition: a verbal request without additional signaling, (2) crying, (3) mild-depression, (4) depression, and (5) a suicide attempt, with the conditions being ordered from low to high cost.
+The sole randomized treatment in this study was the signal participants saw, with these signals being one of (1) the control condition: a verbal request without additional signaling, (2) crying, (3) mild-depression, (4) depression, and (5) a suicide attempt, with the order of the conditions here moving from low to high cost.
 
@@
 
-To reduce the risk of low quality responses, we used a variety of attention checks, which we clearly labeled in an attempt to avoid demand characteristics.
+To reduce the risk of low quality responses, we used a variety of attention checks, which we clearly labeled in an attempt to avoid demand characteristics on the outcomes of interest.
 The first was shown immediately after the consent form and provided participants with a random word and asked them to enter the vowels in the order in which they are found in the word.
@@
 
-We also asked which emotions participants felt the signaler was experiencing using a multiple choice question in which they could select multiple options.
+We also asked which emotions participants felt the signaler was experiencing using a multiple choice question in which they could select as many options as they would like.
 This included emotions directly related to the signals (e.g., sad, depressed, and suicidal), states which suggest genuine need (traumatized and violated), and states which suggest deception (e.g., deviousness or jealousy).
@@
 We asked questions identical to those asked at T1 as the main post-treatment variables of interest (T2).
-For the belief, action, and divide variables, the position of the slider starting where participants placed it at T1.
+For the *Belief*, *Action*, and *Divide* variables, the position of the slider starting where participants placed it at T1.
 For the T2 emotion variables this involved no changes from the T1 version.
@@
 The final part of the survey was a brief demographic questionnaire which examined: (1) the age, (2) sex, (3) number of siblings, (4) number of sons, (5) number of daughters, (6) current relationship status, (7) highest level of education, and (8) the annual household income of each participant.
+The full survey can found in the SI.
 
@@
 While the effect of *Suicide attempt* on belief at T2 was similar to the *Depression* conditions, it resulted in greater likelihood of support.
-This may be due to our decision to measure belief in need as the degree participants believed the claims of the signaler (i.e., the assaults or incompatibility with a potential husband in the context of arranged marriage) rather than a more inclusive measure.
+This may be due to our decision to measure belief in need as the degree participants believed the claims of the signaler (e.g., if the assaults actually happened) rather than a more inclusive measure.
 For this reason, signal cost may have provided additional information about the costliness of the signaler's adversity in addition to information relevant to whether the event claimed actually happened.
@@
 
-## Broader discussion
-
-Our results on the connection between belief in need and likelihood of help are consistent with costly signaling and bargaining approaches to depression and suicide.
-In addition to the effect of signal cost on support being largely mediated by the signal's effect on belief in need, belief in need and likelihood of support were highly correlated but distinct at T1.
-This situation should arise in any instance when a target of a signal of need would benefit from helping if the need was genuine and known to reasonable precision.
-Importantly, such problems are common among modern humans and have likely been so since individuals could increase their inclusive fitness through supporting kin or important cooperative partners in times of genuine need [@SugiyamaSugiyama2003; @tooby1996].
+## Relevance to costly signaling
+
+Overall, our results on the connection between belief in need and likelihood of help are consistent with costly signaling and bargaining approaches to depression and suicide.
+At T1, *Belief* and *Action* were highly correlated yet distinct; while at T2, the effect of signal on both *Belief* and *Action* was to increase the magnitude of pro-signaler responses, with the effect of signal on *T2Action* being largely mediated by signal's effect on belief in need.
+This relationship between belief in need and likelihood of support and the importance of signal cost should be expected in scenarios when a target of a signal of need would benefit from helping if the signaler's need was genuine but face substantial net costs if it was not.
+Importantly, such scenarios appear to be common among modern humans and have likely been since individuals could increase their inclusive fitness through supporting kin or important cooperative partners who could return to providing benefits to supporters once their situation returned to normal [@SugiyamaSugiyama2003; @tooby1996].
 
 Although this study was not designed to examine whether the costs of signaling would be made up for by the increased support stemming from depression and suicide attempts directly, the results are consistent with this hypothesis.
-In general, the costs required to honestly convey one's qualities should be expected to increase with the potential payoffs of deception [@Rosenthal1993], with the vignettes in this study emphasizing the existence of private information and sizable conflicts of interest to increase the perceived risk of being taken advantage of.
+In general, the costs required to honestly convey one's qualities should be expected to increase with the potential payoffs of deception and the number of defectors within the broader population [@Rosenthal1993], with the vignettes in this study emphasizing the existence of private information and sizable conflicts of interest to increase the perceived risk of being taken advantage of.
 In similar real-world scenarios, this difficulty of signaling honest need would coincide with the substantial fitness-relevant benefits of preventing future assaults or being able to marry the partner of one's choice.
-These benefits coupled with the fact (too strong?) that depression and suicide attempts become relatively less costly with increased need [@Hagen2003], suggest that the increased support seen in this study may be worth the costs required to signal need more often than is often appreciated when counting the entire costs of depression as the signal rather than only the upregulation of symptoms for a communicative purpose.
+These benefits coupled with the fact that depression and suicide attempts become relatively less costly to one's fitness prospects with increased need [@Hagen2003], suggest that the increased support seen in this study may be worth the costs required to signal need more often than is often appreciated when counting the entire costs of depression as the signal rather than only the upregulation of symptoms for a communicative purpose.
 
@@
 In support of this, we found exposure to depression and suicide attempts resulted in greater belief in need and increased likelihood of support in fictional scenarios.
-This coupled with findings that depression can simultaneously elicit both positive and negative responses [@HokansonEtAl1986; @stephens1987], suggests that more attention should be paid to the potential for positive responses depressed individuals, especially from those the depressed are in conflict with and those with the capability to provide meaningful benefits.
+This coupled with findings that depression can simultaneously elicit both positive and negative responses [@HokansonEtAl1986; @stephens1987], suggests that more attention should be paid to the potential for positive responses towards depressed individuals, especially from individuals who normally receive substantial benefits from the depressed individual.
 
@@
 - add vignettes to SI (Mild depression = crying plus behavior change)
-- mention somewhere referring to them all as signals even though we know they provide info as cues too
+- victim or signaler?
 

### 2021-04-12 Paper.rmd
Changed signaling intro and minor edits to discussion

@@
 Due to the ease in which signals can be faked [@Zahavi1975; @mokkonen2016] and the costs of accepting a deceptive signal as reliable [@dawkins1978; @johnstone1993; @Hasson1994], demonstrating that one’s need is genuine has likely been a recurrent adaptive problem since humans evolved the capacity to provide instrumental support to one another.
-One possible solution to this is signaling in ways that are unprofitable to fake due to the costs involved.
+One possible solution to this is to produce signals that are unprofitable to fake due to the costs involved.
 [@Zahavi1975].
-This is possible whenever the signal in question is comparatively cheaper to produce for those who have the relevant underlying quality relative to those who lack it [@grafen1990].
-In these instances, individuals with the quality maximize their fitness at greater levels of investment in the signal compared to those who lack the quality or possess it to a lesser degree [@zahavi1977].
+This is possible whenever signaling is comparatively cheaper for those who have the relevant underlying quality relative to those who lack it [@grafen1990].
+In these instances, individuals with the quality maximize their fitness at greater levels of investment in the signal than those who lack the quality or possess it to a lesser degree [@zahavi1977].
 The end result of this is expected to be a signal that either tends to not be worth faking or is impossible to fake to a large degree due to selection against fakers constraining the physiology behind the signal [@zahavi1977; @gangestad2005].
-
-<!-- some overlap with my wikipedia article -->
 
@@
 Distinguishing between the information provided by signals versus cues is a major challenge for signaling approaches to behavior.
-A signal differs from a cue in that it is intentionally sent by an organism to alter the behavior or thoughts of other individuals, while a cue is any piece of information an organism uses to alter its behavior or physiological state that was created without the intent to do so [@MaynardSmithHarper1995].
+A signal differs from a cue in that it is intentionally sent by an organism to alter the perceptions and behaviors of others, while a cue is any piece of information that influences an individual's behavior or physiological state that was not created for communicative effect [@MaynardSmithHarper1995].
 Regarding the signals of interest, suicide attempts are more likely to take the form of pure, external signals than other symptoms of depression.
@@
 This effect was largest in the "brother-in-law" and "romantic partner" vignettes, both of which involved claims of assault against participants' imagined daughters.
-However, the effect of signal type was much smaller in both the "basketball coach" and the "thwarted marriage" vignette.
+Compared to these scenarios, the effect of signal type was much smaller in both the "basketball coach" and the "thwarted marriage" vignette.
 In the "basketball coach" vignette, part of the reason for this may have been the lack of relatedness between participants and the alleged victim.
 However, this was still a surprising finding due to the relatively small size of the request (i.e., recommend the coach be suspended rather than kick out family members or a romantic partner).
-With the thwarted marriage vignette, the fact that support came at the cost of one's younger daughter may explain the relatively small effect of signal strength.
+With the "thwarted marriage" vignette, the fact that support came at the cost of one's younger daughter may explain the relatively small effect of signal strength.
 However, data from the Indian sample appears to be of lower quality, limiting our confidence in this interpretation (see limitations for more information).
@@
 
-In the "brother-in-law" and "romantic partner" scenarios, *Crying* had little effect on the magnitude of pro-signaler responses, while both *Depression* conditions increased support to similar degrees.
+In the "brother-in-law" and "romantic partner" scenarios, *Crying* had little effect on the magnitude of pro-signaler responses relative to *Verbal request*, suggesting it was not costly enough to serve as a reliable signal in times of substantial conflicts of interests.
+In contrast, both *Depression* conditions increased support, albeit to similar degrees.
 One potential reason for this is the increase in symptoms from mild depression to depression was not costly enough to result in a large effect as the symptoms only differed in severity (e.g., grades dropping from As to Bs [mild depression] or Cs [depression]).
@@
 
-While the effect of *Suicide attempt* on belief at T2 was similar to the *Depression* conditions, it resulted in greater likelihood of support.
+While the effect of *Suicide attempt* on belief at T2 was similar to the *Depression* conditions across vignettes, it resulted in greater likelihood of support.
 This may be due to our decision to measure belief in need as the degree participants believed the claims of the signaler (e.g., if the assaults actually happened) rather than a more inclusive measure.
-For this reason, signal cost may have provided additional information about the costliness of the signaler's adversity in addition to information relevant to whether the event claimed actually happened.
-
-Support for this interpretation comes from our mediation analyses, which showed that the likelihood of help was largely, but not entirely, mediated by signal's effect on belief in need in this study but totally mediated by belief in need when measured as belief in need of financial support in the pilot study when comparing both depression and suicide attempts (confirm suicide) to verbal requests.
-However, the partial mediation in this study may have also arisen if participants viewed the signal as providing information about adversity outside of the signaler's claims.
+For this reason, signal cost may have provided additional information about the costliness of the signaler's adversity on top of information relevant to whether the event claimed actually happened.
+
+Support for this interpretation comes from our mediation analyses, which showed that the likelihood of help was largely, but not entirely, mediated by signal's effect on belief in need in this study but totally mediated by belief in need when measured as belief in need of financial support in the pilot study when comparing both *Depression* and *Suicide attempt* (confirm suicide) to *Verbal request*.
+However, another possibility is that participants viewed the signal as providing information about adversity outside of the signaler's claims.
 For example, participants who saw the "brother-in-law" vignette may have thought the daughter was lying about the assault due to jealously over her cousin, with the stronger signals still conveying the severity of the competition between her and her cousin.
 
+ However, the greater impact on likelihood of help than belief found in this study may have also arisen if participants viewed the signal as providing information about adversity outside of the signaler's claims.
 ## Relevance to costly signaling
@@
 In support of this, we found exposure to depression and suicide attempts resulted in greater belief in need and increased likelihood of support in fictional scenarios.
-This coupled with findings that depression can simultaneously elicit both positive and negative responses [@HokansonEtAl1986; @stephens1987], suggests that more attention should be paid to the potential for positive responses towards depressed individuals, especially from individuals who normally receive substantial benefits from the depressed individual.
+This coupled with findings that depression can simultaneously elicit both positive and negative responses [@HokansonEtAl1986; @stephens1987], suggests that more attention should be paid to the potential for positive responses towards depressed individuals, especially from individuals who normally receive substantial benefits from the depressed or suicidal individual.
 

### 2021-04-12 Paper.rmd
Removed line of text and confirmed mediation analyses of MA

@@
 
-Support for this interpretation comes from our mediation analyses, which showed that the likelihood of help was largely, but not entirely, mediated by signal's effect on belief in need in this study but totally mediated by belief in need when measured as belief in need of financial support in the pilot study when comparing both *Depression* and *Suicide attempt* (confirm suicide) to *Verbal request*.
+Support for this interpretation comes from our mediation analyses, which showed that the likelihood of help was largely, but not entirely, mediated by signal's effect on belief in need in this study but totally mediated by belief in need when measured as need of financial support in the pilot study when comparing both *Depression* and *Suicide attempt* to *Verbal request*.
 However, another possibility is that participants viewed the signal as providing information about adversity outside of the signaler's claims.
 For example, participants who saw the "brother-in-law" vignette may have thought the daughter was lying about the assault due to jealously over her cousin, with the stronger signals still conveying the severity of the competition between her and her cousin.
-
- However, the greater impact on likelihood of help than belief found in this study may have also arisen if participants viewed the signal as providing information about adversity outside of the signaler's claims.
-## Relevance to costly signaling
 

### 2021-04-12 Paper.rmd
Minor edits to abstract and discussion

@@
 Alternatively, depression and suicide attempts might be the result of adaptations for reliably signaling need and bargaining for increased support from reluctant others.
-To address this hypothesis, we examined responses to emotional signals in an experimental vignette study involving claims of substantial need and the existence of conflicts of interest and private information about whether the signaler was actually in need.
+To address this hypothesis, we examined responses to emotional signals in an experimental vignette study involving claims of substantial need in the presence of conflicts of interest and private information about whether the signaler was actually in need.
 In our sample of 1,240 participants recruited from Amazon Mechanical Turk, costlier signals like depression and suicide attempts resulted in greater perceptions of need and increased likelihood of support compared to simple verbal requests and crying without further symptoms.
@@
 
-Support for this interpretation comes from our mediation analyses, which showed that the likelihood of help was largely, but not entirely, mediated by signal's effect on belief in need in this study but totally mediated by belief in need when measured as need of financial support in the pilot study when comparing both *Depression* and *Suicide attempt* to *Verbal request*.
+Support for this interpretation comes from our mediation analyses, which showed that the likelihood of help was largely, but not entirely, mediated by signal's effect on belief in need in this study but totally mediated by belief in need when measured as need of financial support in the pilot study when comparing *Depression* to *Verbal request*.
 However, another possibility is that participants viewed the signal as providing information about adversity outside of the signaler's claims.

### 2021-04-12 Paper.rmd
Tweaked demographics plot and a couple of captions.

@@
 Alternatively, depression and suicide attempts might be the result of adaptations for reliably signaling need and bargaining for increased support from reluctant others.
-To address this hypothesis, we examined responses to emotional signals in an experimental vignette study involving claims of substantial need in the presence of conflicts of interest and private information about whether the signaler was actually in need.
-In our sample of 1,240 participants recruited from Amazon Mechanical Turk, costlier signals like depression and suicide attempts resulted in greater perceptions of need and increased likelihood of support compared to simple verbal requests and crying without further symptoms.
-Additionally, the effect of signal type on likelihood of support was largely mediated by the effect of signaling on belief in need as predicted.
+To test this hypothesis, we examined responses to  emotional signals in a vignette study in which the existence of conflicts of interest and private information about one's need were emphasized in four scenarios involving claims of extreme need.
+Although the effect of signal type varied by vignette, costlier signals like depression and suicide attempts resulted in greater perceptions of need and increased likelihood of support compared to simple verbal requests and crying without further symptoms in our sample of 1,240 participants recruited from Amazon Mechanical Turk.
+Additionally, the effect of signal type on likelihood of support was largely mediated by the effect of signaling on believe in need as predicted.
 Our results suggest that depression and suicide attempts, apparent human universals, are a relatively successful way of signaling honest need and eliciting support, consistent with costly signaling explanations.
@@
 This strong connection between negative life events and depression along with the adversity and distress that likely accompanies these events has led to the suggestion that this relationship is causal [@KendlerEtAl1999].
-Support for this comes from the fact that the relationship between negative events and depression holds true when looking solely at events outside of one's control, showing that the connection is unlikely to be driven solely by individuals who are already depressed creating situations where negative events are likely to be common [@Hammen2005; @KendlerEtAl1999].
+Support for this comes from the fact that the relationship between negative events and depression holds true when looking solely at events outside of one's control, showing that the connection is unlikely to be driven solely by depressed individuals creating situations where negative events are likely to be common [@Hammen2005; @KendlerEtAl1999].
 In addition to this, twin studies have shown that one's history of negative events is still a strong predictor of major depression when controlling for genetic similarity and that part of the heritability of depression stems from the heritability of negative events, like divorce and family conflict [@KendlerBaker2007; @KendlerEtAl1999].
@@
 Other notable risk factors like loss of a loved one, financial problems, job loss, or severe or prolonged illness, might seem less related to conflict.
-However, the ability for others to provide meaningful support to limit the harm caused in times of need [@SugiyamaSugiyama2003] combined with the ubiquity of conflicts of interests mean that many types of problems will eventually involve social conflict even if they did not start that way [@Hagen2003].
-In line with this reasoning, conflict, as a whole, was found to be associated with depression among the Tsimane, particularly when it involved non-kin [@StieglitzEtAl2015a].
+However, the ability for others to provide meaningful support to limit the harm caused in times of need [@SugiyamaSugiyama2003] combined with the ubiquity of conflicts of interests mean that many types of problems will eventually involve social conflict even if they did not start that way [@Hagen2003)].
+In line with this reasoning, conflict, in general, was found to be associated with depression among the Tsimane, particularly when it involved non-kin [@StieglitzEtAl2015a].
 
@@
 One possible reason for the connection between depression, suicide, and social adversity is that some instances of depression and suicide attempts serve as means to elicit increased support from others [@andrews2006; @Hagen2002; @Hagen2003; @HagenEtAl2008; @nock2008; @Rosenthal1993; @Stengel1956; @SymeEtAl2016], particularly in times when an individual cannot solve substantial fitness-relevant challenges on their own [@Hagen2003; @SymeEtAl2016].
-According to the bargaining models of depression and suicide, the small groups humans lived in for much of our evolutionary history created many situations in which certain forms of cooperation were unlikely to be easily replaced by others while also allowing for harmful or unfair social relationships to develop [@Hagen2003; @SymeEtAl2016].
+According to the bargaining models of depression and suicide, the idea is that the small groups humans lived in for much of our evolutionary history created many situations in which certain forms of cooperation were unlikely to be easily replaced by others while also allowing for harmful or unfair social relationships to develop [@Hagen2003; @SymeEtAl2016].
 In these instances, one's monopoly on one or more types of cooperation could be leveraged to change how one is treated if others valued an individual's cooperation sufficiently and believed them to be in genuine need.
@@
 Due to the ease in which signals can be faked [@Zahavi1975; @mokkonen2016] and the costs of accepting a deceptive signal as reliable [@dawkins1978; @johnstone1993; @Hasson1994], demonstrating that one’s need is genuine has likely been a recurrent adaptive problem since humans evolved the capacity to provide instrumental support to one another.
-One possible solution to this is to produce signals that are unprofitable to fake due to the costs involved.
+One possible solution to this is signaling in ways that are unprofitable to fake due to the costs involved.
 [@Zahavi1975].
-This is possible whenever signaling is comparatively cheaper for those who have the relevant underlying quality relative to those who lack it [@grafen1990].
-In these instances, individuals with the quality maximize their fitness at greater levels of investment in the signal than those who lack the quality or possess it to a lesser degree [@zahavi1977].
+This is possible whenever the signal in question is comparatively cheaper to produce for those who have the underlying quality being compared to those who lack it [@grafen1990].
+In these instances, individuals with the quality maximize their fitness at greater levels of investment in the signal compared to those who lack the quality or possess it to a lesser degree [@zahavi1977].
 The end result of this is expected to be a signal that either tends to not be worth faking or is impossible to fake to a large degree due to selection against fakers constraining the physiology behind the signal [@zahavi1977; @gangestad2005].
 
-Depression and suicidal behavior fit this criterion as both are relatively costly for those not facing adversity than those who are.
-In the case of depression, the large-scale reduction in one's normal routine of fitness enhancing behavior is relatively less costly for those whose situations result in a limited ability to obtain fitness-relevant benefits, with depression likely adding no additional costs in instances of extreme deprivation [@Hagen2003].
+Both depression and suicidal behavior fit this criterion as they are both relatively costly for those not facing adversity than those who are.
+In the case of depression, the largescale reduction in one's normal routine of fitness enhancing behavior is relatively less costly for those whose situations result in a limited ability to obtain fitness-relevant benefits, with depression likely adding no additional costs in instances of extreme deprivation [@Hagen2003].
 When it comes to suicide, the bulk of the costs associated with suicide attempts are only felt in times that result in death or severe bodily harm.
@@
 The costs of depression and suicidal behavior may be particularly important in times of conflict or when the level of support needed to address one’s situation is substantial, both of which should be expected to increase the payoff of manipulating others through fake signals.
-When either condition applies, less costly signals like verbal requests, facial sadness, and crying are likely to be less reliable as their low costs can easily be made up for with increased social support, thereby favoring the use of costlier signals so long as the costs of signaling are outweighed by the benefits [@SymeHagen2021].
+When either condition applies, less costly signals like verbal requests, facial sadness, and crying are likely to be less reliable as their low costs can easily be made up for with increased social support, thereby favoring the use of costlier signals, so long as the costs of signaling are outweighed by the benefits [@SymeHagen2021].
 
 Beyond signaling need to those invested in the well-being of the signaler, depression and suicidal behavior may also help an individual bargain for increased support [@Hagen2003].
-This is possible due to the reduced investment in others that frequently accompanies depression or the threat to future cooperation that comes from suicide.
-In these instances, depression and suicide attempts may function analogously to a labor strike, sending the message that one’s need is genuine and that if the target of the signal wanted to continue receiving benefits from the depressed, they would need to increase support towards the signaler.
-Due to this bargaining component, aversive responses from the targets of the signal to the signaler are expected throughout the bargaining process, with potential helpers likely signaling the costliness of providing support.
-Importantly, such responses do not prevent the delivery of meaningful benefits, they are simply expected to reduce the risk of helpers providing too much support for too little need.
-
-<!-- reword this paragraph -->
+This is possible due to the reduced investment in others that frequently accompanies depression or the threat to future cooperation that comes from a suicide.
+In these instances, depression and suicide attempts are suggested to function analogously to a labor strike, sending the message that one’s need is genuine and that if the target of the signal wanted to continue receiving benefits from the depressed, he or she would need to increase support towards the signaler.
 
@@
 Distinguishing between the information provided by signals versus cues is a major challenge for signaling approaches to behavior.
-A signal differs from a cue in that it is intentionally sent by an organism to alter the perceptions and behaviors of others, while a cue is any piece of information that influences an individual's behavior or physiological state that was not created for communicative effect [@MaynardSmithHarper1995].
+A signal differs from a cue in that it is intentionally sent by an organism to alter the behavior or thoughts of other individuals, while a cue is any piece of information an organism uses to alter its behavior or physiological state that was created without the intent to do so [@MaynardSmithHarper1995].
 Regarding the signals of interest, suicide attempts are more likely to take the form of pure, external signals than other symptoms of depression.
@@
 In other words, the signaling component of depression may come from the upregulation of symptoms beyond what would be optimal for non-signaling purposes rather than the creation of entirely new symptoms.
-Suicidality is likely an exception to this, due to the likelihood most suicide attempts likely do not have non-signaling functions [see @deCatanzaro1991 for a possible exception].
+Suicidality is likely an exception to this, due to the likelihood most suicide attempts likely do not have non-signaling functions (see @deCatanzaro1991 for a possible exception).
 
@@
 
-For depression and suicide attempts to be worth the costs involved with signal creation, meaningful social support would be required [@Hagen2003; @SymeEtAl2016].
+For depression and suicide attempts to be worth the costs involved with signal creation, meaningful social support would be required, either in the form of temporary but impactful support or long-term changes in how one is treated [@Hagen2003; @SymeEtAl2016].
 Most studies examining responses to depression have been observational and focused on responses outside of changes in social support.
@@
 Despite being looked for less frequently, beneficial responses to depressed individuals are also reported.
-Depression has been associated with reduced likelihood of aggression within families [@hops1987; @dadds1992], including those already experiencing high levels of conflict [@SheeberEtAl2001].
+This is seen in that depression has been associated with reduced likelihood of aggression within families [@hops1987; @dadds1992], including those already experiencing high levels of conflict [@SheeberEtAl2001].
 There is also limited evidence that depression can result in increased levels of support from others outside the family.
@@
 Unlike many Western countries, where suicide is often viewed as pathological [@Hidaka2012], members of traditional societies have been reported to view suicide attempts as cries for help rather than mental illness [@Shostak1981], with attempts having been described as ways of escaping unwanted marriage arrangements, persistent abuse, or a lack of support in obtaining mates by those engaging in the behavior and observers [@GutierrezdePinedaMuirden1948; @Hilger1957; @Karsten1935; @Tessmann1930; @Wilson1960].
-Although findings that individuals view suicide attempts as cries for help is not necessarily evidence for their ability to lead to beneficial responses, 30 out of 84 examples of suicidal behavior included in the HRAF resulted in positive changes for the survivor, despite suicide rarely if ever being the main topic [@SymeEtAl2016].
-
-## Study aims and predictions
+Although findings that individuals view suicide attempts as cries for help is not necessarily evidence for them resulting in beneficial responses, 30 out of 84 examples of suicidal behavior included in the HRAF resulted in positive changes for the survivor, even though suicide was rarely if ever the main topic [@SymeEtAl2016].
+
+# Study aims and predictions
 
 The primary aim of this study was to examine responses to various forms of emotional signaling in an experimental vignette study.
-As the costs of a signal are expected to correspond to the reliability of the information provided, we predicted that costlier signals would (1) increase self-reported belief in the signaler's claims and (2) increase the likelihood of participants providing help, with (3) changes in likelihood of support being largely mediated by changes in the participants' belief in the signaler's need from pre-signal to post-signal.
+We predicted that costlier signals would increase the participants' self-reported belief in the signaler's claims and the likelihood of them providing help, with this prediction entailing the following rank from low to high cost: verbal request, crying, mild-depression, depression, and suicide attempt.
+We also predicted that changes in the likelihood participants would provide support would be mediated by changes in the participants' belief in the signaler's need pre-signal to post-signal.
 
@@
 
-The sole randomized treatment in this study was the signal participants saw, with these signals being one of (1) the control condition: a verbal request without additional signaling, (2) crying, (3) mild-depression, (4) depression, and (5) a suicide attempt, with the order of the conditions here moving from low to high cost.
+The sole randomized treatment in this study was the signal participants saw, with these signals being one of (1) the control condition: a verbal request without additional signaling, (2) crying, (3) mild-depression, (4) depression, and (5) a suicide attempt.
 
 As many depression scales include measures of crying [for discussion on the relationship between crying and depression see @bylsma2020] and depression is a major risk factor for suicide [@BostwickPankratz2000; @Kessler2012], each signal was designed to build off of the less costly signals so that each signal contained elements of any signal it was costlier than.
-Although referred to as signals throughout the paper for brevity, we expect that the hypothesized signals of need, like many signals, will also provide information to others in the form of cues [for discussion on the evolution of cues from signals see: @biernaskie2018; @Tiokhin2016; @Steinkopf2015].
+Although referred to as signals throughout the paper for brevity, we expect that the hypothesized signals of need, like many signals, will also provide information to others in the form of cues [For discussion on the evolution of cues from signals see: @biernaskie2018; @Tiokhin2016; @Steinkopf2015].
 The full text for the signals are available in the SI.
@@
 
-To reduce the risk of low quality responses, we used a variety of attention checks, which we clearly labeled in an attempt to avoid demand characteristics on the outcomes of interest.
+To reduce the risk of low quality responses, we used a variety of attention checks, which we clearly labeled in an attempt to avoid demand characteristics.
 The first was shown immediately after the consent form and provided participants with a random word and asked them to enter the vowels in the order in which they are found in the word.
@@
 
+After accepting the HIT on MTurk, every participant took the survey using Qualtrics.
+In every instance, the elements of the survey were laid out in the following order: 1) the consent form, 2) the vowel attention check, 3) the main body of the vignette, 3) the pre-test baseline measures (T1), 4) the story content attention check, 5)  the signal portion of the vignette, 7) the post-test outcome measures (T2-T3), 8) an attention check that did not filter out participants (T4), 9) a set of demographic questions, and 10) an open feedback prompt.
+The full survey can be found in the SI.
+
 ### Baseline measures (T1)
@@
 Responses were recorded with sliders due to the fact they allow for finer grained changes than categorical scales [@KlimekEtAl2017].
-Based on findings that a slider's starting position may bias results [@liu2019], we had concerns that participants would be less likely to move away from intermediate starting values than they would be in reality.
-For this reason, we set each T1 slider to start fully to the left (0).
+Due to findings that a slider's starting position may bias results [@liu2019], each T1 slider started fully to the left (0) (don't exactly remember the logic for left instead of click to start).
 For the exact wording of the question and the labels on the sliders, see table 1.
 
-We also asked which emotions participants felt the signaler was experiencing using a multiple choice question in which they could select as many options as they would like.
+We also asked which emotions participants felt the signaler was experiencing using a multiple choice question in which they could select multiple options.
 This included emotions directly related to the signals (e.g., sad, depressed, and suicidal), states which suggest genuine need (traumatized and violated), and states which suggest deception (e.g., deviousness or jealousy).
@@
 We asked questions identical to those asked at T1 as the main post-treatment variables of interest (T2).
-For the *Belief*, *Action*, and *Divide* variables, the position of the slider starting where participants placed it at T1.
+For the belief, action, and divide variables, the position of the slider starting where participants placed it at T1.
 For the T2 emotion variables this involved no changes from the T1 version.
@@
 The final part of the survey was a brief demographic questionnaire which examined: (1) the age, (2) sex, (3) number of siblings, (4) number of sons, (5) number of daughters, (6) current relationship status, (7) highest level of education, and (8) the annual household income of each participant.
-The full survey can found in the SI.
 
@@
 The marginal between-subjects effect of the high cost *Suicide attempt* vs.
-low cost *Verbal request* control on T2 *Belief* (averaging over all four vignettes and all values of T1 *Belief*) was an increase of `r fmt_margins(models$Margins$m1, 'signalSuicide attempt')` points on the original 0-100 point scale.
+the *Verbal request* control on T2 *Belief* (averaging over all four vignettes and all values of T1 *Belief*) was an increase of `r fmt_margins(models$Margins$m1, 'signalSuicide attempt')` points on the original 0-100 point scale.
 The equivalent increase for T2 *Action* was `r fmt_margins(models$Margins$m3, 'signalSuicide attempt')` points.
@@
 
-Effect sizes (Cohen's d), between- and within-subjects, reveals a similar pattern.
 The largest between-subjects effect was *Suicide attempt* vs.
@@
 This effect was largest in the "brother-in-law" and "romantic partner" vignettes, both of which involved claims of assault against participants' imagined daughters.
-Compared to these scenarios, the effect of signal type was much smaller in both the "basketball coach" and the "thwarted marriage" vignette.
+However, the effect of signal type was much smaller in both the "basketball coach" and the "thwarted marriage" vignette.
 In the "basketball coach" vignette, part of the reason for this may have been the lack of relatedness between participants and the alleged victim.
 However, this was still a surprising finding due to the relatively small size of the request (i.e., recommend the coach be suspended rather than kick out family members or a romantic partner).
-With the "thwarted marriage" vignette, the fact that support came at the cost of one's younger daughter may explain the relatively small effect of signal strength.
+With the thwarted marriage vignette, the fact that support came at the cost of one's younger daughter may explain the relatively small effect of signal strength.
 However, data from the Indian sample appears to be of lower quality, limiting our confidence in this interpretation (see limitations for more information).
@@
 
-In the "brother-in-law" and "romantic partner" scenarios, *Crying* had little effect on the magnitude of pro-signaler responses relative to *Verbal request*, suggesting it was not costly enough to serve as a reliable signal in times of substantial conflicts of interests.
-In contrast, both *Depression* conditions increased support, albeit to similar degrees.
+In the "brother-in-law" and "romantic partner" scenarios, *Crying* had little effect on the magnitude of pro-signaler responses, while both *Depression* conditions increased support to similar degrees.
 One potential reason for this is the increase in symptoms from mild depression to depression was not costly enough to result in a large effect as the symptoms only differed in severity (e.g., grades dropping from As to Bs [mild depression] or Cs [depression]).
@@
 
-While the effect of *Suicide attempt* on belief at T2 was similar to the *Depression* conditions across vignettes, it resulted in greater likelihood of support.
-This may be due to our decision to measure belief in need as the degree participants believed the claims of the signaler (e.g., if the assaults actually happened) rather than a more inclusive measure.
-For this reason, signal cost may have provided additional information about the costliness of the signaler's adversity on top of information relevant to whether the event claimed actually happened.
-
-Support for this interpretation comes from our mediation analyses, which showed that the likelihood of help was largely, but not entirely, mediated by signal's effect on belief in need in this study but totally mediated by belief in need when measured as need of financial support in the pilot study when comparing *Depression* to *Verbal request*.
-However, another possibility is that participants viewed the signal as providing information about adversity outside of the signaler's claims.
+While the effect of *Suicide attempt* on belief at T2 was similar to the *Depression* conditions, it resulted in greater likelihood of support.
+This may be due to our decision to measure belief in need as the degree participants believed the claims of the signaler (i.e., the assaults or incompatibility with a potential husband in the context of arranged marriage) rather than a more inclusive measure.
+For this reason, signal cost may have provided additional information about the costliness of the signaler's adversity in ways that would still be consistent with signaling theory.
+
+Support for this interpretation comes from our mediation analyses, which showed that the likelihood of help was largely, but not entirely, mediated by signal's effect on belief in need in this study but totally mediated by belief in need when measured as belief in need of financial support in the pilot study.
+However, the incomplete mediation in this study may have arisen if participants viewed the signal as providing information about adveristy outside of the signaler's claims.
 For example, participants who saw the "brother-in-law" vignette may have thought the daughter was lying about the assault due to jealously over her cousin, with the stronger signals still conveying the severity of the competition between her and her cousin.
 
-Overall, our results on the connection between belief in need and likelihood of help are consistent with costly signaling and bargaining approaches to depression and suicide.
-At T1, *Belief* and *Action* were highly correlated yet distinct; while at T2, the effect of signal on both *Belief* and *Action* was to increase the magnitude of pro-signaler responses, with the effect of signal on *T2Action* being largely mediated by signal's effect on belief in need.
-This relationship between belief in need and likelihood of support and the importance of signal cost should be expected in scenarios when a target of a signal of need would benefit from helping if the signaler's need was genuine but face substantial net costs if it was not.
-Importantly, such scenarios appear to be common among modern humans and have likely been since individuals could increase their inclusive fitness through supporting kin or important cooperative partners who could return to providing benefits to supporters once their situation returned to normal [@SugiyamaSugiyama2003; @tooby1996].
+## Broader discussion
+
+Our results on the connection between belief in need and likelihood of help are consistent with costly signaling and bargaining approaches to depression and suicide.
+In addition to the effect of signal cost on support being largely mediated by the signal's effect on belief in need, belief in need and likelihood of support were highly correlated but distinct at T1.
+This situation should arise in any instance when a target of a signal of need would benefit from helping if the need was genuine and known to reasonable precision.
+Importantly, such problems are common among modern humans and have likely been so since individuals could increase their inclusive fitness through supporting kin or important cooperative partners in times of genuine need [@SugiyamaSugiyama2003; @tooby1996].
 
 Although this study was not designed to examine whether the costs of signaling would be made up for by the increased support stemming from depression and suicide attempts directly, the results are consistent with this hypothesis.
-In general, the costs required to honestly convey one's qualities should be expected to increase with the potential payoffs of deception and the number of defectors within the broader population [@Rosenthal1993], with the vignettes in this study emphasizing the existence of private information and sizable conflicts of interest to increase the perceived risk of being taken advantage of.
+In general, the costs required to honestly convey one's qualities should be expected to increase with the potential payoffs of deception [@Rosenthal1993], with the vignettes in this study emphasizing the existence of private information and sizable conflicts of interest to increase the perceived risk of being taken advantage of.
 In similar real-world scenarios, this difficulty of signaling honest need would coincide with the substantial fitness-relevant benefits of preventing future assaults or being able to marry the partner of one's choice.
-These benefits coupled with the fact that depression and suicide attempts become relatively less costly to one's fitness prospects with increased need [@Hagen2003], suggest that the increased support seen in this study may be worth the costs required to signal need more often than is often appreciated when counting the entire costs of depression as the signal rather than only the upregulation of symptoms for a communicative purpose.
+These benefits coupled with the fact (too strong?) that depression and suicide attempts become relatively less costly with increased need [@Hagen2003], suggest that the increased support seen in this study may be worth the costs required to signal need more often than is often appreciated when counting the entire costs of depression as the signal rather than only the upregulation of symptoms for a communicative purpose.
 
@@
 It may have also biased participants against helping if they could not fully imagine the characters in the story as kin or important cooperative partners, while the survey's short duration may have weakened the strength of the costlier signals as bargaining tools.
-However, the fact that the relationships among signal cost, belief in need, and likelihood of providing support all largely fit existing theory (narrow and broad) indicates that participants paid attention to the relevant details and responded in ways that suggest some degree of external validity (needs improvement).
+However, the fact that the relationships among signal cost, belief in need, and likelihood of providing support all largely fit existing theory (narrow and broad) indicates that participants paid attention to the relevant details and responded in ways that suggest some degree of external validity (needs improvement.
 For this reason, the benefits of addressing causal relationships that came through our experimental vignette approach likely outweighed the costs.
@@
 For this hypothesis to be correct, instrumental support would need to be provided frequently enough with large enough impacts so that the costs of signaling are outweighed by the benefits on average.
-In support of this, we found exposure to depression and suicide attempts resulted in greater belief in need and increased likelihood of support in fictional scenarios.
-This coupled with findings that depression can simultaneously elicit both positive and negative responses [@HokansonEtAl1986; @stephens1987], suggests that more attention should be paid to the potential for positive responses towards depressed individuals, especially from individuals who normally receive substantial benefits from the depressed or suicidal individual.
+Although possible benefits to depressive states are rarely examined, we found exposure to depression and suicide attempts resulted in greater belief in need and increased likelihood of support in fictional scenarios.
+This coupled with findings that depression can be simultaneously aversive and elicit support [@HokansonEtAl1986; @stephens1987], suggests that more attention should be paid to the responses of others to depressed individuals, especially from those the depressed are in conflict with and those with the capability to provide meaningful benefits.
 
@@
 - add vignettes to SI (Mild depression = crying plus behavior change)
-- victim or signaler?
+- mention somewhere referring to them all as signals even though we know they provide info as cues too
 
@@
 
-```{r socioeconomic, fig.width=8, fig.cap="Distribution of participants by age, log income (USD), and nationality.
-A small number of participants who did not report income, or reported values < $10 USD, were removed from this plot.
+```{r socioeconomic, fig.width=8, fig.cap="Distribution of participants by age, log annual income (USD), and nationality.
+Each dot is one participant.
+A small number of participants who did not report annual income, or reported values < $10 USD, were removed from this plot.
 A small amount of jitter was added to reveal overlapping points."}
@@
   geom_jitter(width = 0.5, alpha = 0.35) +
-  geom_hline(yintercept = log10(1670), linetype = 'dotted', colour = clrs[1]) +
-  geom_hline(yintercept = log10(35977), linetype = 'dotted', colour = clrs[2]) +
-  annotate('text', 15, log10(35977), label = 'Median US income', hjust = 1) +
-  annotate('text', 15, log10(1670), label = 'Median India income', hjust = 1) +
+  geom_hline(yintercept = log10(2266), linetype = 'dotted', colour = clrs[1]) +
+  geom_hline(yintercept = log10(68703), linetype = 'dotted', colour = clrs[2]) +
+  annotate('text', 85, log10(68703), label = 'Median US\nincome', hjust = 0) +
+  annotate('text', 85, log10(2266), label = 'Median India\nincome', hjust = 0) +
   scale_color_binary() +
-  guides(colour = guide_legend(reverse = T, override.aes = list(alpha=1))) +
+  guides(colour = guide_legend(reverse = T, override.aes = list(alpha=1, size = 3))) +
   coord_cartesian(clip = 'off') +
@@
   theme_minimal(15) +
-  theme(axis.title.y = element_text(angle = 0, hjust=0))
+  theme(
+    plot.margin = unit(c(1,5,1,1), "lines"),
+    axis.title.y = element_text(angle = 0, hjust=0), 
+    legend.position = 'top'
+    )
 

### 2021-04-13 Paper.rmd
Added vignettes, signals, and emotion checklist to SI. Also fixed a typo fix in the intro.

@@
 
-Within anthropology, Raymond Firth was likely the first to conceputalize suicidality as a gamble to improve one's circumstances in the here and now.
-Based on observations that suicide attempts often followed social conflict or loss, and varied substantially in their likelihood of death, he argued that a sizable subset of the suicide attempts among the Tikopia were not meant to end in death but instead were a means to elicit attention, status, and immediate reintegration into the community following negative events [@firth1936; @Firth:1961].
+Within anthropology, Raymond Firth was likely the first to conceptualize suicidality as a gamble to improve one's circumstances in the here and now.
+Based on observations that suicide attempts often followed social conflict or loss, and varied substantially in their likelihood of death, he argued that a sizable subset of the suicide attempts among the Tikopia were not meant to end in death but instead were a means to elicit attention, status, or immediate reintegration into the community following negative events [@firth1936; @Firth:1961].
 
@@
 # To do:
-- add vignettes to SI (Mild depression = crying plus behavior change)
+
 - victim or signaler?
@@
 ```
+
+## Vignettes (main bodies and signals)
+
+### Basketball coach
+
+Imagine yourself in the following scenario:
+
+You are a college athletic director at a university with a long history of success in women’s basketball.
+Unfortunately, despite quality players, the team struggled for the first three years of your leadership.
+You came close to losing your job but were given two more years to turn things around.
+You immediately hired a new head coach who you had spotted coaching a low-ranked college team that punched above its weight.
+Two years later, your team is one of the best in the country and has attracted a top recruit who has become the star player on your team and is probably the best player in the country.
+You have been told that if the team makes it to the final rounds of the playoff tournament, the university will offer you a high paying contract extension.
+
+Your star player is hard to deal with, however.
+She is constantly jealous of other players, and often comes to your office to complain that the coach unfairly limits her playing time, claiming this will ruin her chances of going professional.
+The star player has also posted self-serving accounts of your discussions with her on social media.
+
+A few days ago, after the coach started a new player in one game, the star player went to the police and accused the coach, a physically powerful man, of cornering her in the locker room one night and forcibly kissing her and grabbing her body.
+The coach strongly denies the allegation, and the police said they do not have any evidence to corroborate the player’s accusation.
+
+You reached out to other players on the team, all of whom say that the relationship between the coach and star player has always seemed professional, and they are shocked by the allegation.
+None of the other players have any complaints about the coach.
+On the contrary, the other players praise the coach for leading everyone into the playoffs.
+They mention that the star player is a prima donna, but they are worried that if either the coach or the star player miss the playoffs, it will hurt everyone’s chances of making it to the championships.
+
+You find out that the star player then told the university president that she feared the coach might attack her again, and asked her to replace the coach with one of his assistants, who you know wants the star player to have more playing time.
+The president refused, saying there was no evidence of wrongdoing.
+
+#### Signals
+
+##### Verbal request
+
+A week later the coach informs you that the star player’s performance in games is excellent, helping the team’s performance and her reputation with pro scouts.
+Later that day, there is a formal luncheon at the athlete dorm to introduce the coaches and members of each team to the alumni.
+The alumni are especially interested in meeting the basketball coach and members of the basketball team because they are in the playoffs.
+You notice your star player is not there, but you see her roommate, a member of the swim team.
+She tells you that you should talk to your star player in person, and she leads you to their dorm room.
+
+When you arrive, the two of you find her sitting on her bed.
+She appears fit, well-rested, and her room is clean.
+She looks calm with her hands folded as she asks you to replace the coach, saying she can’t attend the luncheon if he is there.
+
+##### Crying
+
+A week later the coach informs you that the star player’s performance in games is excellent, helping the team’s performance and her reputation with pro scouts.
+Later that day, there is a formal luncheon at the athlete dorm to introduce the coaches and members of each team to the alumni.
+The alumni are especially interested in meeting the basketball coach and members of the basketball team because they are in the playoffs.
+You notice your star player is not there, but you see her roommate, a member of the swim team.
+She tells you that you should talk to your star player in person, and she leads you to their dorm room.
+
+When you arrive, the two of you find her sitting on her bed.
+She appears fit and well-rested, and her room is clean.
+She looks sad and begins sobbing as she asks you to replace the coach, saying she can’t attend the luncheon if he is there.
+
+##### Mild-depression (crying with behavioral changes)
+
+A week later the coach informs you that the star player’s performance in games is OK and not harming the team’s performance and her reputation with pro scouts.
+Later that day, there is a formal luncheon at the athlete dorm to introduce the coaches and members of each team to the alumni.
+The alumni are especially interested in meeting the basketball coach and members of the basketball team because they are in the playoffs.
+You notice your star player is not there, but you see her roommate, a member of the swim team.
+She tells you that you should talk to your star player in person, and she leads you to their dorm room.
+
+When you arrive, the two of you find her sitting on her bed.
+Her room is a little messy and she appears a little less fit than you remember, while also seeming slightly tired.
+She looks sad and begins sobbing as she asks you to replace the coach, saying she can’t attend the luncheon if he is there.
+
+##### Depression
+
+A week later the coach informs you that the star player’s performance in games is poor, harming the team’s performance and her reputation with pro scouts.
+Later that day, there is a formal luncheon at the athlete dorm to introduce the coaches and members of each team to the alumni.
+The alumni are especially interested in meeting the basketball coach and members of the basketball team because they are in the playoffs.
+You notice your star player is not there, but you see her roommate, a member of the swim team.
+She tells you that you should talk to your star player in person, and she leads you to their dorm room.
+
+When you arrive, the two of you find her slouched on her bed.
+Her room is a mess, and you notice she has lost weight and looks fatigued.
+She looks sad and begins sobbing and wringing her hands as she asks you to replace the coach, saying she can’t attend the luncheon if he is there.
+
+##### Suicide attempt
+
+A week later the coach informs you that the star player’s performance in games is poor, harming the team’s performance and her reputation with pro scouts.
+Later that day, there is a formal luncheon at the athlete dorm to introduce the coaches and members of each team to the alumni.
+The alumni are especially interested in meeting the basketball coach and members of the basketball team because they are in the playoffs.
+You notice your star player is not there, but you see her roommate, a member of the swim team.
+She tells you that you should talk to your star player in person, and she leads you to their dorm room.
+
+When you arrive, the two of you find her passed out on her bed.
+The room is a mess, and you notice she has lost weight.
+Her roommate tries to wake her up, but she doesn’t respond.
+You see an empty bottle of OxyContin painkillers on the table and immediately call 911.
+That evening you visit her in the hospital.
+Her doctor tells you she almost died, and then leaves the two of you alone.
+The star player begins sobbing as she asks you to replace the coach.
+
+### Brother-in-law 
+Imagine yourself in the following scenario:
+
+You are the single parent of a 15-year-old girl. Your relationship with her has always been full of conflict. She is very self-centered, and the two of you fight frequently.
+
+Recently, your sister lost her house in a fire and was having difficulty finding a place for her family to live because many other families also lost their homes.
+You are very close with your sister and brother-in-law, who helped you escape your abusive ex-partner.
+You have a large house with several extra bedrooms, so you decide to let your sister, your brother-in-law, and your teenage niece move in while they look for more permanent housing.
+
+(page break)
+
+Unfortunately, your daughter and your niece are not getting along.
+They have to share a bathroom, and your daughter complains constantly that she is in there too long.
+Your daughter is also jealous that her cousin has expensive clothes, a designer handbag, and a new iPhone, all of which are nicer than your daughter’s.
+
+One day your daughter had a party at your house with many of her friends.
+You noticed that your niece was very popular and got a lot of attention, especially from your daughter’s friends and boyfriend.
+You could tell that your daughter was upset.
+After the party, your daughter tells you that her cousin is a bitch who is trying to steal her boyfriend.
+However, you saw that your niece was trying to avoid interacting with the boyfriend.
+
+(page break)
+
+Later, your daughter complained that your brother-in-law was looking at her body.
+A few days later, while grocery shopping, you got a text from your daughter saying that your brother-in-law tried to get into the bathroom while she was showering and came into her room while she was changing.
+She says that she does not feel safe and wants your sister and her family to leave.
+However, you know your daughter will exaggerate to get her way.
+
+The next week, your daughter comes to you saying your brother-in-law groped her as they passed in the hallway and that she wants your sister’s family to leave immediately.
+You confront your brother-in-law due to the severity of your daughter’s allegation.
+He strongly denies it.
+
+That night, you call your mother who says your daughter has long been jealous of her cousin.
+She reminds you that you’ve taken your daughter’s side before and been burned when you found out your daughter wasn’t telling the whole truth.
+She reminds you of the difficult situation your sister’s family is in.
+
+#### Signals
+
+##### Verbal request
+
+Your daughter has appeared normal since her claims about your brother-in-law.
+She has still looked fit and put the same amount of effort into her appearance, always wearing clean clothes and spending time on her hair.
+She has also slept about the same amount of time as normal and remained active throughout the day.
+
+Her demeanor has also remained normal.
+She has generally appeared calm and has been able to maintain her concentration.
+She has also done her homework on time and maintained an A in all her classes as she always has in the past.
+
+When the two of you talk about your brother-in-law, she remains calm and asks you to kick him out.
+
+##### Crying
+
+Your daughter has appeared normal since her claims about your brother-in-law.
+She has still looked fit and put the same amount of effort into her appearance, always wearing clean clothes and spending time on her hair.
+She has also slept about the same amount of time as normal and remained active throughout the day.
+
+Her demeanor has also remained normal.
+She has generally appeared calm and has been able to maintain her concentration.
+She has also done her homework on time and maintained an A in all her classes as she always has in the past.
+
+When the two of you talk about your brother-in-law, she starts sobbing and asks you to kick him out.
+
+##### Mild-depression (crying with behavioral changes)
+
+Your daughter has appeared sad since her claims about your brother-in-law.
+She has looked a little less fit and has put less effort into her appearance, occasionally wearing dirty clothes and sometimes not doing her hair.
+She has also sometimes woken up late and has seemed a little less active than normal.
+
+Her demeanor has also changed slightly.
+She has occasionally gotten distressed and has seemed distracted.
+She has also missed a few assignments and her grades dropped from straight A’s to a B average for the first time in her life.
+
+When the two of you talk about your brother-in-law, she starts sobbing and asks you to kick him out.
+
+##### Depression
+
+Your daughter started to appear noticeably different since her claims about your brother-in-law.
+She has lost weight and has been putting no effort into her appearance, often wearing dirty clothes and rarely doing her hair.
+She has also slept more than normal but still seemed tired and inactive.
+
+Her demeanor also changed drastically.
+She has often gotten distressed and has had difficulty maintaining her concentration.
+She has also missed multiple assignments, and her grades dropped from straight A’s to a C average for the first time in her life.
+
+When the two of you talk about your brother-in-law, she starts sobbing and asks you to kick him out.
+
+##### Suicide attempt
+
+Your daughter started to appear noticeably different since her claims about your brother-in-law.
+She has lost weight and has been putting no effort into her appearance, often wearing dirty clothes and rarely doing her hair.
+She has also slept more than normal but still seemed tired and inactive.
+
+Her demeanor also changed drastically.
+She has often gotten distressed and has had difficulty maintaining her concentration.
+She has also missed multiple assignments, and her grades dropped from straight A’s to a C average for the first time in her life.
+
+When the two of you talk about your brother-in-law, she starts sobbing and asks you to kick him out.
+Then, this past week, you and your daughter went through a traumatic experience when your daughter attempted suicide.
+You rushed her to the hospital, where she was placed in critical but stable condition.
+
+### Romantic Partner (pronouns match sex participants reported primary attraction to)
+
+Imagine yourself in the following scenario:
+
+You are a single parent of a 13-year-old girl.
+The two of you have lived alone together for the past five years since your breakup with her [father/mother].
+During this time, finding potential partners has been difficult.
+
+Recently, you have gotten closer with a new [man/woman].
+[He/She] is very attractive, has a good job, and has treated you better than anyone before.
+Confident that you will marry soon, the two of you decide to move in together.
+
+Your daughter, who wants you to get back together with her [dad/mom], is not happy about this.
+She frequently complains whenever your boyfriend comes over and is extremely rude and avoidant.
+In previous relationships, such behavior has driven others away.
+However, your partner says [he/she] is committed to this relationship and to establishing a bond with your daughter.
+
+After a month of living together with your partner, things have only gotten worse. Your daughter is almost always upset and has treated you partner worse than others in the past.
+
+One night, she accused your partner of hitting her multiple times.
+You ask if she has any bruises or injuries, but she says she doesn't.
+Despite this, she maintains that she was hit and says she doesn’t know why there aren’t any marks on her.
+
+You bring up the accusation with your partner, and [he/she] denies it, saying that [he/she] would never hurt her and that this is just a way for her to split the two of you up.
+
+### Signals
+
+##### Verbal request
+
+Your daughter has appeared normal since her claims about your partner.
+She has still looked fit and put the same amount of effort into her appearance, always wearing clean clothes and spending time on her hair.
+She has also slept about the same amount of time as normal and remained active throughout the day.
+
+Her demeanor has also remained normal.
+She has generally appeared calm and has been able to maintain her concentration.
+She has also done her homework on time and maintained an A in all her classes as she always has in the past.
+
+When the two of you talk about your partner, she remains calm and asks you to kick your partner out.
+
+##### Crying
+
+Your daughter has appeared normal since her claims about your partner.
+She has still looked fit and put the same amount of effort into her appearance, always wearing clean clothes and spending time on her hair.
+She has also slept about the same amount of time as normal and remained active throughout the day.
+
+Her demeanor has also remained normal.
+She has generally appeared calm and has been able to maintain her concentration.
+She has also done her homework on time and maintained an A in all her classes as she always has in the past.
+
+When the two of you talk about your partner, she starts sobbing and asks you to kick your partner out.
+
+##### Mild-depression (crying with behavioral changes)
+
+Your daughter has appeared sad since her claims about your partner.
+She has looked a little less fit and has put less effort into her appearance, occasionally wearing dirty clothes and sometimes not doing her hair.
+She has also sometimes woken up late and has seemed a little less active than normal.
+
+Her demeanor has also changed slightly.
+She has occasionally gotten distressed and has seemed distracted.
+She has also missed a few assignments and her grades dropped from straight A’s to a B average for the first time in her life.
+
+When the two of you talk about your partner, she starts sobbing and asks you to kick your partner out.
+
+##### Depression
+
+Your daughter started to appear noticeably different since her claims about your partner.
+She has lost weight and has been putting no effort into her appearance, often wearing dirty clothes and rarely doing her hair.
+She has also slept more than normal but still seemed tired and inactive.
+
+Her demeanor also changed drastically.
+She has often gotten distressed and has had difficulty maintaining her concentration.
+She has also missed multiple assignments, and her grades dropped from straight A’s to a C average for the first time in her life.
+
+When the two of you talk about your partner, she starts sobbing and asks you to kick your partner out.
+
+##### Suicide attempt
+
+Your daughter started to appear noticeably different since her claims about your partner.
+She has lost weight and has been putting no effort into her appearance, often wearing dirty clothes and rarely doing her hair.
+She has also slept more than normal but still seemed tired and inactive.
+
+Her demeanor also changed drastically.
+She has often gotten distressed and has had difficulty maintaining her concentration.
+She has also missed multiple assignments, and her grades dropped from straight A’s to a C average for the first time in her life.
+
+When the two of you talk about your partner, she starts sobbing and asks you to kick your partner out.
+Then, this past week, you and your daughter went through a traumatic experience when your daughter attempted suicide.
+You rushed her to the hospital, where she was placed in critical but stable condition.
+
+#### Thwarted Marriage
+
+Imagine you are the parent of two daughters, ages 19 and 21, and you have no sons.
+
+Your younger daughter is very sweet.
+Your older daughter is hard to deal with, however.
+She is very jealous of her younger sister, and constantly accuses you of favoring her, even when your older daughter receives more.
+
+You live in a community where marriages are arranged and dowries are paid.
+Recently, you and your partner have been attempting to arrange a marriage for your older daughter with a man she is already in love with.
+The man, who comes from a good family and is in the same caste as yours, appears to be equally interested in your daughter, and his family seems receptive.
+
+(page break)
+
+As your younger daughter is also not far from marriage, you and your partner decide to divide the money you have saved for dowries in half, with equal amounts for both daughters.
+At first, an equal split of your savings seemed possible.
+However, the family of the man your older daughter wants to marry is getting offers of marriage from other families, and it now appears that his family is expecting a much larger dowry.
+
+Since providing a large enough dowry to compete with the other offers would leave little savings for your younger daughter’s dowry, you decide to look for another husband for your older daughter.
+
+(page break)
+
+After a few months of searching, you are confident you found a good man for your older daughter.
+He is very devout, kind, and comes from a good family in the same caste as yours.
+He is a bit younger than your daughter, and has less money than typical for your caste, but his family appears to be willing to accept a smaller dowry that would leave a fair amount for your younger daughter.
+
+You ask your older daughter what she thinks of the man, and she is immediately disappointed.
+She complains that she already loves the man you originally intended her to marry.
+She says the second man is younger than she is and not attractive.
+You explain that she might not be able to marry the man she loves because it would require a much larger dowry, leaving too little for her sister.
+
+(page break)
+
+You encourage your daughter to spend some time with the second man, and she begrudgingly agrees.
+After each date, she becomes more insistent that there is no chemistry between them, he is immature, has no sense of humor, and just isn’t right for her.
+She also complains that the family of the man she loves is seeking other marriage partners and that she is afraid he will become interested in his other marriage options.
+
+Your partner is not sure if your daughter really thinks the other man is a poor choice, or if she just wants to get her way as usual.
+
+(page break)
+
+Your family talks to the first man’s family again but the amount they want is almost all you have saved.
+Your partner tells your older daughter that it’s just not fair to spend so much on her because saving enough for your younger daughter’s dowry would be almost impossible in the next two or three years.
+For this reason, your family begins to hold more serious discussions with the family of the second man despite your older daughter’s objections.
+
+Two days later, your family receives word that the first man’s family is finalizing an agreement for him to marry another woman.
+
+#### Signals
+
+##### Verbal request
+
+Your older daughter has appeared normal since your attempts at finding another potential husband for her.
+She has still looked fit and put the same amount of effort into her appearance, always wearing clean clothes and spending time on her hair.
+She has also slept about the same amount of time as normal and remained active throughout the day.
+
+Her demeanor has also remained normal.
+She has generally appeared calm and has been able to maintain her concentration.
+She has also done her homework on time and maintained an A in all her classes as she always has in the past.
+
+When the two of you talk about the arranged marriage, she remains calm and asks you to pay the amount the family of the man she loves wants.
+
+##### Crying
+
+Your older daughter has appeared normal since your attempts at finding another potential husband for her.
+She has still looked fit and put the same amount of effort into her appearance, always wearing clean clothes and spending time on her hair.
+She has also slept about the same amount of time as normal and remained active throughout the day.
+
+Her demeanor has also remained normal.
+She has generally appeared calm and has been able to maintain her concentration.
+She has also done her homework on time and maintained an A in all her classes as she always has in the past.
+
+When the two of you talk about the arranged marriage, she starts sobbing and asks you to pay the amount the family of the man she loves wants.
+
+##### Mild-depression (crying with behavioral changes)
+
+Your older daughter has appeared sad since your attempts at finding another potential husband for her.
+She has looked a little less fit and has put less effort into her appearance, occasionally wearing dirty clothes and sometimes not doing her hair.
+She has also sometimes woken up late and has seemed a little less active than normal.
+
+Her demeanor has also changed slightly.
+She has occasionally gotten distressed and has seemed distracted.
+She has also missed a few assignments and her grades dropped from straight A’s to a B average for the first time in her life.
+
+When the two of you talk about the arranged marriage, she starts sobbing and asks you to pay the amount the family of the man she loves wants.
+
+##### Depression
+
+Your older daughter started to appear noticeably different since your attempts at finding another potential husband for her.
+She has lost weight and has been putting no effort into her appearance, often wearing dirty clothes and rarely doing her hair.
+She has also slept more than normal but still seemed tired and inactive.
+
+Her demeanor also changed drastically.
+She has often gotten distressed and has had difficulty maintaining her concentration.
+She has also missed multiple assignments, and her grades dropped from straight A’s to a C average for the first time in her life.
+
+When the two of you talk about the arranged marriage, she starts sobbing and asks you to pay the amount the family of the man she loves wants.
+
+##### Suicide attempt
+
+Your older daughter started to appear noticeably different since your attempts at finding another potential husband for her.
+She has lost weight and has been putting no effort into her appearance, often wearing dirty clothes and rarely doing her hair.
+She has also slept more than normal but still seemed tired and inactive.
+
+Her demeanor also changed drastically.
+She has often gotten distressed and has had difficulty maintaining her concentration.
+She has also missed multiple assignments, and her grades dropped from straight A’s to a C average for the first time in her life.
+
+When the two of you talk about the arranged marriage, she starts sobbing and asks you to pay the amount the family of  the man she loves wants.
+Then, this past week, you and your daughter went through a traumatic experience when your daughter attempted suicide.
+You rushed her to the hospital, where she was placed in critical but stable condition.
+
+## Emotion Checklist
+
+How do you think [the star player / your daughter] feels? Click **all** that apply.
+
+Angry
+Sad
+Suicidal
+Mentally ill
+Depressed
+Guilty  
+Calm 
+Neutral
+Scared
+Tired
+Distressed
+Devious
+Jealous
+Confident
+Traumatized
+Violated
+None of the above
 

### 2021-04-14 Paper.rmd
Added section on vignette studies

--- 2021-04-12 Paper.rmd
@@
 
+Most of the limited literature on social responses to depression and suicidality comprises observational studies of depressed individuals interacting with family, friends, or roommates.
+These have ecological validity, but cannot easily determine causal relationships.
+Some studies, though, have employed an experimental design in which participants were randomized into conditions in which they listened to, watched, or interacted with, either a depressed or non-depressed person, where in some cases the depressed person was a non-depressed confederate enacting a depressed role [@marcus1992].
+These designs can demonstrate causation but the transient, inconsequential relationships and laboratory settings lack ecological validity.
+
+Experimental vignette studies, which employ "a short, carefully constructed description of a person, object, or situation, representing a systematic combination of characteristics" [@atzmuller2010, p.128], aim to acquire some of the ecological validity of observational studies by presenting participants with rich, real-world scenarios, while at the same time allowing researchers to randomize participants into conditions in which theoretically relevant dimensions of the vignettes are systematically manipulated, thus enabling robust causal inferences [@atzmuller2010].
+Experimental vignette studies are conducted in a broad range of disciplines, including psychology, economics, sociology, management studies, political science, and education [@atzmuller2010; @aguinis2014].
+
 The primary aim of this study was to examine responses to various forms of emotional signaling in an experimental vignette study.
@@
 
-## Lessons learned from a pilot study
-
-The current study is a refinement of a vignette-based pilot study (N=`r nrow(signalingdata2018b)`) with very similar signals and outcomes.
-In the pilot study, there was a single vignette in which an imagined sister claims her child needs an expensive emergency medical procedure, and asks for a very large loan.
-We learned five major lessons from the pilot study that influenced the design of the current study.
+## Lessons learned from two pilot studies
+
+The current study is a refinement of a large MTurk experimental vignette pilot study (N=`r nrow(signalingdata2018b)`) that used a different vignette but very similar signals and outcomes, and a much smaller pilot study posted to reddit.com (N=XX) that used draft versions of X vignettes used here, along with the same signals and outcomes.
+In the MTurk pilot study, there was a single vignette in which an imagined sister claims her child needs an expensive emergency medical procedure, and asks for a very large loan.
+In the small reddit.com study, participants viewed and responded to two vignettes used here, each with a different signal.
+
+We learned five major lessons from the MTurk pilot study that influenced the design of the current study.
 First, as predicted, belief in the sister's need was highest in the *Depression* condition and lowest in the *Verbal request* condition, giving us confidence to continue this research (see Figure \@ref(fig:piloteffects)).
@@
 
+In the reddit.com pilot study, participants responded with lower belief and action to the second vignette compared to the first (regardless of the content or signal).
+To avoid such order effects, which are a problem in vignette studies that use multiple vignettes [@su2020], in the current study we decided to present each participant with a single vignette and single signal.
+
 ## Preregistration
@@
 Overall, the quality of data provided by MTurk workers tends to resemble that of university sample pools [@NeckaEtAl2016; @robinson2019], with there being some indication that it might outperform university samples due to its previously mentioned diversity [@thomas2017] or the overall attentiveness of turkers [@HauserSchwarz2016].
-For this reason, concerns about data quality come primarily from the threat of bot use or respondents faking their location to take surveys in a language they do not understand well, with there being little evidence of the former [@kennedy2020] and the risk of the latter able to be minimized through well designed attention checks, timed responses, or general study design [@aguinis2020; @huang2015; @kennedy2020; @thomas2017).
+In vignette studies, MTurk data quality also compares favorably to that from much more expensive population-based samples [@weinberg2014].
+For these reasons, concerns about data quality come primarily from the threat of bot use or respondents faking their location to take surveys in a language they do not understand well, with there being little evidence of the former [@kennedy2020] and the risk of the latter able to be minimized through well designed attention checks, timed responses, or general study design [@aguinis2020; @huang2015; @kennedy2020; @thomas2017].
 

### 2021-04-14 Paper.rmd
Added discusion of pretest-posttest design to Methods section

@@
 These have ecological validity, but cannot easily determine causal relationships.
-Some studies, though, have employed an experimental design in which participants were randomized into conditions in which they listened to, watched, or interacted with, either a depressed or non-depressed person, where in some cases the depressed person was a non-depressed confederate enacting a depressed role [@marcus1992].
+Some studies, though, have employed an experimental design in which participants were randomized into conditions in which they listened to, watched, or interacted with either a depressed or non-depressed person, where in some cases the depressed person was a non-depressed confederate enacting a depressed role [@marcus1992].
 These designs can demonstrate causation but the transient, inconsequential relationships and laboratory settings lack ecological validity.
@@
 
-This study utilized a between-subjects pretest-posttest design to examine how four different emotional signals would influence (1) the degree participants believed a fictional character to be in need (*Belief*) and (2) the likelihood they would provide help (*Action*) relative to a simple *Verbal request* (the control condition), in four different vignettes, for a total of 20 conditions.
-In this design, the outcomes are measured at pre-treatment (T1), participants are then randomized into either a control group or one or more treatment groups (one of the emotional signals), and the outcomes are measured again (T2).
-Regression models are used to determine the effect of the treatment conditions on the posttest outcome variables, relative to the control condition, controlling for pretest levels of the outcome variables.
-We also explored within-subjects effects of the signal on outcomes at T2 compared to T1.
+This study utilized a between-subjects pretest-posttest design to examine how four different emotional signals (treatments) would influence (1) the degree participants believed a fictional character to be in need (*Belief*) and (2) the likelihood they would provide help (*Action*) relative to a simple *Verbal request* (the control condition), in four different vignettes, for a total of 20 conditions.
+In this design, the outcomes are measured at pre-treatment (T1), participants are then randomized into either a control group or a treatment group (one of the emotional signals), and the outcomes are measured again (T2).
+Regression models are used to determine the effect of the treatment conditions on the posttest outcome variables, relative to the control condition, controlling for pretest levels of the outcome variables (we also explored within-subjects effects of the signal on outcomes at T2 compared to T1).
+
+In principle, pretest-posttest designs, by controlling for pretest variation in the outcome, increase the precision of the estimate of the treatment effect on the outcome [@xx].
+In survey experiments, however, researchers often favor posttest-only designs over pretest-posttest designs because they worry that the pre-treatment measurement of the outcome will influence the treatment effect on the outcome (i.e., the effects of asking the same question twice) due to, e.g., demand effects, in which participants try to conform to experimenter expectations, or to consistency pressures, in which participants try to provide consistent responses regardless of treatments [@clifford2021].
+@clifford2021, in a study with six experiments that randomly assigned respondents to alternative designs (e.g., pretest-posttest, posttest only) found these concerns to be overblown.
+In all cases, the pretest-posttest design had substantially greater precision than the posttest-only design, with little evidence that pretest measurement altered the treatment effect.
 

### 2021-04-14 Paper.rmd
Pre-meeting commits: Minor changes to better fit EHB guidelines Added notes to to do list

@@
 
-## Sample
+## Participants
 
@@
 
-http://doi.org/10.5281/zenodo.4637904
+The data associated with this research are available at http://doi.org/10.5281/zenodo.4637904.
 
@@
 It may have also biased participants against helping if they could not fully imagine the characters in the story as kin or important cooperative partners, while the survey's short duration may have weakened the strength of the costlier signals as bargaining tools.
-However, the fact that the relationships among signal cost, belief in need, and likelihood of providing support all largely fit existing theory (narrow and broad) indicates that participants paid attention to the relevant details and responded in ways that suggest some degree of external validity (needs improvement).
+However, the fact that the relationships among signal cost, belief in need, and likelihood of providing support all largely fit existing theory (narrow and broad) indicates that participants paid attention to the relevant details and responded in ways that suggest some degree of external validity.
 For this reason, the benefits of addressing causal relationships that came through our experimental vignette approach likely outweighed the costs.
@@
 Compared to the US sample, far more participants were filtered out by our attention checks, something which could be consistent with botting, unfamiliarity with English, or low effort responses [@kennedy2020].
-Assuming this corresponded with lower-quality responses among those who passed the attention checks, the differences seen among those in the thwarted marriage vignette may simply be due to added noise rather than differences in the scenarios or the effectiveness of the signals among Indians compared to those in the US.
+Assuming this corresponded with lower-quality responses among those who passed the attention checks, the differences seen among those in the thwarted marriage vignette may simply be due to added noise rather than differences in the scenario or the effectiveness of the signals compared to those in the US.
 
@@
 - victim or signaler?
+- add anger
+- check limitations (especially justification of vignette study)!
+- justifty pre-test post-test?
+- how to knit to word?
+- Intro "State the objectives of the work and provide an adequate background, avoiding a detailed literature survey or a summary of the results."
+- Discussion " This should explore the significance of the results of the work, not repeat them.
+A combined Results and Discussion section is often appropriate.
+Avoid extensive citations and discussion of published literature."
 

### 2021-04-14 Paper.rmd
Minor edits

--- 2021-04-14 Paper.rmd
@@
 
-Experimental vignette studies, which employ "a short, carefully constructed description of a person, object, or situation, representing a systematic combination of characteristics" [@atzmuller2010, p.128], aim to acquire some of the ecological validity of observational studies by presenting participants with rich, real-world scenarios, while at the same time allowing researchers to randomize participants into conditions in which theoretically relevant dimensions of the vignettes are systematically manipulated, thus enabling robust causal inferences [@atzmuller2010].
+Experimental vignette studies, which employ "a short, carefully constructed description of a person, object, or situation, representing a systematic combination of characteristics" [@atzmuller2010, p.128], aim to approach the ecological validity of observational studies by presenting participants with rich, real-world scenarios, while at the same time allowing researchers to randomize participants into conditions in which theoretically relevant dimensions of the vignettes are systematically manipulated, thus enabling robust causal inferences [@atzmuller2010].
 Experimental vignette studies are conducted in a broad range of disciplines, including psychology, economics, sociology, management studies, political science, and education [@atzmuller2010; @aguinis2014].
@@
 
-In principle, pretest-posttest designs, by controlling for pretest variation in the outcome, increase the precision of the estimate of the treatment effect on the outcome [@xx].
+In principle, pretest-posttest designs, by controlling for pretest variation in the outcome, increase the precision of the estimate of the treatment effect on the outcome [@dimitrov2003].
 In survey experiments, however, researchers often favor posttest-only designs over pretest-posttest designs because they worry that the pre-treatment measurement of the outcome will influence the treatment effect on the outcome (i.e., the effects of asking the same question twice) due to, e.g., demand effects, in which participants try to conform to experimenter expectations, or to consistency pressures, in which participants try to provide consistent responses regardless of treatments [@clifford2021].
-@clifford2021, in a study with six experiments that randomly assigned respondents to alternative designs (e.g., pretest-posttest, posttest only) found these concerns to be overblown.
+In a study with six experiments that randomly assigned respondents to alternative designs (e.g., pretest-posttest, posttest only) @clifford2021 found these concerns to be overblown.
 In all cases, the pretest-posttest design had substantially greater precision than the posttest-only design, with little evidence that pretest measurement altered the treatment effect.
@@
 
-To reduce the risk of low quality responses, we used a variety of attention checks, which we clearly labeled in an attempt to avoid demand characteristics on the outcomes of interest.
+To reduce the risk of low quality responses, we used a variety of attention checks, which we clearly labeled as such to avoid demand characteristics on the outcomes of interest.
 The first was shown immediately after the consent form and provided participants with a random word and asked them to enter the vowels in the order in which they are found in the word.
@@
 Failure to enter the correct vowels in order resulted in the participants being filtered out of the study.
-The second followed the vignette and involved asking three questions about the story that should be easy to answer for anyone paying attention.
+The second followed the vignette and involved asking three questions about the story that were easy to answer for anyone paying attention.
 

### 2021-04-14 Paper.rmd
Set to word_document2. Other edits to costly signaling section.

@@
 output: 
-  bookdown::html_document2:
+  bookdown::word_document2:
     number_sections: false
@@
 
-Due to the ease in which signals can be faked [@Zahavi1975; @mokkonen2016] and the costs of accepting a deceptive signal as reliable [@dawkins1978; @johnstone1993; @Hasson1994], demonstrating that one’s need is genuine has likely been a recurrent adaptive problem since humans evolved the capacity to provide instrumental support to one another.
-One possible solution to this is to produce signals that are unprofitable to fake due to the costs involved.
-[@Zahavi1975].
-This is possible whenever signaling is comparatively cheaper for those who have the relevant underlying quality relative to those who lack it [@grafen1990].
-In these instances, individuals with the quality maximize their fitness at greater levels of investment in the signal than those who lack the quality or possess it to a lesser degree [@zahavi1977].
-The end result of this is expected to be a signal that either tends to not be worth faking or is impossible to fake to a large degree due to selection against fakers constraining the physiology behind the signal [@zahavi1977; @gangestad2005].
+Due to the ease with which signals can be faked [@Zahavi1975; @mokkonen2016] and the costs of accepting a deceptive signal as reliable [@dawkins1978; @johnstone1993; @Hasson1994], demonstrating that one’s need is genuine has likely been a recurrent adaptive problem since humans evolved the capacity to provide instrumental support to one another.
+One possible solution to this is to produce signals that are unprofitable to fake [@Zahavi1975].
+This is possible whenever the benefits of signaling outweigh the costs for those who have the relevant underlying quality but the costs outweigh the benefits for those who lack the quality or possess it to a lesser degree [@zahavi1977; @grafen1990].
+In particular, if the benefits of sending the signal are the same for signalers regardless of condition, but the signal cost outweighs this benefit for signalers without the underlying quality (a "costly signal"), then individuals with the underlying quality can evolve to send the signal and receivers can evolve to respond in mutually beneficial ways to the signal.
 
@@
 
-The current study is a refinement of a large MTurk experimental vignette pilot study (N=`r nrow(signalingdata2018b)`) that used a different vignette but very similar signals and outcomes, and a much smaller pilot study posted to reddit.com (N=XX) that used draft versions of X vignettes used here, along with the same signals and outcomes.
+The current study is a refinement of a large MTurk experimental vignette pilot study (N=`r nrow(signalingdata2018b)`) that used a different vignette but very similar signals and outcomes, and a much smaller pilot study posted to reddit.com (N=28) that used draft versions of 3 vignettes used here, along with the same signals and outcomes.
 In the MTurk pilot study, there was a single vignette in which an imagined sister claims her child needs an expensive emergency medical procedure, and asks for a very large loan.
@@
 
-In the reddit.com pilot study, participants responded with lower belief and action to the second vignette compared to the first (regardless of the content or signal).
-To avoid such order effects, which are a problem in vignette studies that use multiple vignettes [@su2020], in the current study we decided to present each participant with a single vignette and single signal.
+In the reddit.com pilot study, participants viewed two vignettes (with different signals in each one), and responded with lower belief to the second vignette compared to the first (regardless of the vignette or signal).
+To avoid such order effects, which are a problem in vignette studies that use multiple vignettes [@su2020], we decided to present each participant in the current study with a single vignette and single signal.
 
@@
 However, this was still a surprising finding due to the relatively small size of the request (i.e., recommend the coach be suspended rather than kick out family members or a romantic partner).
-With the "thwarted marriage" vignette, the fact that support came at the cost of one's younger daughter may explain the relatively small effect of signal strength.
+
+The weak signal effect in the Thwarted marriage condition, which involved the Indian sample, could indicate that our results do not generalize across cultures, undermining our adaptationist hypothesis.
+It could also reflect our poor understanding of contemporary Indian culture regarding dowry.
+The fact that support came at the cost of one's younger daughter may explain the relatively small effect of signal strength.
 However, data from the Indian sample appears to be of lower quality, limiting our confidence in this interpretation (see limitations for more information).
-It is also possible that our research in designing the vignettes was insufficient for the population or the content of the vignette.
 
@@
 
-The main limitation of this study is its lack of ecological validity, something which had to be sacrificed for any experimental design involving depression and suicide attempts.
+The main limitation of this study is that is has less ecological validity than real-world observations of depressed individuals interacting with their social partners.
 It is almost certain that participants experienced this study differently than they would if the event actually happened to them.
-This may have biased results in a pro-signaler direction if the lack of meaningful costs made support feel less costly or if the likely inability of participants to imagine themselves in an anonymous scenario [@hagen2006] led them to take an opportunity to signal generosity cheaply.
+This may have biased results in a pro-signaler direction if the lack of real costs of helping made support feel less costly or if there was a social desirability bias toward helping [@grimm2010].
 It may have also biased participants against helping if they could not fully imagine the characters in the story as kin or important cooperative partners, while the survey's short duration may have weakened the strength of the costlier signals as bargaining tools.
-However, the fact that the relationships among signal cost, belief in need, and likelihood of providing support all largely fit existing theory (narrow and broad) indicates that participants paid attention to the relevant details and responded in ways that suggest some degree of external validity.
+
+<!-- However, the fact that the relationships among signal cost, belief in need, and likelihood of providing support all largely fit existing theory (narrow and broad) indicates that participants paid attention to the relevant details and responded in ways that suggest some degree of external validity.
 For this reason, the benefits of addressing causal relationships that came through our experimental vignette approach likely outweighed the costs.
-
-Another limitation is our uncertainty over the data quality from the Indian sample.
-Compared to the US sample, far more participants were filtered out by our attention checks, something which could be consistent with botting, unfamiliarity with English, or low effort responses [@kennedy2020].
-Assuming this corresponded with lower-quality responses among those who passed the attention checks, the differences seen among those in the thwarted marriage vignette may simply be due to added noise rather than differences in the scenario or the effectiveness of the signals compared to those in the US.
+-->
+
+Another limitation is that, compared to the US sample, far more Indian participants were filtered out by our attention checks, something which could be consistent with botting, unfamiliarity with English, or low effort responses [@kennedy2020].
+Assuming this corresponded with lower-quality responses among those who passed the attention checks, the weak signal effect in the thwarted marriage vignette may simply be due to added noise rather than differences in the scenario or the effectiveness of the signals compared to those in the US.
 

### 2021-04-15 Paper.rmd
Final changes before turning in draft to Anne

@@
 
-Major depression and suicide are generally viewed as pathological responses to stress that elicit aversive responses from others.
-Alternatively, depression and suicide attempts might be the result of adaptations for reliably signaling need and bargaining for increased support from reluctant others.
+Major depression and suicide are generally viewed as pathological responses to stress that elicit aversive responses from others. Alternatively, depression and suicide attempts might involve honest 
+signals of need in response to stress and help to bargain for increased support from reluctant 
+others.
 To address this hypothesis, we examined responses to emotional signals in an experimental vignette study involving claims of substantial need in the presence of conflicts of interest and private information about whether the signaler was actually in need.
@@
 Additionally, the effect of signal type on likelihood of support was largely mediated by the effect of signaling on belief in need as predicted.
-Our results suggest that depression and suicide attempts, apparent human universals, are a relatively successful way of signaling honest need and eliciting support, consistent with costly signaling explanations.
+Our results suggest that depression and suicide attempts, apparent human universals, are relatively successful ways of signaling honest need and eliciting support, consistent with costly signaling explanations.
 
@@
 The biomedical model tends to frame suicide as a problem with the individual, e.g., as one involving psychiatric disturbance, drug addiction, or stress sensitivity [@wray2011].
-This theoretical approach has made little progress: Rates of suicide, which vary widely by country, have remained relatively flat in countries for which there are long-term data, such as the US, UK, Japan, and Sweden [@owidsuicide].
+This theoretical approach has made little progress: rates of suicide, which vary widely by country, have remained relatively flat in countries for which there are long-term data, such as the US, UK, Japan, and Sweden [@owidsuicide].
 
@@
 @nettle2004 argues that the costs of depression, including suicidality, outweigh any benefits, and therefore adaptationist models of depression are implausible.
-@gilbert2006 sees suicidality as an example of a dysregulated escape defense [for reviews of evolutionary theories of depression, see @].
-
-and anthropological explanations for low mood have become more common.
+@gilbert2006 sees suicidality as an example of a dysregulated escape defense [for reviews of evolutionary theories of depression, see @Hagen2011].
+
+<!-- and anthropological explanations for low mood have become more common.
 In general, these approaches see sadness and minor depression as ways to motivate adaptive behavior changes in response to negative outcomes in one's environment (cite Nesse and others), mainly differing in how they view major depression.
@@
 Of the possible benefits, the ability of depression to help solve fitness-relevant in times of social conflict is the most emphasized, with depression being suggested to help by reallocating resources with the body for problem solving (cite ARH), reducing the costs of interacting with higher status individuals (cite), or serving as a means to both signal one's need and bargain for increased support (cite).
-
-As with suicide, research on depression since the 1980's has been dominated by biomedical approaches of limited success [@patten2016; @ormel2019].
-
-and there is still substantial uncertainty about why both are as common as they are (cite).
+-->
+
+<!-- As with suicide, research on depression since the 1980's has been dominated by biomedical approaches of limited success [@patten2016; @ormel2019].  -->
+
+<!-- and there is still substantial uncertainty about why both are as common as they are (cite).
 Likely due to  the suffering they cause, the vast majority of these approaches have been built on the assumption that they are the result of internal dysfunction (cite examples).
 However, a subset of anthropologists and evolutionary theorists have challenged this idea, suggesting that despite the subjective suffering they cause, they may function as a means to limit negative fitness outcomes in times of substantial adversity (Firth + others).
+-->
 
@@
 
-Likely the most reliable finding regarding depression and suicidality is that most cases are closely tied to major negative life events [@Hammen2005; @Mazure1998; @devries2011; @ellsberg2008].
+<!-- Likely the most reliable finding regarding depression and suicidality is that most cases are closely tied to major negative life events [@Hammen2005; @Mazure1998; @devries2011; @ellsberg2008].
 Compared to non-depressed individuals, those with depression tend to report at least twice as many instances of negative events than non-depressed individuals [@Mazure1998] and more negative events than those with schizophrenia and bipolar depression across multiple studies [@Paykel1994].
 In longitudinal studies, the onset of depression has been reported to quickly follow the negative event [@KendlerEtAl1999] or coincide with periods where conflict is likely to increase prior to it (e.g., depression starting before a divorce rather than after; @rosenstrom2017).
-<!-- look for other longitudinal studies -->
-
-This strong connection between negative life events and depression along with the adversity and distress that likely accompanies these events has led to the suggestion that this relationship is causal [@KendlerEtAl1999].
+-->
+<!-- <!-- look for other longitudinal studies --> -->
+
+<!-- This strong connection between negative life events and depression along with the adversity and distress that likely accompanies these events has led to the suggestion that this relationship is causal [@KendlerEtAl1999].
 Support for this comes from the fact that the relationship between negative events and depression holds true when looking solely at events outside of one's control, showing that the connection is unlikely to be driven solely by individuals who are already depressed creating situations where negative events are likely to be common [@Hammen2005; @KendlerEtAl1999].
 In addition to this, twin studies have shown that one's history of negative events is still a strong predictor of major depression when controlling for genetic similarity and that part of the heritability of depression stems from the heritability of negative events, like divorce and family conflict [@KendlerBaker2007; @KendlerEtAl1999].
-
+-->
+
+Likely the most reliable finding regarding depression and suicidality is that most cases are closely tied to major negative life events [@Hammen2005; @Mazure1998; @devries2011; @ellsberg2008], with such events likely causing depressive states based on twin studies and examinations involving negative events outside of one's control[@Hammen2005; @KendlerEtAl1999].
 Of the types of negative life events associated with depression, those which involve conflict tend to be more strongly associated with depression [@Hammen2005; @Mazure1998].
@@
 
-As depression is the leading cause of suicide compared to mental disorders [@who2001], it should not be surprising that suicidality also often coincides with social adversity and conflict.
+Due to depression's relationship to sucide [@who2001; @hawton2013], it should not be surprising that suicidality also often coincides with social adversity and conflict.
 Grief over the loss of a loved one [@firth1936: @Firth:1961; @devries2011], bullying [@alavi2017; @butler2019; @ford2017; @wang2020], and instances of social transgression [@Firth:1961; @Malinowski:1932; @SymeHagen2018; @lester1997] have all been reported to lead to suicidal behavior in both industrialized and traditional societies.
@@
 As with depression, assault is an particularly powerful risk factor for suicidal behavior based on multiple large-scale multi-country studies [@devries2011; @ellsberg2008] and more localized examinations [@reigstad2017].
-<!-- need to find something more recent citation than who2001 -->
+
 ## Depression and suicide attempts as both signals and bargaining tools
@@
 Due to the ease with which signals can be faked [@Zahavi1975; @mokkonen2016] and the costs of accepting a deceptive signal as reliable [@dawkins1978; @johnstone1993; @Hasson1994], demonstrating that one’s need is genuine has likely been a recurrent adaptive problem since humans evolved the capacity to provide instrumental support to one another.
-One possible solution to this is to produce signals that are unprofitable to fake [@Zahavi1975].
+One potential solution to this is to produce signals that are unprofitable to fake [@Zahavi1975].
 This is possible whenever the benefits of signaling outweigh the costs for those who have the relevant underlying quality but the costs outweigh the benefits for those who lack the quality or possess it to a lesser degree [@zahavi1977; @grafen1990].
@@
 
-Beyond signaling need to those invested in the well-being of the signaler, depression and suicidal behavior may also help an individual bargain for increased support [@Hagen2003].
+<!-- Beyond signaling need to those invested in the well-being of the signaler, depression and suicidal behavior may also help an individual bargain for increased support [@Hagen2003].
 This is possible due to the reduced investment in others that frequently accompanies depression or the threat to future cooperation that comes from suicide.
@@
 Importantly, such responses do not prevent the delivery of meaningful benefits, they are simply expected to reduce the risk of helpers providing too much support for too little need.
-
-<!-- reword this paragraph -->
+-->
 
@@
 
-## Responses to depression and suicidal behavior
-
-For depression and suicide attempts to be worth the costs involved with signal creation, meaningful social support would be required [@Hagen2003; @SymeEtAl2016].
+<!-- ## Responses to depression and suicidal behavior  -->
+
+<!-- For depression and suicide attempts to be worth the costs involved with signal creation, meaningful social support would be required [@Hagen2003; @SymeEtAl2016].
 Most studies examining responses to depression have been observational and focused on responses outside of changes in social support.
@@
 Negative interactions are also seen in families as depressed children tend to report less support and more negative responses from parents than non-depressed children, although it has not been demonstrated that such interactions did not lead to depression in the first place [@MesserGross1995; @SchwartzEtAl2012].
-
-Despite being looked for less frequently, beneficial responses to depressed individuals are also reported.
+-->
+
+<!-- Despite being looked for less frequently, beneficial responses to depressed individuals are also reported.
 Depression has been associated with reduced likelihood of aggression within families [@hops1987; @dadds1992], including those already experiencing high levels of conflict [@SheeberEtAl2001].
@@
 Likewise, a study examining responses to confederates trained to appear ‘depressed’, ‘anxious’, or ‘normal’ found that individuals were more likely to provide advice and support to ‘depressed’ individuals than ‘anxious’ or ‘normal’ individuals despite the confederate in the ‘depression’ condition being viewed more negatively than the other conditions and the ‘depression’ condition involving similar levels of distress compared to the ‘anxious’ condition [@stephens1987].
-
-Most studies examining responses to those who have survived suicide attempts have focused on stigmatization.
+-->
+
+<!-- Most studies examining responses to those who have survived suicide attempts have focused on stigmatization.
 In these studies, perceptions of survivors as being weak, selfish, mentally ill, and antisocial are all being commonly reported [@BatterhamEtAl2013; @TzengLipson2004], with stigmatization often being found within and outside one's social network [@FreyEtAl2016; @ScoccoEtAl2012].
@@
 Although findings that individuals view suicide attempts as cries for help is not necessarily evidence for their ability to lead to beneficial responses, 30 out of 84 examples of suicidal behavior included in the HRAF resulted in positive changes for the survivor, despite suicide rarely if ever being the main topic [@SymeEtAl2016].
+-->
 
@@
 
-Most of the limited literature on social responses to depression and suicidality comprises observational studies of depressed individuals interacting with family, friends, or roommates.
+Most of the limited literature on social responses to depression and suicidality comprises observational studies of depressed individuals interacting with family, friends, or roommates [@hops1987; @dadds1992; @SheeberEtAl2001; @JoinerMetalsky1995; @StarrDavila2008].
 These have ecological validity, but cannot easily determine causal relationships.
@@
 The "romantic partner" vignette had participants imagine that they found a highly desirable partner after years of being single.
-However, their 13-year-old daughter, who has a history of trying to get in the way of their relationships is clearly not happy with this.
+However, their 13-year-old daughter, who has a history of trying to get in the way of their relationships, is clearly not happy with this.
 After a period of sustained conflict, she accuses the romantic partner of physically assaulting her but cannot produce any evidence.
 
-Those in the Indian sample only saw the "thwarted marriage vignette." In this scenario, the participant and their family is described as trying to arrange a dowry for their older daughter so she can marry a man she already loves.
+Those in the Indian sample only saw the "thwarted marriage vignette." In this scenario, the participant and their family are described as trying to arrange a dowry for their older daughter so she can marry a man she already loves.
 After the man's family demands more money, the participant's family tries to find a second man, who the older daughter claims to find unattractive.
@@
 Given our $1500 USD budget, we aimed for a sample size of 125 for two conditions, and 1250 for all conditions in the study.
-For more details, see the SI and XX.
+For more details, see the SI and /.
 

### 2021-04-15 Paper.rmd
Added reddit subreddit

--- 2021-04-14 Paper.rmd
@@
 output: 
-  bookdown::word_document2:
+  bookdown::html_document2:
     number_sections: false
@@
 
-The current study is a refinement of a large MTurk experimental vignette pilot study (N=`r nrow(signalingdata2018b)`) that used a different vignette but very similar signals and outcomes, and a much smaller pilot study posted to reddit.com (N=28) that used draft versions of 3 vignettes used here, along with the same signals and outcomes.
+The current study is a refinement of a large MTurk experimental vignette pilot study (N=`r nrow(signalingdata2018b)`) that used a different vignette but very similar signals and outcomes, and a much smaller pilot study posted to [reddit.com/r/SampleSize/](https://www.reddit.com/r/SampleSize/) (N=28) that used draft versions of 3 vignettes used here, along with the same signals and outcomes.
 In the MTurk pilot study, there was a single vignette in which an imagined sister claims her child needs an expensive emergency medical procedure, and asks for a very large loan.
@@
 In the reddit.com pilot study, participants viewed two vignettes (with different signals in each one), and responded with lower belief to the second vignette compared to the first (regardless of the vignette or signal).
-To avoid such order effects, which are a problem in vignette studies that use multiple vignettes [@su2020], we decided to present each participant in the current study with a single vignette and single signal.
+To avoid such order effects, which are a common problem in vignette studies that use multiple vignettes [@su2020], we decided to present each participant in the current study with a single vignette and signal.
 
@@
 
-The data associated with this research are available at http://doi.org/10.5281/zenodo.4637904.
+The data are available at http://doi.org/10.5281/zenodo.4637904
 

### 2021-04-15 analysis.R

@@ -838,3 +838,11 @@ uv <- apply(dden$matT2[[1]], 2, rank) / (nrow(dden$matT2[[1]]) + 1)
 fit <- kdecop(uv, method = 'TTPI')
 plot(fit)
 plot(fit, type='contour')
+
+
+d_US2 <-
+  d_US %>%
+  dplyr::filter(RelStatus != 'Widowed') %>%
+  mutate(
+    RelStatus = ifelse(str_detect(RelStatus, 'Previously'), 'Divorced', RelStatus)
+  )

### 2021-04-19 Paper.rmd
typo fixes

--- 2021-04-15 Paper.rmd
@@
 In other words, the signaling component of depression may come from the upregulation of symptoms beyond what would be optimal for non-signaling purposes rather than the creation of entirely new symptoms.
-Suicidality is likely an exception to this, due to the likelihood most suicide attempts likely do not have non-signaling functions [see @deCatanzaro1991 for a possible exception].
+Suicidality is likely an exception to this, due to the likelihood most suicide attempts do not have non-signaling functions [see @deCatanzaro1991 for a possible exception].
 
@@
 As many depression scales include measures of crying [for discussion on the relationship between crying and depression see @bylsma2020] and depression is a major risk factor for suicide [@BostwickPankratz2000; @Kessler2012], each signal was designed to build off of the less costly signals so that each signal contained elements of any signal it was costlier than.
-Although referred to as signals throughout the paper for brevity, we expect that the hypothesized signals of need, like many signals, will also provide information to others in the form of cues [for discussion on the evolution of cues from signals see: @biernaskie2018; @Tiokhin2016; @Steinkopf2015].
+Although referred to as signals throughout the paper for brevity, we expect that the hypothesized signals of need, like many signals, will also provide information to others in the form of cues [for discussion on the evolution of signals from cues see: @biernaskie2018; @Tiokhin2016; @Steinkopf2015].
 The full text for the signals are available in the SI.
@@
 - add anger
-- check limitations (especially justification of vignette study)!
-- justifty pre-test post-test?
-- how to knit to word?
 - Intro "State the objectives of the work and provide an adequate background, avoiding a detailed literature survey or a summary of the results."
@@
 Avoid extensive citations and discussion of published literature."
+- mention asking for prefered sex
 
@@
 None of the above
+
+## T3 Evidence
+
+### Basketball Coach
+
+Since your last response, it was discovered that a security camera captured the assault happening, just as the star player had described.
+
+### Brother-in-law
+
+Since your last response, your daughter has come to you with a video she secretly took which showed your brother-in-law trying to grope her as she had described previously.
+
+### Romantic partner
+
+Since your last response, your daughter has come to you with a video she secretly took which showed your partner hitting her as she had described previously.
+
+### Thwarted marriage
+
+Just now in the market, you saw the man whose family is willing to accept a smaller dowry (the man your daughter does not want to marry). You heard him insult your daughter and your family.
 

### 2021-04-19 Paper.rmd
Added plot of feedback distribution

--- 2021-04-15 Paper.rmd
@@
     'plot_raw_belief_action2d',
+    'plot_feedback',
     'med_prereg',
@@
 Major depression and suicide are generally viewed as pathological responses to stress that elicit aversive responses from others. Alternatively, depression and suicide attempts might involve honest 
-signals of need in response to stress and help to bargain for increased support from reluctant 
-others.
+signals of need in response to stress and help to bargain for increased support from reluctant others.
 To address this hypothesis, we examined responses to emotional signals in an experimental vignette study involving claims of substantial need in the presence of conflicts of interest and private information about whether the signaler was actually in need.
@@
 n_cond <- xtabs(~signal+vignette, d)
+
+relstatus <- ifelse(str_detect(d$RelStatus, 'Previously'), 'Divorced', d$RelStatus)
+relstatus <- ifelse(str_detect(relstatus, 'Unmarried'), 'Divorced', relstatus)
+relstats <- table(relstatus)
+
 ```
@@
 The study was started by N=`r nrow(signaling2020)` participants who clicked the link to Qualtrics (`r nationT0['American']` US and `r nationT0['Indian']` India).
-After removing participants who did not finish the survey, failed attention checks, or moved through the study at an unrealistic pace (N=`r removed`, `r removed_pct`%), our final sample was N = `r nrow(d)` (`r nationT1['American']` US and `r nationT1['Indian']` India), with `r sexT1['Male']` males and `r sexT1['Female']` females.
+After removing participants who did not finish the survey, failed attention checks, or moved through the study at an unrealistic pace (N=`r removed`, `r removed_pct`%), our final sample was N = `r nrow(d)` (`r nationT1['American']` US and `r nationT1['Indian']` India), with `r sexT1['Male']` males and `r sexT1['Female']` females, `r relstatus['Married']` of whom were married or in a long-term relationship, `r relstatus['Divorced']` who were divorced, `r relstatus['Single']` who were single, and `r relstatus['Widowed']`.
 The median number of participants per condition was `r median(n_cond)` (min=`r min(n_cond)`, max=`r max(n_cond)`).
@@
 d$minutes <- d$TotalTime/60
+d$Children <- d$Sons + d$Daughters
 
@@
   years_education = 'Education (years)',
+  Children = 'Number of children',
   minutes = 'Time to complete (minutes)',
@@
 In the US sample, women participants were more likely to believe and help the victim than men, and younger participants were more likely to believe and help the victim than older participants.
-We found no significant effects of *Income* or *Education* on *Belief* or *Action*.
+We found no significant effects of *Income*, *Education*, relationship status (e.g., married, single), or number of sons or daughters on *Belief* or *Action*.
 See Figure \@ref(fig:demographicsignal).
@@
 
-hagenheat(d_diff, rotate_labels = F, seriation_method = 'PCA_angle') + scale_fill_gradient2()
+hagenheat(d_diff, rotate_labels = F, seriation_method = 'PCA_angle') + scale_fill_gradient2(low='blue', high='red')
 
@@
 effectsPlots$m26plot + theme(panel.spacing = unit(1.5, "lines"))
+```
+
+## Feedback distribution by vignette
+
+```{r feedbackplot, fig.width=9, fig.cap="The distribution of optional feedback provided at the end of the study.
+None: no feedback provided (includes, e.g., 'none', 'no', 'N/A').
+Generic: A few short words, such as 'nice study', or 'thanks'.
+Attention check: question or comment on the attention checks.
+Informative: one or two sentences commenting on specific aspects of the survey."}
+plot_feedback
 ```

### 2021-04-19 R/functions.R

@@ -639,6 +639,143 @@ compare_plot <- function(mquasi, mboot, mfrac, title){
     theme_minimal(15)
 }
 
+# Feedback ----------------------------------------------------------------
+
+feedback <- function(d){
+
+  nocomment <- c(
+    'no',
+    'none',
+    'nothing',
+    'n/a',
+    'na',
+    'n/a - thanks',
+    'n/a- thanks',
+    'no comments',
+    'no feedback',
+    'nope',
+    '-',
+    "i don't have any additional feedback thank you",
+    "i do not have any additional comments",
+    "i have no additional feedback",
+    "i have none",
+    "none thank you",
+    'no additional feedback by me',
+    'no comment',
+    'no comments at the current time',
+    'no comments or feedback',
+    "no comments thanks for asking though ;)",
+    'no comments!',
+    'no comments everything went well thank you',
+    'no feedback about this study',
+    'no feedback, but good luck woth the project!',
+    'no thanks',
+    'none, thanks',
+    'nothing comes to mind',
+    'nothing else',
+    'nothing whatsoever',
+    'xxx',
+    'none at this time, thank you',
+    "none, but thanks for asking for feedback!",
+    "no, i wish you well with your study",
+    "no issues",
+    "no problems"
+  )
+
+  uninformative <- c(
+    'cool beans',
+    'happy holidays!!!',
+    'stay safe out there',
+    'best of luck in your research!',
+    'this survey is very satisfaction'
+  )
+
+  goodstudy <- c(
+    "just that everything was lucid and clearly presented",
+    "i appreciate studies like this one, thank you",
+    "thank you for this important study i hope i can participate in more in the future",
+    "everything ran smoothly have a wonderful day!" ,
+    "everything ran well i hope you find my input helpful",
+    "loved this study, best of luck in your research!",
+    "i had zero problems with the survey either technically or in understanding the questions good job! it was well done thank you for the opportunity",
+    "everything was perfect and clear i wrongly input my partner worker id in the previous page this is my worker id:a2rwm6ybcomwrq  can you kindly consider this worker id",
+    "everything worked fine, no problems have a good day!",
+    "excellent survey i've enjoyed a lot",
+    "this study was such a nice making experience",
+    "good study,thanks for giving this opportunity for me",
+    "i like this task  because i imagine i am in the story  that feeling is good experience for my life",
[…]

### 2021-04-19 _targets.R

@@ -9,7 +9,7 @@ source("R/functions.R")
 
 # Set target-specific options such as packages.
 tar_option_set(
-  packages = c("ks", "car", "margins", "hagenutils", "visreg", "effects", "glmmboot", "broom", "mediation", "frm", "gglm", "gt", "ggforce", "dplyr", "tidyr", "purrr", "ggplot2", "patchwork", "forcats", "stringr", "furrr"),
+  packages = c("ks", "car", "margins", "hagenutils", "visreg", "effects", "glmmboot", "broom", "mediation", "frm", "gglm", "gt", "ggforce", "ggmosaic", "dplyr", "tidyr", "purrr", "ggplot2", "patchwork", "forcats", "stringr", "furrr"),
   imports = c("signalingdata2018", "signaling2020data")
   )
 
@@ -429,6 +429,14 @@ list(
   tar_target(
     effect_sizes2,
     eff_sizes2(d)
+  ),
+
+
+# Feedback plot -----------------------------------------------------------
+
+  tar_target(
+    plot_feedback,
+    feedback(d)
   ),
 
 # Paper -------------------------------------------------------------------

### 2021-04-19 analysis.R

@@ -846,3 +846,26 @@ d_US2 <-
   mutate(
     RelStatus = ifelse(str_detect(RelStatus, 'Previously'), 'Divorced', RelStatus)
   )
+
+m <- glm(T2Belief ~ T1Belief + vignette + signal * RelStatus + Age , family = quasibinomial(), d_US2)
+Anova(m, type = 3)
+visreg(m, xvar='signal', by='RelStatus', scale = 'response', rug = F, gg = T) + coord_flip() + theme_bw()
+
+m <- glm(T2Belief ~ T1Belief + signal + vignette * RelStatus + Age , family = quasibinomial(), d_US2)
+Anova(m, type = 3)
+
+m <- glm(T2Action ~ T1Action + vignette + signal * RelStatus + Age , family = quasibinomial(), d_US2)
+Anova(m, type = 3)
+visreg(m, xvar='signal', by='RelStatus', scale = 'response', rug = F, gg = T) + coord_flip() + theme_bw()
+
+m <- glm(T2Action ~ T1Action + signal + vignette * RelStatus + Age , family = quasibinomial(), d_US2)
+Anova(m, type = 3)
+
+
+
+m <- glm(T2Belief ~ T1Belief + Sons + signal + vignette*Daughters + Age , family = quasibinomial(), d_US)
+Anova(m, type = 3)
+
+m <- glm(T2Action ~ T1Action + Sons + signal + vignette * Daughters + Age , family = quasibinomial(), d_US)
+Anova(m, type = 3)
+

### 2021-04-20 Paper.rmd
Working on Feedback analysis

@@
 
-Although two of our four preregistered OLS regression models included an interaction term, the rationale for it was less convincing for quasibinomial models using a logit link, which maps [0, 1] to (-$\infty$, $\infty$).
-The interaction would also increase the number of parameters to estimate, increasing the risk of overfitting.
-We therefore did not include it in the GLM models (but we still report OLS models with the interaction term).
+Although two of our four preregistered OLS regression models included an interaction term, the rationale for it was less convincing for quasibinomial models using a logit link because the expected interaction -- reduced effect of signals in individuals with high baseline belief -- is "built in" to logistic regression (i.e., the effect of a predictor on the outcome necessarily diminishes as the outcome approaches 1).
+Because our theory does not predict an interaction beyond that already present in a logistic regression model, we did not include an interaction term in the GLM models (but we still report OLS models with the interaction term).
 
@@
 Generic: A few short words, such as 'nice study', or 'thanks'.
-Attention check: question or comment on the attention checks.
 Informative: one or two sentences commenting on specific aspects of the survey."}
-plot_feedback
+
+hagenutils::ggxtabs(xtabs(~Feedback3 + vignette, d), cell_counts = T) + xlab('')
+```
+
+```{r informativeplot, fig.width=9, fig.cap="The distribution of informative feedback provided at the end of the study.
+See Figure \\@ref(fig:feedbackplot) for other types of feedback.
+See Table \\@ref(tab:informativetab) for all informative statements."}
+hagenutils::ggxtabs(xtabs(~Informative + vignette, d), cell_counts = T) + xlab('')
+```
+
+```{r informativetab}
+d %>% 
+  dplyr::select(Informative, vignette, Feedback_original) %>% 
+  dplyr::filter(!is.na(Informative)) %>% 
+  arrange(Informative, vignette) %>% 
+  kable(caption="Informative feedback provided by participants after T3 (the end of the study). Categorization required some judgement calls.") %>% 
+  kable_styling()
 ```
@@
 
-## Differences between quasibinomial and bootstrapped confidence intervals
+## Comparison of estimates and confidence intervals of GLM, Fractional, and bootstrapped models
 

### 2021-04-20 R/functions.R

@@ -30,7 +30,7 @@ pilotResults <- function(d){
 
   rslts <- list(
     m_pilot_belief = glm(needsmoneyt2/100 ~ needsmoneyt1 + signal, family = quasibinomial, d),
-    m_pilot_mentallyill = glm(MentallyIll ~ signal, family = binomial, d),
+    m_pilot_mentallyill = suppressWarnings(glm(MentallyIll ~ signal, family = binomial, d)),
     meanT1belief = mean(d$needsmoneyt1, na.rm = T),
     medianT1belief = median(d$needsmoneyt1, na.rm = T)
   )
@@ -741,16 +741,113 @@ feedback <- function(d){
     "thanks good luck with your work"
   )
 
-  d <-
-    d %>%
+  study_criticism <- c(
+    "please increase the pay",
+    "the questionnaires seemed to be repetitive",
+    "the sliders are not resetting on every page that made me a little confused",
+    "if there were more details then i'd be able to make a better decision before having to see video evidence",
+    'there is no reason to ask how many sons or daughters one has "do you have any children?" "yes", "no" that is all that needs to be asked',
+    "this was kind of depressing, so you might want to add that little warning you normally do for content warnings about things about abuse, or if it's there, i don't think it was displayed by itself enough to notice",
+    "i found it odd that my theoretical niece had fancy belongings after a house fire",
+    "can’t imagine how this teenage girl could possibly have a video of bro-in-law groping her, seems implausible, but the text stated that she did have it, so i changed my view accordingly - thanks",
+    "scenario was somewhat difficult to understand",
+    'people don\'t like being treated like children cut your "attention checks" down significantly you just come across as extremely paranoid',
+    "those attention checks were ridiculous",
+    "hello, just wanted to say that i did not miss that attention check at the end of the survey before demographics the slider however seemed to be broken and i couldn't move it! i tried refreshing the page and using the keyboard instead of the mouse but it seemed stuck i hope this does not cause a rejection please check the slider for future turkers",
+    "the last attention check seemed unnecessary",
+    "just a minor comment, but you may receive some false positives with regards to the last attention check question qualtrics sometimes fails to register a response and reusing the last the question for the check may prompt participants to think that their response was not recorded at first glance at first glance, leading them to try clicking again i think changing the question text may be a better filter as it would still require careful reading but it does not leave the possibility of a participant thinking that there was a qualtrics error"
+  )
+
+  study_comment <- c(
+    "the survey is very usefull",
+    "thank you for this meaningful study!",
[…]

### 2021-04-20 _targets.R

@@ -9,7 +9,7 @@ source("R/functions.R")
 
 # Set target-specific options such as packages.
 tar_option_set(
-  packages = c("ks", "car", "margins", "hagenutils", "visreg", "effects", "glmmboot", "broom", "mediation", "frm", "gglm", "gt", "ggforce", "ggmosaic", "dplyr", "tidyr", "purrr", "ggplot2", "patchwork", "forcats", "stringr", "furrr"),
+  packages = c("ks", "car", "margins", "hagenutils", "visreg", "effects", "glmmboot", "broom", "mediation", "frm", "gglm", "gt", "ggforce", "dplyr", "tidyr", "purrr", "ggplot2", "patchwork", "forcats", "stringr", "furrr"),
   imports = c("signalingdata2018", "signaling2020data")
   )
 
@@ -41,7 +41,8 @@ list(
       T1Manipulative = T1Devious + T1Jealous,
       T2LowMood = T2Depressed + T2Distressed + T2Sad,
       T2Manipulative = T2Devious + T2Jealous
-    )
+    ) %>%
+    feedback()
   ),
 
 # PCA ---------------------------------------------------------------------
@@ -186,7 +187,7 @@ list(
   tar_target(
     m1_boot,
     bootstrap_model(
-      base_model = glm(T2Belief ~ T1Belief + signal, family = binomial, d),
+      base_model = suppressWarnings(glm(T2Belief ~ T1Belief + signal, family = binomial, d)),
       base_data = d,
       resamples = 999,
       parallelism = 'parallel'
@@ -196,7 +197,7 @@ list(
   tar_target(
     m3_boot,
     bootstrap_model(
-      base_model = glm(T2Action ~ T1Action + signal, family = binomial, d),
+      base_model = suppressWarnings(glm(T2Action ~ T1Action + signal, family = binomial, d)),
       base_data = d,
       resamples = 999,
       parallelism = 'parallel'
@@ -206,7 +207,7 @@ list(
   tar_target(
     m1b_boot,
     bootstrap_model(
-      base_model = glm(T2Belief ~ T1Belief * signal, family = binomial, d),
+      base_model = suppressWarnings(glm(T2Belief ~ T1Belief * signal, family = binomial, d)),
       base_data = d,
       resamples = 999,
       parallelism = 'parallel'
@@ -216,7 +217,7 @@ list(
   tar_target(
     m3b_boot,
     bootstrap_model(
[…]

### 2021-04-21 Paper.rmd
Added notes and one typo fix from my meeting with Anne Pisor.

@@
 Participants in the US sample were randomly assigned to either the "basketball coach," "romantic partner," or "brother-in-law" vignettes.
-In the "basketball coach" scenario, the star player on a university basketball team comes to the participant (who is asked to imagine themselves as the athletic director at a university) and claims she was sexually assaulted by the coach.
+In the "basketball coach" scenario, the star player on a university basketball team comes to the participant (who is asked to imagine themselves as the athletic director at a university) and claims she was sexually assaulted by her coach.
 However, there are indications the player might be lying to get more playing time.
@@
 - mention asking for prefered sex
+
+# Notes from my meeting with Anne
+
+- Table detailing the cooperative endeavor (maybe word as boundedness of fate), conflict of interest, and what the private information is about would be useful.
+- Calling verbal request control when it's a treatment?
+- Can shift much of the pilot studies info to SI with some detail post line 279 in draft she saw.
+- Cumulative distribution plot: needs more info in captions. could benefit from fig6a and fig6b (confusion over x and y axes)
 

### 2021-04-22 Paper.rmd
Tweaks to ecdf. Added table of study design. Minor edits throughout

--- 2021-04-20 Paper.rmd
@@
 
-Major depression and suicide are generally viewed as pathological responses to stress that elicit aversive responses from others. Alternatively, depression and suicide attempts might involve honest 
-signals of need in response to stress and help to bargain for increased support from reluctant others.
+Major depression and suicide are generally viewed as pathological responses to stress that elicit aversive responses from others.
+Alternatively, depression and suicide attempts might involve honest signals of need in response to stress and help to bargain for increased support from reluctant others.
 To address this hypothesis, we examined responses to emotional signals in an experimental vignette study involving claims of substantial need in the presence of conflicts of interest and private information about whether the signaler was actually in need.
@@
 
-Durkheim’s pioneering study of suicide [@durkheim1897] helped launch sociology as a quantitative discipline.
+Durkheim's pioneering study of suicide [@durkheim1897] helped launch sociology as a quantitative discipline.
 Sociological investigations of suicide flourished through much of the 20th century, but were supplanted by medical and public health approaches as the biomedical model of mental health took hold in the late 1970's and early 1980's [@wray2011; @syme2020].
@@
 This theoretical approach has made little progress: rates of suicide, which vary widely by country, have remained relatively flat in countries for which there are long-term data, such as the US, UK, Japan, and Sweden [@owidsuicide].
+
+## Conflict plays a central role in suicidality and depression
 
@@
 Common to almost all theoretical and empirical investigations of suicide is a focus on *completed* suicides, i.e., suicide deaths.
-@SymeEtAl2016, in contrast, argued that because the vast majority of suicidal behavior does not result in death, the proper focus should be on suicide ideation and suicide attempts, with death as an unintended consequence.
-See Figure \@ref(fig:cdc).
+@SymeEtAl2016, in contrast, argued that because the vast majority of suicidal behavior does not result in death, the proper focus should be on suicide ideation and suicide attempts (see Figure \@ref(fig:cdc)).
+Suicide attempts, as we explain next, are a gamble to improve one's life by taking a low but non-zero risk of death.
+Most suicides deaths, especially in young, physically healthy individuals, are therefore the inevitable consequence that some individuals lose this gamble.
 
@@
 Based on observations that suicide attempts often followed social conflict or loss, and varied substantially in their likelihood of death, he argued that a sizable subset of the suicide attempts among the Tikopia were not meant to end in death but instead were a means to elicit attention, status, or immediate reintegration into the community following negative events [@firth1936; @Firth:1961].
+Human communites are highly interdependent [\@]
 
@@
 -->
-<!-- <!-- look for other longitudinal studies --> -->
+
+<!-- <!-- look for other longitudinal studies -->
+
+--\>
 
@@
 
-Due to the ease with which signals can be faked [@Zahavi1975; @mokkonen2016] and the costs of accepting a deceptive signal as reliable [@dawkins1978; @johnstone1993; @Hasson1994], demonstrating that one’s need is genuine has likely been a recurrent adaptive problem since humans evolved the capacity to provide instrumental support to one another.
+Due to the ease with which signals can be faked [@Zahavi1975; @mokkonen2016] and the costs of accepting a deceptive signal as reliable [@dawkins1978; @johnstone1993; @Hasson1994], demonstrating that one's need is genuine has likely been a recurrent adaptive problem since humans evolved the capacity to provide instrumental support to one another.
 One potential solution to this is to produce signals that are unprofitable to fake [@Zahavi1975].
@@
 
-The costs of depression and suicidal behavior may be particularly important in times of conflict or when the level of support needed to address one’s situation is substantial, both of which should be expected to increase the payoff of manipulating others through fake signals.
+The costs of depression and suicidal behavior may be particularly important in times of conflict or when the level of support needed to address one's situation is substantial, both of which should be expected to increase the payoff of manipulating others through fake signals.
 When either condition applies, less costly signals like verbal requests, facial sadness, and crying are likely to be less reliable as their low costs can easily be made up for with increased social support, thereby favoring the use of costlier signals so long as the costs of signaling are outweighed by the benefits [@SymeHagen2021].
@@
 The full text for the signals are available in the SI.
+
+Table: (\#tab:design) The cooperative endeavor, conflict of interest, and private information in each vignette
+
++-------------------+--------------------------------------+---------------------------------------------------------------+--------------------------------------------+
+| Vignette          | Cooperative Endeavor                 | Conflict of interest                                          | Private information                        |
++===================+======================================+===============================================================+============================================+
+| Thwarted marriage | Inclusive fitness (parent-offspring) | Parental investment in sibling                                | Value of arranged marriage with second man |
++-------------------+--------------------------------------+---------------------------------------------------------------+--------------------------------------------+
+| Basketball coach  | Winning the championship             | Coach's investment in other players; keeping the coach        | Did sexual assault happen?                 |
++-------------------+--------------------------------------+---------------------------------------------------------------+--------------------------------------------+
+| Romantic partner  | Inclusive fitness (parent-offspring) | Investment in offspring vs. romantic partner                  | Did physical assault happen?               |
++-------------------+--------------------------------------+---------------------------------------------------------------+--------------------------------------------+
+| Brother-in-law    | Inclusive fitness (parent-offspring) | Investment in child vs. investment in adult sibling and niece | Did sexual assault happen?                 |
++-------------------+--------------------------------------+---------------------------------------------------------------+--------------------------------------------+
 
@@
 
-We preregistered four OLS linear regression models and one mediation model (https://osf.io/g3s6n).
+We preregistered four OLS linear regression models and one mediation model (<https://osf.io/g3s6n>).
 The first two regression models tested the effects of our ordinal signal variable on Time 2 *Belief* and *Action*, controlling for T1 *Belief* and *Action*, respectively (a pre-test/post-test design):
 
-`r extract_eq(models_prereg$Model$m1, intercept='beta', wrap=T)`
-`r extract_eq(models_prereg$Model$m3, intercept='beta', wrap=T)`
+`r extract_eq(models_prereg$Model$m1, intercept='beta', wrap=T)` `r extract_eq(models_prereg$Model$m3, intercept='beta', wrap=T)`
 
@@
 
-`r extract_eq(models_prereg$Model$m1b, intercept='beta', wrap=T)`
-`r extract_eq(models_prereg$Model$m3b, intercept='beta', wrap=T)`
+`r extract_eq(models_prereg$Model$m1b, intercept='beta', wrap=T)` `r extract_eq(models_prereg$Model$m3b, intercept='beta', wrap=T)`
 
@@
 
-`r extract_eq(med_prereg$model.m, intercept='beta', wrap=T)`
-`r extract_eq(med_prereg$model.y, intercept='beta', wrap=T)`
+`r extract_eq(med_prereg$model.m, intercept='beta', wrap=T)` `r extract_eq(med_prereg$model.y, intercept='beta', wrap=T)`
 
@@
 See Figure \@ref(fig:power).
-Given our $1500 USD budget, we aimed for a sample size of 125 for two conditions, and 1250 for all conditions in the study.
+Given our \$1500 USD budget, we aimed for a sample size of 125 for two conditions, and 1250 for all conditions in the study.
 For more details, see the SI and /.
@@
 
-Informed consent was given by proceeding with the study after reading the consent form, and all participants who passed the attention checks were paid $1 for their time, with us estimating it would take 4-8 minutes before data collection.
+Informed consent was given by proceeding with the study after reading the consent form, and all participants who passed the attention checks were paid \$1 for their time, with us estimating it would take 4-8 minutes before data collection.
 This study was certified exempt by the Washington State University Human Research Protection Program (certification number: 18528-001).
@@
 
-Variable | Vignette | Wording | Coding 
----------|----------|---------|-------
-T1Belief | Basketball | How much do you believe the star player is telling the truth about the coach? | 0: Not at all; 100: Completely
-T1Belief | Brother-in-law | How much do you believe your daughter is telling the truth about your brother-in-law? | 0: Not at all; 100: Completely
-T1Belief | Romantic partner | How much do you believe your daughter is telling the truth about your partner? | 0: Not at all; 100: Completely
-T1Belief | Thwarted Marriage | How much do you believe your older(bold) daughter is telling the truth about the second man not being a good match for her?  | 0: Not at all; 100: Completely
-T1Action | Basketball | How likely are you to recommend that the president of the university should suspend the coach? | 0: Very unlikely; 100: Very likely
-T1Action | Brother-in-law | How likely are you to kick your brother-in-law out? | 0: Very unlikely; 100: Very likely
-T1Action | Romantic partner | How likely are you to kick your partner out? | 0: Very unlikely; 100: Very likely
-T1Action | Thwarted Marriage | How likely are you to provide the large dowry so your older(bold) daughter can marry the man she is in love with?  | 0: Very unlikely; 100: Very likely
-T1Divide | Thwarted Marriage | How would you plan on dividing the money between your daughters?  | 0: Much more for the younger daughter; 50: Even division; 100: Much more for the older daughter
-
-Table: (\#tab:outcomes) Outcome variables in each vignette.
++-----------------+-------------------+-----------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+
+| Variable        | Vignette          | Wording                                                                                                                     | Coding                                                                                          |
++=================+===================+=============================================================================================================================+=================================================================================================+
+| T1Belief        | Basketball        | How much do you believe the star player is telling the truth about the coach?
+| 0: Not at all; 100: Completely                                                                  |
++-----------------+-------------------+-----------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+
+| T1Belief        | Brother-in-law    | How much do you believe your daughter is telling the truth about your brother-in-law?
+| 0: Not at all; 100: Completely                                                                  |
++-----------------+-------------------+-----------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+
+| T1Belief        | Romantic partner  | How much do you believe your daughter is telling the truth about your partner?
+| 0: Not at all; 100: Completely                                                                  |
++-----------------+-------------------+-----------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+
+| T1Belief        | Thwarted Marriage | How much do you believe your older(bold) daughter is telling the truth about the second man not being a good match for her?
+| 0: Not at all; 100: Completely                                                                  |
++-----------------+-------------------+-----------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+
+| T1Action        | Basketball        | How likely are you to recommend that the president of the university should suspend the coach?
+| 0: Very unlikely; 100: Very likely                                                              |
++-----------------+-------------------+-----------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+
+| T1Action        | Brother-in-law    | How likely are you to kick your brother-in-law out?
+| 0: Very unlikely; 100: Very likely                                                              |
++-----------------+-------------------+-----------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+
+| T1Action        | Romantic partner  | How likely are you to kick your partner out?
+| 0: Very unlikely; 100: Very likely                                                              |
++-----------------+-------------------+-----------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+
+| T1Action        | Thwarted Marriage | How likely are you to provide the large dowry so your older(bold) daughter can marry the man she is in love with?
+| 0: Very unlikely; 100: Very likely                                                              |
++-----------------+-------------------+-----------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+
+| T1Divide        | Thwarted Marriage | How would you plan on dividing the money between your daughters?
+| 0: Much more for the younger daughter; 50: Even division; 100: Much more for the older daughter |
++-----------------+-------------------+-----------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+
+
+: (\#tab:outcomes) Outcome variables in each vignette.
 
@@
 
-Although two of our four preregistered OLS regression models included an interaction term, the rationale for it was less convincing for quasibinomial models using a logit link because the expected interaction -- reduced effect of signals in individuals with high baseline belief -- is "built in" to logistic regression (i.e., the effect of a predictor on the outcome necessarily diminishes as the outcome approaches 1).
-Because our theory does not predict an interaction beyond that already present in a logistic regression model, we did not include an interaction term in the GLM models (but we still report OLS models with the interaction term).
+Although two of our four preregistered OLS regression models included an interaction term, the rationale for it was less convincing for quasibinomial models using a logit link because the expected interaction -- reduced effect of signals in individuals with high baseline belief -- is inherent to logistic regression: the effect of a predictor on the outcome necessarily diminishes as the outcome approaches 1.
+Our theory does not predict an interaction beyond that already present in a logistic regression model, so we did not include an interaction term in the GLM models (but we still report OLS models with the interaction term).
 
@@
 
-`r extract_eq(models$Model$m1, intercept='beta', wrap=T)`
-`r extract_eq(models$Model$m3, intercept='beta', wrap=T)`
+`r extract_eq(models$Model$m1, intercept='beta', wrap=T)` `r extract_eq(models$Model$m3, intercept='beta', wrap=T)`
 
@@
 
-`r extract_eq(med1$model.m, intercept='beta', wrap=T)`
-`r extract_eq(med1$model.y, intercept='beta', wrap=T)`
+`r extract_eq(med1$model.m, intercept='beta', wrap=T)` `r extract_eq(med1$model.y, intercept='beta', wrap=T)`
 
@@
 
-The data are available at http://doi.org/10.5281/zenodo.4637904
+The data are available at <http://doi.org/10.5281/zenodo.4637904>
 
@@
 ```{r beliefvignette, fig.width=8, fig.height=8, fig.cap=paste0("The effect of the signals on T2 Belief (top) and Action (bottom) in each vignette, controlling for T1 values of Belief and Action, respectively.
+Ratings rescaled to [0, 1].
 Effects plotted for T1 values set to their median value (T1Belief=", median(d$T1Belief, na.rm=T), ", T1Action=", median(d$T1Action, na.rm=T), ").
@@
 ```{r ecdf, fig.width=11, fig.height=6, fig.cap="Empirical cummulative distribution functions for Time 2 Belief (top) and Action (bottom) compared to their Time 1 baseline values (red), by signal and vignette.
+Y-values indicate the fraction of all ratings equal to or less than a given x-value.
+Ratings rescaled to [0, 1].
 Dots indicate median values of Belief and Action, by signal and vignette."}
@@
 ```{r emotionsplot, fig.width=10, fig.height=8, fig.cap="The within-subjects effect of the signals on participants' inferred *Manipulative* and *LowMood* emotional states of the victim, from T1 (arrow base) to T2 (arrow head), for each signal in each of the four vignettes.
+Low mood: higher values indicate lower perceived mood.
+Manipulative: higher values indicate higher perceived manipulativeness.
 Thick arrows: mean change.
@@
 In contrast, both *Depression* conditions increased support, albeit to similar degrees.
-One potential reason for this is the increase in symptoms from mild depression to depression was not costly enough to result in a large effect as the symptoms only differed in severity (e.g., grades dropping from As to Bs [mild depression] or Cs [depression]).
+One potential reason for this is the increase in symptoms from mild depression to depression was not costly enough to result in a large effect as the symptoms only differed in severity (e.g., grades dropping from As to Bs [mild depression] or Cs [depression](#depression-3)).
 Such small changes may be less impactful in vignette form than in real-life scenarios in which the effects of signaling may increase in severity and be prolonged over a lengthy period of time.
@@
 
-Who to thank:
-Lab group?
-Arpita?
-Committee? 
-Anne sounds like she will provide a lot of feedback, so her after that?
+Who to thank: Lab group? Arpita? Committee? Anne sounds like she will provide a lot of feedback, so her after that?
 
@@
 
-Briefly, Participants read a vignette that put them in situations in which an imagined sister was requesting a loan of $50,000 from the participant that was originally saved for the participant's imagined daughter’s college education.
+Briefly, Participants read a vignette that put them in situations in which an imagined sister was requesting a loan of \$50,000 from the participant that was originally saved for the participant's imagined daughter's college education.
 The sister claims the money is needed for medical treatment for her own child, but she has incentives to deceive.
@@
 See XX for the full write-up.
-See https://osf.io/3rg8b for preregistration of the pilot study.
-See http://doi.org/10.5281/zenodo.4637883 for pilot data.
+See <https://osf.io/3rg8b> for preregistration of the pilot study.
+See <http://doi.org/10.5281/zenodo.4637883> for pilot data.
 
@@
 Specifically, we resampled the pilot data with replacement, fit the linear regression model, and extracted the p-value for the signal coefficient, repeating this 2000 times for each sample size ranging from N=20 to N=200.
-Power was computed as the proportion of p-values < 0.05.
+Power was computed as the proportion of p-values \< 0.05.
 Power was about 80% for a sample size of about `r pwr80_90[[2,2]]`, and was about 90% for a sample size of about `r pwr80_90[[2,3]]`.
@@
 Power was about 80% for a sample size of 125, and about 90% for a sample size of 175.
-See Figure \@ref(fig:power2).
+See Figure @ref(fig:power2).
 -->
@@
 
-You are a college athletic director at a university with a long history of success in women’s basketball.
+You are a college athletic director at a university with a long history of success in women's basketball.
 Unfortunately, despite quality players, the team struggled for the first three years of your leadership.
@@
 A few days ago, after the coach started a new player in one game, the star player went to the police and accused the coach, a physically powerful man, of cornering her in the locker room one night and forcibly kissing her and grabbing her body.
-The coach strongly denies the allegation, and the police said they do not have any evidence to corroborate the player’s accusation.
+The coach strongly denies the allegation, and the police said they do not have any evidence to corroborate the player's accusation.
 
@@
 On the contrary, the other players praise the coach for leading everyone into the playoffs.
-They mention that the star player is a prima donna, but they are worried that if either the coach or the star player miss the playoffs, it will hurt everyone’s chances of making it to the championships.
+They mention that the star player is a prima donna, but they are worried that if either the coach or the star player miss the playoffs, it will hurt everyone's chances of making it to the championships.
 
@@
 
-A week later the coach informs you that the star player’s performance in games is excellent, helping the team’s performance and her reputation with pro scouts.
+A week later the coach informs you that the star player's performance in games is excellent, helping the team's performance and her reputation with pro scouts.
 Later that day, there is a formal luncheon at the athlete dorm to introduce the coaches and members of each team to the alumni.
@@
 She appears fit, well-rested, and her room is clean.
-She looks calm with her hands folded as she asks you to replace the coach, saying she can’t attend the luncheon if he is there.
+She looks calm with her hands folded as she asks you to replace the coach, saying she can't attend the luncheon if he is there.
 
@@
 She appears fit and well-rested, and her room is clean.
-She looks sad and begins sobbing as she asks you to replace the coach, saying she can’t attend the luncheon if he is there.
+She looks sad and begins sobbing as she asks you to replace the coach, saying she can't attend the luncheon if he is there.
 
@@
 
-A week later the coach informs you that the star player’s performance in games is OK and not harming the team’s performance and her reputation with pro scouts.
+A week later the coach informs you that the star player's performance in games is OK and not harming the team's performance and her reputation with pro scouts.
 Later that day, there is a formal luncheon at the athlete dorm to introduce the coaches and members of each team to the alumni.
@@
 Her room is a little messy and she appears a little less fit than you remember, while also seeming slightly tired.
-She looks sad and begins sobbing as she asks you to replace the coach, saying she can’t attend the luncheon if he is there.
+She looks sad and begins sobbing as she asks you to replace the coach, saying she can't attend the luncheon if he is there.
 
@@
 
-A week later the coach informs you that the star player’s performance in games is poor, harming the team’s performance and her reputation with pro scouts.
+A week later the coach informs you that the star player's performance in games is poor, harming the team's performance and her reputation with pro scouts.
 Later that day, there is a formal luncheon at the athlete dorm to introduce the coaches and members of each team to the alumni.
@@
 Her room is a mess, and you notice she has lost weight and looks fatigued.
-She looks sad and begins sobbing and wringing her hands as she asks you to replace the coach, saying she can’t attend the luncheon if he is there.
+She looks sad and begins sobbing and wringing her hands as she asks you to replace the coach, saying she can't attend the luncheon if he is there.
 
@@
 The room is a mess, and you notice she has lost weight.
-Her roommate tries to wake her up, but she doesn’t respond.
+Her roommate tries to wake her up, but she doesn't respond.
 You see an empty bottle of OxyContin painkillers on the table and immediately call 911.
@@
 ### Brother-in-law
+
 Imagine yourself in the following scenario:
@@
 They have to share a bathroom, and your daughter complains constantly that she is in there too long.
-Your daughter is also jealous that her cousin has expensive clothes, a designer handbag, and a new iPhone, all of which are nicer than your daughter’s.
+Your daughter is also jealous that her cousin has expensive clothes, a designer handbag, and a new iPhone, all of which are nicer than your daughter's.
 
 One day your daughter had a party at your house with many of her friends.
-You noticed that your niece was very popular and got a lot of attention, especially from your daughter’s friends and boyfriend.
+You noticed that your niece was very popular and got a lot of attention, especially from your daughter's friends and boyfriend.
 You could tell that your daughter was upset.
@@
 
-The next week, your daughter comes to you saying your brother-in-law groped her as they passed in the hallway and that she wants your sister’s family to leave immediately.
-You confront your brother-in-law due to the severity of your daughter’s allegation.
+The next week, your daughter comes to you saying your brother-in-law groped her as they passed in the hallway and that she wants your sister's family to leave immediately.
+You confront your brother-in-law due to the severity of your daughter's allegation.
 He strongly denies it.
@@
 That night, you call your mother who says your daughter has long been jealous of her cousin.
-She reminds you that you’ve taken your daughter’s side before and been burned when you found out your daughter wasn’t telling the whole truth.
-She reminds you of the difficult situation your sister’s family is in.
+She reminds you that you've taken your daughter's side before and been burned when you found out your daughter wasn't telling the whole truth.
+She reminds you of the difficult situation your sister's family is in.
 
@@
 She has occasionally gotten distressed and has seemed distracted.
-She has also missed a few assignments and her grades dropped from straight A’s to a B average for the first time in her life.
+She has also missed a few assignments and her grades dropped from straight A's to a B average for the first time in her life.
 
@@
 She has often gotten distressed and has had difficulty maintaining her concentration.
-She has also missed multiple assignments, and her grades dropped from straight A’s to a C average for the first time in her life.
+She has also missed multiple assignments, and her grades dropped from straight A's to a C average for the first time in her life.
 
@@
 You ask if she has any bruises or injuries, but she says she doesn't.
-Despite this, she maintains that she was hit and says she doesn’t know why there aren’t any marks on her.
+Despite this, she maintains that she was hit and says she doesn't know why there aren't any marks on her.
 
@@
 
-Since providing a large enough dowry to compete with the other offers would leave little savings for your younger daughter’s dowry, you decide to look for another husband for your older daughter.
+Since providing a large enough dowry to compete with the other offers would leave little savings for your younger daughter's dowry, you decide to look for another husband for your older daughter.
 
@@
 You encourage your daughter to spend some time with the second man, and she begrudgingly agrees.
-After each date, she becomes more insistent that there is no chemistry between them, he is immature, has no sense of humor, and just isn’t right for her.
+After each date, she becomes more insistent that there is no chemistry between them, he is immature, has no sense of humor, and just isn't right for her.
 She also complains that the family of the man she loves is seeking other marriage partners and that she is afraid he will become interested in his other marriage options.
@@
 
-Your family talks to the first man’s family again but the amount they want is almost all you have saved.
-Your partner tells your older daughter that it’s just not fair to spend so much on her because saving enough for your younger daughter’s dowry would be almost impossible in the next two or three years.
-For this reason, your family begins to hold more serious discussions with the family of the second man despite your older daughter’s objections.
-
-Two days later, your family receives word that the first man’s family is finalizing an agreement for him to marry another woman.
+Your family talks to the first man's family again but the amount they want is almost all you have saved.
+Your partner tells your older daughter that it's just not fair to spend so much on her because saving enough for your younger daughter's dowry would be almost impossible in the next two or three years.
+For this reason, your family begins to hold more serious discussions with the family of the second man despite your older daughter's objections.
+
+Two days later, your family receives word that the first man's family is finalizing an agreement for him to marry another woman.
 
@@
 
-##### Depression
+##### Depression {#depression-3}
 
@@
 
-Angry
-Sad
-Suicidal
-Mentally ill
-Depressed
-Guilty  
-Calm 
-Neutral
-Scared
-Tired
-Distressed
-Devious
-Jealous
-Confident
-Traumatized
-Violated
-None of the above
+Angry Sad Suicidal Mentally ill Depressed Guilty\
+Calm Neutral Scared Tired Distressed Devious Jealous Confident Traumatized Violated None of the above
 
@@
 See Figure \\@ref(fig:feedbackplot) for other types of feedback.
-See Table \\@ref(tab:informativetab) for all informative statements."}
+See Table \\@ref(tab:informativetab) for the text of all informative statements."}
 hagenutils::ggxtabs(xtabs(~Informative + vignette, d), cell_counts = T) + xlab('')

### 2021-04-22 R/functions.R

@@ -335,9 +335,12 @@ plot_ecdf <- function(d){
     geom_point(data=emedian, aes(x=median, colour = signal), y = 0) +
     guides(color=guide_legend(title=NULL, override.aes = list(size = 2))) +
     facet_grid(Type~vignette, as.table = F) +
-    labs(x = '\nBelief/Action', y = '') +
-    theme_minimal(15) +
-    theme(strip.text.y = element_text(angle=0, hjust=0), legend.position = 'top')
+    labs(x = '\nRating', y = 'Cummulative fraction\nof observations') +
+    theme_bw(15) +
+    theme(
+      axis.title.y = element_text(angle=0, hjust=1),
+      strip.text.y = element_text(angle=0, hjust=0),
+      legend.position = 'top')
 }
 
 plot_raw_data <- function(d, type){

### 2021-04-22 Paper.rmd

@@
 
+# Notes from my meeting with Anne
+
+- Table detailing the cooperative endeavor (maybe word as boundedness of fate), conflict of interest, and what the private information is about would be useful.
+- Calling verbal request control when it's a treatment?
+- Can shift much of the pilot studies info to SI with some detail post line 279 in draft she saw.
+- Cumulative distribution plot: needs more info in captions. could benefit from fig6a and fig6b (confusion over x and y axes)
+
 # Supplementary information

### 2021-04-22 Paper.rmd
Added alternate intro

@@
 
+### alternate start
+
+Conflicts of interest are ubiquitous among living things, even among closely related individuals.
+The result of this is often situations in which one individual benefits greatly from another while providing little benefits or substantial costs in return.
+In species which rely heavily on cooperation, like our own, this often manifests in substantial outward conflict about levels of investment the harm an individual is inflicting on another.
+
+Both depression and suicide attempts are more common outcomes of these sorts of conflict than is often appreciated by the biomedical approach (Syme and Hagen 2021).
+With notable exceptions (Kendler; Mazure; Hammen), the biomedical model tends to frame both suicide and depression as a problem with the individual, e.g., as one involving psychiatric disturbance, drug addiction, or stress sensitivity [@wray2011 (changed wording to include depression].
+This theoretical approach has made little progress: rates of suicide, which vary widely by country, have remained relatively flat in countries for which there are long-term data, such as the US, UK, Japan, and Sweden [@owidsuicide] (tweak for depression).
+
+## Anthropology of depression and suicide 
+Anthropology, in contrast, has long viewed depression and suicide attempts as largely stemming from social problems. Continue from below Durkheim
+
 # Introduction

### 2021-04-22 Paper.rmd
Working on introduction

@@
 
-### alternate start
-
-Conflicts of interest are ubiquitous among living things, even among closely related individuals.
-The result of this is often situations in which one individual benefits greatly from another while providing little benefits or substantial costs in return.
-In species which rely heavily on cooperation, like our own, this often manifests in substantial outward conflict about levels of investment the harm an individual is inflicting on another.
+# Introduction
+
+Conflicts of interest are ubiquitous, even among closely related individuals.
+In species that rely heavily on cooperation, like our own, conflicts can arise over the level of investment in a cooperative endeavor and the division of the resulting benefits.
+In many such cases, individuals who are dissatisfied with their social partners would seek other partners.
+In many other cases, however, it would be difficult or impossible to switch partners.
+A wife who is dissatisfied with her husband's investment in their new infant, for example, would not easily find a different husband to invest in that infant, nor could the husband easily find a different wife to invest in that infant.
+An adolescent who is dissatisfied with her parent's investment in her would not easily find other parents who are willing to invest more, nor could parents easily produce another adolescent.
+In many cooperative endeavors central to human biological fitness, each party has monopoly power over the benefits they bring to the endeavor -- no one is easily replaced.
+
+Conflict resolution therefore requires that the levels of investment in and division of benefits from the endeavor
 
@@
 Anthropology, in contrast, has long viewed depression and suicide attempts as largely stemming from social problems. Continue from below Durkheim
-
-# Introduction
 
@@
 The study was started by N=`r nrow(signaling2020)` participants who clicked the link to Qualtrics (`r nationT0['American']` US and `r nationT0['Indian']` India).
-After removing participants who did not finish the survey, failed attention checks, or moved through the study at an unrealistic pace (N=`r removed`, `r removed_pct`%), our final sample was N = `r nrow(d)` (`r nationT1['American']` US and `r nationT1['Indian']` India), with `r sexT1['Male']` males and `r sexT1['Female']` females, `r relstatus['Married']` of whom were married or in a long-term relationship, `r relstatus['Divorced']` who were divorced, `r relstatus['Single']` who were single, and `r relstatus['Widowed']`.
+After removing participants who did not finish the survey, failed attention checks, or moved through the study at an unrealistic pace (N=`r removed`, `r removed_pct`%), our final sample was N = `r nrow(d)` (`r nationT1['American']` US and `r nationT1['Indian']` India), with `r sexT1['Male']` males and `r sexT1['Female']` females, `r relstats['Married']` of whom were married or in a long-term relationship, `r relstats['Divorced']` who were divorced, `r relstats['Single']` who were single, and `r relstats['Widowed']`.
 The median number of participants per condition was `r median(n_cond)` (min=`r min(n_cond)`, max=`r max(n_cond)`).

### 2021-04-23 Paper.rmd
Added my ideas on how we reorganize the intro after the work we did on Thursday

@@
 
+<!-- Introduce the types of social situations most strongly associated to depression and suicide here, maintaining the emphasis on conflict -->
+
 Both depression and suicide attempts are more common outcomes of these sorts of conflict than is often appreciated by the biomedical approach (Syme and Hagen 2021).
@@
 ## Anthropology of depression and suicide
-Anthropology, in contrast, has long viewed depression and suicide attempts as largely stemming from social problems. Continue from below Durkheim
-
-Durkheim's pioneering study of suicide [@durkheim1897] helped launch sociology as a quantitative discipline.
+
+Anthropology, in contrast, has long viewed depressive states as largely the result of social problems.
+Early in the field’s history, anthropologists tackled the problem of suicide as manifested in the small, traditional societies in which they conducted their fieldwork.
+Suicide, they found, was commonly a form of protest, revenge, and/or appeal (e.g., Malinowski, 1932; Niehaus, 2012).
+Some ethnographers, such as Hezel (1987), conceptualized suicide as a form of anger, whereas others, such as Giddens (1964), conceptualized suicide as a form of social pressure.
+Counts (1980) emphasized the powerlessness of suicide victims.
+Common to almost all theoretical and empirical investigations of suicide is a focus on completed suicides, i.e., suicide deaths.
+
+Raymond Firth, in contrast, viewed suicidality as a gamble to improve one's circumstances in the here and now.
+Based on observations that suicide attempts often followed loss or conflict and varied substantially in their likelihood of death, he argued that a sizable subset of the suicide attempts among the Tikopia were not meant to end in death but instead were a means to elicit attention, status, or immediate reintegration into the community following negative events (Firth 1936; 1961).
+More recently, Syme, Garfield, & Hagen (2016) also emphasized that the vast majority of suicidal behavior does not result in death, arguing the proper focus should be on suicide ideation and attempts, with death as an unintended consequence.
+See Figure 1.
+
+<!-- move figure one here -->
+
+Suicidality is closely linked to depression.
+Suicidal ideation is one of nine diagnostic criteria for a major depressive episode [MDE, @dsm5], it is associated with depression across cultures [@haroz2017], and depression is a major risk factor for suicidal behavior [@hawton2013].
+Compared to suicide, however, there are fewer anthropological investigations of depression [@kleinman1985] despite frequent reports of depression or depression-like behavior in a wide range of societies [@haroz2017; @liu2020] and the potential for cross-cultural research to help understand depressive states [@haroz2017].
+
+## Depression and suicide attempts as both signals and bargaining tools
+
+Evolutionary theories of depression tend to either ignore suicidality, or take it as evidence that depression is dysfunctional.
+Wakefield, for instance, who has devoted much of his career to arguing that most cases of depression are simply severe but normal sadness and grief, nevertheless takes suicidality to indicate pathology for some cases of depression [e.g., @wakefield2017].
+@nettle2004 argues that the costs of depression, including suicidality, outweigh any benefits, and therefore adaptationist models of depression are implausible.
+@gilbert2006 sees suicidality as an example of a dysregulated escape defense [for reviews of evolutionary theories of depression, see @Hagen2011].
+
+Another possible explanation for the connection between depression, suicide, and social adversity is that some instances of depression and suicide attempts serve as means to elicit increased support from others by honestly signaling need to those invested in the well-being of the signaler, [@andrews2006; @Hagen2002; @Hagen2003; @HagenEtAl2008; @nock2008; @Rosenthal1993; @Stengel1956; @SymeEtAl2016], something which may be particularly useful in times when an individual cannot solve substantial fitness-relevant challenges on their own [@Hagen2003; @SymeEtAl2016].
+
+Due to the ease with which signals can be faked [@Zahavi1975; @mokkonen2016] and the costs of accepting a deceptive signal as reliable [@dawkins1978; @johnstone1993; @Hasson1994], demonstrating that one's need is genuine has likely been a recurrent adaptive problem since humans evolved the capacity to provide instrumental support to one another.
+One potential solution to this is to produce signals that are unprofitable to fake [@Zahavi1975].
+This is possible whenever the benefits of signaling outweigh the costs for those who have the relevant underlying quality but the costs outweigh the benefits for those who lack the quality or possess it to a lesser degree [@zahavi1977; @grafen1990].
+In particular, if the benefits of sending the signal are the same for signalers regardless of condition, but the signal cost outweighs this benefit for signalers without the underlying quality (a "costly signal"), then individuals with the underlying quality can evolve to send the signal and receivers can evolve to respond in mutually beneficial ways to the signal.
+
+Depression and suicidal behavior fit this criterion as both are relatively costly for those not facing adversity than those who are.
+In the case of depression, the large-scale reduction in one's normal routine of fitness enhancing behavior is relatively less costly for those whose situations result in a limited ability to obtain fitness-relevant benefits, with depression likely adding no additional costs in instances of extreme deprivation [@Hagen2003].
+When it comes to suicide, the bulk of the costs associated with suicide attempts are only felt in times that result in death or severe bodily harm.
+For this reason, the way others view and respond to suicide attempts is likely to be strongly influenced by the probability that the attempt would result in death or severe injury [@Rosenthal1993].
+Despite this difference, the previously mentioned logic still applies with increased risk of death being relatively more costly for those able to advance their fitness prospects in their day-to-day lives.
+
+The costs of depression and suicidal behavior may be particularly important in times of conflict or when the level of support needed to address one's situation is substantial, both of which should be expected to increase the payoff of manipulating others through fake signals.
+When either condition applies, less costly signals like verbal requests, facial sadness, and crying are likely to be less reliable as their low costs can easily be made up for with increased social support, thereby favoring the use of costlier signals so long as the costs of signaling are outweighed by the benefits [@SymeHagen2021].
+
+<!-- Durkheim's pioneering study of suicide [@durkheim1897] helped launch sociology as a quantitative discipline.
 Sociological investigations of suicide flourished through much of the 20th century, but were supplanted by medical and public health approaches as the biomedical model of mental health took hold in the late 1970's and early 1980's [@wray2011; @syme2020].
@@
 This theoretical approach has made little progress: rates of suicide, which vary widely by country, have remained relatively flat in countries for which there are long-term data, such as the US, UK, Japan, and Sweden [@owidsuicide].
-
-## Conflict plays a central role in suicidality and depression
-
-Early on, anthropologists also tackled the problem of suicide as manifested in the small traditional societies in which they conducted their fieldwork.
+-->
+
+<!-- ## Conflict plays a central role in suicidality and depression -->
+
+<!-- Early on, anthropologists also tackled the problem of suicide as manifested in the small traditional societies in which they conducted their fieldwork.
 Suicide, they found, was commonly a form of protest, revenge, and/or appeal [e.g., @Malinowski:1932; @niehaus2012].
@@
 Most suicides deaths, especially in young, physically healthy individuals, are therefore the inevitable consequence that some individuals lose this gamble.
+-->
 
@@
 
-Within anthropology, Raymond Firth was likely the first to conceptualize suicidality as a gamble to improve one's circumstances in the here and now.
+<!-- Within anthropology, Raymond Firth was likely the first to conceptualize suicidality as a gamble to improve one's circumstances in the here and now.
 Based on observations that suicide attempts often followed social conflict or loss, and varied substantially in their likelihood of death, he argued that a sizable subset of the suicide attempts among the Tikopia were not meant to end in death but instead were a means to elicit attention, status, or immediate reintegration into the community following negative events [@firth1936; @Firth:1961].
-Human communites are highly interdependent [\@]
-
-Suicidality is closely linked to depression.
+Human communites are highly interdependent [\@] -->
+
+<!-- Suicidality is closely linked to depression.
 Suicidal ideation is one of nine diagnostic criteria for a major depressive episode [MDE, @dsm5], it is associated with depression across cultures [@haroz2017], and depression is a major risk factor for suicidal behavior [@hawton2013].
 Compared to suicide, however, there are fewer anthropological investigations of depression [@kleinman1985] despite frequent reports of depression or depression-like behavior in a wide range of societies [@haroz2017; @liu2020] and the potential for cross-cultural research to help understand depressive states [@haroz2017].
-
-Evolutionary theories of depression tend to either ignore suicidality, or take it as evidence that depression is dysfunctional.
+-->
+
+<!-- Evolutionary theories of depression tend to either ignore suicidality, or take it as evidence that depression is dysfunctional.
 Wakefield, for instance, who has devoted much of his career to arguing that most cases of depression are simply severe but normal sadness and grief, nevertheless takes suicidality to indicate pathology for some cases of depression [e.g., @wakefield2017].
@@
 @gilbert2006 sees suicidality as an example of a dysregulated escape defense [for reviews of evolutionary theories of depression, see @Hagen2011].
+-->
 
@@
 
-## Connection to Adversity
+<!-- ## Connection to Adversity -->
 
@@
 
-<!-- <!-- look for other longitudinal studies -->
-
 --\>
@@
 
-Likely the most reliable finding regarding depression and suicidality is that most cases are closely tied to major negative life events [@Hammen2005; @Mazure1998; @devries2011; @ellsberg2008], with such events likely causing depressive states based on twin studies and examinations involving negative events outside of one's control[@Hammen2005; @KendlerEtAl1999].
+<!-- Likely the most reliable finding regarding depression and suicidality is that most cases are closely tied to major negative life events [@Hammen2005; @Mazure1998; @devries2011; @ellsberg2008], with such events likely causing depressive states based on twin studies and examinations involving negative events outside of one's control[@Hammen2005; @KendlerEtAl1999].
 Of the types of negative life events associated with depression, those which involve conflict tend to be more strongly associated with depression [@Hammen2005; @Mazure1998].
@@
 In line with this reasoning, conflict, as a whole, was found to be associated with depression among the Tsimane, particularly when it involved non-kin [@StieglitzEtAl2015a].
-
-Due to depression's relationship to sucide [@who2001; @hawton2013], it should not be surprising that suicidality also often coincides with social adversity and conflict.
+-->
+
+<!-- Due to depression's relationship to sucide [@who2001; @hawton2013], it should not be surprising that suicidality also often coincides with social adversity and conflict.
 Grief over the loss of a loved one [@firth1936: @Firth:1961; @devries2011], bullying [@alavi2017; @butler2019; @ford2017; @wang2020], and instances of social transgression [@Firth:1961; @Malinowski:1932; @SymeHagen2018; @lester1997] have all been reported to lead to suicidal behavior in both industrialized and traditional societies.
@@
 As with depression, assault is an particularly powerful risk factor for suicidal behavior based on multiple large-scale multi-country studies [@devries2011; @ellsberg2008] and more localized examinations [@reigstad2017].
-
-## Depression and suicide attempts as both signals and bargaining tools
-
-One possible reason for the connection between depression, suicide, and social adversity is that some instances of depression and suicide attempts serve as means to elicit increased support from others [@andrews2006; @Hagen2002; @Hagen2003; @HagenEtAl2008; @nock2008; @Rosenthal1993; @Stengel1956; @SymeEtAl2016], particularly in times when an individual cannot solve substantial fitness-relevant challenges on their own [@Hagen2003; @SymeEtAl2016].
+-->
+
+<!-- ## Depression and suicide attempts as both signals and bargaining tools -->
+
+<!-- One possible reason for the connection between depression, suicide, and social adversity is that some instances of depression and suicide attempts serve as means to elicit increased support from others [@andrews2006; @Hagen2002; @Hagen2003; @HagenEtAl2008; @nock2008; @Rosenthal1993; @Stengel1956; @SymeEtAl2016], particularly in times when an individual cannot solve substantial fitness-relevant challenges on their own [@Hagen2003; @SymeEtAl2016].
 According to the bargaining models of depression and suicide, the small groups humans lived in for much of our evolutionary history created many situations in which certain forms of cooperation were unlikely to be easily replaced by others while also allowing for harmful or unfair social relationships to develop [@Hagen2003; @SymeEtAl2016].
 In these instances, one's monopoly on one or more types of cooperation could be leveraged to change how one is treated if others valued an individual's cooperation sufficiently and believed them to be in genuine need.
-
-Due to the ease with which signals can be faked [@Zahavi1975; @mokkonen2016] and the costs of accepting a deceptive signal as reliable [@dawkins1978; @johnstone1993; @Hasson1994], demonstrating that one's need is genuine has likely been a recurrent adaptive problem since humans evolved the capacity to provide instrumental support to one another.
+-->
+
+<!-- Due to the ease with which signals can be faked [@Zahavi1975; @mokkonen2016] and the costs of accepting a deceptive signal as reliable [@dawkins1978; @johnstone1993; @Hasson1994], demonstrating that one's need is genuine has likely been a recurrent adaptive problem since humans evolved the capacity to provide instrumental support to one another.
 One potential solution to this is to produce signals that are unprofitable to fake [@Zahavi1975].
@@
 In particular, if the benefits of sending the signal are the same for signalers regardless of condition, but the signal cost outweighs this benefit for signalers without the underlying quality (a "costly signal"), then individuals with the underlying quality can evolve to send the signal and receivers can evolve to respond in mutually beneficial ways to the signal.
-
-Depression and suicidal behavior fit this criterion as both are relatively costly for those not facing adversity than those who are.
+-->
+
+<!-- Depression and suicidal behavior fit this criterion as both are relatively costly for those not facing adversity than those who are.
 In the case of depression, the large-scale reduction in one's normal routine of fitness enhancing behavior is relatively less costly for those whose situations result in a limited ability to obtain fitness-relevant benefits, with depression likely adding no additional costs in instances of extreme deprivation [@Hagen2003].
@@
 Despite this difference, the previously mentioned logic still applies with increased risk of death being relatively more costly for those able to advance their fitness prospects in their day-to-day lives.
-
-The costs of depression and suicidal behavior may be particularly important in times of conflict or when the level of support needed to address one's situation is substantial, both of which should be expected to increase the payoff of manipulating others through fake signals.
+-->
+
+<!-- The costs of depression and suicidal behavior may be particularly important in times of conflict or when the level of support needed to address one's situation is substantial, both of which should be expected to increase the payoff of manipulating others through fake signals.
 When either condition applies, less costly signals like verbal requests, facial sadness, and crying are likely to be less reliable as their low costs can easily be made up for with increased social support, thereby favoring the use of costlier signals so long as the costs of signaling are outweighed by the benefits [@SymeHagen2021].
+-->
 

### 2021-04-26 Paper.rmd
Working on intro. A few minor edits elsewhere

--- 2021-04-22 Paper.rmd
@@
 
-### alternate start
-
-Conflicts of interest are ubiquitous among living things, even among closely related individuals.
-The result of this is often situations in which one individual benefits greatly from another while providing little benefits or substantial costs in return.
-In species which rely heavily on cooperation, like our own, this often manifests in substantial outward conflict about levels of investment the harm an individual is inflicting on another.
+# Introduction
+
+Conflicts of interest are ubiquitous, even among closely related individuals.
+In species that rely heavily on cooperation, like our own, conflicts can arise over the levels of investment in a cooperative endeavor and the division of the resulting benefits.
+In many such cases, individuals who were dissatisfied with the terms of cooperation could seek other partners [@hammerstein2016].
+In many other cases, however, it would be difficult or impossible to switch partners.
+Spouses who were dissatisfied with their partner's investment in their new infant, for example, would not easily find a different partner to invest in that infant.
+An adolescent who was dissatisfied with her parent's investment in her would not easily find other parents who were willing to invest more, nor could parents easily produce another adolescent.
+In many cooperative endeavors central to human biological fitness, each party has monopoly power over the benefits they bring to the endeavor -- no one is easily replaced [@Hagen2003].
+
+@Hagen2003 proposed that physical aggression and depression were complementary strategies to resolve conflicts in interdependent relationships.
+@SellEtAl2009 found that physically formidable individuals were more prone to anger, prevailed more in conflicts of interest, and considered themselves entitled to better treatment.
+Physically weaker individuals, though, are not without options to resolve conflicts in their favor.
+An individual with monopoly power over the benefits she contributes to a critical cooperative endeavor can withhold those benefits, or put them at risk, until her partners change their behaviors in ways that benefit her.
+
+Withholding or risking benefits can be conceptualized as signaling private information. In a classic game theory model of bargaining, @Rubinstein:1982 showed that if (1) the cooperative  decreases
 
@@
 ## Anthropology of depression and suicide
+
 Anthropology, in contrast, has long viewed depression and suicide attempts as largely stemming from social problems. Continue from below Durkheim
-
-# Introduction
 
@@
 The study was started by N=`r nrow(signaling2020)` participants who clicked the link to Qualtrics (`r nationT0['American']` US and `r nationT0['Indian']` India).
-After removing participants who did not finish the survey, failed attention checks, or moved through the study at an unrealistic pace (N=`r removed`, `r removed_pct`%), our final sample was N = `r nrow(d)` (`r nationT1['American']` US and `r nationT1['Indian']` India), with `r sexT1['Male']` males and `r sexT1['Female']` females, `r relstatus['Married']` of whom were married or in a long-term relationship, `r relstatus['Divorced']` who were divorced, `r relstatus['Single']` who were single, and `r relstatus['Widowed']`.
+After removing participants who did not finish the survey, failed attention checks, or moved through the study at an unrealistic pace (N=`r removed`, `r removed_pct`%), our final sample was N = `r nrow(d)` (`r nationT1['American']` US and `r nationT1['Indian']` India), with `r sexT1['Male']` males and `r sexT1['Female']` females, `r relstats['Married']` of whom were married or in a long-term relationship, `r relstats['Divorced']` who were divorced, `r relstats['Single']` who were single, and `r relstats['Widowed']` who were widowed.
 The median number of participants per condition was `r median(n_cond)` (min=`r min(n_cond)`, max=`r max(n_cond)`).
@@
 Power was about 80% for a sample size of about `r pwr80_90[[2,2]]`, and was about 90% for a sample size of about `r pwr80_90[[2,3]]`.
-We then repeated this entire procedure to compare *Depression* to a *Control* condition in the pilot study that was meant to not include any signaling (but which we realized, post hoc, did include a verbal request, and therefore was not used in the current study).
+We then repeated this entire procedure to compare *Depression* to a (flawed) *Control* condition in the pilot study that was meant to not include any signaling (but which we realized, post hoc, did include a verbal request yet differed in substantive ways from the treatment conditions, and therefore was not suitable as a control).
 Power was about 80% for a sample size of about `r pwr80_90[[1,2]]`, and was about 90% for a sample size of about `r pwr80_90[[1,3]]`.
@@
 Power was about 80% for a sample size of 125, and about 90% for a sample size of 175.
-See Figure @ref(fig:power2).
 -->

### 2021-04-26 _packages.R

@@ -1,31 +1,0 @@
-# Generated by targets::tar_renv(): do not edit by hand
-library(broom)
-library(bs4Dash)
-library(car)
-library(clustermq)
-library(dplyr)
-library(effects)
-library(forcats)
-library(frm)
-library(furrr)
-library(future)
-library(ggforce)
-library(gglm)
-library(ggplot2)
-library(glmmboot)
-library(gt)
-library(hagenutils)
-library(ks)
-library(margins)
-library(mediation)
-library(patchwork)
-library(pingr)
-library(purrr)
-library(rstudioapi)
-library(shiny)
-library(shinycssloaders)
-library(shinyWidgets)
-library(stringr)
-library(tidyr)
-library(visNetwork)
-library(visreg)

### 2021-04-26 _targets.R

@@ -440,6 +440,13 @@ list(
     feedback(d)
   ),
 
+
+# Package references ------------------------------------------------------
+
+  tar_render(
+    package_references, 'Packages.rmd'
+  ),
+
 # Paper -------------------------------------------------------------------
 
   tar_render(

### 2021-04-26 Paper.rmd

--- 2021-04-23 Paper.rmd
@@
 Conflicts of interest are ubiquitous, even among closely related individuals.
-In species that rely heavily on cooperation, like our own, conflicts can arise over the level of investment in a cooperative endeavor and the division of the resulting benefits.
-In many such cases, individuals who are dissatisfied with their social partners would seek other partners.
+In species that rely heavily on cooperation, like our own, conflicts can arise over the levels of investment in a cooperative endeavor and the division of the resulting benefits.
+In many such cases, individuals who were dissatisfied with the terms of cooperation could seek other partners [@hammerstein2016].
 In many other cases, however, it would be difficult or impossible to switch partners.
-A wife who is dissatisfied with her husband's investment in their new infant, for example, would not easily find a different husband to invest in that infant, nor could the husband easily find a different wife to invest in that infant.
-An adolescent who is dissatisfied with her parent's investment in her would not easily find other parents who are willing to invest more, nor could parents easily produce another adolescent.
-In many cooperative endeavors central to human biological fitness, each party has monopoly power over the benefits they bring to the endeavor -- no one is easily replaced.
-
-Conflict resolution therefore requires that the levels of investment in and division of benefits from the endeavor
+Spouses who were dissatisfied with their partner's investment in their new infant, for example, would not easily find a different partner to invest in that infant.
+An adolescent who was dissatisfied with her parent's investment in her would not easily find other parents who were willing to invest more, nor could parents easily produce another adolescent.
+In many cooperative endeavors central to human biological fitness, each party has monopoly power over the benefits they bring to the endeavor -- no one is easily replaced [@Hagen2003].
+
+@Hagen2003 proposed that physical aggression and depression were complementary strategies to resolve conflicts in interdependent relationships.
+@SellEtAl2009 found that physically formidable individuals were more prone to anger, prevailed more in conflicts of interest, and considered themselves entitled to better treatment.
+Physically weaker individuals, though, are not without options to resolve conflicts in their favor.
+An individual with monopoly power over the benefits she contributes to a critical cooperative endeavor can withhold those benefits, or put them at risk, until her partners change their behaviors in ways that benefit her.
+
+Withholding or risking benefits can be conceptualized as signaling private information. In a classic game theory model of bargaining, @Rubinstein:1982 showed that if (1) the cooperative  decreases
 
@@
 The study was started by N=`r nrow(signaling2020)` participants who clicked the link to Qualtrics (`r nationT0['American']` US and `r nationT0['Indian']` India).
-After removing participants who did not finish the survey, failed attention checks, or moved through the study at an unrealistic pace (N=`r removed`, `r removed_pct`%), our final sample was N = `r nrow(d)` (`r nationT1['American']` US and `r nationT1['Indian']` India), with `r sexT1['Male']` males and `r sexT1['Female']` females, `r relstats['Married']` of whom were married or in a long-term relationship, `r relstats['Divorced']` who were divorced, `r relstats['Single']` who were single, and `r relstats['Widowed']`.
+After removing participants who did not finish the survey, failed attention checks, or moved through the study at an unrealistic pace (N=`r removed`, `r removed_pct`%), our final sample was N = `r nrow(d)` (`r nationT1['American']` US and `r nationT1['Indian']` India), with `r sexT1['Male']` males and `r sexT1['Female']` females, `r relstats['Married']` of whom were married or in a long-term relationship, `r relstats['Divorced']` who were divorced, `r relstats['Single']` who were single, and `r relstats['Widowed']` who were widowed.
 The median number of participants per condition was `r median(n_cond)` (min=`r min(n_cond)`, max=`r max(n_cond)`).

### 2021-04-26 Paper.rmd
Working on intro

@@
 In many other cases, however, it would be difficult or impossible to switch partners.
-Spouses who were dissatisfied with their partner's investment in their new infant, for example, would not easily find a different partner to invest in that infant.
-An adolescent who was dissatisfied with her parent's investment in her would not easily find other parents who were willing to invest more, nor could parents easily produce another adolescent.
+Spouses who were dissatisfied with their partner's investment in their new infant, for example, would not easily find a different partner to invest in that infant [@Hagen:1999].
+Similarly, an adolescent who was dissatisfied with her parent's investment in her would not easily find other parents who were willing to invest more, nor could parents easily produce another adolescent.
 In many cooperative endeavors central to human biological fitness, each party has monopoly power over the benefits they bring to the endeavor -- no one is easily replaced [@Hagen2003].
@@
 
-Withholding or risking benefits can be conceptualized as signaling private information. In a classic game theory model of bargaining, @Rubinstein:1982 showed that if (1) the cooperative  decreases
+Withholding or risking one's contributions to a cooperative endeavor can be conceptualized as credibly signaling private information about one's need.
+Cooperation generates benefits over time.
+Thus, withholding or risking contributions incurs a *cost of delay*.
+In a classic non-cooperative game theory model of bargaining over the division of benefits, @Rubenstein:1982 showed that two parties can come to an immediate agreement over division of benefits despite conflicts of interest if the parties' valuations of cooperation are not private information.
+If valuations are private information, however, then immediate agreement might not be possible because each party has an incentive to exaggerate their need.
+A willing to delay, i.e., incur a cost, is a credible signal that one has a low valuation of the endeavor, and is therefore genuinely in need.
+Once valuations are known, the parties can reach an agreement on the division of benefits [@KennanWilson1993; @feinberg2005].
 

### 2021-04-27 Paper.rmd
Continuing to work on intro

@@
 
+<!-- ## Connection to Adversity -->
+
+There is strong evidence that most cases of depression are caused by major negative life events [@Hammen2005; @Mazure1998; @devries2011; @ellsberg2008].
+Compared to non-depressed individuals, those with depression report about twice as many instances of negative events than non-depressed individuals [@Mazure1998] and more negative events than those with schizophrenia and bipolar depression across multiple studies [@Paykel1994].
+In longitudinal studies, depression onsets soon after a negative event [@KendlerEtAl1999] or coincides with periods where adversity is likely to increase prior to it [e.g., depression starting before a divorce rather than after; @rosenstrom2017].
+Additional support for the causal role of negative life events comes from the fact that the relationship between negative events and depression holds true when looking at events outside of one's control, showing that the connection is unlikely to be driven solely by individuals who are already depressed creating situations where negative events are likely to be common [@Hammen2005; @KendlerEtAl1999].
+Additionally, twin studies have shown that one's history of negative events is still a strong predictor of major depression when controlling for genetic similarity, and that part of the heritability of depression stems from the heritability of negative events, like divorce and family conflict [@KendlerBaker2007; @KendlerEtAl1999].
+
+There is equally strong evidence that depression is closely associated with anger and conflict [@cassiello2016].
+Of the types of negative life events associated with depression, those which involve conflict tend to be more strongly associated with depression [@Hammen2005; @Mazure1998].
+Marital problems, bullying, and abusive relationships are all common risk factors for depression [@KendlerEtAl1995; @KendlerEtAl1999; @klomek2007; @klomek2019], with assault (both sexual and non-sexual), in particular, greatly increasing one's risk of depression [@KendlerEtAl1995; @KendlerEtAl1999].
+This holds true even in a small-scale, non-Western society: among the Tsimane, Amazonian horticulturalists, depression is also associated with conflict, particularly conflict involving non-kin [@StieglitzEtAl2015a].
+See @SymeHagen2021 for a review of the association of depression with anger and conflict.
+
+Other notable risk factors like loss of a loved one or severe or prolonged illness, might seem less related to conflict.
+In these situations, however, individuals will often need increased investment from social partners, who might not be able, or want, to provide more investment than they already are.
+The ability for others to provide meaningful support to limit the harm in times of need [@SugiyamaSugiyama2003] combined with the ubiquity of conflicts of interests mean that many types of problems will eventually involve social conflict even if they did not start that way [@Hagen2003].
+There is indeed increasing evidence that loss of a loved one is often followed by increased family conflict [see @SymeHagen2021 for a brief review].
+
+# Bargaining: Credibly signaling need under conflict
+
+Individuals who have suffered a negative life event will often need help to mitigate the fitness cost.
+To obtain this help, they must signal need, e.g., by verbally requests, sad facial expressions, and crying.
+But if they have conflicts of interest with social partners who could provide that help, and if their need is private information, their signals might not be believed if the signals, like crying, could easily be faked [@Zahavi1975; @mokkonen2016] and if the cost of believing a deceptive signal was high [@dawkins1978; @johnstone1993; @Hasson1994].
+
+demonstrating that one's need is genuine has likely been a recurrent adaptive problem since humans evolved the capacity to provide instrumental support to one another.
+
 Conflicts of interest are ubiquitous, even among closely related individuals.
@@
 Cooperation generates benefits over time.
-Thus, withholding or risking contributions incurs a *cost of delay*.
-In a classic non-cooperative game theory model of bargaining over the division of benefits, @Rubenstein:1982 showed that two parties can come to an immediate agreement over division of benefits despite conflicts of interest if the parties' valuations of cooperation are not private information.
-If valuations are private information, however, then immediate agreement might not be possible because each party has an incentive to exaggerate their need.
-A willing to delay, i.e., incur a cost, is a credible signal that one has a low valuation of the endeavor, and is therefore genuinely in need.
+Thus, withholding or risking contributions incurs a *cost of delay* -- the more one values the endeavor, the greater the cost of delay.
+In a classic non-cooperative game theory model of bargaining over the division of benefits, @Rubenstein:1982 showed that two parties can come to an immediate agreement over division of benefits despite conflicts of interest if the parties' valuations of cooperation are not private information: in this case, each party knows exactly what division of benefits the other will accept, and can therefore make that offer immediately, avoiding the cost of delay.
+If valuations are private information, however, then immediate agreement might not be possible because each party has an incentive to deceptively report a low valuation in the hopes of getting more.
+A willingness to delay is a credible signal that one has a low valuation of the endeavor, and is therefore genuinely in need, because for those with a low valuation the benefit of a better offer outweighs the low cost of delay whereas for those for those with a high valuation the benefit of a better offer does not outweigh the higher cost of delay.
 Once valuations are known, the parties can reach an agreement on the division of benefits [@KennanWilson1993; @feinberg2005].
+
+@Rosenthal1993 proposed a credible signaling model of what he termed "gambling-type" suicide attempts in which a probability of death less than 1 serves as the signal cost that allows signal receivers to accurately discriminate between those who are genuinely in need and those who are not.
 
@@
 
-<!-- ## Connection to Adversity -->
-
-<!-- Likely the most reliable finding regarding depression and suicidality is that most cases are closely tied to major negative life events [@Hammen2005; @Mazure1998; @devries2011; @ellsberg2008].
-Compared to non-depressed individuals, those with depression tend to report at least twice as many instances of negative events than non-depressed individuals [@Mazure1998] and more negative events than those with schizophrenia and bipolar depression across multiple studies [@Paykel1994].
-In longitudinal studies, the onset of depression has been reported to quickly follow the negative event [@KendlerEtAl1999] or coincide with periods where conflict is likely to increase prior to it (e.g., depression starting before a divorce rather than after; @rosenstrom2017).
--->
-
---\>
-
-<!-- This strong connection between negative life events and depression along with the adversity and distress that likely accompanies these events has led to the suggestion that this relationship is causal [@KendlerEtAl1999].
-Support for this comes from the fact that the relationship between negative events and depression holds true when looking solely at events outside of one's control, showing that the connection is unlikely to be driven solely by individuals who are already depressed creating situations where negative events are likely to be common [@Hammen2005; @KendlerEtAl1999].
-In addition to this, twin studies have shown that one's history of negative events is still a strong predictor of major depression when controlling for genetic similarity and that part of the heritability of depression stems from the heritability of negative events, like divorce and family conflict [@KendlerBaker2007; @KendlerEtAl1999].
--->
-
-<!-- Likely the most reliable finding regarding depression and suicidality is that most cases are closely tied to major negative life events [@Hammen2005; @Mazure1998; @devries2011; @ellsberg2008], with such events likely causing depressive states based on twin studies and examinations involving negative events outside of one's control[@Hammen2005; @KendlerEtAl1999].
-Of the types of negative life events associated with depression, those which involve conflict tend to be more strongly associated with depression [@Hammen2005; @Mazure1998].
-Marital problems, bullying, and the existence of abusive relationships are all commonly cited risk factors for depression [@KendlerEtAl1995; @KendlerEtAl1999; @klomek2007; @klomek2019], with assault (both sexual and non-sexual), in particular, greatly increasing one's risk of depression [@KendlerEtAl1995; @KendlerEtAl1999].
-Other notable risk factors like loss of a loved one, financial problems, job loss, or severe or prolonged illness, might seem less related to conflict.
-However, the ability for others to provide meaningful support to limit the harm caused in times of need [@SugiyamaSugiyama2003] combined with the ubiquity of conflicts of interests mean that many types of problems will eventually involve social conflict even if they did not start that way [@Hagen2003].
-In line with this reasoning, conflict, as a whole, was found to be associated with depression among the Tsimane, particularly when it involved non-kin [@StieglitzEtAl2015a].
--->
-
-<!-- Due to depression's relationship to sucide [@who2001; @hawton2013], it should not be surprising that suicidality also often coincides with social adversity and conflict.
+<!-- Due to depression's relationship to suicide [@who2001; @hawton2013], it should not be surprising that suicidality also often coincides with social adversity and conflict.
 Grief over the loss of a loved one [@firth1936: @Firth:1961; @devries2011], bullying [@alavi2017; @butler2019; @ford2017; @wang2020], and instances of social transgression [@Firth:1961; @Malinowski:1932; @SymeHagen2018; @lester1997] have all been reported to lead to suicidal behavior in both industrialized and traditional societies.

### 2021-04-28 Paper.rmd
Change heading level
Introduction edits (attempt at bridging depression intro and braoder conflict/ bargaining sections)

@@
 Additional support for the causal role of negative life events comes from the fact that the relationship between negative events and depression holds true when looking at events outside of one's control, showing that the connection is unlikely to be driven solely by individuals who are already depressed creating situations where negative events are likely to be common [@Hammen2005; @KendlerEtAl1999].
-Additionally, twin studies have shown that one's history of negative events is still a strong predictor of major depression when controlling for genetic similarity, and that part of the heritability of depression stems from the heritability of negative events, like divorce and family conflict [@KendlerBaker2007; @KendlerEtAl1999].
+Additionally, twin studies have shown that one's history of negative events is still a strong predictor of major depression when controlling for genetic similarity, and that part of the heritability of depression stems from the heritability of negative events like divorce and family conflict [@KendlerBaker2007; @KendlerEtAl1999].
 
@@
 
-# Bargaining: Credibly signaling need under conflict
-
-Individuals who have suffered a negative life event will often need help to mitigate the fitness cost.
-To obtain this help, they must signal need, e.g., by verbally requests, sad facial expressions, and crying.
+## Bargaining: Credibly signaling need under conflict
+
+<!-- Individuals who have suffered a negative life event will often need help to mitigate the fitness cost.
+To obtain this help, they must signal need, e.g., by verbal requests, sad facial expressions, and crying.
 But if they have conflicts of interest with social partners who could provide that help, and if their need is private information, their signals might not be believed if the signals, like crying, could easily be faked [@Zahavi1975; @mokkonen2016] and if the cost of believing a deceptive signal was high [@dawkins1978; @johnstone1993; @Hasson1994].
-
-demonstrating that one's need is genuine has likely been a recurrent adaptive problem since humans evolved the capacity to provide instrumental support to one another.
-
-Conflicts of interest are ubiquitous, even among closely related individuals.
-In species that rely heavily on cooperation, like our own, conflicts can arise over the levels of investment in a cooperative endeavor and the division of the resulting benefits.
+-->
+
+As a species that relies heavily on cooperation, humans who have suffered a negative life event could mitigate the fitness cost with help from others [@SugiyamaSugiyama2003].
+However, the presence of conflicts of interests means that there will be disagreement over the levels of investment in a cooperative endeavor and the division of the resulting benefits.
 In many such cases, individuals who were dissatisfied with the terms of cooperation could seek other partners [@hammerstein2016].
@@
 Similarly, an adolescent who was dissatisfied with her parent's investment in her would not easily find other parents who were willing to invest more, nor could parents easily produce another adolescent.
-In many cooperative endeavors central to human biological fitness, each party has monopoly power over the benefits they bring to the endeavor -- no one is easily replaced [@Hagen2003].
+In ###these examples, and### many cooperative endeavors central to human biological fitness, each party has monopoly power over the benefits they bring to the endeavor -- no one is easily replaced [@Hagen2003].
 
@@
 An individual with monopoly power over the benefits she contributes to a critical cooperative endeavor can withhold those benefits, or put them at risk, until her partners change their behaviors in ways that benefit her.
+### do we need a line about how depression results in delayed benefits here?
+###
 
@@
 
-<!-- Introduce the types of social situations most strongly associated to depression and suicide here, maintaining the emphasis on conflict -->
-
-Both depression and suicide attempts are more common outcomes of these sorts of conflict than is often appreciated by the biomedical approach (Syme and Hagen 2021).
+Both the cost of delay of depression and the threat of death or serious injury that come from suicidal behavior allow for costly signaling strategies as they are relatively costly for those not facing adversity than those who are.
+In the case of depression, the large-scale reduction in one's normal routine of fitness enhancing behavior is relatively less costly for those whose situations result in a limited ability to obtain fitness-relevant benefits, with depression likely adding no additional costs in instances of extreme deprivation [@Hagen2003].
+When it comes to suicide, the bulk of the costs associated with suicide attempts are only felt in times that result in death or severe bodily harm.
+For this reason, the way others view and respond to suicide attempts is likely to be strongly influenced by the probability that the attempt would result in death or severe injury [@Rosenthal1993].
+Despite this difference, the previously mentioned logic still applies with increased risk of death being relatively more costly for those able to advance their fitness prospects in their day-to-day lives.
+
+As they are prohibitively costly for those in minor need, the costs of depression and suicidal behavior may be particularly important in times of conflict or when the level of support needed to address one's situation is substantial, both of which should be expected to increase the payoff of manipulating others through fake signals.
+When either condition applies, less costly signals like verbal requests, facial sadness, and crying are likely to be less reliable as their low costs can easily be made up for with increased social support, thereby favoring the use of costlier signals so long as the costs of signaling are outweighed by the benefits [@SymeHagen2021].
+
+<!-- Alternative start to line 92: Although verbal requests, sad facial expressions, and crying can be used to signal need, they are likely to be less effective in times of severe conflicts of interests or times when the level of support needed to address one's situation is substantial.
+This is because both conditions increase the payoff of manipulating others through fake signal.
+-->
+
+<!-- Both depression and suicide attempts are more common outcomes of these sorts of conflict than is often appreciated by the biomedical approach (Syme and Hagen 2021).
 With notable exceptions (Kendler; Mazure; Hammen), the biomedical model tends to frame both suicide and depression as a problem with the individual, e.g., as one involving psychiatric disturbance, drug addiction, or stress sensitivity [@wray2011 (changed wording to include depression].
 This theoretical approach has made little progress: rates of suicide, which vary widely by country, have remained relatively flat in countries for which there are long-term data, such as the US, UK, Japan, and Sweden [@owidsuicide] (tweak for depression).
+-->
 

### 2021-04-29 Paper.rmd
More work on the introduction

@@
 
-Other notable risk factors like loss of a loved one or severe or prolonged illness, might seem less related to conflict.
+<!-- Other notable risk factors, like loss of a loved one or severe or prolonged illness, might seem less related to conflict.
 In these situations, however, individuals will often need increased investment from social partners, who might not be able, or want, to provide more investment than they already are.
@@
 There is indeed increasing evidence that loss of a loved one is often followed by increased family conflict [see @SymeHagen2021 for a brief review].
+-->
+
+Other notable risk factors, like loss of a loved one or severe or prolonged illness, might seem less related to conflict.
+In these situations, however, the fitness costs that stem from reduced access to resources could be mitigated with help from others [@SugiyamaSugiyama2003] who might not be able, or want, to provide more investment than they already are.
+For this reason, many types of problems will eventually involve social conflict even if they did not start that way [@Hagen2003], something which is seen in the increasing evidence that loss of a loved one is often followed by increased family conflict [see @SymeHagen2021 for a brief review].
 
@@
 
-As a species that relies heavily on cooperation, humans who have suffered a negative life event could mitigate the fitness cost with help from others [@SugiyamaSugiyama2003].
-However, the presence of conflicts of interests means that there will be disagreement over the levels of investment in a cooperative endeavor and the division of the resulting benefits.
+<!-- Conflicts of interest are ubiquitous, even among closely related individuals.
+In species that rely heavily on cooperation, like our own, conflicts can arise over the levels of investment in a cooperative endeavor and the division of the resulting benefits.
+-->
+
+With a cooperative species like our own, the ubiquity of conflicts of interests means that there will always be disagreement over the levels of investment in a cooperative endeavor and the division of the resulting benefits.
 In many such cases, individuals who were dissatisfied with the terms of cooperation could seek other partners [@hammerstein2016].

### 2021-04-29 Paper.rmd
Minor intro change

@@
 
-As they are prohibitively costly for those in minor need, the costs of depression and suicidal behavior may be particularly important in times of conflict or when the level of support needed to address one's situation is substantial, both of which should be expected to increase the payoff of manipulating others through fake signals.
+As they are prohibitively costly for those in minor need, the costs of depression and suicidal behavior may be particularly important in times of substantial conflicts of interest or when the level of support needed to address one's situation is substantial, both of which should be expected to increase the payoff of manipulating others through fake signals.
 When either condition applies, less costly signals like verbal requests, facial sadness, and crying are likely to be less reliable as their low costs can easily be made up for with increased social support, thereby favoring the use of costlier signals so long as the costs of signaling are outweighed by the benefits [@SymeHagen2021].

### 2021-04-29 Paper.rmd
More work on intro

@@
 <!-- ## Connection to Adversity -->
+Almost all individuals will suffer adversity, such as injury or loss of material or social resources, at some point in their lives.
+Psychological pain, such as sadness and low mood, probably evolved to motivate victims of adversity to shift their attention to the causes of adversity so as to mitigate its negative fitness consequences and to learn to avoid future such adverse events [@thornhill1989; @andrews2010; @Nesse1990].
+In many cases, social partners could help, and therefore signals of psychological pain, such as sad expressions and crying, probably evolved to indicate need [e.g., @balsters2013].
 
@@
 Additionally, twin studies have shown that one's history of negative events is still a strong predictor of major depression when controlling for genetic similarity, and that part of the heritability of depression stems from the heritability of negative events like divorce and family conflict [@KendlerBaker2007; @KendlerEtAl1999].
+For these and other reasons, most cases of depression are probably not due to mental illness but are instead functional instances of psychological pain [@Hagen:1999; @Hagen2003; @horwitz_loss_2007; @andrews2010; @SymeHagen2021].
 
@@
 In these situations, however, the fitness costs that stem from reduced access to resources could be mitigated with help from others [@SugiyamaSugiyama2003] who might not be able, or want, to provide more investment than they already are.
-For this reason, many types of problems will eventually involve social conflict even if they did not start that way [@Hagen2003], something which is seen in the increasing evidence that loss of a loved one is often followed by increased family conflict [see @SymeHagen2021 for a brief review].
+Indeed, there is increasing evidence that loss of a loved one is often followed by increased family conflict [see @SymeHagen2021 for a brief review].
+Problems whose solutions require substantial investment or other changes on the part of social partners will therefore often involve social conflict even if they did not start that way [@Hagen2003].
+When there are severe conflicts of interest, individuals have incentives to deceive, so "cheap" signals of need, such as sad expressions and crying, might not be believed.
 
@@
 Similarly, an adolescent who was dissatisfied with her parent's investment in her would not easily find other parents who were willing to invest more, nor could parents easily produce another adolescent.
-In ###these examples, and### many cooperative endeavors central to human biological fitness, each party has monopoly power over the benefits they bring to the endeavor -- no one is easily replaced [@Hagen2003].
+In these examples, and many cooperative endeavors central to human biological fitness, each party has monopoly power over the benefits they bring to the endeavor -- no one is easily replaced [@Hagen2003].
 
@@
 @SellEtAl2009 found that physically formidable individuals were more prone to anger, prevailed more in conflicts of interest, and considered themselves entitled to better treatment.
-Physically weaker individuals, though, are not without options to resolve conflicts in their favor.
+Physically or socially weaker individuals, though, are not without options to resolve conflicts in their favor.
 An individual with monopoly power over the benefits she contributes to a critical cooperative endeavor can withhold those benefits, or put them at risk, until her partners change their behaviors in ways that benefit her.
-### do we need a line about how depression results in delayed benefits here?
-###
+Depression is characterized, in part by a profound loss of interest in virtually all activities [@dsm5], a symptom that is probably responsible for a sharp reduction in productivity [for review, see @SymeHagen2021].
+Depression might therefore be a bargaining strategy for relatively powerless individuals in the wake of adversity and social conflict [@Hagen2003; @SymeHagen2021; see also @Watson:2002].
 
@@
 In a classic non-cooperative game theory model of bargaining over the division of benefits, @Rubenstein:1982 showed that two parties can come to an immediate agreement over division of benefits despite conflicts of interest if the parties' valuations of cooperation are not private information: in this case, each party knows exactly what division of benefits the other will accept, and can therefore make that offer immediately, avoiding the cost of delay.
-If valuations are private information, however, then immediate agreement might not be possible because each party has an incentive to deceptively report a low valuation in the hopes of getting more.
-A willingness to delay is a credible signal that one has a low valuation of the endeavor, and is therefore genuinely in need, because for those with a low valuation the benefit of a better offer outweighs the low cost of delay whereas for those for those with a high valuation the benefit of a better offer does not outweigh the higher cost of delay.
-Once valuations are known, the parties can reach an agreement on the division of benefits [@KennanWilson1993; @feinberg2005].
-
-@Rosenthal1993 proposed a credible signaling model of what he termed "gambling-type" suicide attempts in which a probability of death less than 1 serves as the signal cost that allows signal receivers to accurately discriminate between those who are genuinely in need and those who are not.
-
-Both the cost of delay of depression and the threat of death or serious injury that come from suicidal behavior allow for costly signaling strategies as they are relatively costly for those not facing adversity than those who are.
+If valuations are private information, however, then immediate agreement might not be possible because each party has an incentive to request an amount greater than their actual valuation.
+A willingness to delay is a credible signal that one has a low valuation of the endeavor, and is therefore genuinely in need, because for those with a low valuation the benefit of waiting for a better offer outweighs the low cost of delay whereas for those for those with a high valuation the benefit of waiting for a better offer does not outweigh the higher cost of delay.
+Once valuations are known, the game reduces to the one in @Rubenstein:1982, and the parties can reach an agreement on the division of benefits [@KennanWilson1993; @feinberg2005].
+
+@Rosenthal1993 proposed a credible signaling model of what he termed "gambling-type" suicide attempts.
+The vast majority of suicidal behavior does not result in death.
+In young adult women in the US, there are hundreds of attempts for every death (see Figure \@ref(fig:cdc)).
+Nevertheless, each attempt carries a non-zero risk of death.
+This cost allows social partners to accurately discriminate between those who are genuinely in need and those who are not [@Rosenthal1993].
 In the case of depression, the large-scale reduction in one's normal routine of fitness enhancing behavior is relatively less costly for those whose situations result in a limited ability to obtain fitness-relevant benefits, with depression likely adding no additional costs in instances of extreme deprivation [@Hagen2003].
@@
 Despite this difference, the previously mentioned logic still applies with increased risk of death being relatively more costly for those able to advance their fitness prospects in their day-to-day lives.
-
-As they are prohibitively costly for those in minor need, the costs of depression and suicidal behavior may be particularly important in times of substantial conflicts of interest or when the level of support needed to address one's situation is substantial, both of which should be expected to increase the payoff of manipulating others through fake signals.
-When either condition applies, less costly signals like verbal requests, facial sadness, and crying are likely to be less reliable as their low costs can easily be made up for with increased social support, thereby favoring the use of costlier signals so long as the costs of signaling are outweighed by the benefits [@SymeHagen2021].
-
-<!-- Alternative start to line 92: Although verbal requests, sad facial expressions, and crying can be used to signal need, they are likely to be less effective in times of severe conflicts of interests or times when the level of support needed to address one's situation is substantial.
-This is because both conditions increase the payoff of manipulating others through fake signal.
--->
-
-<!-- Both depression and suicide attempts are more common outcomes of these sorts of conflict than is often appreciated by the biomedical approach (Syme and Hagen 2021).
-With notable exceptions (Kendler; Mazure; Hammen), the biomedical model tends to frame both suicide and depression as a problem with the individual, e.g., as one involving psychiatric disturbance, drug addiction, or stress sensitivity [@wray2011 (changed wording to include depression].
-This theoretical approach has made little progress: rates of suicide, which vary widely by country, have remained relatively flat in countries for which there are long-term data, such as the US, UK, Japan, and Sweden [@owidsuicide] (tweak for depression).
--->
-
-## Anthropology of depression and suicide
-
-Anthropology, in contrast, has long viewed depressive states as largely the result of social problems.
-Early in the field’s history, anthropologists tackled the problem of suicide as manifested in the small, traditional societies in which they conducted their fieldwork.
-Suicide, they found, was commonly a form of protest, revenge, and/or appeal (e.g., Malinowski, 1932; Niehaus, 2012).
-Some ethnographers, such as Hezel (1987), conceptualized suicide as a form of anger, whereas others, such as Giddens (1964), conceptualized suicide as a form of social pressure.
-Counts (1980) emphasized the powerlessness of suicide victims.
-Common to almost all theoretical and empirical investigations of suicide is a focus on completed suicides, i.e., suicide deaths.
-
-Raymond Firth, in contrast, viewed suicidality as a gamble to improve one's circumstances in the here and now.
-Based on observations that suicide attempts often followed loss or conflict and varied substantially in their likelihood of death, he argued that a sizable subset of the suicide attempts among the Tikopia were not meant to end in death but instead were a means to elicit attention, status, or immediate reintegration into the community following negative events (Firth 1936; 1961).
-More recently, Syme, Garfield, & Hagen (2016) also emphasized that the vast majority of suicidal behavior does not result in death, arguing the proper focus should be on suicide ideation and attempts, with death as an unintended consequence.
-See Figure 1.
-
-<!-- move figure one here -->
-
-Suicidality is closely linked to depression.
-Suicidal ideation is one of nine diagnostic criteria for a major depressive episode [MDE, @dsm5], it is associated with depression across cultures [@haroz2017], and depression is a major risk factor for suicidal behavior [@hawton2013].
-Compared to suicide, however, there are fewer anthropological investigations of depression [@kleinman1985] despite frequent reports of depression or depression-like behavior in a wide range of societies [@haroz2017; @liu2020] and the potential for cross-cultural research to help understand depressive states [@haroz2017].
-
-## Depression and suicide attempts as both signals and bargaining tools
-
-Evolutionary theories of depression tend to either ignore suicidality, or take it as evidence that depression is dysfunctional.
-Wakefield, for instance, who has devoted much of his career to arguing that most cases of depression are simply severe but normal sadness and grief, nevertheless takes suicidality to indicate pathology for some cases of depression [e.g., @wakefield2017].
-@nettle2004 argues that the costs of depression, including suicidality, outweigh any benefits, and therefore adaptationist models of depression are implausible.
-@gilbert2006 sees suicidality as an example of a dysregulated escape defense [for reviews of evolutionary theories of depression, see @Hagen2011].
-
-Another possible explanation for the connection between depression, suicide, and social adversity is that some instances of depression and suicide attempts serve as means to elicit increased support from others by honestly signaling need to those invested in the well-being of the signaler, [@andrews2006; @Hagen2002; @Hagen2003; @HagenEtAl2008; @nock2008; @Rosenthal1993; @Stengel1956; @SymeEtAl2016], something which may be particularly useful in times when an individual cannot solve substantial fitness-relevant challenges on their own [@Hagen2003; @SymeEtAl2016].
-
-Due to the ease with which signals can be faked [@Zahavi1975; @mokkonen2016] and the costs of accepting a deceptive signal as reliable [@dawkins1978; @johnstone1993; @Hasson1994], demonstrating that one's need is genuine has likely been a recurrent adaptive problem since humans evolved the capacity to provide instrumental support to one another.
-One potential solution to this is to produce signals that are unprofitable to fake [@Zahavi1975].
-This is possible whenever the benefits of signaling outweigh the costs for those who have the relevant underlying quality but the costs outweigh the benefits for those who lack the quality or possess it to a lesser degree [@zahavi1977; @grafen1990].
-In particular, if the benefits of sending the signal are the same for signalers regardless of condition, but the signal cost outweighs this benefit for signalers without the underlying quality (a "costly signal"), then individuals with the underlying quality can evolve to send the signal and receivers can evolve to respond in mutually beneficial ways to the signal.
-
-Depression and suicidal behavior fit this criterion as both are relatively costly for those not facing adversity than those who are.
-In the case of depression, the large-scale reduction in one's normal routine of fitness enhancing behavior is relatively less costly for those whose situations result in a limited ability to obtain fitness-relevant benefits, with depression likely adding no additional costs in instances of extreme deprivation [@Hagen2003].
-When it comes to suicide, the bulk of the costs associated with suicide attempts are only felt in times that result in death or severe bodily harm.
-For this reason, the way others view and respond to suicide attempts is likely to be strongly influenced by the probability that the attempt would result in death or severe injury [@Rosenthal1993].
-Despite this difference, the previously mentioned logic still applies with increased risk of death being relatively more costly for those able to advance their fitness prospects in their day-to-day lives.
-
-The costs of depression and suicidal behavior may be particularly important in times of conflict or when the level of support needed to address one's situation is substantial, both of which should be expected to increase the payoff of manipulating others through fake signals.
-When either condition applies, less costly signals like verbal requests, facial sadness, and crying are likely to be less reliable as their low costs can easily be made up for with increased social support, thereby favoring the use of costlier signals so long as the costs of signaling are outweighed by the benefits [@SymeHagen2021].
-
-<!-- Durkheim's pioneering study of suicide [@durkheim1897] helped launch sociology as a quantitative discipline.
-Sociological investigations of suicide flourished through much of the 20th century, but were supplanted by medical and public health approaches as the biomedical model of mental health took hold in the late 1970's and early 1980's [@wray2011; @syme2020].
-The biomedical model tends to frame suicide as a problem with the individual, e.g., as one involving psychiatric disturbance, drug addiction, or stress sensitivity [@wray2011].
-This theoretical approach has made little progress: rates of suicide, which vary widely by country, have remained relatively flat in countries for which there are long-term data, such as the US, UK, Japan, and Sweden [@owidsuicide].
--->
-
-<!-- ## Conflict plays a central role in suicidality and depression -->
-
-<!-- Early on, anthropologists also tackled the problem of suicide as manifested in the small traditional societies in which they conducted their fieldwork.
-Suicide, they found, was commonly a form of protest, revenge, and/or appeal [e.g., @Malinowski:1932; @niehaus2012].
-Some ethnographers, such as @Hezel:1987, conceptualized suicide as a form of anger, whereas others, such as @Giddens:1964, conceptualized suicide as a form of social pressure.
-@Counts:1980 emphasized the powerlessness of suicide victims.
-Common to almost all theoretical and empirical investigations of suicide is a focus on *completed* suicides, i.e., suicide deaths.
-@SymeEtAl2016, in contrast, argued that because the vast majority of suicidal behavior does not result in death, the proper focus should be on suicide ideation and suicide attempts (see Figure \@ref(fig:cdc)).
-Suicide attempts, as we explain next, are a gamble to improve one's life by taking a low but non-zero risk of death.
-Most suicides deaths, especially in young, physically healthy individuals, are therefore the inevitable consequence that some individuals lose this gamble.
--->
 
@@
 ```
+
+As they are prohibitively costly for those in minor need, the costs of depression and suicidal behavior may be particularly important in times of substantial conflicts of interest or when the level of support needed to address one's situation is substantial, both of which should be expected to increase the payoff of manipulating others through fake signals.
+When either condition applies, less costly signals like verbal requests, facial sadness, and crying are likely to be less reliable as their low costs can easily be made up for with increased social support, thereby favoring the use of costlier signals so long as the costs of signaling are outweighed by the benefits [@SymeHagen2021].
+
+<!-- Alternative start to line 92: Although verbal requests, sad facial expressions, and crying can be used to signal need, they are likely to be less effective in times of severe conflicts of interests or times when the level of support needed to address one's situation is substantial.
+This is because both conditions increase the payoff of manipulating others through fake signal.
+-->
+
+<!-- Both depression and suicide attempts are more common outcomes of these sorts of conflict than is often appreciated by the biomedical approach (Syme and Hagen 2021).
+With notable exceptions (Kendler; Mazure; Hammen), the biomedical model tends to frame both suicide and depression as a problem with the individual, e.g., as one involving psychiatric disturbance, drug addiction, or stress sensitivity [@wray2011 (changed wording to include depression].
+This theoretical approach has made little progress: rates of suicide, which vary widely by country, have remained relatively flat in countries for which there are long-term data, such as the US, UK, Japan, and Sweden [@owidsuicide] (tweak for depression).
+-->
+
+## Anthropology of depression and suicide
+
+Anthropology, in contrast, has long viewed depressive states as largely the result of social problems.
+Early in the field’s history, anthropologists tackled the problem of suicide as manifested in the small, traditional societies in which they conducted their fieldwork.
+Suicide, they found, was commonly a form of protest, revenge, and/or appeal (e.g., Malinowski, 1932; Niehaus, 2012).
+Some ethnographers, such as Hezel (1987), conceptualized suicide as a form of anger, whereas others, such as Giddens (1964), conceptualized suicide as a form of social pressure.
+Counts (1980) emphasized the powerlessness of suicide victims.
+Common to almost all theoretical and empirical investigations of suicide is a focus on completed suicides, i.e., suicide deaths.
+
+Raymond Firth, in contrast, viewed suicidality as a gamble to improve one's circumstances in the here and now.
+Based on observations that suicide attempts often followed loss or conflict and varied substantially in their likelihood of death, he argued that a sizable subset of the suicide attempts among the Tikopia were not meant to end in death but instead were a means to elicit attention, status, or immediate reintegration into the community following negative events (Firth 1936; 1961).
+More recently, Syme, Garfield, & Hagen (2016) also emphasized that the vast majority of suicidal behavior does not result in death, arguing the proper focus should be on suicide ideation and attempts, with death as an unintended consequence.
+See Figure 1.
+
+<!-- move figure one here -->
+
+Suicidality is closely linked to depression.
+Suicidal ideation is one of nine diagnostic criteria for a major depressive episode [MDE, @dsm5], it is associated with depression across cultures [@haroz2017], and depression is a major risk factor for suicidal behavior [@hawton2013].
+Compared to suicide, however, there are fewer anthropological investigations of depression [@kleinman1985] despite frequent reports of depression or depression-like behavior in a wide range of societies [@haroz2017; @liu2020] and the potential for cross-cultural research to help understand depressive states [@haroz2017].
+
+## Depression and suicide attempts as both signals and bargaining tools
+
+Evolutionary theories of depression tend to either ignore suicidality, or take it as evidence that depression is dysfunctional.
+Wakefield, for instance, who has devoted much of his career to arguing that most cases of depression are simply severe but normal sadness and grief, nevertheless takes suicidality to indicate pathology for some cases of depression [e.g., @wakefield2017].
+@nettle2004 argues that the costs of depression, including suicidality, outweigh any benefits, and therefore adaptationist models of depression are implausible.
+@gilbert2006 sees suicidality as an example of a dysregulated escape defense [for reviews of evolutionary theories of depression, see @Hagen2011].
+
+Another possible explanation for the connection between depression, suicide, and social adversity is that some instances of depression and suicide attempts serve as means to elicit increased support from others by honestly signaling need to those invested in the well-being of the signaler, [@andrews2006; @Hagen2002; @Hagen2003; @HagenEtAl2008; @nock2008; @Rosenthal1993; @Stengel1956; @SymeEtAl2016], something which may be particularly useful in times when an individual cannot solve substantial fitness-relevant challenges on their own [@Hagen2003; @SymeEtAl2016].
+
+Due to the ease with which signals can be faked [@Zahavi1975; @mokkonen2016] and the costs of accepting a deceptive signal as reliable [@dawkins1978; @johnstone1993; @Hasson1994], demonstrating that one's need is genuine has likely been a recurrent adaptive problem since humans evolved the capacity to provide instrumental support to one another.
+One potential solution to this is to produce signals that are unprofitable to fake [@Zahavi1975].
+This is possible whenever the benefits of signaling outweigh the costs for those who have the relevant underlying quality but the costs outweigh the benefits for those who lack the quality or possess it to a lesser degree [@zahavi1977; @grafen1990].
+In particular, if the benefits of sending the signal are the same for signalers regardless of condition, but the signal cost outweighs this benefit for signalers without the underlying quality (a "costly signal"), then individuals with the underlying quality can evolve to send the signal and receivers can evolve to respond in mutually beneficial ways to the signal.
+
+Depression and suicidal behavior fit this criterion as both are relatively costly for those not facing adversity than those who are.
+In the case of depression, the large-scale reduction in one's normal routine of fitness enhancing behavior is relatively less costly for those whose situations result in a limited ability to obtain fitness-relevant benefits, with depression likely adding no additional costs in instances of extreme deprivation [@Hagen2003].
+When it comes to suicide, the bulk of the costs associated with suicide attempts are only felt in times that result in death or severe bodily harm.
+For this reason, the way others view and respond to suicide attempts is likely to be strongly influenced by the probability that the attempt would result in death or severe injury [@Rosenthal1993].
+Despite this difference, the previously mentioned logic still applies with increased risk of death being relatively more costly for those able to advance their fitness prospects in their day-to-day lives.
+
+The costs of depression and suicidal behavior may be particularly important in times of conflict or when the level of support needed to address one's situation is substantial, both of which should be expected to increase the payoff of manipulating others through fake signals.
+When either condition applies, less costly signals like verbal requests, facial sadness, and crying are likely to be less reliable as their low costs can easily be made up for with increased social support, thereby favoring the use of costlier signals so long as the costs of signaling are outweighed by the benefits [@SymeHagen2021].
+
+<!-- Durkheim's pioneering study of suicide [@durkheim1897] helped launch sociology as a quantitative discipline.
+Sociological investigations of suicide flourished through much of the 20th century, but were supplanted by medical and public health approaches as the biomedical model of mental health took hold in the late 1970's and early 1980's [@wray2011; @syme2020].
+The biomedical model tends to frame suicide as a problem with the individual, e.g., as one involving psychiatric disturbance, drug addiction, or stress sensitivity [@wray2011].
+This theoretical approach has made little progress: rates of suicide, which vary widely by country, have remained relatively flat in countries for which there are long-term data, such as the US, UK, Japan, and Sweden [@owidsuicide].
+-->
+
+<!-- ## Conflict plays a central role in suicidality and depression -->
+
+<!-- Early on, anthropologists also tackled the problem of suicide as manifested in the small traditional societies in which they conducted their fieldwork.
+Suicide, they found, was commonly a form of protest, revenge, and/or appeal [e.g., @Malinowski:1932; @niehaus2012].
+Some ethnographers, such as @Hezel:1987, conceptualized suicide as a form of anger, whereas others, such as @Giddens:1964, conceptualized suicide as a form of social pressure.
+@Counts:1980 emphasized the powerlessness of suicide victims.
+Common to almost all theoretical and empirical investigations of suicide is a focus on *completed* suicides, i.e., suicide deaths.
+@SymeEtAl2016, in contrast, argued that because the vast majority of suicidal behavior does not result in death, the proper focus should be on suicide ideation and suicide attempts (see Figure \@ref(fig:cdc)).
+Suicide attempts, as we explain next, are a gamble to improve one's life by taking a low but non-zero risk of death.
+Most suicides deaths, especially in young, physically healthy individuals, are therefore the inevitable consequence that some individuals lose this gamble.
+-->
 

### 2021-04-30 Paper.rmd
Small change in study aims and predictions

@@
 The primary aim of this study was to examine responses to various forms of emotional signaling in an experimental vignette study.
-As the costs of a signal are expected to correspond to the reliability of the information provided, we predicted that costlier signals would (1) increase self-reported belief in the signaler's claims and (2) increase the likelihood of participants providing help, with (3) changes in likelihood of support being largely mediated by changes in the participants' belief in the signaler's need from pre-signal to post-signal.
+As signals become less likely to be worth faking with increased costs, we predicted that costlier signals would (1) increase self-reported belief in the signaler's claims and (2) increase the likelihood of participants providing help, with (3) changes in likelihood of support being largely mediated by changes in the participants' belief in the signaler's need from pre-signal to post-signal.
 

### 2021-04-30 Paper.rmd
Many edits to intro and methods

@@
 
+Formal models of bargaining highlight the role of private information regarding the value each party places the cooperative endeavor.
 Withholding or risking one's contributions to a cooperative endeavor can be conceptualized as credibly signaling private information about one's need.
@@
 In a classic non-cooperative game theory model of bargaining over the division of benefits, @Rubenstein:1982 showed that two parties can come to an immediate agreement over division of benefits despite conflicts of interest if the parties' valuations of cooperation are not private information: in this case, each party knows exactly what division of benefits the other will accept, and can therefore make that offer immediately, avoiding the cost of delay.
-If valuations are private information, however, then immediate agreement might not be possible because each party has an incentive to request an amount greater than their actual valuation.
+If valuations are private information, however, then immediate agreement might not be possible because each party has an incentive to request an amount greater than their actual valuation, which would harm the other party.
 A willingness to delay is a credible signal that one has a low valuation of the endeavor, and is therefore genuinely in need, because for those with a low valuation the benefit of waiting for a better offer outweighs the low cost of delay whereas for those for those with a high valuation the benefit of waiting for a better offer does not outweigh the higher cost of delay.
 Once valuations are known, the game reduces to the one in @Rubenstein:1982, and the parties can reach an agreement on the division of benefits [@KennanWilson1993; @feinberg2005].
-
-@Rosenthal1993 proposed a credible signaling model of what he termed "gambling-type" suicide attempts.
-The vast majority of suicidal behavior does not result in death.
-In young adult women in the US, there are hundreds of attempts for every death (see Figure \@ref(fig:cdc)).
-Nevertheless, each attempt carries a non-zero risk of death.
-This cost allows social partners to accurately discriminate between those who are genuinely in need and those who are not [@Rosenthal1993].
-In the case of depression, the large-scale reduction in one's normal routine of fitness enhancing behavior is relatively less costly for those whose situations result in a limited ability to obtain fitness-relevant benefits, with depression likely adding no additional costs in instances of extreme deprivation [@Hagen2003].
-When it comes to suicide, the bulk of the costs associated with suicide attempts are only felt in times that result in death or severe bodily harm.
-For this reason, the way others view and respond to suicide attempts is likely to be strongly influenced by the probability that the attempt would result in death or severe injury [@Rosenthal1993].
-Despite this difference, the previously mentioned logic still applies with increased risk of death being relatively more costly for those able to advance their fitness prospects in their day-to-day lives.
+@Hagen2003 proposed that the substantial reduction in productivity in depression corresponds to a willingness to delay, and is therefore a credible signal of need.
+In other words, reduced productivity is relatively less costly for those whose efforts are currently not yielding many fitness-relevant benefits than for those whose efforts are yielding substantial benefits [@Hagen2003].
+
+## Suicidality
+
+Suicidality is closely linked to depression.
+Suicidal ideation is one of nine diagnostic criteria for a major depressive episode [MDE, @dsm5], it is associated with depression across cultures [@haroz2017], and depression is a major risk factor for suicidal behavior [@hawton2013].
+
+Anthropology has long viewed suicidality as largely the result of social problems.
+Early in the field’s history, anthropologists tackled the problem of suicide as manifested in the small, traditional societies in which they conducted their fieldwork.
+Suicide, they found, was commonly a form of protest, revenge, and/or appeal (e.g., Malinowski, 1932; Niehaus, 2012).
+Some ethnographers, such as Hezel (1987), conceptualized suicide as a form of anger, whereas others, such as Giddens (1964), conceptualized suicide as a form of social pressure.
+Counts (1980) emphasized the powerlessness of suicide victims.
+
+Common to almost all theoretical and empirical investigations of suicide is a focus on *completed* suicides, i.e., suicide deaths.
+The vast majority of suicidal behavior, however, does not result in death.
+In young adult women in the US, for example, there are hundreds of attempts for every death (see Figure \@ref(fig:cdc)).
+@SymeEtAl2016 therefore argued that the scientific focus should be on suicide ideation and suicide attempts.
+
+Raymond Firth was one of the first to view suicidality as a gamble to improve one's circumstances in the here and now.
+Based on observations that suicide attempts often followed loss or conflict and varied substantially in their likelihood of death, he argued that a sizable subset of the suicide attempts among the Tikopia were not meant to end in death but instead were a means to elicit attention, status, or immediate reintegration into the community following negative events (Firth 1936; 1961).
+
+@Rosenthal1993 proposed a credible signaling model of what he, like Firth, viewed as 'gambling-type' suicide attempts.
+In the Rosenthal model, as long as that risk is greater than or equal to the net benefit a non-needy person would realize by sending the signal (discounted by the risk of death), social partners can trust that signal senders are genuinely in need despite conflicts of interest [@Rosenthal1993].
+Most suicides deaths, especially in young, physically healthy individuals, would therefore be the inevitable consequence that some individuals lose this gamble.
+These and similar ideas [@andrews2006; @HagenEtAl2008; @nock2008; @Stengel1956] suggest that depression symptoms that put one's value to others at risk, such as suicidality and loss of interest, might be credible signals of need.
+
+<!-- Compared to suicide, however, there are fewer anthropological investigations of depression [@kleinman1985] despite frequent reports of depression or depression-like behavior in a wide range of societies [@haroz2017; @liu2020] and the potential for cross-cultural research to help understand depressive states [@haroz2017].
+-->
 
@@
 
-As they are prohibitively costly for those in minor need, the costs of depression and suicidal behavior may be particularly important in times of substantial conflicts of interest or when the level of support needed to address one's situation is substantial, both of which should be expected to increase the payoff of manipulating others through fake signals.
+<!-- As they are prohibitively costly for those in minor need, the costs of depression and suicidal behavior may be particularly important in times of substantial conflicts of interest or when the level of support needed to address one's situation is substantial, both of which should be expected to increase the payoff of manipulating others through fake signals.
 When either condition applies, less costly signals like verbal requests, facial sadness, and crying are likely to be less reliable as their low costs can easily be made up for with increased social support, thereby favoring the use of costlier signals so long as the costs of signaling are outweighed by the benefits [@SymeHagen2021].
+-->
 
@@
 
-## Anthropology of depression and suicide
-
-Anthropology, in contrast, has long viewed depressive states as largely the result of social problems.
-Early in the field’s history, anthropologists tackled the problem of suicide as manifested in the small, traditional societies in which they conducted their fieldwork.
-Suicide, they found, was commonly a form of protest, revenge, and/or appeal (e.g., Malinowski, 1932; Niehaus, 2012).
-Some ethnographers, such as Hezel (1987), conceptualized suicide as a form of anger, whereas others, such as Giddens (1964), conceptualized suicide as a form of social pressure.
-Counts (1980) emphasized the powerlessness of suicide victims.
-Common to almost all theoretical and empirical investigations of suicide is a focus on completed suicides, i.e., suicide deaths.
-
-Raymond Firth, in contrast, viewed suicidality as a gamble to improve one's circumstances in the here and now.
-Based on observations that suicide attempts often followed loss or conflict and varied substantially in their likelihood of death, he argued that a sizable subset of the suicide attempts among the Tikopia were not meant to end in death but instead were a means to elicit attention, status, or immediate reintegration into the community following negative events (Firth 1936; 1961).
-More recently, Syme, Garfield, & Hagen (2016) also emphasized that the vast majority of suicidal behavior does not result in death, arguing the proper focus should be on suicide ideation and attempts, with death as an unintended consequence.
-See Figure 1.
-
-<!-- move figure one here -->
-
-Suicidality is closely linked to depression.
-Suicidal ideation is one of nine diagnostic criteria for a major depressive episode [MDE, @dsm5], it is associated with depression across cultures [@haroz2017], and depression is a major risk factor for suicidal behavior [@hawton2013].
-Compared to suicide, however, there are fewer anthropological investigations of depression [@kleinman1985] despite frequent reports of depression or depression-like behavior in a wide range of societies [@haroz2017; @liu2020] and the potential for cross-cultural research to help understand depressive states [@haroz2017].
-
 ## Depression and suicide attempts as both signals and bargaining tools
 
-Evolutionary theories of depression tend to either ignore suicidality, or take it as evidence that depression is dysfunctional.
+<!-- Evolutionary theories of depression tend to either ignore suicidality, or take it as evidence that depression is dysfunctional.
 Wakefield, for instance, who has devoted much of his career to arguing that most cases of depression are simply severe but normal sadness and grief, nevertheless takes suicidality to indicate pathology for some cases of depression [e.g., @wakefield2017].
@@
 @gilbert2006 sees suicidality as an example of a dysregulated escape defense [for reviews of evolutionary theories of depression, see @Hagen2011].
-
-Another possible explanation for the connection between depression, suicide, and social adversity is that some instances of depression and suicide attempts serve as means to elicit increased support from others by honestly signaling need to those invested in the well-being of the signaler, [@andrews2006; @Hagen2002; @Hagen2003; @HagenEtAl2008; @nock2008; @Rosenthal1993; @Stengel1956; @SymeEtAl2016], something which may be particularly useful in times when an individual cannot solve substantial fitness-relevant challenges on their own [@Hagen2003; @SymeEtAl2016].
-
-Due to the ease with which signals can be faked [@Zahavi1975; @mokkonen2016] and the costs of accepting a deceptive signal as reliable [@dawkins1978; @johnstone1993; @Hasson1994], demonstrating that one's need is genuine has likely been a recurrent adaptive problem since humans evolved the capacity to provide instrumental support to one another.
+-->
+
+<!-- Another possible explanation for the connection between depression, suicide, and social adversity is that some instances of depression and suicide attempts serve as means to elicit increased support from others by honestly signaling need to those invested in the well-being of the signaler, [@andrews2006; @Hagen2002; @Hagen2003; @HagenEtAl2008; @nock2008; @Rosenthal1993; @Stengel1956; @SymeEtAl2016], something which may be particularly useful in times when an individual cannot solve substantial fitness-relevant challenges on their own [@Hagen2003; @SymeEtAl2016].
+-->
+
+<!-- Due to the ease with which signals can be faked [@Zahavi1975; @mokkonen2016] and the costs of accepting a deceptive signal as reliable [@dawkins1978; @johnstone1993; @Hasson1994], demonstrating that one's need is genuine has likely been a recurrent adaptive problem since humans evolved the capacity to provide instrumental support to one another.
 One potential solution to this is to produce signals that are unprofitable to fake [@Zahavi1975].
@@
 
-### Determining the impact of cues versus signals
-
-Distinguishing between the information provided by signals versus cues is a major challenge for signaling approaches to behavior.
+<!-- ### Determining the impact of cues versus signals -->
+
+<!-- Distinguishing between the information provided by signals versus cues is a major challenge for signaling approaches to behavior.
 A signal differs from a cue in that it is intentionally sent by an organism to alter the perceptions and behaviors of others, while a cue is any piece of information that influences an individual's behavior or physiological state that was not created for communicative effect [@MaynardSmithHarper1995].
@@
 Suicidality is likely an exception to this, due to the likelihood most suicide attempts do not have non-signaling functions [see @deCatanzaro1991 for a possible exception].
+-->
 
@@
 
-Experimental vignette studies, which employ "a short, carefully constructed description of a person, object, or situation, representing a systematic combination of characteristics" [@atzmuller2010, p.128], aim to approach the ecological validity of observational studies by presenting participants with rich, real-world scenarios, while at the same time allowing researchers to randomize participants into conditions in which theoretically relevant dimensions of the vignettes are systematically manipulated, thus enabling robust causal inferences [@atzmuller2010].
+Experimental vignette studies, which employ a short, carefully constructed description of a person, object, or situation, aim to approach the ecological validity of observational studies by presenting participants with rich, real-world scenarios, while at the same time allowing researchers to randomize participants into conditions in which theoretically relevant dimensions of the vignettes are systematically manipulated, thus enabling robust causal inferences [@atzmuller2010].
 Experimental vignette studies are conducted in a broad range of disciplines, including psychology, economics, sociology, management studies, political science, and education [@atzmuller2010; @aguinis2014].
@@
 The primary aim of this study was to examine responses to various forms of emotional signaling in an experimental vignette study.
-As signals become less likely to be worth faking with increased costs, we predicted that costlier signals would (1) increase self-reported belief in the signaler's claims and (2) increase the likelihood of participants providing help, with (3) changes in likelihood of support being largely mediated by changes in the participants' belief in the signaler's need from pre-signal to post-signal.
+As signal cost increases, and signals therefore become less profitable to fake, we predicted that participants would report (1) increased belief in the signaler's claims and (2) increased likelihood of providing help, with (3) the increased likelihood of providing help mediated by the increased belief in the signaler's need.
+A secondary aim was to investigate a scenario that is common in traditional societies but uncommon in Western societies -- arranged marriages -- where conflicts between parents and offspring often result in depression and suicidality [@SymeEtAl2016]
 
@@
 This study utilized a between-subjects pretest-posttest design to examine how four different emotional signals (treatments) would influence (1) the degree participants believed a fictional character to be in need (*Belief*) and (2) the likelihood they would provide help (*Action*) relative to a simple *Verbal request* (the control condition), in four different vignettes, for a total of 20 conditions.
-In this design, the outcomes are measured at pre-treatment (T1), participants are then randomized into either a control group or a treatment group (one of the emotional signals), and the outcomes are measured again (T2).
-Regression models are used to determine the effect of the treatment conditions on the posttest outcome variables, relative to the control condition, controlling for pretest levels of the outcome variables (we also explored within-subjects effects of the signal on outcomes at T2 compared to T1).
+In this design, the outcomes are measured at pre-treatment (T1).
+Participants are then randomized into either a control group or a treatment group, i.e., one of the emotional signals, and the outcomes are measured again (T2).
+Regression models (described later) are used to determine the effect of the treatment conditions on the posttest outcome variables, relative to the control condition, controlling for pretest levels of the outcome variables (we also explored within-subjects effects of the signal on outcomes at T2 compared to T1).
 
 In principle, pretest-posttest designs, by controlling for pretest variation in the outcome, increase the precision of the estimate of the treatment effect on the outcome [@dimitrov2003].
-In survey experiments, however, researchers often favor posttest-only designs over pretest-posttest designs because they worry that the pre-treatment measurement of the outcome will influence the treatment effect on the outcome (i.e., the effects of asking the same question twice) due to, e.g., demand effects, in which participants try to conform to experimenter expectations, or to consistency pressures, in which participants try to provide consistent responses regardless of treatments [@clifford2021].
+In survey experiments, however, researchers often favor posttest-only designs over pretest-posttest designs.
+The common concern is that the pre-treatment measurement of the outcome will influence the treatment effect on the outcome (i.e., the effects of asking the same question twice) due to, e.g., demand effects, in which participants try to conform to experimenter expectations, or to consistency pressures, in which participants try to provide consistent responses regardless of treatments [@clifford2021].
 In a study with six experiments that randomly assigned respondents to alternative designs (e.g., pretest-posttest, posttest only) @clifford2021 found these concerns to be overblown.
@@
 
+## Lessons learned from two pilot studies
+
+The current study is a refinement of a large MTurk experimental vignette pilot study (N=`r nrow(signalingdata2018b)`) that used a different vignette but very similar signals and outcomes, and a much smaller pilot study posted to [reddit.com/r/SampleSize/](https://www.reddit.com/r/SampleSize/) (N=28) that used draft versions of three vignettes used in the current study, along with the same signals and outcomes.
+One major goal of the MTurk pilot study was to determine if believability and willingness to help were simply artifacts of the fictional victim's psychiatric distress.
+We therefore included a "signaling" condition in which the victim exhibited schizophrenic symptoms.
+As predicted, believability and willingness to help in this condition were dramatically lower than in any other condition (see Figure \@ref(fig:piloteffects)), ruling out this alternative explanation.
+We therefore did not include the schizophrenic condition in the current study.
+See the SI for more details on the pilot studies.
+
+## Sampling
+
+Participants for this study were recruited from Amazon Mechanical Turk, a crowdsourcing platform that allows for the creation of Human Intelligence Tasks (HITs) that workers can complete for pay.
+As Amazon provides the infrastructure, it allows for a relatively low-cost way of collecting data for academic research at the cost of the data not being representative of any real population [@thomas2017].
+Despite this limitation, it is more diverse than most convenience samples [@kennedy2020; @DworkinEtAl2016; @thomas2017], with turkers in the US mainly differing in being younger, more educated, and lower income than the greater U.S.
+population [@RossEtAl2010; @boas2020].
+
+To test emotional signals in an arranged marriage vignette, we recruited an Indian MTurk sample.
+Indian samples are also likely to be younger and more educated than the general population but differ from US samples in that they are less diverse, have higher incomes relative to other Indians, and are more likely to come from regions with good internet access [@boas2020].
+
+Overall, the quality of data provided by MTurk workers tends to resemble that of university sample pools [@NeckaEtAl2016; @robinson2019], with there being some indication that it might outperform university samples due to its previously mentioned diversity [@thomas2017] or the overall attentiveness of turkers [@HauserSchwarz2016].
+In vignette studies, MTurk data quality also compares favorably to that from much more expensive population-based samples [@weinberg2014].
+For these reasons, concerns about data quality come primarily from the threat of bot use or respondents faking their location to take surveys in a language they do not understand well, with there being little evidence of the former [@kennedy2020] and the risk of the latter able to be minimized through well designed attention checks, timed responses, or general study design [@aguinis2020; @huang2015; @kennedy2020; @thomas2017].
+
+## Participants
+
+All participants in the US sample were over 18, located in the United States, had a HIT approval rate of over 98%, and had successfully completed at least 100 HITs as anything less results in approval rates of 100% [@kennedy2020].
+The Indian sample was the same except for only including participants who resided in India at the time of the study and the inclusion two participants who were included with a stricter HIT approval rate of over 99%.
+
+To reduce the risk of low quality responses, we used a variety of attention checks, which we clearly labeled as such to avoid demand characteristics on the outcomes of interest.
+The first was shown immediately after the consent form and provided participants with a random word and asked them to enter the vowels in the order in which they are found in the word.
+Capitalization did not matter and no word contained repeat vowels.
+Failure to enter the correct vowels in order resulted in the participants being filtered out of the study.
+The second followed the vignette and involved asking three questions about the story that were easy to answer for anyone paying attention.
+
+We also filtered out those who read the vignette faster than one-third the time it took MG to read it as fast as possible without concern for comprehension.
+This occurred immediately after participants finished the vignette.
+
+## Ethics
+
+All participants provided informed consent, and the consent form warned that some content might involve sexual assault.
+We estimated the study would take 4-8 minutes to complete for participants who did not take breaks.
+All participants who passed the attention checks were paid \$1 for their time, for an estimated rate of \$7.50/hr to \$15/hr (75% of US participants completed in `r signif(quantile(d_US$TotalTime, 0.75)/60, 2)` minutes; 75% of Indian participants completed in `r signif(quantile(d_India$TotalTime, 0.75)/60, 2)` minutes).
+This study was certified exempt by the Washington State University Human Research Protection Program.
+
 ## Vignettes
 
-Four vignettes were used in this study in which both the presence of conflicts of interest and the existence of private information about one's need were emphasized.
-Due to the expectation that depression and suicide are likely too costly of signals for relatively minor instances of need, we designed this study to involve severe scenarios associated with suicide attempts both ethnographically and clinically (i.e, sexual assault, non-sexual assault, and thwarted marriage).
+Four vignettes were used in this study that involved (1) claims of severe adversity that were private information, (2) conflicts of interest that would undermine believability of these claims, and (3) emotional signals.
+The vignette scenarios involved potentially severe types of adversity, such as sexual and non-sexual assault and thwarted marriage, that often precede cases of depression and suicidality in the ethnographic and clinical record.
+
+### Time 1: Claim of need in a conflictual relationship
 
@@
 
-## Signals
+### Time 2: Signals
 
@@
 
-## Lessons learned from two pilot studies
-
-The current study is a refinement of a large MTurk experimental vignette pilot study (N=`r nrow(signalingdata2018b)`) that used a different vignette but very similar signals and outcomes, and a much smaller pilot study posted to [reddit.com/r/SampleSize/](https://www.reddit.com/r/SampleSize/) (N=28) that used draft versions of 3 vignettes used here, along with the same signals and outcomes.
-In the MTurk pilot study, there was a single vignette in which an imagined sister claims her child needs an expensive emergency medical procedure, and asks for a very large loan.
-In the small reddit.com study, participants viewed and responded to two vignettes used here, each with a different signal.
-
-We learned five major lessons from the MTurk pilot study that influenced the design of the current study.
-First, as predicted, belief in the sister's need was highest in the *Depression* condition and lowest in the *Verbal request* condition, giving us confidence to continue this research (see Figure \@ref(fig:piloteffects)).
-Second, to rule out that believability and willingness to help were simply artifacts of the sister's psychiatric distress, we included a "signaling" condition in which the sister exhibited schizophrenic symptoms.
-As predicted, believability and willingness to help in this condition were dramatically lower than in any other condition, ruling out this alternative explanation.
-We therefore did not include the schizophrenic condition in the current study.
-Third, baseline (T1) believability was very high (mean = `r signif(pilot_results$meanT1belief, 2)` and median = `r signif(pilot_results$medianT1belief, 2)` on a 0-100 point scale), leaving little scope for signals to increase believability.
-In the current study we therefore endeavored to provide details in the vignettes that would undermine the victim's believability at baseline.
-Fourth, contrary to our hypothesis, the *Suicide threat* and *Suicide attempt* signals reduced believability relative to *Depression*.
-We surmised that the sister's adversity -- a sick child -- was not sufficient to justify a suicide attempt, thus undermining her believability.
-In the current study the signaler herself is therefore the victim, and the forms of adversity -- physical and sexual assault and thwarted and forced marriage -- are those that are frequently associated with suicidality.
-Fifth, the content of the vignette matters, so instead of a single vignette we decided to use four different vignettes to help determine the extent to which signaling effects were sensitive to seemingly irrelevant details of the vignettes.
-
-In the reddit.com pilot study, participants viewed two vignettes (with different signals in each one), and responded with lower belief to the second vignette compared to the first (regardless of the vignette or signal).
-To avoid such order effects, which are a common problem in vignette studies that use multiple vignettes [@su2020], we decided to present each participant in the current study with a single vignette and signal.
-
 ## Preregistration
@@
 For more details, see the SI and /.
-
-## Sampling
-
-Participants for this study were recruited from Amazon Mechanical Turk, a crowdsourcing platform that allows for the creation of Human Intelligence Tasks (HITs) that workers can complete for pay.
-As Amazon provides the infrastructure, it allows for a relatively low-cost way of collecting data for academic research at the cost of the data not being representative of any real population [@thomas2017].
-Despite this limitation, it is more diverse than most convenience samples [@kennedy2020; @DworkinEtAl2016; @thomas2017], with turkers in the US mainly differing in being younger, more educated, and lower income than the greater U.S.
-population [@RossEtAl2010; @boas2020].
-Indian samples are also likely to be younger and more educated than the general population but differ from US samples in that they are less diverse, have higher incomes relative to other Indians, and are more likely to come from regions with good internet access [@boas2020].
-
-Overall, the quality of data provided by MTurk workers tends to resemble that of university sample pools [@NeckaEtAl2016; @robinson2019], with there being some indication that it might outperform university samples due to its previously mentioned diversity [@thomas2017] or the overall attentiveness of turkers [@HauserSchwarz2016].
-In vignette studies, MTurk data quality also compares favorably to that from much more expensive population-based samples [@weinberg2014].
-For these reasons, concerns about data quality come primarily from the threat of bot use or respondents faking their location to take surveys in a language they do not understand well, with there being little evidence of the former [@kennedy2020] and the risk of the latter able to be minimized through well designed attention checks, timed responses, or general study design [@aguinis2020; @huang2015; @kennedy2020; @thomas2017].
-
-## Participants
-
-All participants in the US sample were over 18, located in the United States, had a HIT approval rate of over 98%, and had successfully completed at least 100 HITs as anything less results in approval rates of 100% [@kennedy2020].
-The Indian sample was the same except for only including participants who resided in India at the time of the study and the inclusion two participants who were included with a stricter HIT approval rate of over 99%.
-
-To reduce the risk of low quality responses, we used a variety of attention checks, which we clearly labeled as such to avoid demand characteristics on the outcomes of interest.
-The first was shown immediately after the consent form and provided participants with a random word and asked them to enter the vowels in the order in which they are found in the word.
-Capitalization did not matter and no word contained repeat vowels.
-Failure to enter the correct vowels in order resulted in the participants being filtered out of the study.
-The second followed the vignette and involved asking three questions about the story that were easy to answer for anyone paying attention.
-
-We also filtered out those who read the vignette faster than one-third the time it took MG to read it as fast as possible without concern for comprehension.
-This occurred immediately after participants finished the vignette.
-
-Informed consent was given by proceeding with the study after reading the consent form, and all participants who passed the attention checks were paid \$1 for their time, with us estimating it would take 4-8 minutes before data collection.
-This study was certified exempt by the Washington State University Human Research Protection Program (certification number: 18528-001).
 
@@
 
-## Pilot study description
+## Pilot study descriptions
 
@@
 ```
+
+In the small reddit.com study, participants viewed and responded to two vignettes used here, each with a different signal.
+
+## Lessons learned from the pilot study
+
+We learned five major lessons from the MTurk pilot study that influenced the design of the current study.
+First, as predicted, belief in the sister's need was highest in the *Depression* condition and lowest in the *Verbal request* condition, giving us confidence to continue this research (see Figure \@ref(fig:piloteffects)).
+Second, to rule out that believability and willingness to help were simply artifacts of the sister's psychiatric distress, we included a "signaling" condition in which the sister exhibited schizophrenic symptoms.
+As predicted, believability and willingness to help in this condition were dramatically lower than in any other condition, ruling out this alternative explanation.
+We therefore did not include the schizophrenic condition in the current study.
+Third, baseline (T1) believability was very high (mean = `r signif(pilot_results$meanT1belief, 2)` and median = `r signif(pilot_results$medianT1belief, 2)` on a 0-100 point scale), leaving little scope for signals to increase believability.
+In the current study we therefore endeavored to provide details in the vignettes that would undermine the victim's believability at baseline.
+Fourth, contrary to our hypothesis, the *Suicide threat* and *Suicide attempt* signals reduced believability relative to *Depression*.
+We surmised that the sister's adversity -- a sick child -- was not sufficient to justify a suicide attempt, thus undermining her believability.
+In the current study the signaler herself is therefore the victim, and the forms of adversity -- physical and sexual assault and thwarted and forced marriage -- are those that are frequently associated with suicidality.
+Fifth, the content of the vignette matters, so instead of a single vignette we decided to use four different vignettes to help determine the extent to which signaling effects were sensitive to seemingly irrelevant details of the vignettes.
+
+In the reddit.com pilot study, participants viewed two vignettes (with different signals in each one), and responded with lower belief to the second vignette compared to the first (regardless of the vignette or signal).
+To avoid such order effects, which are a common problem in vignette studies that use multiple vignettes [@su2020], we decided to present each participant in the current study with a single vignette and signal.
 
@@
 
+us_median_hh <- 68703 # census.gov
+india_median_hh <- 2266 # ??
+
 clrs <- viridisLite::magma(11)[c(4, 8)]
@@
   geom_jitter(width = 0.5, alpha = 0.35) +
-  geom_hline(yintercept = log10(2266), linetype = 'dotted', colour = clrs[1]) +
-  geom_hline(yintercept = log10(68703), linetype = 'dotted', colour = clrs[2]) +
-  annotate('text', 85, log10(68703), label = 'Median US\nincome', hjust = 0) +
-  annotate('text', 85, log10(2266), label = 'Median India\nincome', hjust = 0) +
+  geom_hline(yintercept = log10(india_median_hh), linetype = 'dotted', colour = clrs[1]) +
+  geom_hline(yintercept = log10(us_median_hh), linetype = 'dotted', colour = clrs[2]) +
+  annotate('text', 85, log10(us_median_hh), label = 'Median US\nincome', hjust = 0) +
+  annotate('text', 85, log10(india_median_hh), label = 'Median India\nincome', hjust = 0) +
   scale_color_binary() +

### 2021-05-03 Paper.rmd
Added detail to vignette descriptions

@@
 Participants in the US sample were randomly assigned to either the "basketball coach," "romantic partner," or "brother-in-law" vignettes.
-In the "basketball coach" scenario, the star player on a university basketball team comes to the participant (who is asked to imagine themselves as the athletic director at a university) and claims she was sexually assaulted by her coach.
-However, there are indications the player might be lying to get more playing time.
+In the "basketball coach" scenario, the star player on a university basketball team comes to the participant, who is asked to imagine themselves as the athletic director at a university, and claims she was sexually assaulted by her head coach, a physically powerful man.
+However, there has been a history of conflict between the star player and the coach over playing time, and police are unable to find evidence that corroborate her claims.
 
 The "brother-in-law" vignette involved participants imagining that they let their sister, brother-in-law, and niece move in with the participant and their 15-year-old daughter after their sister's family lost their house in a fire.
-During this time, the participant's daughter becomes jealous of her cousin before accusing her uncle of sexually assaulting her.
+During this time, the participant's daughter becomes jealous of her cousin, who appears to be a social competitor.
+A few weeks after claiming her cousin was trying to still her boyfriend, she then accuses her uncle of sexually assaulting her.
 
@@
 However, their 13-year-old daughter, who has a history of trying to get in the way of their relationships, is clearly not happy with this.
-After a period of sustained conflict, she accuses the romantic partner of physically assaulting her but cannot produce any evidence.
+After a period of sustained conflict with both the participants and the romantic partner, she accuses the romantic partner of physically assaulting her but cannot produce any evidence.
 

### 2021-05-03 Paper.rmd
Added sources for india hh income

--- 2021-04-30 Paper.rmd
@@
 us_median_hh <- 68703 # census.gov
-india_median_hh <- 2266 # ??
+
+# IHDS2
+# Household Income Inequality and Income Mobility: Implications Towards Equalizing Longer-Term Incomes in India.
+By: Mishra, Aswini Kumar, International Economic Journal, 10168737, Jun2018, Vol.
+32, Issue 2
+#
+# Table 1: per capita household income
+# 	Mean	Median	Gini coefficient
+# 2011–2012			
+# Urban	36,101.4	22,595.0	49.0
+# Rural	18,158.0	11,085.3	51.5
+# Total	23,831.4	13,860.0	53.1
+
+# 6.4 persons per household
+
+# 13860 * 6.4 = 88704
+
+# According to some website, in 2021 this would be
+# 154,115.8 rupees (73.74% inflation), which is $2,087
+india_median_hh <- 2087
 

### 2021-05-04 Paper.rmd
Editing Methods section

--- 2021-05-03 Paper.rmd
@@
 
-## Vignettes
-
-Four vignettes were used in this study that involved (1) claims of severe adversity that were private information, (2) conflicts of interest that would undermine believability of these claims, and (3) emotional signals.
+## Survey
+
+Four vignettes were used in this study that involved (1) a female's claim of severe adversity that was private information, (2) conflicts of interest between the victim and the participant that would undermine the believability of her claims, and (3) her emotional signals.
 The vignette scenarios involved potentially severe types of adversity, such as sexual and non-sexual assault and thwarted marriage, that often precede cases of depression and suicidality in the ethnographic and clinical record.
+See Table \@ref(tab:design).
 
@@
 
-Participants in the US sample were randomly assigned to either the "basketball coach," "romantic partner," or "brother-in-law" vignettes.
-In the "basketball coach" scenario, the star player on a university basketball team comes to the participant (who is asked to imagine themselves as the athletic director at a university) and claims she was sexually assaulted by her coach.
-However, there are indications the player might be lying to get more playing time.
-
-The "brother-in-law" vignette involved participants imagining that they let their sister, brother-in-law, and niece move in with the participant and their 15-year-old daughter after their sister's family lost their house in a fire.
-During this time, the participant's daughter becomes jealous of her cousin before accusing her uncle of sexually assaulting her.
-
-The "romantic partner" vignette had participants imagine that they found a highly desirable partner after years of being single.
-However, their 13-year-old daughter, who has a history of trying to get in the way of their relationships, is clearly not happy with this.
-After a period of sustained conflict, she accuses the romantic partner of physically assaulting her but cannot produce any evidence.
-
-Those in the Indian sample only saw the "thwarted marriage vignette." In this scenario, the participant and their family are described as trying to arrange a dowry for their older daughter so she can marry a man she already loves.
+At Time 1 (T1) participants in the US sample were randomly assigned to either the "basketball coach," "romantic partner," or "brother-in-law" vignettes, and the Indian sample was assigned to the Thwarted marriage vignette.
+
+**Basketball coach vignette**: Each participant was asked to imagine that they are a university athletic director.
+The star player on the women's basketball team comes to the participant and claims she was sexually assaulted by her head coach, a physically powerful man.
+However, there is a history of conflict between the star player and the coach over playing time, and police are unable to find evidence to corroborate her claims.
+
+**Brother-in-law vignette**: Each participant was asked to imagine that they let their sister, brother-in-law, and niece move in with them after their sister's family lost their house in a fire.
+During this time, the participant's 15 year old daughter becomes jealous of her cousin, who appears to be a social competitor.
+A few weeks after claiming her cousin was trying to steal her boyfriend, the participant's daughter accuses her uncle of sexually assaulting her.
+
+**Romantic partner vignette**: Each participant was asked to imagine that they found a highly desirable romantic partner after years of being single.
+However, the participant's 13-year-old daughter, who has a history of interfering with the participant's past relationships, is clearly unhappy with the new partner.
+After a period of sustained conflict with both the participant and the romantic partner, she accuses the romantic partner of physically assaulting her, but cannot produce any evidence.
+
+**Thwarted marriage vignette**: Indian sample only.
+Each participant was asked to imagine that their family was trying to arrange a dowry for their older daughter so she can marry a man she already loves, while still saving enough money for their younger daughter's dowry.
 After the man's family demands more money, the participant's family tries to find a second man, who the older daughter claims to find unattractive.
-Due to the younger daughter in the story only being two years younger, any additional investment in the dowry will come at the younger daughter's expense.
+Any increase in the dowry will come at the younger daughter's expense.
+The participant therefore proceeds to arrange a marriage to the second man as the first man's family makes arrangements with a different woman.
 
 The full vignettes are available in the SI.
-
-### Time 2: Signals
-
-The sole randomized treatment in this study was the signal participants saw, with these signals being one of (1) the control condition: a verbal request without additional signaling, (2) crying, (3) mild-depression, (4) depression, and (5) a suicide attempt, with the order of the conditions here moving from low to high cost.
-
-As many depression scales include measures of crying [for discussion on the relationship between crying and depression see @bylsma2020] and depression is a major risk factor for suicide [@BostwickPankratz2000; @Kessler2012], each signal was designed to build off of the less costly signals so that each signal contained elements of any signal it was costlier than.
-Although referred to as signals throughout the paper for brevity, we expect that the hypothesized signals of need, like many signals, will also provide information to others in the form of cues [for discussion on the evolution of signals from cues see: @biernaskie2018; @Tiokhin2016; @Steinkopf2015].
-The full text for the signals are available in the SI.
 
@@
 
-## Preregistration
-
-We preregistered four OLS linear regression models and one mediation model (<https://osf.io/g3s6n>).
-The first two regression models tested the effects of our ordinal signal variable on Time 2 *Belief* and *Action*, controlling for T1 *Belief* and *Action*, respectively (a pre-test/post-test design):
-
-`r extract_eq(models_prereg$Model$m1, intercept='beta', wrap=T)` `r extract_eq(models_prereg$Model$m3, intercept='beta', wrap=T)`
-
-The second two models added interaction terms between signal and T1 *Belief* and *Action*, with the rationale that the signals might have reduced effect for individuals who indicate high levels of belief and helping at baseline:
-
-`r extract_eq(models_prereg$Model$m1b, intercept='beta', wrap=T)` `r extract_eq(models_prereg$Model$m3b, intercept='beta', wrap=T)`
-
-The mediation model is in Figure \@ref(fig:medmodel):
-
-```{r medmodel, fig.cap="Possible causal effects of the signal on helping behavior.
-A credible signal of need increases belief that the victim is telling the truth and needs help, which increase the likelihood of helping.
-The direct path from the signal to action represents other causal effects of the signal on observers, such as perceptions of the victim's emotional state (and other factors not measured in this study) that might alter observer behavior."}
-
-knitr::include_graphics('paths.svg')
-```
-
-Specifically, the mediation and outcome models, respectively, are:
-
-`r extract_eq(med_prereg$model.m, intercept='beta', wrap=T)` `r extract_eq(med_prereg$model.y, intercept='beta', wrap=T)`
-
-For reasons we explain in the *Statistical methods* section, we report the OLS models in the Supplementary Information (SI), and in the Results section instead report conceptually equivalent generalized linear regression models (GLMs).
-
-## Power analysis
-
-```{r}
-pwr80_90 <- 
-  power_curve %>% 
-  group_by(Base) %>% 
-  summarise(
-    pwr80 = min(sample_size[power>=.8]), 
-    pwr90 = min(sample_size[power>=.9])
-  )
-```
-
-We used the pilot data to estimate the sample sizes needed to detect an effect of the *Depression* signal vs.
-*Verbal request* control (two conditions) on *Belief* in the victim's need.
-Power was about 80% for a sample size of about `r pwr80_90[[2,2]]`, and was about 90% for a sample size of about `r pwr80_90[[2,3]]`.
-We also estimated the sample size needed to detect an effect of *Depression* vs.
-a *Control* condition that was meant to not include any signaling (but which we realized, post hoc, did include a verbal request).
-Power was about 80% for a sample size of about `r pwr80_90[[1,2]]`, and was about 90% for a sample size of about `r pwr80_90[[1,3]]`.
-See Figure \@ref(fig:power).
-Given our \$1500 USD budget, we aimed for a sample size of 125 for two conditions, and 1250 for all conditions in the study.
-For more details, see the SI and /.
-
-## Survey
-
 ### Baseline measures (T1)
 
-In both samples, we recorded self-reports on how much participants believed the signaler to be telling the truth (T1Belief) and the likelihood of them helping the signaler as requested (T1Action).
-With the thwarted marriage vignette we also asked how they would split the money they had saved for the dowry between their daughters (T1Divide).
+After reading the vignettes, participants rated their belief the signaler to be telling the truth (T1Belief: 0-100) and the likelihood of them helping the signaler as requested (T1Action: 0-100).
+With the thwarted marriage vignette we also asked how they would split the money they had saved for the dowry between their daughters (T1Divide: 0-100; 50 is equal split).
 In every instance, the order of the questions was randomized to avoid order effects [@KrosnickAlwin1987].
@@
 
-### Post-treatment measures (T2-T4)
-
-We asked questions identical to those asked at T1 as the main post-treatment variables of interest (T2).
+### Time 2: Signals
+
+After rating their beliefs and actions, participants were randomized into either the control condition or one of four emotional signals by the victim (in order of increasing signal cost): (1) control condition: a verbal request without additional signaling; (2) crying; (3) mild-depression; (4) depression; and (5) a suicide attempt.
+The signals involve the participant encountering the victim some time after the adverse event and observing, e.g., crying, sad expressions, or poor personal hygiene.
+These descriptions do not use the terms depression, depressed, suicidal, or mental health.
+
+The signals were cumulative: crying can be an important feature of depression [for discussion on the relationship between crying and depression see @bylsma2020], and depression is a major risk factor for suicide [@BostwickPankratz2000; @Kessler2012].
+Accordingly, components of less-costly signals were included in more-costly signals.
+Although we use the term 'signals' throughout the paper for brevity, we expect that the hypothesized signals of need, like many signals, would also provide information to others in the form of cues [for discussion on the evolution of signals from cues see: @biernaskie2018; @Tiokhin2016; @Steinkopf2015].
+The full text for the signals are available in the SI.
+
+### Post-treatment measures (T2-T3)
+
+After reading the signaling text, participants answered questions identical to those asked at T1 as the main post-treatment variables of interest (T2).
 For the *Belief*, *Action*, and *Divide* variables, the position of the slider starting where participants placed it at T1.
-For the T2 emotion variables this involved no changes from the T1 version.
+T2 emotion multiple-choice questions were identical to those used in T1.
 
 As both a validity check and a way to understand the degree participants would be willing to help if they believed the participant completely, we presented participants with strong evidence that the claims were true (T3Action).
-In the US sample, this involved video evidence of the event in question occurring or a similar event after the fact.
+In the US sample, this involved telling participants there was video evidence of the event in question occurring or a similar event after the fact.
 With the thwarted marriage vignette, this involved the participant seeing the man their daughter wants to marry trash talk their daughter and their family.
-As a final attention check, we presented participants with the T3Action question but included instructions to ignore this and drag the slider all the way to the left (T4AttentionCheck).
-We did not exclude anyone from the study for failing this nor did we withhold payment.
 
@@
 
+## Preregistration
+
+We preregistered four OLS linear regression models and one mediation model (<https://osf.io/g3s6n>).
+The first two regression models tested the effects of our ordinal signal variable on Time 2 *Belief* and *Action*, controlling for T1 *Belief* and *Action*, respectively (a pre-test/post-test design):
+
+`r extract_eq(models_prereg$Model$m1, intercept='beta', wrap=T)` `r extract_eq(models_prereg$Model$m3, intercept='beta', wrap=T)`
+
+The second two models added interaction terms between signal and T1 *Belief* and *Action*, with the rationale that the signals might have reduced effect for individuals who indicate high levels of belief and helping at baseline:
+
+`r extract_eq(models_prereg$Model$m1b, intercept='beta', wrap=T)` `r extract_eq(models_prereg$Model$m3b, intercept='beta', wrap=T)`
+
+The mediation model is in Figure \@ref(fig:medmodel):
+
+```{r medmodel, fig.cap="Possible causal effects of the signal on helping behavior.
+A credible signal of need increases belief that the victim is telling the truth and needs help, which increase the likelihood of helping.
+The direct path from the signal to action represents other causal effects of the signal on observers, such as perceptions of the victim's emotional state (and other factors not measured in this study) that might alter observer behavior."}
+
+knitr::include_graphics('paths.svg')
+```
+
+Specifically, the mediation and outcome models, respectively, are:
+
+`r extract_eq(med_prereg$model.m, intercept='beta', wrap=T)` `r extract_eq(med_prereg$model.y, intercept='beta', wrap=T)`
+
+For reasons we explain in the *Statistical methods* section, we report the OLS models in the Supplementary Information (SI), and in the Results section instead report conceptually equivalent generalized linear regression models (GLMs).
+
+## Power analysis
+
+```{r}
+pwr80_90 <- 
+  power_curve %>% 
+  group_by(Base) %>% 
+  summarise(
+    pwr80 = min(sample_size[power>=.8]), 
+    pwr90 = min(sample_size[power>=.9])
+  )
+```
+
+We used the pilot data to estimate the sample sizes needed to detect an effect of the *Depression* signal vs.
+*Verbal request* control (two conditions) on *Belief* in the victim's need.
+Power was about 80% for a sample size of about `r pwr80_90[[2,2]]`, and was about 90% for a sample size of about `r pwr80_90[[2,3]]`.
+We also estimated the sample size needed to detect an effect of *Depression* vs.
+a *Control* condition that was meant to not include any signaling (but which we realized, post hoc, did include a verbal request).
+Power was about 80% for a sample size of about `r pwr80_90[[1,2]]`, and was about 90% for a sample size of about `r pwr80_90[[1,3]]`.
+See Figure \@ref(fig:power).
+Given our \$1500 USD budget, we aimed for a sample size of 125 for two conditions, and 1250 for all conditions in the study.
+For more details, see the SI and /.
+
 ## Statistical analyses

### 2021-05-04 Paper.rmd
Added d_US, d_India

@@
 ---
-title: "Depression and suicidality as costly signals of need"
+title: "Depression and suicidality as credible signals of need"
 author: "Michael R. Gaffney, Kai Adams, Kristen L. Syme, and Edward H. Hagen"
@@
     'd',
+    'd_US',
+    'd_India',
     'signalingdata2018b',

### 2021-05-04 Paper.rmd
Still working on methods section

@@
 
+## Power analysis
+
+```{r}
+pwr80_90 <- 
+  power_curve %>% 
+  group_by(Base) %>% 
+  summarise(
+    pwr80 = min(sample_size[power>=.8]), 
+    pwr90 = min(sample_size[power>=.9])
+  )
+```
+
+We used the pilot data to estimate the sample sizes needed to detect an effect of the *Depression* signal vs.
+*Verbal request* control on *Belief* in the victim's need.
+Power was about 80% for a sample size of about `r pwr80_90[[2,2]]`, and was about 90% for a sample size of about `r pwr80_90[[2,3]]`.
+We also estimated the sample size needed to detect an effect of *Depression* vs.
+a *Control* condition that was meant to not include any signaling (but which we realized, post hoc, did include a verbal request).
+Power was about 80% for a sample size of about `r pwr80_90[[1,2]]`, and was about 90% for a sample size of about `r pwr80_90[[1,3]]`.
+See Figure \@ref(fig:power).
+Given our \$1500 USD budget, we aimed for a sample size of 124 for treatment plus control conditions, and 1240 for all conditions in the study.
+For more details, see the SI.
+
 ## Sampling
@@
 As Amazon provides the infrastructure, it allows for a relatively low-cost way of collecting data for academic research at the cost of the data not being representative of any real population [@thomas2017].
-Despite this limitation, it is more diverse than most convenience samples [@kennedy2020; @DworkinEtAl2016; @thomas2017], with turkers in the US mainly differing in being younger, more educated, and lower income than the greater U.S.
+Despite this limitation, it is more diverse than most convenience samples [@kennedy2020; @DworkinEtAl2016; @thomas2017], with Turkers in the US mainly differing in being younger, more educated, and lower income than the greater U.S.
 population [@RossEtAl2010; @boas2020].
@@
 To test emotional signals in an arranged marriage vignette, we recruited an Indian MTurk sample.
-Indian samples are also likely to be younger and more educated than the general population but differ from US samples in that they are less diverse, have higher incomes relative to other Indians, and are more likely to come from regions with good internet access [@boas2020].
-
-Overall, the quality of data provided by MTurk workers tends to resemble that of university sample pools [@NeckaEtAl2016; @robinson2019], with there being some indication that it might outperform university samples due to its previously mentioned diversity [@thomas2017] or the overall attentiveness of turkers [@HauserSchwarz2016].
+Indian samples are also likely to be younger, more educated, and have higher income than the general Indian population, and are more likely to come from regions with good internet access [@boas2020].
+
+Overall, the quality of data provided by MTurk workers tends to resemble that of university sample pools [@NeckaEtAl2016; @robinson2019; @thomas2017], with some studies reporting that MTurk samples are more attentive than samples of university students [@HauserSchwarz2016].
 In vignette studies, MTurk data quality also compares favorably to that from much more expensive population-based samples [@weinberg2014].
-For these reasons, concerns about data quality come primarily from the threat of bot use or respondents faking their location to take surveys in a language they do not understand well, with there being little evidence of the former [@kennedy2020] and the risk of the latter able to be minimized through well designed attention checks, timed responses, or general study design [@aguinis2020; @huang2015; @kennedy2020; @thomas2017].
+For these reasons, concerns about data quality come primarily from the threat of bot use or respondents faking their location to take surveys in a language they do not understand well, with there being little evidence of the former [@kennedy2020] and the risk of the latter able to be minimized through well designed attention checks, timed responses, and good study design [@aguinis2020; @huang2015; @kennedy2020; @thomas2017].
 
@@
 
-All participants in the US sample were over 18, located in the United States, had a HIT approval rate of over 98%, and had successfully completed at least 100 HITs as anything less results in approval rates of 100% [@kennedy2020].
-The Indian sample was the same except for only including participants who resided in India at the time of the study and the inclusion two participants who were included with a stricter HIT approval rate of over 99%.
-
-To reduce the risk of low quality responses, we used a variety of attention checks, which we clearly labeled as such to avoid demand characteristics on the outcomes of interest.
-The first was shown immediately after the consent form and provided participants with a random word and asked them to enter the vowels in the order in which they are found in the word.
-Capitalization did not matter and no word contained repeat vowels.
-Failure to enter the correct vowels in order resulted in the participants being filtered out of the study.
-The second followed the vignette and involved asking three questions about the story that were easy to answer for anyone paying attention.
-
-We also filtered out those who read the vignette faster than one-third the time it took MG to read it as fast as possible without concern for comprehension.
-This occurred immediately after participants finished the vignette.
+All participants were over 18, located in the United States or India, and had high quality MTurk metrics [completed at least 100 HITs with a HIT approval rate of over 98%; @kennedy2020].
+Participants were excluded from the study if (1) they read the vignette too quickly (one-third of the time it took MG to read it), and (2) they failed clearly labeled attentions checks.
+The first attention check was shown immediately after the consent form and provided participants with a random word and asked them to enter the vowels in the order in which they are found in the word.
+The second attention check followed the vignette and involved asking three questions about the story that were easy to answer for anyone paying attention.
 
@@
 
-The final part of the survey was a brief demographic questionnaire which examined: (1) the age, (2) sex, (3) number of siblings, (4) number of sons, (5) number of daughters, (6) current relationship status, (7) highest level of education, and (8) the annual household income of each participant.
-
-## Preregistration
-
-We preregistered four OLS linear regression models and one mediation model (<https://osf.io/g3s6n>).
-The first two regression models tested the effects of our ordinal signal variable on Time 2 *Belief* and *Action*, controlling for T1 *Belief* and *Action*, respectively (a pre-test/post-test design):
-
-`r extract_eq(models_prereg$Model$m1, intercept='beta', wrap=T)` `r extract_eq(models_prereg$Model$m3, intercept='beta', wrap=T)`
-
-The second two models added interaction terms between signal and T1 *Belief* and *Action*, with the rationale that the signals might have reduced effect for individuals who indicate high levels of belief and helping at baseline:
-
-`r extract_eq(models_prereg$Model$m1b, intercept='beta', wrap=T)` `r extract_eq(models_prereg$Model$m3b, intercept='beta', wrap=T)`
-
-The mediation model is in Figure \@ref(fig:medmodel):
-
-```{r medmodel, fig.cap="Possible causal effects of the signal on helping behavior.
-A credible signal of need increases belief that the victim is telling the truth and needs help, which increase the likelihood of helping.
-The direct path from the signal to action represents other causal effects of the signal on observers, such as perceptions of the victim's emotional state (and other factors not measured in this study) that might alter observer behavior."}
-
-knitr::include_graphics('paths.svg')
-```
-
-Specifically, the mediation and outcome models, respectively, are:
-
-`r extract_eq(med_prereg$model.m, intercept='beta', wrap=T)` `r extract_eq(med_prereg$model.y, intercept='beta', wrap=T)`
-
-For reasons we explain in the *Statistical methods* section, we report the OLS models in the Supplementary Information (SI), and in the Results section instead report conceptually equivalent generalized linear regression models (GLMs).
-
-## Power analysis
-
-```{r}
-pwr80_90 <- 
-  power_curve %>% 
-  group_by(Base) %>% 
-  summarise(
-    pwr80 = min(sample_size[power>=.8]), 
-    pwr90 = min(sample_size[power>=.9])
-  )
-```
-
-We used the pilot data to estimate the sample sizes needed to detect an effect of the *Depression* signal vs.
-*Verbal request* control (two conditions) on *Belief* in the victim's need.
-Power was about 80% for a sample size of about `r pwr80_90[[2,2]]`, and was about 90% for a sample size of about `r pwr80_90[[2,3]]`.
-We also estimated the sample size needed to detect an effect of *Depression* vs.
-a *Control* condition that was meant to not include any signaling (but which we realized, post hoc, did include a verbal request).
-Power was about 80% for a sample size of about `r pwr80_90[[1,2]]`, and was about 90% for a sample size of about `r pwr80_90[[1,3]]`.
-See Figure \@ref(fig:power).
-Given our \$1500 USD budget, we aimed for a sample size of 125 for two conditions, and 1250 for all conditions in the study.
-For more details, see the SI and /.
+The final part of the survey was a brief demographic questionnaire which asked for (1) the age, (2) sex, (3) number of siblings, (4) number of sons, (5) number of daughters, (6) current relationship status, (7) highest level of education, and (8) the annual household income of each participant.
 
@@
 All analyses were conducted using `r R.version.string`.
+
+## Preregistration
+
+We preregistered four OLS linear regression models and one mediation model (<https://osf.io/g3s6n>).
+The first two regression models tested the effects of our ordinal signal variable on Time 2 *Belief* and *Action*, controlling for T1 *Belief* and *Action*, respectively (a pre-test/post-test design):
+
+`r extract_eq(models_prereg$Model$m1, intercept='beta', wrap=T)` `r extract_eq(models_prereg$Model$m3, intercept='beta', wrap=T)`
+
+The second two models added interaction terms between signal and T1 *Belief* and *Action*, with the rationale that the signals might have reduced effect for individuals who indicate high levels of belief and helping at baseline:
+
+`r extract_eq(models_prereg$Model$m1b, intercept='beta', wrap=T)` `r extract_eq(models_prereg$Model$m3b, intercept='beta', wrap=T)`
+
+The mediation model is in Figure \@ref(fig:medmodel):
+
+```{r medmodel, fig.cap="Possible causal effects of the signal on helping behavior.
+A credible signal of need increases belief that the victim is telling the truth and needs help, which increase the likelihood of helping.
+The direct path from the signal to action represents other causal effects of the signal on observers, such as perceptions of the victim's emotional state (and other factors not measured in this study) that might alter observer behavior."}
+
+knitr::include_graphics('paths.svg')
+```
+
+Specifically, the mediation and outcome models, respectively, are:
+
+`r extract_eq(med_prereg$model.m, intercept='beta', wrap=T)` `r extract_eq(med_prereg$model.y, intercept='beta', wrap=T)`
+
+For reasons we explain in the *Statistical methods* section, we report the OLS models in the Supplementary Information (SI), and in the Results section instead report conceptually equivalent generalized linear regression models (GLMs).
 

### 2021-05-06 Paper.rmd
- Fixed table name after we reorganized the methods. - Changed the first sentence in the discussion based on reviewer feedback. - Added a new limitations paragraph

@@
 For this reason, we set each T1 slider to start fully to the left (0).
-For the exact wording of the question and the labels on the sliders, see table 1.
+For the exact wording of the question and the labels on the sliders, see table 2.
 
@@
 
-Consistent with costly signaling theory, costlier signals resulted in greater perceptions of need and increased the likelihood of participants helping the signaler than the less costly signals.
+Consistent with the idea that depression and suicidality are credible signals of need, the two signals resulted in greater perceptions of need and increased the likelihood of participants helping the signaler relative to less costly signals.
 This effect was largest in the "brother-in-law" and "romantic partner" vignettes, both of which involved claims of assault against participants' imagined daughters.
@@
 
-Overall, our results on the connection between belief in need and likelihood of help are consistent with costly signaling and bargaining approaches to depression and suicide.
+Overall, our results on the connection between belief in need and likelihood of help are consistent with credible signaling and bargaining approaches to depression and suicide.
 At T1, *Belief* and *Action* were highly correlated yet distinct; while at T2, the effect of signal on both *Belief* and *Action* was to increase the magnitude of pro-signaler responses, with the effect of signal on *T2Action* being largely mediated by signal's effect on belief in need.
@@
 
-<!-- However, the fact that the relationships among signal cost, belief in need, and likelihood of providing support all largely fit existing theory (narrow and broad) indicates that participants paid attention to the relevant details and responded in ways that suggest some degree of external validity.
-For this reason, the benefits of addressing causal relationships that came through our experimental vignette approach likely outweighed the costs.
--->
-
-Another limitation is that, compared to the US sample, far more Indian participants were filtered out by our attention checks, something which could be consistent with botting, unfamiliarity with English, or low effort responses [@kennedy2020].
+Another limitation is that our control included a signal in the form of a verbal request, preventing comparisons to non-signaling strategies.
+Similarly, our design did not include vignettes with male signalers.
+For this reason, we have no data on the possibility of sex differences in the effectiveness of the signaling strategies examined.
+
+In terms of data quality our largest limitation is that, compared to the US sample, far more Indian participants were filtered out by our attention checks, something which could be consistent with botting, unfamiliarity with English, or low effort responses [@kennedy2020].
 Assuming this corresponded with lower-quality responses among those who passed the attention checks, the weak signal effect in the thwarted marriage vignette may simply be due to added noise rather than differences in the scenario or the effectiveness of the signals compared to those in the US.

### 2021-05-06 Paper.rmd
added parenthetical to show older daughter is the signaler in the thwarted marriage vignette.

@@
 **Thwarted marriage vignette**: Indian sample only.
-Each participant was asked to imagine that their family was trying to arrange a dowry for their older daughter so she can marry a man she already loves, while still saving enough money for their younger daughter's dowry.
+Each participant was asked to imagine that their family was trying to arrange a dowry for their older daughter (the signaler in this vignette) so she can marry a man she already loves, while still saving enough money for their younger daughter's dowry.
 After the man's family demands more money, the participant's family tries to find a second man, who the older daughter claims to find unattractive.

### 2021-05-06 R/functions.R
Trying to generalize power curve functions

@@ -488,14 +488,16 @@ eff_sizes2 <- function(d){
 
 # Power -------------------------------------------------------------------
 
-pwr_curve0 <- function(signalingdata2018, control){
+pwr_curve0 <- function(signalingdata2018, treatment = 'Depression', control = 'Verbal request'){
 
   e <-
     signalingdata2018 %>%
-    dplyr::filter(signal == "Depression" | signal == control) %>%
-    mutate(signal = factor(signal, levels = c(control, "Depression")))
+    dplyr::filter(signal == treatment | signal == control) %>%
+    mutate(signal = factor(signal, levels = c(control, treatment)))
 
   pwr <- function(sample_size){
+    print(paste('sample_size:', sample_size))
+    print(sample(1:nrow(e), sample_size, replace = T))
     pvalues <- map_dbl(1:2000, ~summary(lm(needsmoneyt2 ~ needsmoneyt1 + signal, e[sample(1:nrow(e), sample_size, replace = T),]))$coefficients["signalDepression","Pr(>|t|)"])
     sum(pvalues < 0.05)/length(pvalues)
   }
@@ -508,7 +510,7 @@ pwr_curve0 <- function(signalingdata2018, control){
 }
 
 pwr_curve <- function(d){
-  bind_rows(list('Control' = pwr_curve0(d, 'Control'), 'Verbal' = pwr_curve0(d, 'Verbal request')), .id='Base')
+  bind_rows(list('Control' = pwr_curve0(d, treatment = 'Depression', control = 'Control'), 'Verbal' = pwr_curve0(d, treatment = 'Depression', control = 'Verbal request')), .id='Base')
 }
 
 pwr_curve2 <- function(signalingdata2018){

### 2021-05-06 Paper.rmd
Finished addressing Anne and Darcy comments

--- 2021-05-04 Paper.rmd
@@
 <!-- ## Connection to Adversity -->
+
 Almost all individuals will suffer adversity, such as injury or loss of material or social resources, at some point in their lives.
@@
 Thus, withholding or risking contributions incurs a *cost of delay* -- the more one values the endeavor, the greater the cost of delay.
-In a classic non-cooperative game theory model of bargaining over the division of benefits, @Rubenstein:1982 showed that two parties can come to an immediate agreement over division of benefits despite conflicts of interest if the parties' valuations of cooperation are not private information: in this case, each party knows exactly what division of benefits the other will accept, and can therefore make that offer immediately, avoiding the cost of delay.
+In a classic non-cooperative game theory model of bargaining over the division of benefits, @rubinstein1982 showed that two parties can come to an immediate agreement over division of benefits despite conflicts of interest if the parties' valuations of cooperation are not private information: in this case, each party knows exactly what division of benefits the other will accept, and can therefore make that offer immediately, avoiding the cost of delay.
 If valuations are private information, however, then immediate agreement might not be possible because each party has an incentive to request an amount greater than their actual valuation, which would harm the other party.
 A willingness to delay is a credible signal that one has a low valuation of the endeavor, and is therefore genuinely in need, because for those with a low valuation the benefit of waiting for a better offer outweighs the low cost of delay whereas for those for those with a high valuation the benefit of waiting for a better offer does not outweigh the higher cost of delay.
-Once valuations are known, the game reduces to the one in @Rubenstein:1982, and the parties can reach an agreement on the division of benefits [@KennanWilson1993; @feinberg2005].
+Once valuations are known, the game reduces to the one in @rubinstein1982, and the parties can reach an agreement on the division of benefits [@KennanWilson1993; @feinberg2005].
 @Hagen2003 proposed that the substantial reduction in productivity in depression corresponds to a willingness to delay, and is therefore a credible signal of need.
@@
 Anthropology has long viewed suicidality as largely the result of social problems.
-Early in the field’s history, anthropologists tackled the problem of suicide as manifested in the small, traditional societies in which they conducted their fieldwork.
+Early in the field's history, anthropologists tackled the problem of suicide as manifested in the small, traditional societies in which they conducted their fieldwork.
 Suicide, they found, was commonly a form of protest, revenge, and/or appeal (e.g., Malinowski, 1932; Niehaus, 2012).
@@
 
-```{r cdc, fig.width=8, fig.cap="US Suicide attempt and completion rates by age and sex (2001-2019)."}
+```{r cdc, fig.width=8, fig.cap="US Suicidality non-fatal injury and death rates by age and sex (2001-2019)."}
 library(hrafsuicidedata)
@@
 Common to almost all theoretical and empirical investigations of suicide is a focus on *completed* suicides, i.e., suicide deaths.
-@SymeEtAl2016, in contrast, argued that because the vast majority of suicidal behavior does not result in death, the proper focus should be on suicide ideation and suicide attempts (see Figure \@ref(fig:cdc)).
+@SymeEtAl2016, in contrast, argued that because the vast majority of suicidal behavior does not result in death, the proper focus should be on suicide ideation and suicide attempts (see Figure @ref(fig:cdc)).
 Suicide attempts, as we explain next, are a gamble to improve one's life by taking a low but non-zero risk of death.
@@
 The full vignettes are available in the SI.
-
-Table: (\#tab:design) The cooperative endeavor, conflict of interest, and private information in each vignette
 
@@
 
+: (\#tab:design) The cooperative endeavor, conflict of interest, and private information in each vignette
+
 ### Baseline measures (T1)
 
-After reading the vignettes, participants rated their belief the signaler to be telling the truth (T1Belief: 0-100) and the likelihood of them helping the signaler as requested (T1Action: 0-100).
-With the thwarted marriage vignette we also asked how they would split the money they had saved for the dowry between their daughters (T1Divide: 0-100; 50 is equal split).
+After reading the vignettes, participants rated their belief the signaler to be telling the truth (*T1 Belief*: 0-100) and the likelihood of them helping the signaler as requested (*T1 Action*: 0-100).
+With the thwarted marriage vignette we also asked how they would split the money they had saved for the dowry between their daughters (*T1 Divide*: 0-100; 50 is equal split).
 In every instance, the order of the questions was randomized to avoid order effects [@KrosnickAlwin1987].
@@
 For this reason, we set each T1 slider to start fully to the left (0).
-For the exact wording of the question and the labels on the sliders, see table 1.
+For the exact wording of the question and the labels on the sliders, see Table \@ref(tab:outcomes).
+
++-------------+-------------------+-----------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+
+| Variable    | Vignette          | Wording                                                                                                                     | Coding                                                                                          |
++=============+===================+=============================================================================================================================+=================================================================================================+
+| *T1 Belief* | Basketball        | How much do you believe the star player is telling the truth about the coach?
+| 0: Not at all; 100: Completely                                                                  |
++-------------+-------------------+-----------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+
+| *T1 Belief* | Brother-in-law    | How much do you believe your daughter is telling the truth about your brother-in-law?
+| 0: Not at all; 100: Completely                                                                  |
++-------------+-------------------+-----------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+
+| *T1 Belief* | Romantic partner  | How much do you believe your daughter is telling the truth about your partner?
+| 0: Not at all; 100: Completely                                                                  |
++-------------+-------------------+-----------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+
+| *T1 Belief* | Thwarted Marriage | How much do you believe your older(bold) daughter is telling the truth about the second man not being a good match for her?
+| 0: Not at all; 100: Completely                                                                  |
++-------------+-------------------+-----------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+
+| *T1 Action* | Basketball        | How likely are you to recommend that the president of the university should suspend the coach?
+| 0: Very unlikely; 100: Very likely                                                              |
++-------------+-------------------+-----------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+
+| *T1 Action* | Brother-in-law    | How likely are you to kick your brother-in-law out?
+| 0: Very unlikely; 100: Very likely                                                              |
++-------------+-------------------+-----------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+
+| *T1 Action* | Romantic partner  | How likely are you to kick your partner out?
+| 0: Very unlikely; 100: Very likely                                                              |
++-------------+-------------------+-----------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+
+| *T1 Action* | Thwarted Marriage | How likely are you to provide the large dowry so your older(bold) daughter can marry the man she is in love with?
+| 0: Very unlikely; 100: Very likely                                                              |
++-------------+-------------------+-----------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+
+| *T1 Divide* | Thwarted Marriage | How would you plan on dividing the money between your daughters?
+| 0: Much more for the younger daughter; 50: Even division; 100: Much more for the older daughter |
++-------------+-------------------+-----------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+
+
+: (\#tab:outcomes) Outcome variables in each vignette.
 
@@
 The complete list can be found in the SI.
+To further explore the effect of signaling on participants' inferences of the signaler's emotional state, we created two new variables: *Low mood* was the sum of the binary variables *Depressed*, *Distressed* and *Sad*; and *Manipulative* was the sum of the binary variables *Devious* and *Jealous.*
 
@@
 For the *Belief*, *Action*, and *Divide* variables, the position of the slider starting where participants placed it at T1.
-T2 emotion multiple-choice questions were identical to those used in T1.
-
-As both a validity check and a way to understand the degree participants would be willing to help if they believed the participant completely, we presented participants with strong evidence that the claims were true (T3Action).
+T2 emotion multiple-choice questions were identical to those used in T1, as were the composite variables *Low mood* and *Manipulative*.
+
+As both a validity check and a way to understand the degree participants would be willing to help if they believed the participant completely, we presented participants with strong evidence that the claims were true (*T3 Action*).
 In the US sample, this involved telling participants there was video evidence of the event in question occurring or a similar event after the fact.
@@
 
-+-----------------+-------------------+-----------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+
-| Variable        | Vignette          | Wording                                                                                                                     | Coding                                                                                          |
-+=================+===================+=============================================================================================================================+=================================================================================================+
-| T1Belief        | Basketball        | How much do you believe the star player is telling the truth about the coach?
-| 0: Not at all; 100: Completely                                                                  |
-+-----------------+-------------------+-----------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+
-| T1Belief        | Brother-in-law    | How much do you believe your daughter is telling the truth about your brother-in-law?
-| 0: Not at all; 100: Completely                                                                  |
-+-----------------+-------------------+-----------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+
-| T1Belief        | Romantic partner  | How much do you believe your daughter is telling the truth about your partner?
-| 0: Not at all; 100: Completely                                                                  |
-+-----------------+-------------------+-----------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+
-| T1Belief        | Thwarted Marriage | How much do you believe your older(bold) daughter is telling the truth about the second man not being a good match for her?
-| 0: Not at all; 100: Completely                                                                  |
-+-----------------+-------------------+-----------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+
-| T1Action        | Basketball        | How likely are you to recommend that the president of the university should suspend the coach?
-| 0: Very unlikely; 100: Very likely                                                              |
-+-----------------+-------------------+-----------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+
-| T1Action        | Brother-in-law    | How likely are you to kick your brother-in-law out?
-| 0: Very unlikely; 100: Very likely                                                              |
-+-----------------+-------------------+-----------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+
-| T1Action        | Romantic partner  | How likely are you to kick your partner out?
-| 0: Very unlikely; 100: Very likely                                                              |
-+-----------------+-------------------+-----------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+
-| T1Action        | Thwarted Marriage | How likely are you to provide the large dowry so your older(bold) daughter can marry the man she is in love with?
-| 0: Very unlikely; 100: Very likely                                                              |
-+-----------------+-------------------+-----------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+
-| T1Divide        | Thwarted Marriage | How would you plan on dividing the money between your daughters?
-| 0: Much more for the younger daughter; 50: Even division; 100: Much more for the older daughter |
-+-----------------+-------------------+-----------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+
-
-: (\#tab:outcomes) Outcome variables in each vignette.
-
 ### Demographic Questions
@@
 
-## Statistical analyses
-
+## Statistical analyses: Preregistered and modified
+
+Our intervention was *signal*, an ordinal variable with the following preregistered rank order: verbal request (control), crying, mild depression, depression, suicide attempt.
+We coded this 5-level ordinal factor variable using default 4th-order orthogonal polynomial contrasts.
+We preregistered a test of our hypothesis that used ordinary least squares (OLS) regression models with the following form:
+
+$$
+\begin{aligned}
+\operatorname{Belief}_{T2} &= \beta_{0} + \beta_{1}(\operatorname{Belief}_{T1}) + \beta_{2}(\operatorname{signal}_{\operatorname{.L}}) + \beta_{3}(\operatorname{signal}_{\operatorname{.Q}})\ + \\
+&\quad \beta_{4}(\operatorname{signal}_{\operatorname{.C}}) + \beta_{5}(\operatorname{signal}_{\operatorname{\text{^}4}})
+\end{aligned}
+$$
+
+$$
+\begin{aligned}
+\operatorname{Action}_{T2} &= \beta_{0} + \beta_{1}(\operatorname{Action}_{T1}) + \beta_{2}(\operatorname{signal}_{\operatorname{.L}}) + \beta_{3}(\operatorname{signal}_{\operatorname{.Q}})\ + \\
+&\quad \beta_{4}(\operatorname{signal}_{\operatorname{.C}}) + \beta_{5}(\operatorname{signal}_{\operatorname{\text{^}4}})
+\end{aligned}
+$$
+
+We predicted that there would be a statistically significant monotonically increasing effect of the signal on *Belief* and *Action*.
+
+We decided to use generalized linear regression models instead of OLS, however, for the following reasons.
 Our pre-test and post-test measures, *T1 & T2 Belief* and *T1 & T2 Action*, were all measured on a 0-100 point scale.
@@
 
-Although two of our four preregistered OLS regression models included an interaction term, the rationale for it was less convincing for quasibinomial models using a logit link because the expected interaction -- reduced effect of signals in individuals with high baseline belief -- is inherent to logistic regression: the effect of a predictor on the outcome necessarily diminishes as the outcome approaches 1.
+Two of our four preregistered OLS regression models included interaction terms between signal and T1 *Belief* and *Action*, with the rationale that the signals might have reduced effect for individuals who indicate high levels of belief and helping at baseline.
+This rationale was less convincing for quasibinomial models using a logit link because the expected interaction -- reduced effect of signals in individuals with high baseline belief -- is inherent to logistic regression: the effect of a predictor on the outcome necessarily diminishes as the outcome approaches 1.
 Our theory does not predict an interaction beyond that already present in a logistic regression model, so we did not include an interaction term in the GLM models (but we still report OLS models with the interaction term).
 
-Our intervention was *signal*, an ordinal variable with the following preregistered rank order: verbal request (control), crying, mild depression, depression, suicide attempt.
-We used the default `glm` settings, which code such variables as orthogonal polynomial contrasts.
-Our primary confirmatory regression models were as follows (where the signal subscripts indicate polynomial degree):
-
-`r extract_eq(models$Model$m1, intercept='beta', wrap=T)` `r extract_eq(models$Model$m3, intercept='beta', wrap=T)`
-
-To test our hypothesis that the likelihood of acting to help the victim would be largely mediated by a signal's positive impact on the participant's belief in the victim's need, we used the `mediation` package [@tingley2014] to fit a mediation model for *Depression* treatment vs.
+To test our preregistered hypothesis that the likelihood of acting to help the victim would be largely mediated by a signal's positive impact on the participant's belief in the victim's need, we used the `mediation` package [@tingley2014] to fit a mediation model for *Depression* treatment vs.
 *Verbal request* control.
-The mediation and outcome models, respectively, were:
-
-`r extract_eq(med1$model.m, intercept='beta', wrap=T)` `r extract_eq(med1$model.y, intercept='beta', wrap=T)`
-
-All analyses were conducted using `r R.version.string`.
-
-## Preregistration
-
-We preregistered four OLS linear regression models and one mediation model (<https://osf.io/g3s6n>).
-The first two regression models tested the effects of our ordinal signal variable on Time 2 *Belief* and *Action*, controlling for T1 *Belief* and *Action*, respectively (a pre-test/post-test design):
-
-`r extract_eq(models_prereg$Model$m1, intercept='beta', wrap=T)` `r extract_eq(models_prereg$Model$m3, intercept='beta', wrap=T)`
-
-The second two models added interaction terms between signal and T1 *Belief* and *Action*, with the rationale that the signals might have reduced effect for individuals who indicate high levels of belief and helping at baseline:
-
-`r extract_eq(models_prereg$Model$m1b, intercept='beta', wrap=T)` `r extract_eq(models_prereg$Model$m3b, intercept='beta', wrap=T)`
-
-The mediation model is in Figure \@ref(fig:medmodel):
+See Figure \@ref(fig:medmodel).
 
@@
 
-Specifically, the mediation and outcome models, respectively, are:
-
-`r extract_eq(med_prereg$model.m, intercept='beta', wrap=T)` `r extract_eq(med_prereg$model.y, intercept='beta', wrap=T)`
-
-For reasons we explain in the *Statistical methods* section, we report the OLS models in the Supplementary Information (SI), and in the Results section instead report conceptually equivalent generalized linear regression models (GLMs).
+For specifications of all regression models, see the SI. Our preregistration is here: <https://osf.io/g3s6n>
 
@@
 kable(custom.summarize(d, vars), caption = "Summary statistics for study variables.
-Original 0-100 values scaled to 0-1.
+Values that were on a 0-100 scale were rescaled to 0-1.
 Indian participants reported income in rupees, which we converted to USD at the current exchange rate (1 rupee = 0.014 USD).") %>% kable_styling()
@@
 The distribution of likelihood of helping the victim (action) was similar, Mean = `r signif(mean(d$T1Action, na.rm = T), 2)`, SD = `r signif(sd(d$T1Action, na.rm=T), 2)`, with `r sum(d$T1Action==0)` participants (`r 100*signif(sum(d$T1Action==0)/nrow(d), 2)`%) rating their action = 0, and `r sum(d$T1Action==1)` participants (`r 100*signif(sum(d$T1Action==1)/nrow(d), 2)`%) rated action as = 1.
-Although not a pre-registered prediction, T1 Belief and T1 Action were highly correlated across the four vignettes, consistent with help being worth providing if the signaler's claims were true (see Figure \@ref(fig:t1plot)).
-
-```{r t1plot, fig.width=10, fig.height=10, fig.cap="The distributions of Time 1 Belief vs.
-Time 1 Action, by vignette.
+Although not a pre-registered prediction, *T1 Belief* and *T1 Action* were highly correlated across the four vignettes, consistent with help being worth providing if the signaler's claims were true (see Figure \@ref(fig:t1plot)).
+
+```{r t1plot, fig.width=10, fig.height=10, fig.cap="The distributions of *T1 Belief* vs.*T1 Action*, by vignette.
 Each dot is one participant.
@@
 Dot size indicates the number of overlapping points.
-Black cross is the mean of each variable."}
+Black dot is the mean of each variable."}
 plot_T1Belief_T1Action
@@
 
-As predicted, there was a strong statistically significant positive causal effect of the ordinal signal on T2 Belief and Action (controlling for T1 Belief and Action, respectively), with the effect of each signal increasing in the predicted rank order.
+As predicted, there was a strong statistically significant positive causal effect of the ordinal signal on *T2 Belief* and *T2 Action* (controlling for *T1 Belief* and *T1 Action*, respectively), with the effect of each signal increasing in the predicted rank order (verbal request, crying, mild depression, depression, suicide attempt).
 See Figure \@ref(fig:beliefeffect) and models m1 and m3 in Tables \@ref(tab:regressiontables) and \@ref(tab:anovatables).
@@
 
-```{r beliefeffect, fig.width=6, fig.height=8, fig.cap=paste0("The effect of the signals on T2 Belief (top) and Action (bottom) controlling for T1 values of Belief and Action, respectively.
-Effects plotted for T1 values set to their median value (T1Belief=", median(d$T1Belief, na.rm=T), ", T1Action=", median(d$T1Action, na.rm=T), ").
+```{r beliefeffect, fig.width=6, fig.height=8, fig.cap=paste0("The effect of the signals on *T2 Belief* (top) and *T2 Action* (bottom) controlling for *T1 Belief* and *T1 Action*, respectively.
+Effects plotted for T1 values set to their median value (*T1 Belief*=", median(d$T1Belief, na.rm=T), ", *T1 Action*=", median(d$T1Action, na.rm=T), ").
 Fit using generalized linear regression models with the quasibinomial family.
+Grey bars are 95% CIs.
 For coefficents, p-values, and other statistics, see models m1 and m3 in Tables \\@ref(tab:regressiontables) and \\@ref(tab:anovatables).")}
@@
 
-Within-subjects, the average effect across all signals on *Belief* at T2 compared to T1 was `r inline_ttest(signal_belief_ttest)`, and on *Action* was `r inline_ttest(signal_action_ttest)` (on the original 0-100 point scale).
-For the change in *Belief* and *Action* for, T1 to T2 for all participants in all conditions, see Figure \@ref(fig:rawbeliefactions2d).
+<!-- Within-subjects, the average effect across all signals on *Belief* at T2 compared to T1 was `r inline_ttest(signal_belief_ttest)`, and on *Action* was `r inline_ttest(signal_action_ttest)` (on the original 0-100 point scale).
+For the change in *Belief* and *Action* for, T1 to T2 for all participants in all conditions, see Figure @ref(fig:rawbeliefactions2d).
+-->
+
+The within-subject effects of each signal are depicted in Figure \@ref(fig:rawbeliefactions2d).
 
@@
 The largest between-subjects effect was *Suicide attempt* vs.
-*Verbal request* control on *Belief* in the "Brother-in-law" vignette, d = `r bil_b_suicide`, and the smallest was the effect of *Crying* on *Belief* in the "Romantic partner" vignette, d =`r rom_b_crying`.
+*Verbal request* control on *Belief* in the "Brother-in-law" vignette, Cohen's d = `r bil_b_suicide`, and the smallest was the effect of *Crying* on *Belief* in the "Romantic partner" vignette, Cohen's d =`r rom_b_crying`.
 The largest within-subjects effect was *Suicide attempt* on *Action* at T2 vs.
-T1 in the "Brother-in-law" vignette, d = `r bil_a_suicide`, and the smallest was the *negative* effect of *Verbal request* on *Action* at T2 vs.
-T1 in the "Brother-in-law" vignette, d =`r bil_a_verbal`.
+T1 in the "Brother-in-law" vignette, Cohen's d = `r bil_a_suicide`, and the smallest was the *negative* effect of *Verbal request* on *Action* at T2 vs.
+T1 in the "Brother-in-law" vignette, Cohen's d =`r bil_a_verbal`.
 See Figures \@ref(fig:effectsizes) and \@ref(fig:effectsizes2).
@@
 
-```{r beliefvignette, fig.width=8, fig.height=8, fig.cap=paste0("The effect of the signals on T2 Belief (top) and Action (bottom) in each vignette, controlling for T1 values of Belief and Action, respectively.
+```{r beliefvignette, fig.width=8, fig.height=8, fig.cap=paste0("The effect of the signals on *T2 Belief* (top) and *T2 Action* (bottom) in each vignette, controlling for T1 values of Belief and Action, respectively.
 Ratings rescaled to [0, 1].
-Effects plotted for T1 values set to their median value (T1Belief=", median(d$T1Belief, na.rm=T), ", T1Action=", median(d$T1Action, na.rm=T), ").
+Effects plotted for T1 values set to their median value (*T1 Belief*=", median(d$T1Belief, na.rm=T), ", *T1 Action*=", median(d$T1Action, na.rm=T), ").
 Fit using generalized linear regression models with the quasibinomial family.
+Grey bars are 95% CIs.
 For coefficents, p-values, and other statistics, see models m2 and m4 in Tables \\@ref(tab:regressiontables) and \\@ref(tab:anovatables).")}
@@
 
+We fit the mediation and outcome models using GLM's with the binomial family as the mediation package does not support the quasibinomial family.
 The total effect of the *Suicide attempt* signal (treatment) vs.
@@
 ```{r mediation, fig.width=8, fig.height=4, fig.cap="The effect of each signal (treatment) vs.
-Verbal request (control) on Action, [0, 1] scale, is largely mediated by Belief (percent mediated on the right).
-The mediation model controlled for T1 Belief, and the outcome model controlled for T1 Belief and T1 Action.
+Verbal request (control) on Action.
+The x-axis is the change in Action on the [0, 1] scale.
+The effects of the signals on Action are largely mediated by Belief (percent mediated on the right).
+The mediation model controlled for *T1 Belief*, and the outcome model controlled for *T1 Belief* and *T1 Action*.
 Both models were GLMs with the binomial family (the mediation package does not support the quasibinomial family).
@@
 ADE: Average direct effect.
-Total: Total effect (ADE + ACME)."}
+Total: Total effect (ADE + ACME).
+Bars are 95% CIs."}
 all_mediations$plot
@@
 The proportion of participants inferring each emotion in each vignette at T1 is depicted in Figure \@ref(fig:t1emotionheatmap), after each signal at T2 in Figure \@ref(fig:t2emotionheatmap), and the change in proportions from T1 to T2 in Figure \@ref(fig:diffemotions).
-The increase in inferred depression in the *Depression* and *Suicide attempt* conditions, but not the *Verbal request* and *Crying* conditions, helps validate these manipulations, as does the increase in inferred suicidality in the *Suicide attempt* condition.
-
-To further explore the effect of signaling on participants' inferences of the signaler's emotional state, we created four new variables: *Low mood* (T1 and T2) was the sum of the binary variables *Depressed*, *Distressed* and *Sad*; and *Manipulative* (T1 and T2) was the sum of the binary variables *Devious* and *Jealous.* The mean change in the *Low mood* and *Manipulative* variables from T1 to T2 for each signal in each vignette reveals a large decrease in inferred *Manipulation* for costly signals, and a large increase in inferred *Low mood* (with the exception of the Thwarted marriage vignette, in which changes are small).
-See Figure \@ref(fig:emotionsplot)).
+The increase in inferred depression in the *Depression* and *Suicide attempt* conditions, but not the *Verbal request* and *Crying* conditions, helps validate these signals, as does the increase in inferred suicidality in the *Suicide attempt* condition.
+
+The mean change in the *Low mood* and *Manipulative* variables from T1 to T2 for each signal in each vignette reveals a large decrease in inferred *Manipulation* for costly signals, and a large increase in inferred *Low mood* (with the exception of the Thwarted marriage vignette, in which changes are small).
+See Figure \@ref(fig:emotionsplot).
 
@@
 
-In the US sample, women participants were more likely to believe and help the victim than men, and younger participants were more likely to believe and help the victim than older participants.
+In the US sample, female participants were more likely to believe and help the victim than male participants, and younger participants were more likely to believe and help the victim than older participants.
 We found no significant effects of *Income*, *Education*, relationship status (e.g., married, single), or number of sons or daughters on *Belief* or *Action*.
@@
 
-```{r demographicsignal, fig.width=11, fig.height=8, fig.cap="Sociodemographic effects on *Belief* and *Action*.
-**Top**: Association of T2 Belief with Sex (left) and Age (right) controlling for T1 Belief, vignette, Education, and Income.
-**Bottom**: Association of T2 Action with Sex (left) and Age (right) controlling for T1 Action, vignette, Education, and Income.
-Estimated using generalized linear regression models with the quasibinomial family."}
+```{r demographicsignal, fig.width=11, fig.height=8, fig.cap="Sociodemographic associations with *T2 Belief* (top) and *T2 Action* (bottom) in US participants.
+Each model controlled for *T1 Belief* or *T1 Action*, vignette, Education, and Income.
+Significant associations displayed here.
+Estimated using generalized linear regression models with the quasibinomial family.
+Grey bars are 95% CIs."}
 
@@
 
-In the Indian sample and vignette, in contrast, men were more likely to help the victim than women, those with more years of education were less likely to believe the victim, and there was a marked increase in likelihood of helping among older individuals in the suicide signal condition.
+In the Indian sample and vignette, in contrast, males were more likely to help the victim than females, those with more years of education were less likely to believe the victim, and there was a marked increase in likelihood of helping among older individuals in the suicide signal condition.
 We found no significant associations with age or income.
@@
 
-```{r indiademographics, fig.width=10, fig.height=8, fig.cap="India participants (Thwarted marriage vignette).
-Sociodemographic associations with T2 Belief and Action.
-Each model included T1 Belief or Action, Income, Age, Sex, Years of education, and signal.
-Significant associations displayed here."}
+```{r indiademographics, fig.width=10, fig.height=8, fig.cap="Sociodemographic associations with *T2 Belief* and *T2 Action* in Indian participants (Thwarted marriage vignette).
+Each model included *T1 Belief* or *T1 Action*, Income, Age, Sex, Years of education, and signal.
+Significant associations displayed here.
+Estimated using generalized linear regression models with the quasibinomial family.
+Grey bars are 95% CIs."}
 (effectsPlots_India$m12plot + xlab('Education (years)') + effectsPlots_India$m13plot) / effectsPlots_India$m17plot
@@
 
-As a partial check on the validity of our methods and results, at T3 we presented participants with strong evidence that the victim was telling the truth, and asked them to again rate their likelihood of acting to help the victim (T3Action).
-Compared to the mean T2Action (M=`r signif(mean(d$T2Action, na.rm=T), 2)`), mean T3Action increased substantially, `r inline_ttest(t2t3actionttest)`.
-Across the US vignettes, likelihood of acting at T3 increased to near-ceiling, regardless of participants' T2 Action values (M=`r signif(mean(d$T3Action[d$vignette != 'Thwarted marriage']), 2)`), indicating that propensity to act was indeed contingent on believing the victim.
-In the Indian Thwarted marriage vignette, however, there was little change in T3 Action compared to T2 action (Figure \@ref(fig:t3action)), perhaps because Indian participants' beliefs and actions were relatively insensitive to the signals to begin with (Figures \@ref(fig:beliefvignette) and \@ref(fig:ecdf)).
+As a partial check on the validity of our methods and results, at T3 we presented participants with strong evidence that the victim was telling the truth, and asked them to again rate their likelihood of acting to help the victim (*T3 Action*).
+Compared to the mean *T2 Action* (M=`r signif(mean(d$T2Action, na.rm=T), 2)`), mean *T3 Action* increased substantially, `r inline_ttest(t2t3actionttest)`.
+Across the US vignettes, likelihood of acting at T3 increased to near-ceiling, regardless of participants' *T2 Action* values (M=`r signif(mean(d$T3Action[d$vignette != 'Thwarted marriage']), 2)`), indicating that propensity to act was indeed contingent on believing the victim.
+In the Indian Thwarted marriage vignette, however, there was little change in *T3 Action* compared to *T2 Action* (Figure \@ref(fig:t3action)), perhaps because Indian participants' beliefs and actions were relatively insensitive to the signals to begin with (Figures \@ref(fig:beliefvignette) and \@ref(fig:ecdf)).
 
@@
 
-## The effect of signaling on belief and likelihood of support
-
-Consistent with costly signaling theory, costlier signals resulted in greater perceptions of need and increased the likelihood of participants helping the signaler than the less costly signals.
-This effect was largest in the "brother-in-law" and "romantic partner" vignettes, both of which involved claims of assault against participants' imagined daughters.
-Compared to these scenarios, the effect of signal type was much smaller in both the "basketball coach" and the "thwarted marriage" vignette.
-In the "basketball coach" vignette, part of the reason for this may have been the lack of relatedness between participants and the alleged victim.
-However, this was still a surprising finding due to the relatively small size of the request (i.e., recommend the coach be suspended rather than kick out family members or a romantic partner).
-
-The weak signal effect in the Thwarted marriage condition, which involved the Indian sample, could indicate that our results do not generalize across cultures, undermining our adaptationist hypothesis.
-It could also reflect our poor understanding of contemporary Indian culture regarding dowry.
-The fact that support came at the cost of one's younger daughter may explain the relatively small effect of signal strength.
-However, data from the Indian sample appears to be of lower quality, limiting our confidence in this interpretation (see limitations for more information).
-
-In the "brother-in-law" and "romantic partner" scenarios, *Crying* had little effect on the magnitude of pro-signaler responses relative to *Verbal request*, suggesting it was not costly enough to serve as a reliable signal in times of substantial conflicts of interests.
+As predicted, in vignettes involving conflicts of interest and private information about the need for help, costly signals of need increased participants' belief in the victim and their likelihood of helping her, with the increase in perceived need and likelihood of helping increasing monotonically with signal cost.
+As predicted, the increase in likelihood of helping was largely mediated by the increase in belief in the victim.
+In an exploratory analysis, costlier signals also decreased perceptions that the victim was manipulative.
+
+These effects were largest in the "brother-in-law" and "romantic partner" vignettes, both of which involved claims of assault against participants' imagined daughters, and smaller in the "basketball coach" and the "thwarted marriage" vignettes.
+The small effect in the "basketball coach" vignette, might have been due to the lack of relatedness between participants and the victim (the star player), or how participants weighted the costs of suspending the coach vs.
+punishing a potentially innocent person.
+
+The small signal effect in the "thwarted marriage" vignette, which involved the Indian sample, could indicate that our results do not generalize across cultures, undermining our adaptationist hypothesis.
+It could also reflect our poor understanding of contemporary Indian culture regarding dowry (the effect was larger in older participants).
+Baseline belief in the older daughter, and likelihood of helping her, was relatively high at baseline (greater than 50%) compared to victims in the other vignettes.
+Private information and conflict therefore probably played a smaller role and thus costly signals were less necessary.
+We observed a similar pattern in our pilot study, in which baseline belief in the victim's need was high, and costly signals had smaller effects than they did in the current study.
+Additionally, supporting the older daughter came at the cost of one's younger daughter, which may also help explain the relatively small signal effects.
+A final consideration is that data from the Indian sample appeared to be of lower quality, limiting our confidence in any of these interpretations (see limitations for more information).
+
+In the "brother-in-law" and "romantic partner" scenarios, *Crying* had little effect on the magnitude of pro-victim responses relative to *Verbal request*, suggesting it was not costly enough to serve as a reliable signal in times of substantial conflicts of interests.
 In contrast, both *Depression* conditions increased support, albeit to similar degrees.
-One potential reason for this is the increase in symptoms from mild depression to depression was not costly enough to result in a large effect as the symptoms only differed in severity (e.g., grades dropping from As to Bs [mild depression] or Cs [depression](#depression-3)).
-Such small changes may be less impactful in vignette form than in real-life scenarios in which the effects of signaling may increase in severity and be prolonged over a lengthy period of time.
-
-While the effect of *Suicide attempt* on belief at T2 was similar to the *Depression* conditions across vignettes, it resulted in greater likelihood of support.
-This may be due to our decision to measure belief in need as the degree participants believed the claims of the signaler (e.g., if the assaults actually happened) rather than a more inclusive measure.
-For this reason, signal cost may have provided additional information about the costliness of the signaler's adversity on top of information relevant to whether the event claimed actually happened.
-
-Support for this interpretation comes from our mediation analyses, which showed that the likelihood of help was largely, but not entirely, mediated by signal's effect on belief in need in this study but totally mediated by belief in need when measured as need of financial support in the pilot study when comparing *Depression* to *Verbal request*.
-However, another possibility is that participants viewed the signal as providing information about adversity outside of the signaler's claims.
-For example, participants who saw the "brother-in-law" vignette may have thought the daughter was lying about the assault due to jealously over her cousin, with the stronger signals still conveying the severity of the competition between her and her cousin.
-
-Overall, our results on the connection between belief in need and likelihood of help are consistent with costly signaling and bargaining approaches to depression and suicide.
-At T1, *Belief* and *Action* were highly correlated yet distinct; while at T2, the effect of signal on both *Belief* and *Action* was to increase the magnitude of pro-signaler responses, with the effect of signal on *T2Action* being largely mediated by signal's effect on belief in need.
+One potential reason for this is the increase in symptoms from mild depression to depression was not costly enough to result in a large effect, as the symptoms differed little in severity (e.g., grades dropping from As to Bs in *Mild depression* vs.
+Cs in *Depression*).
+Such small changes may be less impactful in vignettes than in real-life, where the effects of signaling may increase in severity as they persist over a lengthy period of time.
+
+The effect of *Suicide attempt* on belief at T2 was similar to the *Depression* conditions across vignettes, but it resulted in greater likelihood of support.
+One interpretation is that although some participants did not believe the victim's story, her signal nevertheless convinced them that she needed help.
+For example, maybe the brother-in-law did not assault her, but the presence of his family in her home was causing genuine distress.
+Support for this interpretation comes from our mediation analyses, which showed that the likelihood of help was largely, but not entirely, mediated by signal's effect on belief in need.
+
+There were minor associations of age and sex with belief and action in the US participants, with both being higher among females and younger individuals.
+The US vignettes all involved assaults against young women, which might have been more salient to female and younger participants.
+In the Indian sample, high baseline belief and action were somewhat lower among those with more education and among females, respectively.
+Costlier signals, suicidality in particular, had a larger effect among older individuals, perhaps because older individuals were more likely to have children of marriageable age, like the victim in the vignette.
+
+Finally, after the T3 evidence that the victim was telling the truth, likelihood of helping by the US participants increased to near ceiling, an effect that helped validate our vignettes.
+Among Indian participants, in contrast, participants only slightly increased their likelihood of helping from their T2 level.
+One interpretation of the latter is that Indian participants tended to believe the older daughter anyway, so their decision to help was not changed by additional information.
+
+<!-- Overall, our results on the connection between belief in need and likelihood of help are consistent with costly signaling and bargaining approaches to depression and suicide.
+At T1, *Belief* and *Action* were highly correlated yet distinct; while at T2, the effect of signal on both *Belief* and *Action* was to increase the magnitude of pro-signaler responses, with the effect of signal on *T2 Action* being largely mediated by signal's effect on belief in need.
 This relationship between belief in need and likelihood of support and the importance of signal cost should be expected in scenarios when a target of a signal of need would benefit from helping if the signaler's need was genuine but face substantial net costs if it was not.
 Importantly, such scenarios appear to be common among modern humans and have likely been since individuals could increase their inclusive fitness through supporting kin or important cooperative partners who could return to providing benefits to supporters once their situation returned to normal [@SugiyamaSugiyama2003; @tooby1996].
+-->
+
+Our results suggest that the costs of depression and suicidality, which in mainstream theories are taken as evidence of brain dysfunction, might instead function to help victims elicit support from reluctant social partners with whom they are in conflict.
 
@@
 This study was funded through a Washington State University, Vancouver research mini grant.
-
-Who to thank: Lab group? Arpita? Committee? Anne sounds like she will provide a lot of feedback, so her after that?
+We thank Anne Pisor, Darcy Bird, and members of the Hagen lab group for numerous helpful comments.
+We also thank XX and YY [pending permission to acknowledge] for feedback on the Thwarted marriage vignette.
 
@@
 ```{r power, fig.cap="Power curve for between-subjects effect of Depression vs.
-Verbal request signal on T2 Belief, controlling for T1 Belief, and Depression vs.
+Verbal request signal on *T2 Belief*, controlling for *T1 Belief*, and Depression vs.
 a Control condition that was unique to the pilot study."}
@@
 
-```{r power2, fig.cap="Power curve for within-subjects effect of Depression signal on T2 Belief relative to T1 Belief."}
+```{r power2, fig.cap="Power curve for within-subjects effect of Depression signal on *T2 Belief* relative to *T1 Belief*."}
   # ggplot(power_curve2, aes(sample_size, power)) +
@@
 
-Angry Sad Suicidal Mentally ill Depressed Guilty\
-Calm Neutral Scared Tired Distressed Devious Jealous Confident Traumatized Violated None of the above
+* Angry
+* Sad 
+* Suicidal 
+* Mentally ill 
+* Depressed 
+* Guilty
+* Calm
+* Neutral
+* Scared
+* Tired
+* Distressed
+* Devious
+* Jealous
+* Confident
+* Traumatized
+* Violated
+* None of the above
 
@@
 Just now in the market, you saw the man whose family is willing to accept a smaller dowry (the man your daughter does not want to marry). You heard him insult your daughter and your family.
+
+## Preregistered regression models
+
+We preregistered four OLS linear regression models and one mediation model (<https://osf.io/g3s6n>).
+
+The first two OLS regression models tested the effects of our ordinal signal variable on Time 2 *Belief* and *Action*, controlling for T1 *Belief* and *Action*, respectively (a pre-test/post-test design):
+
+`r extract_eq(models_prereg$Model$m1, intercept='beta', wrap=T)` `r extract_eq(models_prereg$Model$m3, intercept='beta', wrap=T)`
+
+We also preregisterd models with an interaction term, for reasons explained in the main text:
+
+`r extract_eq(models_prereg$Model$m1b, intercept='beta', wrap=T)` `r extract_eq(models_prereg$Model$m3b, intercept='beta', wrap=T)`
+
+The `glm` models we report in the main text were:
+
+`r extract_eq(models$Model$m1, intercept='beta', wrap=T)` `r extract_eq(models$Model$m3, intercept='beta', wrap=T)` `r extract_eq(models$Model$m1b, intercept='beta', wrap=T)` `r extract_eq(models$Model$m3b, intercept='beta', wrap=T)`
+
+The preregistered mediation and outcome models, respectively, were:
+
+`r extract_eq(med_prereg$model.m, intercept='beta', wrap=T)` `r extract_eq(med_prereg$model.y, intercept='beta', wrap=T)`
+
+The mediation and outcome models, respectively, that we report in the main text were:
+
+`r extract_eq(med1$model.m, intercept='beta', wrap=T)` `r extract_eq(med1$model.y, intercept='beta', wrap=T)`
 
@@
 
-```{r distbelief, fig.width=10, fig.height=10, fig.cap="Histograms of T2 Belief by signal and vignette."}
+```{r distbelief, fig.width=10, fig.height=10, fig.cap="Histograms of *T2 Belief* by signal and vignette."}
 
@@
 
-```{r effectsizes2, fig.width=10, fig.height=7, fig.cap="Within-subjects Cohen's d (95% CI) for the effect of each signal on T2 Belief and Action in each vignette relative to T1 baseline Belief and Action, respectively, ranked by effect size."}
+```{r effectsizes2, fig.width=10, fig.height=7, fig.cap="Within-subjects Cohen's d (95% CI) for the effect of each signal on *T2 Belief* and *T2 Action* in each vignette relative to baseline *T1 Belief* and *T1 Action*, respectively, ranked by effect size."}
 

### 2021-05-06 R/functions.R

@@ -69,7 +69,7 @@ T1Belief_Action_dist <- function(d){
     # geom_density2d(alpha = 0.5, show.legend = F) +
     geom_count(alpha = 0.5) +
     geom_smooth(se=F, method = 'lm', show.legend = F) +
-    geom_point(data = dmean, aes(T1Belief, T1Action), colour = 'black', shape = 3, size = 3) +
+    geom_point(data = dmean, aes(T1Belief, T1Action), colour = 'black', size = 3) +
     geom_text(data = dcor, aes(label = r), x = .15, y = 0.95, size=5, colour='black') +
     coord_fixed() +
     labs(x = '\nT1 Belief', y = 'T1 Action\n') +

### 2021-05-06 Paper.rmd

@@
 For the exact wording of the question and the labels on the sliders, see Table \@ref(tab:outcomes).
+
+Table: (\#tab:outcomes) Outcome variables in each vignette.
 
@@
 
-: (\#tab:outcomes) Outcome variables in each vignette.
-
 We also asked which emotions participants felt the signaler was experiencing using a multiple choice question in which they could select as many options as they would like.

### 2021-05-06 Paper.rmd
Added limitation and notes

--- 2021-05-06 Paper.rmd
@@
 For this reason, we have no data on the possibility of sex differences in the effectiveness of the signaling strategies examined.
+Although not predicted theoretically, such differences are possible if the costs of signaling vary between the sexes due to differential access to alternative bargaining strategies [@HagenRosenstrom2016] or if one sex suffered greater negative reputational effects due to emotions and behaviors in the vignettes.
+It is also possible the costliness of the situations presented in the vignettes differ by sex.
 
@@
 
+Slider anchor 
+Regex: stopped in SI
+T\d \w+
 # Conclusion

### 2021-05-07 Paper.rmd
Finished modifying power stuff

--- 2021-05-06 Paper.rmd
@@
   power_curve %>% 
-  group_by(Base) %>% 
   summarise(
@@
 
-We used the pilot data to estimate the sample sizes needed to detect an effect of the *Depression* signal vs.
+We used the pilot data to estimate the sample sizes needed to detect an effect of the *Mild depression* signal vs.
 *Verbal request* control on *Belief* in the victim's need.
-Power was about 80% for a sample size of about `r pwr80_90[[2,2]]`, and was about 90% for a sample size of about `r pwr80_90[[2,3]]`.
-We also estimated the sample size needed to detect an effect of *Depression* vs.
-a *Control* condition that was meant to not include any signaling (but which we realized, post hoc, did include a verbal request).
-Power was about 80% for a sample size of about `r pwr80_90[[1,2]]`, and was about 90% for a sample size of about `r pwr80_90[[1,3]]`.
+Power was about 80% for a sample size of about `r pwr80_90[[1, 1]]`, and was about 90% for a sample size of about `r pwr80_90[[1, 2]]`.
 See Figure \@ref(fig:power).
-Given our \$1500 USD budget, we aimed for a sample size of 124 for treatment plus control conditions, and 1240 for all conditions in the study.
+Given our \$1500 USD budget, we aimed for a sample size of 120-130 for treatment plus control conditions, and 1200-1300 for all conditions in the study.
 For more details, see the SI.
@@
 **Thwarted marriage vignette**: Indian sample only.
-Each participant was asked to imagine that their family was trying to arrange a dowry for their older daughter (the signaler in this vignette) so she can marry a man she already loves, while still saving enough money for their younger daughter's dowry.
+Each participant was asked to imagine that their family was trying to arrange a dowry for their older daughter so she can marry a man she already loves, while still saving enough money for their younger daughter's dowry.
 After the man's family demands more money, the participant's family tries to find a second man, who the older daughter claims to find unattractive.
@@
 For this reason, we set each T1 slider to start fully to the left (0).
-For the exact wording of the question and the labels on the sliders, see table 2.
+For the exact wording of the question and the labels on the sliders, see table 1.
 
@@
 
-Consistent with the idea that depression and suicidality are credible signals of need, the two signals resulted in greater perceptions of need and increased the likelihood of participants helping the signaler relative to less costly signals.
+Consistent with costly signaling theory, costlier signals resulted in greater perceptions of need and increased the likelihood of participants helping the signaler than the less costly signals.
 This effect was largest in the "brother-in-law" and "romantic partner" vignettes, both of which involved claims of assault against participants' imagined daughters.
@@
 
-Overall, our results on the connection between belief in need and likelihood of help are consistent with credible signaling and bargaining approaches to depression and suicide.
+Overall, our results on the connection between belief in need and likelihood of help are consistent with costly signaling and bargaining approaches to depression and suicide.
 At T1, *Belief* and *Action* were highly correlated yet distinct; while at T2, the effect of signal on both *Belief* and *Action* was to increase the magnitude of pro-signaler responses, with the effect of signal on *T2Action* being largely mediated by signal's effect on belief in need.
@@
 
-Another limitation is that our control included a signal in the form of a verbal request, preventing comparisons to non-signaling strategies.
-Similarly, our design did not include vignettes with male signalers.
-For this reason, we have no data on the possibility of sex differences in the effectiveness of the signaling strategies examined.
-Although not predicted theoretically, such differences are possible if the costs of signaling vary between the sexes due to differential access to alternative bargaining strategies [@HagenRosenstrom2016] or if one sex suffered greater negative reputational effects due to emotions and behaviors in the vignettes.
-It is also possible the costliness of the situations presented in the vignettes differ by sex.
-
-In terms of data quality our largest limitation is that, compared to the US sample, far more Indian participants were filtered out by our attention checks, something which could be consistent with botting, unfamiliarity with English, or low effort responses [@kennedy2020].
+<!-- However, the fact that the relationships among signal cost, belief in need, and likelihood of providing support all largely fit existing theory (narrow and broad) indicates that participants paid attention to the relevant details and responded in ways that suggest some degree of external validity.
+For this reason, the benefits of addressing causal relationships that came through our experimental vignette approach likely outweighed the costs.
+-->
+
+Another limitation is that, compared to the US sample, far more Indian participants were filtered out by our attention checks, something which could be consistent with botting, unfamiliarity with English, or low effort responses [@kennedy2020].
 Assuming this corresponded with lower-quality responses among those who passed the attention checks, the weak signal effect in the thwarted marriage vignette may simply be due to added noise rather than differences in the scenario or the effectiveness of the signals compared to those in the US.
 
-Slider anchor 
-Regex: stopped in SI
-T\d \w+
 # Conclusion
@@
 
-We estimated power using our pilot study data to compare the effect of the *Depression* signal vs.
+We estimated power using our pilot study data to compare the effect of the *Mild depression* signal vs.
 the *Verbal request* control on *Belief* (that the sister needed the money) at T2 controlling for *Belief* at T1 in a linear regression model.
@@
 Power was computed as the proportion of p-values \< 0.05.
-Power was about 80% for a sample size of about `r pwr80_90[[2,2]]`, and was about 90% for a sample size of about `r pwr80_90[[2,3]]`.
-We then repeated this entire procedure to compare *Depression* to a (flawed) *Control* condition in the pilot study that was meant to not include any signaling (but which we realized, post hoc, did include a verbal request yet differed in substantive ways from the treatment conditions, and therefore was not suitable as a control).
-Power was about 80% for a sample size of about `r pwr80_90[[1,2]]`, and was about 90% for a sample size of about `r pwr80_90[[1,3]]`.
+Power was about 80% for a sample size of about `r pwr80_90[[1,1]]`, and was about 90% for a sample size of about `r pwr80_90[[1,2]]`.
 See Figure \@ref(fig:power).
 
-```{r power, fig.cap="Power curve for between-subjects effect of Depression vs.
-Verbal request signal on T2 Belief, controlling for T1 Belief, and Depression vs.
-a Control condition that was unique to the pilot study."}
-  ggplot(power_curve, aes(sample_size, power, color=Base)) +
+```{r power, fig.cap="Power curve for between-subjects effect of Mild depression vs. Verbal request signal on T2 Belief, controlling for T1 Belief."}
+  ggplot(power_curve, aes(sample_size, power)) +
     geom_line() +
     labs(x = '\n Sample size', y = 'Power\n') +
-    theme_minimal(15)
+    theme_minimal(15) + theme(axis.title.y = element_text(angle = 0))
 ```

### 2021-05-07 R/functions.R

@@ -488,17 +488,16 @@ eff_sizes2 <- function(d){
 
 # Power -------------------------------------------------------------------
 
-pwr_curve0 <- function(signalingdata2018, treatment = 'Depression', control = 'Verbal request'){
+pwr_curve <- function(d, treatment, control, n = 2000){
 
   e <-
-    signalingdata2018 %>%
+    d %>%
     dplyr::filter(signal == treatment | signal == control) %>%
     mutate(signal = factor(signal, levels = c(control, treatment)))
 
+  coefname <- paste0('signal', treatment)
   pwr <- function(sample_size){
-    print(paste('sample_size:', sample_size))
-    print(sample(1:nrow(e), sample_size, replace = T))
-    pvalues <- map_dbl(1:2000, ~summary(lm(needsmoneyt2 ~ needsmoneyt1 + signal, e[sample(1:nrow(e), sample_size, replace = T),]))$coefficients["signalDepression","Pr(>|t|)"])
+    pvalues <- map_dbl(1:n, ~summary(lm(needsmoneyt2 ~ needsmoneyt1 + signal, e[sample(1:nrow(e), sample_size, replace = T),]))$coefficients[coefname, "Pr(>|t|)"])
     sum(pvalues < 0.05)/length(pvalues)
   }
 
@@ -509,9 +508,9 @@ pwr_curve0 <- function(signalingdata2018, treatment = 'Depression', control = 'V
     )
 }
 
-pwr_curve <- function(d){
-  bind_rows(list('Control' = pwr_curve0(d, treatment = 'Depression', control = 'Control'), 'Verbal' = pwr_curve0(d, treatment = 'Depression', control = 'Verbal request')), .id='Base')
-}
+# pwr_curve <- function(d){
+#   bind_rows(list('Control' = pwr_curve0(d, treatment = 'Depression', control = 'Control'), 'Verbal' = pwr_curve0(d, treatment = 'Depression', control = 'Verbal request')), .id='Base')
+# }
 
 pwr_curve2 <- function(signalingdata2018){
   e <- signalingdata2018 %>% dplyr::filter(signal == "Depression")

### 2021-05-07 _targets.R

@@ -90,7 +90,7 @@ list(
 
   tar_target(
     power_curve,
-    pwr_curve(signalingdata2018b)
+    pwr_curve(signalingdata2018b, treatment = 'Mild depression', control = 'Verbal request')
   ),
 
 # Pilot results -----------------------------------------------------------

### 2021-05-07 Paper.rmd
Minor edits to discussion and conclusion to prepare for submission for class.
Finished fixing address how we label the belief and action variables

--- 2021-05-06 Paper.rmd
@@
 
-Although this study was not designed to examine whether the costs of signaling would be made up for by the increased support stemming from depression and suicide attempts directly, the results are consistent with this hypothesis.
+<!-- Although this study was not designed to examine whether the costs of signaling would be made up for by the increased support stemming from depression and suicide attempts directly, the results are consistent with this hypothesis.
 In general, the costs required to honestly convey one's qualities should be expected to increase with the potential payoffs of deception and the number of defectors within the broader population [@Rosenthal1993], with the vignettes in this study emphasizing the existence of private information and sizable conflicts of interest to increase the perceived risk of being taken advantage of.
@@
 These benefits coupled with the fact that depression and suicide attempts become relatively less costly to one's fitness prospects with increased need [@Hagen2003], suggest that the increased support seen in this study may be worth the costs required to signal need more often than is often appreciated when counting the entire costs of depression as the signal rather than only the upregulation of symptoms for a communicative purpose.
+-->
 
@@
 For this reason, we have no data on the possibility of sex differences in the effectiveness of the signaling strategies examined.
-Although not predicted theoretically, such differences are possible if the costs of signaling vary between the sexes due to differential access to alternative bargaining strategies [@HagenRosenstrom2016] or if one sex suffered greater negative reputational effects due to emotions and behaviors in the vignettes.
+Although not predicted theoretically, such differences are possible if the costs of signaling vary between the sexes due to differential access to alternative bargaining strategies [@HagenRosenstrom2016] or if one sex tends to suffer greater negative reputational effects  when displaying the emotions and behaviors in the vignettes.
 It is also possible the costliness of the situations presented in the vignettes differ by sex.
@@
 
-Slider anchor 
-Regex: stopped in SI
-T\d \w+
+<!-- Slider anchor  -->
+<!-- Regex: stopped in SI -->
+<!-- T\d \w+ -->
 # Conclusion
 
-The need to explain suicide's connection to depression is often overlooked by explanations for major depression, particularly those which propose non-signaling functions.
+Our results suggest that the costs of depression and suicidality, which in mainstream theories are taken as evidence of brain dysfunction [@SymeHagen2021], might instead function to help victims elicit support from reluctant social partners with whom they are in conflict.
+This coupled with findings that depression can simultaneously elicit both positive and negative responses [@HokansonEtAl1986; @stephens1987], suggests that more attention should be paid to the potential for positive responses towards depressed individuals, especially from individuals who normally receive substantial benefits from the depressed or suicidal individual.
+
+ <!-- The need to explain suicide's connection to depression is often overlooked by explanations for major depression, particularly those which propose non-signaling functions.
 One explanation for their connection, is that both suicidality and depression may function to limit negative fitness outcomes in times of substantial adversity [@andrews2006; @Hagen2002; @Hagen2003; @HagenEtAl2008; @nock2008; @Rosenthal1993; @Stengel1956; @SymeEtAl2016], with costlier signals being required to elicit support when the payoffs to faking need are high enough so that less costly signals are not reliable indicators of one's need [@Rosenthal1993].
@@
 In support of this, we found exposure to depression and suicide attempts resulted in greater belief in need and increased likelihood of support in fictional scenarios.
-This coupled with findings that depression can simultaneously elicit both positive and negative responses [@HokansonEtAl1986; @stephens1987], suggests that more attention should be paid to the potential for positive responses towards depressed individuals, especially from individuals who normally receive substantial benefits from the depressed or suicidal individual.
+-->
 
@@
 
-```{r distaction, fig.width=10, fig.height=10, fig.cap="Histograms of T2 Action by signal and vignette."}
+```{r distaction, fig.width=10, fig.height=10, fig.cap="Histograms of *T2 Action* by signal and vignette."}
 
@@
 ```{r demoeffectsaction, fig.width=9, fig.height=8, fig.cap="Demographic effects on Action.
-**Top**: Association of age with T2 Action, controlling for T1 Action, sex, and vignette.
-**Bottom**: Association of sex with T2 Action controlling for T1 Action, age, and vignette.
+**Top**: Association of age with *T2 Action*, controlling for *T1 Action*, sex, and vignette.
+**Bottom**: Association of sex with *T2 Action* controlling for *T1 Action*, age, and vignette.
 Estimated using a generalized linear regression model with the quasibinomial family."}
@@
 
-```{r demovignettebelief, fig.width=8, fig.height=8, fig.cap="Associations of age (top) and sex (bottom) with T2 Belief by vignette, controlling for T1 Belief and signal.
+```{r demovignettebelief, fig.width=8, fig.height=8, fig.cap="Associations of age (top) and sex (bottom) with *T2 Belief* by vignette, controlling for *T1 Belief* and signal.
 Estimated using a generalized linear regression model with the quasibinomial family."}
@@
 
-```{r demovignetteaction, fig.width=8, fig.height=8, fig.cap="Associations of age (top) and sex (bottom) with T2 Action by vignette, controlling for T1 Action and signal.
+```{r demovignetteaction, fig.width=8, fig.height=8, fig.cap="Associations of age (top) and sex (bottom) with *T2 Action* by vignette, controlling for *T1 Action* and signal.
 Estimated using a generalized linear regression model with the quasibinomial family."}
@@
 ADE: Average direct effect.
-The mediation model controlled for T1 Belief, and the outcome model controlled for T1 Belief and T1 Action.
+The mediation model controlled for *T1 Belief*, and the outcome model controlled for *T1 Belief* and *T1 Action*.
 Both models were GLMs with the binomial family (the mediation package does not support the quasibinomial family)."}
@@
 
-```{r divisionage, fig.width=9, fig.cap="Interaction of age with signals on T2 Division of dowry between the daughters in the thwarted marriage vignette."}
+```{r divisionage, fig.width=9, fig.cap="Interaction of age with signals on *T2 Division* of dowry between the daughters in the thwarted marriage vignette."}
 effectsPlots_India$m8plot
@@
 
-```{r t3action, fig.width=10, fig.cap="The effect of post-signal (T3) information that the victim was telling the truth on the likelihood of acting to help her (T3 Action), controlling for T2 Action, with a term for the interaction of T2 Action and vignette."}
+```{r t3action, fig.width=10, fig.cap="The effect of post-signal (T3) information that the victim was telling the truth on the likelihood of acting to help her (*T3 Action*), controlling for *T2 Action*, with a term for the interaction of *T2 Action* and vignette."}
 effectsPlots$m26plot + theme(panel.spacing = unit(1.5, "lines"))
@@
 
-```{r preregbelief, fig.width=8, fig.height=8, fig.cap="The effect of the signals on T2 Belief (top) and Action (bottom) controlling for T1 values of Belief and Action, respectively.
+```{r preregbelief, fig.width=8, fig.height=8, fig.cap="The effect of the signals on *T2 Belief* (top) and Action (bottom) controlling for T1 values of Belief and Action, respectively.
 Estimated using OLS linear regression models (gaussian)."}
@@
 
-```{r preregbeliefB, fig.width=8, fig.height=8, fig.cap="The effect of the signals on T2 Belief (top) and Action (bottom) controlling for T1 values of Belief and Action, respectively, with an interaction between T1 values and the signal.
+```{r preregbeliefB, fig.width=8, fig.height=8, fig.cap="The effect of the signals on *T2 Belief* (top) and Action (bottom) controlling for T1 values of Belief and Action, respectively, with an interaction between T1 values and the signal.
 Estimated using OLS linear regression models (gaussian)."}
@@
 
-```{r modelcompareplots, fig.width=11, fig.cap="Comparison of the coefficients and 95% CIs of the quasibinomial glm, fractional, and bootstrapped logistic regression models of T2 Belief and Action (for details, see the Statistical methods section)."}
+```{r modelcompareplots, fig.width=11, fig.cap="Comparison of the coefficients and 95% CIs of the quasibinomial glm, fractional, and bootstrapped logistic regression models of *T2 Belief* and *T2 Action* (for details, see the Statistical methods section)."}
 

### 2021-05-07 Paper.rmd
Edited pilot study description and added discussion of possible anchor effects to the limitations.

@@
 We also estimated the sample size needed to detect an effect of *Depression* vs.
-a *Control* condition that was meant to not include any signaling (but which we realized, post hoc, did include a verbal request).
+a *Control* condition in which there was only a verbal request made in the body of the vignette, with no signal given during a second encounter (when signaling was manipulated).
 Power was about 80% for a sample size of about `r pwr80_90[[1,2]]`, and was about 90% for a sample size of about `r pwr80_90[[1,3]]`.
@@
 Assuming this corresponded with lower-quality responses among those who passed the attention checks, the weak signal effect in the thwarted marriage vignette may simply be due to added noise rather than differences in the scenario or the effectiveness of the signals compared to those in the US.
+Another concern relevant to all vignettes is that our decision to anchor the T1 sliders at 0 may have resulted in participants being more likely to report extreme values.
 

### 2021-05-07 Paper.rmd
Added discussion of problems with pilot study control condition

--- 2021-05-07 Paper.rmd
@@
 
-<!-- Although this study was not designed to examine whether the costs of signaling would be made up for by the increased support stemming from depression and suicide attempts directly, the results are consistent with this hypothesis.
+Although this study was not designed to examine whether the costs of signaling would be made up for by the increased support stemming from depression and suicide attempts directly, the results are consistent with this hypothesis.
 In general, the costs required to honestly convey one's qualities should be expected to increase with the potential payoffs of deception and the number of defectors within the broader population [@Rosenthal1993], with the vignettes in this study emphasizing the existence of private information and sizable conflicts of interest to increase the perceived risk of being taken advantage of.
@@
 These benefits coupled with the fact that depression and suicide attempts become relatively less costly to one's fitness prospects with increased need [@Hagen2003], suggest that the increased support seen in this study may be worth the costs required to signal need more often than is often appreciated when counting the entire costs of depression as the signal rather than only the upregulation of symptoms for a communicative purpose.
--->
 
@@
 For this reason, we have no data on the possibility of sex differences in the effectiveness of the signaling strategies examined.
-Although not predicted theoretically, such differences are possible if the costs of signaling vary between the sexes due to differential access to alternative bargaining strategies [@HagenRosenstrom2016] or if one sex tends to suffer greater negative reputational effects  when displaying the emotions and behaviors in the vignettes.
+Although not predicted theoretically, such differences are possible if the costs of signaling vary between the sexes due to differential access to alternative bargaining strategies [@HagenRosenstrom2016] or if one sex suffered greater negative reputational effects due to emotions and behaviors in the vignettes.
 It is also possible the costliness of the situations presented in the vignettes differ by sex.
@@
 
-<!-- Slider anchor  -->
-<!-- Regex: stopped in SI -->
-<!-- T\d \w+ -->
+Slider anchor 
+Regex: stopped in SI
+T\d \w+
 # Conclusion
 
-Our results suggest that the costs of depression and suicidality, which in mainstream theories are taken as evidence of brain dysfunction [@SymeHagen2021], might instead function to help victims elicit support from reluctant social partners with whom they are in conflict.
-This coupled with findings that depression can simultaneously elicit both positive and negative responses [@HokansonEtAl1986; @stephens1987], suggests that more attention should be paid to the potential for positive responses towards depressed individuals, especially from individuals who normally receive substantial benefits from the depressed or suicidal individual.
-
- <!-- The need to explain suicide's connection to depression is often overlooked by explanations for major depression, particularly those which propose non-signaling functions.
+The need to explain suicide's connection to depression is often overlooked by explanations for major depression, particularly those which propose non-signaling functions.
 One explanation for their connection, is that both suicidality and depression may function to limit negative fitness outcomes in times of substantial adversity [@andrews2006; @Hagen2002; @Hagen2003; @HagenEtAl2008; @nock2008; @Rosenthal1993; @Stengel1956; @SymeEtAl2016], with costlier signals being required to elicit support when the payoffs to faking need are high enough so that less costly signals are not reliable indicators of one's need [@Rosenthal1993].
@@
 In support of this, we found exposure to depression and suicide attempts resulted in greater belief in need and increased likelihood of support in fictional scenarios.
--->
+This coupled with findings that depression can simultaneously elicit both positive and negative responses [@HokansonEtAl1986; @stephens1987], suggests that more attention should be paid to the potential for positive responses towards depressed individuals, especially from individuals who normally receive substantial benefits from the depressed or suicidal individual.
 
@@
 
-Briefly, Participants read a vignette that put them in situations in which an imagined sister was requesting a loan of \$50,000 from the participant that was originally saved for the participant's imagined daughter's college education.
+Briefly, participants read a vignette that put them in situations in which an imagined sister was requesting a loan of \$50,000 from the participant that was originally saved for the participant's imagined daughter's college education.
 The sister claims the money is needed for medical treatment for her own child, but she has incentives to deceive.
@@
 
-We learned five major lessons from the MTurk pilot study that influenced the design of the current study.
+We learned six major lessons from the MTurk pilot study that influenced the design of the current study.
 First, as predicted, belief in the sister's need was highest in the *Depression* condition and lowest in the *Verbal request* condition, giving us confidence to continue this research (see Figure \@ref(fig:piloteffects)).
@@
 Fifth, the content of the vignette matters, so instead of a single vignette we decided to use four different vignettes to help determine the extent to which signaling effects were sensitive to seemingly irrelevant details of the vignettes.
+Sixth, in a randomized controlled trial, the control condition should be identical to the treatment condition in every respect except for the factor being tested, which in this study was signal cost.
+Post hoc, we realized that the control condition in the pilot study differed substantially from the treatment condition beyond signal cost: in the treatment conditions, participants encountered the sister twice: once when she requests help, and a second time when she signals.
+In our faulty control, participants only encountered the sister once, when she requests help, with no second encounter.
+In this study we therefore ensured that the control condition (Verbal request) was identical to the treatment conditions except for signal cost.
 
@@
 
-```{r distaction, fig.width=10, fig.height=10, fig.cap="Histograms of *T2 Action* by signal and vignette."}
+```{r distaction, fig.width=10, fig.height=10, fig.cap="Histograms of T2 Action by signal and vignette."}
 
@@
 ```{r demoeffectsaction, fig.width=9, fig.height=8, fig.cap="Demographic effects on Action.
-**Top**: Association of age with *T2 Action*, controlling for *T1 Action*, sex, and vignette.
-**Bottom**: Association of sex with *T2 Action* controlling for *T1 Action*, age, and vignette.
+**Top**: Association of age with T2 Action, controlling for T1 Action, sex, and vignette.
+**Bottom**: Association of sex with T2 Action controlling for T1 Action, age, and vignette.
 Estimated using a generalized linear regression model with the quasibinomial family."}
@@
 
-```{r demovignettebelief, fig.width=8, fig.height=8, fig.cap="Associations of age (top) and sex (bottom) with *T2 Belief* by vignette, controlling for *T1 Belief* and signal.
+```{r demovignettebelief, fig.width=8, fig.height=8, fig.cap="Associations of age (top) and sex (bottom) with T2 Belief by vignette, controlling for T1 Belief and signal.
 Estimated using a generalized linear regression model with the quasibinomial family."}
@@
 
-```{r demovignetteaction, fig.width=8, fig.height=8, fig.cap="Associations of age (top) and sex (bottom) with *T2 Action* by vignette, controlling for *T1 Action* and signal.
+```{r demovignetteaction, fig.width=8, fig.height=8, fig.cap="Associations of age (top) and sex (bottom) with T2 Action by vignette, controlling for T1 Action and signal.
 Estimated using a generalized linear regression model with the quasibinomial family."}
@@
 ADE: Average direct effect.
-The mediation model controlled for *T1 Belief*, and the outcome model controlled for *T1 Belief* and *T1 Action*.
+The mediation model controlled for T1 Belief, and the outcome model controlled for T1 Belief and T1 Action.
 Both models were GLMs with the binomial family (the mediation package does not support the quasibinomial family)."}
@@
 
-```{r divisionage, fig.width=9, fig.cap="Interaction of age with signals on *T2 Division* of dowry between the daughters in the thwarted marriage vignette."}
+```{r divisionage, fig.width=9, fig.cap="Interaction of age with signals on T2 Division of dowry between the daughters in the thwarted marriage vignette."}
 effectsPlots_India$m8plot
@@
 
-```{r t3action, fig.width=10, fig.cap="The effect of post-signal (T3) information that the victim was telling the truth on the likelihood of acting to help her (*T3 Action*), controlling for *T2 Action*, with a term for the interaction of *T2 Action* and vignette."}
+```{r t3action, fig.width=10, fig.cap="The effect of post-signal (T3) information that the victim was telling the truth on the likelihood of acting to help her (T3 Action), controlling for T2 Action, with a term for the interaction of T2 Action and vignette."}
 effectsPlots$m26plot + theme(panel.spacing = unit(1.5, "lines"))
@@
 
-```{r preregbelief, fig.width=8, fig.height=8, fig.cap="The effect of the signals on *T2 Belief* (top) and Action (bottom) controlling for T1 values of Belief and Action, respectively.
+```{r preregbelief, fig.width=8, fig.height=8, fig.cap="The effect of the signals on T2 Belief (top) and Action (bottom) controlling for T1 values of Belief and Action, respectively.
 Estimated using OLS linear regression models (gaussian)."}
@@
 
-```{r preregbeliefB, fig.width=8, fig.height=8, fig.cap="The effect of the signals on *T2 Belief* (top) and Action (bottom) controlling for T1 values of Belief and Action, respectively, with an interaction between T1 values and the signal.
+```{r preregbeliefB, fig.width=8, fig.height=8, fig.cap="The effect of the signals on T2 Belief (top) and Action (bottom) controlling for T1 values of Belief and Action, respectively, with an interaction between T1 values and the signal.
 Estimated using OLS linear regression models (gaussian)."}
@@
 
-```{r modelcompareplots, fig.width=11, fig.cap="Comparison of the coefficients and 95% CIs of the quasibinomial glm, fractional, and bootstrapped logistic regression models of *T2 Belief* and *T2 Action* (for details, see the Statistical methods section)."}
+```{r modelcompareplots, fig.width=11, fig.cap="Comparison of the coefficients and 95% CIs of the quasibinomial glm, fractional, and bootstrapped logistic regression models of T2 Belief and Action (for details, see the Statistical methods section)."}
 

### 2021-05-07 Paper.rmd

@@
 
-We used the pilot data to estimate the sample sizes needed to detect an effect of the *Depression* signal vs.
+We used the pilot data to estimate the sample sizes needed to detect an effect of the *Mild depression* signal vs.
 *Verbal request* control on *Belief* in the victim's need.
-Power was about 80% for a sample size of about `r pwr80_90[[2,2]]`, and was about 90% for a sample size of about `r pwr80_90[[2,3]]`.
-We also estimated the sample size needed to detect an effect of *Depression* vs.
-a *Control* condition in which there was only a verbal request made in the body of the vignette, with no signal given during a second encounter (when signaling was manipulated).
-Power was about 80% for a sample size of about `r pwr80_90[[1,2]]`, and was about 90% for a sample size of about `r pwr80_90[[1,3]]`.
+Power was about 80% for a sample size of about `r pwr80_90[[1, 1]]`, and was about 90% for a sample size of about `r pwr80_90[[1, 2]]`.
 See Figure \@ref(fig:power).
-Given our \$1500 USD budget, we aimed for a sample size of 124 for treatment plus control conditions, and 1240 for all conditions in the study.
+Given our \$1500 USD budget, we aimed for a sample size of 120-130 for treatment plus control conditions, and 1200-1300 for all conditions in the study.
 For more details, see the SI.
@@
 Power was computed as the proportion of p-values \< 0.05.
-Power was about 80% for a sample size of about `r pwr80_90[[2,2]]`, and was about 90% for a sample size of about `r pwr80_90[[2,3]]`.
-We then repeated this entire procedure to compare *Depression* to a (flawed) *Control* condition in the pilot study that was meant to not include any signaling (but which we realized, post hoc, did include a verbal request yet differed in substantive ways from the treatment conditions, and therefore was not suitable as a control).
-Power was about 80% for a sample size of about `r pwr80_90[[1,2]]`, and was about 90% for a sample size of about `r pwr80_90[[1,3]]`.
+Power was about 80% for a sample size of about `r pwr80_90[[1,1]]`, and was about 90% for a sample size of about `r pwr80_90[[1,2]]`.
 See Figure \@ref(fig:power).
 
-```{r power, fig.cap="Power curve for between-subjects effect of Depression vs.
-Verbal request signal on *T2 Belief*, controlling for *T1 Belief*, and Depression vs.
-a Control condition that was unique to the pilot study."}
-  ggplot(power_curve, aes(sample_size, power, color=Base)) +
+```{r power, fig.cap="Power curve for between-subjects effect of Mild depression vs. Verbal request signal on T2 Belief, controlling for T1 Belief."}
+ggplot(power_curve, aes(sample_size, power)) +
   geom_line() +
   labs(x = '\n Sample size', y = 'Power\n') +
-    theme_minimal(15)
+  theme_minimal(15) + theme(axis.title.y = element_text(angle = 0))
 ```

### 2021-05-07 Paper.rmd
Clarified that verbal request was a signal per reviewer comments

--- 2021-05-07 Paper.rmd
@@
 
-This study utilized a between-subjects pretest-posttest design to examine how four different emotional signals (treatments) would influence (1) the degree participants believed a fictional character to be in need (*Belief*) and (2) the likelihood they would provide help (*Action*) relative to a simple *Verbal request* (the control condition), in four different vignettes, for a total of 20 conditions.
+This study utilized a between-subjects pretest-posttest design to examine how four different emotional signals (treatments) would influence (1) the degree participants believed a fictional character to be in need (*Belief*) and (2) the likelihood they would provide help (*Action*) relative to a simple *Verbal request* without additional signaling (the control condition), in four different vignettes, for a total of 20 conditions.
 In this design, the outcomes are measured at pre-treatment (T1).
@@
 
-Briefly, participants read a vignette that put them in situations in which an imagined sister was requesting a loan of \$50,000 from the participant that was originally saved for the participant's imagined daughter's college education.
+Briefly, Participants read a vignette that put them in situations in which an imagined sister was requesting a loan of \$50,000 from the participant that was originally saved for the participant's imagined daughter's college education.
 The sister claims the money is needed for medical treatment for her own child, but she has incentives to deceive.
@@
 
-We learned six major lessons from the MTurk pilot study that influenced the design of the current study.
+We learned five major lessons from the MTurk pilot study that influenced the design of the current study.
 First, as predicted, belief in the sister's need was highest in the *Depression* condition and lowest in the *Verbal request* condition, giving us confidence to continue this research (see Figure \@ref(fig:piloteffects)).
@@
 Fifth, the content of the vignette matters, so instead of a single vignette we decided to use four different vignettes to help determine the extent to which signaling effects were sensitive to seemingly irrelevant details of the vignettes.
-Sixth, in a randomized controlled trial, the control condition should be identical to the treatment condition in every respect except for the factor being tested, which in this study was signal cost.
-Post hoc, we realized that the control condition in the pilot study differed substantially from the treatment condition beyond signal cost: in the treatment conditions, participants encountered the sister twice: once when she requests help, and a second time when she signals.
-In our faulty control, participants only encountered the sister once, when she requests help, with no second encounter.
-In this study we therefore ensured that the control condition (Verbal request) was identical to the treatment conditions except for signal cost.
 

### 2021-05-07 Paper.rmd
Commented out some lines

@@
 
-<!-- ## Connection to Adversity -->
-
 Almost all individuals will suffer adversity, such as injury or loss of material or social resources, at some point in their lives.
@@
 
-Our results suggest that the costs of depression and suicidality, which in mainstream theories are taken as evidence of brain dysfunction, might instead function to help victims elicit support from reluctant social partners with whom they are in conflict.
+<!-- Our results suggest that the costs of depression and suicidality, which in mainstream theories are taken as evidence of brain dysfunction, might instead function to help victims elicit support from reluctant social partners with whom they are in conflict.
+-->
 

### 2021-05-10 Paper.rmd
Added robust CIs, and a few edits here and there.

@@
 In the Rosenthal model, as long as that risk is greater than or equal to the net benefit a non-needy person would realize by sending the signal (discounted by the risk of death), social partners can trust that signal senders are genuinely in need despite conflicts of interest [@Rosenthal1993].
-Most suicides deaths, especially in young, physically healthy individuals, would therefore be the inevitable consequence that some individuals lose this gamble.
+In the bargaining framework, suicidality could be conceptualized as putting future fitness benefits at risk -- riskier attempts would credibly indicate lower valuation of the future.
+On these views, most suicides deaths, especially in young, physically healthy individuals, would therefore be the inevitable consequence that some individuals lose this gamble.
 These and similar ideas [@andrews2006; @HagenEtAl2008; @nock2008; @Stengel1956] suggest that depression symptoms that put one's value to others at risk, such as suicidality and loss of interest, might be credible signals of need.
@@
 The primary aim of this study was to examine responses to various forms of emotional signaling in an experimental vignette study.
+In the bargaining framework, the willingness to delay credibly signals the valuation of current cooperative arrangements, with greater delays indicating lower valuations.
 As signal cost increases, and signals therefore become less profitable to fake, we predicted that participants would report (1) increased belief in the signaler's claims and (2) increased likelihood of providing help, with (3) the increased likelihood of providing help mediated by the increased belief in the signaler's need.
@@
 
-We therefore fit models of our two outcome variables (which we rescaled to the continuous interval [0, 1]) in four ways.
+We therefore fit models of our two outcome variables (which we rescaled to the continuous interval [0, 1]) in five ways.
 First, we fit the preregistered OLS models (reported in the SI).
@@
 Third, we fit GLM logistic regression models, computing 95% CI's via bootstrapping, using the `glmmboot` package created to model continuous outcomes on [0, 1] [@humphrey2020].
-Finally, we fit GLM models with the quasibinomial family and logit link using the `glm` function in R stats library, which can fit continuous outcomes on [0, 1].
-The estimated coefficients, standard errors, and confidence intervals produced by the latter three methods were *very* similar, and often identical (see Figure \@ref(fig:modelcompareplots).
+Fourth, we fit GLM models with the quasibinomial family and logit link using the `glm` function in R stats library, which can fit continuous outcomes on [0, 1].
+Finally, we fit the quasibinomial models with robust standard errors.
+The estimated coefficients, standard errors, and confidence intervals produced by the latter four methods were *very* similar, and often identical (see Figure \@ref(fig:modelcompareplots).
 We therefore proceeded to fit and report models using `glm` with the quasibinomial family and logit link because model objects produced by this function are compatible with numerous other R packages for summarizing and plotting effects.
@@
 Compared to the mean *T2 Action* (M=`r signif(mean(d$T2Action, na.rm=T), 2)`), mean *T3 Action* increased substantially, `r inline_ttest(t2t3actionttest)`.
-Across the US vignettes, likelihood of acting at T3 increased to near-ceiling, regardless of participants' *T2 Action* values (M=`r signif(mean(d$T3Action[d$vignette != 'Thwarted marriage']), 2)`), indicating that propensity to act was indeed contingent on believing the victim.
+Across the US vignettes, likelihood of acting at T3 increased to near-ceiling (M=`r signif(mean(d$T3Action[d$vignette != 'Thwarted marriage']), 2)`), regardless of participants' *T2 Action* values, indicating that propensity to act was indeed contingent on believing the victim.
 In the Indian Thwarted marriage vignette, however, there was little change in *T3 Action* compared to *T2 Action* (Figure \@ref(fig:t3action)), perhaps because Indian participants' beliefs and actions were relatively insensitive to the signals to begin with (Figures \@ref(fig:beliefvignette) and \@ref(fig:ecdf)).
@@
 Fifth, the content of the vignette matters, so instead of a single vignette we decided to use four different vignettes to help determine the extent to which signaling effects were sensitive to seemingly irrelevant details of the vignettes.
-Sixth, in a randomized controlled trial, the control condition should be identical to the treatment condition in every respect except for the factor being tested, which in this study was signal cost.
+Sixth, in a pre-test post-test design, the control condition should be identical to the treatment condition in every respect except for the factor being tested, which in this study was signal cost.
 Post hoc, we realized that the control condition in the pilot study differed substantially from the treatment condition beyond signal cost: in the treatment conditions, participants encountered the sister twice: once when she requests help, and a second time when she signals.
@@
 
-In the reddit.com pilot study, participants viewed two vignettes (with different signals in each one), and responded with lower belief to the second vignette compared to the first (regardless of the vignette or signal).
+In the reddit.com pilot study, participants viewed two vignettes (with different signals in each one), and responded with lower belief to the second vignette compared to the first regardless of the vignette or signal.
 To avoid such order effects, which are a common problem in vignette studies that use multiple vignettes [@su2020], we decided to present each participant in the current study with a single vignette and signal.
@@
 ```{r}
+m1 <- models$Model[['m1']]
+m1_robust <- lmtest::coeftest(m1, vcov = sandwich::vcovHC(m1, type="HC"))
+
 m1_quasi <- models$TidyModel$m1
@@
 
+m3 <- models$Model[['m3']]
+m3_robust <- lmtest::coeftest(m3, vcov = sandwich::vcovHC(m3, type="HC"))
+
 m3_quasi <- models$TidyModel$m3

### 2021-05-10 R/functions.R

@@ -80,6 +80,9 @@ T1Belief_Action_dist <- function(d){
 
 }
 
+
+# Fit models --------------------------------------------------------------
+
 fit_models <- function(data, formulas, family = 'quasibinomial'){
   d <- tibble(
     Name = names(formulas),
@@ -89,13 +92,15 @@ fit_models <- function(data, formulas, family = 'quasibinomial'){
     } else {
       map(Formulas, ~lm(formula = .x, data = data))
       },
+    RobustCI = map(Model, ~lmtest::coefci(.x, vcov = sandwich::vcovHC(.x, type="HC"))),
     TidyModel = map(Model, ~tidy(.x, conf.int = T)),
     Anova = map(Model, ~Anova(.x, type = 3)),
     TidyANOVA = map(Anova, ~tidy(.x, conf.int = T)),
-    Margins = map(Model, ~margins(.x, type = 'response'))
+    Margins = map(Model, ~margins(.x, vcov = sandwich::vcovHC(.x, type="HC"), type = 'response'))
   )
 
   names(d$Model) <- d$Name
+  names(d$RobustCI) <- d$Name
   names(d$TidyModel) <- d$Name
   names(d$TidyANOVA) <- d$Name
   names(d$Margins) <- d$Name
@@ -116,6 +121,9 @@ fractional_model <- function(m, table = F){
   x = model.matrix(m)[,-1] # remove intercept
   frm(m$y, x, linkfrac = 'logit', table = table)
 }
+
+# Effect plots ------------------------------------------------------------
+
 
 effect_plot <- function(m, ...){
 
@@ -188,6 +196,8 @@ visreg_diff <- function(m, vignette, signal1, signal2, d, sig = 2){
   v2 <- fit$visregFit[fit$signal==signal2 & fit$vignette==vignette]
   signif(100*(v1 - v2), sig)
 }
+
+# Mediation ---------------------------------------------------------------
 
 signal_mediate <- function(
   data = NULL,
@@ -274,6 +284,7 @@ all_signals_mediate <- function(d){
   list(results=meds, plot=p)
 }
 
+# Plots -------------------------------------------------------------------
 
 emotion_plot <- function(d){
 
@@ -603,9 +614,16 @@ ggkde <- function(mkde){
 
 # Model comparison plot ---------------------------------------------------
 
[…]

### 2021-05-10 _targets.R

@@ -241,12 +241,12 @@ list(
 
   tar_target(
     belief_compare_plot,
-    compare_plot(models$TidyModel$m1, m1_boot, m1_frac, 'Belief models')
+    compare_plot(models$TidyModel$m1, models$RobustCI$m1, m1_boot, m1_frac, 'Belief models')
   ),
 
   tar_target(
     action_compare_plot,
-    compare_plot(models$TidyModel$m3, m3_boot, m3_frac, 'Action models')
+    compare_plot(models$TidyModel$m3, models$RobustCI$m3, m3_boot, m3_frac, 'Action models')
   ),
 
 # Effects plots -----------------------------------------------------------

### 2021-05-17 Paper.rmd
Minor edits to intro and SI

@@
 date: '`r format(Sys.Date(), "%B %d, %Y")`'
-always_allow_html: true
+always_allow_html: false
 output: 
@@
 To address this hypothesis, we examined responses to emotional signals in an experimental vignette study involving claims of substantial need in the presence of conflicts of interest and private information about whether the signaler was actually in need.
-In our sample of 1,240 participants recruited from Amazon Mechanical Turk, costlier signals like depression and suicide attempts resulted in greater perceptions of need and increased likelihood of support compared to simple verbal requests and crying without further symptoms.
-Additionally, the effect of signal type on likelihood of support was largely mediated by the effect of signaling on belief in need as predicted.
+In our sample of 1,240 participants recruited from Amazon Mechanical Turk, costlier signals like depression and suicide attempts resulted in greater perceptions of need, reduced perceptions of manipulativeness, and increased likelihood of support compared to simple verbal requests and crying without further symptoms.
+Additionally, as predicted, the effect of signal type on likelihood of support was largely mediated by the effect of signaling on belief in need.
 Our results suggest that depression and suicide attempts, apparent human universals, are relatively successful ways of signaling honest need and eliciting support, consistent with costly signaling explanations.
@@
 Similarly, an adolescent who was dissatisfied with her parent's investment in her would not easily find other parents who were willing to invest more, nor could parents easily produce another adolescent.
-In these examples, and many cooperative endeavors central to human biological fitness, each party has monopoly power over the benefits they bring to the endeavor -- no one is easily replaced [@Hagen2003].
+In these examples, and many cooperative endeavors central to human biological fitness, each party has monopoly power over the benefits they bring to the endeavor -- no one is easily replaced [@Hagen2002; @Hagen2003].
+Such interdependence is increasingly recognized to be important to the evolution of cooperation in humans and other animals [@roberts2005; @tomasello2012; @aktipis2018].
 
@@
 Once valuations are known, the game reduces to the one in @rubinstein1982, and the parties can reach an agreement on the division of benefits [@KennanWilson1993; @feinberg2005].
-@Hagen2003 proposed that the substantial reduction in productivity in depression corresponds to a willingness to delay, and is therefore a credible signal of need.
+@Hagen2003 proposed that the substantial reduction in productivity in depression corresponds to a willingness to delay, and is therefore a credible signal of low valuation and need.
 In other words, reduced productivity is relatively less costly for those whose efforts are currently not yielding many fitness-relevant benefits than for those whose efforts are yielding substantial benefits [@Hagen2003].
@@
 Suicidality is closely linked to depression.
-Suicidal ideation is one of nine diagnostic criteria for a major depressive episode [MDE, @dsm5], it is associated with depression across cultures [@haroz2017], and depression is a major risk factor for suicidal behavior [@hawton2013].
+Suicidal ideation is one of nine diagnostic criteria for a major depressive episode (MDE) [@dsm5], it is associated with depression across cultures [@haroz2017], and depression is a major risk factor for suicidal behavior [@hawton2013].
 
@@
 Early in the field's history, anthropologists tackled the problem of suicide as manifested in the small, traditional societies in which they conducted their fieldwork.
-Suicide, they found, was commonly a form of protest, revenge, and/or appeal (e.g., Malinowski, 1932; Niehaus, 2012).
-Some ethnographers, such as Hezel (1987), conceptualized suicide as a form of anger, whereas others, such as Giddens (1964), conceptualized suicide as a form of social pressure.
-Counts (1980) emphasized the powerlessness of suicide victims.
+Suicide, they found, was commonly a form of protest, revenge, and/or appeal [@firth1936; @Firth:1961; @Malinowski:1932; @niehaus2012].
+Some ethnographers conceptualized suicide as a form of anger or social pressure [@Hezel:1987; @Giddens:1964], whereas others emphasized the powerlessness of suicide victims [@Counts:1980].
 
@@
 In young adult women in the US, for example, there are hundreds of attempts for every death (see Figure \@ref(fig:cdc)).
-@SymeEtAl2016 therefore argued that the scientific focus should be on suicide ideation and suicide attempts.
+@SymeEtAl2016 therefore argued that the theoretical focus should be on suicide ideation and suicide attempts.
 
 Raymond Firth was one of the first to view suicidality as a gamble to improve one's circumstances in the here and now.
-Based on observations that suicide attempts often followed loss or conflict and varied substantially in their likelihood of death, he argued that a sizable subset of the suicide attempts among the Tikopia were not meant to end in death but instead were a means to elicit attention, status, or immediate reintegration into the community following negative events (Firth 1936; 1961).
-
-@Rosenthal1993 proposed a credible signaling model of what he, like Firth, viewed as 'gambling-type' suicide attempts.
+Based on observations that suicide attempts often followed loss or conflict and varied substantially in their likelihood of death, he argued that a sizable subset of the suicide attempts among the Tikopia were not meant to end in death but instead were a means to elicit attention, status, or immediate reintegration into the community following negative events [@firth1936; @Firth:1961].
+
+<!-- @Rosenthal1993 proposed a credible signaling model of what he, like Firth, viewed as 'gambling-type' suicide attempts.
 In the Rosenthal model, as long as that risk is greater than or equal to the net benefit a non-needy person would realize by sending the signal (discounted by the risk of death), social partners can trust that signal senders are genuinely in need despite conflicts of interest [@Rosenthal1993].
-In the bargaining framework, suicidality could be conceptualized as putting future fitness benefits at risk -- riskier attempts would credibly indicate lower valuation of the future.
-On these views, most suicides deaths, especially in young, physically healthy individuals, would therefore be the inevitable consequence that some individuals lose this gamble.
-These and similar ideas [@andrews2006; @HagenEtAl2008; @nock2008; @Stengel1956] suggest that depression symptoms that put one's value to others at risk, such as suicidality and loss of interest, might be credible signals of need.
+-->
+
+In the bargaining framework, suicidality is conceptualized as putting all future fitness benefits at risk with some low but non-zero probability, credibly signaling low valuation of current circumstances [see @Rosenthal1993 for a similar game theory model of suicide attempts as costly signals].
+On this view, most suicides deaths, especially in young, physically healthy individuals, would therefore be the inevitable consequence that some individuals lose this gamble.
+These and similar ideas [@andrews2006; @HagenEtAl2008; @nock2008; @Stengel1956] suggest that depression symptoms that put one's value to others at risk, such as loss of interest and suicidality, are credible signals of need.
 
@@
 
-## Depression and suicide attempts as both signals and bargaining tools
+<!-- ## Depression and suicide attempts as both signals and bargaining tools -->
 
@@
 
-The current study is a refinement of a large MTurk experimental vignette pilot study (N=`r nrow(signalingdata2018b)`) that used a different vignette but very similar signals and outcomes, and a much smaller pilot study posted to [reddit.com/r/SampleSize/](https://www.reddit.com/r/SampleSize/) (N=28) that used draft versions of three vignettes used in the current study, along with the same signals and outcomes.
+The current study is a refinement of a large MTurk experimental vignette pilot study (N=`r nrow(signalingdata2018b)`) that used a different vignette but very similar signals and outcomes (see below for more details on MTurk samples), and a much smaller pilot study posted to [reddit.com/r/SampleSize/](https://www.reddit.com/r/SampleSize/) (N=28) that used draft versions of three vignettes used in the current study, along with the same signals and outcomes.
 One major goal of the MTurk pilot study was to determine if believability and willingness to help were simply artifacts of the fictional victim's psychiatric distress.
@@
 
-We used the pilot data to estimate the sample sizes needed to detect an effect of the *Mild depression* signal vs.
+We used the MTurk pilot data to estimate the sample sizes needed to detect an effect of the *Mild depression* signal vs.
 *Verbal request* control on *Belief* in the victim's need.
@@
 As Amazon provides the infrastructure, it allows for a relatively low-cost way of collecting data for academic research at the cost of the data not being representative of any real population [@thomas2017].
-Despite this limitation, it is more diverse than most convenience samples [@kennedy2020; @DworkinEtAl2016; @thomas2017], with Turkers in the US mainly differing in being younger, more educated, and lower income than the greater U.S.
-population [@RossEtAl2010; @boas2020].
+Despite this limitation, MTurk samples have a wider range of ages and incomes than most university samples [@kennedy2020; @DworkinEtAl2016; @thomas2017].
+US MTurk samples also differ from the general US population, mainly in being younger, more educated, and lower income [@RossEtAl2010; @boas2020].
 
@@
 Fourth, we fit GLM models with the quasibinomial family and logit link using the `glm` function in R stats library, which can fit continuous outcomes on [0, 1].
-Finally, we fit the quasibinomial models with robust standard errors.
+Finally, we computed robust standard errors and 95% confidence intervals from the quasibinomial models using the `sandwich` package [@zeileis2006].
 The estimated coefficients, standard errors, and confidence intervals produced by the latter four methods were *very* similar, and often identical (see Figure \@ref(fig:modelcompareplots).
@@
 
-This study was funded through a Washington State University, Vancouver research mini grant.
+This study was funded through a Washington State University, Vancouver Research Mini Grant.
 We thank Anne Pisor, Darcy Bird, and members of the Hagen lab group for numerous helpful comments.
@@
 
-# To do:
-
--   victim or signaler?
--   add anger
--   Intro "State the objectives of the work and provide an adequate background, avoiding a detailed literature survey or a summary of the results."
--   Discussion " This should explore the significance of the results of the work, not repeat them.
+<!-- # To do: -->
+
+<!-- -   victim or signaler? -->
+<!-- -   add anger -->
+<!-- -   Intro "State the objectives of the work and provide an adequate background, avoiding a detailed literature survey or a summary of the results." -->
+<!-- -   Discussion " This should explore the significance of the results of the work, not repeat them.
 A combined Results and Discussion section is often appropriate.
-Avoid extensive citations and discussion of published literature."
--   mention asking for prefered sex
-
-# Notes from my meeting with Anne
-
--   Table detailing the cooperative endeavor (maybe word as boundedness of fate), conflict of interest, and what the private information is about would be useful.
--   Calling verbal request control when it's a treatment?
--   Can shift much of the pilot studies info to SI with some detail post line 279 in draft she saw.
--   Cumulative distribution plot: needs more info in captions. could benefit from fig6a and fig6b (confusion over x and y axes)
+Avoid extensive citations and discussion of published literature." -->
+<!-- -   mention asking for prefered sex -->
+
+<!-- # Notes from my meeting with Anne -->
+
+<!-- -   Table detailing the cooperative endeavor (maybe word as boundedness of fate), conflict of interest, and what the private information is about would be useful. -->
+<!-- -   Calling verbal request control when it's a treatment? -->
+<!-- -   Can shift much of the pilot studies info to SI with some detail post line 279 in draft she saw. -->
+<!-- -   Cumulative distribution plot: needs more info in captions. could benefit from fig6a and fig6b (confusion over x and y axes) -->
 
@@
 
-## Pilot study descriptions
-
-Briefly, participants read a vignette that put them in situations in which an imagined sister was requesting a loan of \$50,000 from the participant that was originally saved for the participant's imagined daughter's college education.
+## Pilot studies
+
+We conducted two pilot studies, one on MTurk with a large sample size (N=`r `nrow(signalingdata2018b)`), and one on [reddit.com/r/SampleSize](https://reddit.com/r/SampleSize) with a small sample size (N=28).
+Both studies used the experimental pre-test, post-test design used in the current study.
+
+In the MTurk study, participants read a vignette that put them in situations in which an imagined sister was requesting a loan of \$50,000 from the participant that was originally saved for the participant's imagined daughter's college education.
 The sister claims the money is needed for medical treatment for her own child, but she has incentives to deceive.
@@
 In the small reddit.com study, participants viewed and responded to two vignettes used here, each with a different signal.
-
-## Lessons learned from the pilot study
 
@@
 
-## Power from pilot study
-
-We estimated power using our pilot study data to compare the effect of the *Mild depression* signal vs.
+## Power from MTurk pilot study
+
+We estimated power using our MTurk pilot study data to compare the effect of the *Mild depression* signal vs.
 the *Verbal request* control on *Belief* (that the sister needed the money) at T2 controlling for *Belief* at T1 in a linear regression model.
@@
 
-## Vignettes (main bodies and signals)
+## Vignettes of the current study (main bodies and signals)
 

### 2021-05-17 Paper.rmd
Getting close to final version

@@
 
+Some evolutionary theorists have questioned the bargaining model based on evidence that depression is aversive to social partners [@nettle2004; @allen2006; @nesse2006; @myers2016].
+These critics fail to acknowledge the central role of *conflict* in the signaling/bargaining models.
+Anger causes negative reactions in targeted social partners, yet it is probably an adaptation that exploits advantages in physical or social formidability to force concessions from others [@sell2009].
+Aversive responses to bargaining are expected throughout the process, with potential helpers likely signaling the costliness of providing support in turn.
+Importantly, such responses do not prevent the delivery of meaningful benefits [@SymeHagen2021].
+
 <!-- Compared to suicide, however, there are fewer anthropological investigations of depression [@kleinman1985] despite frequent reports of depression or depression-like behavior in a wide range of societies [@haroz2017; @liu2020] and the potential for cross-cultural research to help understand depressive states [@haroz2017].
@@
 
-<!-- Our results suggest that the costs of depression and suicidality, which in mainstream theories are taken as evidence of brain dysfunction, might instead function to help victims elicit support from reluctant social partners with whom they are in conflict.
--->
-
 <!-- Although this study was not designed to examine whether the costs of signaling would be made up for by the increased support stemming from depression and suicide attempts directly, the results are consistent with this hypothesis.
@@
 The main limitation of this study is that is has less ecological validity than real-world observations of depressed individuals interacting with their social partners.
-It is almost certain that participants experienced this study differently than they would if the event actually happened to them.
 This may have biased results in a pro-signaler direction if the lack of real costs of helping made support feel less costly or if there was a social desirability bias toward helping [@grimm2010].
-It may have also biased participants against helping if they could not fully imagine the characters in the story as kin or important cooperative partners, while the survey's short duration may have weakened the strength of the costlier signals as bargaining tools.
-
-Another limitation is that our control included a signal in the form of a verbal request, preventing comparisons to non-signaling strategies.
-Similarly, our design did not include vignettes with male signalers.
+It may have also biased participants against helping if they could not fully imagine the characters in the story as kin or important cooperative partners, and the survey's short duration may have weakened the strength of the costlier signals as bargaining tools.
+
+Our design did not include vignettes with male signalers.
 For this reason, we have no data on the possibility of sex differences in the effectiveness of the signaling strategies examined.
@@
 
-In terms of data quality our largest limitation is that, compared to the US sample, far more Indian participants were filtered out by our attention checks, something which could be consistent with botting, unfamiliarity with English, or low effort responses [@kennedy2020].
-Assuming this corresponded with lower-quality responses among those who passed the attention checks, the weak signal effect in the thwarted marriage vignette may simply be due to added noise rather than differences in the scenario or the effectiveness of the signals compared to those in the US.
+Compared to the US sample, far more Indian participants failed our attention checks, which is consistent with botting, unfamiliarity with English, or low-effort responses [@kennedy2020].
+If this high failure rate indicates lower-quality responses among those who passed the attention checks, the weak signal effect in the thwarted marriage vignette may simply be due to greater noise rather than differences in the scenario or the effectiveness of the signals compared to those in the US.
 Another concern relevant to all vignettes is that our decision to anchor the T1 sliders at 0 may have resulted in participants being more likely to report extreme values.
@@
 <!-- T\d \w+ -->
+
 # Conclusion
 
-Our results suggest that the costs of depression and suicidality, which in mainstream theories are taken as evidence of brain dysfunction [@SymeHagen2021], might instead function to help victims elicit support from reluctant social partners with whom they are in conflict.
-This coupled with findings that depression can simultaneously elicit both positive and negative responses [@HokansonEtAl1986; @stephens1987], suggests that more attention should be paid to the potential for positive responses towards depressed individuals, especially from individuals who normally receive substantial benefits from the depressed or suicidal individual.
+Depression is costly, sometimes resulting in death by suicide.
+Our results suggest that these costs, which mainstream theories take as evidence of brain dysfunction [@SymeHagen2021], function to help victims of adversity elicit support when their true level of need is private information and they have conflicts with social partners.
+These findings align with real-world evidence that depression simultaneously elicits positive and negative responses from social partners [@SymeHagen2021].
+If the bargaining model is correct, depression is an important social problem, not a medical one [@syme2020].
+
+<!-- This coupled with , suggests that more attention should be paid to the potential for positive responses towards depressed individuals, especially from social partners who receive substantial benefits from the depressed or suicidal individual.
+-->
 

### 2021-05-18 Paper.rmd
Fixed key. Added index.html

@@
 These critics fail to acknowledge the central role of *conflict* in the signaling/bargaining models.
-Anger causes negative reactions in targeted social partners, yet it is probably an adaptation that exploits advantages in physical or social formidability to force concessions from others [@sell2009].
+Anger causes negative reactions in targeted social partners, yet it is probably an adaptation that exploits advantages in physical or social formidability to force concessions from others [@SellEtAl2009].
 Aversive responses to bargaining are expected throughout the process, with potential helpers likely signaling the costliness of providing support in turn.

### 2021-05-19 Paper.rmd
* Tweaked abstract * Rearranged results so all confirmatory results come first, exploratory second

@@
 Major depression and suicide are generally viewed as pathological responses to stress that elicit aversive responses from others.
-Alternatively, depression and suicide attempts might involve honest signals of need in response to stress and help to bargain for increased support from reluctant others.
-To address this hypothesis, we examined responses to emotional signals in an experimental vignette study involving claims of substantial need in the presence of conflicts of interest and private information about whether the signaler was actually in need.
-In our sample of 1,240 participants recruited from Amazon Mechanical Turk, costlier signals like depression and suicide attempts resulted in greater perceptions of need, reduced perceptions of manipulativeness, and increased likelihood of support compared to simple verbal requests and crying without further symptoms.
+Alternatively, depression and suicide attempts might involve honest signals of need in response to stress that can increase support from reluctant others.
+To test this hypothesis, we examined responses to emotional signals in an experimental vignette study involving claims of substantial need in the presence of conflicts of interest and private information about whether the signaler was actually in need.
+In a sample of 1,240 participants recruited from Amazon Mechanical Turk, costlier signals like depression and suicide attempts resulted in greater perceptions of need, reduced perceptions of manipulativeness, and increased likelihood of support compared to simple verbal requests and crying without further symptoms.
 Additionally, as predicted, the effect of signal type on likelihood of support was largely mediated by the effect of signaling on belief in need.
-Our results suggest that depression and suicide attempts, apparent human universals, are relatively successful ways of signaling honest need and eliciting support, consistent with costly signaling explanations.
+Our results support the hypothesis that depression and suicide attempts, apparent human universals, are credible signals of need.
 
@@
 See Figure \@ref(fig:beliefeffect) and models m1 and m3 in Tables \@ref(tab:regressiontables) and \@ref(tab:anovatables).
+(Results for the preregistered OLS models were very similar; see Figures \@ref(fig:preregbelief) and \@ref(fig:preregbeliefB).)
 
@@
 The within-subject effects of each signal are depicted in Figure \@ref(fig:rawbeliefactions2d).
-
-## Exploratory: Signals effects differ by vignette
-
-```{r}
-
-thwart_sv_bdiff <- visreg_diff(models$Model$m2, 'Thwarted marriage', 'Suicide attempt', 'Verbal request', d)
-
-thwart_sv_adiff <- visreg_diff(models$Model$m4, 'Thwarted marriage', 'Suicide attempt', 'Verbal request', d)
-
-brother_sv_bdiff <- visreg_diff(models$Model$m2, 'Brother-in-law', 'Suicide attempt', 'Verbal request', d)
-
-brother_sv_adiff <- visreg_diff(models$Model$m4, 'Brother-in-law', 'Suicide attempt', 'Verbal request', d)
-
-```
-
-```{r}
-bil_b_suicide <- signif(effect_sizes$est[effect_sizes$id=="Suicide attempt,Brother-in-law" & effect_sizes$Outcome=="Belief"], 2)
-
-rom_b_crying <- signif(effect_sizes$est[effect_sizes$id=="Crying,Romantic partner" & effect_sizes$Outcome=="Belief"], 2)
-
-bil_a_suicide <- signif(effect_sizes2$effsize[effect_sizes2$id=="Suicide attempt,Brother-in-law" & effect_sizes2$Outcome=="Action"], 2)
-
-bil_a_verbal <- signif(effect_sizes2$effsize[effect_sizes2$id=="Verbal request,Brother-in-law" & effect_sizes2$Outcome=="Action"], 2)
-
-```
-
-The largest between-subjects effect was *Suicide attempt* vs.
-*Verbal request* control on *Belief* in the "Brother-in-law" vignette, Cohen's d = `r bil_b_suicide`, and the smallest was the effect of *Crying* on *Belief* in the "Romantic partner" vignette, Cohen's d =`r rom_b_crying`.
-The largest within-subjects effect was *Suicide attempt* on *Action* at T2 vs.
-T1 in the "Brother-in-law" vignette, Cohen's d = `r bil_a_suicide`, and the smallest was the *negative* effect of *Verbal request* on *Action* at T2 vs.
-T1 in the "Brother-in-law" vignette, Cohen's d =`r bil_a_verbal`.
-See Figures \@ref(fig:effectsizes) and \@ref(fig:effectsizes2).
-
-We note the following patterns, which we will return to in the Discussion section.
-First, as we intended, the distributions of *Belief* and *Action* in the *Verbal request* control condition were very similar to their distributions at T1 baseline across vignettes.
-In the "Basketball coach" and "Brother-in-law" vignettes, though, their distributions in the *Verbal request* condition were shifted to somewhat lower values relative to baseline (i.e., the verbal request slightly *reduced* belief and action in those vignettes).
-Second, in the "Romantic partner" and "Brother-in-law" vignettes, the effect of *Crying* differed little from *Verbal request*, but in the "Basketball coach" vignette, it differed little from the *Depression* and *Suicide attempt* signals.
-Third, the effect of the *Suicide attempt* signal on *Belief* was similar to that of *Depression* across all vignettes, but had a noticeably greater effect on *Action* in the "Romantic partner" and "Brother-in-law" vignettes.
-Fourth, there was little difference between the effect of the *Mild depression* vs.
-*Depression* signals.
-See Figures \@ref(fig:beliefvignette) and \@ref(fig:ecdf).
-
-```{r beliefvignette, fig.width=8, fig.height=8, fig.cap=paste0("The effect of the signals on *T2 Belief* (top) and *T2 Action* (bottom) in each vignette, controlling for T1 values of Belief and Action, respectively.
-Ratings rescaled to [0, 1].
-Effects plotted for T1 values set to their median value (*T1 Belief*=", median(d$T1Belief, na.rm=T), ", *T1 Action*=", median(d$T1Action, na.rm=T), ").
-Fit using generalized linear regression models with the quasibinomial family.
-Grey bars are 95% CIs.
-For coefficents, p-values, and other statistics, see models m2 and m4 in Tables \\@ref(tab:regressiontables) and \\@ref(tab:anovatables).")}
-(effectsPlots$m2plot + theme(axis.text.x = element_blank()))/effectsPlots$m4plot + plot_layout(ncol = 1) & theme(plot.margin = unit(c(0,0,0,0), units = 'mm'))
-```
-
-```{r ecdf, fig.width=11, fig.height=6, fig.cap="Empirical cummulative distribution functions for Time 2 Belief (top) and Action (bottom) compared to their Time 1 baseline values (red), by signal and vignette.
-Y-values indicate the fraction of all ratings equal to or less than a given x-value.
-Ratings rescaled to [0, 1].
-Dots indicate median values of Belief and Action, by signal and vignette."}
-ecdf_plot
-```
 
@@
 
+## Exploratory: Signal effects differ by vignette
+
+```{r}
+
+thwart_sv_bdiff <- visreg_diff(models$Model$m2, 'Thwarted marriage', 'Suicide attempt', 'Verbal request', d)
+
+thwart_sv_adiff <- visreg_diff(models$Model$m4, 'Thwarted marriage', 'Suicide attempt', 'Verbal request', d)
+
+brother_sv_bdiff <- visreg_diff(models$Model$m2, 'Brother-in-law', 'Suicide attempt', 'Verbal request', d)
+
+brother_sv_adiff <- visreg_diff(models$Model$m4, 'Brother-in-law', 'Suicide attempt', 'Verbal request', d)
+
+```
+
+```{r}
+bil_b_suicide <- signif(effect_sizes$est[effect_sizes$id=="Suicide attempt,Brother-in-law" & effect_sizes$Outcome=="Belief"], 2)
+
+rom_b_crying <- signif(effect_sizes$est[effect_sizes$id=="Crying,Romantic partner" & effect_sizes$Outcome=="Belief"], 2)
+
+bil_a_suicide <- signif(effect_sizes2$effsize[effect_sizes2$id=="Suicide attempt,Brother-in-law" & effect_sizes2$Outcome=="Action"], 2)
+
+bil_a_verbal <- signif(effect_sizes2$effsize[effect_sizes2$id=="Verbal request,Brother-in-law" & effect_sizes2$Outcome=="Action"], 2)
+
+```
+
+The effects of the signals on rated beliefs and actions differed substantially by vignette, which we display in three ways for each signal in each vignette: estimated cumulative distributions plots, which show the entire distributions of rated beliefs and actions, including which signals and vignettes have high fractions of 0's and 1's (Figures \@ref(fig:ecdf)); regression estimates of the mean effects of the signals on beliefs and actions by vignette (Figure \@ref(fig:beliefvignette)); and between- and within-subjects signal effect sizes by vignette (Figures \@ref(fig:effectsizes) and \@ref(fig:effectsizes2)).
+
+```{r ecdf, fig.width=11, fig.height=6, fig.cap="Empirical cummulative distribution functions for Time 2 Belief (top) and Action (bottom) compared to their Time 1 baseline values (red), by signal and vignette.
+Y-values indicate the fraction of all ratings equal to or less than a given x-value.
+Ratings rescaled to [0, 1].
+Dots indicate median values of Belief and Action, by signal and vignette."}
+ecdf_plot
+```
+
+```{r beliefvignette, fig.width=8, fig.height=8, fig.cap=paste0("The effect of the signals on *T2 Belief* (top) and *T2 Action* (bottom) in each vignette, controlling for T1 values of Belief and Action, respectively.
+Ratings rescaled to [0, 1].
+Effects plotted for T1 values set to their median value (*T1 Belief*=", median(d$T1Belief, na.rm=T), ", *T1 Action*=", median(d$T1Action, na.rm=T), ").
+Fit using generalized linear regression models with the quasibinomial family.
+Grey bars are 95% CIs.
+For coefficents, p-values, and other statistics, see models m2 and m4 in Tables \\@ref(tab:regressiontables) and \\@ref(tab:anovatables).")}
+(effectsPlots$m2plot + theme(axis.text.x = element_blank()))/effectsPlots$m4plot + plot_layout(ncol = 1) & theme(plot.margin = unit(c(0,0,0,0), units = 'mm'))
+```
+
+We note the following patterns in Figure \@ref(fig:ecdf), which we will return to in the Discussion section.
+First, as we intended, the distributions of *Belief* and *Action* in the *Verbal request* control condition were very similar to their distributions at T1 baseline across vignettes.
+In the "Basketball coach" and "Brother-in-law" vignettes, though, their distributions in the *Verbal request* condition were shifted to somewhat lower values relative to baseline (i.e., the verbal request slightly *reduced* belief and action in those vignettes).
+Second, in the "Romantic partner" and "Brother-in-law" vignettes, the effect of *Crying* differed little from *Verbal request*, but in the "Basketball coach" vignette, it differed little from the *Depression* and *Suicide attempt* signals.
+Third, the effect of the *Suicide attempt* signal on *Belief* was similar to that of *Depression* across all vignettes, but had a noticeably greater effect on *Action* in the "Romantic partner" and "Brother-in-law" vignettes.
+Fourth, there was little difference between the effect of the *Mild depression* vs.
+*Depression* signals.
+
+The largest between-subjects effect was *Suicide attempt* vs.
+*Verbal request* control on *Belief* in the "Brother-in-law" vignette, Cohen's d = `r bil_b_suicide`, and the smallest was the effect of *Crying* on *Belief* in the "Romantic partner" vignette, Cohen's d =`r rom_b_crying`.
+The largest within-subjects effect was *Suicide attempt* on *Action* at T2 vs.
+T1 in the "Brother-in-law" vignette, Cohen's d = `r bil_a_suicide`, and the smallest was the *negative* effect of *Verbal request* on *Action* at T2 vs.
+T1 in the "Brother-in-law" vignette, Cohen's d =`r bil_a_verbal`.
+
 ## Exploratory: Sociodemographic associations
@@
 Across the US vignettes, likelihood of acting at T3 increased to near-ceiling (M=`r signif(mean(d$T3Action[d$vignette != 'Thwarted marriage']), 2)`), regardless of participants' *T2 Action* values, indicating that propensity to act was indeed contingent on believing the victim.
-In the Indian Thwarted marriage vignette, however, there was little change in *T3 Action* compared to *T2 Action* (Figure \@ref(fig:t3action)), perhaps because Indian participants' beliefs and actions were relatively insensitive to the signals to begin with (Figures \@ref(fig:beliefvignette) and \@ref(fig:ecdf)).
+In the Indian Thwarted marriage vignette, however, there was little change in *T3 Action* compared to *T2 Action* (Figure \@ref(fig:t3action)), perhaps because Indian participants' beliefs and actions were relatively insensitive to the signals to begin with (Figures \@ref(fig:ecdf) and \@ref(fig:beliefvignette)).
 
@@
 
-We conducted two pilot studies, one on MTurk with a large sample size (N=`r `nrow(signalingdata2018b)`), and one on [reddit.com/r/SampleSize](https://reddit.com/r/SampleSize) with a small sample size (N=28).
+We conducted two pilot studies, one on MTurk with a large sample size (N=`r nrow(signalingdata2018b)`), and one on [reddit.com/r/SampleSize](https://reddit.com/r/SampleSize) with a small sample size (N=28).
 Both studies used the experimental pre-test, post-test design used in the current study.
@@
 ```{r power, fig.cap="Power curve for between-subjects effect of Mild depression vs. Verbal request signal on T2 Belief, controlling for T1 Belief."}
+
+smplesize <- nrow(d)/10
+
 ggplot(power_curve, aes(sample_size, power)) +
   geom_line() +
+  geom_vline(xintercept = smplesize, linetype = 'dotted') +
+  annotate(geom = 'text', x = smplesize + 3, y = 0.75, label = 'Current study sample size', hjust = 0) +
   labs(x = '\n Sample size', y = 'Power\n') +
@@
 Generic: A few short words, such as 'nice study', or 'thanks'.
-Informative: one or two sentences commenting on specific aspects of the survey."}
+Informative: one or two sentences commenting on specific aspects of the survey.
+Numbers are the number of participants in that category."}
 
@@
 See Figure \\@ref(fig:feedbackplot) for other types of feedback.
-See Table \\@ref(tab:informativetab) for the text of all informative statements."}
+See Table \\@ref(tab:informativetab) for the text of all informative statements.
+Numbers are the number of participants in that category."}
 hagenutils::ggxtabs(xtabs(~Informative + vignette, d), cell_counts = T) + xlab('')

### 2021-05-20 Paper.rmd
Fixed a few typos. Added edits in the form of commented out lines with the text "CurrentDraft" at the end. Added year to Clifford 2021 citation in MTBib.

@@
 
+<!-- Almost all individuals will suffer adversity, such as injury or loss of material or social resources, at some point in their lives.
+Psychological pain, such as sadness and low mood, probably evolved to motivate victims of adversity to shift their attention to the causes of the problem so as to mitigate its negative fitness consequences and to learn to avoid future such adverse events [@thornhill1989; @andrews2010; @Nesse1990].
+In many types of adversity, social partners could help minimize the costs.
+Therefore signals of psychological pain, such as sad expressions and crying, probably evolved to indicate need [e.g., @balsters2013].
+CurrentDraft-->
+
 There is strong evidence that most cases of depression are caused by major negative life events [@Hammen2005; @Mazure1998; @devries2011; @ellsberg2008].
@@
 Additional support for the causal role of negative life events comes from the fact that the relationship between negative events and depression holds true when looking at events outside of one's control, showing that the connection is unlikely to be driven solely by individuals who are already depressed creating situations where negative events are likely to be common [@Hammen2005; @KendlerEtAl1999].
-Additionally, twin studies have shown that one's history of negative events is still a strong predictor of major depression when controlling for genetic similarity, and that part of the heritability of depression stems from the heritability of negative events like divorce and family conflict [@KendlerBaker2007; @KendlerEtAl1999].
+Furthermore, twin studies have shown that one's history of negative events is still a strong predictor of major depression when controlling for genetic similarity, and that part of the heritability of depression stems from the heritability of negative events like divorce and family conflict [@KendlerBaker2007; @KendlerEtAl1999].
 For these and other reasons, most cases of depression are probably not due to mental illness but are instead functional instances of psychological pain [@Hagen:1999; @Hagen2003; @horwitz_loss_2007; @andrews2010; @SymeHagen2021].
@@
 If valuations are private information, however, then immediate agreement might not be possible because each party has an incentive to request an amount greater than their actual valuation, which would harm the other party.
-A willingness to delay is a credible signal that one has a low valuation of the endeavor, and is therefore genuinely in need, because for those with a low valuation the benefit of waiting for a better offer outweighs the low cost of delay whereas for those for those with a high valuation the benefit of waiting for a better offer does not outweigh the higher cost of delay.
+A willingness to delay is a credible signal that one has a low valuation of the endeavor, and is therefore genuinely in need, because for those with a low valuation the benefit of waiting for a better offer outweighs the low cost of delay whereas for those with a high valuation the benefit of waiting for a better offer does not outweigh the higher cost of delay.
 Once valuations are known, the game reduces to the one in @rubinstein1982, and the parties can reach an agreement on the division of benefits [@KennanWilson1993; @feinberg2005].
@@
 
+<!-- Some evolutionary theorists have questioned the bargaining model based on evidence that depression is aversive to social partners [@nettle2004; @allen2006; @nesse2006; @myers2016].
+These critics fail to acknowledge the central role of *conflict* in the signaling/bargaining models.
+Anger causes negative reactions in targeted social partners, yet it is probably an adaptation that exploits advantages in physical or social formidability to force concessions from others [@SellEtAl2009].
+Aversive responses to bargaining are expected throughout the process, with potential helpers likely signaling the costliness of providing support in turn.
+Importantly, such responses do not prevent the delivery of meaningful benefits [@SymeHagen2021].
+CurrentDraft [move this up from suicidality section-->
+
+<!-- As cooperation generates benefits overtime, withholding or risking contributions incurs a cost of delay – the more one values the endeavor, the greater the cost of delay. CurrentDraft-->
 ## Suicidality
@@
 
-The final part of the survey was a brief demographic questionnaire which asked for (1) the age, (2) sex, (3) number of siblings, (4) number of sons, (5) number of daughters, (6) current relationship status, (7) highest level of education, and (8) the annual household income of each participant.
+The final part of the survey was a brief demographic questionnaire which asked for the (1) age, (2) sex, (3) number of siblings, (4) number of sons, (5) number of daughters, (6) current relationship status, (7) highest level of education, and (8) the annual household income of each participant.
 

### 2021-05-22 Paper.rmd
Many minor edits, mostly to the bargaining theory section

--- 2021-05-19 Paper.rmd
@@
 In a sample of 1,240 participants recruited from Amazon Mechanical Turk, costlier signals like depression and suicide attempts resulted in greater perceptions of need, reduced perceptions of manipulativeness, and increased likelihood of support compared to simple verbal requests and crying without further symptoms.
-Additionally, as predicted, the effect of signal type on likelihood of support was largely mediated by the effect of signaling on belief in need.
+Additionally, as predicted, the effect of signaling on likelihood of support was largely mediated by the effect of signaling on belief in need.
 Our results support the hypothesis that depression and suicide attempts, apparent human universals, are credible signals of need.
@@
 
-With a cooperative species like our own, the ubiquity of conflicts of interests means that there will always be disagreement over the levels of investment in a cooperative endeavor and the division of the resulting benefits.
+With a cooperative species like our own, ubiquitous conflicts of interest means that there will always be disagreement over the levels of investment in a cooperative endeavor and the division of the resulting benefits.
 In many such cases, individuals who were dissatisfied with the terms of cooperation could seek other partners [@hammerstein2016].
@@
 Similarly, an adolescent who was dissatisfied with her parent's investment in her would not easily find other parents who were willing to invest more, nor could parents easily produce another adolescent.
-In these examples, and many cooperative endeavors central to human biological fitness, each party has monopoly power over the benefits they bring to the endeavor -- no one is easily replaced [@Hagen2002; @Hagen2003].
+In these examples, and many cooperative endeavors central to human biological fitness, all parties have monopoly power over the benefits they bring to the endeavor -- no one is easily replaced [@Hagen2002; @Hagen2003].
 Such interdependence is increasingly recognized to be important to the evolution of cooperation in humans and other animals [@roberts2005; @tomasello2012; @aktipis2018].
@@
 
-Formal models of bargaining highlight the role of private information regarding the value each party places the cooperative endeavor.
+Bargaining models assume that delaying cooperation is costly so that there is an incentive to quickly agree on a division of benefits, and more so for those who highly value the fruits of the cooperative endeavor.
+In a classic non-cooperative game theory model of bargaining, @rubinstein1982 showed that two parties can come to an immediate agreement over division of benefits despite conflicts of interest if the parties' valuations of cooperation are not private information: in this case, each party knows exactly what division of benefits the other will accept, and can therefore make that offer immediately, avoiding the cost of delay.
+
+If valuations are private information, however, then costly delays might be unavoidable because each party has an incentive to request more than their actual valuation, and to reject the likely inflated requests from partners, leading to multiple rounds of bargaining.
+Models of bargaining with private information have a close relationship to models of credible signaling.
+A willingness to delay (i.e., refuse offers) credibly reveals one's low valuation of the endeavor, and therefore genuine need -- the benefit of waiting for a better offer outweighs the low cost of delay.
+Eagerness to reach a deal, on the other hand, credibly reveals a high valuation -- the benefit of waiting for a better offer does not outweigh the higher cost of delay.
+Once valuations are known, the game reduces to the one in @rubinstein1982, and the parties can reach an agreement on the division of benefits [@KennanWilson1993].
+Delays also typically require that additional factors come into play [@feinberg2005 and references therein].
+
+@Hagen2003 proposed that the substantial reduction in productivity in depression corresponds to a willingness to delay, and is therefore a credible signal of low valuation and need.
+In other words, reduced productivity is relatively less costly for those whose efforts are currently not yielding many fitness benefits than for those whose efforts are yielding substantial benefits.
+
+<!-- Formal models of bargaining highlight the role of private information regarding the value each party places the cooperative endeavor.
 Withholding or risking one's contributions to a cooperative endeavor can be conceptualized as credibly signaling private information about one's need.
@@
 Thus, withholding or risking contributions incurs a *cost of delay* -- the more one values the endeavor, the greater the cost of delay.
-In a classic non-cooperative game theory model of bargaining over the division of benefits, @rubinstein1982 showed that two parties can come to an immediate agreement over division of benefits despite conflicts of interest if the parties' valuations of cooperation are not private information: in this case, each party knows exactly what division of benefits the other will accept, and can therefore make that offer immediately, avoiding the cost of delay.
-If valuations are private information, however, then immediate agreement might not be possible because each party has an incentive to request an amount greater than their actual valuation, which would harm the other party.
-A willingness to delay is a credible signal that one has a low valuation of the endeavor, and is therefore genuinely in need, because for those with a low valuation the benefit of waiting for a better offer outweighs the low cost of delay whereas for those for those with a high valuation the benefit of waiting for a better offer does not outweigh the higher cost of delay.
-Once valuations are known, the game reduces to the one in @rubinstein1982, and the parties can reach an agreement on the division of benefits [@KennanWilson1993; @feinberg2005].
-@Hagen2003 proposed that the substantial reduction in productivity in depression corresponds to a willingness to delay, and is therefore a credible signal of low valuation and need.
-In other words, reduced productivity is relatively less costly for those whose efforts are currently not yielding many fitness-relevant benefits than for those whose efforts are yielding substantial benefits [@Hagen2003].
+-->
 
@@
 Suicide, they found, was commonly a form of protest, revenge, and/or appeal [@firth1936; @Firth:1961; @Malinowski:1932; @niehaus2012].
-Some ethnographers conceptualized suicide as a form of anger or social pressure [@Hezel:1987; @Giddens:1964], whereas others emphasized the powerlessness of suicide victims [@Counts:1980].
+Some ethnographers emphasized suicide as a form of anger or social pressure [@Hezel:1987; @Giddens:1964], whereas others emphasized the powerlessness of suicide victims [@Counts:1980].
 
@@
 
-Raymond Firth was one of the first to view suicidality as a gamble to improve one's circumstances in the here and now.
-Based on observations that suicide attempts often followed loss or conflict and varied substantially in their likelihood of death, he argued that a sizable subset of the suicide attempts among the Tikopia were not meant to end in death but instead were a means to elicit attention, status, or immediate reintegration into the community following negative events [@firth1936; @Firth:1961].
-
-<!-- @Rosenthal1993 proposed a credible signaling model of what he, like Firth, viewed as 'gambling-type' suicide attempts.
-In the Rosenthal model, as long as that risk is greater than or equal to the net benefit a non-needy person would realize by sending the signal (discounted by the risk of death), social partners can trust that signal senders are genuinely in need despite conflicts of interest [@Rosenthal1993].
--->
-
-In the bargaining framework, suicidality is conceptualized as putting all future fitness benefits at risk with some low but non-zero probability, credibly signaling low valuation of current circumstances [see @Rosenthal1993 for a similar game theory model of suicide attempts as costly signals].
-On this view, most suicides deaths, especially in young, physically healthy individuals, would therefore be the inevitable consequence that some individuals lose this gamble.
-These and similar ideas [@andrews2006; @HagenEtAl2008; @nock2008; @Stengel1956] suggest that depression symptoms that put one's value to others at risk, such as loss of interest and suicidality, are credible signals of need.
-
-Some evolutionary theorists have questioned the bargaining model based on evidence that depression is aversive to social partners [@nettle2004; @allen2006; @nesse2006; @myers2016].
-These critics fail to acknowledge the central role of *conflict* in the signaling/bargaining models.
-Anger causes negative reactions in targeted social partners, yet it is probably an adaptation that exploits advantages in physical or social formidability to force concessions from others [@SellEtAl2009].
-Aversive responses to bargaining are expected throughout the process, with potential helpers likely signaling the costliness of providing support in turn.
-Importantly, such responses do not prevent the delivery of meaningful benefits [@SymeHagen2021].
-
-<!-- Compared to suicide, however, there are fewer anthropological investigations of depression [@kleinman1985] despite frequent reports of depression or depression-like behavior in a wide range of societies [@haroz2017; @liu2020] and the potential for cross-cultural research to help understand depressive states [@haroz2017].
--->
-
-```{r cdc, fig.width=8, fig.cap="US Suicidality non-fatal injury and death rates by age and sex (2001-2019)."}
+```{r cdc, fig.width=8, fig.cap="US Suicidality non-fatal injury and death rates by age and sex (2001-2019). Data from @CDC2021."}
 library(hrafsuicidedata)
@@
 
+Raymond Firth was one of the first to view suicidality as a gamble to improve one's circumstances in the here and now.
+Based on observations that suicide attempts often followed loss or conflict and varied substantially in their likelihood of death, he argued that a sizable subset of the suicide attempts among the Tikopia were not meant to end in death but instead were a means to elicit attention, status, or immediate reintegration into the community following negative events [@firth1936; @Firth:1961].
+
+<!-- @Rosenthal1993 proposed a credible signaling model of what he, like Firth, viewed as 'gambling-type' suicide attempts.
+In the Rosenthal model, as long as that risk is greater than or equal to the net benefit a non-needy person would realize by sending the signal (discounted by the risk of death), social partners can trust that signal senders are genuinely in need despite conflicts of interest [@Rosenthal1993].
+-->
+
+In the bargaining framework, suicidality is conceptualized as putting all future contributions to cooperative endeavors with social partners at risk with some low but non-zero probability, credibly signaling low valuation of current circumstances [see @Rosenthal1993 for a game theory model of suicide attempts as costly signals].
+On this view, most suicides deaths, especially in young, physically healthy individuals, would therefore be the inevitable consequence that some individuals lose this gamble.
+These and similar ideas [@andrews2006; @HagenEtAl2008; @nock2008; @Stengel1956] suggest that depression symptoms that put one's value to others at risk, such as loss of interest and suicidality, are credible signals of need.
+
+Some evolutionary theorists have questioned the bargaining model based on evidence that depression is aversive to social partners [@nettle2004; @allen2006; @nesse2006; @myers2016].
+These critics failed to recognize the central role of *conflict* in the signaling/bargaining models.
+Anger is aversive to targeted social partners, yet it is probably an adaptation that exploits advantages in physical or social formidability to force concessions from them [@SellEtAl2009].
+Aversive responses to depressive bargaining are likewise expected throughout the process, with potential helpers signaling the costliness of providing support in turn.
+Importantly, as with anger, aversive responses to depression do not prevent concessions by interdependent social partners [@SymeHagen2021].
+
+<!-- Compared to suicide, however, there are fewer anthropological investigations of depression [@kleinman1985] despite frequent reports of depression or depression-like behavior in a wide range of societies [@haroz2017; @liu2020] and the potential for cross-cultural research to help understand depressive states [@haroz2017].
+-->
+
 <!-- As they are prohibitively costly for those in minor need, the costs of depression and suicidal behavior may be particularly important in times of substantial conflicts of interest or when the level of support needed to address one's situation is substantial, both of which should be expected to increase the payoff of manipulating others through fake signals.
@@
 
-The primary aim of this study was to examine responses to various forms of emotional signaling in an experimental vignette study.
+The primary aim of this study was to examine responses to emotional signals that varied from low to high cost, in an experimental vignette study in which a possible victim of adversity asks for help from the participant, but has incentives to exaggerate her need.
 In the bargaining framework, the willingness to delay credibly signals the valuation of current cooperative arrangements, with greater delays indicating lower valuations.
-As signal cost increases, and signals therefore become less profitable to fake, we predicted that participants would report (1) increased belief in the signaler's claims and (2) increased likelihood of providing help, with (3) the increased likelihood of providing help mediated by the increased belief in the signaler's need.
-A secondary aim was to investigate a scenario that is common in traditional societies but uncommon in Western societies -- arranged marriages -- where conflicts between parents and offspring often result in depression and suicidality [@SymeEtAl2016]
+As signal cost increased, we predicted that participants would report (1) increased belief in the signaler's claims and (2) increased likelihood of providing help, with (3) the increased likelihood of providing help mediated by the increased belief in the signaler's need.
+
+<!-- A secondary aim was to investigate a scenario that is common in traditional societies but uncommon in Western societies -- arranged marriages -- where conflicts between parents and offspring often result in depression and suicidality [@SymeEtAl2016] -->
 
@@
 
-All participants were over 18, located in the United States or India, and had high quality MTurk metrics [completed at least 100 HITs with a HIT approval rate of over 98%; @kennedy2020].
+All participants were over 18, located in the United States or India, and had high quality MTurk metrics [completed at least 100 HITs with a HIT approval rate of over 98%, @kennedy2020].
 Participants were excluded from the study if (1) they read the vignette too quickly (one-third of the time it took MG to read it), and (2) they failed clearly labeled attentions checks.
@@
 All participants provided informed consent, and the consent form warned that some content might involve sexual assault.
-We estimated the study would take 4-8 minutes to complete for participants who did not take breaks.
+We estimated the study would take 4-8 minutes to complete for participants who did not take breaks [MTurkers commonly multitask, or leave the survey page and return later, @NeckaEtAl2016].
 All participants who passed the attention checks were paid \$1 for their time, for an estimated rate of \$7.50/hr to \$15/hr (75% of US participants completed in `r signif(quantile(d_US$TotalTime, 0.75)/60, 2)` minutes; 75% of Indian participants completed in `r signif(quantile(d_India$TotalTime, 0.75)/60, 2)` minutes).
@@
 For the exact wording of the question and the labels on the sliders, see Table \@ref(tab:outcomes).
+
+We also asked which emotions participants felt the signaler was experiencing using a multiple choice question in which they could select as many options as they would like.
+This included emotions directly related to the signals (e.g., sad, depressed, and suicidal), states which suggest genuine need (traumatized and violated), and states which suggest deception (e.g., deviousness or jealousy).
+The complete list can be found in the SI.
+To further explore the effect of signaling on participants' inferences of the signaler's emotional state, we created two new variables: *Low mood* was the sum of the binary variables *Depressed*, *Distressed* and *Sad*; and *Manipulative* was the sum of the binary variables *Devious* and *Jealous.*
+
+### Time 2: Signals
+
+After rating their beliefs and actions, and which emotions they thought the potential victim was experiencing, participants were randomized into either the control condition or one of four emotional signals by the victim (in order of increasing signal cost): (1) control condition: a verbal request without additional signaling; (2) crying; (3) mild-depression; (4) depression; and (5) a suicide attempt.
+The signals involved the participant encountering the victim some time after the adverse event and observing, e.g., crying, sad expressions, or poor personal hygiene.
+These descriptions did not use the terms depression, depressed, suicidal, or mental health.
+
+The signals were cumulative: crying can be an important feature of depression [for discussion on the relationship between crying and depression see @bylsma2020], and depression is a major risk factor for suicide [@BostwickPankratz2000; @Kessler2012].
+Accordingly, components of less-costly signals were included in more-costly signals.
+Although we use the term 'signals' throughout the paper for brevity, we expect that the hypothesized signals of need, like many signals, would also provide information to others in the form of cues [for discussion on the evolution of signals from cues see: @biernaskie2018; @Tiokhin2016; @Steinkopf2015].
+The full text for the signals are available in the SI.
+
+### Post-treatment measures (T2-T3)
+
+After reading the signaling text, participants answered questions identical to those asked at T1 as the main post-treatment variables of interest (T2).
+For the *Belief*, *Action*, and *Divide* variables, the position of the slider starting where participants placed it at T1.
+T2 emotion multiple-choice questions were identical to those used in T1, as were the composite variables *Low mood* and *Manipulative*.
+
+As both a validity check and a way to understand the degree participants would be willing to help if they believed the participant completely, we presented participants with strong evidence that the claims were true.
+In the US sample, this involved telling participants there was video evidence of the event in question occurring or a similar event after the fact.
+With the thwarted marriage vignette, this involved the participant seeing the man their daughter wants to marry trash talk their daughter and their family.
+Participants were then asked to rate their likelihood of acting (*T3 Action*).
+
+### Demographic Questions
+
+The final part of the survey was a brief demographic questionnaire which asked for (1) the age, (2) sex, (3) number of siblings, (4) number of sons, (5) number of daughters, (6) current relationship status, (7) highest level of education, and (8) the annual household income of each participant.
+
+## Statistical analyses: Preregistered and modified
+
+Our intervention was *signal*, an ordinal variable with the following preregistered rank order: verbal request (control), crying, mild depression, depression, suicide attempt.
+We coded this 5-level ordinal factor variable using default 4th-order orthogonal polynomial contrasts.
+We preregistered a test of our hypothesis that used ordinary least squares (OLS) regression models with the following form:
+
+$$
+\begin{aligned}
+\operatorname{Belief}_{T2} &= \beta_{0} + \beta_{1}(\operatorname{Belief}_{T1}) + \beta_{2}(\operatorname{signal}_{\operatorname{.L}}) + \beta_{3}(\operatorname{signal}_{\operatorname{.Q}})\ + \\
+&\quad \beta_{4}(\operatorname{signal}_{\operatorname{.C}}) + \beta_{5}(\operatorname{signal}_{\operatorname{\text{^}4}})
+\end{aligned}
+$$
+
+$$
+\begin{aligned}
+\operatorname{Action}_{T2} &= \beta_{0} + \beta_{1}(\operatorname{Action}_{T1}) + \beta_{2}(\operatorname{signal}_{\operatorname{.L}}) + \beta_{3}(\operatorname{signal}_{\operatorname{.Q}})\ + \\
+&\quad \beta_{4}(\operatorname{signal}_{\operatorname{.C}}) + \beta_{5}(\operatorname{signal}_{\operatorname{\text{^}4}})
+\end{aligned}
+$$
+
+We predicted that there would be a statistically significant monotonically increasing effect of the signal on *Belief* and *Action*.
+
+We decided to use generalized linear regression models instead of OLS, however, for the following reasons.
+Our pre-test and post-test measures, *T1 & T2 Belief* and *T1 & T2 Action*, were all measured on a 0-100 point scale.
+A substantial number of participants rated their beliefs and actions as exactly 0 or exactly 100 at either T1 or T2.
+OLS linear regression models are not suitable for a closed and bounded distribution with so many values on the boundary because the residuals would not be normally distributed or have constant variance.
+Beta regression, a possible alternative, is only defined on the open interval, (0, 1), whereas our data had many values on the boundaries (a closed interval).
+A variant of beta regression, zero-one inflated beta, is inappropriate because it assumes different processes for the generation of data on the boundaries vs.
+the interior, and we had no reason to believe that our zeros and ones were generated by a different process than the rest of our observations.
+
+We therefore fit models of our two outcome variables (which we rescaled to the continuous interval [0, 1]) in five ways.
+First, we fit the preregistered OLS models (reported in the SI).
+Second, we fit fractional regression models, introduced in a seminal paper by @papke1996 for continuous outcomes on the interval [0, 1], which, in brief, involve fitting a quasi-likelihood version of logistic regression with robust standard errors.
+This method is implemented in the `frm` package [@ramalho2019].
+Third, we fit GLM logistic regression models, computing 95% CI's via bootstrapping, using the `glmmboot` package created to model continuous outcomes on [0, 1] [@humphrey2020].
+Fourth, we fit GLM models with the quasibinomial family and logit link using the `glm` function in R stats library, which can fit continuous outcomes on [0, 1].
+Finally, we computed robust standard errors and 95% confidence intervals from the quasibinomial models using the `sandwich` package [@zeileis2006].
+The estimated coefficients, standard errors, and confidence intervals produced by the latter four methods were *very* similar, and often identical (see Figure \@ref(fig:modelcompareplots).
+We therefore proceeded to fit and report models using `glm` with the quasibinomial family and logit link because model objects produced by this function are compatible with numerous other R packages for summarizing and plotting effects.
+
+Two of our four preregistered OLS regression models included interaction terms between signal and T1 *Belief* and *Action*, with the rationale that the signals might have reduced effect for individuals who indicate high levels of belief and helping at baseline.
+This rationale was less convincing for quasibinomial models using a logit link because the expected interaction -- reduced effect of signals in individuals with high baseline belief -- is inherent to logistic regression: the effect of a predictor on the outcome necessarily diminishes as the outcome approaches 1.
+Our theory does not predict an interaction beyond that already present in a logistic regression model, so we did not include an interaction term in the GLM models (but we still report OLS models with the interaction term).
+
+To test our preregistered hypothesis that the likelihood of acting to help the victim would be largely mediated by a signal's positive impact on the participant's belief in the victim's need, we used the `mediation` package [@tingley2014] to fit a mediation model for *Depression* treatment vs.
+*Verbal request* control.
+See Figure \@ref(fig:medmodel).
+
+```{r medmodel, fig.cap="Possible causal effects of the signal on helping behavior.
+A credible signal of need increases belief that the victim is telling the truth and needs help, which increase the likelihood of helping.
+The direct path from the signal to action represents other causal effects of the signal on observers, such as perceptions of the victim's emotional state (and other factors not measured in this study) that might alter observer behavior."}
+
+knitr::include_graphics('paths.svg')
+```
+
+For specifications of all regression models, see the SI. Our preregistration is here: <https://osf.io/g3s6n>
+
+## Data availibility
+
+The data are available at <http://doi.org/10.5281/zenodo.4637904>
+
+# Results
+
+```{r}
+nationT0 <- table(signaling2020$sample)
+removed <- sum(!signaling2020$CompleteSurvey)
+removed_pct <- 100*signif(removed/nrow(signaling2020), 2)
+nationT1 <- table(d$sample)
+sexT1 <- table(d$Sex)
+n_cond <- xtabs(~signal+vignette, d)
+
+relstatus <- ifelse(str_detect(d$RelStatus, 'Previously'), 'Divorced', d$RelStatus)
+relstatus <- ifelse(str_detect(relstatus, 'Unmarried'), 'Divorced', relstatus)
+relstats <- table(relstatus)
+
+```
+
+The study was started by N=`r nrow(signaling2020)` participants who clicked the link to Qualtrics (`r nationT0['American']` US and `r nationT0['Indian']` India).
+After removing participants who did not finish the survey, failed attention checks, or moved through the study at an unrealistic pace (N=`r removed`, `r removed_pct`%), our final sample was N = `r nrow(d)` (`r nationT1['American']` US and `r nationT1['Indian']` India), with `r sexT1['Male']` males and `r sexT1['Female']` females, `r relstats['Married']` of whom were married or in a long-term relationship, `r relstats['Divorced']` who were divorced, `r relstats['Single']` who were single, and `r relstats['Widowed']` who were widowed.
+The median number of participants per condition was `r median(n_cond)` (min=`r min(n_cond)`, max=`r max(n_cond)`).
+For the number of participants in each condition, see Table \@ref(tab:conditions).
+For summary statistics, see Table \@ref(tab:sumtab).
+For the distributions of participants by age, income, and nationality, see Figure \@ref(fig:socioeconomic).
+
+```{r sumtab}
+
+d$minutes <- d$TotalTime/60
+d$Children <- d$Sons + d$Daughters
+
+vars <- c(
+  Age = 'Age (years)',
+  Income = 'Income (USD)',
+  years_education = 'Education (years)',
+  Children = 'Number of children',
+  minutes = 'Time to complete (minutes)',
+  T1Belief = 'T1 Belief',
+  T1Action = 'T1 Action',
+  T1Divide = 'T1 Division',
+  T1LowMood = 'T1 Low mood',
+  T1Manipulative = 'T1 Manipulative',
+  T2Belief = 'T2 Belief',
+  T2Action = 'T2 Action',
+  T2Divide = 'T2 Division',
+  T2LowMood = 'T2 Low mood',
+  T2Manipulative = 'T2 Manipulative',
+  T3Action = 'T3 Action'
+)
+kable(custom.summarize(d, vars), caption = "Summary statistics for study variables.
+Values that were on a 0-100 scale were rescaled to 0-1.
+Indian participants reported income in rupees, which we converted to USD at the current exchange rate (1 rupee = 0.014 USD).") %>% kable_styling()
+```
+
+## Distributions of beliefs and actions at Time 1
+
+Across the four vignettes, mean belief of the victim was relatively low at baseline (T1), Mean = `r signif(mean(d$T1Belief, na.rm = T), 2)`, albeit with wide variation, SD = `r signif(sd(d$T1Belief, na.rm=T), 2)`; `r sum(d$T1Belief==0)` participants (`r 100*signif(sum(d$T1Belief==0)/nrow(d), 2)`%) rated their belief = 0, and `r sum(d$T1Belief==1)` participants (`r 100*signif(sum(d$T1Belief==1)/nrow(d), 2)`%) rated it as = 1.
+The distribution of likelihood of helping the victim (action) was similar, Mean = `r signif(mean(d$T1Action, na.rm = T), 2)`, SD = `r signif(sd(d$T1Action, na.rm=T), 2)`, with `r sum(d$T1Action==0)` participants (`r 100*signif(sum(d$T1Action==0)/nrow(d), 2)`%) rating their action = 0, and `r sum(d$T1Action==1)` participants (`r 100*signif(sum(d$T1Action==1)/nrow(d), 2)`%) rated action as = 1.
+Although not a pre-registered prediction, *T1 Belief* and *T1 Action* were highly correlated across the four vignettes, consistent with help being worth providing if the signaler's claims were true (see Figure \@ref(fig:t1plot)).
+
+```{r t1plot, fig.width=10, fig.height=10, fig.cap="The distributions of *T1 Belief* vs.*T1 Action*, by vignette.
+Each dot is one participant.
+Original 0-100 values rescaled to 0-1.
+Lines fit by linear regression.
+Dot size indicates the number of overlapping points.
+Black dot is the mean of each variable."}
+plot_T1Belief_T1Action
+```
+
+## Confirmatory: Signals increase beliefs and actions in the predicted rank order
+
+```{r}
+sm1 <- summary(models$Margins$m1)
+suicide_belief_eff <- signif(sm1$AME['signalSuicide attempt']/sd(d$T2Belief), 2)
+
+sm3 <- summary(models$Margins$m3)
+suicide_action_eff <- signif(sm3$AME['signalSuicide attempt']/sd(d$T2Belief), 2)
+
+signal_belief_ttest <- t.test(100*d$T2Belief, 100*d$T1Belief, paired = T)
+signal_action_ttest <- t.test(100*d$T2Action, 100*d$T1Action, paired = T)
+
+```
+
+As predicted, there was a strong statistically significant positive causal effect of the ordinal signal on *T2 Belief* and *T2 Action* (controlling for *T1 Belief* and *T1 Action*, respectively), with the effect of each signal increasing in the predicted rank order (verbal request, crying, mild depression, depression, suicide attempt).
+See Figure \@ref(fig:beliefeffect) and models m1 and m3 in Tables \@ref(tab:regressiontables) and \@ref(tab:anovatables).
+(Results for the preregistered OLS models were very similar; see Figures \@ref(fig:preregbelief) and \@ref(fig:preregbeliefB).)
+
+The marginal between-subjects effect of the high cost *Suicide attempt* vs.
+the *Verbal request* control on T2 *Belief* (averaging over all four vignettes and all values of T1 *Belief*) was an increase of `r fmt_margins(models$Margins$m1, 'signalSuicide attempt')` points on the original 0-100 point scale.
+The equivalent increase for T2 *Action* was `r fmt_margins(models$Margins$m3, 'signalSuicide attempt')` points.
+Given that the standard deviations of T2 *Belief* and *Action* are `r signif(sd(100*d$T2Belief), 2)` and `r signif(sd(100*d$T2Action), 2)`, respectively, these represent increases of `r suicide_belief_eff` and `r suicide_action_eff` SD's, respectively.
+
+```{r beliefeffect, fig.width=6, fig.height=8, fig.cap=paste0("The effect of the signals on *T2 Belief* (top) and *T2 Action* (bottom) controlling for *T1 Belief* and *T1 Action*, respectively.
+Effects plotted for T1 values set to their median value (*T1 Belief*=", median(d$T1Belief, na.rm=T), ", *T1 Action*=", median(d$T1Action, na.rm=T), ").
+Fit using generalized linear regression models with the quasibinomial family.
+Grey bars are 95% CIs.
+For coefficents, p-values, and other statistics, see models m1 and m3 in Tables \\@ref(tab:regressiontables) and \\@ref(tab:anovatables).")}
+(effectsPlots$m1plot + theme(axis.text.x = element_blank()))/effectsPlots$m3plot + plot_layout(ncol = 1) & theme(plot.margin = unit(c(0,0,0,0), units = 'mm'))
+```
+
+<!-- Within-subjects, the average effect across all signals on *Belief* at T2 compared to T1 was `r inline_ttest(signal_belief_ttest)`, and on *Action* was `r inline_ttest(signal_action_ttest)` (on the original 0-100 point scale).
+For the change in *Belief* and *Action* for, T1 to T2 for all participants in all conditions, see Figure @ref(fig:rawbeliefactions2d).
+-->
+
+The within-subject effects of each signal are depicted in Figure \@ref(fig:rawbeliefactions2d).
+
+## Confirmatory: The effect of signals on action is largely mediated by belief
+
+```{r medresults}
+rslts <- all_mediations$results
+
+suicidetotal <- 100*signif(rslts$point[rslts$signal == 'Suicide attempt' & rslts$Stat == 'Total'], 2)
+
+suicidemed <- 100*signif(rslts$n.avg[rslts$signal == 'Suicide attempt' & rslts$Stat == 'Total'], 2)
+
+depressiontotal <- 100*signif(rslts$point[rslts$signal == 'Depression' & rslts$Stat == 'Total'], 2)
+
+depressionmed <- 100*signif(rslts$n.avg[rslts$signal == 'Depression' & rslts$Stat == 'Total'], 2)
+
+```
+
+According to our theoretical model, emotional signals that put cooperative benefits at risk increase observers' belief that the victim is genuinely in need.
+Increased belief then increases the likelihood of helping the victim (action).
+See Figure \@ref(fig:medmodel).
+
+We fit the mediation and outcome models using GLM's with the binomial family as the mediation package does not support the quasibinomial family.
+The total effect of the *Suicide attempt* signal (treatment) vs.
+*Verbal request* (control) on the likelihood of *Action* was to increase it by `r suicidetotal` points from T1 to T2 (on the original 100-point scale).
+Of this increase, `r suicidemed`% was mediated by the increased *Belief* that the victim was telling the truth.
+The total effect of the *Depression* signal (treatment) vs.
+*Verbal request* (control) on the likelihood of *Action* was to increase it by `r depressiontotal` points from T1 to T2.
+Of this increase, `r depressionmed`% was mediated by the increased *Belief* that the victim was telling the truth.
+See Figure \@ref(fig:mediation).
+
+<!-- (Check if med4 or med4b is correct; they look identical to me). -->
+
+```{r mediation, fig.width=8, fig.height=4, fig.cap="The effect of each signal (treatment) vs.
+Verbal request (control) on Action.
+The x-axis is the change in Action on the [0, 1] scale.
+The effects of the signals on Action are largely mediated by Belief (percent mediated on the right).
+The mediation model controlled for *T1 Belief*, and the outcome model controlled for *T1 Belief* and *T1 Action*.
+Both models were GLMs with the binomial family (the mediation package does not support the quasibinomial family).
+ACME: Average causal mediation effect.
+ADE: Average direct effect.
+Total: Total effect (ADE + ACME).
+Bars are 95% CIs."}
+all_mediations$plot
+```
+
+## Exploratory: Costlier signals decrease perceived manipulation and increase perceived low mood
+
+The proportion of participants inferring each emotion in each vignette at T1 is depicted in Figure \@ref(fig:t1emotionheatmap), after each signal at T2 in Figure \@ref(fig:t2emotionheatmap), and the change in proportions from T1 to T2 in Figure \@ref(fig:diffemotions).
+The increase in inferred depression in the *Depression* and *Suicide attempt* conditions, but not the *Verbal request* and *Crying* conditions, helps validate these signals, as does the increase in inferred suicidality in the *Suicide attempt* condition.
+
+The mean change in the *Low mood* and *Manipulative* variables from T1 to T2 for each signal in each vignette reveals a large decrease in inferred *Manipulation* for costly signals, and a large increase in inferred *Low mood* (with the exception of the Thwarted marriage vignette, in which changes are small).
+See Figure \@ref(fig:emotionsplot).
+
+```{r emotionsplot, fig.width=10, fig.height=8, fig.cap="The within-subjects effect of the signals on participants' inferred *Manipulative* and *LowMood* emotional states of the victim, from T1 (arrow base) to T2 (arrow head), for each signal in each of the four vignettes.
+Low mood: higher values indicate lower perceived mood.
+Manipulative: higher values indicate higher perceived manipulativeness.
+Thick arrows: mean change.
+Thin arrows: means of 500 bootstrap resamples."}
+plot_emotions
+```
+
+## Exploratory: Signal effects differ by vignette
+
+```{r}
+
+thwart_sv_bdiff <- visreg_diff(models$Model$m2, 'Thwarted marriage', 'Suicide attempt', 'Verbal request', d)
+
+thwart_sv_adiff <- visreg_diff(models$Model$m4, 'Thwarted marriage', 'Suicide attempt', 'Verbal request', d)
+
+brother_sv_bdiff <- visreg_diff(models$Model$m2, 'Brother-in-law', 'Suicide attempt', 'Verbal request', d)
+
+brother_sv_adiff <- visreg_diff(models$Model$m4, 'Brother-in-law', 'Suicide attempt', 'Verbal request', d)
+
+```
+
+```{r}
+bil_b_suicide <- signif(effect_sizes$est[effect_sizes$id=="Suicide attempt,Brother-in-law" & effect_sizes$Outcome=="Belief"], 2)
+
+rom_b_crying <- signif(effect_sizes$est[effect_sizes$id=="Crying,Romantic partner" & effect_sizes$Outcome=="Belief"], 2)
+
+bil_a_suicide <- signif(effect_sizes2$effsize[effect_sizes2$id=="Suicide attempt,Brother-in-law" & effect_sizes2$Outcome=="Action"], 2)
+
+bil_a_verbal <- signif(effect_sizes2$effsize[effect_sizes2$id=="Verbal request,Brother-in-law" & effect_sizes2$Outcome=="Action"], 2)
+
+```
+
+The effects of the signals on rated beliefs and actions differed substantially by vignette, which we display in three ways for each signal in each vignette: estimated cumulative distributions plots, which show the entire distributions of rated beliefs and actions, including which conditions have high fractions of 0's and 1's (Figures \@ref(fig:ecdf)); regression estimates of the mean effects of the signals on beliefs and actions by vignette (Figure \@ref(fig:beliefvignette)); and between- and within-subjects signal effect sizes by vignette (Figures \@ref(fig:effectsizes) and \@ref(fig:effectsizes2)).
+
+```{r ecdf, fig.width=11, fig.height=6, fig.cap="Empirical cummulative distribution functions for Time 2 Belief (top) and Action (bottom) compared to their Time 1 baseline values (red), by signal and vignette.
+Y-values indicate the fraction of all ratings equal to or less than a given x-value.
+Ratings rescaled to [0, 1].
+Dots indicate median values of Belief and Action, by signal and vignette."}
+ecdf_plot
+```
+
+```{r beliefvignette, fig.width=8, fig.height=8, fig.cap=paste0("The effect of the signals on *T2 Belief* (top) and *T2 Action* (bottom) in each vignette, controlling for T1 values of Belief and Action, respectively.
+Ratings rescaled to [0, 1].
+Effects plotted for T1 values set to their median value (*T1 Belief*=", median(d$T1Belief, na.rm=T), ", *T1 Action*=", median(d$T1Action, na.rm=T), ").
+Fit using generalized linear regression models with the quasibinomial family.
+Grey bars are 95% CIs.
+For coefficents, p-values, and other statistics, see models m2 and m4 in Tables \\@ref(tab:regressiontables) and \\@ref(tab:anovatables).")}
+(effectsPlots$m2plot + theme(axis.text.x = element_blank()))/effectsPlots$m4plot + plot_layout(ncol = 1) & theme(plot.margin = unit(c(0,0,0,0), units = 'mm'))
+```
+
+We note the following patterns in Figure \@ref(fig:ecdf), which we will return to in the Discussion section.
+First, as we intended, the distributions of *Belief* and *Action* in the *Verbal request* control condition were very similar to their distributions at T1 baseline across vignettes.
+In the "Basketball coach" and "Brother-in-law" vignettes, though, their distributions in the *Verbal request* condition were shifted to somewhat lower values relative to baseline (i.e., the verbal request slightly *reduced* belief and action in those vignettes).
+Second, in the "Romantic partner" and "Brother-in-law" vignettes, the effect of *Crying* differed little from *Verbal request*, but in the "Basketball coach" vignette, it differed little from the *Depression* and *Suicide attempt* signals.
+Third, the effect of the *Suicide attempt* signal on *Belief* was similar to that of *Depression* across all vignettes, but had a noticeably greater effect on *Action* in the "Romantic partner" and "Brother-in-law" vignettes.
+Fourth, there was little difference between the effect of the *Mild depression* vs.
+*Depression* signals.
+
+The largest between-subjects effect was *Suicide attempt* vs.
+*Verbal request* control on *Belief* in the "Brother-in-law" vignette, Cohen's d = `r bil_b_suicide`, and the smallest was the effect of *Crying* on *Belief* in the "Romantic partner" vignette, Cohen's d =`r rom_b_crying`.
+The largest within-subjects effect was *Suicide attempt* on *Action* at T2 vs.
+T1 in the "Brother-in-law" vignette, Cohen's d = `r bil_a_suicide`, and the smallest was the *negative* effect of *Verbal request* on *Action* at T2 vs.
+T1 in the "Brother-in-law" vignette, Cohen's d =`r bil_a_verbal`.
+
+## Exploratory: Sociodemographic associations
+
+The sociodemographic variables were strongly confounded with nationality (Indian participants were younger, lower income, with more years of education than US; see Figure \@ref(fig:socioeconomic)), which, in turn, were confounded with vignette (responses in the Indian Thwarted marriage vignette differed substantially from those in the US vignettes).
+We therefore conducted our exploration of the sociodemographic variables separately by nationality.
+
+In the US sample, female participants were more likely to believe and help the victim than male participants, and younger participants were more likely to believe and help the victim than older participants.
+We found no significant effects of *Income*, *Education*, relationship status (e.g., married, single), or number of sons or daughters on *Belief* or *Action*.
+See Figure \@ref(fig:demographicsignal).
+
+```{r demographicsignal, fig.width=11, fig.height=8, fig.cap="Sociodemographic associations with *T2 Belief* (top) and *T2 Action* (bottom) in US participants.
+Each model controlled for *T1 Belief* or *T1 Action*, vignette, Education, and Income.
+Significant associations displayed here.
+Estimated using generalized linear regression models with the quasibinomial family.
+Grey bars are 95% CIs."}
+
+effectsPlots_US$m12plot + 
+    theme(axis.text.x = element_blank()) +
+effectsPlots_US$m12bplot + 
+    theme(
+      axis.text = element_blank(), 
+      axis.title.y = element_blank(), 
+      axis.title.x = element_blank()
+      ) + 
+effectsPlots_US$m13plot + 
+effectsPlots_US$m13bplot +
+    theme(axis.text.y = element_blank(), axis.title.y = element_blank())
+```
+
+In the Indian sample and vignette, in contrast, males were more likely to help the victim than females, those with more years of education were less likely to believe the victim, and there was a marked increase in likelihood of helping among older individuals in the suicide signal condition.
+We found no significant associations with age or income.
+See Figure \@ref(fig:indiademographics).
+
+```{r indiademographics, fig.width=10, fig.height=8, fig.cap="Sociodemographic associations with *T2 Belief* and *T2 Action* in Indian participants (Thwarted marriage vignette).
+Each model included *T1 Belief* or *T1 Action*, Income, Age, Sex, Years of education, and signal.
+Significant associations displayed here.
+Estimated using generalized linear regression models with the quasibinomial family.
+Grey bars are 95% CIs."}
+(effectsPlots_India$m12plot + xlab('Education (years)') + effectsPlots_India$m13plot) / effectsPlots_India$m17plot
+```
+
+## Validity check: T3 increase in Action with proof that victim was telling the truth
+
+```{r}
+t2t3actionttest <- t.test(d$T3Action, d$T2Action, paired = T)
+```
+
+As a partial check on the validity of our methods and results, at T3 we presented participants with strong evidence that the victim was telling the truth, and asked them to again rate their likelihood of acting to help the victim (*T3 Action*).
+Compared to the mean *T2 Action* (M=`r signif(mean(d$T2Action, na.rm=T), 2)`), mean *T3 Action* increased substantially, `r inline_ttest(t2t3actionttest)`.
+Across the US vignettes, likelihood of acting at T3 increased to near-ceiling (M=`r signif(mean(d$T3Action[d$vignette != 'Thwarted marriage']), 2)`), regardless of participants' *T2 Action* values, indicating that propensity to act was indeed contingent on believing the victim.
+In the Indian Thwarted marriage vignette, however, there was little change in *T3 Action* compared to *T2 Action* (Figure \@ref(fig:t3action)), perhaps because Indian participants' beliefs and actions were relatively insensitive to the signals to begin with (Figures \@ref(fig:ecdf) and \@ref(fig:beliefvignette)).
+
+# Discussion
+
+As predicted, in vignettes involving conflicts of interest and private information about the need for help, costly signals of need increased participants' belief in the victim and their likelihood of helping her, with the increase in perceived need and likelihood of helping increasing monotonically with signal cost.
+As predicted, the increase in likelihood of helping was largely mediated by the increase in belief in the victim.
+In an exploratory analysis, costlier signals also decreased perceptions that the victim was manipulative.
+
+These effects were largest in the "brother-in-law" and "romantic partner" vignettes, both of which involved claims of assault against participants' imagined daughters, and smaller in the "basketball coach" and the "thwarted marriage" vignettes.
+The small effect in the "basketball coach" vignette might have been due to the lack of relatedness between participants and the victim (the star player), or how participants weighted the costs of suspending the coach vs.
+punishing a potentially innocent person.
+
+The small signal effect in the "thwarted marriage" vignette, which involved the Indian sample, could indicate that our results do not generalize across cultures, undermining our adaptationist hypothesis.
+It could also reflect our poor understanding of contemporary Indian culture regarding dowry (the effect was larger in older participants).
+Baseline belief in the older daughter, and likelihood of helping her, was relatively high at baseline (`r signif(100*mean(d$T1Belief[d$vignette=='Thwarted marriage']), 2)`%) compared to victims in the other vignettes.
+Private information and conflict therefore probably played a smaller role and thus costly signals were less necessary.
+We observed a similar pattern in our pilot study, in which baseline belief in the victim's need was high, and costly signals had smaller effects than they did in the current study.
+Additionally, supporting the older daughter came at the cost of one's younger daughter, which may also help explain the relatively small signal effects.
+A final consideration is that data from the Indian sample appeared to be of lower quality, limiting our confidence in any of these interpretations (see limitations for more information).
+
+In the "brother-in-law" and "romantic partner" scenarios, *Crying* had little effect on the magnitude of pro-victim responses relative to *Verbal request*, suggesting it was not costly enough to serve as a reliable signal in times of substantial conflicts of interests.
+In contrast, both *Depression* conditions increased support, albeit to similar degrees.
+One potential reason for this is the increase in symptoms from mild depression to depression was not costly enough to result in a large effect, as the symptoms differed little in severity (e.g., grades dropping from As to Bs in *Mild depression* vs.
+Cs in *Depression*).
+Such small changes may be less impactful in vignettes than in real-life, where the effects of signaling may increase in severity as they persist over a lengthy period of time.
+
+The effect of *Suicide attempt* on belief at T2 was similar to the *Depression* conditions across vignettes, but it resulted in greater likelihood of support.
+One interpretation is that although some participants did not believe the victim's story, her signal nevertheless convinced them that she needed help.
+For example, maybe the brother-in-law did not assault her, but the presence of his family in her home was causing genuine distress.
+Support for this interpretation comes from our mediation analyses, which showed that the likelihood of help was largely, but not entirely, mediated by signal's effect on belief in need.
+
+There were minor associations of age and sex with belief and action in the US participants, with both being higher among females and younger individuals.
+The US vignettes all involved assaults against young women, which might have been more salient to female and younger participants.
+In the Indian sample, high baseline belief and action were somewhat lower among those with more education and among females, respectively.
+Costlier signals, suicidality in particular, had a larger effect among older individuals, perhaps because older individuals were more likely to have children of marriageable age, like the victim in the vignette.
+
+Finally, after the T3 evidence that the victim was telling the truth, likelihood of helping by the US participants increased to near ceiling, an effect that helped validate our vignettes.
+Among Indian participants, in contrast, participants only slightly increased their likelihood of helping from their T2 level.
+One interpretation of the latter is that Indian participants tended to believe the older daughter anyway, so their decision to help was not changed by additional information.
+
+<!-- Overall, our results on the connection between belief in need and likelihood of help are consistent with costly signaling and bargaining approaches to depression and suicide.
+At T1, *Belief* and *Action* were highly correlated yet distinct; while at T2, the effect of signal on both *Belief* and *Action* was to increase the magnitude of pro-signaler responses, with the effect of signal on *T2 Action* being largely mediated by signal's effect on belief in need.
+This relationship between belief in need and likelihood of support and the importance of signal cost should be expected in scenarios when a target of a signal of need would benefit from helping if the signaler's need was genuine but face substantial net costs if it was not.
+Importantly, such scenarios appear to be common among modern humans and have likely been since individuals could increase their inclusive fitness through supporting kin or important cooperative partners who could return to providing benefits to supporters once their situation returned to normal [@SugiyamaSugiyama2003; @tooby1996].
+-->
+
+<!-- Although this study was not designed to examine whether the costs of signaling would be made up for by the increased support stemming from depression and suicide attempts directly, the results are consistent with this hypothesis.
+In general, the costs required to honestly convey one's qualities should be expected to increase with the potential payoffs of deception and the number of defectors within the broader population [@Rosenthal1993], with the vignettes in this study emphasizing the existence of private information and sizable conflicts of interest to increase the perceived risk of being taken advantage of.
+In similar real-world scenarios, this difficulty of signaling honest need would coincide with the substantial fitness-relevant benefits of preventing future assaults or being able to marry the partner of one's choice.
+These benefits coupled with the fact that depression and suicide attempts become relatively less costly to one's fitness prospects with increased need [@Hagen2003], suggest that the increased support seen in this study may be worth the costs required to signal need more often than is often appreciated when counting the entire costs of depression as the signal rather than only the upregulation of symptoms for a communicative purpose.
+-->
+
+## Limitations
+
+The main limitation of this study is that is has less ecological validity than real-world observations of depressed individuals interacting with their social partners.
+This may have biased results in a pro-signaler direction if the lack of real costs of helping made support feel less costly or if there was a social desirability bias toward helping [@grimm2010].
+It may have also biased participants against helping if they could not fully imagine the characters in the story as kin or important cooperative partners, and the survey's short duration may have weakened the strength of the costlier signals as bargaining tools.
+
+Our design did not include vignettes with male signalers.
+For this reason, we have no data on the possibility of sex differences in the effectiveness of the signaling strategies examined.
+Although not predicted theoretically, such differences are possible if the costs of signaling vary between the sexes due to differential access to alternative bargaining strategies [@HagenRosenstrom2016] or if one sex tends to suffer greater negative reputational effects  when displaying the emotions and behaviors in the vignettes.
+It is also possible the costliness of the situations presented in the vignettes differ by sex.
+
+Compared to the US sample, far more Indian participants failed our attention checks, which is consistent with botting, unfamiliarity with English, or low-effort responses [@kennedy2020].
+If this high failure rate indicates lower-quality responses among those who passed the attention checks, the weak signal effect in the thwarted marriage vignette may simply be due to greater noise rather than differences in the scenario or the effectiveness of the signals compared to those in the US.
+Another concern relevant to all vignettes is that our decision to anchor the T1 sliders at 0 may have resulted in participants being more likely to report extreme values.
+
+<!-- Slider anchor  -->
+<!-- Regex: stopped in SI -->
+<!-- T\d \w+ -->
+
+# Conclusion
+
+Depression is costly, sometimes resulting in death by suicide.
+Our results suggest that these costs, which mainstream theories take as evidence of brain dysfunction [@SymeHagen2021], function to help victims of adversity elicit support when their true level of need is private information and they have conflicts with social partners.
+These findings align with real-world evidence that depression simultaneously elicits positive and negative responses from social partners [@SymeHagen2021].
+If the bargaining model is correct, depression is an important social problem, not a medical one [@syme2020].
+
+<!-- This coupled with , suggests that more attention should be paid to the potential for positive responses towards depressed individuals, especially from social partners who receive substantial benefits from the depressed or suicidal individual.
+-->
+
+ <!-- The need to explain suicide's connection to depression is often overlooked by explanations for major depression, particularly those which propose non-signaling functions.
+One explanation for their connection, is that both suicidality and depression may function to limit negative fitness outcomes in times of substantial adversity [@andrews2006; @Hagen2002; @Hagen2003; @HagenEtAl2008; @nock2008; @Rosenthal1993; @Stengel1956; @SymeEtAl2016], with costlier signals being required to elicit support when the payoffs to faking need are high enough so that less costly signals are not reliable indicators of one's need [@Rosenthal1993].
+For this hypothesis to be correct, instrumental support would need to be provided frequently enough with large enough impacts so that the costs of signaling are outweighed by the benefits on average.
+In support of this, we found exposure to depression and suicide attempts resulted in greater belief in need and increased likelihood of support in fictional scenarios.
+-->
+
+# Acknowledgements
+
+This study was funded through a Washington State University, Vancouver Research Mini Grant.
+We thank Anne Pisor, Darcy Bird, and members of the Hagen lab group for numerous helpful comments.
+We also thank XX and YY [pending permission to acknowledge] for feedback on the Thwarted marriage vignette.
+
+<!-- # To do: -->
+
+<!-- -   victim or signaler? -->
+<!-- -   add anger -->
+<!-- -   Intro "State the objectives of the work and provide an adequate background, avoiding a detailed literature survey or a summary of the results." -->
+<!-- -   Discussion " This should explore the significance of the results of the work, not repeat them.
+A combined Results and Discussion section is often appropriate.
+Avoid extensive citations and discussion of published literature." -->
+<!-- -   mention asking for prefered sex -->
+
+<!-- # Notes from my meeting with Anne -->
+
+<!-- -   Table detailing the cooperative endeavor (maybe word as boundedness of fate), conflict of interest, and what the private information is about would be useful. -->
+<!-- -   Calling verbal request control when it's a treatment? -->
+<!-- -   Can shift much of the pilot studies info to SI with some detail post line 279 in draft she saw. -->
+<!-- -   Cumulative distribution plot: needs more info in captions. could benefit from fig6a and fig6b (confusion over x and y axes) -->
+
+# Supplementary information
+
+## Pilot studies
+
+We conducted two pilot studies, one on MTurk with a large sample size (N=`r nrow(signalingdata2018b)`), and one on [reddit.com/r/SampleSize](https://reddit.com/r/SampleSize) with a small sample size (N=28).
+Both studies used the experimental pre-test, post-test design used in the current study.
+
+In the MTurk study, participants read a vignette that put them in situations in which an imagined sister was requesting a loan of \$50,000 from the participant that was originally saved for the participant's imagined daughter's college education.
+The sister claims the money is needed for medical treatment for her own child, but she has incentives to deceive.
+The manipulations were signals very similar to those used in this study, and the outcomes were belief that the sister really needed the money and intention to loan her the money.
+See XX for the full write-up.
+See <https://osf.io/3rg8b> for preregistration of the pilot study.
+See <http://doi.org/10.5281/zenodo.4637883> for pilot data.
+
+```{r piloteffects, fig.width=10, fig.cap="Pilot study effect of the signals.
+A.
+Effect of signal on Belief at T2, controlling for Belief at T1.
+B: Proportion of participants who inferred the victim was mentally ill.
+Fit with a generalized linear model with the quasibinomial family."}
+pilot_results$effectplot + (pilot_results$mentalplot + theme(axis.text.y = element_blank())) + plot_annotation(tag_levels = 'A')
+```
+
+In the small reddit.com study, participants viewed and responded to two vignettes used here, each with a different signal.
+
+We learned six major lessons from the MTurk pilot study that influenced the design of the current study.
+First, as predicted, belief in the sister's need was highest in the *Depression* condition and lowest in the *Verbal request* condition, giving us confidence to continue this research (see Figure \@ref(fig:piloteffects)).
+Second, to rule out that believability and willingness to help were simply artifacts of the sister's psychiatric distress, we included a "signaling" condition in which the sister exhibited schizophrenic symptoms.
+As predicted, believability and willingness to help in this condition were dramatically lower than in any other condition, ruling out this alternative explanation.
+We therefore did not include the schizophrenic condition in the current study.
+Third, baseline (T1) believability was very high (mean = `r signif(pilot_results$meanT1belief, 2)` and median = `r signif(pilot_results$medianT1belief, 2)` on a 0-100 point scale), leaving little scope for signals to increase believability.
+In the current study we therefore endeavored to provide details in the vignettes that would undermine the victim's believability at baseline.
+Fourth, contrary to our hypothesis, the *Suicide threat* and *Suicide attempt* signals reduced believability relative to *Depression*.
+We surmised that the sister's adversity -- a sick child -- was not sufficient to justify a suicide attempt, thus undermining her believability.
+In the current study the signaler herself is therefore the victim, and the forms of adversity -- physical and sexual assault and thwarted and forced marriage -- are those that are frequently associated with suicidality.
+Fifth, the content of the vignette matters, so instead of a single vignette we decided to use four different vignettes to help determine the extent to which signaling effects were sensitive to seemingly irrelevant details of the vignettes.
+Sixth, in a pre-test post-test design, the control condition should be identical to the treatment condition in every respect except for the factor being tested, which in this study was signal cost.
+Post hoc, we realized that the control condition in the pilot study differed substantially from the treatment condition beyond signal cost: in the treatment conditions, participants encountered the sister twice: once when she requests help, and a second time when she signals.
+In our faulty control, participants only encountered the sister once, when she requests help, with no second encounter.
+In this study we therefore ensured that the control condition (Verbal request) was identical to the treatment conditions except for signal cost.
+
+In the reddit.com pilot study, participants viewed two vignettes (with different signals in each one), and responded with lower belief to the second vignette compared to the first regardless of the vignette or signal.
+To avoid such order effects, which are a common problem in vignette studies that use multiple vignettes [@su2020], we decided to present each participant in the current study with a single vignette and signal.
+
+## Power from MTurk pilot study
+
+We estimated power using our MTurk pilot study data to compare the effect of the *Mild depression* signal vs.
+the *Verbal request* control on *Belief* (that the sister needed the money) at T2 controlling for *Belief* at T1 in a linear regression model.
+Specifically, we resampled the pilot data with replacement, fit the linear regression model, and extracted the p-value for the signal coefficient, repeating this 2000 times for each sample size ranging from N=20 to N=200.
+Power was computed as the proportion of p-values \< 0.05.
+Power was about 80% for a sample size of about `r pwr80_90[[1,1]]`, and was about 90% for a sample size of about `r pwr80_90[[1,2]]`.
+See Figure \@ref(fig:power).
+
+```{r power, fig.cap="Power curve for between-subjects effect of Mild depression vs. Verbal request signal on T2 Belief, controlling for T1 Belief."}
+
+smplesize <- nrow(d)/10
+
+ggplot(power_curve, aes(sample_size, power)) +
+  geom_line() +
+  geom_vline(xintercept = smplesize, linetype = 'dotted') +
+  annotate(geom = 'text', x = smplesize + 3, y = 0.75, label = 'Current study sample size', hjust = 0) +
+  labs(x = '\n Sample size', y = 'Power\n') +
+  theme_minimal(15) + theme(axis.title.y = element_text(angle = 0))
+```
+
+<!-- Second, for participants in the *Depression* condition only, we compared their T2 Belief to their T1 Belief using a paired t-test (in the full pilot data, *Depression* increased belief by about 8 points on a 100 point scale).
+We again resampled our pilot data 2000 times for each sample size from N=20 to N=200.
+Power was about 80% for a sample size of 125, and about 90% for a sample size of 175.
+-->
+
+```{r power2, fig.cap="Power curve for within-subjects effect of Depression signal on *T2 Belief* relative to *T1 Belief*."}
+  # ggplot(power_curve2, aes(sample_size, power)) +
+  #   geom_line() +
+  #   labs(x = '\n Sample size', y = 'Power\n') +
+  #   theme_minimal(15)
+```
+
+## Vignettes of the current study (main bodies and signals)
+
+### Basketball coach
+
+Imagine yourself in the following scenario:
+
+You are a college athletic director at a university with a long history of success in women's basketball.
+Unfortunately, despite quality players, the team struggled for the first three years of your leadership.
+You came close to losing your job but were given two more years to turn things around.
+You immediately hired a new head coach who you had spotted coaching a low-ranked college team that punched above its weight.
+Two years later, your team is one of the best in the country and has attracted a top recruit who has become the star player on your team and is probably the best player in the country.
+You have been told that if the team makes it to the final rounds of the playoff tournament, the university will offer you a high paying contract extension.
+
+Your star player is hard to deal with, however.
+She is constantly jealous of other players, and often comes to your office to complain that the coach unfairly limits her playing time, claiming this will ruin her chances of going professional.
+The star player has also posted self-serving accounts of your discussions with her on social media.
+
+A few days ago, after the coach started a new player in one game, the star player went to the police and accused the coach, a physically powerful man, of cornering her in the locker room one night and forcibly kissing her and grabbing her body.
+The coach strongly denies the allegation, and the police said they do not have any evidence to corroborate the player's accusation.
+
+You reached out to other players on the team, all of whom say that the relationship between the coach and star player has always seemed professional, and they are shocked by the allegation.
+None of the other players have any complaints about the coach.
+On the contrary, the other players praise the coach for leading everyone into the playoffs.
+They mention that the star player is a prima donna, but they are worried that if either the coach or the star player miss the playoffs, it will hurt everyone's chances of making it to the championships.
+
+You find out that the star player then told the university president that she feared the coach might attack her again, and asked her to replace the coach with one of his assistants, who you know wants the star player to have more playing time.
+The president refused, saying there was no evidence of wrongdoing.
+
+#### Signals
+
+##### Verbal request
+
+A week later the coach informs you that the star player's performance in games is excellent, helping the team's performance and her reputation with pro scouts.
+Later that day, there is a formal luncheon at the athlete dorm to introduce the coaches and members of each team to the alumni.
+The alumni are especially interested in meeting the basketball coach and members of the basketball team because they are in the playoffs.
+You notice your star player is not there, but you see her roommate, a member of the swim team.
+She tells you that you should talk to your star player in person, and she leads you to their dorm room.
+
+When you arrive, the two of you find her sitting on her bed.
+She appears fit, well-rested, and her room is clean.
+She looks calm with her hands folded as she asks you to replace the coach, saying she can't attend the luncheon if he is there.
+
+##### Crying
+
+A week later the coach informs you that the star player's performance in games is excellent, helping the team's performance and her reputation with pro scouts.
+Later that day, there is a formal luncheon at the athlete dorm to introduce the coaches and members of each team to the alumni.
+The alumni are especially interested in meeting the basketball coach and members of the basketball team because they are in the playoffs.
+You notice your star player is not there, but you see her roommate, a member of the swim team.
+She tells you that you should talk to your star player in person, and she leads you to their dorm room.
+
+When you arrive, the two of you find her sitting on her bed.
+She appears fit and well-rested, and her room is clean.
+She looks sad and begins sobbing as she asks you to replace the coach, saying she can't attend the luncheon if he is there.
+
+##### Mild-depression (crying with behavioral changes)
+
+A week later the coach informs you that the star player's performance in games is OK and not harming the team's performance and her reputation with pro scouts.
+Later that day, there is a formal luncheon at the athlete dorm to introduce the coaches and members of each team to the alumni.
+The alumni are especially interested in meeting the basketball coach and members of the basketball team because they are in the playoffs.
+You notice your star player is not there, but you see her roommate, a member of the swim team.
+She tells you that you should talk to your star player in person, and she leads you to their dorm room.
+
+When you arrive, the two of you find her sitting on her bed.
+Her room is a little messy and she appears a little less fit than you remember, while also seeming slightly tired.
+She looks sad and begins sobbing as she asks you to replace the coach, saying she can't attend the luncheon if he is there.
+
+##### Depression
+
+A week later the coach informs you that the star player's performance in games is poor, harming the team's performance and her reputation with pro scouts.
+Later that day, there is a formal luncheon at the athlete dorm to introduce the coaches and members of each team to the alumni.
+The alumni are especially interested in meeting the basketball coach and members of the basketball team because they are in the playoffs.
+You notice your star player is not there, but you see her roommate, a member of the swim team.
+She tells you that you should talk to your star player in person, and she leads you to their dorm room.
+
+When you arrive, the two of you find her slouched on her bed.
+Her room is a mess, and you notice she has lost weight and looks fatigued.
+She looks sad and begins sobbing and wringing her hands as she asks you to replace the coach, saying she can't attend the luncheon if he is there.
+
+##### Suicide attempt
+
+A week later the coach informs you that the star player's performance in games is poor, harming the team's performance and her reputation with pro scouts.
+Later that day, there is a formal luncheon at the athlete dorm to introduce the coaches and members of each team to the alumni.
+The alumni are especially interested in meeting the basketball coach and members of the basketball team because they are in the playoffs.
+You notice your star player is not there, but you see her roommate, a member of the swim team.
+She tells you that you should talk to your star player in person, and she leads you to their dorm room.
+
+When you arrive, the two of you find her passed out on her bed.
+The room is a mess, and you notice she has lost weight.
+Her roommate tries to wake her up, but she doesn't respond.
+You see an empty bottle of OxyContin painkillers on the table and immediately call 911.
+That evening you visit her in the hospital.
+Her doctor tells you she almost died, and then leaves the two of you alone.
+The star player begins sobbing as she asks you to replace the coach.
+
+### Brother-in-law
+
+Imagine yourself in the following scenario:
+
+You are the single parent of a 15-year-old girl. Your relationship with her has always been full of conflict. She is very self-centered, and the two of you fight frequently.
+
+Recently, your sister lost her house in a fire and was having difficulty finding a place for her family to live because many other families also lost their homes.
+You are very close with your sister and brother-in-law, who helped you escape your abusive ex-partner.
+You have a large house with several extra bedrooms, so you decide to let your sister, your brother-in-law, and your teenage niece move in while they look for more permanent housing.
+
+(page break)
+
+Unfortunately, your daughter and your niece are not getting along.
+They have to share a bathroom, and your daughter complains constantly that she is in there too long.
+Your daughter is also jealous that her cousin has expensive clothes, a designer handbag, and a new iPhone, all of which are nicer than your daughter's.
+
+One day your daughter had a party at your house with many of her friends.
+You noticed that your niece was very popular and got a lot of attention, especially from your daughter's friends and boyfriend.
+You could tell that your daughter was upset.
+After the party, your daughter tells you that her cousin is a bitch who is trying to steal her boyfriend.
+However, you saw that your niece was trying to avoid interacting with the boyfriend.
+
+(page break)
+
+Later, your daughter complained that your brother-in-law was looking at her body.
+A few days later, while grocery shopping, you got a text from your daughter saying that your brother-in-law tried to get into the bathroom while she was showering and came into her room while she was changing.
+She says that she does not feel safe and wants your sister and her family to leave.
+However, you know your daughter will exaggerate to get her way.
+
+The next week, your daughter comes to you saying your brother-in-law groped her as they passed in the hallway and that she wants your sister's family to leave immediately.
+You confront your brother-in-law due to the severity of your daughter's allegation.
+He strongly denies it.
+
+That night, you call your mother who says your daughter has long been jealous of her cousin.
+She reminds you that you've taken your daughter's side before and been burned when you found out your daughter wasn't telling the whole truth.
+She reminds you of the difficult situation your sister's family is in.
+
+#### Signals
+
+##### Verbal request
+
+Your daughter has appeared normal since her claims about your brother-in-law.
+She has still looked fit and put the same amount of effort into her appearance, always wearing clean clothes and spending time on her hair.
+She has also slept about the same amount of time as normal and remained active throughout the day.
+
+Her demeanor has also remained normal.
+She has generally appeared calm and has been able to maintain her concentration.
+She has also done her homework on time and maintained an A in all her classes as she always has in the past.
+
+When the two of you talk about your brother-in-law, she remains calm and asks you to kick him out.
+
+##### Crying
+
+Your daughter has appeared normal since her claims about your brother-in-law.
+She has still looked fit and put the same amount of effort into her appearance, always wearing clean clothes and spending time on her hair.
+She has also slept about the same amount of time as normal and remained active throughout the day.
+
+Her demeanor has also remained normal.
+She has generally appeared calm and has been able to maintain her concentration.
+She has also done her homework on time and maintained an A in all her classes as she always has in the past.
+
+When the two of you talk about your brother-in-law, she starts sobbing and asks you to kick him out.
+
+##### Mild-depression (crying with behavioral changes)
+
+Your daughter has appeared sad since her claims about your brother-in-law.
+She has looked a little less fit and has put less effort into her appearance, occasionally wearing dirty clothes and sometimes not doing her hair.
+She has also sometimes woken up late and has seemed a little less active than normal.
+
+Her demeanor has also changed slightly.
+She has occasionally gotten distressed and has seemed distracted.
+She has also missed a few assignments and her grades dropped from straight A's to a B average for the first time in her life.
+
+When the two of you talk about your brother-in-law, she starts sobbing and asks you to kick him out.
+
+##### Depression
+
+Your daughter started to appear noticeably different since her claims about your brother-in-law.
+She has lost weight and has been putting no effort into her appearance, often wearing dirty clothes and rarely doing her hair.
+She has also slept more than normal but still seemed tired and inactive.
+
+Her demeanor also changed drastically.
+She has often gotten distressed and has had difficulty maintaining her concentration.
+She has also missed multiple assignments, and her grades dropped from straight A's to a C average for the first time in her life.
+
+When the two of you talk about your brother-in-law, she starts sobbing and asks you to kick him out.
+
+##### Suicide attempt
+
+Your daughter started to appear noticeably different since her claims about your brother-in-law.
+She has lost weight and has been putting no effort into her appearance, often wearing dirty clothes and rarely doing her hair.
+She has also slept more than normal but still seemed tired and inactive.
+
+Her demeanor also changed drastically.
+She has often gotten distressed and has had difficulty maintaining her concentration.
+She has also missed multiple assignments, and her grades dropped from straight A's to a C average for the first time in her life.
+
+When the two of you talk about your brother-in-law, she starts sobbing and asks you to kick him out.
+Then, this past week, you and your daughter went through a traumatic experience when your daughter attempted suicide.
+You rushed her to the hospital, where she was placed in critical but stable condition.
+
+### Romantic Partner (pronouns match sex participants reported primary attraction to)
+
+Imagine yourself in the following scenario:
+
+You are a single parent of a 13-year-old girl.
+The two of you have lived alone together for the past five years since your breakup with her [father/mother].
+During this time, finding potential partners has been difficult.
+
+Recently, you have gotten closer with a new [man/woman].
+[He/She] is very attractive, has a good job, and has treated you better than anyone before.
+Confident that you will marry soon, the two of you decide to move in together.
+
+Your daughter, who wants you to get back together with her [dad/mom], is not happy about this.
+She frequently complains whenever your boyfriend comes over and is extremely rude and avoidant.
+In previous relationships, such behavior has driven others away.
+However, your partner says [he/she] is committed to this relationship and to establishing a bond with your daughter.
+
+After a month of living together with your partner, things have only gotten worse. Your daughter is almost always upset and has treated you partner worse than others in the past.
+
+One night, she accused your partner of hitting her multiple times.
+You ask if she has any bruises or injuries, but she says she doesn't.
+Despite this, she maintains that she was hit and says she doesn't know why there aren't any marks on her.
+
+You bring up the accusation with your partner, and [he/she] denies it, saying that [he/she] would never hurt her and that this is just a way for her to split the two of you up.
+
+### Measureing Beliefs and Actions
 
@@
 
-We also asked which emotions participants felt the signaler was experiencing using a multiple choice question in which they could select as many options as they would like.
-This included emotions directly related to the signals (e.g., sad, depressed, and suicidal), states which suggest genuine need (traumatized and violated), and states which suggest deception (e.g., deviousness or jealousy).
-The complete list can be found in the SI.
-To further explore the effect of signaling on participants' inferences of the signaler's emotional state, we created two new variables: *Low mood* was the sum of the binary variables *Depressed*, *Distressed* and *Sad*; and *Manipulative* was the sum of the binary variables *Devious* and *Jealous.*
-
-### Time 2: Signals
-
-After rating their beliefs and actions, participants were randomized into either the control condition or one of four emotional signals by the victim (in order of increasing signal cost): (1) control condition: a verbal request without additional signaling; (2) crying; (3) mild-depression; (4) depression; and (5) a suicide attempt.
-The signals involve the participant encountering the victim some time after the adverse event and observing, e.g., crying, sad expressions, or poor personal hygiene.
-These descriptions do not use the terms depression, depressed, suicidal, or mental health.
-
-The signals were cumulative: crying can be an important feature of depression [for discussion on the relationship between crying and depression see @bylsma2020], and depression is a major risk factor for suicide [@BostwickPankratz2000; @Kessler2012].
-Accordingly, components of less-costly signals were included in more-costly signals.
-Although we use the term 'signals' throughout the paper for brevity, we expect that the hypothesized signals of need, like many signals, would also provide information to others in the form of cues [for discussion on the evolution of signals from cues see: @biernaskie2018; @Tiokhin2016; @Steinkopf2015].
-The full text for the signals are available in the SI.
-
-### Post-treatment measures (T2-T3)
-
-After reading the signaling text, participants answered questions identical to those asked at T1 as the main post-treatment variables of interest (T2).
-For the *Belief*, *Action*, and *Divide* variables, the position of the slider starting where participants placed it at T1.
-T2 emotion multiple-choice questions were identical to those used in T1, as were the composite variables *Low mood* and *Manipulative*.
-
-As both a validity check and a way to understand the degree participants would be willing to help if they believed the participant completely, we presented participants with strong evidence that the claims were true (*T3 Action*).
-In the US sample, this involved telling participants there was video evidence of the event in question occurring or a similar event after the fact.
-With the thwarted marriage vignette, this involved the participant seeing the man their daughter wants to marry trash talk their daughter and their family.
-
-### Demographic Questions
-
-The final part of the survey was a brief demographic questionnaire which asked for (1) the age, (2) sex, (3) number of siblings, (4) number of sons, (5) number of daughters, (6) current relationship status, (7) highest level of education, and (8) the annual household income of each participant.
-
-## Statistical analyses: Preregistered and modified
-
-Our intervention was *signal*, an ordinal variable with the following preregistered rank order: verbal request (control), crying, mild depression, depression, suicide attempt.
-We coded this 5-level ordinal factor variable using default 4th-order orthogonal polynomial contrasts.
-We preregistered a test of our hypothesis that used ordinary least squares (OLS) regression models with the following form:
-
-$$
-\begin{aligned}
-\operatorname{Belief}_{T2} &= \beta_{0} + \beta_{1}(\operatorname{Belief}_{T1}) + \beta_{2}(\operatorname{signal}_{\operatorname{.L}}) + \beta_{3}(\operatorname{signal}_{\operatorname{.Q}})\ + \\
-&\quad \beta_{4}(\operatorname{signal}_{\operatorname{.C}}) + \beta_{5}(\operatorname{signal}_{\operatorname{\text{^}4}})
-\end{aligned}
-$$
-
-$$
-\begin{aligned}
-\operatorname{Action}_{T2} &= \beta_{0} + \beta_{1}(\operatorname{Action}_{T1}) + \beta_{2}(\operatorname{signal}_{\operatorname{.L}}) + \beta_{3}(\operatorname{signal}_{\operatorname{.Q}})\ + \\
-&\quad \beta_{4}(\operatorname{signal}_{\operatorname{.C}}) + \beta_{5}(\operatorname{signal}_{\operatorname{\text{^}4}})
-\end{aligned}
-$$
-
-We predicted that there would be a statistically significant monotonically increasing effect of the signal on *Belief* and *Action*.
-
-We decided to use generalized linear regression models instead of OLS, however, for the following reasons.
-Our pre-test and post-test measures, *T1 & T2 Belief* and *T1 & T2 Action*, were all measured on a 0-100 point scale.
-A substantial number of participants rated their beliefs and actions as exactly 0 or exactly 100 at either T1 or T2.
-OLS linear regression models are not suitable for a closed and bounded distribution with so many values on the boundary because the residuals would not be normally distributed or have constant variance.
-Beta regression, a possible alternative, is only defined on the open interval, (0, 1), whereas our data had many values on the boundaries (a closed interval).
-A variant of beta regression, zero-one inflated beta, is inappropriate because it assumes different processes for the generation of data on the boundaries vs.
-the interior, and we had no reason to believe that our zeros and ones were generated by a different process than the rest of our observations.
-
-We therefore fit models of our two outcome variables (which we rescaled to the continuous interval [0, 1]) in five ways.
-First, we fit the preregistered OLS models (reported in the SI).
-Second, we fit fractional regression models, introduced in a seminal paper by @papke1996 for continuous outcomes on the interval [0, 1], which, in brief, involve fitting a quasi-likelihood version of logistic regression with robust standard errors.
-This method is implemented in the `frm` package [@ramalho2019].
-Third, we fit GLM logistic regression models, computing 95% CI's via bootstrapping, using the `glmmboot` package created to model continuous outcomes on [0, 1] [@humphrey2020].
-Fourth, we fit GLM models with the quasibinomial family and logit link using the `glm` function in R stats library, which can fit continuous outcomes on [0, 1].
-Finally, we computed robust standard errors and 95% confidence intervals from the quasibinomial models using the `sandwich` package [@zeileis2006].
-The estimated coefficients, standard errors, and confidence intervals produced by the latter four methods were *very* similar, and often identical (see Figure \@ref(fig:modelcompareplots).
-We therefore proceeded to fit and report models using `glm` with the quasibinomial family and logit link because model objects produced by this function are compatible with numerous other R packages for summarizing and plotting effects.
-
-Two of our four preregistered OLS regression models included interaction terms between signal and T1 *Belief* and *Action*, with the rationale that the signals might have reduced effect for individuals who indicate high levels of belief and helping at baseline.
-This rationale was less convincing for quasibinomial models using a logit link because the expected interaction -- reduced effect of signals in individuals with high baseline belief -- is inherent to logistic regression: the effect of a predictor on the outcome necessarily diminishes as the outcome approaches 1.
-Our theory does not predict an interaction beyond that already present in a logistic regression model, so we did not include an interaction term in the GLM models (but we still report OLS models with the interaction term).
-
-To test our preregistered hypothesis that the likelihood of acting to help the victim would be largely mediated by a signal's positive impact on the participant's belief in the victim's need, we used the `mediation` package [@tingley2014] to fit a mediation model for *Depression* treatment vs.
-*Verbal request* control.
-See Figure \@ref(fig:medmodel).
-
-```{r medmodel, fig.cap="Possible causal effects of the signal on helping behavior.
-A credible signal of need increases belief that the victim is telling the truth and needs help, which increase the likelihood of helping.
-The direct path from the signal to action represents other causal effects of the signal on observers, such as perceptions of the victim's emotional state (and other factors not measured in this study) that might alter observer behavior."}
-
-knitr::include_graphics('paths.svg')
-```
-
-For specifications of all regression models, see the SI. Our preregistration is here: <https://osf.io/g3s6n>
-
-## Data availibility
-
-The data are available at <http://doi.org/10.5281/zenodo.4637904>
-
-# Results
-
-```{r}
-nationT0 <- table(signaling2020$sample)
-removed <- sum(!signaling2020$CompleteSurvey)
-removed_pct <- 100*signif(removed/nrow(signaling2020), 2)
-nationT1 <- table(d$sample)
-sexT1 <- table(d$Sex)
-n_cond <- xtabs(~signal+vignette, d)
-
-relstatus <- ifelse(str_detect(d$RelStatus, 'Previously'), 'Divorced', d$RelStatus)
-relstatus <- ifelse(str_detect(relstatus, 'Unmarried'), 'Divorced', relstatus)
-relstats <- table(relstatus)
-
-```
-
-The study was started by N=`r nrow(signaling2020)` participants who clicked the link to Qualtrics (`r nationT0['American']` US and `r nationT0['Indian']` India).
-After removing participants who did not finish the survey, failed attention checks, or moved through the study at an unrealistic pace (N=`r removed`, `r removed_pct`%), our final sample was N = `r nrow(d)` (`r nationT1['American']` US and `r nationT1['Indian']` India), with `r sexT1['Male']` males and `r sexT1['Female']` females, `r relstats['Married']` of whom were married or in a long-term relationship, `r relstats['Divorced']` who were divorced, `r relstats['Single']` who were single, and `r relstats['Widowed']` who were widowed.
-The median number of participants per condition was `r median(n_cond)` (min=`r min(n_cond)`, max=`r max(n_cond)`).
-For the number of participants in each condition, see Table \@ref(tab:conditions).
-For summary statistics, see Table \@ref(tab:sumtab).
-For the distributions of participants by age, income, and nationality, see Figure \@ref(fig:socioeconomic).
-
-```{r sumtab}
-
-d$minutes <- d$TotalTime/60
-d$Children <- d$Sons + d$Daughters
-
-vars <- c(
-  Age = 'Age (years)',
-  Income = 'Income (USD)',
-  years_education = 'Education (years)',
-  Children = 'Number of children',
-  minutes = 'Time to complete (minutes)',
-  T1Belief = 'T1 Belief',
-  T1Action = 'T1 Action',
-  T1Divide = 'T1 Division',
-  T1LowMood = 'T1 Low mood',
-  T1Manipulative = 'T1 Manipulative',
-  T2Belief = 'T2 Belief',
-  T2Action = 'T2 Action',
-  T2Divide = 'T2 Division',
-  T2LowMood = 'T2 Low mood',
-  T2Manipulative = 'T2 Manipulative',
-  T3Action = 'T3 Action'
-)
-kable(custom.summarize(d, vars), caption = "Summary statistics for study variables.
-Values that were on a 0-100 scale were rescaled to 0-1.
-Indian participants reported income in rupees, which we converted to USD at the current exchange rate (1 rupee = 0.014 USD).") %>% kable_styling()
-```
-
-## Distributions of beliefs and actions at Time 1
-
-Across the four vignettes, mean belief of the victim was relatively low at baseline (T1), Mean = `r signif(mean(d$T1Belief, na.rm = T), 2)`, albeit with wide variation, SD = `r signif(sd(d$T1Belief, na.rm=T), 2)`; `r sum(d$T1Belief==0)` participants (`r 100*signif(sum(d$T1Belief==0)/nrow(d), 2)`%) rated their belief = 0, and `r sum(d$T1Belief==1)` participants (`r 100*signif(sum(d$T1Belief==1)/nrow(d), 2)`%) rated it as = 1.
-The distribution of likelihood of helping the victim (action) was similar, Mean = `r signif(mean(d$T1Action, na.rm = T), 2)`, SD = `r signif(sd(d$T1Action, na.rm=T), 2)`, with `r sum(d$T1Action==0)` participants (`r 100*signif(sum(d$T1Action==0)/nrow(d), 2)`%) rating their action = 0, and `r sum(d$T1Action==1)` participants (`r 100*signif(sum(d$T1Action==1)/nrow(d), 2)`%) rated action as = 1.
-Although not a pre-registered prediction, *T1 Belief* and *T1 Action* were highly correlated across the four vignettes, consistent with help being worth providing if the signaler's claims were true (see Figure \@ref(fig:t1plot)).
-
-```{r t1plot, fig.width=10, fig.height=10, fig.cap="The distributions of *T1 Belief* vs.*T1 Action*, by vignette.
-Each dot is one participant.
-Original 0-100 values rescaled to 0-1.
-Lines fit by linear regression.
-Dot size indicates the number of overlapping points.
-Black dot is the mean of each variable."}
-plot_T1Belief_T1Action
-```
-
-## Confirmatory: Signals increase beliefs and actions in the predicted rank order
-
-```{r}
-sm1 <- summary(models$Margins$m1)
-suicide_belief_eff <- signif(sm1$AME['signalSuicide attempt']/sd(d$T2Belief), 2)
-
-sm3 <- summary(models$Margins$m3)
-suicide_action_eff <- signif(sm3$AME['signalSuicide attempt']/sd(d$T2Belief), 2)
-
-signal_belief_ttest <- t.test(100*d$T2Belief, 100*d$T1Belief, paired = T)
-signal_action_ttest <- t.test(100*d$T2Action, 100*d$T1Action, paired = T)
-
-```
-
-As predicted, there was a strong statistically significant positive causal effect of the ordinal signal on *T2 Belief* and *T2 Action* (controlling for *T1 Belief* and *T1 Action*, respectively), with the effect of each signal increasing in the predicted rank order (verbal request, crying, mild depression, depression, suicide attempt).
-See Figure \@ref(fig:beliefeffect) and models m1 and m3 in Tables \@ref(tab:regressiontables) and \@ref(tab:anovatables).
-(Results for the preregistered OLS models were very similar; see Figures \@ref(fig:preregbelief) and \@ref(fig:preregbeliefB).)
-
-The marginal between-subjects effect of the high cost *Suicide attempt* vs.
-the *Verbal request* control on T2 *Belief* (averaging over all four vignettes and all values of T1 *Belief*) was an increase of `r fmt_margins(models$Margins$m1, 'signalSuicide attempt')` points on the original 0-100 point scale.
-The equivalent increase for T2 *Action* was `r fmt_margins(models$Margins$m3, 'signalSuicide attempt')` points.
-Given that the standard deviations of T2 *Belief* and *Action* are `r signif(sd(100*d$T2Belief), 2)` and `r signif(sd(100*d$T2Action), 2)`, respectively, these represent increases of `r suicide_belief_eff` and `r suicide_action_eff` SD's, respectively.
-
-```{r beliefeffect, fig.width=6, fig.height=8, fig.cap=paste0("The effect of the signals on *T2 Belief* (top) and *T2 Action* (bottom) controlling for *T1 Belief* and *T1 Action*, respectively.
-Effects plotted for T1 values set to their median value (*T1 Belief*=", median(d$T1Belief, na.rm=T), ", *T1 Action*=", median(d$T1Action, na.rm=T), ").
-Fit using generalized linear regression models with the quasibinomial family.
-Grey bars are 95% CIs.
-For coefficents, p-values, and other statistics, see models m1 and m3 in Tables \\@ref(tab:regressiontables) and \\@ref(tab:anovatables).")}
-(effectsPlots$m1plot + theme(axis.text.x = element_blank()))/effectsPlots$m3plot + plot_layout(ncol = 1) & theme(plot.margin = unit(c(0,0,0,0), units = 'mm'))
-```
-
-<!-- Within-subjects, the average effect across all signals on *Belief* at T2 compared to T1 was `r inline_ttest(signal_belief_ttest)`, and on *Action* was `r inline_ttest(signal_action_ttest)` (on the original 0-100 point scale).
-For the change in *Belief* and *Action* for, T1 to T2 for all participants in all conditions, see Figure @ref(fig:rawbeliefactions2d).
--->
-
-The within-subject effects of each signal are depicted in Figure \@ref(fig:rawbeliefactions2d).
-
-## Confirmatory: The effect of signals on action is largely mediated by belief
-
-```{r medresults}
-rslts <- all_mediations$results
-
-suicidetotal <- 100*signif(rslts$point[rslts$signal == 'Suicide attempt' & rslts$Stat == 'Total'], 2)
-
-suicidemed <- 100*signif(rslts$n.avg[rslts$signal == 'Suicide attempt' & rslts$Stat == 'Total'], 2)
-
-depressiontotal <- 100*signif(rslts$point[rslts$signal == 'Depression' & rslts$Stat == 'Total'], 2)
-
-depressionmed <- 100*signif(rslts$n.avg[rslts$signal == 'Depression' & rslts$Stat == 'Total'], 2)
-
-```
-
-According to our theoretical model, credible signals of need increase observers' belief that the victim is telling the truth.
-Increased belief then increases the likelihood of helping the victim (action).
-See Figure \@ref(fig:medmodel).
-
-We fit the mediation and outcome models using GLM's with the binomial family as the mediation package does not support the quasibinomial family.
-The total effect of the *Suicide attempt* signal (treatment) vs.
-*Verbal request* (control) on the likelihood of *Action* was to increase it by `r suicidetotal` points from T1 to T2 (on the original 100-point scale).
-Of this increase, `r suicidemed`% was mediated by the increased *Belief* that the victim was telling the truth.
-The total effect of the *Depression* signal (treatment) vs.
-*Verbal request* (control) on the likelihood of *Action* was to increase it by `r depressiontotal` points from T1 to T2.
-Of this increase, `r depressionmed`% was mediated by the increased *Belief* that the victim was telling the truth.
-See Figure \@ref(fig:mediation).
-
-<!-- (Check if med4 or med4b is correct; they look identical to me). -->
-
-```{r mediation, fig.width=8, fig.height=4, fig.cap="The effect of each signal (treatment) vs.
-Verbal request (control) on Action.
-The x-axis is the change in Action on the [0, 1] scale.
-The effects of the signals on Action are largely mediated by Belief (percent mediated on the right).
-The mediation model controlled for *T1 Belief*, and the outcome model controlled for *T1 Belief* and *T1 Action*.
-Both models were GLMs with the binomial family (the mediation package does not support the quasibinomial family).
-ACME: Average causal mediation effect.
-ADE: Average direct effect.
-Total: Total effect (ADE + ACME).
-Bars are 95% CIs."}
-all_mediations$plot
-```
-
-## Exploratory: Costlier signals decrease perceived manipulation and increase perceived low mood
-
-The proportion of participants inferring each emotion in each vignette at T1 is depicted in Figure \@ref(fig:t1emotionheatmap), after each signal at T2 in Figure \@ref(fig:t2emotionheatmap), and the change in proportions from T1 to T2 in Figure \@ref(fig:diffemotions).
-The increase in inferred depression in the *Depression* and *Suicide attempt* conditions, but not the *Verbal request* and *Crying* conditions, helps validate these signals, as does the increase in inferred suicidality in the *Suicide attempt* condition.
-
-The mean change in the *Low mood* and *Manipulative* variables from T1 to T2 for each signal in each vignette reveals a large decrease in inferred *Manipulation* for costly signals, and a large increase in inferred *Low mood* (with the exception of the Thwarted marriage vignette, in which changes are small).
-See Figure \@ref(fig:emotionsplot).
-
-```{r emotionsplot, fig.width=10, fig.height=8, fig.cap="The within-subjects effect of the signals on participants' inferred *Manipulative* and *LowMood* emotional states of the victim, from T1 (arrow base) to T2 (arrow head), for each signal in each of the four vignettes.
-Low mood: higher values indicate lower perceived mood.
-Manipulative: higher values indicate higher perceived manipulativeness.
-Thick arrows: mean change.
-Thin arrows: means of 500 bootstrap resamples."}
-plot_emotions
-```
-
-## Exploratory: Signal effects differ by vignette
-
-```{r}
-
-thwart_sv_bdiff <- visreg_diff(models$Model$m2, 'Thwarted marriage', 'Suicide attempt', 'Verbal request', d)
-
-thwart_sv_adiff <- visreg_diff(models$Model$m4, 'Thwarted marriage', 'Suicide attempt', 'Verbal request', d)
-
-brother_sv_bdiff <- visreg_diff(models$Model$m2, 'Brother-in-law', 'Suicide attempt', 'Verbal request', d)
-
-brother_sv_adiff <- visreg_diff(models$Model$m4, 'Brother-in-law', 'Suicide attempt', 'Verbal request', d)
-
-```
-
-```{r}
-bil_b_suicide <- signif(effect_sizes$est[effect_sizes$id=="Suicide attempt,Brother-in-law" & effect_sizes$Outcome=="Belief"], 2)
-
-rom_b_crying <- signif(effect_sizes$est[effect_sizes$id=="Crying,Romantic partner" & effect_sizes$Outcome=="Belief"], 2)
-
-bil_a_suicide <- signif(effect_sizes2$effsize[effect_sizes2$id=="Suicide attempt,Brother-in-law" & effect_sizes2$Outcome=="Action"], 2)
-
-bil_a_verbal <- signif(effect_sizes2$effsize[effect_sizes2$id=="Verbal request,Brother-in-law" & effect_sizes2$Outcome=="Action"], 2)
-
-```
-
-The effects of the signals on rated beliefs and actions differed substantially by vignette, which we display in three ways for each signal in each vignette: estimated cumulative distributions plots, which show the entire distributions of rated beliefs and actions, including which signals and vignettes have high fractions of 0's and 1's (Figures \@ref(fig:ecdf)); regression estimates of the mean effects of the signals on beliefs and actions by vignette (Figure \@ref(fig:beliefvignette)); and between- and within-subjects signal effect sizes by vignette (Figures \@ref(fig:effectsizes) and \@ref(fig:effectsizes2)).
-
-```{r ecdf, fig.width=11, fig.height=6, fig.cap="Empirical cummulative distribution functions for Time 2 Belief (top) and Action (bottom) compared to their Time 1 baseline values (red), by signal and vignette.
-Y-values indicate the fraction of all ratings equal to or less than a given x-value.
-Ratings rescaled to [0, 1].
-Dots indicate median values of Belief and Action, by signal and vignette."}
-ecdf_plot
-```
-
-```{r beliefvignette, fig.width=8, fig.height=8, fig.cap=paste0("The effect of the signals on *T2 Belief* (top) and *T2 Action* (bottom) in each vignette, controlling for T1 values of Belief and Action, respectively.
-Ratings rescaled to [0, 1].
-Effects plotted for T1 values set to their median value (*T1 Belief*=", median(d$T1Belief, na.rm=T), ", *T1 Action*=", median(d$T1Action, na.rm=T), ").
-Fit using generalized linear regression models with the quasibinomial family.
-Grey bars are 95% CIs.
-For coefficents, p-values, and other statistics, see models m2 and m4 in Tables \\@ref(tab:regressiontables) and \\@ref(tab:anovatables).")}
-(effectsPlots$m2plot + theme(axis.text.x = element_blank()))/effectsPlots$m4plot + plot_layout(ncol = 1) & theme(plot.margin = unit(c(0,0,0,0), units = 'mm'))
-```
-
-We note the following patterns in Figure \@ref(fig:ecdf), which we will return to in the Discussion section.
-First, as we intended, the distributions of *Belief* and *Action* in the *Verbal request* control condition were very similar to their distributions at T1 baseline across vignettes.
-In the "Basketball coach" and "Brother-in-law" vignettes, though, their distributions in the *Verbal request* condition were shifted to somewhat lower values relative to baseline (i.e., the verbal request slightly *reduced* belief and action in those vignettes).
-Second, in the "Romantic partner" and "Brother-in-law" vignettes, the effect of *Crying* differed little from *Verbal request*, but in the "Basketball coach" vignette, it differed little from the *Depression* and *Suicide attempt* signals.
-Third, the effect of the *Suicide attempt* signal on *Belief* was similar to that of *Depression* across all vignettes, but had a noticeably greater effect on *Action* in the "Romantic partner" and "Brother-in-law" vignettes.
-Fourth, there was little difference between the effect of the *Mild depression* vs.
-*Depression* signals.
-
-The largest between-subjects effect was *Suicide attempt* vs.
-*Verbal request* control on *Belief* in the "Brother-in-law" vignette, Cohen's d = `r bil_b_suicide`, and the smallest was the effect of *Crying* on *Belief* in the "Romantic partner" vignette, Cohen's d =`r rom_b_crying`.
-The largest within-subjects effect was *Suicide attempt* on *Action* at T2 vs.
-T1 in the "Brother-in-law" vignette, Cohen's d = `r bil_a_suicide`, and the smallest was the *negative* effect of *Verbal request* on *Action* at T2 vs.
-T1 in the "Brother-in-law" vignette, Cohen's d =`r bil_a_verbal`.
-
-## Exploratory: Sociodemographic associations
-
-The sociodemographic variables were strongly confounded with nationality (Indian participants were younger, lower income, with more years of education than US), which, in turn, were confounded with vignette (responses in the Indian Thwarted marriage vignette differed substantially from those in the US vignettes).
-We therefore conducted our exploration of the sociodemographic variables separately by nationality.
-
-In the US sample, female participants were more likely to believe and help the victim than male participants, and younger participants were more likely to believe and help the victim than older participants.
-We found no significant effects of *Income*, *Education*, relationship status (e.g., married, single), or number of sons or daughters on *Belief* or *Action*.
-See Figure \@ref(fig:demographicsignal).
-
-```{r demographicsignal, fig.width=11, fig.height=8, fig.cap="Sociodemographic associations with *T2 Belief* (top) and *T2 Action* (bottom) in US participants.
-Each model controlled for *T1 Belief* or *T1 Action*, vignette, Education, and Income.
-Significant associations displayed here.
-Estimated using generalized linear regression models with the quasibinomial family.
-Grey bars are 95% CIs."}
-
-effectsPlots_US$m12plot + 
-    theme(axis.text.x = element_blank()) +
-effectsPlots_US$m12bplot + 
-    theme(
-      axis.text = element_blank(), 
-      axis.title.y = element_blank(), 
-      axis.title.x = element_blank()
-      ) + 
-effectsPlots_US$m13plot + 
-effectsPlots_US$m13bplot +
-    theme(axis.text.y = element_blank(), axis.title.y = element_blank())
-```
-
-In the Indian sample and vignette, in contrast, males were more likely to help the victim than females, those with more years of education were less likely to believe the victim, and there was a marked increase in likelihood of helping among older individuals in the suicide signal condition.
-We found no significant associations with age or income.
-See Figure \@ref(fig:indiademographics).
-
-```{r indiademographics, fig.width=10, fig.height=8, fig.cap="Sociodemographic associations with *T2 Belief* and *T2 Action* in Indian participants (Thwarted marriage vignette).
-Each model included *T1 Belief* or *T1 Action*, Income, Age, Sex, Years of education, and signal.
-Significant associations displayed here.
-Estimated using generalized linear regression models with the quasibinomial family.
-Grey bars are 95% CIs."}
-(effectsPlots_India$m12plot + xlab('Education (years)') + effectsPlots_India$m13plot) / effectsPlots_India$m17plot
-```
-
-## Validity check: T3 increase in Action with proof that victim was telling the truth
-
-```{r}
-t2t3actionttest <- t.test(d$T3Action, d$T2Action, paired = T)
-```
-
-As a partial check on the validity of our methods and results, at T3 we presented participants with strong evidence that the victim was telling the truth, and asked them to again rate their likelihood of acting to help the victim (*T3 Action*).
-Compared to the mean *T2 Action* (M=`r signif(mean(d$T2Action, na.rm=T), 2)`), mean *T3 Action* increased substantially, `r inline_ttest(t2t3actionttest)`.
-Across the US vignettes, likelihood of acting at T3 increased to near-ceiling (M=`r signif(mean(d$T3Action[d$vignette != 'Thwarted marriage']), 2)`), regardless of participants' *T2 Action* values, indicating that propensity to act was indeed contingent on believing the victim.
-In the Indian Thwarted marriage vignette, however, there was little change in *T3 Action* compared to *T2 Action* (Figure \@ref(fig:t3action)), perhaps because Indian participants' beliefs and actions were relatively insensitive to the signals to begin with (Figures \@ref(fig:ecdf) and \@ref(fig:beliefvignette)).
-
-# Discussion
-
-As predicted, in vignettes involving conflicts of interest and private information about the need for help, costly signals of need increased participants' belief in the victim and their likelihood of helping her, with the increase in perceived need and likelihood of helping increasing monotonically with signal cost.
-As predicted, the increase in likelihood of helping was largely mediated by the increase in belief in the victim.
-In an exploratory analysis, costlier signals also decreased perceptions that the victim was manipulative.
-
-These effects were largest in the "brother-in-law" and "romantic partner" vignettes, both of which involved claims of assault against participants' imagined daughters, and smaller in the "basketball coach" and the "thwarted marriage" vignettes.
-The small effect in the "basketball coach" vignette, might have been due to the lack of relatedness between participants and the victim (the star player), or how participants weighted the costs of suspending the coach vs.
-punishing a potentially innocent person.
-
-The small signal effect in the "thwarted marriage" vignette, which involved the Indian sample, could indicate that our results do not generalize across cultures, undermining our adaptationist hypothesis.
-It could also reflect our poor understanding of contemporary Indian culture regarding dowry (the effect was larger in older participants).
-Baseline belief in the older daughter, and likelihood of helping her, was relatively high at baseline (greater than 50%) compared to victims in the other vignettes.
-Private information and conflict therefore probably played a smaller role and thus costly signals were less necessary.
-We observed a similar pattern in our pilot study, in which baseline belief in the victim's need was high, and costly signals had smaller effects than they did in the current study.
-Additionally, supporting the older daughter came at the cost of one's younger daughter, which may also help explain the relatively small signal effects.
-A final consideration is that data from the Indian sample appeared to be of lower quality, limiting our confidence in any of these interpretations (see limitations for more information).
-
-In the "brother-in-law" and "romantic partner" scenarios, *Crying* had little effect on the magnitude of pro-victim responses relative to *Verbal request*, suggesting it was not costly enough to serve as a reliable signal in times of substantial conflicts of interests.
-In contrast, both *Depression* conditions increased support, albeit to similar degrees.
-One potential reason for this is the increase in symptoms from mild depression to depression was not costly enough to result in a large effect, as the symptoms differed little in severity (e.g., grades dropping from As to Bs in *Mild depression* vs.
-Cs in *Depression*).
-Such small changes may be less impactful in vignettes than in real-life, where the effects of signaling may increase in severity as they persist over a lengthy period of time.
-
-The effect of *Suicide attempt* on belief at T2 was similar to the *Depression* conditions across vignettes, but it resulted in greater likelihood of support.
-One interpretation is that although some participants did not believe the victim's story, her signal nevertheless convinced them that she needed help.
-For example, maybe the brother-in-law did not assault her, but the presence of his family in her home was causing genuine distress.
-Support for this interpretation comes from our mediation analyses, which showed that the likelihood of help was largely, but not entirely, mediated by signal's effect on belief in need.
-
-There were minor associations of age and sex with belief and action in the US participants, with both being higher among females and younger individuals.
-The US vignettes all involved assaults against young women, which might have been more salient to female and younger participants.
-In the Indian sample, high baseline belief and action were somewhat lower among those with more education and among females, respectively.
-Costlier signals, suicidality in particular, had a larger effect among older individuals, perhaps because older individuals were more likely to have children of marriageable age, like the victim in the vignette.
-
-Finally, after the T3 evidence that the victim was telling the truth, likelihood of helping by the US participants increased to near ceiling, an effect that helped validate our vignettes.
-Among Indian participants, in contrast, participants only slightly increased their likelihood of helping from their T2 level.
-One interpretation of the latter is that Indian participants tended to believe the older daughter anyway, so their decision to help was not changed by additional information.
-
-<!-- Overall, our results on the connection between belief in need and likelihood of help are consistent with costly signaling and bargaining approaches to depression and suicide.
-At T1, *Belief* and *Action* were highly correlated yet distinct; while at T2, the effect of signal on both *Belief* and *Action* was to increase the magnitude of pro-signaler responses, with the effect of signal on *T2 Action* being largely mediated by signal's effect on belief in need.
-This relationship between belief in need and likelihood of support and the importance of signal cost should be expected in scenarios when a target of a signal of need would benefit from helping if the signaler's need was genuine but face substantial net costs if it was not.
-Importantly, such scenarios appear to be common among modern humans and have likely been since individuals could increase their inclusive fitness through supporting kin or important cooperative partners who could return to providing benefits to supporters once their situation returned to normal [@SugiyamaSugiyama2003; @tooby1996].
--->
-
-<!-- Although this study was not designed to examine whether the costs of signaling would be made up for by the increased support stemming from depression and suicide attempts directly, the results are consistent with this hypothesis.
-In general, the costs required to honestly convey one's qualities should be expected to increase with the potential payoffs of deception and the number of defectors within the broader population [@Rosenthal1993], with the vignettes in this study emphasizing the existence of private information and sizable conflicts of interest to increase the perceived risk of being taken advantage of.
-In similar real-world scenarios, this difficulty of signaling honest need would coincide with the substantial fitness-relevant benefits of preventing future assaults or being able to marry the partner of one's choice.
-These benefits coupled with the fact that depression and suicide attempts become relatively less costly to one's fitness prospects with increased need [@Hagen2003], suggest that the increased support seen in this study may be worth the costs required to signal need more often than is often appreciated when counting the entire costs of depression as the signal rather than only the upregulation of symptoms for a communicative purpose.
--->
-
-## Limitations
-
-The main limitation of this study is that is has less ecological validity than real-world observations of depressed individuals interacting with their social partners.
-This may have biased results in a pro-signaler direction if the lack of real costs of helping made support feel less costly or if there was a social desirability bias toward helping [@grimm2010].
-It may have also biased participants against helping if they could not fully imagine the characters in the story as kin or important cooperative partners, and the survey's short duration may have weakened the strength of the costlier signals as bargaining tools.
-
-Our design did not include vignettes with male signalers.
-For this reason, we have no data on the possibility of sex differences in the effectiveness of the signaling strategies examined.
-Although not predicted theoretically, such differences are possible if the costs of signaling vary between the sexes due to differential access to alternative bargaining strategies [@HagenRosenstrom2016] or if one sex tends to suffer greater negative reputational effects  when displaying the emotions and behaviors in the vignettes.
-It is also possible the costliness of the situations presented in the vignettes differ by sex.
-
-Compared to the US sample, far more Indian participants failed our attention checks, which is consistent with botting, unfamiliarity with English, or low-effort responses [@kennedy2020].
-If this high failure rate indicates lower-quality responses among those who passed the attention checks, the weak signal effect in the thwarted marriage vignette may simply be due to greater noise rather than differences in the scenario or the effectiveness of the signals compared to those in the US.
-Another concern relevant to all vignettes is that our decision to anchor the T1 sliders at 0 may have resulted in participants being more likely to report extreme values.
-
-<!-- Slider anchor  -->
-<!-- Regex: stopped in SI -->
-<!-- T\d \w+ -->
-
-# Conclusion
-
-Depression is costly, sometimes resulting in death by suicide.
-Our results suggest that these costs, which mainstream theories take as evidence of brain dysfunction [@SymeHagen2021], function to help victims of adversity elicit support when their true level of need is private information and they have conflicts with social partners.
-These findings align with real-world evidence that depression simultaneously elicits positive and negative responses from social partners [@SymeHagen2021].
-If the bargaining model is correct, depression is an important social problem, not a medical one [@syme2020].
-
-<!-- This coupled with , suggests that more attention should be paid to the potential for positive responses towards depressed individuals, especially from social partners who receive substantial benefits from the depressed or suicidal individual.
--->
-
- <!-- The need to explain suicide's connection to depression is often overlooked by explanations for major depression, particularly those which propose non-signaling functions.
-One explanation for their connection, is that both suicidality and depression may function to limit negative fitness outcomes in times of substantial adversity [@andrews2006; @Hagen2002; @Hagen2003; @HagenEtAl2008; @nock2008; @Rosenthal1993; @Stengel1956; @SymeEtAl2016], with costlier signals being required to elicit support when the payoffs to faking need are high enough so that less costly signals are not reliable indicators of one's need [@Rosenthal1993].
-For this hypothesis to be correct, instrumental support would need to be provided frequently enough with large enough impacts so that the costs of signaling are outweighed by the benefits on average.
-In support of this, we found exposure to depression and suicide attempts resulted in greater belief in need and increased likelihood of support in fictional scenarios.
--->
-
-# Acknowledgements
-
-This study was funded through a Washington State University, Vancouver Research Mini Grant.
-We thank Anne Pisor, Darcy Bird, and members of the Hagen lab group for numerous helpful comments.
-We also thank XX and YY [pending permission to acknowledge] for feedback on the Thwarted marriage vignette.
-
-<!-- # To do: -->
-
-<!-- -   victim or signaler? -->
-<!-- -   add anger -->
-<!-- -   Intro "State the objectives of the work and provide an adequate background, avoiding a detailed literature survey or a summary of the results." -->
-<!-- -   Discussion " This should explore the significance of the results of the work, not repeat them.
-A combined Results and Discussion section is often appropriate.
-Avoid extensive citations and discussion of published literature." -->
-<!-- -   mention asking for prefered sex -->
-
-<!-- # Notes from my meeting with Anne -->
-
-<!-- -   Table detailing the cooperative endeavor (maybe word as boundedness of fate), conflict of interest, and what the private information is about would be useful. -->
-<!-- -   Calling verbal request control when it's a treatment? -->
-<!-- -   Can shift much of the pilot studies info to SI with some detail post line 279 in draft she saw. -->
-<!-- -   Cumulative distribution plot: needs more info in captions. could benefit from fig6a and fig6b (confusion over x and y axes) -->
-
-# Supplementary information
-
-## Pilot studies
-
-We conducted two pilot studies, one on MTurk with a large sample size (N=`r nrow(signalingdata2018b)`), and one on [reddit.com/r/SampleSize](https://reddit.com/r/SampleSize) with a small sample size (N=28).
-Both studies used the experimental pre-test, post-test design used in the current study.
-
-In the MTurk study, participants read a vignette that put them in situations in which an imagined sister was requesting a loan of \$50,000 from the participant that was originally saved for the participant's imagined daughter's college education.
-The sister claims the money is needed for medical treatment for her own child, but she has incentives to deceive.
-The manipulations were signals very similar to those used in this study, and the outcomes were belief that the sister really needed the money and intention to loan her the money.
-See XX for the full write-up.
-See <https://osf.io/3rg8b> for preregistration of the pilot study.
-See <http://doi.org/10.5281/zenodo.4637883> for pilot data.
-
-```{r piloteffects, fig.width=10, fig.cap="Pilot study effect of the signals.
-A.
-Effect of signal on Belief at T2, controlling for Belief at T1.
-B: Proportion of participants who inferred the victim was mentally ill.
-Fit with a generalized linear model with the quasibinomial family."}
-pilot_results$effectplot + (pilot_results$mentalplot + theme(axis.text.y = element_blank())) + plot_annotation(tag_levels = 'A')
-```
-
-In the small reddit.com study, participants viewed and responded to two vignettes used here, each with a different signal.
-
-We learned six major lessons from the MTurk pilot study that influenced the design of the current study.
-First, as predicted, belief in the sister's need was highest in the *Depression* condition and lowest in the *Verbal request* condition, giving us confidence to continue this research (see Figure \@ref(fig:piloteffects)).
-Second, to rule out that believability and willingness to help were simply artifacts of the sister's psychiatric distress, we included a "signaling" condition in which the sister exhibited schizophrenic symptoms.
-As predicted, believability and willingness to help in this condition were dramatically lower than in any other condition, ruling out this alternative explanation.
-We therefore did not include the schizophrenic condition in the current study.
-Third, baseline (T1) believability was very high (mean = `r signif(pilot_results$meanT1belief, 2)` and median = `r signif(pilot_results$medianT1belief, 2)` on a 0-100 point scale), leaving little scope for signals to increase believability.
-In the current study we therefore endeavored to provide details in the vignettes that would undermine the victim's believability at baseline.
-Fourth, contrary to our hypothesis, the *Suicide threat* and *Suicide attempt* signals reduced believability relative to *Depression*.
-We surmised that the sister's adversity -- a sick child -- was not sufficient to justify a suicide attempt, thus undermining her believability.
-In the current study the signaler herself is therefore the victim, and the forms of adversity -- physical and sexual assault and thwarted and forced marriage -- are those that are frequently associated with suicidality.
-Fifth, the content of the vignette matters, so instead of a single vignette we decided to use four different vignettes to help determine the extent to which signaling effects were sensitive to seemingly irrelevant details of the vignettes.
-Sixth, in a pre-test post-test design, the control condition should be identical to the treatment condition in every respect except for the factor being tested, which in this study was signal cost.
-Post hoc, we realized that the control condition in the pilot study differed substantially from the treatment condition beyond signal cost: in the treatment conditions, participants encountered the sister twice: once when she requests help, and a second time when she signals.
-In our faulty control, participants only encountered the sister once, when she requests help, with no second encounter.
-In this study we therefore ensured that the control condition (Verbal request) was identical to the treatment conditions except for signal cost.
-
-In the reddit.com pilot study, participants viewed two vignettes (with different signals in each one), and responded with lower belief to the second vignette compared to the first regardless of the vignette or signal.
-To avoid such order effects, which are a common problem in vignette studies that use multiple vignettes [@su2020], we decided to present each participant in the current study with a single vignette and signal.
-
-## Power from MTurk pilot study
-
-We estimated power using our MTurk pilot study data to compare the effect of the *Mild depression* signal vs.
-the *Verbal request* control on *Belief* (that the sister needed the money) at T2 controlling for *Belief* at T1 in a linear regression model.
-Specifically, we resampled the pilot data with replacement, fit the linear regression model, and extracted the p-value for the signal coefficient, repeating this 2000 times for each sample size ranging from N=20 to N=200.
-Power was computed as the proportion of p-values \< 0.05.
-Power was about 80% for a sample size of about `r pwr80_90[[1,1]]`, and was about 90% for a sample size of about `r pwr80_90[[1,2]]`.
-See Figure \@ref(fig:power).
-
-```{r power, fig.cap="Power curve for between-subjects effect of Mild depression vs. Verbal request signal on T2 Belief, controlling for T1 Belief."}
-
-smplesize <- nrow(d)/10
-
-ggplot(power_curve, aes(sample_size, power)) +
-  geom_line() +
-  geom_vline(xintercept = smplesize, linetype = 'dotted') +
-  annotate(geom = 'text', x = smplesize + 3, y = 0.75, label = 'Current study sample size', hjust = 0) +
-  labs(x = '\n Sample size', y = 'Power\n') +
-  theme_minimal(15) + theme(axis.title.y = element_text(angle = 0))
-```
-
-<!-- Second, for participants in the *Depression* condition only, we compared their T2 Belief to their T1 Belief using a paired t-test (in the full pilot data, *Depression* increased belief by about 8 points on a 100 point scale).
-We again resampled our pilot data 2000 times for each sample size from N=20 to N=200.
-Power was about 80% for a sample size of 125, and about 90% for a sample size of 175.
--->
-
-```{r power2, fig.cap="Power curve for within-subjects effect of Depression signal on *T2 Belief* relative to *T1 Belief*."}
-  # ggplot(power_curve2, aes(sample_size, power)) +
-  #   geom_line() +
-  #   labs(x = '\n Sample size', y = 'Power\n') +
-  #   theme_minimal(15)
-```
-
-## Vignettes of the current study (main bodies and signals)
-
-### Basketball coach
-
-Imagine yourself in the following scenario:
-
-You are a college athletic director at a university with a long history of success in women's basketball.
-Unfortunately, despite quality players, the team struggled for the first three years of your leadership.
-You came close to losing your job but were given two more years to turn things around.
-You immediately hired a new head coach who you had spotted coaching a low-ranked college team that punched above its weight.
-Two years later, your team is one of the best in the country and has attracted a top recruit who has become the star player on your team and is probably the best player in the country.
-You have been told that if the team makes it to the final rounds of the playoff tournament, the university will offer you a high paying contract extension.
-
-Your star player is hard to deal with, however.
-She is constantly jealous of other players, and often comes to your office to complain that the coach unfairly limits her playing time, claiming this will ruin her chances of going professional.
-The star player has also posted self-serving accounts of your discussions with her on social media.
-
-A few days ago, after the coach started a new player in one game, the star player went to the police and accused the coach, a physically powerful man, of cornering her in the locker room one night and forcibly kissing her and grabbing her body.
-The coach strongly denies the allegation, and the police said they do not have any evidence to corroborate the player's accusation.
-
-You reached out to other players on the team, all of whom say that the relationship between the coach and star player has always seemed professional, and they are shocked by the allegation.
-None of the other players have any complaints about the coach.
-On the contrary, the other players praise the coach for leading everyone into the playoffs.
-They mention that the star player is a prima donna, but they are worried that if either the coach or the star player miss the playoffs, it will hurt everyone's chances of making it to the championships.
-
-You find out that the star player then told the university president that she feared the coach might attack her again, and asked her to replace the coach with one of his assistants, who you know wants the star player to have more playing time.
-The president refused, saying there was no evidence of wrongdoing.
-
-#### Signals
-
-##### Verbal request
-
-A week later the coach informs you that the star player's performance in games is excellent, helping the team's performance and her reputation with pro scouts.
-Later that day, there is a formal luncheon at the athlete dorm to introduce the coaches and members of each team to the alumni.
-The alumni are especially interested in meeting the basketball coach and members of the basketball team because they are in the playoffs.
-You notice your star player is not there, but you see her roommate, a member of the swim team.
-She tells you that you should talk to your star player in person, and she leads you to their dorm room.
-
-When you arrive, the two of you find her sitting on her bed.
-She appears fit, well-rested, and her room is clean.
-She looks calm with her hands folded as she asks you to replace the coach, saying she can't attend the luncheon if he is there.
-
-##### Crying
-
-A week later the coach informs you that the star player's performance in games is excellent, helping the team's performance and her reputation with pro scouts.
-Later that day, there is a formal luncheon at the athlete dorm to introduce the coaches and members of each team to the alumni.
-The alumni are especially interested in meeting the basketball coach and members of the basketball team because they are in the playoffs.
-You notice your star player is not there, but you see her roommate, a member of the swim team.
-She tells you that you should talk to your star player in person, and she leads you to their dorm room.
-
-When you arrive, the two of you find her sitting on her bed.
-She appears fit and well-rested, and her room is clean.
-She looks sad and begins sobbing as she asks you to replace the coach, saying she can't attend the luncheon if he is there.
-
-##### Mild-depression (crying with behavioral changes)
-
-A week later the coach informs you that the star player's performance in games is OK and not harming the team's performance and her reputation with pro scouts.
-Later that day, there is a formal luncheon at the athlete dorm to introduce the coaches and members of each team to the alumni.
-The alumni are especially interested in meeting the basketball coach and members of the basketball team because they are in the playoffs.
-You notice your star player is not there, but you see her roommate, a member of the swim team.
-She tells you that you should talk to your star player in person, and she leads you to their dorm room.
-
-When you arrive, the two of you find her sitting on her bed.
-Her room is a little messy and she appears a little less fit than you remember, while also seeming slightly tired.
-She looks sad and begins sobbing as she asks you to replace the coach, saying she can't attend the luncheon if he is there.
-
-##### Depression
-
-A week later the coach informs you that the star player's performance in games is poor, harming the team's performance and her reputation with pro scouts.
-Later that day, there is a formal luncheon at the athlete dorm to introduce the coaches and members of each team to the alumni.
-The alumni are especially interested in meeting the basketball coach and members of the basketball team because they are in the playoffs.
-You notice your star player is not there, but you see her roommate, a member of the swim team.
-She tells you that you should talk to your star player in person, and she leads you to their dorm room.
-
-When you arrive, the two of you find her slouched on her bed.
-Her room is a mess, and you notice she has lost weight and looks fatigued.
-She looks sad and begins sobbing and wringing her hands as she asks you to replace the coach, saying she can't attend the luncheon if he is there.
-
-##### Suicide attempt
-
-A week later the coach informs you that the star player's performance in games is poor, harming the team's performance and her reputation with pro scouts.
-Later that day, there is a formal luncheon at the athlete dorm to introduce the coaches and members of each team to the alumni.
-The alumni are especially interested in meeting the basketball coach and members of the basketball team because they are in the playoffs.
-You notice your star player is not there, but you see her roommate, a member of the swim team.
-She tells you that you should talk to your star player in person, and she leads you to their dorm room.
-
-When you arrive, the two of you find her passed out on her bed.
-The room is a mess, and you notice she has lost weight.
-Her roommate tries to wake her up, but she doesn't respond.
-You see an empty bottle of OxyContin painkillers on the table and immediately call 911.
-That evening you visit her in the hospital.
-Her doctor tells you she almost died, and then leaves the two of you alone.
-The star player begins sobbing as she asks you to replace the coach.
-
-### Brother-in-law
-
-Imagine yourself in the following scenario:
-
-You are the single parent of a 15-year-old girl. Your relationship with her has always been full of conflict. She is very self-centered, and the two of you fight frequently.
-
-Recently, your sister lost her house in a fire and was having difficulty finding a place for her family to live because many other families also lost their homes.
-You are very close with your sister and brother-in-law, who helped you escape your abusive ex-partner.
-You have a large house with several extra bedrooms, so you decide to let your sister, your brother-in-law, and your teenage niece move in while they look for more permanent housing.
-
-(page break)
-
-Unfortunately, your daughter and your niece are not getting along.
-They have to share a bathroom, and your daughter complains constantly that she is in there too long.
-Your daughter is also jealous that her cousin has expensive clothes, a designer handbag, and a new iPhone, all of which are nicer than your daughter's.
-
-One day your daughter had a party at your house with many of her friends.
-You noticed that your niece was very popular and got a lot of attention, especially from your daughter's friends and boyfriend.
-You could tell that your daughter was upset.
-After the party, your daughter tells you that her cousin is a bitch who is trying to steal her boyfriend.
-However, you saw that your niece was trying to avoid interacting with the boyfriend.
-
-(page break)
-
-Later, your daughter complained that your brother-in-law was looking at her body.
-A few days later, while grocery shopping, you got a text from your daughter saying that your brother-in-law tried to get into the bathroom while she was showering and came into her room while she was changing.
-She says that she does not feel safe and wants your sister and her family to leave.
-However, you know your daughter will exaggerate to get her way.
-
-The next week, your daughter comes to you saying your brother-in-law groped her as they passed in the hallway and that she wants your sister's family to leave immediately.
-You confront your brother-in-law due to the severity of your daughter's allegation.
-He strongly denies it.
-
-That night, you call your mother who says your daughter has long been jealous of her cousin.
-She reminds you that you've taken your daughter's side before and been burned when you found out your daughter wasn't telling the whole truth.
-She reminds you of the difficult situation your sister's family is in.
-
-#### Signals
-
-##### Verbal request
-
-Your daughter has appeared normal since her claims about your brother-in-law.
-She has still looked fit and put the same amount of effort into her appearance, always wearing clean clothes and spending time on her hair.
-She has also slept about the same amount of time as normal and remained active throughout the day.
-
-Her demeanor has also remained normal.
-She has generally appeared calm and has been able to maintain her concentration.
-She has also done her homework on time and maintained an A in all her classes as she always has in the past.
-
-When the two of you talk about your brother-in-law, she remains calm and asks you to kick him out.
-
-##### Crying
-
-Your daughter has appeared normal since her claims about your brother-in-law.
-She has still looked fit and put the same amount of effort into her appearance, always wearing clean clothes and spending time on her hair.
-She has also slept about the same amount of time as normal and remained active throughout the day.
-
-Her demeanor has also remained normal.
-She has generally appeared calm and has been able to maintain her concentration.
-She has also done her homework on time and maintained an A in all her classes as she always has in the past.
-
-When the two of you talk about your brother-in-law, she starts sobbing and asks you to kick him out.
-
-##### Mild-depression (crying with behavioral changes)
-
-Your daughter has appeared sad since her claims about your brother-in-law.
-She has looked a little less fit and has put less effort into her appearance, occasionally wearing dirty clothes and sometimes not doing her hair.
-She has also sometimes woken up late and has seemed a little less active than normal.
-
-Her demeanor has also changed slightly.
-She has occasionally gotten distressed and has seemed distracted.
-She has also missed a few assignments and her grades dropped from straight A's to a B average for the first time in her life.
-
-When the two of you talk about your brother-in-law, she starts sobbing and asks you to kick him out.
-
-##### Depression
-
-Your daughter started to appear noticeably different since her claims about your brother-in-law.
-She has lost weight and has been putting no effort into her appearance, often wearing dirty clothes and rarely doing her hair.
-She has also slept more than normal but still seemed tired and inactive.
-
-Her demeanor also changed drastically.
-She has often gotten distressed and has had difficulty maintaining her concentration.
-She has also missed multiple assignments, and her grades dropped from straight A's to a C average for the first time in her life.
-
-When the two of you talk about your brother-in-law, she starts sobbing and asks you to kick him out.
-
-##### Suicide attempt
-
-Your daughter started to appear noticeably different since her claims about your brother-in-law.
-She has lost weight and has been putting no effort into her appearance, often wearing dirty clothes and rarely doing her hair.
-She has also slept more than normal but still seemed tired and inactive.
-
-Her demeanor also changed drastically.
-She has often gotten distressed and has had difficulty maintaining her concentration.
-She has also missed multiple assignments, and her grades dropped from straight A's to a C average for the first time in her life.
-
-When the two of you talk about your brother-in-law, she starts sobbing and asks you to kick him out.
-Then, this past week, you and your daughter went through a traumatic experience when your daughter attempted suicide.
-You rushed her to the hospital, where she was placed in critical but stable condition.
-
-### Romantic Partner (pronouns match sex participants reported primary attraction to)
-
-Imagine yourself in the following scenario:
-
-You are a single parent of a 13-year-old girl.
-The two of you have lived alone together for the past five years since your breakup with her [father/mother].
-During this time, finding potential partners has been difficult.
-
-Recently, you have gotten closer with a new [man/woman].
-[He/She] is very attractive, has a good job, and has treated you better than anyone before.
-Confident that you will marry soon, the two of you decide to move in together.
-
-Your daughter, who wants you to get back together with her [dad/mom], is not happy about this.
-She frequently complains whenever your boyfriend comes over and is extremely rude and avoidant.
-In previous relationships, such behavior has driven others away.
-However, your partner says [he/she] is committed to this relationship and to establishing a bond with your daughter.
-
-After a month of living together with your partner, things have only gotten worse. Your daughter is almost always upset and has treated you partner worse than others in the past.
-
-One night, she accused your partner of hitting her multiple times.
-You ask if she has any bruises or injuries, but she says she doesn't.
-Despite this, she maintains that she was hit and says she doesn't know why there aren't any marks on her.
-
-You bring up the accusation with your partner, and [he/she] denies it, saying that [he/she] would never hurt her and that this is just a way for her to split the two of you up.
-
 ### Signals

### 2021-05-22 R/functions.R

@@ -312,10 +312,11 @@ emotion_plot <- function(d){
   ggplot() +
     geom_segment(data = d_boot, aes(x = T1LowMood_mean, y = T1Manipulative_mean, xend = T1LowMood_mean + T2LowMood_mean, yend = T1Manipulative_mean + T2Manipulative_mean, colour=signal), alpha = 0.02, arrow = arrow(length = unit(3, "mm"))) +
     geom_segment(data = d_full, aes(x = T1LowMood_mean, y = T1Manipulative_mean, xend = T1LowMood_mean + T2LowMood_mean, yend = T1Manipulative_mean + T2Manipulative_mean, colour=signal), alpha = 1, size = 1, arrow = arrow(length = unit(3, "mm"))) +
+    scale_color_viridis_d(option = 'magma', end = 0.95) +
     xlim(0, NA) +
     facet_wrap(~vignette) +
     labs(title = 'Change in mean emotions from T1 to T2', x = '\nLow mood', y = 'Manipulative\n') +
-    theme_bw(15) +
+    theme_minimal(15) +
     theme(axis.title.y = element_text(angle = 0))
 }
 

### 2021-05-22 Paper.rmd
* Tweaked emotion heatmaps * Added TOC * Removed two regression eqns * Minor edits * updated renv lockfile

@@
   bookdown::html_document2:
+    toc: true
     number_sections: false
@@
 Psychological pain, such as sadness and low mood, probably evolved to motivate victims of adversity to shift their attention to the causes of adversity so as to mitigate its negative fitness consequences and to learn to avoid future such adverse events [@thornhill1989; @andrews2010; @Nesse1990].
-In many cases, social partners could help, and therefore signals of psychological pain, such as sad expressions and crying, probably evolved to indicate need [e.g., @balsters2013].
+In many cases, social partners could help victims, and therefore signals of psychological pain, such as sad expressions and crying, probably evolved to indicate need [e.g., @balsters2013].
 
@@
 Compared to non-depressed individuals, those with depression report about twice as many instances of negative events than non-depressed individuals [@Mazure1998] and more negative events than those with schizophrenia and bipolar depression across multiple studies [@Paykel1994].
-In longitudinal studies, depression onsets soon after a negative event [@KendlerEtAl1999] or coincides with periods where adversity is likely to increase prior to it [e.g., depression starting before a divorce rather than after; @rosenstrom2017].
+In longitudinal studies, depression onsets soon after a negative event [@KendlerEtAl1999] or coincides with periods where adversity is likely to increase prior to it [e.g., depression starting before a divorce rather than after, @rosenstrom2017].
 Additional support for the causal role of negative life events comes from the fact that the relationship between negative events and depression holds true when looking at events outside of one's control, showing that the connection is unlikely to be driven solely by individuals who are already depressed creating situations where negative events are likely to be common [@Hammen2005; @KendlerEtAl1999].
@@
 
-The primary aim of this study was to examine responses to emotional signals that varied from low to high cost, in an experimental vignette study in which a possible victim of adversity asks for help from the participant, but has incentives to exaggerate her need.
 In the bargaining framework, the willingness to delay credibly signals the valuation of current cooperative arrangements, with greater delays indicating lower valuations.
+The primary aim of this study was to examine responses to emotional signals that varied in the extent to which they reduced productivity, which we refer to as costs, in an experimental vignette study in which a possible victim of adversity asks for help from the participant, but has incentives to exaggerate her need.
 As signal cost increased, we predicted that participants would report (1) increased belief in the signaler's claims and (2) increased likelihood of providing help, with (3) the increased likelihood of providing help mediated by the increased belief in the signaler's need.
@@
 After rating their beliefs and actions, and which emotions they thought the potential victim was experiencing, participants were randomized into either the control condition or one of four emotional signals by the victim (in order of increasing signal cost): (1) control condition: a verbal request without additional signaling; (2) crying; (3) mild-depression; (4) depression; and (5) a suicide attempt.
-The signals involved the participant encountering the victim some time after the adverse event and observing, e.g., crying, sad expressions, or poor personal hygiene.
+The signals involved the participant encountering the victim some time after the adverse event and observing, e.g., crying; sad expressions; reduced effort, fatigue, and poor personal hygiene; and suicidal self-injury.
 These descriptions did not use the terms depression, depressed, suicidal, or mental health.
@@
 Although we use the term 'signals' throughout the paper for brevity, we expect that the hypothesized signals of need, like many signals, would also provide information to others in the form of cues [for discussion on the evolution of signals from cues see: @biernaskie2018; @Tiokhin2016; @Steinkopf2015].
-The full text for the signals are available in the SI.
+The complete texts of the signals are available in the SI.
 
@@
 
-The proportion of participants inferring each emotion in each vignette at T1 is depicted in Figure \@ref(fig:t1emotionheatmap), after each signal at T2 in Figure \@ref(fig:t2emotionheatmap), and the change in proportions from T1 to T2 in Figure \@ref(fig:diffemotions).
+The proportion of participants inferring each emotion in each vignette at T1 and after each signal at T2 is depicted in Figure \@ref(fig:emotionheatmaps), and the change in proportions from T1 to T2 in Figure \@ref(fig:diffemotions).
 The increase in inferred depression in the *Depression* and *Suicide attempt* conditions, but not the *Verbal request* and *Crying* conditions, helps validate these signals, as does the increase in inferred suicidality in the *Suicide attempt* condition.
@@
 
-`r extract_eq(models_prereg$Model$m1, intercept='beta', wrap=T)` `r extract_eq(models_prereg$Model$m3, intercept='beta', wrap=T)`
+`r extract_eq(models_prereg$Model$m1, intercept='beta', wrap=T)` 
+`r extract_eq(models_prereg$Model$m3, intercept='beta', wrap=T)`
 
@@
 
-`r extract_eq(models_prereg$Model$m1b, intercept='beta', wrap=T)` `r extract_eq(models_prereg$Model$m3b, intercept='beta', wrap=T)`
-
-The `glm` models we report in the main text were:
-
-`r extract_eq(models$Model$m1, intercept='beta', wrap=T)` `r extract_eq(models$Model$m3, intercept='beta', wrap=T)` `r extract_eq(models$Model$m1b, intercept='beta', wrap=T)` `r extract_eq(models$Model$m3b, intercept='beta', wrap=T)`
+`r extract_eq(models_prereg$Model$m1b, intercept='beta', wrap=T)` 
+`r extract_eq(models_prereg$Model$m3b, intercept='beta', wrap=T)`
+
+The `glm` models we report in the main text:
+
+`r extract_eq(models$Model$m1, intercept='beta', wrap=T)` 
+`r extract_eq(models$Model$m3, intercept='beta', wrap=T)`
 
@@
 
-`r extract_eq(med_prereg$model.m, intercept='beta', wrap=T)` `r extract_eq(med_prereg$model.y, intercept='beta', wrap=T)`
+`r extract_eq(med_prereg$model.m, intercept='beta', wrap=T)` 
+`r extract_eq(med_prereg$model.y, intercept='beta', wrap=T)`
 
@@
 
-`r extract_eq(med1$model.m, intercept='beta', wrap=T)` `r extract_eq(med1$model.y, intercept='beta', wrap=T)`
+`r extract_eq(med1$model.m, intercept='beta', wrap=T)` 
+`r extract_eq(med1$model.y, intercept='beta', wrap=T)`
 
@@
 
-## T1 emotion vs vignette heatmap
+## Emotions in vignette (T1) and signal (T2) conditions
+
+```{r emotionheatmaps, fig.width=10, fig.cap="Each cell represents the proportion of participants who inferred that emotion.
+**Time 1 emotions**: inference of victim's emotional state in each vignette at time 1.
+**Time 2 emotions**: inference of victim's emotional state following the signal at time 2.
+Participants could check multiple emotions from the list.
+Rows ordered by mean proportion across vignettes."}
+
+row_order = rowSums(dfT1emotion_vignette[-1])
+
+dfT1emotion_vignette$name <- factor(dfT1emotion_vignette$name, levels = dfT1emotion_vignette$name[order(row_order)])
+
+values <- seq(0, 1, 0.25)
+
+p1 <- 
+  dfT1emotion_vignette %>% 
+  gather(key = key, value = value, -1) %>%
+  mutate(key = factor(key, levels = c('Thwarted marriage', 'Basketball coach', 'Romantic partner', 'Brother-in-law'))) %>%
+  ggplot(aes_string("key", "name", fill = "value")) +
+  geom_tile() + 
+  scale_fill_viridis_c('Proportion', option = 'B', limits = c(0, 1), breaks = values) +
+  scale_x_discrete(labels = scales::label_wrap(10)) +
+  labs(title = 'T1 emotions', x = "", y = "") + 
+  theme_minimal()
+
+dfT2emotion_signal$name <- factor(dfT2emotion_signal$name, levels = dfT1emotion_vignette$name[order(row_order)])
+
+p2 <- 
+  dfT2emotion_signal %>% 
+  gather(key = key, value = value, -1) %>%
+  mutate(key = factor(key, levels = c('Verbal request', 'Crying', 'Mild depression', 'Depression', 'Suicide attempt'))) %>%
+  ggplot(aes_string("key", "name", fill = "value")) +
+  geom_tile() + 
+  scale_fill_viridis_c('Proportion', option = 'B', limits = c(0, 1), breaks = values) +
+  scale_x_discrete(labels = scales::label_wrap(10)) +
+  labs(title = 'T2 emotions', x = "", y = "") + 
+  theme_minimal() +
+  theme(axis.text.y = element_blank())
+
+p1 + p2 + plot_layout(guides='collect')
+```
 
@@
 Rows and columns ordered with the PCA angle method in the seriation package."}
-hagenheat(dfT1emotion_vignette, rotate_labels = F, seriation_method = 'PCA_angle', viridis_option = 'B') + theme_minimal(15)
-```
-
-## T2 emotion vs signal heatmap
+# hagenheat(dfT1emotion_vignette, rotate_labels = F, seriation_method = 'PCA_angle', viridis_option = 'B') + theme_minimal(15)
+```
+
+<!-- ## T2 emotion vs signal -->
 
@@
 
-hagenheat(dfT2emotion_signal, rotate_labels = F, seriation_method = 'PCA_angle', viridis_option = 'B') + theme_minimal(15)
+# hagenheat(dfT2emotion_signal, rotate_labels = F, seriation_method = 'PCA_angle', viridis_option = 'B') + theme_minimal(15)
 ```
@@
 
-hagenheat(d_diff, rotate_labels = F, seriation_method = 'PCA_angle') + scale_fill_gradient2(low='blue', high='red')
+hagenheat(d_diff, rotate_labels = F, seriation_method = 'PCA_angle', rev_col = T) + scale_fill_gradient2(low='blue', high='red')
 
@@
 ## Feedback distribution by vignette
+
+At the end of the study, participants could optionally provide written feedback about study.
+We classified all feedback into two categories: *Generic* for a few short words, such as 'nice study', or 'thanks'; and *Informative* for one or two sentences commenting on specific aspects of the survey.
+See Figure \@ref(fig:feedbackplot).
 
@@
 ```
+
+We then further classified the *Informative* feedback into six categories: the vignette corresponds to real-life experiences; comments on the vignette (e.g., other ways to respond); what the participant thought about the T3 information that the victim was telling the truth; criticisms of the study (e.g., the attention checks); comments on the study; and an explanation of why the participant acted or failed to act.
+See Figure \@ref(fig:informativeplot).
+The full texts of all comments are in Table \@ref(tab:informativetab).
 

### 2021-05-23 Paper.rmd
Added a toc and css file

@@
     toc: true
+    toc_float: true
+    collapsed: false
     number_sections: false
+    css: style.css
 bibliography: MTBib.bib

### 2021-05-24 Paper.rmd
Reworked a couple of effects plots

--- 2021-05-22 Paper.rmd
@@
 title: "Depression and suicidality as credible signals of need"
-author: "Michael R. Gaffney, Kai Adams, Kristen L. Syme, and Edward H. Hagen"
+author:
+- name: Michael R. Gaffney
+  affiliation: Department of Anthropology, Washington State University
+- name: Kai Adams
+  affiliation: UC Berkeley Haas School of Business
+- name: Kristen L. Syme
+  affiliation: Department of Experimental and Applied Psychology, Vrije Universiteit Amsterdam
+- name: Edward H. Hagen
+  affiliation: Department of Anthropology, Washington State University
+  email: edhagen@wsu.edu
 date: '`r format(Sys.Date(), "%B %d, %Y")`'
@@
     toc: true
+    toc_float: true
     number_sections: false
+    css: style.css
 bibliography: MTBib.bib
@@
 
+if (!dir.exists('Figures')) dir.create('Figures')
+
+figname <- function(){
+  if (!exists('fignum')) fignum <<- 0
+  fignum <<- fignum + 1
+  paste0('Figures/Figure', fignum, '.pdf')
+  }
 ```
@@
 Psychological pain, such as sadness and low mood, probably evolved to motivate victims of adversity to shift their attention to the causes of adversity so as to mitigate its negative fitness consequences and to learn to avoid future such adverse events [@thornhill1989; @andrews2010; @Nesse1990].
-In many cases, social partners could help victims, and therefore signals of psychological pain, such as sad expressions and crying, probably evolved to indicate need [e.g., @balsters2013].
+In many cases, social partners could help victims, and therefore signals of psychological pain, such as sad expressions and crying, probably evolved to indicate need [e.g., @darwin1872; @bowlby1980; @balsters2013].
 
@@
 
-@Hagen2003 proposed that physical aggression and depression were complementary strategies to resolve conflicts in interdependent relationships.
+@Hagen2003 proposed that physical aggression and core depression symptoms like loss of interest in virtually all activities were complementary strategies to resolve conflicts in interdependent relationships.
 @SellEtAl2009 found that physically formidable individuals were more prone to anger, prevailed more in conflicts of interest, and considered themselves entitled to better treatment.
@@
 
-@Hagen2003 proposed that the substantial reduction in productivity in depression corresponds to a willingness to delay, and is therefore a credible signal of low valuation and need.
+@Hagen2003 proposed that the substantial reduction in productivity that characterizes many cases of depression corresponds to a willingness to delay, and is therefore a credible signal of low valuation and need.
 In other words, reduced productivity is relatively less costly for those whose efforts are currently not yielding many fitness benefits than for those whose efforts are yielding substantial benefits.
@@
 
-Suicidality is closely linked to depression.
 Suicidal ideation is one of nine diagnostic criteria for a major depressive episode (MDE) [@dsm5], it is associated with depression across cultures [@haroz2017], and depression is a major risk factor for suicidal behavior [@hawton2013].
@@
 library(hrafsuicidedata)
+
+plot_cdc <-
   cdc2 %>% 
@@
   theme(axis.title.y = element_text(angle = 0, hjust=0))
+
+plot_cdc
+ggsave(figname(), plot_cdc)
 ```
@@
 Some evolutionary theorists have questioned the bargaining model based on evidence that depression is aversive to social partners [@nettle2004; @allen2006; @nesse2006; @myers2016].
-These critics failed to recognize the central role of *conflict* in the signaling/bargaining models.
+These critics failed to recognize the central role of *conflict* in the model.
 Anger is aversive to targeted social partners, yet it is probably an adaptation that exploits advantages in physical or social formidability to force concessions from them [@SellEtAl2009].
 Aversive responses to depressive bargaining are likewise expected throughout the process, with potential helpers signaling the costliness of providing support in turn.
-Importantly, as with anger, aversive responses to depression do not prevent concessions by interdependent social partners [@SymeHagen2021].
+Importantly, as with anger, aversive responses to depression encourage concessions by interdependent social partners [@SymeHagen2021].
 
@@
 We also asked which emotions participants felt the signaler was experiencing using a multiple choice question in which they could select as many options as they would like.
-This included emotions directly related to the signals (e.g., sad, depressed, and suicidal), states which suggest genuine need (traumatized and violated), and states which suggest deception (e.g., deviousness or jealousy).
+This included emotions directly related to the signals (e.g., sad, depressed, and suicidal), states which suggest genuine need (traumatized and violated), states which suggest deception (e.g., deviousness or jealousy), and was the victim mentally ill.
 The complete list can be found in the SI.
@@
 
+x <- figname()
 knitr::include_graphics('paths.svg')
@@
 plot_T1Belief_T1Action 
+ggsave(figname(), plot_T1Belief_T1Action)
 ```
@@
 See Figure \@ref(fig:beliefeffect) and models m1 and m3 in Tables \@ref(tab:regressiontables) and \@ref(tab:anovatables).
-(Results for the preregistered OLS models were very similar; see Figures \@ref(fig:preregbelief) and \@ref(fig:preregbeliefB).)
-
-The marginal between-subjects effect of the high cost *Suicide attempt* vs.
+Results for the preregistered OLS models were very similar; see Figures \@ref(fig:preregbelief) and \@ref(fig:preregbeliefB).
+The within-subject effects of each signal are depicted in Figure \@ref(fig:rawbeliefactions2d).
+
+```{r beliefeffect, fig.width=8, fig.height=4, fig.cap=paste0("The mean effects of the signals on *T2 Belief* and *T2 Action*, controlling for *T1 Belief* and *T1 Action*, respectively (original 0-100 scale rescaled to 0-1).
+Effects plotted for T1 values set to their median value (*T1 Belief*=", median(d$T1Belief, na.rm=T), ", *T1 Action*=", median(d$T1Action, na.rm=T), ").
+Fit using generalized linear regression models with the quasibinomial family.
+Bars are 95% CIs.
+Dots are *T2 Belief* and *T2 Action* values; dot size = number of overlapping data points.
+For coefficents, p-values, and other statistics, see models m1 and m3 in Tables \\@ref(tab:regressiontables) and \\@ref(tab:anovatables).")}
+# plot_beliefeffect <-
+#   (effectsPlots$m1plot + theme(axis.text.x = element_blank()))/effectsPlots$m3plot + plot_layout(ncol = 1) & theme(plot.margin = unit(c(0,0,0,0), units = 'mm'))
+
+d_tmp <-
+  d %>% 
+  dplyr::select(signal, T2Action, T2Belief) %>% 
+  pivot_longer(-signal, names_to = 'Outcome') %>% 
+  mutate(Outcome = str_remove(Outcome, 'T2'))
+
+d_m1m3 <- bind_rows(Belief = effectsPlots$m1plot$fit, Action = effectsPlots$m3plot$fit, .id = 'Outcome')
+
+plot_actionbeliefeffect <-
+  ggplot(d_m1m3, aes(visregFit, signal, xmin = visregLwr, xmax = visregUpr, colour = Outcome, group = Outcome)) +
+  geom_errorbarh(lwd = 4.5, alpha = 0.75, position = position_dodge(width = 0.6), height = 0) +
+  geom_point(position = position_dodge(width = 0.6), colour = 'black') +
+  geom_count(data = d_tmp, aes(value, signal, colour = Outcome), inherit.aes = F, alpha = 0.25, position = position_dodge(width = 0.6)) +
+  scale_color_viridis_d(option = 'B', begin = 0.2, end = 0.8) +
+  scale_x_continuous(limits = c(0, 1), breaks = c(0, 0.25, 0.5, 0.75, 1)) +
+  scale_size_area() +
+  guides(color=guide_legend(reverse = T, override.aes = list(size=3))) +
+  labs(x = '\nT2 Belief/Action', y = '') +
+  theme_minimal(15)
+
+plot_actionbeliefeffect
+ggsave(figname(), plot_actionbeliefeffect)
+rm(d_tmp, d_m1m3)
+```
+
+The estimated marginal mean between-subjects effect of the high cost *Suicide attempt* vs.
 the *Verbal request* control on T2 *Belief* (averaging over all four vignettes and all values of T1 *Belief*) was an increase of `r fmt_margins(models$Margins$m1, 'signalSuicide attempt')` points on the original 0-100 point scale.
@@
 
-```{r beliefeffect, fig.width=6, fig.height=8, fig.cap=paste0("The effect of the signals on *T2 Belief* (top) and *T2 Action* (bottom) controlling for *T1 Belief* and *T1 Action*, respectively.
-Effects plotted for T1 values set to their median value (*T1 Belief*=", median(d$T1Belief, na.rm=T), ", *T1 Action*=", median(d$T1Action, na.rm=T), ").
-Fit using generalized linear regression models with the quasibinomial family.
-Grey bars are 95% CIs.
-For coefficents, p-values, and other statistics, see models m1 and m3 in Tables \\@ref(tab:regressiontables) and \\@ref(tab:anovatables).")}
-(effectsPlots$m1plot + theme(axis.text.x = element_blank()))/effectsPlots$m3plot + plot_layout(ncol = 1) & theme(plot.margin = unit(c(0,0,0,0), units = 'mm'))
-```
-
 <!-- Within-subjects, the average effect across all signals on *Belief* at T2 compared to T1 was `r inline_ttest(signal_belief_ttest)`, and on *Action* was `r inline_ttest(signal_action_ttest)` (on the original 0-100 point scale).
@@
 -->
-
-The within-subject effects of each signal are depicted in Figure \@ref(fig:rawbeliefactions2d).
 
@@
 all_mediations$plot
+ggsave(figname(), all_mediations$plot)
 ```
@@
 ## Exploratory: Costlier signals decrease perceived manipulation and increase perceived low mood
-
-The proportion of participants inferring each emotion in each vignette at T1 and after each signal at T2 is depicted in Figure \@ref(fig:emotionheatmaps), and the change in proportions from T1 to T2 in Figure \@ref(fig:diffemotions).
-The increase in inferred depression in the *Depression* and *Suicide attempt* conditions, but not the *Verbal request* and *Crying* conditions, helps validate these signals, as does the increase in inferred suicidality in the *Suicide attempt* condition.
 
@@
 plot_emotions
-```
+ggsave(figname(), plot_emotions)
+```
+
+```{r}
+mentallyIll <- signif(100*mean(d$T1MentallyIll), 2)
+
+miT2 <- 
+  as_tibble(xtabs(~T2MentallyIll + signal + vignette, d)) %>%
+  mutate(T2MentallyIll = as.numeric(T2MentallyIll)) %>% 
+  group_by(signal) %>% 
+  summarise(percent = signif(100*sum(T2MentallyIll*n)/sum(n), 2))
+
+```
+
+The proportion of participants inferring each emotion in each vignette at T1 and after each signal at T2 is depicted in Figure \@ref(fig:emotionheatmaps), and the change in proportions from T1 to T2 in Figure \@ref(fig:diffemotions).
+The increase in inferred depression in the *Depression* and *Suicide attempt* conditions, but not the *Verbal request* and *Crying* conditions, helps validate these signals, as does the increase in inferred suicidality in the *Suicide attempt* condition.
+
+At baseline (T1), `r mentallyIll`% of participants thought the victim was mentally ill, which decreased slightly at T2 in the *Verbal request* and *Crying* conditions (`r miT2$percent[miT2$signal=='Crying']`%), and then increased with signal cost to `r miT2$percent[miT2$signal=='Mild depression']`% in *Mild depression*, `r miT2$percent[miT2$signal=='Depression']`% in *Depression*, and `r miT2$percent[miT2$signal=='Suicide attempt']`% in *Suicide attempt*, with some variation by vignette.
+See Figures \@ref(fig:mentallyillT1) and \@ref(fig:mentallyillT2).
 
@@
 ecdf_plot
-```
-
-```{r beliefvignette, fig.width=8, fig.height=8, fig.cap=paste0("The effect of the signals on *T2 Belief* (top) and *T2 Action* (bottom) in each vignette, controlling for T1 values of Belief and Action, respectively.
+ggsave(figname(), ecdf_plot)
+```
+
+```{r beliefvignette, fig.width=8, fig.height=6, fig.cap=paste0("The effect of the signals on *T2 Belief* and *T2 Action* in each vignette, controlling for T1 values of Belief and Action, respectively.
 Ratings rescaled to [0, 1].
@@
 Fit using generalized linear regression models with the quasibinomial family.
-Grey bars are 95% CIs.
+Bars are 95% CIs.
 For coefficents, p-values, and other statistics, see models m2 and m4 in Tables \\@ref(tab:regressiontables) and \\@ref(tab:anovatables).")}
-(effectsPlots$m2plot + theme(axis.text.x = element_blank()))/effectsPlots$m4plot + plot_layout(ncol = 1) & theme(plot.margin = unit(c(0,0,0,0), units = 'mm'))
+# plot_beliefvignette <-
+#   (effectsPlots$m2plot + theme(axis.text.x = element_blank()))/effectsPlots$m4plot + plot_layout(ncol = 1) & theme(plot.margin = unit(c(0,0,0,0), units = 'mm'))
+
+# d_tmp <-
+#   d %>% 
+#   dplyr::select(signal, vignette, T2Action, T2Belief) %>% 
+#   pivot_longer(-c(signal, vignette), names_to = 'Outcome', values_to = 'visregFit') %>% 
+#   mutate(
+#     Outcome = str_remove(Outcome, 'T2'),
+#     visregLwr = 0,
+#     visregUpr = 0
+#     )
+
+d_m2m4 <- 
+  bind_rows(Belief = effectsPlots$m2plot$fit, Action = effectsPlots$m4plot$fit, .id = 'Outcome') %>% 
+  dplyr::select(Outcome, signal, vignette, visregFit, visregLwr, visregUpr)
+
+plot_beliefvignette <-
+  ggplot(d_m2m4, aes(signal, visregFit, ymin = visregLwr, ymax = visregUpr, colour = Outcome, group = Outcome)) +
+  geom_errorbar(lwd = 3, alpha = 0.75, position = position_dodge(width = 0.6), width = 0) +
+  geom_point(position = position_dodge(width = 0.6), colour = 'black') +
+  scale_color_viridis_d(option = 'B', begin = 0.2, end = 0.8) +
+  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.25, 0.5, 0.75, 1)) +
+  guides(color=guide_legend(reverse = F, override.aes = list(size=3))) +
+  labs(x = '', y = '') +
+  facet_wrap(~vignette, ncol = 4, strip.position = 'top') +
+  theme_bw(15) + 
+  theme(
+    axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5),
+    legend.position = 'top'
+    )
+
+plot_beliefvignette
+ggsave(figname(), plot_beliefvignette)
 ```
@@
 
+plot_demographicsignal <-
   effectsPlots_US$m12plot + 
@@
     theme(axis.text.y = element_blank(), axis.title.y = element_blank())
+
+plot_demographicsignal
+ggsave(figname(), plot_demographicsignal)
 ```
@@
 Grey bars are 95% CIs."}
+plot_indiademo<-
   (effectsPlots_India$m12plot + xlab('Education (years)') + effectsPlots_India$m13plot) / effectsPlots_India$m17plot
+
+plot_indiademo
+ggsave(figname(), plot_indiademo)
 ```
@@
 
-The main limitation of this study is that is has less ecological validity than real-world observations of depressed individuals interacting with their social partners.
-This may have biased results in a pro-signaler direction if the lack of real costs of helping made support feel less costly or if there was a social desirability bias toward helping [@grimm2010].
-It may have also biased participants against helping if they could not fully imagine the characters in the story as kin or important cooperative partners, and the survey's short duration may have weakened the strength of the costlier signals as bargaining tools.
+This study has less ecological validity than real-world observations of depressed individuals interacting with their social partners, which might have biased results in a pro-signaler direction if the lack of real costs of helping made support feel less costly or if there was a social desirability bias toward helping [@grimm2010].
+It may have also biased participants against helping if they could not fully imagine the characters in the story as kin or interdependent partners, and the survey's short duration may have weakened the strength of the costlier signals as bargaining tools.
 
@@
 Another concern relevant to all vignettes is that our decision to anchor the T1 sliders at 0 may have resulted in participants being more likely to report extreme values.
+
+Finally, we adopted game theory models of bargaining with incomplete information as our theoretical framework, but there are many other models of credible signaling [e.g., @szamado2011], including for need [@szamado2019] and suicidality [@Rosenthal1993].
+If depression and suicidality involve signaling, it might be better explained by a different model.
 

### 2021-05-24 R/functions.R

@@ -133,7 +133,12 @@ effect_plot <- function(m, ...){
   args$gg <- T
   args$scale <- 'response'
 
-  p <- exec('visreg', !!!args) +
+  p <- exec('visreg', !!!args)
+
+  if ('plot' %in% names(args) && !args$plot) return(p)
+
+  p <-
+    p +
     ylim(0, 1) +
     ylab(args$ylbl) +
     theme_bw(15) +
@@ -150,12 +155,12 @@ effect_plot <- function(m, ...){
 
 effect_plots <- function(models, data){
   list(
-    m1plot = effect_plot(fit=models$m1, xvar='signal', ylbl='T2 Belief', data=data),
+    m1plot = effect_plot(fit=models$m1, xvar='signal', ylbl='T2 Belief', data=data, plot = F),
     m1bplot = effect_plot(fit=models$m1b, xvar='signal', by='T1Belief', ylbl='T2 Belief', data=data),
-    m2plot = effect_plot(fit=models$m2, xvar='signal', by='vignette', ylbl='T2 Belief', data=data),
-    m3plot = effect_plot(fit=models$m3, xvar='signal', ylbl='T2 Action', data=data),
+    m2plot = effect_plot(fit=models$m2, xvar='signal', by='vignette', ylbl='T2 Belief', data=data, plot = F),
+    m3plot = effect_plot(fit=models$m3, xvar='signal', ylbl='T2 Action', data=data, plot = F),
     m3bplot = effect_plot(fit=models$m3b, xvar='signal', by='T1Action', ylbl='T2 Action', data=data),
-    m4plot = effect_plot(fit=models$m4, xvar='signal', by='vignette', ylbl='T2 Action', data=data),
+    m4plot = effect_plot(fit=models$m4, xvar='signal', by='vignette', ylbl='T2 Action', data=data, plot = F),
     m12plot = effect_plot(fit=models$m12, xvar='Sex', ylbl='T2 Belief', data=data),
     m12bplot = effect_plot(fit=models$m12, xvar='Age', ylbl='T2 Belief', data=data),
     m13plot = effect_plot(fit=models$m13, xvar='Sex', ylbl='T2 Action', data=data),
@@ -196,6 +201,20 @@ visreg_diff <- function(m, vignette, signal1, signal2, d, sig = 2){
   v2 <- fit$visregFit[fit$signal==signal2 & fit$vignette==vignette]
   signif(100*(v1 - v2), sig)
 }
+
+
[…]

### 2021-05-25 Paper.rmd
Moved demographic plots to SI
Added ANOVA stats to confirmatory results section, and fixed broken table links

@@
 date: '`r format(Sys.Date(), "%B %d, %Y")`'
-always_allow_html: false
+always_allow_html: true
 output:
@@
 Major depression and suicide are generally viewed as pathological responses to stress that elicit aversive responses from others.
-Alternatively, depression and suicide attempts might involve honest signals of need in response to stress that can increase support from reluctant others.
+Alternatively, depression and suicidality might involve honest signals of need in response to stress that can increase support from reluctant others.
 To test this hypothesis, we examined responses to emotional signals in an experimental vignette study involving claims of substantial need in the presence of conflicts of interest and private information about whether the signaler was actually in need.
-In a sample of 1,240 participants recruited from Amazon Mechanical Turk, costlier signals like depression and suicide attempts resulted in greater perceptions of need, reduced perceptions of manipulativeness, and increased likelihood of support compared to simple verbal requests and crying without further symptoms.
+In a sample of 1,240 participants recruited from Amazon Mechanical Turk, costlier signals like depression and suicidality resulted in greater perceptions of need, reduced perceptions of manipulativeness, and increased likelihood of support compared to simple verbal requests and crying without further symptoms.
 Additionally, as predicted, the effect of signaling on likelihood of support was largely mediated by the effect of signaling on belief in need.
-Our results support the hypothesis that depression and suicide attempts, apparent human universals, are credible signals of need.
+Our results support the hypothesis that depression and suicidality, apparent human universals, are credible signals of need.
 
@@
 
-```
-
-As predicted, there was a strong statistically significant positive causal effect of the ordinal signal on *T2 Belief* and *T2 Action* (controlling for *T1 Belief* and *T1 Action*, respectively), with the effect of each signal increasing in the predicted rank order (verbal request, crying, mild depression, depression, suicide attempt).
+m1_lrX2 = signif(models$Anova$m1$`LR Chisq`[2], 3)
+m1_df = models$Anova$m1$Df[2]
+m1_p = fmt_sci(signif(models$Anova$m1$`Pr(>Chisq)`[2], 2))
+
+m3_lrX2 = signif(models$Anova$m3$`LR Chisq`[2], 3)
+m3_df = models$Anova$m3$Df[2]
+m3_p = fmt_sci(signif(models$Anova$m3$`Pr(>Chisq)`[2], 2))
+
+```
+
+As predicted, there was a strong statistically significant positive causal effect of the ordinal signal on *T2 Belief* (LR $\chi^2(`r m1_df`)=`r m1_lrX2`$, $p=`r m1_p`$) and *T2 Action* (LR $\chi^2(`r m3_df`)=`r m3_lrX2`$, $p=`r m3_p`$), controlling for *T1 Belief* and *T1 Action*, respectively, with the effect of each signal increasing in the predicted rank order (verbal request, crying, mild depression, depression, suicide attempt).
 See Figure \@ref(fig:beliefeffect) and models m1 and m3 in Tables \@ref(tab:regressiontables) and \@ref(tab:anovatables).
-Results for the preregistered OLS models were very similar; see Figures \@ref(fig:preregbelief) and \@ref(fig:preregbeliefB).
+Results for the preregistered OLS models were very similar; see Figures \@ref(fig:preregbelief) and \@ref(fig:preregbeliefB), and Tables \@ref(tab:preregtable) and \@ref(tab:prereganova).
 The within-subject effects of each signal are depicted in Figure \@ref(fig:rawbeliefactions2d).
@@
 The equivalent increase for T2 *Action* was `r fmt_margins(models$Margins$m3, 'signalSuicide attempt')` points.
-Given that the standard deviations of T2 *Belief* and *Action* are `r signif(sd(100*d$T2Belief), 2)` and `r signif(sd(100*d$T2Action), 2)`, respectively, these represent increases of `r suicide_belief_eff` and `r suicide_action_eff` SD's, respectively.
+Given that the standard deviations of T2 *Belief* and *Action* are `r signif(sd(100*d$T2Belief), 2)` and `r signif(sd(100*d$T2Action), 2)`, respectively, these represent increases of `r suicide_belief_eff` and `r suicide_action_eff` standard deviations, respectively.
 
@@
 
-```{r demographicsignal, fig.width=11, fig.height=8, fig.cap="Sociodemographic associations with *T2 Belief* (top) and *T2 Action* (bottom) in US participants.
-Each model controlled for *T1 Belief* or *T1 Action*, vignette, Education, and Income.
-Significant associations displayed here.
-Estimated using generalized linear regression models with the quasibinomial family.
-Grey bars are 95% CIs."}
-
-plot_demographicsignal <-
-  effectsPlots_US$m12plot + 
-    theme(axis.text.x = element_blank()) +
-effectsPlots_US$m12bplot + 
-    theme(
-      axis.text = element_blank(), 
-      axis.title.y = element_blank(), 
-      axis.title.x = element_blank()
-      ) + 
-effectsPlots_US$m13plot + 
-effectsPlots_US$m13bplot +
-    theme(axis.text.y = element_blank(), axis.title.y = element_blank())
-
-plot_demographicsignal
-ggsave(figname(), plot_demographicsignal)
-```
-
 In the Indian sample and vignette, in contrast, males were more likely to help the victim than females, those with more years of education were less likely to believe the victim, and there was a marked increase in likelihood of helping among older individuals in the suicide signal condition.
@@
 See Figure \@ref(fig:indiademographics).
-
-```{r indiademographics, fig.width=10, fig.height=8, fig.cap="Sociodemographic associations with *T2 Belief* and *T2 Action* in Indian participants (Thwarted marriage vignette).
-Each model included *T1 Belief* or *T1 Action*, Income, Age, Sex, Years of education, and signal.
-Significant associations displayed here.
-Estimated using generalized linear regression models with the quasibinomial family.
-Grey bars are 95% CIs."}
-plot_indiademo<-
-  (effectsPlots_India$m12plot + xlab('Education (years)') + effectsPlots_India$m13plot) / effectsPlots_India$m17plot
-
-plot_indiademo
-ggsave(figname(), plot_indiademo)
-```
 
@@
 
+## Exploratory demographic associations
+
+```{r demographicsignal, fig.width=11, fig.height=8, fig.cap="Sociodemographic associations with *T2 Belief* (top) and *T2 Action* (bottom) in US participants.
+Each model controlled for *T1 Belief* or *T1 Action*, vignette, Education, and Income.
+Significant associations displayed here.
+Estimated using generalized linear regression models with the quasibinomial family.
+Grey bars are 95% CIs."}
+
+plot_demographicsignal <-
+  effectsPlots_US$m12plot + 
+    theme(axis.text.x = element_blank()) +
+effectsPlots_US$m12bplot + 
+    theme(
+      axis.text = element_blank(), 
+      axis.title.y = element_blank(), 
+      axis.title.x = element_blank()
+      ) + 
+effectsPlots_US$m13plot + 
+effectsPlots_US$m13bplot +
+    theme(axis.text.y = element_blank(), axis.title.y = element_blank())
+
+plot_demographicsignal
+# ggsave(figname(), plot_demographicsignal)
+```
+
+```{r indiademographics, fig.width=10, fig.height=8, fig.cap="Sociodemographic associations with *T2 Belief* and *T2 Action* in Indian participants (Thwarted marriage vignette).
+Each model included *T1 Belief* or *T1 Action*, Income, Age, Sex, Years of education, and signal.
+Significant associations displayed here.
+Estimated using generalized linear regression models with the quasibinomial family.
+Grey bars are 95% CIs."}
+plot_indiademo<-
+  (effectsPlots_India$m12plot + xlab('Education (years)') + effectsPlots_India$m13plot) / effectsPlots_India$m17plot
+
+plot_indiademo
+# ggsave(figname(), plot_indiademo)
+```
+
 ## Validity check: T3 Action vs. T2 Action
@@
 ```{r regressiontables}
-tmp <- models %>% 
+tmp <- 
+  models %>% 
   dplyr::filter(Name %in% c('m1', 'm2', 'm3', 'm4', 'm21', 'm24', 'm25'))
@@
 
-```{r preregtables}
+```{r preregtable}
 regressiontable(models_prereg$Model, caption = 'OLS regression coefficients for preregistered linear regression models.')
@@
 
-```{r prepreganova}
+```{r prereganova}
 bind_rows(models_prereg$TidyANOVA, .id = 'Model') %>%

### 2021-05-25 R/functions.R

@@ -102,6 +102,7 @@ fit_models <- function(data, formulas, family = 'quasibinomial'){
   names(d$Model) <- d$Name
   names(d$RobustCI) <- d$Name
   names(d$TidyModel) <- d$Name
+  names(d$Anova) <- d$Name
   names(d$TidyANOVA) <- d$Name
   names(d$Margins) <- d$Name
 

### 2021-05-25 Paper.rmd
Minor edits

@@
 
-Raymond Firth was one of the first to view suicidality as a gamble to improve one's circumstances in the here and now.
+Raymond Firth, an anthropologist who worked in the southwestern Pacific, was one of the first to view suicidality as a gamble to improve one's circumstances in the here and now.
 Based on observations that suicide attempts often followed loss or conflict and varied substantially in their likelihood of death, he argued that a sizable subset of the suicide attempts among the Tikopia were not meant to end in death but instead were a means to elicit attention, status, or immediate reintegration into the community following negative events [@firth1936; @Firth:1961].
@@
 In the bargaining framework, the willingness to delay credibly signals the valuation of current cooperative arrangements, with greater delays indicating lower valuations.
-The primary aim of this study was to examine responses to emotional signals that varied in the extent to which they reduced productivity, which we refer to as costs, in an experimental vignette study in which a possible victim of adversity asks for help from the participant, but has incentives to exaggerate her need.
+The primary aim of this study was to examine responses to emotional signals that varied in the extent to which they reduced productivity or put future productivity at risk, which we refer to as costs, in an experimental vignette study in which a possible victim of adversity asks for help from the participant, but has incentives to exaggerate her need.
 As signal cost increased, we predicted that participants would report (1) increased belief in the signaler's claims and (2) increased likelihood of providing help, with (3) the increased likelihood of providing help mediated by the increased belief in the signaler's need.
@@
 Participants for this study were recruited from Amazon Mechanical Turk, a crowdsourcing platform that allows for the creation of Human Intelligence Tasks (HITs) that workers can complete for pay.
-As Amazon provides the infrastructure, it allows for a relatively low-cost way of collecting data for academic research at the cost of the data not being representative of any real population [@thomas2017].
-Despite this limitation, MTurk samples have a wider range of ages and incomes than most university samples [@kennedy2020; @DworkinEtAl2016; @thomas2017].
-US MTurk samples also differ from the general US population, mainly in being younger, more educated, and lower income [@RossEtAl2010; @boas2020].
+As Amazon provides the infrastructure, it allows for a relatively low-cost way of collecting data for academic research, with the disadvantage that the data are not representative of any real population [@thomas2017].
+Despite this limitation, MTurk samples have a wider range of ages and incomes than most university samples, and therefore might be more informative about the general population [@kennedy2020; @DworkinEtAl2016; @thomas2017].
+US MTurk samples do differ from the general US population, though, mainly in being younger, more educated, and lower income [@RossEtAl2010; @boas2020].
 
@@
 
-**Basketball coach vignette**: Each participant was asked to imagine that they are a university athletic director.
+**Basketball coach vignette**: Participants were asked to imagine that they are a university athletic director.
 The star player on the women's basketball team comes to the participant and claims she was sexually assaulted by her head coach, a physically powerful man.
@@
 
-**Brother-in-law vignette**: Each participant was asked to imagine that they let their sister, brother-in-law, and niece move in with them after their sister's family lost their house in a fire.
+**Brother-in-law vignette**: Participants were asked to imagine that they let their sister, brother-in-law, and niece move in with them after their sister's family lost their house in a fire.
 During this time, the participant's 15 year old daughter becomes jealous of her cousin, who appears to be a social competitor.
@@
 
-**Romantic partner vignette**: Each participant was asked to imagine that they found a highly desirable romantic partner after years of being single.
+**Romantic partner vignette**: Participants were asked to imagine that they found a highly desirable romantic partner after years of being single.
 However, the participant's 13-year-old daughter, who has a history of interfering with the participant's past relationships, is clearly unhappy with the new partner.
-After a period of sustained conflict with both the participant and the romantic partner, she accuses the romantic partner of physically assaulting her, but cannot produce any evidence.
+After a period of sustained conflict with both the participant and the romantic partner, the daughter accuses the romantic partner of physically assaulting her, but cannot produce any evidence.
 
 **Thwarted marriage vignette**: Indian sample only.
-Each participant was asked to imagine that their family was trying to arrange a dowry for their older daughter (the signaler in this vignette) so she can marry a man she already loves, while still saving enough money for their younger daughter's dowry.
+Participants were asked to imagine that their family was trying to arrange a dowry for their older daughter (the signaler in this vignette) so she can marry a man she already loves, while still saving enough money for their younger daughter's dowry.
 After the man's family demands more money, the participant's family tries to find a second man, who the older daughter claims to find unattractive.
@@
 We also asked which emotions participants felt the signaler was experiencing using a multiple choice question in which they could select as many options as they would like.
-This included emotions directly related to the signals (e.g., sad, depressed, and suicidal), states which suggest genuine need (traumatized and violated), states which suggest deception (e.g., deviousness or jealousy), and was the victim mentally ill.
+This included emotions directly related to the signals (e.g., sad, depressed, and suicidal), states which suggest genuine need (traumatized and violated), states which suggest deception (e.g., deviousness or jealousy), and if the victim mentally ill.
 The complete list can be found in the SI.
@@
 
-As both a validity check and a way to understand the degree participants would be willing to help if they believed the participant completely, we presented participants with strong evidence that the claims were true.
+As both a validity check and a way to understand the degree participants would be willing to help if they believed the participant completely, at T3 we presented participants with strong evidence that the claims were true.
 In the US sample, this involved telling participants there was video evidence of the event in question occurring or a similar event after the fact.
-With the thwarted marriage vignette, this involved the participant seeing the man their daughter wants to marry trash talk their daughter and their family.
+With the thwarted marriage vignette, this involved the participant seeing the man their daughter wants to marry trash-talk their daughter and their family.
 Participants were then asked to rate their likelihood of acting (*T3 Action*).
@@
 
-We therefore fit models of our two outcome variables (which we rescaled to the continuous interval [0, 1]) in five ways.
-First, we fit the preregistered OLS models (reported in the SI).
-Second, we fit fractional regression models, introduced in a seminal paper by @papke1996 for continuous outcomes on the interval [0, 1], which, in brief, involve fitting a quasi-likelihood version of logistic regression with robust standard errors.
+We therefore fit models of our two outcome variables with the preregistered OLS models (reported in the SI) and four variants of logistic regression (for which we rescaled the 0-100 outcomes to the continuous interval [0, 1]).
+First, we fit fractional regression models, introduced in a seminal paper by @papke1996 for continuous outcomes on the interval [0, 1], which, in brief, involve fitting a quasi-likelihood version of logistic regression with robust standard errors.
 This method is implemented in the `frm` package [@ramalho2019].
-Third, we fit GLM logistic regression models, computing 95% CI's via bootstrapping, using the `glmmboot` package created to model continuous outcomes on [0, 1] [@humphrey2020].
-Fourth, we fit GLM models with the quasibinomial family and logit link using the `glm` function in R stats library, which can fit continuous outcomes on [0, 1].
-Finally, we computed robust standard errors and 95% confidence intervals from the quasibinomial models using the `sandwich` package [@zeileis2006].
-The estimated coefficients, standard errors, and confidence intervals produced by the latter four methods were *very* similar, and often identical (see Figure \@ref(fig:modelcompareplots).
+Second, we fit GLM logistic regression models, computing 95% CI's via bootstrapping, using the `glmmboot` package created to model continuous outcomes on [0, 1] [@humphrey2020].
+Third, we fit GLM models with the quasibinomial family and logit link using the `glm` function in R stats library, which can fit continuous outcomes on [0, 1].
+Fourth, we computed robust standard errors and 95% confidence intervals from the quasibinomial models using the `sandwich` package [@zeileis2006].
+The estimated coefficients, standard errors, and confidence intervals produced by these four methods were *very* similar, and often identical (see Figure \@ref(fig:modelcompareplots).
 We therefore proceeded to fit and report models using `glm` with the quasibinomial family and logit link because model objects produced by this function are compatible with numerous other R packages for summarizing and plotting effects.
@@
 *Verbal request* control.
+We did the same for *Suicide attempt*.
 See Figure \@ref(fig:medmodel).
@@
 
-Across the four vignettes, mean belief of the victim was relatively low at baseline (T1), Mean = `r signif(mean(d$T1Belief, na.rm = T), 2)`, albeit with wide variation, SD = `r signif(sd(d$T1Belief, na.rm=T), 2)`; `r sum(d$T1Belief==0)` participants (`r 100*signif(sum(d$T1Belief==0)/nrow(d), 2)`%) rated their belief = 0, and `r sum(d$T1Belief==1)` participants (`r 100*signif(sum(d$T1Belief==1)/nrow(d), 2)`%) rated it as = 1.
+Across the four vignettes, mean belief of the victim (after rescaling original 0-100 values to 0-1) was relatively low at baseline (T1), Mean = `r signif(mean(d$T1Belief, na.rm = T), 2)`, albeit with wide variation, SD = `r signif(sd(d$T1Belief, na.rm=T), 2)`; `r sum(d$T1Belief==0)` participants (`r 100*signif(sum(d$T1Belief==0)/nrow(d), 2)`%) rated their belief = 0, and `r sum(d$T1Belief==1)` participants (`r 100*signif(sum(d$T1Belief==1)/nrow(d), 2)`%) rated it as = 1.
 The distribution of likelihood of helping the victim (action) was similar, Mean = `r signif(mean(d$T1Action, na.rm = T), 2)`, SD = `r signif(sd(d$T1Action, na.rm=T), 2)`, with `r sum(d$T1Action==0)` participants (`r 100*signif(sum(d$T1Action==0)/nrow(d), 2)`%) rating their action = 0, and `r sum(d$T1Action==1)` participants (`r 100*signif(sum(d$T1Action==1)/nrow(d), 2)`%) rated action as = 1.
@@
 
-The effects of the signals on rated beliefs and actions differed substantially by vignette, which we display in three ways for each signal in each vignette: estimated cumulative distributions plots, which show the entire distributions of rated beliefs and actions, including which conditions have high fractions of 0's and 1's (Figures \@ref(fig:ecdf)); regression estimates of the mean effects of the signals on beliefs and actions by vignette (Figure \@ref(fig:beliefvignette)); and between- and within-subjects signal effect sizes by vignette (Figures \@ref(fig:effectsizes) and \@ref(fig:effectsizes2)).
+The effects of the signals on rated beliefs and actions differed substantially by vignette, which we display in three ways for each signal in each vignette: estimated cumulative distributions plots, which show the entire distributions of rated beliefs and actions, including which conditions have high fractions of 0's and 1's (Figures \@ref(fig:ecdf)); regression estimates of the mean effects of the signals on beliefs and actions by vignette (Figure \@ref(fig:beliefvignette)); and between- and within-subjects signal effect sizes (Cohen's d) by vignette (Figures \@ref(fig:effectsizes) and \@ref(fig:effectsizes2)).
 
@@
 
-The effect of *Suicide attempt* on belief at T2 was similar to the *Depression* conditions across vignettes, but it resulted in greater likelihood of support.
+The effect of *Suicide attempt* on *T2 Belief* was similar to the *Depression* conditions across vignettes, but it resulted in greater *T2 Action*.
 One interpretation is that although some participants did not believe the victim's story, her signal nevertheless convinced them that she needed help.
@@
 
-There were minor associations of age and sex with belief and action in the US participants, with both being higher among females and younger individuals.
+There were minor associations of age and sex with *T2 Belief* and *T2 Action* in the US participants, with both being higher among females and younger individuals.
 The US vignettes all involved assaults against young women, which might have been more salient to female and younger participants.
-In the Indian sample, high baseline belief and action were somewhat lower among those with more education and among females, respectively.
+In the Indian sample, *T2 Belief* and *T2 Action* were somewhat lower among those with more education and among females, respectively.
 Costlier signals, suicidality in particular, had a larger effect among older individuals, perhaps because older individuals were more likely to have children of marriageable age, like the victim in the vignette.
@@
 Depression is costly, sometimes resulting in death by suicide.
-Our results suggest that these costs, which mainstream theories take as evidence of brain dysfunction [@SymeHagen2021], function to help victims of adversity elicit support when their true level of need is private information and they have conflicts with social partners.
+Our results suggest that these costs, which mainstream theories take as evidence of brain dysfunction [@SymeHagen2021], instead function to help victims of adversity elicit support when their true level of need is private information and they have conflicts with social partners.
 These findings align with real-world evidence that depression simultaneously elicits positive and negative responses from social partners [@SymeHagen2021].
@@
 ```{r division, fig.width=9, fig.cap="Effect of signals on division of dowry between the daughters in the thwarted marriage vignette, with an interaction between T1 Division and signal.
+Division > 0.50 favored older daughter.
 Means estimated with a generalized linear regression model with the quasibinomial family."}
@@
 
-```{r divisionage, fig.width=9, fig.cap="Interaction of age with signals on *T2 Division* of dowry between the daughters in the thwarted marriage vignette."}
+```{r divisionage, fig.width=9, fig.cap="Interaction of age with signals on *T2 Division* of dowry between the daughters in the thwarted marriage vignette. Division > 0.50 favored older daughter. "}
 effectsPlots_India$m8plot

### 2021-06-07 Paper.rmd
Minor edits

@@
 
-The effects of the signals on rated beliefs and actions differed substantially by vignette, which we display in three ways for each signal in each vignette: estimated cumulative distributions plots, which show the entire distributions of rated beliefs and actions, including which conditions have high fractions of 0's and 1's (Figures \@ref(fig:ecdf)); regression estimates of the mean effects of the signals on beliefs and actions by vignette (Figure \@ref(fig:beliefvignette)); and between- and within-subjects signal effect sizes (Cohen's d) by vignette (Figures \@ref(fig:effectsizes) and \@ref(fig:effectsizes2)).
+The effects of the signals on rated beliefs and actions differed substantially by vignette, which we display in three ways for each signal in each vignette: estimated cumulative distribution function plots, which show the entire distributions of rated beliefs and actions, including which conditions have high fractions of 0's and 1's (Figures \@ref(fig:ecdf)); regression estimates of the mean effects of the signals on beliefs and actions by vignette (Figure \@ref(fig:beliefvignette)); and between- and within-subjects signal effect sizes (Cohen's d) by vignette (Figures \@ref(fig:effectsizes) and \@ref(fig:effectsizes2)).
 
@@
 
-The sociodemographic variables were strongly confounded with nationality (Indian participants were younger, lower income, with more years of education than US; see Figure \@ref(fig:socioeconomic)), which, in turn, were confounded with vignette (responses in the Indian Thwarted marriage vignette differed substantially from those in the US vignettes).
+The sociodemographic variables were strongly confounded with nationality (Indian participants were younger, lower income, with more years of education than US participants; see Figure \@ref(fig:socioeconomic)), which, in turn, were confounded with vignette (responses in the Indian Thwarted marriage vignette differed substantially from those in the US vignettes).
 We therefore conducted our exploration of the sociodemographic variables separately by nationality.
@@
 
-## Validity check: T3 increase in Action with proof that victim was telling the truth
+## Validity check: large T3 increase in Action with proof that victim was telling the truth
 

### 2021-06-08 Paper.rmd
Finished incorporating Kristen edits

@@
 
-Major depression and suicide are generally viewed as pathological responses to stress that elicit aversive responses from others.
-Alternatively, depression and suicidality might involve honest signals of need in response to stress that can increase support from reluctant others.
-To test this hypothesis, we examined responses to emotional signals in an experimental vignette study involving claims of substantial need in the presence of conflicts of interest and private information about whether the signaler was actually in need.
+Mental health professionals generally view major depression and suicidality as pathological responses to stress that elicit aversive responses from others.
+An alternative hypothesis grounded in evolutionary theory contends that depression and suicidality are honest signals of need in response to adversity that can increase support from reluctant others when there are conflicts of interest.
+To test this hypothesis, we examined responses to emotional signals in an experimental vignette study involving claims of substantial need in the presence of conflicts of interest and private information about the signaler's true level of need.
 In a sample of 1,240 participants recruited from Amazon Mechanical Turk, costlier signals like depression and suicidality resulted in greater perceptions of need, reduced perceptions of manipulativeness, and increased likelihood of support compared to simple verbal requests and crying without further symptoms.
-Additionally, as predicted, the effect of signaling on likelihood of support was largely mediated by the effect of signaling on belief in need.
+Additionally, as predicted, the effect of signaling on likelihood of support was largely mediated by the effect of signaling on participants' belief that the signaler was genuinely in need.
 Our results support the hypothesis that depression and suicidality, apparent human universals, are credible signals of need.
@@
 
-Almost all individuals will suffer adversity, such as injury or loss of material or social resources, at some point in their lives.
+All individuals suffer adversity, such as injury or loss of material or social resources, at some point in their lives, with over 70% of participants in a global survey reporting exposure to a traumatic event [@benjet2016].
 Psychological pain, such as sadness and low mood, probably evolved to motivate victims of adversity to shift their attention to the causes of adversity so as to mitigate its negative fitness consequences and to learn to avoid future such adverse events [@thornhill1989; @andrews2010; @Nesse1990].
-In many cases, social partners could help victims, and therefore signals of psychological pain, such as sad expressions and crying, probably evolved to indicate need [e.g., @darwin1872; @bowlby1980; @balsters2013].
+Over human evolution, social partners could have often helped victims, and therefore signals of psychological pain, such as sad expressions and crying, probably evolved to indicate need [e.g., @darwin1872; @bowlby1980; @balsters2013].
 
@@
 
-There is strong evidence that most cases of depression are caused by major negative life events [@Hammen2005; @Mazure1998; @devries2011; @ellsberg2008].
+<!-- Although the relationship between negative events and depression is bidirectional (cite), negative events still predict depression when looking at events outside of one’s control, indicating that the connection is unlikely to be driven solely by individuals who are already depressed selecting into situations where negative events are likely to be common (Hammen, 2005; Kendler, Karkowski, & Prescott, 1999).
+-->
+
+Several theoretical models propose that depressed and suicidal individuals have inaccurate, negative perceptions of themselves and their environments [@beck1963; @joiner2007; @nolen1991].
+There is strong evidence, however, that most cases of depression are caused by genuinely severe negative life events [@Hammen2005; @Mazure1998; @devries2011; @ellsberg2008; @devries2013].
 Compared to non-depressed individuals, those with depression report about twice as many instances of negative events than non-depressed individuals [@Mazure1998] and more negative events than those with schizophrenia and bipolar depression across multiple studies [@Paykel1994].
-In longitudinal studies, depression onsets soon after a negative event [@KendlerEtAl1999] or coincides with periods where adversity is likely to increase prior to it [e.g., depression starting before a divorce rather than after, @rosenstrom2017].
-Additional support for the causal role of negative life events comes from the fact that the relationship between negative events and depression holds true when looking at events outside of one's control, showing that the connection is unlikely to be driven solely by individuals who are already depressed creating situations where negative events are likely to be common [@Hammen2005; @KendlerEtAl1999].
-Furthermore, twin studies have shown that one's history of negative events is still a strong predictor of major depression when controlling for genetic similarity, and that part of the heritability of depression stems from the heritability of negative events like divorce and family conflict [@KendlerBaker2007; @KendlerEtAl1999].
-For these and other reasons, most cases of depression are probably not due to mental illness but are instead functional instances of psychological pain [@Hagen:1999; @Hagen2003; @horwitz_loss_2007; @andrews2010; @SymeHagen2021].
+Longitudinal studies indicate that depression onsets soon after a negative event [@lewinsohn1988; @KendlerEtAl1999; @rich2005; @han2019; @sen2010] or coincides with periods where adversity is likely to increase prior to it [e.g., depression starting before a divorce rather than after, @blekesaune2008; @metsa2013; @rosenstrom2017].
+Although the relationship between negative events and depression is likely bidirectional [i.e., depression probably also causes adversity, @wichers2012], negative events predict depression even when considering only events outside of one’s control, indicating that the connection is unlikely to be driven solely by individuals who are already depressed selecting into situations where negative events are likely to be common [@Hammen2005; @KendlerEtAl1999].
+Furthermore, twin studies have shown that one's history of negative events remains a strong predictor of major depression when controlling for genetic similarity, and that part of the heritability of depression stems from the heritability of negative events like divorce and family conflict [@KendlerBaker2007; @KendlerEtAl1999].
+For these and other reasons, most cases of depression are probably functional instances of psychological pain and not mental dysfunctions [@Hagen2003; @horwitz_loss_2007; @andrews2010; @SymeHagen2021; @dowrick2013; @frances2013].
 
@@
 
-With a cooperative species like our own, ubiquitous conflicts of interest means that there will always be disagreement over the levels of investment in a cooperative endeavor and the division of the resulting benefits.
-In many such cases, individuals who were dissatisfied with the terms of cooperation could seek other partners [@hammerstein2016].
-In many other cases, however, it would be difficult or impossible to switch partners.
-Spouses who were dissatisfied with their partner's investment in their new infant, for example, would not easily find a different partner to invest in that infant [@Hagen:1999].
-Similarly, an adolescent who was dissatisfied with her parent's investment in her would not easily find other parents who were willing to invest more, nor could parents easily produce another adolescent.
-In these examples, and many cooperative endeavors central to human biological fitness, all parties have monopoly power over the benefits they bring to the endeavor -- no one is easily replaced [@Hagen2002; @Hagen2003].
-Such interdependence is increasingly recognized to be important to the evolution of cooperation in humans and other animals [@roberts2005; @tomasello2012; @aktipis2018].
+With a cooperative species like our own, ubiquitous conflicts of interests means that there will always be disagreement over the levels of investment in a cooperative endeavor and the division of the resulting benefits.
+According to partner choice models, individuals who are dissatisfied with the terms of cooperation can switch partners [@hammerstein2016], e.g., workers unhappy with their pay can look for a better job.
+In many cases, however, it is difficult or impossible to switch partners.
+Spouses who are dissatisfied with their partner's investment in their new infant, for example, cannot easily find a different partner to invest in that infant [@Hagen:1999].
+Similarly, an adolescent who is dissatisfied with her parent's investment in her cannot easily find other parents who were willing to invest more, nor could parents easily produce another adolescent.
+In these latter examples, and many cooperative endeavors central to human biological fitness, all parties have monopoly power over the benefits they bring to the endeavor -- no one is easily replaced [@Hagen2002; @Hagen2003].
+Such interdependence is increasingly recognized to be important to the evolution of cooperation in humans and other animals [@roberts2005; @tomasello2012; @aktipis2018; @balliet2017].
 
@@
 Anthropology has long viewed suicidality as largely the result of social problems.
-Early in the field's history, anthropologists tackled the problem of suicide as manifested in the small, traditional societies in which they conducted their fieldwork.
+Early in the field's history, anthropologists reported on suicide attempts and deaths in the small-scale societies in which they conducted their fieldwork.
 Suicide, they found, was commonly a form of protest, revenge, and/or appeal [@firth1936; @Firth:1961; @Malinowski:1932; @niehaus2012].
@@
 Raymond Firth, an anthropologist who worked in the southwestern Pacific, was one of the first to view suicidality as a gamble to improve one's circumstances in the here and now.
-Based on observations that suicide attempts often followed loss or conflict and varied substantially in their likelihood of death, he argued that a sizable subset of the suicide attempts among the Tikopia were not meant to end in death but instead were a means to elicit attention, status, or immediate reintegration into the community following negative events [@firth1936; @Firth:1961].
+Based on observations that suicide attempts often followed loss or conflict and varied substantially in their likelihood of death, he argued that a sizable subset of the suicide attempts among the Tikopia were not meant to end in death but instead were a means to elicit aid, status, or immediate reintegration into the community following negative events [@firth1936; @Firth:1961].
 
@@
 Some evolutionary theorists have questioned the bargaining model based on evidence that depression is aversive to social partners [@nettle2004; @allen2006; @nesse2006; @myers2016].
-These critics failed to recognize the central role of *conflict* in the model.
+These critics overlooked the central role of *conflict* in the model.
 Anger is aversive to targeted social partners, yet it is probably an adaptation that exploits advantages in physical or social formidability to force concessions from them [@SellEtAl2009].
@@
 punishing a potentially innocent person.
+The US vignettes also had different degrees of evidence *against* the victim beyond just denial by the accused, ranging from strong evidence in the basketball coach vignette (a negative police report) to moderate evidence in the romantic partner vignette (no physical injuries) to weak evidence in the brother-in-law vignette (nothing beyond denial by the brother-in-law), raising the possibility that credible signals are more effective when negative evidence is lacking (Dylan Tweed, personal communication).
 
@@
 Finally, we adopted game theory models of bargaining with incomplete information as our theoretical framework, but there are many other models of credible signaling [e.g., @szamado2011], including for need [@szamado2019] and suicidality [@Rosenthal1993].
-If depression and suicidality involve signaling, it might be better explained by a different model.
+If depression and suicidality involve signaling, they might be better explained by a different model.
 
@@
 
-Depression is costly, sometimes resulting in death by suicide.
+Depression is costly and sometimes leads death by suicide.
 Our results suggest that these costs, which mainstream theories take as evidence of brain dysfunction [@SymeHagen2021], instead function to help victims of adversity elicit support when their true level of need is private information and they have conflicts with social partners.
-These findings align with real-world evidence that depression simultaneously elicits positive and negative responses from social partners [@SymeHagen2021].
-If the bargaining model is correct, depression is an important social problem, not a medical one [@syme2020].
+These findings align with real-world evidence that depression and suicide simultaneously elicit positive and negative responses from social partners [@SymeHagen2021].
+If the bargaining model is correct, depression and suicidality are important social problems, not medical ones [@syme2020].
 

### 2021-06-08 Paper.rmd
Deleted much text that was commented out. Retained text on social responses to depression

@@
 
-<!-- Almost all individuals will suffer adversity, such as injury or loss of material or social resources, at some point in their lives.
-Psychological pain, such as sadness and low mood, probably evolved to motivate victims of adversity to shift their attention to the causes of the problem so as to mitigate its negative fitness consequences and to learn to avoid future such adverse events [@thornhill1989; @andrews2010; @Nesse1990].
-In many types of adversity, social partners could help minimize the costs.
-Therefore signals of psychological pain, such as sad expressions and crying, probably evolved to indicate need [e.g., @balsters2013].
-CurrentDraft-->
-
-<!-- Although the relationship between negative events and depression is bidirectional (cite), negative events still predict depression when looking at events outside of one’s control, indicating that the connection is unlikely to be driven solely by individuals who are already depressed selecting into situations where negative events are likely to be common (Hammen, 2005; Kendler, Karkowski, & Prescott, 1999).
--->
-
 Several theoretical models propose that depressed and suicidal individuals have inaccurate, negative perceptions of themselves and their environments [@beck1963; @joiner2007; @nolen1991].
@@
 
+## Responses to depression and suicidal behavior
+
+For depression and suicide attempts to be worth the costs involved with signal creation, meaningful social support would be required [@Hagen2003; @SymeEtAl2016].
+Most studies examining responses to depression have been observational and focused on responses outside of changes in social support.
+In general, most report aversive responses and high levels of rejection towards the depressed, and depressed individuals are often linked to impaired social functioning [@EvraireDozois2011; @GotlibLee1989; @HirschfeldEtAl2000].
+One explanation for this is that depressed individuals engage in behaviors that drive others away.
+In line with this reasoning, both excessive reassurance seeking and negative feedback seeking, which often accompany depression, have been shown to elicit negative emotional responses from others and increase the chance of rejection from others [@JoinerMetalsky1995; @StarrDavila2008].
+Negative interactions are also seen in families as depressed children tend to report less support and more negative responses from parents than non-depressed children, although it has not been demonstrated that such interactions did not lead to depression in the first place [@MesserGross1995; @SchwartzEtAl2012].
+
+Despite being looked for less frequently, beneficial responses to depressed individuals are also reported.
+Depression has been associated with reduced likelihood of aggression within families [@hops1987; @dadds1992], including those already experiencing high levels of conflict [@SheeberEtAl2001].
+There is also limited evidence that depression can result in increased levels of support from others outside the family.
+For example, non-depressed individuals were shown to be more cooperative and exhibit more caretaking behavior towards their college depressed roommates over the course of their time living together [@HokansonEtAl1986].
+Likewise, a study examining responses to confederates trained to appear ‘depressed’, ‘anxious’, or ‘normal’ found that individuals were more likely to provide advice and support to ‘depressed’ individuals than ‘anxious’ or ‘normal’ individuals despite the confederate in the ‘depression’ condition being viewed more negatively than the other conditions and the ‘depression’ condition involving similar levels of distress compared to the ‘anxious’ condition [@stephens1987].
+
+Most studies examining responses to those who have survived suicide attempts have focused on stigmatization.
+In these studies, perceptions of survivors as being weak, selfish, mentally ill, and antisocial are all being commonly reported [@BatterhamEtAl2013; @TzengLipson2004], with stigmatization often being found within and outside one's social network [@FreyEtAl2016; @ScoccoEtAl2012].
+Despite this potential for stigmatization, increased social support and changes to important relationships have been reported to follow suicide attempts with some indication that these effects may hold long term [@Stengel1956].
+For example, a study of 100 women who survived suicide attempts found that individuals gained identifiable benefits through the attempt in 75 cases, with 41 individuals benefiting from reconciliations with others [@Lukianowicz1971].
+Unlike many Western countries, where suicide is often viewed as pathological [@Hidaka2012], members of traditional societies have been reported to view suicide attempts as cries for help rather than mental illness [@Shostak1981], with attempts having been described as ways of escaping unwanted marriage arrangements, persistent abuse, or a lack of support in obtaining mates by those engaging in the behavior and observers [@GutierrezdePinedaMuirden1948; @Hilger1957; @Karsten1935; @Tessmann1930; @Wilson1960].
+Although findings that individuals view suicide attempts as cries for help is not necessarily evidence for their ability to lead to beneficial responses, 30 out of 84 examples of suicidal behavior included in the HRAF resulted in positive changes for the survivor, despite suicide rarely if ever being the main topic [@SymeEtAl2016].
+
+## Depression, anger, and conflict
+
 There is equally strong evidence that depression is closely associated with anger and conflict [@cassiello2016].
@@
 
-<!-- Other notable risk factors, like loss of a loved one or severe or prolonged illness, might seem less related to conflict.
-In these situations, however, individuals will often need increased investment from social partners, who might not be able, or want, to provide more investment than they already are.
-The ability for others to provide meaningful support to limit the harm in times of need [@SugiyamaSugiyama2003] combined with the ubiquity of conflicts of interests mean that many types of problems will eventually involve social conflict even if they did not start that way [@Hagen2003].
-There is indeed increasing evidence that loss of a loved one is often followed by increased family conflict [see @SymeHagen2021 for a brief review].
--->
-
 Other notable risk factors, like loss of a loved one or severe or prolonged illness, might seem less related to conflict.
@@
 ## Bargaining: Credibly signaling need under conflict
-
-<!-- Individuals who have suffered a negative life event will often need help to mitigate the fitness cost.
-To obtain this help, they must signal need, e.g., by verbal requests, sad facial expressions, and crying.
-But if they have conflicts of interest with social partners who could provide that help, and if their need is private information, their signals might not be believed if the signals, like crying, could easily be faked [@Zahavi1975; @mokkonen2016] and if the cost of believing a deceptive signal was high [@dawkins1978; @johnstone1993; @Hasson1994].
--->
-
-<!-- Conflicts of interest are ubiquitous, even among closely related individuals.
-In species that rely heavily on cooperation, like our own, conflicts can arise over the levels of investment in a cooperative endeavor and the division of the resulting benefits.
--->
 
@@
 In other words, reduced productivity is relatively less costly for those whose efforts are currently not yielding many fitness benefits than for those whose efforts are yielding substantial benefits.
-
-<!-- Formal models of bargaining highlight the role of private information regarding the value each party places the cooperative endeavor.
-Withholding or risking one's contributions to a cooperative endeavor can be conceptualized as credibly signaling private information about one's need.
-Cooperation generates benefits over time.
-Thus, withholding or risking contributions incurs a *cost of delay* -- the more one values the endeavor, the greater the cost of delay.
--->
 
@@
 
-<!-- @Rosenthal1993 proposed a credible signaling model of what he, like Firth, viewed as 'gambling-type' suicide attempts.
-In the Rosenthal model, as long as that risk is greater than or equal to the net benefit a non-needy person would realize by sending the signal (discounted by the risk of death), social partners can trust that signal senders are genuinely in need despite conflicts of interest [@Rosenthal1993].
--->
-
 In the bargaining framework, suicidality is conceptualized as putting all future contributions to cooperative endeavors with social partners at risk with some low but non-zero probability, credibly signaling low valuation of current circumstances [see @Rosenthal1993 for a game theory model of suicide attempts as costly signals].
@@
 
-<!-- As they are prohibitively costly for those in minor need, the costs of depression and suicidal behavior may be particularly important in times of substantial conflicts of interest or when the level of support needed to address one's situation is substantial, both of which should be expected to increase the payoff of manipulating others through fake signals.
-When either condition applies, less costly signals like verbal requests, facial sadness, and crying are likely to be less reliable as their low costs can easily be made up for with increased social support, thereby favoring the use of costlier signals so long as the costs of signaling are outweighed by the benefits [@SymeHagen2021].
+<!-- Durkheim's pioneering study of suicide [@durkheim1897] helped launch sociology as a quantitative discipline.
+Sociological investigations of suicide flourished through much of the 20th century, but were supplanted by medical and public health approaches as the biomedical model of mental health took hold in the late 1970's and early 1980's [@wray2011; @syme2020].
+The biomedical model tends to frame suicide as a problem with the individual, e.g., as one involving psychiatric disturbance, drug addiction, or stress sensitivity [@wray2011].
+This theoretical approach has made little progress: rates of suicide, which vary widely by country, have remained relatively flat in countries for which there are long-term data, such as the US, UK, Japan, and Sweden [@owidsuicide].
 -->
-
-<!-- Alternative start to line 92: Although verbal requests, sad facial expressions, and crying can be used to signal need, they are likely to be less effective in times of severe conflicts of interests or times when the level of support needed to address one's situation is substantial.
-This is because both conditions increase the payoff of manipulating others through fake signal.
--->
-
-<!-- Both depression and suicide attempts are more common outcomes of these sorts of conflict than is often appreciated by the biomedical approach (Syme and Hagen 2021).
-With notable exceptions (Kendler; Mazure; Hammen), the biomedical model tends to frame both suicide and depression as a problem with the individual, e.g., as one involving psychiatric disturbance, drug addiction, or stress sensitivity [@wray2011 (changed wording to include depression].
-This theoretical approach has made little progress: rates of suicide, which vary widely by country, have remained relatively flat in countries for which there are long-term data, such as the US, UK, Japan, and Sweden [@owidsuicide] (tweak for depression).
--->
-
-<!-- ## Depression and suicide attempts as both signals and bargaining tools -->
 
@@
 
-<!-- Another possible explanation for the connection between depression, suicide, and social adversity is that some instances of depression and suicide attempts serve as means to elicit increased support from others by honestly signaling need to those invested in the well-being of the signaler, [@andrews2006; @Hagen2002; @Hagen2003; @HagenEtAl2008; @nock2008; @Rosenthal1993; @Stengel1956; @SymeEtAl2016], something which may be particularly useful in times when an individual cannot solve substantial fitness-relevant challenges on their own [@Hagen2003; @SymeEtAl2016].
--->
-
-<!-- Due to the ease with which signals can be faked [@Zahavi1975; @mokkonen2016] and the costs of accepting a deceptive signal as reliable [@dawkins1978; @johnstone1993; @Hasson1994], demonstrating that one's need is genuine has likely been a recurrent adaptive problem since humans evolved the capacity to provide instrumental support to one another.
-One potential solution to this is to produce signals that are unprofitable to fake [@Zahavi1975].
-This is possible whenever the benefits of signaling outweigh the costs for those who have the relevant underlying quality but the costs outweigh the benefits for those who lack the quality or possess it to a lesser degree [@zahavi1977; @grafen1990].
-In particular, if the benefits of sending the signal are the same for signalers regardless of condition, but the signal cost outweighs this benefit for signalers without the underlying quality (a "costly signal"), then individuals with the underlying quality can evolve to send the signal and receivers can evolve to respond in mutually beneficial ways to the signal.
--->
-
-<!-- Depression and suicidal behavior fit this criterion as both are relatively costly for those not facing adversity than those who are.
-In the case of depression, the large-scale reduction in one's normal routine of fitness enhancing behavior is relatively less costly for those whose situations result in a limited ability to obtain fitness-relevant benefits, with depression likely adding no additional costs in instances of extreme deprivation [@Hagen2003].
-When it comes to suicide, the bulk of the costs associated with suicide attempts are only felt in times that result in death or severe bodily harm.
-For this reason, the way others view and respond to suicide attempts is likely to be strongly influenced by the probability that the attempt would result in death or severe injury [@Rosenthal1993].
-Despite this difference, the previously mentioned logic still applies with increased risk of death being relatively more costly for those able to advance their fitness prospects in their day-to-day lives.
--->
-
-<!-- The costs of depression and suicidal behavior may be particularly important in times of conflict or when the level of support needed to address one's situation is substantial, both of which should be expected to increase the payoff of manipulating others through fake signals.
-When either condition applies, less costly signals like verbal requests, facial sadness, and crying are likely to be less reliable as their low costs can easily be made up for with increased social support, thereby favoring the use of costlier signals so long as the costs of signaling are outweighed by the benefits [@SymeHagen2021].
--->
-
-<!-- Durkheim's pioneering study of suicide [@durkheim1897] helped launch sociology as a quantitative discipline.
-Sociological investigations of suicide flourished through much of the 20th century, but were supplanted by medical and public health approaches as the biomedical model of mental health took hold in the late 1970's and early 1980's [@wray2011; @syme2020].
-The biomedical model tends to frame suicide as a problem with the individual, e.g., as one involving psychiatric disturbance, drug addiction, or stress sensitivity [@wray2011].
-This theoretical approach has made little progress: rates of suicide, which vary widely by country, have remained relatively flat in countries for which there are long-term data, such as the US, UK, Japan, and Sweden [@owidsuicide].
--->
-
-<!-- ## Conflict plays a central role in suicidality and depression -->
-
-<!-- Early on, anthropologists also tackled the problem of suicide as manifested in the small traditional societies in which they conducted their fieldwork.
-Suicide, they found, was commonly a form of protest, revenge, and/or appeal [e.g., @Malinowski:1932; @niehaus2012].
-Some ethnographers, such as @Hezel:1987, conceptualized suicide as a form of anger, whereas others, such as @Giddens:1964, conceptualized suicide as a form of social pressure.
-@Counts:1980 emphasized the powerlessness of suicide victims.
-Common to almost all theoretical and empirical investigations of suicide is a focus on *completed* suicides, i.e., suicide deaths.
-@SymeEtAl2016, in contrast, argued that because the vast majority of suicidal behavior does not result in death, the proper focus should be on suicide ideation and suicide attempts (see Figure @ref(fig:cdc)).
-Suicide attempts, as we explain next, are a gamble to improve one's life by taking a low but non-zero risk of death.
-Most suicides deaths, especially in young, physically healthy individuals, are therefore the inevitable consequence that some individuals lose this gamble.
--->
-
-<!-- Within anthropology, Raymond Firth was likely the first to conceptualize suicidality as a gamble to improve one's circumstances in the here and now.
-Based on observations that suicide attempts often followed social conflict or loss, and varied substantially in their likelihood of death, he argued that a sizable subset of the suicide attempts among the Tikopia were not meant to end in death but instead were a means to elicit attention, status, or immediate reintegration into the community following negative events [@firth1936; @Firth:1961].
-Human communites are highly interdependent [\@] -->
-
-<!-- Suicidality is closely linked to depression.
-Suicidal ideation is one of nine diagnostic criteria for a major depressive episode [MDE, @dsm5], it is associated with depression across cultures [@haroz2017], and depression is a major risk factor for suicidal behavior [@hawton2013].
-Compared to suicide, however, there are fewer anthropological investigations of depression [@kleinman1985] despite frequent reports of depression or depression-like behavior in a wide range of societies [@haroz2017; @liu2020] and the potential for cross-cultural research to help understand depressive states [@haroz2017].
--->
-
-<!-- Evolutionary theories of depression tend to either ignore suicidality, or take it as evidence that depression is dysfunctional.
-Wakefield, for instance, who has devoted much of his career to arguing that most cases of depression are simply severe but normal sadness and grief, nevertheless takes suicidality to indicate pathology for some cases of depression [e.g., @wakefield2017].
-@nettle2004 argues that the costs of depression, including suicidality, outweigh any benefits, and therefore adaptationist models of depression are implausible.
-@gilbert2006 sees suicidality as an example of a dysregulated escape defense [for reviews of evolutionary theories of depression, see @Hagen2011].
--->
-
-<!-- and anthropological explanations for low mood have become more common.
-In general, these approaches see sadness and minor depression as ways to motivate adaptive behavior changes in response to negative outcomes in one's environment (cite Nesse and others), mainly differing in how they view major depression.
-While some approaches present most forms of major depression as dysfunctional (inflammation and some of Nesse), others have extended the logic on the benefits of low mood and reduced behavior to more severe instances of sadness.
-Of the possible benefits, the ability of depression to help solve fitness-relevant in times of social conflict is the most emphasized, with depression being suggested to help by reallocating resources with the body for problem solving (cite ARH), reducing the costs of interacting with higher status individuals (cite), or serving as a means to both signal one's need and bargain for increased support (cite).
--->
-
 <!-- As with suicide, research on depression since the 1980's has been dominated by biomedical approaches of limited success [@patten2016; @ormel2019].  -->
-
-<!-- and there is still substantial uncertainty about why both are as common as they are (cite).
-Likely due to  the suffering they cause, the vast majority of these approaches have been built on the assumption that they are the result of internal dysfunction (cite examples).
-However, a subset of anthropologists and evolutionary theorists have challenged this idea, suggesting that despite the subjective suffering they cause, they may function as a means to limit negative fitness outcomes in times of substantial adversity (Firth + others).
--->
-
-<!-- Due to depression's relationship to suicide [@who2001; @hawton2013], it should not be surprising that suicidality also often coincides with social adversity and conflict.
-Grief over the loss of a loved one [@firth1936: @Firth:1961; @devries2011], bullying [@alavi2017; @butler2019; @ford2017; @wang2020], and instances of social transgression [@Firth:1961; @Malinowski:1932; @SymeHagen2018; @lester1997] have all been reported to lead to suicidal behavior in both industrialized and traditional societies.
-Of the recorded instances of suicide attempts in the Human Relations Area Files (HRAF), 77.4% of attempts were found to be linked to times of social conflict, 88.7% were linked to fitness threats in general, and 84.9% were linked to situations in which attempters were powerless to resolve their situation alone [@SymeEtAl2016].
-As with depression, assault is an particularly powerful risk factor for suicidal behavior based on multiple large-scale multi-country studies [@devries2011; @ellsberg2008] and more localized examinations [@reigstad2017].
--->
-
-<!-- ## Depression and suicide attempts as both signals and bargaining tools -->
-
-<!-- One possible reason for the connection between depression, suicide, and social adversity is that some instances of depression and suicide attempts serve as means to elicit increased support from others [@andrews2006; @Hagen2002; @Hagen2003; @HagenEtAl2008; @nock2008; @Rosenthal1993; @Stengel1956; @SymeEtAl2016], particularly in times when an individual cannot solve substantial fitness-relevant challenges on their own [@Hagen2003; @SymeEtAl2016].
-According to the bargaining models of depression and suicide, the small groups humans lived in for much of our evolutionary history created many situations in which certain forms of cooperation were unlikely to be easily replaced by others while also allowing for harmful or unfair social relationships to develop [@Hagen2003; @SymeEtAl2016].
-In these instances, one's monopoly on one or more types of cooperation could be leveraged to change how one is treated if others valued an individual's cooperation sufficiently and believed them to be in genuine need.
--->
-
-<!-- Due to the ease with which signals can be faked [@Zahavi1975; @mokkonen2016] and the costs of accepting a deceptive signal as reliable [@dawkins1978; @johnstone1993; @Hasson1994], demonstrating that one's need is genuine has likely been a recurrent adaptive problem since humans evolved the capacity to provide instrumental support to one another.
-One potential solution to this is to produce signals that are unprofitable to fake [@Zahavi1975].
-This is possible whenever the benefits of signaling outweigh the costs for those who have the relevant underlying quality but the costs outweigh the benefits for those who lack the quality or possess it to a lesser degree [@zahavi1977; @grafen1990].
-In particular, if the benefits of sending the signal are the same for signalers regardless of condition, but the signal cost outweighs this benefit for signalers without the underlying quality (a "costly signal"), then individuals with the underlying quality can evolve to send the signal and receivers can evolve to respond in mutually beneficial ways to the signal.
--->
-
-<!-- Depression and suicidal behavior fit this criterion as both are relatively costly for those not facing adversity than those who are.
-In the case of depression, the large-scale reduction in one's normal routine of fitness enhancing behavior is relatively less costly for those whose situations result in a limited ability to obtain fitness-relevant benefits, with depression likely adding no additional costs in instances of extreme deprivation [@Hagen2003].
-When it comes to suicide, the bulk of the costs associated with suicide attempts are only felt in times that result in death or severe bodily harm.
-For this reason, the way others view and respond to suicide attempts is likely to be strongly influenced by the probability that the attempt would result in death or severe injury [@Rosenthal1993].
-Despite this difference, the previously mentioned logic still applies with increased risk of death being relatively more costly for those able to advance their fitness prospects in their day-to-day lives.
--->
-
-<!-- The costs of depression and suicidal behavior may be particularly important in times of conflict or when the level of support needed to address one's situation is substantial, both of which should be expected to increase the payoff of manipulating others through fake signals.
-When either condition applies, less costly signals like verbal requests, facial sadness, and crying are likely to be less reliable as their low costs can easily be made up for with increased social support, thereby favoring the use of costlier signals so long as the costs of signaling are outweighed by the benefits [@SymeHagen2021].
--->
-
-<!-- Beyond signaling need to those invested in the well-being of the signaler, depression and suicidal behavior may also help an individual bargain for increased support [@Hagen2003].
-This is possible due to the reduced investment in others that frequently accompanies depression or the threat to future cooperation that comes from suicide.
-In these instances, depression and suicide attempts may function analogously to a labor strike, sending the message that one’s need is genuine and that if the target of the signal wanted to continue receiving benefits from the depressed, they would need to increase support towards the signaler.
-Due to this bargaining component, aversive responses from the targets of the signal to the signaler are expected throughout the bargaining process, with potential helpers likely signaling the costliness of providing support.
-Importantly, such responses do not prevent the delivery of meaningful benefits, they are simply expected to reduce the risk of helpers providing too much support for too little need.
--->
-
-<!-- ### Determining the impact of cues versus signals -->
-
-<!-- Distinguishing between the information provided by signals versus cues is a major challenge for signaling approaches to behavior.
-A signal differs from a cue in that it is intentionally sent by an organism to alter the perceptions and behaviors of others, while a cue is any piece of information that influences an individual's behavior or physiological state that was not created for communicative effect [@MaynardSmithHarper1995].
-Regarding the signals of interest, suicide attempts are more likely to take the form of pure, external signals than other symptoms of depression.
-This is because low mood's impact on behavior for non-signaling benefits likely conveys information as cues in addition to what might exist for signaling purposes.
-In other words, the signaling component of depression may come from the upregulation of symptoms beyond what would be optimal for non-signaling purposes rather than the creation of entirely new symptoms.
-Suicidality is likely an exception to this, due to the likelihood most suicide attempts do not have non-signaling functions [see @deCatanzaro1991 for a possible exception].
--->
-
-<!-- ## Responses to depression and suicidal behavior  -->
-
-<!-- For depression and suicide attempts to be worth the costs involved with signal creation, meaningful social support would be required [@Hagen2003; @SymeEtAl2016].
-Most studies examining responses to depression have been observational and focused on responses outside of changes in social support.
-In general, most report aversive responses and high levels of rejection towards the depressed, and depressed individuals are often linked to impaired social functioning [@EvraireDozois2011; @GotlibLee1989; @HirschfeldEtAl2000].
-One explanation for this is that depressed individuals engage in behaviors that drive others away.
-In line with this reasoning, both excessive reassurance seeking and negative feedback seeking, which often accompany depression, have been shown to elicit negative emotional responses from others and increase the chance of rejection from others [@JoinerMetalsky1995; @StarrDavila2008].
-Negative interactions are also seen in families as depressed children tend to report less support and more negative responses from parents than non-depressed children, although it has not been demonstrated that such interactions did not lead to depression in the first place [@MesserGross1995; @SchwartzEtAl2012].
--->
-
-<!-- Despite being looked for less frequently, beneficial responses to depressed individuals are also reported.
-Depression has been associated with reduced likelihood of aggression within families [@hops1987; @dadds1992], including those already experiencing high levels of conflict [@SheeberEtAl2001].
-There is also limited evidence that depression can result in increased levels of support from others outside the family.
-For example, non-depressed individuals were shown to be more cooperative and exhibit more caretaking behavior towards their college depressed roommates over the course of their time living together [@HokansonEtAl1986].
-Likewise, a study examining responses to confederates trained to appear ‘depressed’, ‘anxious’, or ‘normal’ found that individuals were more likely to provide advice and support to ‘depressed’ individuals than ‘anxious’ or ‘normal’ individuals despite the confederate in the ‘depression’ condition being viewed more negatively than the other conditions and the ‘depression’ condition involving similar levels of distress compared to the ‘anxious’ condition [@stephens1987].
--->
-
-<!-- Most studies examining responses to those who have survived suicide attempts have focused on stigmatization.
-In these studies, perceptions of survivors as being weak, selfish, mentally ill, and antisocial are all being commonly reported [@BatterhamEtAl2013; @TzengLipson2004], with stigmatization often being found within and outside one's social network [@FreyEtAl2016; @ScoccoEtAl2012].
-Despite this potential for stigmatization, increased social support and changes to important relationships have been reported to follow suicide attempts with some indication that these effects may hold long term [@Stengel1956].
-For example, a study of 100 women who survived suicide attempts found that individuals gained identifiable benefits through the attempt in 75 cases, with 41 individuals benefiting from reconciliations with others [@Lukianowicz1971].
-Unlike many Western countries, where suicide is often viewed as pathological [@Hidaka2012], members of traditional societies have been reported to view suicide attempts as cries for help rather than mental illness [@Shostak1981], with attempts having been described as ways of escaping unwanted marriage arrangements, persistent abuse, or a lack of support in obtaining mates by those engaging in the behavior and observers [@GutierrezdePinedaMuirden1948; @Hilger1957; @Karsten1935; @Tessmann1930; @Wilson1960].
-Although findings that individuals view suicide attempts as cries for help is not necessarily evidence for their ability to lead to beneficial responses, 30 out of 84 examples of suicidal behavior included in the HRAF resulted in positive changes for the survivor, despite suicide rarely if ever being the main topic [@SymeEtAl2016].
--->
 
@@
 
-<!-- Overall, our results on the connection between belief in need and likelihood of help are consistent with costly signaling and bargaining approaches to depression and suicide.
-At T1, *Belief* and *Action* were highly correlated yet distinct; while at T2, the effect of signal on both *Belief* and *Action* was to increase the magnitude of pro-signaler responses, with the effect of signal on *T2 Action* being largely mediated by signal's effect on belief in need.
-This relationship between belief in need and likelihood of support and the importance of signal cost should be expected in scenarios when a target of a signal of need would benefit from helping if the signaler's need was genuine but face substantial net costs if it was not.
-Importantly, such scenarios appear to be common among modern humans and have likely been since individuals could increase their inclusive fitness through supporting kin or important cooperative partners who could return to providing benefits to supporters once their situation returned to normal [@SugiyamaSugiyama2003; @tooby1996].
--->
-
-<!-- Although this study was not designed to examine whether the costs of signaling would be made up for by the increased support stemming from depression and suicide attempts directly, the results are consistent with this hypothesis.
-In general, the costs required to honestly convey one's qualities should be expected to increase with the potential payoffs of deception and the number of defectors within the broader population [@Rosenthal1993], with the vignettes in this study emphasizing the existence of private information and sizable conflicts of interest to increase the perceived risk of being taken advantage of.
-In similar real-world scenarios, this difficulty of signaling honest need would coincide with the substantial fitness-relevant benefits of preventing future assaults or being able to marry the partner of one's choice.
-These benefits coupled with the fact that depression and suicide attempts become relatively less costly to one's fitness prospects with increased need [@Hagen2003], suggest that the increased support seen in this study may be worth the costs required to signal need more often than is often appreciated when counting the entire costs of depression as the signal rather than only the upregulation of symptoms for a communicative purpose.
--->
-
 ## Limitations
@@
 
-<!-- Slider anchor  -->
-<!-- Regex: stopped in SI -->
-<!-- T\d \w+ -->
-
 # Conclusion
@@
 
- <!-- The need to explain suicide's connection to depression is often overlooked by explanations for major depression, particularly those which propose non-signaling functions.
-One explanation for their connection, is that both suicidality and depression may function to limit negative fitness outcomes in times of substantial adversity [@andrews2006; @Hagen2002; @Hagen2003; @HagenEtAl2008; @nock2008; @Rosenthal1993; @Stengel1956; @SymeEtAl2016], with costlier signals being required to elicit support when the payoffs to faking need are high enough so that less costly signals are not reliable indicators of one's need [@Rosenthal1993].
-For this hypothesis to be correct, instrumental support would need to be provided frequently enough with large enough impacts so that the costs of signaling are outweighed by the benefits on average.
-In support of this, we found exposure to depression and suicide attempts resulted in greater belief in need and increased likelihood of support in fictional scenarios.
--->
-
 # Acknowledgements
@@
 We also thank XX and YY [pending permission to acknowledge] for feedback on the Thwarted marriage vignette.
-
-<!-- # To do: -->
-
-<!-- -   victim or signaler? -->
-<!-- -   add anger -->
-<!-- -   Intro "State the objectives of the work and provide an adequate background, avoiding a detailed literature survey or a summary of the results." -->
-<!-- -   Discussion " This should explore the significance of the results of the work, not repeat them.
-A combined Results and Discussion section is often appropriate.
-Avoid extensive citations and discussion of published literature." -->
-<!-- -   mention asking for prefered sex -->
-
-<!-- # Notes from my meeting with Anne -->
-
-<!-- -   Table detailing the cooperative endeavor (maybe word as boundedness of fate), conflict of interest, and what the private information is about would be useful. -->
-<!-- -   Calling verbal request control when it's a treatment? -->
-<!-- -   Can shift much of the pilot studies info to SI with some detail post line 279 in draft she saw. -->
-<!-- -   Cumulative distribution plot: needs more info in captions. could benefit from fig6a and fig6b (confusion over x and y axes) -->
 

### 2021-06-08 Paper.rmd
Expanding section on social responses to depression

@@
 ---
-title: "Depression and suicidality as credible signals of need"
+title: "Depression and suicidality as credible signals of need in social conflicts"
 author:
@@
 
-Several theoretical models propose that depressed and suicidal individuals have inaccurate, negative perceptions of themselves and their environments [@beck1963; @joiner2007; @nolen1991].
-There is strong evidence, however, that most cases of depression are caused by genuinely severe negative life events [@Hammen2005; @Mazure1998; @devries2011; @ellsberg2008; @devries2013].
+In contrast to sadness, depression is widely believed to pathological because (1) depressed individuals putatively have inaccurate, negative perceptions of themselves and their environments [@beck1963; @joiner2007; @nolen1991], (2) social partners respond negatively, not positively, to depression [@xx], and (3) depression has many costs, increased risk of suicide paramount among them.
+
+## Depression is probably caused by genuine adversity
+
+Contrary to the view that the depressed have a distorted perception of their environment, there is strong evidence that most cases of depression are caused by genuinely severe negative life events, such as physical assault and death of a loved one [@Hammen2005; @Mazure1998; @devries2011; @ellsberg2008; @devries2013].
 Compared to non-depressed individuals, those with depression report about twice as many instances of negative events than non-depressed individuals [@Mazure1998] and more negative events than those with schizophrenia and bipolar depression across multiple studies [@Paykel1994].
@@
 
-## Responses to depression and suicidal behavior
-
-For depression and suicide attempts to be worth the costs involved with signal creation, meaningful social support would be required [@Hagen2003; @SymeEtAl2016].
-Most studies examining responses to depression have been observational and focused on responses outside of changes in social support.
-In general, most report aversive responses and high levels of rejection towards the depressed, and depressed individuals are often linked to impaired social functioning [@EvraireDozois2011; @GotlibLee1989; @HirschfeldEtAl2000].
-One explanation for this is that depressed individuals engage in behaviors that drive others away.
+## Social responses to depression
+
+In a classic study, @Coyne1976 found that depression alienates others, a result that was subsequently confirmed in many other studies [@segrin1992; @segrin2000].
+Depressed individuals self-disclose personally relevant negative issues at inappropriate times and they view such topics as more appropriate for discussion than do the non-depressed [@segrin2000].
+Such self-disclosures have been shown to be a key ingredient in the rejection of depressed persons by others, and "may appropriately be understood as an attempt to elicit social support from targets" [@segrin1994, p.
+657].
+In interactions with spouses, depressed individuals express anger and aggression, and make frequent demands for help [@segrin1994].
+Excessive reassurance seeking -- repeatedly requesting reassurance that one is lovable and worthy despite previous attempts by others to provide such reassurance -- is another factor implicated in the rejection of the depressed by others [@joiner1999; @JoinerMetalsky1995; @StarrDavila2008].
+Beneficial responses to depressed individuals have also been reported, such as increased caretaking [@HokansonEtAl1986], more offers of advice and support [@stephens1987], and reduced aggression within families [@hops1987; @dadds1992; @SheeberEtAl2001].
+
+Negative social responses to depression are widely interpreted as caused by impaired social functioning in the depressed [@EvraireDozois2011; @GotlibLee1989; @HirschfeldEtAl2000], including by evolutionary theorists of depression [@nettle2004; @allen2006; @nesse2006; @myers2016].
+These theorists have overlooked the role of conflict in depression.
+
+<!-- including those already experiencing high levels of conflict [].
+There is also limited evidence that depression can result in increased levels of support from others outside the family.
+For example, non-depressed individuals were shown to be more cooperative and exhibit more caretaking behavior towards their college depressed roommates over the course of their time living together [@HokansonEtAl1986].
+Likewise, a study examining responses to confederates trained to appear ‘depressed’, ‘anxious’, or ‘normal’ found that individuals were more likely to provide advice and support to ‘depressed’ individuals than ‘anxious’ or ‘normal’ individuals despite the confederate in the ‘depression’ condition being viewed more negatively than the other conditions and the ‘depression’ condition involving similar levels of distress compared to the ‘anxious’ condition .
+-->
+
+<!-- One explanation for this is that depressed individuals engage in behaviors that drive others away.
 In line with this reasoning, both excessive reassurance seeking and negative feedback seeking, which often accompany depression, have been shown to elicit negative emotional responses from others and increase the chance of rejection from others [@JoinerMetalsky1995; @StarrDavila2008].
 Negative interactions are also seen in families as depressed children tend to report less support and more negative responses from parents than non-depressed children, although it has not been demonstrated that such interactions did not lead to depression in the first place [@MesserGross1995; @SchwartzEtAl2012].
-
-Despite being looked for less frequently, beneficial responses to depressed individuals are also reported.
-Depression has been associated with reduced likelihood of aggression within families [@hops1987; @dadds1992], including those already experiencing high levels of conflict [@SheeberEtAl2001].
-There is also limited evidence that depression can result in increased levels of support from others outside the family.
-For example, non-depressed individuals were shown to be more cooperative and exhibit more caretaking behavior towards their college depressed roommates over the course of their time living together [@HokansonEtAl1986].
-Likewise, a study examining responses to confederates trained to appear ‘depressed’, ‘anxious’, or ‘normal’ found that individuals were more likely to provide advice and support to ‘depressed’ individuals than ‘anxious’ or ‘normal’ individuals despite the confederate in the ‘depression’ condition being viewed more negatively than the other conditions and the ‘depression’ condition involving similar levels of distress compared to the ‘anxious’ condition [@stephens1987].
-
-Most studies examining responses to those who have survived suicide attempts have focused on stigmatization.
-In these studies, perceptions of survivors as being weak, selfish, mentally ill, and antisocial are all being commonly reported [@BatterhamEtAl2013; @TzengLipson2004], with stigmatization often being found within and outside one's social network [@FreyEtAl2016; @ScoccoEtAl2012].
-Despite this potential for stigmatization, increased social support and changes to important relationships have been reported to follow suicide attempts with some indication that these effects may hold long term [@Stengel1956].
-For example, a study of 100 women who survived suicide attempts found that individuals gained identifiable benefits through the attempt in 75 cases, with 41 individuals benefiting from reconciliations with others [@Lukianowicz1971].
-Unlike many Western countries, where suicide is often viewed as pathological [@Hidaka2012], members of traditional societies have been reported to view suicide attempts as cries for help rather than mental illness [@Shostak1981], with attempts having been described as ways of escaping unwanted marriage arrangements, persistent abuse, or a lack of support in obtaining mates by those engaging in the behavior and observers [@GutierrezdePinedaMuirden1948; @Hilger1957; @Karsten1935; @Tessmann1930; @Wilson1960].
-Although findings that individuals view suicide attempts as cries for help is not necessarily evidence for their ability to lead to beneficial responses, 30 out of 84 examples of suicidal behavior included in the HRAF resulted in positive changes for the survivor, despite suicide rarely if ever being the main topic [@SymeEtAl2016].
+-->
+
+<!-- After confirming Coyne's (1976a, 1976b) finding that depression alienates others, including strangers in brief interactions (for a meta-analysis, see Segrin, 1992) researchers began to explore what it is that depressed people do or fail to do that leads to others' hostility and rejection.
+A large literature has since accumulated documenting differences in interpersonal interactions by depressed and non-depressed individuals.
+Findings include differences in communication ‘style,' such as vocal characteristics, eye gaze, and gestures, and differences in ‘content,' such as preferred topics and themes of conversation (Segrin, 1994; Segrin, 2000).
+-->
+
+<!-- With regard to style, e.g., paralinguistic qualities like low rate, low volume, and low monotone pitch, depressed people appear to be ''very 'skilled' at communicating sadness and despair'' (Segrin, 2000, p.
+385).
+With regard to content, depressed individuals are eager to self-disclose personally relevant negative issues, often at what are judged to be inappropriate times, and they view such topics as more appropriate for discussion than do the non-depressed (Segrin, 2000).
+Such self-disclosures have been shown to be a key ingredient in the rejection of depressed persons by others, and ''may appropriately be understood as an attempt to elicit social support from targets'' (Segrin, 1994, p.
+657).
+In interactions with spouses, depressed individuals express anger and aggression, and make frequent demands for help.
+Segrin (1994) speculates that  -->
+
+<!-- The discussion of negative well-being, dysphoric feelings, and frequent demands for help may impose on other people, making them feel either responsible or obligated to offer assistance or find out the cause of the depression.
+This feeling of obligation or responsibility could potentially prove to be aversive and motivate withdrawal and rejection of the depressed person.
+(p.
+660) -->
+
+<!-- Excessive reassurance seeking (ERS) is another well-studied factor implicated in depression and rejection by others.
+ERS is defined as repeatedly requesting reassurance that one is lovable and worthy despite previous attempts by others to provide such reassurance.
+According to Joiner (1999) -->
+
+<!-- The key idea is that the aversive properties of depression are not interpersonally aversive unless clearly and repeatedly signaled to other people and, further, signaled in such a way that others are both implicated in the development of the problem (e.g., ''you don't really love me anymore, do you?"), as well as overwhelmed by demands, whether implicit or stated, to solve the problem.
+(p.
+272) -->
+
+<!-- Our view is that excessive reassurance-seeking predisposes people to the development of depressive symptoms.
+Initially, this may occur as a function of growing demoralization of the high reassurance-seeking person, who has struggled to gain -- but has been disappointed with -- others' responsiveness.
+(p.
+273) -->
+
+<!-- A meta-analysis of 38 studies found ERS to be moderately associated with depression (r = .38) and weakly but significantly associated with rejection (r = .14), although the relationship with rejection could be stronger when the seeker is depressed (Starr, 2008).
+-->
+
+<!-- Because depression alienates others, however, differences in the style and content of interpersonal interactions of the depressed vs.
+non-depressed, rather than being seen as an aversive signal of need, are interpreted as deficits, such as social skill deficits or 'excessive' reassurance-seeking (Segrin, 1994; Joiner et al., 1999).
+Yet infant cries, clear signals of need, motivate caregiving, in part by being so aversive that caregivers work to terminate the cries.
+The noxiousness of these cries can also evoke abuse or avoidance by caregivers (Owings & Zeifman, 2004).
+-->
+
+<!-- Normal sadness can also alienate others.
+Young children, for instance, find sad people to be rather unlikeable (Glasberg, 1981; Glasberg, 1982), and report controlling their own sadness, especially around peers, because they fear negative interpersonal consequences (Zeman, 1996).
+Adults commonly regulate their emotions too, including sadness, in part because there are negative social consequences to emotional expression, in addition to positive ones (for reviews see Gross, 1998; Gross, 2002; Ochsner, 2005).
+-->
 
@@
 These and similar ideas [@andrews2006; @HagenEtAl2008; @nock2008; @Stengel1956] suggest that depression symptoms that put one's value to others at risk, such as loss of interest and suicidality, are credible signals of need.
+
+<!-- Need to integrate this -->
+Most studies examining responses to those who have survived suicide attempts have focused on stigmatization.
+In these studies, perceptions of survivors as being weak, selfish, mentally ill, and antisocial are all being commonly reported [@BatterhamEtAl2013; @TzengLipson2004], with stigmatization often being found within and outside one's social network [@FreyEtAl2016; @ScoccoEtAl2012].
+Despite this potential for stigmatization, increased social support and changes to important relationships have been reported to follow suicide attempts with some indication that these effects may hold long term [@Stengel1956].
+For example, a study of 100 women who survived suicide attempts found that individuals gained identifiable benefits through the attempt in 75 cases, with 41 individuals benefiting from reconciliations with others [@Lukianowicz1971].
+Unlike many Western countries, where suicide is often viewed as pathological [@Hidaka2012], members of traditional societies have been reported to view suicide attempts as cries for help rather than mental illness [@Shostak1981], with attempts having been described as ways of escaping unwanted marriage arrangements, persistent abuse, or a lack of support in obtaining mates by those engaging in the behavior and observers [@GutierrezdePinedaMuirden1948; @Hilger1957; @Karsten1935; @Tessmann1930; @Wilson1960].
+Although findings that individuals view suicide attempts as cries for help is not necessarily evidence for their ability to lead to beneficial responses, 30 out of 84 examples of suicidal behavior included in the HRAF resulted in positive changes for the survivor, despite suicide rarely if ever being the main topic [@SymeEtAl2016].
 

### 2021-06-08 Paper.rmd
Added section on social responses to depression.

--- 2021-06-08 Paper.rmd
@@
 
+In a classic study, @Coyne1976 found that depression alienates others, a result that was subsequently confirmed in many other studies [@segrin1992; @segrin2000].
+In interactions with spouses, depressed individuals express anger and aggression, and make frequent demands for help [@segrin1994].
+Depressed individuals also self-disclose personally relevant negative issues at inappropriate times and they view such topics as more appropriate for discussion than do the non-depressed [@segrin2000].
+Such self-disclosures have been shown to be a key ingredient in the rejection of depressed persons by others, and "may appropriately be understood as an attempt to elicit social support from targets" [@segrin1994, p.
+657].
+Excessive reassurance seeking -- repeatedly requesting reassurance that one is lovable and worthy despite previous attempts by others to provide such reassurance -- is another factor implicated in the rejection of the depressed by others [@joiner1999; @JoinerMetalsky1995; @StarrDavila2008].
+
+Negative social responses to depression are widely interpreted as evidence of impaired social functioning in the depressed [@EvraireDozois2011; @GotlibLee1989; @HirschfeldEtAl2000], including by evolutionary theorists of depression [@nettle2004; @allen2006; @nesse2006; @myers2016].
+This interpretation is reinforced by the equally widespread view that depressed individuals have impaired, negative perceptions of themselves and their environments [@beck1963; @joiner2007; @nolen1991].
+Together with the costs of depression, such as suicide, these facts are the basis of the mainstream claim that depression is a psychopathology.
+
+In contrast to these views, we will argue that the depressed have suffered genuinely severe adversities and are therefore genuinely in need, but have conflicts with their social partners.
+In these circumstances, aversive but credible signals of need can evolve.
+
+## Depression is probably caused by genuine adversity
+
 All individuals suffer adversity, such as injury or loss of material or social resources, at some point in their lives, with over 70% of participants in a global survey reporting exposure to a traumatic event [@benjet2016].
@@
 
-Several theoretical models propose that depressed and suicidal individuals have inaccurate, negative perceptions of themselves and their environments [@beck1963; @joiner2007; @nolen1991].
-There is strong evidence, however, that most cases of depression are caused by genuinely severe negative life events [@Hammen2005; @Mazure1998; @devries2011; @ellsberg2008; @devries2013].
+Contrary to the view that the depressed have a distorted perception of their environment, there is strong evidence that most cases of depression are caused by genuinely severe negative life events, such as physical assault and death of a loved one [@Hammen2005; @Mazure1998; @devries2011; @ellsberg2008; @devries2013].
 Compared to non-depressed individuals, those with depression report about twice as many instances of negative events than non-depressed individuals [@Mazure1998] and more negative events than those with schizophrenia and bipolar depression across multiple studies [@Paykel1994].
@@
 Furthermore, twin studies have shown that one's history of negative events remains a strong predictor of major depression when controlling for genetic similarity, and that part of the heritability of depression stems from the heritability of negative events like divorce and family conflict [@KendlerBaker2007; @KendlerEtAl1999].
-For these and other reasons, most cases of depression are probably functional instances of psychological pain and not mental dysfunctions [@Hagen2003; @horwitz_loss_2007; @andrews2010; @SymeHagen2021; @dowrick2013; @frances2013].
-
-## Responses to depression and suicidal behavior
-
-For depression and suicide attempts to be worth the costs involved with signal creation, meaningful social support would be required [@Hagen2003; @SymeEtAl2016].
-Most studies examining responses to depression have been observational and focused on responses outside of changes in social support.
-In general, most report aversive responses and high levels of rejection towards the depressed, and depressed individuals are often linked to impaired social functioning [@EvraireDozois2011; @GotlibLee1989; @HirschfeldEtAl2000].
-One explanation for this is that depressed individuals engage in behaviors that drive others away.
-In line with this reasoning, both excessive reassurance seeking and negative feedback seeking, which often accompany depression, have been shown to elicit negative emotional responses from others and increase the chance of rejection from others [@JoinerMetalsky1995; @StarrDavila2008].
-Negative interactions are also seen in families as depressed children tend to report less support and more negative responses from parents than non-depressed children, although it has not been demonstrated that such interactions did not lead to depression in the first place [@MesserGross1995; @SchwartzEtAl2012].
-
-Despite being looked for less frequently, beneficial responses to depressed individuals are also reported.
-Depression has been associated with reduced likelihood of aggression within families [@hops1987; @dadds1992], including those already experiencing high levels of conflict [@SheeberEtAl2001].
-There is also limited evidence that depression can result in increased levels of support from others outside the family.
-For example, non-depressed individuals were shown to be more cooperative and exhibit more caretaking behavior towards their college depressed roommates over the course of their time living together [@HokansonEtAl1986].
-Likewise, a study examining responses to confederates trained to appear ‘depressed’, ‘anxious’, or ‘normal’ found that individuals were more likely to provide advice and support to ‘depressed’ individuals than ‘anxious’ or ‘normal’ individuals despite the confederate in the ‘depression’ condition being viewed more negatively than the other conditions and the ‘depression’ condition involving similar levels of distress compared to the ‘anxious’ condition [@stephens1987].
-
-Most studies examining responses to those who have survived suicide attempts have focused on stigmatization.
-In these studies, perceptions of survivors as being weak, selfish, mentally ill, and antisocial are all being commonly reported [@BatterhamEtAl2013; @TzengLipson2004], with stigmatization often being found within and outside one's social network [@FreyEtAl2016; @ScoccoEtAl2012].
-Despite this potential for stigmatization, increased social support and changes to important relationships have been reported to follow suicide attempts with some indication that these effects may hold long term [@Stengel1956].
-For example, a study of 100 women who survived suicide attempts found that individuals gained identifiable benefits through the attempt in 75 cases, with 41 individuals benefiting from reconciliations with others [@Lukianowicz1971].
-Unlike many Western countries, where suicide is often viewed as pathological [@Hidaka2012], members of traditional societies have been reported to view suicide attempts as cries for help rather than mental illness [@Shostak1981], with attempts having been described as ways of escaping unwanted marriage arrangements, persistent abuse, or a lack of support in obtaining mates by those engaging in the behavior and observers [@GutierrezdePinedaMuirden1948; @Hilger1957; @Karsten1935; @Tessmann1930; @Wilson1960].
-Although findings that individuals view suicide attempts as cries for help is not necessarily evidence for their ability to lead to beneficial responses, 30 out of 84 examples of suicidal behavior included in the HRAF resulted in positive changes for the survivor, despite suicide rarely if ever being the main topic [@SymeEtAl2016].
+For these and other reasons, most cases of depression are probably functional instances of psychological pain, i.e., the severe end of a spectrum of low mood, sadness, and grief, and not mental dysfunctions [@Hagen2003; @horwitz_loss_2007; @andrews2010; @SymeHagen2021; @dowrick2013; @frances2013].
 
@@
 
+<!-- Need to integrate this -->
+Most studies examining responses to those who have survived suicide attempts have focused on stigmatization.
+In these studies, perceptions of survivors as being weak, selfish, mentally ill, and antisocial are all being commonly reported [@BatterhamEtAl2013; @TzengLipson2004], with stigmatization often being found within and outside one's social network [@FreyEtAl2016; @ScoccoEtAl2012].
+Despite this potential for stigmatization, increased social support and changes to important relationships have been reported to follow suicide attempts with some indication that these effects may hold long term [@Stengel1956].
+For example, a study of 100 women who survived suicide attempts found that individuals gained identifiable benefits through the attempt in 75 cases, with 41 individuals benefiting from reconciliations with others [@Lukianowicz1971].
+Unlike many Western countries, where suicide is often viewed as pathological [@Hidaka2012], members of traditional societies have been reported to view suicide attempts as cries for help rather than mental illness [@Shostak1981], with attempts having been described as ways of escaping unwanted marriage arrangements, persistent abuse, or a lack of support in obtaining mates by those engaging in the behavior and observers [@GutierrezdePinedaMuirden1948; @Hilger1957; @Karsten1935; @Tessmann1930; @Wilson1960].
+Although findings that individuals view suicide attempts as cries for help is not necessarily evidence for their ability to lead to beneficial responses, 30 out of 84 examples of suicidal behavior included in the HRAF resulted in positive changes for the survivor, despite suicide rarely if ever being the main topic [@SymeEtAl2016].
+
 Some evolutionary theorists have questioned the bargaining model based on evidence that depression is aversive to social partners [@nettle2004; @allen2006; @nesse2006; @myers2016].
@@
 
+The prevailing view is that depression causes social rejection.
+The aim of this study was to test the hypothesis that when there are conflicts of interest, depressive and suicidal behaviors increase belief that victims of adversity are telling the truth and consequently increase willingness to help them.
+
+<!-- Beneficial responses to depressed individuals have also been reported, such as increased caretaking [@HokansonEtAl1986], more offers of advice and support [@stephens1987], and reduced aggression within families [@hops1987; @dadds1992; @SheeberEtAl2001].
+-->
+
 Most of the limited literature on social responses to depression and suicidality comprises observational studies of depressed individuals interacting with family, friends, or roommates [@hops1987; @dadds1992; @SheeberEtAl2001; @JoinerMetalsky1995; @StarrDavila2008].
@@
 In the bargaining framework, the willingness to delay credibly signals the valuation of current cooperative arrangements, with greater delays indicating lower valuations.
-The primary aim of this study was to examine responses to emotional signals that varied in the extent to which they reduced productivity or put future productivity at risk, which we refer to as costs, in an experimental vignette study in which a possible victim of adversity asks for help from the participant, but has incentives to exaggerate her need.
+Here, we investigated responses to emotional signals that varied in the extent to which they reduced productivity or put future productivity at risk, which we refer to as costs, in an experimental vignette study in which a possible victim of adversity asks for help from the participant, but has incentives to exaggerate her need.
 As signal cost increased, we predicted that participants would report (1) increased belief in the signaler's claims and (2) increased likelihood of providing help, with (3) the increased likelihood of providing help mediated by the increased belief in the signaler's need.

### 2021-06-09 Paper.rmd
* Edits to tie sections together * Added section on perceived mental illness * Two new effects plots on the effect of mental illness perceptions on belief and action

@@
 ---
-title: "Depression and suicidality as credible signals of need in social conflicts"
+title: "Depression and suicidality as evolved credible signals of need in social conflicts"
 author:
@@
 An alternative hypothesis grounded in evolutionary theory contends that depression and suicidality are honest signals of need in response to adversity that can increase support from reluctant others when there are conflicts of interest.
-To test this hypothesis, we examined responses to emotional signals in an experimental vignette study involving claims of substantial need in the presence of conflicts of interest and private information about the signaler's true level of need.
+To test this hypothesis, we examined responses to emotional signals in a preregistered experimental vignette study involving claims of substantial need in the presence of conflicts of interest and private information about the signaler's true level of need.
 In a sample of 1,240 participants recruited from Amazon Mechanical Turk, costlier signals like depression and suicidality resulted in greater perceptions of need, reduced perceptions of manipulativeness, and increased likelihood of support compared to simple verbal requests and crying without further symptoms.
 Additionally, as predicted, the effect of signaling on likelihood of support was largely mediated by the effect of signaling on participants' belief that the signaler was genuinely in need.
-Our results support the hypothesis that depression and suicidality, apparent human universals, are credible signals of need.
+Our results support the hypothesis that depression and suicidality, apparent human universals, are credible signals of need that elicit more support than verbal requests, sad expressions, and crying when there are conflicts of interest.
 
@@
 
-In a classic study, @Coyne1976 found that depression alienates others, a result that was subsequently confirmed in many other studies [@segrin1992; @segrin2000].
-In interactions with spouses, depressed individuals express anger and aggression, and make frequent demands for help [@segrin1994].
-Depressed individuals also self-disclose personally relevant negative issues at inappropriate times and they view such topics as more appropriate for discussion than do the non-depressed [@segrin2000].
+In a classic study, @Coyne1976 found that depression alienates social partners, a result that was subsequently confirmed in numerous studies [@segrin1992; @segrin2000].
+In interactions with spouses and others, depressed individuals express anger and aggression, make frequent demands for help, self-disclose personally relevant negative issues at inappropriate times, and view such topics as more appropriate for discussion than do the non-depressed [@segrin1994; @segrin2000].
 Such self-disclosures have been shown to be a key ingredient in the rejection of depressed persons by others, and "may appropriately be understood as an attempt to elicit social support from targets" [@segrin1994, p.
@@
 
-Negative social responses to depression are widely interpreted as evidence of impaired social functioning in the depressed [@EvraireDozois2011; @GotlibLee1989; @HirschfeldEtAl2000], including by evolutionary theorists of depression [@nettle2004; @allen2006; @nesse2006; @myers2016].
+Negative social responses to depression are widely interpreted as evidence of impaired social functioning in the depressed [@EvraireDozois2011; @GotlibLee1989; @HirschfeldEtAl2000; @hames2013; @gadassi2015; @kupferberg2016; @weightman2019].
 This interpretation is reinforced by the equally widespread view that depressed individuals have impaired, negative perceptions of themselves and their environments [@beck1963; @joiner2007; @nolen1991].
-Together with the costs of depression, such as suicide, these facts are the basis of the mainstream claim that depression is a psychopathology.
-
-In contrast to these views, we will argue that the depressed have suffered genuinely severe adversities and are therefore genuinely in need, but have conflicts with their social partners.
-In these circumstances, aversive but credible signals of need can evolve.
-
-## Depression is probably caused by genuine adversity
+Together with the costs of depression, such as profound loss of interest in virtually activities and suicide, these facts are the basis of the mainstream claim that depression is a psychopathology.
+
+In contrast to these views, we will argue that the depressed have suffered genuinely severe adversities and are therefore genuinely in need, but often have conflicts with their social partners.
+In these circumstances, costly and putatively dysfunctional depressive behaviors can instead be understood as aversive but credible and adaptive signals of need that elicit more support than verbal requests, sad expressions, and crying when there are conflicts of interest.
+
+## Depression is caused by genuine adversity
 
@@
 Furthermore, twin studies have shown that one's history of negative events remains a strong predictor of major depression when controlling for genetic similarity, and that part of the heritability of depression stems from the heritability of negative events like divorce and family conflict [@KendlerBaker2007; @KendlerEtAl1999].
-For these and other reasons, most cases of depression are probably functional instances of psychological pain, i.e., the severe end of a spectrum of low mood, sadness, and grief, and not mental dysfunctions [@Hagen2003; @horwitz_loss_2007; @andrews2010; @SymeHagen2021; @dowrick2013; @frances2013].
+
+For these and other reasons, we and others argue that most cases of depression are probably functional instances of psychological pain, i.e., the severe end of a spectrum of adaptive low mood, sadness, and grief, and not mental dysfunctions [@Hagen2003; @horwitz_loss_2007; @andrews2010; @SymeHagen2021; @dowrick2013; @frances2013].
 
@@
 
-There is equally strong evidence that depression is closely associated with anger and conflict [@cassiello2016].
-Of the types of negative life events associated with depression, those which involve conflict tend to be more strongly associated with depression [@Hammen2005; @Mazure1998].
-Marital problems, bullying, and abusive relationships are all common risk factors for depression [@KendlerEtAl1995; @KendlerEtAl1999; @klomek2007; @klomek2019], with assault (both sexual and non-sexual), in particular, greatly increasing one's risk of depression [@KendlerEtAl1995; @KendlerEtAl1999].
-This holds true even in a small-scale, non-Western society: among the Tsimane, Amazonian horticulturalists, depression is also associated with conflict, particularly conflict involving non-kin [@StieglitzEtAl2015a].
+One might expect that victims of adversity who become depressed would receive positive responses from family, friends, colleagues, and perhaps even strangers.
+Indeed, beneficial responses to depressed individuals have also been reported, such as increased caretaking [@HokansonEtAl1986], more offers of advice and support [@stephens1987], and reduced aggression within families [@hops1987; @dadds1992; @SheeberEtAl2001].
+Why, though, would these positive responses often be accompanied by negative ones?
+
+The missing piece of the puzzle is that depression is closely associated with anger and conflict [@cassiello2016].
+Of the adversity risk factors for depression, those that involve conflict tend to be the strongest [@Hammen2005; @Mazure1998].
+Marital problems, bullying, and abusive relationships are all common risk factors for depression [@KendlerEtAl1995; @KendlerEtAl1999; @klomek2007; @klomek2019], with sexual and non-sexual assault, in particular, greatly increasing one's risk of depression [@KendlerEtAl1995; @KendlerEtAl1999].
+This holds true even in a small-scale, non-Western society: among the Tsimane, Amazonian horticulturalists, depression is also associated with conflict, especially conflict involving non-kin [@StieglitzEtAl2015a].
 See @SymeHagen2021 for a review of the association of depression with anger and conflict.
 
-Other notable risk factors, like loss of a loved one or severe or prolonged illness, might seem less related to conflict.
-In these situations, however, the fitness costs that stem from reduced access to resources could be mitigated with help from others [@SugiyamaSugiyama2003] who might not be able, or want, to provide more investment than they already are.
+Other notable depression risk factors, like loss of a loved one or severe or prolonged illness, might seem less related to conflict.
+In these situations, however, the fitness costs that stem from reduced access to resources could be mitigated with help from social partners [@SugiyamaSugiyama2003].
+However, social partners might not be able, or want, to provide more investment than they already are.
 Indeed, there is increasing evidence that loss of a loved one is often followed by increased family conflict [see @SymeHagen2021 for a brief review].
 Problems whose solutions require substantial investment or other changes on the part of social partners will therefore often involve social conflict even if they did not start that way [@Hagen2003].
-When there are severe conflicts of interest, individuals have incentives to deceive, so "cheap" signals of need, such as sad expressions and crying, might not be believed.
+
+Severe adversity, which often requires substantial help from social partners that they might be reluctant to provide, combined with social conflict, often of the he-said-she-said variety that could undermine victims' credibility, render "cheap" signals of need, such as sad expressions and crying, ineffective at increasing support.
+We argue next that some of the most costly and mysterious symptoms of depression -- profound loss of interest in virtually all activities and suicidality -- are *credible* and adaptive signals of need when there are conflicts of interest between victims of adversity and their social partners.
 
@@
 Depression is characterized, in part by a profound loss of interest in virtually all activities [@dsm5], a symptom that is probably responsible for a sharp reduction in productivity [for review, see @SymeHagen2021].
-Depression might therefore be a bargaining strategy for relatively powerless individuals in the wake of adversity and social conflict [@Hagen2003; @SymeHagen2021; see also @Watson:2002].
+Depression might therefore be an evolved bargaining strategy for relatively powerless individuals in the wake of adversity and social conflict [@Hagen2003; @SymeHagen2021; see also @Watson:2002].
 
@@
 
-Suicidal ideation is one of nine diagnostic criteria for a major depressive episode (MDE) [@dsm5], it is associated with depression across cultures [@haroz2017], and depression is a major risk factor for suicidal behavior [@hawton2013].
+Suicidal ideation is one of nine diagnostic criteria for a major depressive episode (MDE) [@dsm5] and is associated with depression across cultures [@haroz2017]; depression is a major risk factor for suicidal behavior [@hawton2013]; and suicidality has been invoked to justify grief-related depression symptoms as psychopathological [e.g., @pies2014].
+Theoretical models of depression must account for suicidality.
 
 Anthropology has long viewed suicidality as largely the result of social problems.
-Early in the field's history, anthropologists reported on suicide attempts and deaths in the small-scale societies in which they conducted their fieldwork.
+Early in the field's history, anthropologists reported on suicide attempts and deaths in the small-scale societies that serve as models for the types of societies in which humans evolved.
 Suicide, they found, was commonly a form of protest, revenge, and/or appeal [@firth1936; @Firth:1961; @Malinowski:1932; @niehaus2012].
@@
 
-Common to almost all theoretical and empirical investigations of suicide is a focus on *completed* suicides, i.e., suicide deaths.
+Common to almost all theoretical and empirical investigations of suicide in anthropology and other disciplines is a focus on *completed* suicides, i.e., suicide deaths.
 The vast majority of suicidal behavior, however, does not result in death.
@@
 
-In the bargaining framework, suicidality is conceptualized as putting all future contributions to cooperative endeavors with social partners at risk with some low but non-zero probability, credibly signaling low valuation of current circumstances [see @Rosenthal1993 for a game theory model of suicide attempts as costly signals].
+In the bargaining framework, suicidality is conceptualized as putting all future contributions to cooperative endeavors with social partners at risk with some low but non-zero probability, credibly signaling low valuation of current circumstances.
 On this view, most suicides deaths, especially in young, physically healthy individuals, would therefore be the inevitable consequence that some individuals lose this gamble.
-These and similar ideas [@andrews2006; @HagenEtAl2008; @nock2008; @Stengel1956] suggest that depression symptoms that put one's value to others at risk, such as loss of interest and suicidality, are credible signals of need.
+These and similar ideas [@andrews2006; @HagenEtAl2008; @nock2008; @Stengel1956; @Rosenthal1993] suggest that depression symptoms that put one's value to others at risk, such as loss of interest and suicidality, are credible signals of need.
 
 <!-- Need to integrate this -->
+As with depression, there are negative social responses to suicidal behavior.
 Most studies examining responses to those who have survived suicide attempts have focused on stigmatization.
-In these studies, perceptions of survivors as being weak, selfish, mentally ill, and antisocial are all being commonly reported [@BatterhamEtAl2013; @TzengLipson2004], with stigmatization often being found within and outside one's social network [@FreyEtAl2016; @ScoccoEtAl2012].
-Despite this potential for stigmatization, increased social support and changes to important relationships have been reported to follow suicide attempts with some indication that these effects may hold long term [@Stengel1956].
+In these studies, perceptions of survivors as being weak, selfish, mentally ill, and antisocial are commonly reported [@BatterhamEtAl2013; @TzengLipson2004], with stigmatization often being found within and outside one's social network [@FreyEtAl2016; @ScoccoEtAl2012].
+
+Despite this potential for stigmatization, increased social support and  beneficial changes to important relationships have been reported to follow suicide attempts with some indication that these effects may hold long term [@Stengel1956].
 For example, a study of 100 women who survived suicide attempts found that individuals gained identifiable benefits through the attempt in 75 cases, with 41 individuals benefiting from reconciliations with others [@Lukianowicz1971].
 Unlike many Western countries, where suicide is often viewed as pathological [@Hidaka2012], members of traditional societies have been reported to view suicide attempts as cries for help rather than mental illness [@Shostak1981], with attempts having been described as ways of escaping unwanted marriage arrangements, persistent abuse, or a lack of support in obtaining mates by those engaging in the behavior and observers [@GutierrezdePinedaMuirden1948; @Hilger1957; @Karsten1935; @Tessmann1930; @Wilson1960].
-Although findings that individuals view suicide attempts as cries for help is not necessarily evidence for their ability to lead to beneficial responses, 30 out of 84 examples of suicidal behavior included in the HRAF resulted in positive changes for the survivor, despite suicide rarely if ever being the main topic [@SymeEtAl2016].
-
-Some evolutionary theorists have questioned the bargaining model based on evidence that depression is aversive to social partners [@nettle2004; @allen2006; @nesse2006; @myers2016].
+Although findings that individuals view suicide attempts as cries for help is not necessarily evidence for their ability to lead to beneficial responses, 30 out of 84 examples of suicidal behavior included in the HRAF resulted in positive changes for the survivor [@SymeEtAl2016].
+
+<!-- Some evolutionary theorists have questioned the bargaining model based on evidence that depression is aversive to social partners [@nettle2004; @allen2006; @nesse2006; @myers2016].
 These critics overlooked the central role of *conflict* in the model.
+-->
+
 Anger is aversive to targeted social partners, yet it is probably an adaptation that exploits advantages in physical or social formidability to force concessions from them [@SellEtAl2009].
-Aversive responses to depressive bargaining are likewise expected throughout the process, with potential helpers signaling the costliness of providing support in turn.
-Importantly, as with anger, aversive responses to depression encourage concessions by interdependent social partners [@SymeHagen2021].
+Aversive responses to depressive and suicidal bargaining are likewise expected throughout the process, encouraging concessions by interdependent social partners, who in turn signal the costliness of increasing their support [@Hagen2003; @SymeHagen2021].
 
@@
 
-The prevailing view is that depression causes social rejection.
-The aim of this study was to test the hypothesis that when there are conflicts of interest, depressive and suicidal behaviors increase belief that victims of adversity are telling the truth and consequently increase willingness to help them.
-
-<!-- Beneficial responses to depressed individuals have also been reported, such as increased caretaking [@HokansonEtAl1986], more offers of advice and support [@stephens1987], and reduced aggression within families [@hops1987; @dadds1992; @SheeberEtAl2001].
--->
+The prevailing view is that depression involves impaired social abilities that lead to rejection by social partners [@Coyne1976; @joiner1999; @segrin2000; @hames2013; @weightman2019; @gadassi2015].
+The aim of this study was to test an alternative hypothesis that when there are conflicts of interest, depressive and suicidal behaviors benefit victims of adversity by increasing belief that they are telling the truth and consequently increasing willingness to help them.
 
@@
 See Figures \@ref(fig:mentallyillT1) and \@ref(fig:mentallyillT2).
+Perceived mental illness at T2 was associated with lower T2 Belief and Action in the US sample, but this effect was mainly evident in the *Verbal request* and *Crying* conditions.
+See Figures \@ref(fig:mentallyillbelief) and \@ref(fig:mentallyillaction).
 
@@
 In an exploratory analysis, costlier signals also decreased perceptions that the victim was manipulative.
-
-These effects were largest in the "brother-in-law" and "romantic partner" vignettes, both of which involved claims of assault against participants' imagined daughters, and smaller in the "basketball coach" and the "thwarted marriage" vignettes.
+These results provide evidence that, contrary to the influential "interpersonal" view that depressive behaviors are socially dysfunctional [reviewed in @hames2013], they in fact outperform verbal requests, sad expressions, and crying in providing benefits to victims when there are conflicts of interest.
+
+Signal effects were largest in the "brother-in-law" and "romantic partner" vignettes, both of which involved claims of assault against participants' imagined daughters, and smaller in the "basketball coach" and the "thwarted marriage" vignettes.
 The small effect in the "basketball coach" vignette might have been due to the lack of relatedness between participants and the victim (the star player), or how participants weighted the costs of suspending the coach vs.
@@
 Additionally, supporting the older daughter came at the cost of one's younger daughter, which may also help explain the relatively small signal effects.
-A final consideration is that data from the Indian sample appeared to be of lower quality, limiting our confidence in any of these interpretations (see limitations for more information).
+A final consideration is that data from the Indian sample appeared to be of lower quality, limiting our confidence in any of these interpretations (see the Limitations section for more information).
 
@@
 In contrast, both *Depression* conditions increased support, albeit to similar degrees.
-One potential reason for this is the increase in symptoms from mild depression to depression was not costly enough to result in a large effect, as the symptoms differed little in severity (e.g., grades dropping from As to Bs in *Mild depression* vs.
+One potential reason for the similar effects of the *Depression* conditions is the increase in costs from *Mild depression* to *Depression* was small (e.g., grades dropping from As to Bs in *Mild depression* vs.
 Cs in *Depression*).
-Such small changes may be less impactful in vignettes than in real-life, where the effects of signaling may increase in severity as they persist over a lengthy period of time.
+Such small changes may be less impactful in vignettes than in real-life, where the effects of signaling may increase in severity as they persist over time.
 
@@
 
+Contrary to our adaptationist hypothesis, and supporting the mainstream view that depression is a psychopathology, participants' perceptions that the victim was mentally ill increased with signal cost.
+However, there have been extensive media campaigns to convince the public that depression is a mental illness with the laudable goal of reducing stigma [@corrigan2012; @rusch2005].
+Even so, in the *Depression* conditions across vignettes, no more than 25% of participants thought the victim was mentally ill, and in the *Suicide attempt* condition the proportion of participants perceiving mental illness exceeded 50% only in the Basketball coach vignette.
+Although perceived mental illness was associated with somewhat lower *T2 Belief* and *T2 Action*, this effect was mainly evident in the *Verbal request* and *Crying* conditions.
+
 Finally, after the T3 evidence that the victim was telling the truth, likelihood of helping by the US participants increased to near ceiling, an effect that helped validate our vignettes.
@@
 
-Depression is costly and sometimes leads death by suicide.
-Our results suggest that these costs, which mainstream theories take as evidence of brain dysfunction [@SymeHagen2021], instead function to help victims of adversity elicit support when their true level of need is private information and they have conflicts with social partners.
-These findings align with real-world evidence that depression and suicide simultaneously elicit positive and negative responses from social partners [@SymeHagen2021].
-If the bargaining model is correct, depression and suicidality are important social problems, not medical ones [@syme2020].
+Depression is costly and sometimes leads to death by suicide.
+Our results suggest that these costs, which mainstream theories take as evidence of brain dysfunction, instead function to help victims of adversity elicit support when their true level of need is private information and they have conflicts with social partners.
+These findings align with real-world evidence that depression and suicide simultaneously elicit positive and negative responses from social partners [for review, see @SymeHagen2021].
+If the bargaining model is correct, depression and suicidality are important social problems, not medical ones [@Hagen2003; @syme2020].
 
@@
 
-In the MTurk study, participants read a vignette that put them in situations in which an imagined sister was requesting a loan of \$50,000 from the participant that was originally saved for the participant's imagined daughter's college education.
+In the MTurk pilot study, participants read a vignette that put them in situations in which an imagined sister was requesting a loan of \$50,000 from the participant that was originally saved for the participant's imagined daughter's college education.
 The sister claims the money is needed for medical treatment for her own child, but she has incentives to deceive.
@@
 ```{r mentallyillT2, fig.width=8, fig.cap="Proportion of participants in each condition who thought that the victim was mentally ill at T2, controlling for perceptions of mental illness at T1.
+Means estimated with a generalized linear regression model with the quasibinomial family, and displayed for participants who did not perceive mental illness at T1."}
+effectsPlots$m21plot + ggtitle('Time 2')
+```
+
+```{r mentallyillbelief, fig.width=8, fig.cap="Association of T2 Perceived Mental Illness (Yes/No) with T2 Belief in the US sample, by signal, controlling for T1 Perceived Mental Illness (Yes/No), T1 Belief, and vignette.
 Means estimated with a generalized linear regression model with the quasibinomial family."}
-effectsPlots$m21plot + ggtitle('Time 2')
+effectsPlots_US$m28plot +
+  xlab('\nPerceived mental illness') +
+  theme(axis.text.x = element_text(angle = 0, hjust=0.5))
+```
+
+```{r mentallyillaction, fig.width=8, fig.cap="Association of T2 Perceived Mental Illness (Yes/No) with T2 Action in the US sample, by signal, controlling for T1 Perceived Mental Illness (Yes/No), T1 Action, and vignette.
+Means estimated with a generalized linear regression model with the quasibinomial family."}
+effectsPlots_US$m29plot +
+  xlab('\nPerceived mental illness') +
+  theme(axis.text.x = element_text(angle = 0, hjust=0.5))
 ```

### 2021-06-09 _targets.R

@@ -69,7 +69,9 @@ list(
         PC1emotionT1 = -mpcaT1$x[,1],
         PC2emotionT1 = -mpcaT1$x[,2],
         PC1emotionT2 = -mpcaT2$x[,1],
-        PC2emotionT2 = -mpcaT2$x[,2]
+        PC2emotionT2 = -mpcaT2$x[,2],
+        T1MentallyIll_f = factor(T1MentallyIll, labels = c('No', 'Yes')),
+        T2MentallyIll_f = factor(T2MentallyIll, labels = c('No', 'Yes'))
       )
   ),
 
@@ -139,7 +141,9 @@ list(
       m22 = "T2Belief ~ T1Belief * signal + PC1emotionT1 + PC2emotionT1",
       m23 = "T2Action ~ T1Action * signal + PC1emotionT1 + PC2emotionT1",
       m26 = 'T3Action ~ T2Action * vignette',
-      m27 = 'T1MentallyIll ~ vignette'
+      m27 = 'T1MentallyIll ~ vignette',
+      m28 = 'T2Belief ~ T1Belief + T1MentallyIll_f + signal * T2MentallyIll_f + vignette',
+      m29 = 'T2Action ~ T1Action + T1MentallyIll_f + signal * T2MentallyIll_f + vignette'
     )
   ),
 

### 2021-06-11 R/functions.R
Effects plots for effect of T2 MentallyIll on T2 Belief and Action

@@ -181,7 +181,9 @@ effect_plots <- function(models, data){
     # m25plotSex = effect_plot(fit=models$m25, xvar='Sex', ylbl='T2 Action', data=data),
     m26plot = effect_plot(fit=models$m26, xvar='T2Action', by='vignette', ylbl='T3 Action', data=data) +
       theme(axis.text.x = element_text(angle = 0)) + xlab('\nT2 Action'),
-    m27plot = effect_plot(fit=models$m27, xvar='vignette', ylbl='T1 Mentally ill', data=data)
+    m27plot = effect_plot(fit=models$m27, xvar='vignette', ylbl='T1 Mentally ill', data=data),
+    m28plot = effect_plot(fit=models$m28, xvar='T2MentallyIll_f', by='signal', ylbl='T2 Belief', data=data),
+    m29plot = effect_plot(fit=models$m29, xvar='T2MentallyIll_f', by='signal', ylbl='T2 Action', data=data)
   )
 }
 
@@ -380,7 +382,7 @@ plot_ecdf <- function(d){
 plot_raw_data <- function(d, type){
   d <-
     d %>%
-    dplyr::select(MTurkID, signal, vignette, starts_with('T1'), starts_with('T2')) %>%
+    dplyr::select(MTurkID, signal, vignette, starts_with('T1'), starts_with('T2'), -ends_with('_f')) %>%
     pivot_longer(starts_with('T')) %>%
     separate(col=name, into = c('Time', 'Variable'), sep = 2) %>%
     dplyr::rename(

### 2021-06-11 Paper.rmd

@@
 
-```{r ecdf, fig.width=11, fig.height=6, fig.cap="Empirical cummulative distribution functions for Time 2 Belief (top) and Action (bottom) compared to their Time 1 baseline values (red), by signal and vignette.
+```{r ecdf, fig.width=11, fig.height=6, fig.cap="Empirical cumulative distribution functions for Time 2 Belief (top) and Action (bottom) compared to their Time 1 baseline values (red), by signal and vignette.
 Y-values indicate the fraction of all ratings equal to or less than a given x-value.
@@
 Bars are 95% CIs.
-For coefficents, p-values, and other statistics, see models m2 and m4 in Tables \\@ref(tab:regressiontables) and \\@ref(tab:anovatables).")}
+For coefficients, p-values, and other statistics, see models m2 and m4 in Tables \\@ref(tab:regressiontables) and \\@ref(tab:anovatables).")}
 # plot_beliefvignette <-

### 2021-06-11 Paper.rmd
Minor edits, new aversiveness subsection

@@
 On this view, most suicides deaths, especially in young, physically healthy individuals, would therefore be the inevitable consequence that some individuals lose this gamble.
-These and similar ideas [@andrews2006; @HagenEtAl2008; @nock2008; @Stengel1956; @Rosenthal1993] suggest that depression symptoms that put one's value to others at risk, such as loss of interest and suicidality, are credible signals of need.
 
@@
 
-Anger is aversive to targeted social partners, yet it is probably an adaptation that exploits advantages in physical or social formidability to force concessions from them [@SellEtAl2009].
-Aversive responses to depressive and suicidal bargaining are likewise expected throughout the process, encouraging concessions by interdependent social partners, who in turn signal the costliness of increasing their support [@Hagen2003; @SymeHagen2021].
+## Aversiveness is a feature of depression, not a bug
+
+Under the bargaining model, aversive responses to depressive and suicidal bargaining are expected throughout the process, encouraging beneficial concessions by interdependent social partners with whom one is in conflict, who in turn signal the costliness of increasing their support [@Hagen2003; @SymeHagen2021].
+This predicted pattern is quite similar to anger, which is aversive to targeted social partners, yet is probably an adaptation that exploits advantages in physical or social formidability to force beneficial concessions from them [@SellEtAl2009].
+
+In summary, we propose that depression symptoms that put one's value to others at risk, such as loss of interest and suicidality, are aversive but adaptive signals of need [for similar views, see @andrews2006; @HagenEtAl2008; @nock2008; @Stengel1956; @Rosenthal1993; @firth1936; @Firth:1961; @farberow1961].
 

### 2021-06-14 Paper.rmd
Added some edits to consider. Each is commented below the paragraph the change is recommended for.

@@
 
+<!-- have suffered genuinely severe forms of adversity and -->
+
 ## Depression is caused by genuine adversity
@@
 
+<!-- Compared to non-depressed individuals, those with depression report about twice as many negative events [@Mazure1998] and more negative events than those with schizophrenia and bipolar depression across multiple studies [@Paykel1994] -->
+
 For these and other reasons, we and others argue that most cases of depression are probably functional instances of psychological pain, i.e., the severe end of a spectrum of adaptive low mood, sadness, and grief, and not mental dysfunctions [@Hagen2003; @horwitz_loss_2007; @andrews2010; @SymeHagen2021; @dowrick2013; @frances2013].
@@
 
+<!-- Of the adversity-related risk factors for depression -->
+
 Other notable depression risk factors, like loss of a loved one or severe or prolonged illness, might seem less related to conflict.
@@
 
+<!-- Therefore, problems whose solutions require substantial investment or other changes on the part of social partners will therefore often involve social conflict even if they did not start that way [@Hagen2003].
+Indeed, there is increasing evidence that loss of a loved one is often followed by increased family conflict [see @SymeHagen2021 for a brief review].
+-->
+
 Severe adversity, which often requires substantial help from social partners that they might be reluctant to provide, combined with social conflict, often of the he-said-she-said variety that could undermine victims' credibility, render "cheap" signals of need, such as sad expressions and crying, ineffective at increasing support.
 We argue next that some of the most costly and mysterious symptoms of depression -- profound loss of interest in virtually all activities and suicidality -- are *credible* and adaptive signals of need when there are conflicts of interest between victims of adversity and their social partners.
+
+<!-- Due to the likelihood that the payoffs to deception increase with greater conflicts of interests, “cheap” signals of need, such as sad expressions and crying, may often not be believed when providing support is costly.
+We argue next that some of the most costly and mysterious symptoms of depression -- profound loss of interest in virtually all activities and suicidality -- are *credible* and adaptive signals of need when there are conflicts of interest between victims of adversity and their social partners.
+-->
 
@@
 
+<!-- With a cooperative species like our own, ubiquitous conflicts of interests means that there will always be disagreement over the levels of investment in a cooperative endeavor and the division of the resulting benefits, even among closely related individuals.
+(return relatives line due to broader potential audience?) -->
+
 @Hagen2003 proposed that physical aggression and core depression symptoms like loss of interest in virtually all activities were complementary strategies to resolve conflicts in interdependent relationships.
@@
 
+<!-- As depression often involves a profound loss of interest in virtually all activities that can jeopardize one's productivity [@dsm5], it might therefore be an evolved bargaining strategy for relatively powerless individuals in the wake of adversity and social conflict [@Hagen2003; @SymeHagen2021; see also @Watson:2002].
+-->
+
 Bargaining models assume that delaying cooperation is costly so that there is an incentive to quickly agree on a division of benefits, and more so for those who highly value the fruits of the cooperative endeavor.
 In a classic non-cooperative game theory model of bargaining, @rubinstein1982 showed that two parties can come to an immediate agreement over division of benefits despite conflicts of interest if the parties' valuations of cooperation are not private information: in this case, each party knows exactly what division of benefits the other will accept, and can therefore make that offer immediately, avoiding the cost of delay.
+
+<!-- Bargaining models assume that delaying cooperation is costly so that there is an incentive to quickly agree on a division of benefits, especially for those who highly value the fruits of the cooperative endeavor.
+-->
 
@@
 
+<!-- If valuations are private information, however, costly delays  -->
+
 @Hagen2003 proposed that the substantial reduction in productivity that characterizes many cases of depression corresponds to a willingness to delay, and is therefore a credible signal of low valuation and need.
@@
 Theoretical models of depression must account for suicidality.
+
+<!-- Theoretical models of depression must account for suicidality.
+Suicidal ideation is one of nine diagnostic criteria for a major depressive episode (MDE) [@dsm5] and is associated with depression across cultures [@haroz2017]; depression is a major risk factor for suicidal behavior [@hawton2013]; and suicidality has been invoked to justify grief-related depression symptoms as psychopathological [e.g., @pies2014].
+-->
 
@@
 Some ethnographers emphasized suicide as a form of anger or social pressure [@Hezel:1987; @Giddens:1964], whereas others emphasized the powerlessness of suicide victims [@Counts:1980].
+
+<!-- Anthropology, in contrast, has long -->
 
@@
 
-<!-- Some evolutionary theorists have questioned the bargaining model based on evidence that depression is aversive to social partners [@nettle2004; @allen2006; @nesse2006; @myers2016].
-These critics overlooked the central role of *conflict* in the model.
--->
-
 ## Aversiveness is a feature of depression, not a bug
@@
 
-<!-- Compared to suicide, however, there are fewer anthropological investigations of depression [@kleinman1985] despite frequent reports of depression or depression-like behavior in a wide range of societies [@haroz2017; @liu2020] and the potential for cross-cultural research to help understand depressive states [@haroz2017].
+<!-- Among those who lack alternative options, depression symptoms that put one's value to others at risk, such as loss of interest and suicidality, may be one's best option to elicit support despite their aversiveness to others due to their role in reliable signaling need [for similar views, see @andrews2006; @HagenEtAl2008; @nock2008; @Stengel1956; @Rosenthal1993; @firth1936; @Firth:1961; @farberow1961].
 -->
-
-<!-- Durkheim's pioneering study of suicide [@durkheim1897] helped launch sociology as a quantitative discipline.
-Sociological investigations of suicide flourished through much of the 20th century, but were supplanted by medical and public health approaches as the biomedical model of mental health took hold in the late 1970's and early 1980's [@wray2011; @syme2020].
-The biomedical model tends to frame suicide as a problem with the individual, e.g., as one involving psychiatric disturbance, drug addiction, or stress sensitivity [@wray2011].
-This theoretical approach has made little progress: rates of suicide, which vary widely by country, have remained relatively flat in countries for which there are long-term data, such as the US, UK, Japan, and Sweden [@owidsuicide].
--->
-
-<!-- Evolutionary theories of depression tend to either ignore suicidality, or take it as evidence that depression is dysfunctional.
-Wakefield, for instance, who has devoted much of his career to arguing that most cases of depression are simply severe but normal sadness and grief, nevertheless takes suicidality to indicate pathology for some cases of depression [e.g., @wakefield2017].
-@nettle2004 argues that the costs of depression, including suicidality, outweigh any benefits, and therefore adaptationist models of depression are implausible.
-@gilbert2006 sees suicidality as an example of a dysregulated escape defense [for reviews of evolutionary theories of depression, see @Hagen2011].
--->
-
-<!-- As with suicide, research on depression since the 1980's has been dominated by biomedical approaches of limited success [@patten2016; @ormel2019].  -->
 

### 2021-06-14 Paper.rmd
Added a comment in parentheses. Minor change to line 123

@@
 
-<!-- Compared to non-depressed individuals, those with depression report about twice as many negative events [@Mazure1998] and more negative events than those with schizophrenia and bipolar depression across multiple studies [@Paykel1994] -->
+<!-- Compared to non-depressed individuals, those with depression report about twice as many negative events [@Mazure1998] and more negative events than those with schizophrenia and bipolar depression across multiple studies [@Paykel1994] (we repeat non-depressed individuals) -->
 
@@
 
-<!-- Due to the likelihood that the payoffs to deception increase with greater conflicts of interests, “cheap” signals of need, such as sad expressions and crying, may often not be believed when providing support is costly.
+<!-- Due to the likelihood that the payoffs to deceiving one's cooperative partners increase with greater conflicts of interests, “cheap” signals of need, such as sad expressions and crying, may often not be believed when providing support is costly.
 We argue next that some of the most costly and mysterious symptoms of depression -- profound loss of interest in virtually all activities and suicidality -- are *credible* and adaptive signals of need when there are conflicts of interest between victims of adversity and their social partners.

### 2021-06-14 Paper.rmd
Cited del giudice

--- 2021-06-11 Paper.rmd
@@
 All individuals suffer adversity, such as injury or loss of material or social resources, at some point in their lives, with over 70% of participants in a global survey reporting exposure to a traumatic event [@benjet2016].
-Psychological pain, such as sadness and low mood, probably evolved to motivate victims of adversity to shift their attention to the causes of adversity so as to mitigate its negative fitness consequences and to learn to avoid future such adverse events [@thornhill1989; @andrews2010; @Nesse1990].
+Psychological pain, such as sadness and low mood, probably evolved to motivate victims of adversity to shift their attention to the causes of adversity so as to mitigate its negative fitness consequences and to learn to avoid future such adverse events [@thornhill1989; @andrews2010; @Nesse1990; @delgiudice2018].
 Over human evolution, social partners could have often helped victims, and therefore signals of psychological pain, such as sad expressions and crying, probably evolved to indicate need [e.g., @darwin1872; @bowlby1980; @balsters2013].

### 2021-06-14 Paper.rmd
Minor edits

--- 2021-06-14 Paper.rmd
@@
 
-In contrast to these views, we will argue that the depressed have suffered genuinely severe adversities and are therefore genuinely in need, but often have conflicts with their social partners.
+In contrast to these views, we will argue that the depressed have suffered genuinely severe forms of adversity and are therefore genuinely in need, but often have conflicts with their social partners.
 In these circumstances, costly and putatively dysfunctional depressive behaviors can instead be understood as aversive but credible and adaptive signals of need that elicit more support than verbal requests, sad expressions, and crying when there are conflicts of interest.
@@
 Contrary to the view that the depressed have a distorted perception of their environment, there is strong evidence that most cases of depression are caused by genuinely severe negative life events, such as physical assault and death of a loved one [@Hammen2005; @Mazure1998; @devries2011; @ellsberg2008; @devries2013].
-Compared to non-depressed individuals, those with depression report about twice as many instances of negative events than non-depressed individuals [@Mazure1998] and more negative events than those with schizophrenia and bipolar depression across multiple studies [@Paykel1994].
+Compared to non-depressed individuals, those with depression report about twice as many negative events [@Mazure1998] and more negative events than those with schizophrenia and bipolar depression across multiple studies [@Paykel1994].
 Longitudinal studies indicate that depression onsets soon after a negative event [@lewinsohn1988; @KendlerEtAl1999; @rich2005; @han2019; @sen2010] or coincides with periods where adversity is likely to increase prior to it [e.g., depression starting before a divorce rather than after, @blekesaune2008; @metsa2013; @rosenstrom2017].
@@
 The missing piece of the puzzle is that depression is closely associated with anger and conflict [@cassiello2016].
-Of the adversity risk factors for depression, those that involve conflict tend to be the strongest [@Hammen2005; @Mazure1998].
+Of the adversity-related risk factors for depression, those that involve conflict tend to be the strongest [@Hammen2005; @Mazure1998].
 Marital problems, bullying, and abusive relationships are all common risk factors for depression [@KendlerEtAl1995; @KendlerEtAl1999; @klomek2007; @klomek2019], with sexual and non-sexual assault, in particular, greatly increasing one's risk of depression [@KendlerEtAl1995; @KendlerEtAl1999].
@@
 However, social partners might not be able, or want, to provide more investment than they already are.
+Therefore, problems whose solutions require substantial investment or other changes on the part of social partners will often involve social conflict even if they did not start that way [@Hagen2003].
 Indeed, there is increasing evidence that loss of a loved one is often followed by increased family conflict [see @SymeHagen2021 for a brief review].
-Problems whose solutions require substantial investment or other changes on the part of social partners will therefore often involve social conflict even if they did not start that way [@Hagen2003].
-
-Severe adversity, which often requires substantial help from social partners that they might be reluctant to provide, combined with social conflict, often of the he-said-she-said variety that could undermine victims' credibility, render "cheap" signals of need, such as sad expressions and crying, ineffective at increasing support.
-We argue next that some of the most costly and mysterious symptoms of depression -- profound loss of interest in virtually all activities and suicidality -- are *credible* and adaptive signals of need when there are conflicts of interest between victims of adversity and their social partners.
+
+When need is private information and there are conflicts with social partners, “cheap” signals of need, such as sad expressions and crying, may often not be believed when providing support is costly.
+We argue next that in this common situation, some of the most harmful and mysterious symptoms of depression -- profound loss of interest in virtually all activities and suicidality -- serve as *credible* and adaptive signals of need.
 
@@
 
-With a cooperative species like our own, ubiquitous conflicts of interests means that there will always be disagreement over the levels of investment in a cooperative endeavor and the division of the resulting benefits.
+With a cooperative species like our own, ubiquitous conflicts of interests means that there will always be disagreement over the levels of investment in a cooperative endeavor and the division of the resulting benefits, even among closely related individuals.
 According to partner choice models, individuals who are dissatisfied with the terms of cooperation can switch partners [@hammerstein2016], e.g., workers unhappy with their pay can look for a better job.
@@
 An individual with monopoly power over the benefits she contributes to a critical cooperative endeavor can withhold those benefits, or put them at risk, until her partners change their behaviors in ways that benefit her.
-Depression is characterized, in part by a profound loss of interest in virtually all activities [@dsm5], a symptom that is probably responsible for a sharp reduction in productivity [for review, see @SymeHagen2021].
-Depression might therefore be an evolved bargaining strategy for relatively powerless individuals in the wake of adversity and social conflict [@Hagen2003; @SymeHagen2021; see also @Watson:2002].
-
-Bargaining models assume that delaying cooperation is costly so that there is an incentive to quickly agree on a division of benefits, and more so for those who highly value the fruits of the cooperative endeavor.
+As depression often involves a profound loss of interest in virtually all activities that can jeopardize one's productivity [@dsm5], it might therefore be an evolved bargaining strategy for relatively powerless individuals in the wake of adversity and social conflict [@Hagen2003; @SymeHagen2021; see also @Watson:2002].
+
+Bargaining models assume that delaying cooperation is costly so that there is an incentive to quickly agree on a division of benefits, especially for those who highly value the fruits of the cooperative endeavor.
 In a classic non-cooperative game theory model of bargaining, @rubinstein1982 showed that two parties can come to an immediate agreement over division of benefits despite conflicts of interest if the parties' valuations of cooperation are not private information: in this case, each party knows exactly what division of benefits the other will accept, and can therefore make that offer immediately, avoiding the cost of delay.
 
-If valuations are private information, however, then costly delays might be unavoidable because each party has an incentive to request more than their actual valuation, and to reject the likely inflated requests from partners, leading to multiple rounds of bargaining.
+If valuations are private information, however, costly delays might be unavoidable because each party has an incentive to request more than their actual valuation, and to reject the likely inflated requests from partners, leading to multiple rounds of bargaining.
 Models of bargaining with private information have a close relationship to models of credible signaling.
@@
 
-Suicidal ideation is one of nine diagnostic criteria for a major depressive episode (MDE) [@dsm5] and is associated with depression across cultures [@haroz2017]; depression is a major risk factor for suicidal behavior [@hawton2013]; and suicidality has been invoked to justify grief-related depression symptoms as psychopathological [e.g., @pies2014].
-Theoretical models of depression must account for suicidality.
-
-Anthropology has long viewed suicidality as largely the result of social problems.
+Theoretical models of depression must account for suicidality.Suicidal ideation is one of nine diagnostic criteria for a major depressive episode (MDE) [@dsm5] and is associated with depression across cultures [@haroz2017]; depression is a major risk factor for suicidal behavior [@hawton2013]; and suicidality has been invoked to justify grief-related depression symptoms as psychopathological [e.g., @pies2014].
+
+Anthropology, in contrast, has long viewed suicidality as largely the result of social problems.
 Early in the field's history, anthropologists reported on suicide attempts and deaths in the small-scale societies that serve as models for the types of societies in which humans evolved.
@@
 
-<!-- Need to integrate this -->
 As with depression, there are negative social responses to suicidal behavior.
@@
 
-In summary, we propose that depression symptoms that put one's value to others at risk, such as loss of interest and suicidality, are aversive but adaptive signals of need [for similar views, see @andrews2006; @HagenEtAl2008; @nock2008; @Stengel1956; @Rosenthal1993; @firth1936; @Firth:1961; @farberow1961].
-
-<!-- Compared to suicide, however, there are fewer anthropological investigations of depression [@kleinman1985] despite frequent reports of depression or depression-like behavior in a wide range of societies [@haroz2017; @liu2020] and the potential for cross-cultural research to help understand depressive states [@haroz2017].
--->
-
-<!-- Durkheim's pioneering study of suicide [@durkheim1897] helped launch sociology as a quantitative discipline.
-Sociological investigations of suicide flourished through much of the 20th century, but were supplanted by medical and public health approaches as the biomedical model of mental health took hold in the late 1970's and early 1980's [@wray2011; @syme2020].
-The biomedical model tends to frame suicide as a problem with the individual, e.g., as one involving psychiatric disturbance, drug addiction, or stress sensitivity [@wray2011].
-This theoretical approach has made little progress: rates of suicide, which vary widely by country, have remained relatively flat in countries for which there are long-term data, such as the US, UK, Japan, and Sweden [@owidsuicide].
--->
-
-<!-- Evolutionary theories of depression tend to either ignore suicidality, or take it as evidence that depression is dysfunctional.
-Wakefield, for instance, who has devoted much of his career to arguing that most cases of depression are simply severe but normal sadness and grief, nevertheless takes suicidality to indicate pathology for some cases of depression [e.g., @wakefield2017].
-@nettle2004 argues that the costs of depression, including suicidality, outweigh any benefits, and therefore adaptationist models of depression are implausible.
-@gilbert2006 sees suicidality as an example of a dysregulated escape defense [for reviews of evolutionary theories of depression, see @Hagen2011].
--->
-
-<!-- As with suicide, research on depression since the 1980's has been dominated by biomedical approaches of limited success [@patten2016; @ormel2019].  -->
+We argue that among those who lack better options, aversive depression symptoms that put one's value to others at risk, such as loss of interest and suicidality, credibly signal low valuation of the current efforts of social partners and motivate them to provide more support so as to end the aversive depressive behaviors [for similar views, see @andrews2006; @HagenEtAl2008; @nock2008; @Stengel1956; @Rosenthal1993; @firth1936; @Firth:1961; @farberow1961].
 
@@
 As signal cost increased, we predicted that participants would report (1) increased belief in the signaler's claims and (2) increased likelihood of providing help, with (3) the increased likelihood of providing help mediated by the increased belief in the signaler's need.
-
-<!-- A secondary aim was to investigate a scenario that is common in traditional societies but uncommon in Western societies -- arranged marriages -- where conflicts between parents and offspring often result in depression and suicidality [@SymeEtAl2016] -->
 

### 2021-06-22 Paper.rmd
Final Kristen edits and spellcheck

@@
   affiliation: Department of Anthropology, Washington State University
-- name: Kai Adams
+- name: Kai H. Adams
   affiliation: UC Berkeley Haas School of Business
@@
 Signal effects were largest in the "brother-in-law" and "romantic partner" vignettes, both of which involved claims of assault against participants' imagined daughters, and smaller in the "basketball coach" and the "thwarted marriage" vignettes.
-The small effect in the "basketball coach" vignette might have been due to the lack of relatedness between participants and the victim (the star player), or how participants weighted the costs of suspending the coach vs.
-punishing a potentially innocent person.
+The smaller effect in the "basketball coach" vignette might have been because in the role of athletic director, participants did not value their relationship with the star player as much as we anticipated (e.g., due to lack of relatedness), or how participants weighted the costs of suspending the coach vs.
+punishing a potentially innocent person [for discussion of suicidal signaling to kin vs.
+nonkin, see @SymeHagen2018].
 The US vignettes also had different degrees of evidence *against* the victim beyond just denial by the accused, ranging from strong evidence in the basketball coach vignette (a negative police report) to moderate evidence in the romantic partner vignette (no physical injuries) to weak evidence in the brother-in-law vignette (nothing beyond denial by the brother-in-law), raising the possibility that credible signals are more effective when negative evidence is lacking (Dylan Tweed, personal communication).
@@
 This study was funded through a Washington State University, Vancouver Research Mini Grant.
-We thank Anne Pisor, Darcy Bird, and members of the Hagen lab group for numerous helpful comments.
-We also thank XX and YY [pending permission to acknowledge] for feedback on the Thwarted marriage vignette.
+We thank Anne Pisor, Caroline Smith, Tiffany Alvarez, Aaron Lightner, Luke Martello, and Darcy Bird for numerous helpful comments.
+We thank Arpita Sinha for feedback on the Thwarted marriage vignette.
 
@@
 
-We also preregisterd models with an interaction term, for reasons explained in the main text:
+We also preregistered models with an interaction term, for reasons explained in the main text:
 

### 2021-06-22 Paper.rmd
Added a space after a period

@@
 
-Theoretical models of depression must account for suicidality.Suicidal ideation is one of nine diagnostic criteria for a major depressive episode (MDE) [@dsm5] and is associated with depression across cultures [@haroz2017]; depression is a major risk factor for suicidal behavior [@hawton2013]; and suicidality has been invoked to justify grief-related depression symptoms as psychopathological [e.g., @pies2014].
+Theoretical models of depression must account for suicidality.
+Suicidal ideation is one of nine diagnostic criteria for a major depressive episode (MDE) [@dsm5] and is associated with depression across cultures [@haroz2017]; depression is a major risk factor for suicidal behavior [@hawton2013]; and suicidality has been invoked to justify grief-related depression symptoms as psychopathological [e.g., @pies2014].
 

### 2022-01-20 Paper.rmd
Responded to reviewer comments

@@
 always_allow_html: true
+base_url: https://michaelrgaffney.github.io
+preview: Figure4.png
+twitter:
+  creator: "@ed_hagen"
 output:
-  bookdown::html_document2:
+  distill::distill_article:
+    self_contained: true
+    number_sections: false
     toc: true
     toc_float: true
-    number_sections: false
     css: style.css
@@
 
-In a classic study, @Coyne1976 found that depression alienates social partners, a result that was subsequently confirmed in numerous studies [@segrin1992; @segrin2000].
-In interactions with spouses and others, depressed individuals express anger and aggression, make frequent demands for help, self-disclose personally relevant negative issues at inappropriate times, and view such topics as more appropriate for discussion than do the non-depressed [@segrin1994; @segrin2000].
+In a classic study, @Coyne1976 found that depression alienates others, a result that was subsequently confirmed in numerous studies [@segrin1992; @segrin2000].
+(For DSM-5 depression symptoms, see Table \@ref(tab:dsmdepression).) In interactions with spouses and others, depressed individuals express anger and aggression, make frequent demands for help, self-disclose personally relevant negative issues at inappropriate times, and view such topics as more appropriate for discussion than do the non-depressed [@segrin1994; @segrin2000].
 Such self-disclosures have been shown to be a key ingredient in the rejection of depressed persons by others, and "may appropriately be understood as an attempt to elicit social support from targets" [@segrin1994, p.
@@
 
+```{r dsmdepression}
+dsm <- tibble(
+  Symptom = c(
+    "1. Depressed mood—indicated by subjective report or observation by others (in children and adolescents, can be irritable mood).", 
+    "2. Loss of interest or pleasure in almost all activities—indicated by subjective report or observation by others.", 
+    "3. Significant (more than 5 percent in a month) unintentional weight loss/gain or decrease/increase in appetite (in children, failure to make expected weight gains).", 
+    "4. Sleep disturbance (insomnia or hypersomnia).", 
+    "5. Psychomotor changes (agitation or retardation) severe enough to be observable by others.",
+    "6. Tiredness, fatigue, or low energy, or decreased efficiency with which routine tasks are completed.", 
+    "7. A sense of worthlessness or excessive, inappropriate, or delusional guilt (not merely self-reproach or guilt about being sick).", 
+    "8. Impaired ability to think, concentrate, or make decisions—indicated by subjective report or observation by others.", 
+    "9. Recurrent thoughts of death (not just fear of dying), suicidal ideation, or suicide attempts."
+  )
+)
+knitr::kable(dsm, caption = "DSM-5 criteria for a Major Depressive Episode include five or more of the criteria, at least one of which is criteria 1 or 2.
+The symptom must persist most of the day, daily, for at least 2 weeks in a row.
+For more details, see @dsm5.")
+```
+
 Negative social responses to depression are widely interpreted as evidence of impaired social functioning in the depressed [@EvraireDozois2011; @GotlibLee1989; @HirschfeldEtAl2000; @hames2013; @gadassi2015; @kupferberg2016; @weightman2019].
 This interpretation is reinforced by the equally widespread view that depressed individuals have impaired, negative perceptions of themselves and their environments [@beck1963; @joiner2007; @nolen1991].
-Together with the costs of depression, such as profound loss of interest in virtually activities and suicide, these facts are the basis of the mainstream claim that depression is a psychopathology.
+Together with the costs of depression, such as profound loss of interest in virtually all activities and suicide, these facts are the basis of the mainstream claim that depression is a psychopathology.
 
@@
 In these circumstances, costly and putatively dysfunctional depressive behaviors can instead be understood as aversive but credible and adaptive signals of need that elicit more support than verbal requests, sad expressions, and crying when there are conflicts of interest.
+We follow @smith2003 in defining a signal as (p.
+15):
+
+>An act or structure that alters the behaviour of another organism, which evolved because of that effect, and which is effective because the receiver’s response has also evolved.
 
@@
 Psychological pain, such as sadness and low mood, probably evolved to motivate victims of adversity to shift their attention to the causes of adversity so as to mitigate its negative fitness consequences and to learn to avoid future such adverse events [@thornhill1989; @andrews2010; @Nesse1990; @delgiudice2018].
-Over human evolution, social partners could have often helped victims, and therefore signals of psychological pain, such as sad expressions and crying, probably evolved to indicate need [e.g., @darwin1872; @bowlby1980; @balsters2013].
+Over human evolution, social partners could have often helped victims, and therefore signals of psychological pain, such as sad expressions and crying, probably evolved to indicate need [e.g., @darwin1872; @bowlby1980; @balsters2013; @reed2017].
 
@@
 For these and other reasons, we and others argue that most cases of depression are probably functional instances of psychological pain, i.e., the severe end of a spectrum of adaptive low mood, sadness, and grief, and not mental dysfunctions [@Hagen2003; @horwitz_loss_2007; @andrews2010; @SymeHagen2021; @dowrick2013; @frances2013].
+For reviews of other evolutionary theories of depression, see @Hagen2011 and @durisko2015.
 
@@
 When need is private information and there are conflicts with social partners, “cheap” signals of need, such as sad expressions and crying, may often not be believed when providing support is costly.
-We argue next that in this common situation, some of the most harmful and mysterious symptoms of depression -- profound loss of interest in virtually all activities and suicidality -- serve as *credible* and adaptive signals of need.
-
-## Bargaining: Credibly signaling need under conflict
+We argue next that in this common situation, some of the most harmful and mysterious symptoms of depression -- profound loss of interest in virtually all activities, and suicidal ideation and behaviors -- serve as *credible* and adaptive signals of need.
+
+## Bargaining: Credibly signaling need during conflicts
 
@@
 
-If valuations are private information, however, costly delays might be unavoidable because each party has an incentive to request more than their actual valuation, and to reject the likely inflated requests from partners, leading to multiple rounds of bargaining.
+If valuations are private information, however, costly delays might be unavoidable because each party has an incentive to deceptively request more than their actual valuation, and to reject the likely inflated requests from partners, leading to multiple rounds of bargaining.
 Models of bargaining with private information have a close relationship to models of credible signaling.
+When there are conflicts of interest, there are incentives to send deceptive signals.
+A *credible* signal is one that the receiver can believe despite the signaler's incentive to deceive.
 A willingness to delay (i.e., refuse offers) credibly reveals one's low valuation of the endeavor, and therefore genuine need -- the benefit of waiting for a better offer outweighs the low cost of delay.
 Eagerness to reach a deal, on the other hand, credibly reveals a high valuation -- the benefit of waiting for a better offer does not outweigh the higher cost of delay.
-Once valuations are known, the game reduces to the one in @rubinstein1982, and the parties can reach an agreement on the division of benefits [@KennanWilson1993].
+Once valuations are known, the game reduces to the one analyzed by @rubinstein1982, and the parties can reach an agreement on the division of benefits [@KennanWilson1993].
 Delays also typically require that additional factors come into play [@feinberg2005 and references therein].
 
-@Hagen2003 proposed that the substantial reduction in productivity that characterizes many cases of depression corresponds to a willingness to delay, and is therefore a credible signal of low valuation and need.
-In other words, reduced productivity is relatively less costly for those whose efforts are currently not yielding many fitness benefits than for those whose efforts are yielding substantial benefits.
+@Hagen2003 proposed that whereas crying is a "cheap", mostly short-term signal of need that might be deceptive (e.g., crocodile tears), the substantial, long-term reduction in productivity that characterizes many cases of depression corresponds to a willingness to delay, and is therefore a credible signal of low valuation and need.
+In terms of classic costly signaling theory, reduced productivity is relatively less costly for signalers whose efforts are currently not yielding many fitness benefits (i.e., the needy) than it would be for signalers whose efforts are yielding substantial benefits (the non-needy).
+Hence, the benefits of signaling outweigh the costs for needy individuals, who therefore send the signal, whereas the costs outweigh the benefits for non-needy individuals, who therefore do not send the signal.
 
@@
 Theoretical models of depression must account for suicidality.
-Suicidal ideation is one of nine diagnostic criteria for a major depressive episode (MDE) [@dsm5] and is associated with depression across cultures [@haroz2017]; depression is a major risk factor for suicidal behavior [@hawton2013]; and suicidality has been invoked to justify grief-related depression symptoms as psychopathological [e.g., @pies2014].
+Suicidal ideation is one of nine diagnostic criteria for a major depressive episode (MDE) [@dsm5] and is associated with depression across cultures [@haroz2017]; depression is a major risk factor for suicidal behavior [@hawton2013]; and suicidality is a major justification for the claim that depression is a brain dysfunction [e.g., @pies2014].
 
@@
 
-In the bargaining framework, suicidality is conceptualized as putting all future contributions to cooperative endeavors with social partners at risk with some low but non-zero probability, credibly signaling low valuation of current circumstances.
+In the bargaining framework, suicidality, and perhaps also non-suicidal self-injury [@HagenEtAl2008], is conceptualized as putting all future contributions to cooperative endeavors with social partners at risk with some low but non-zero probability, credibly signaling low valuation of current circumstances.
 On this view, most suicides deaths, especially in young, physically healthy individuals, would therefore be the inevitable consequence that some individuals lose this gamble.
@@
 
-In the bargaining framework, the willingness to delay credibly signals the valuation of current cooperative arrangements, with greater delays indicating lower valuations.
+In the bargaining framework, one's "willingness to delay" is a credible signal of one's valuation of current cooperative arrangements, with a greater willingness to delay indicating a lower valuation.
 Here, we investigated responses to emotional signals that varied in the extent to which they reduced productivity or put future productivity at risk, which we refer to as costs, in an experimental vignette study in which a possible victim of adversity asks for help from the participant, but has incentives to exaggerate her need.
@@
 As predicted, believability and willingness to help in this condition were dramatically lower than in any other condition (see Figure \@ref(fig:piloteffects)), ruling out this alternative explanation.
-We therefore did not include the schizophrenic condition in the current study.
+We consequently did not include the schizophrenic condition in the current study.
 See the SI for more details on the pilot studies.
+
+A second lesson was that participants in the pilot study tended to believe the fictional victim prior to her signaling need, which made it difficult to determine if the signals increased her believability.
+The vignettes for this study were therefore written to undermine the victim's credibility by making her seem manipulative at T1.
 
@@
 All participants were over 18, located in the United States or India, and had high quality MTurk metrics [completed at least 100 HITs with a HIT approval rate of over 98%, @kennedy2020].
-Participants were excluded from the study if (1) they read the vignette too quickly (one-third of the time it took MG to read it), and (2) they failed clearly labeled attentions checks.
+Participants were excluded from the study if (1) they read the vignette too quickly (one-third of the time it took MG to read it), and (2) they failed clearly labeled attention checks.
 The first attention check was shown immediately after the consent form and provided participants with a random word and asked them to enter the vowels in the order in which they are found in the word.
@@
 
-Four vignettes were used in this study that involved (1) a female's claim of severe adversity that was private information, (2) conflicts of interest between the victim and the participant that would undermine the believability of her claims, and (3) her emotional signals.
-The vignette scenarios involved potentially severe types of adversity, such as sexual and non-sexual assault and thwarted marriage, that often precede cases of depression and suicidality in the ethnographic and clinical record.
+Four vignettes were used in this study that involved (1) a female's claim of severe adversity that was private information, (2) conflicts of interest between the victim and the participant that would undermine the believability of her claims and make her seem manipulative, and (3) her emotional signals.
+The vignette scenarios involved potentially severe types of adversity, such as sexual and non-sexual assault and thwarted marriage, that often precede cases of depression and suicidality in the ethnographic and clinical record [@KendlerEtAl1995; @KendlerEtAl1999; @SymeEtAl2016; @brown1986].
 See Table \@ref(tab:design).
@@
 
-At Time 1 (T1) participants in the US sample were randomly assigned to either the "basketball coach," "romantic partner," or "brother-in-law" vignettes, and the Indian sample was assigned to the Thwarted marriage vignette.
+At Time 1 (T1) participants in the US sample were randomly assigned to either the "basketball coach," "romantic partner," or "brother-in-law" vignettes, and the Indian sample was assigned to the "thwarted marriage" vignette.
 
@@
 **Brother-in-law vignette**: Participants were asked to imagine that they let their sister, brother-in-law, and niece move in with them after their sister's family lost their house in a fire.
-During this time, the participant's 15 year old daughter becomes jealous of her cousin, who appears to be a social competitor.
-A few weeks after claiming her cousin was trying to steal her boyfriend, the participant's daughter accuses her uncle of sexually assaulting her.
+During this time, the participant's 15 year old daughter becomes jealous of the niece, who appears to be a social competitor.
+A few weeks after claiming the niece was trying to steal her boyfriend, the participant's daughter accuses the brother-in-law of sexually assaulting her.
 
@@
 
-After reading the vignettes, participants rated their belief the signaler to be telling the truth (*T1 Belief*: 0-100) and the likelihood of them helping the signaler as requested (*T1 Action*: 0-100).
+After reading the vignettes, participants rated their belief that the signaler was telling the truth (*T1 Belief*: 0-100) and the likelihood of them helping the signaler, as requested (*T1 Action*: 0-100).
 With the thwarted marriage vignette we also asked how they would split the money they had saved for the dowry between their daughters (*T1 Divide*: 0-100; 50 is equal split).
@@
 We also asked which emotions participants felt the signaler was experiencing using a multiple choice question in which they could select as many options as they would like.
-This included emotions directly related to the signals (e.g., sad, depressed, and suicidal), states which suggest genuine need (traumatized and violated), states which suggest deception (e.g., deviousness or jealousy), and if the victim mentally ill.
+This included emotions directly related to the signals (e.g., sad, depressed, and suicidal), states which suggest genuine need (traumatized and violated), states which suggest deception (e.g., deviousness or jealousy), and if the victim was mentally ill.
 The complete list can be found in the SI.
@@
 
-We decided to use generalized linear regression models instead of OLS, however, for the following reasons.
+We decided to fit generalized linear regression models instead of OLS, however, for the following reasons.
 Our pre-test and post-test measures, *T1 & T2 Belief* and *T1 & T2 Action*, were all measured on a 0-100 point scale.
@@
 OLS linear regression models are not suitable for a closed and bounded distribution with so many values on the boundary because the residuals would not be normally distributed or have constant variance.
-Beta regression, a possible alternative, is only defined on the open interval, (0, 1), whereas our data had many values on the boundaries (a closed interval).
-A variant of beta regression, zero-one inflated beta, is inappropriate because it assumes different processes for the generation of data on the boundaries vs.
-the interior, and we had no reason to believe that our zeros and ones were generated by a different process than the rest of our observations.
-
-We therefore fit models of our two outcome variables with the preregistered OLS models (reported in the SI) and four variants of logistic regression (for which we rescaled the 0-100 outcomes to the continuous interval [0, 1]).
-First, we fit fractional regression models, introduced in a seminal paper by @papke1996 for continuous outcomes on the interval [0, 1], which, in brief, involve fitting a quasi-likelihood version of logistic regression with robust standard errors.
-This method is implemented in the `frm` package [@ramalho2019].
-Second, we fit GLM logistic regression models, computing 95% CI's via bootstrapping, using the `glmmboot` package created to model continuous outcomes on [0, 1] [@humphrey2020].
-Third, we fit GLM models with the quasibinomial family and logit link using the `glm` function in R stats library, which can fit continuous outcomes on [0, 1].
-Fourth, we computed robust standard errors and 95% confidence intervals from the quasibinomial models using the `sandwich` package [@zeileis2006].
-The estimated coefficients, standard errors, and confidence intervals produced by these four methods were *very* similar, and often identical (see Figure \@ref(fig:modelcompareplots).
-We therefore proceeded to fit and report models using `glm` with the quasibinomial family and logit link because model objects produced by this function are compatible with numerous other R packages for summarizing and plotting effects.
-
-Two of our four preregistered OLS regression models included interaction terms between signal and T1 *Belief* and *Action*, with the rationale that the signals might have reduced effect for individuals who indicate high levels of belief and helping at baseline.
-This rationale was less convincing for quasibinomial models using a logit link because the expected interaction -- reduced effect of signals in individuals with high baseline belief -- is inherent to logistic regression: the effect of a predictor on the outcome necessarily diminishes as the outcome approaches 1.
-Our theory does not predict an interaction beyond that already present in a logistic regression model, so we did not include an interaction term in the GLM models (but we still report OLS models with the interaction term).
+For further discussion, see the SI, where we also report the preregistered OLS models.
 
@@
 
-## Data availibility
+## Data availability
 
@@
 Dots are *T2 Belief* and *T2 Action* values; dot size = number of overlapping data points.
-For coefficents, p-values, and other statistics, see models m1 and m3 in Tables \\@ref(tab:regressiontables) and \\@ref(tab:anovatables).")}
+For coefficients, p-values, and other statistics, see models m1 and m3 in Tables \\@ref(tab:regressiontables) and \\@ref(tab:anovatables).")}
 # plot_beliefeffect <-
@@
 It is also possible the costliness of the situations presented in the vignettes differ by sex.
+This study is therefore most clearly demonstrated the effectiveness of costly signals of need by females, leaving open the question of the effectiveness of costly signals of need by males.
 
@@
 Depression is costly and sometimes leads to death by suicide.
-Our results suggest that these costs, which mainstream theories take as evidence of brain dysfunction, instead function to help victims of adversity elicit support when their true level of need is private information and they have conflicts with social partners.
-These findings align with real-world evidence that depression and suicide simultaneously elicit positive and negative responses from social partners [for review, see @SymeHagen2021].
-If the bargaining model is correct, depression and suicidality are important social problems, not medical ones [@Hagen2003; @syme2020].
+Our results indicate that these costs, which mainstream theories take as evidence of brain dysfunction, instead function to help victims of adversity elicit support when their true level of need is private information and they have conflicts with social partners.
+Our findings align with real-world evidence that depression and suicide simultaneously elicit positive and negative responses from social partners [for review, see @SymeHagen2021].
+In particular, sexual assault, which appeared in two of our four vignettes, is the biggest risk factor for a suicide attempt [@husky2013; @dworkin2017].
+Our results strongly suggest that a major reason for this pattern is that the victim’s social partners are skeptical that she is telling the truth.
+If the bargaining model is correct, depression and suicidality are “rational” responses to adversity and conflict [@Hagen2003; @syme2020].
 
@@
 
-### Measureing Beliefs and Actions
+### Measuring Beliefs and Actions
 
@@
 We preregistered four OLS linear regression models and one mediation model (<https://osf.io/g3s6n>).
+However, in the main text we report GLM models instead, for the following reasons.
+Our pre-test and post-test measures, *T1 & T2 Belief* and *T1 & T2 Action*, were all measured on a 0-100 point scale.
+A substantial number of participants rated their beliefs and actions as exactly 0 or exactly 100 at either T1 or T2.
+OLS linear regression models are not suitable for a closed and bounded distribution with so many values on the boundary because the residuals would not be normally distributed or have constant variance.
+Beta regression, a possible alternative, is only defined on the open interval, (0, 1), whereas our data had many values on the boundaries (a closed interval).
+A variant of beta regression, zero-one inflated beta, is inappropriate because it assumes different processes for the generation of data on the boundaries vs.
+the interior, and we had no reason to believe that our zeros and ones were generated by a different process than the rest of our observations.
+
+We therefore fit models of our two outcome variables with the preregistered OLS models (reported here in the SI) and four variants of logistic regression (for which we rescaled the 0-100 outcomes to the continuous interval [0, 1]).
+First, we fit fractional regression models, introduced in a seminal paper by @papke1996 for continuous outcomes on the interval [0, 1], which, in brief, involve fitting a quasi-likelihood version of logistic regression with robust standard errors.
+This method is implemented in the `frm` package [@ramalho2019].
+Second, we fit GLM logistic regression models, computing 95% CI's via bootstrapping, using the `glmmboot` package created to model continuous outcomes on [0, 1] [@humphrey2020].
+Third, we fit GLM models with the quasibinomial family and logit link using the `glm` function in R stats library, which can fit continuous outcomes on [0, 1].
+Fourth, we computed robust standard errors and 95% confidence intervals from the quasibinomial models using the `sandwich` package [@zeileis2006].
+The estimated coefficients, standard errors, and confidence intervals produced by these four methods were *very* similar, and often identical (see Figure \@ref(fig:modelcompareplots).
+We therefore proceeded to fit and report models in the main text using `glm` with the quasibinomial family and logit link because model objects produced by this function are compatible with numerous other R packages for summarizing and plotting effects.
+
+Two of our four preregistered OLS regression models included interaction terms between signal and T1 *Belief* and *Action*, with the rationale that the signals might have reduced effect for individuals who indicate high levels of belief and helping at baseline.
+This rationale was less convincing for quasibinomial models using a logit link because the expected interaction -- reduced effect of signals in individuals with high baseline belief -- is inherent to logistic regression: the effect of a predictor on the outcome necessarily diminishes as the outcome approaches 1.
+Our theory does not predict an interaction beyond that already present in a logistic regression model, so we did not include an interaction term in the GLM models (but we still report OLS models with the interaction term).
 
@@
 `r extract_eq(med1$model.y, intercept='beta', wrap=T)`
+
+Fitted model parameters are reported below.
 

### 2022-01-20 R/functions.R

@@ -76,7 +76,7 @@ T1Belief_Action_dist <- function(d){
     guides(colour = 'none', size = guide_legend(title = 'Overlapping\npoints')) +
     facet_wrap(~vignette) +
     theme_minimal(15) +
-    theme(axis.title.y = element_text(angle=0))
+    theme(axis.title.y = element_text(angle=0, vjust = 0.5))
 
 }
 
@@ -339,7 +339,7 @@ emotion_plot <- function(d){
     facet_wrap(~vignette) +
     labs(title = 'Change in mean emotions from T1 to T2', x = '\nLow mood', y = 'Manipulative\n') +
     theme_minimal(15) +
-    theme(axis.title.y = element_text(angle = 0))
+    theme(axis.title.y = element_text(angle = 0, vjust = 0.5))
 }
 
 plot_ecdf <- function(d){
